### 2018-10-11 2018_nips_vigil/vqa_mac.tex
Initial (content-free) version for NIPS-VIGIL

\documentclass{article}

%\usepackage{nips_2018}

% to compile a preprint version, e.g., for submission to arXiv, add
% add the [preprint] option:
% \usepackage[preprint]{nips_2018}

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{nips_2018}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2018}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{cite}
\usepackage[hyphens]{url}
\urlstyle{same}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true, % false: boxed links; true: colored links
	linkcolor=red, % color of internal links
	citecolor=green, % color of links to bibliography
	filecolor=magenta, % color of file links
	urlcolor=cyan, % color of external links
	bookmarksnumbered=true,
	hyperfootnotes=true,
	breaklinks
}

\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{On the performance of the MAC model}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  MI-Prometheus\thanks{%
  It's scary --- \href{https://www.imdb.com/title/tt1446714/}{and it's back!}} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch
  (3~picas) on both the left- and right-hand margins. Use 10~point
  type, with a vertical spacing (leading) of 11~points.  The word
  \textbf{Abstract} must be centered, bold, and in point size 12. Two
  line spaces precede the abstract. The abstract must be limited to
  one paragraph.
\end{abstract}

\section{Submission of papers to NIPS 2018}

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2018/}
\end{center}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NIPS 2018 must be prepared according to the
instructions presented here. Papers may only be up to eight pages
long, including figures. Additional pages \emph{containing only
  acknowledgments and/or cited references} are allowed. Papers that
exceed eight pages of content (ignoring references) will not be
reviewed, or in any other way considered for presentation at the
conference.

The margins in 2018 are the same as since 2007, which allow for
$\sim$$15\%$ more words in the paper compared to earlier years.

Authors are required to use the NIPS \LaTeX{} style files obtainable
at the NIPS website as indicated below. Please make sure you use the
current files and not previous versions. Tweaking the style files may
be grounds for rejection.

\subsection{Retrieval of style files}

The style files for NIPS and other conference information are
available on the World Wide Web at
\begin{center}
  \url{http://www.nips.cc/}
\end{center}
The file \verb+nips_2018.pdf+ contains these instructions and
illustrates the various formatting requirements your NIPS paper must
satisfy.

The only supported style file for NIPS 2018 is \verb+nips_2018.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
  2.09, Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+,
which creates a camera-ready copy, \verb+preprint+, which creates a
preprint for submission to, e.g., arXiv, and \verb+nonatbib+, which will
not load the \verb+natbib+ package for you in case of package clash.

\paragraph{New preprint option for 2018}
If you wish to post a preprint of your work online, e.g., on arXiv,
using the NIPS style, please use the \verb+preprint+ option. This will
create a nonanonymized version of your work with the text
``Preprint. Work in progress.''  in the footer. This version may be
distributed as you see fit. Please \textbf{do not} use the
\verb+final+ option, which should \textbf{only} be used for papers
accepted to NIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper
as they will be removed during generation of camera-ready copies.

The file \verb+nips_2018.tex+ may be used as a ``shell'' for writing
your paper. All you have to do is replace the author, title, abstract,
and text of the paper with your own.

The formatting instructions contained in these style files are
summarized in Sections \ref{gen_inst}, \ref{headings}, and
\ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas)
wide and 9~inches (54~picas) long. The left margin is 1.5~inch
(9~picas).  Use 10~point type with a vertical spacing (leading) of
11~points.  Times New Roman is the preferred typeface throughout, and
will be selected for you by default.  Paragraphs are separated by
\nicefrac{1}{2}~line space (5.5 points), with no indentation.

The paper title should be 17~point, initial caps/lower case, bold,
centered between two horizontal rules. The top rule should be 4~points
thick and the bottom rule should be 1~point thick. Allow
\nicefrac{1}{4}~inch space above and below the title to rules. All
pages should start at 1~inch (6~picas) from the top of the page.

For the final version, authors' names are set in boldface, and each
name is centered above the corresponding address. The lead author's
name is to be listed first (left-most), and the co-authors' names (if
different address) are set to follow. If there is only one co-author,
list both author and co-author side by side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper
nouns), flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the
heading in bold, flush left, and inline with the text, with the
heading followed by 1\,em of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.
Citations may be author/year or numeric, as long as you maintain
internal consistency.  As to the format of the references themselves,
any style is acceptable as long as it is used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may
add the following before loading the \verb+nips_2018+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add
the optional argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{nips_2018}
\end{verbatim}

As submission is double blind, refer to your own published work in the
third person. That is, use ``In the previous work of Jones et
al.\ [4],'' not ``In our previous work [4].'' If you cite your other
papers that are not widely available (e.g., a journal paper under
review), use anonymous author names in the citation, e.g., an author
of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote,
indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Place the footnotes at the bottom of the
page on which they appear.  Precede the footnote with a horizontal
rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction. The figure number and caption
always appear after the figure. Place one line space before the figure
caption and one line space after the figure. The figure caption should
be lower case (except for first word and proper nouns); figures are
numbered consecutively.

You may use color figures.  However, it is best for the figure
captions and the paper body to be legible if the paper is printed in
either black/white or in color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table
number and title always appear before the table.  See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical
  rules.} We strongly suggest the use of the \verb+booktabs+ package,
which allows for typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style
files.  In particular, do not modify the width or length of the
rectangle the text should fit into, and do not change font sizes
(except perhaps in the \textbf{References} section; see below). Please
note that pages should be numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and
not, for example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file
must only contain Type 1 or Embedded TrueType fonts. Here are a few
instructions to achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader,
  select the menu Files$>$Document Properties$>$Fonts and select Show
  All Fonts. You can also use the program \verb+pdffonts+ which comes
  with \verb+xpdf+ and is available out-of-the-box on most Linux
  machines.

\item The IEEE has recommendations for generating PDF files whose
  fonts are also acceptable for NIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap
  fonts.  Use "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
  should use the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
can also use the following workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the
\verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we
will ask you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always
specify the figure width as a multiple of the line width as in the
example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly
hyphenate a line. Please give LaTeX hyphenation hints using the
\verb+\-+ command when necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include
acknowledgments in the anonymized submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can use more than eight pages as long as the
  additional pages contain \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
  Exploring Realistic Neural Models with the GEneral NEural SImulation
  System.}  New York: TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
learning and recall at excitatory recurrent synapses and cholinergic
modulation in rat hippocampal region CA3. {\it Journal of
  Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2018-10-24 2018_nips_vigil/introduction.tex
introduction first draft - pretty average

\section{Introduction}
Reasoning over visual inputs is a fundamental characteristic of human intelligence.
Reproducing this ability with artificial agents is a challenge that requires learning relations and compositionality (Hu et al. 2017; Johnson et al. 2017b).
Visual Question Answering datasets have been tailored to benchmark those reasoning performances. The recent CLEVR dataset (Johnson et al., 2017a) proposes a challenging multimodal task that requires to answer compositional questions about an image. Solving this problem involves a broad array of skills such as counting, comparison and understanding transitive reasoning (Hudson et al. 2018) . CLEVR is a generated synthetic dataset that allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.
Recent work on CLEVR from Hudson et al. 2018;  has introduced  MAC ( Memory, Attention, and Composition). The MAC model has been deliberately designed to decompose the problem into a sequence of attention-based reasoning operations. Its ability to arbitrarily draw a complex reasoning graph while still featuring end-to-end differentiability made its sucess. 
MAC achieves state-of-the-art accuracy on CLEVR and also on the most difficult CLEVR Humans dataset, were questions are written by humans. Although the performance of MAC has been proven, does the model learn relations between objects? How does the model represent those relations and reasoning steps? 
Is the model representing notions and concepts like objects attributes? 
In this work, we first question the complexity of the MAC model and explore simplification possibilities. We propose a new set of equations that aims to simplify the model and improve training performance. 
We also put to proof the MAC model on the CLEVR CoGenT dataset. The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability. By mixing attributes other two sub-datasets, the CLEVR CoGenT allow us to see what relations and concepts the model has really learned. We show how MAC performs on CLEVR CoGenT
and propose a study about the model failures. This work points out some of the MAC model weaknesses, in particular its failure to differentiate concepts of colors and shape. We finally discuss some improvement possibilities.

### 2018-10-25 2018_nips_vigil/smac.tex
Changed style files. Added simplified mac equations

\section{Simplified MAC model}

Idealized equations:
\subsection*{Control Unit}

\begin{align*}
	&q_i = U_i^{[d \times 2d]} q + b_i^{[d]}  \tag{c0} \\
	\cline{1-2}
	&cq_i = W_{\textsf{cq}}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
	&ca_{is} = W_{\textsf{ca}}^{[1 \times d]} (cq_i \odot \mathbf{cw}_s)  \tag{c2.1}\\
	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
	&\mathbf{c}_i = \sum_s cv_{is} \, \mathbf{cw}_s  \tag{c2.3}
\end{align*}
Only eqn.~(c0) above is \emph{position dependent}

\subsection*{Read Unit}

\begin{align*}
	&\mathbf{\tk}_{hw} = U_{\textsf{proj}}^{[d \times d]} \mathbf{k}_{hw} + b_{\textsf{proj}}^{[d]} \tag{r0} \\
	\cline{1-2}
	&I_{ihw} = \mathbf{m}_{i-1} \odot \mathbf{\tk}_{hw} \tag{r1} \\
	&I'_{ihw} = \mathbf{\tk}_{hw}  + W_{\textsf{I}}^{[d \times d]} I_{ihw} + b_{\textsf{I}}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{\textsf{ra}}^{[1 \times d]} (\mathbf{c}_i \odot I'_{ihw})  \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\mathbf{r}_i = \sum_s rv_{ihw} \, \mathbf{\tk}_{hw}  \tag{r3.3}
\end{align*}

Note that $\mathbf{\tk}_{hw}$ can be \emph{precomputed} before the reasoning steps.

\subsection*{Write Unit}

\begin{equation}
\mathbf{m}_i = W_{\textsf{m}}^{[d \times d]} \mathbf{r}_i + b_{\textsf{m}}^{[d]} \tag{w1}
\end{equation}

### 2018-10-26 2018_nips_vigil/introduction.tex
Introduction - second version

@@
 Reasoning over visual inputs is a fundamental characteristic of human intelligence.
-Reproducing this ability with artificial agents is a challenge that requires learning relations and compositionality (Hu et al. 2017; Johnson et al. 2017b).
-Visual Question Answering datasets have been tailored to benchmark those reasoning performances.
+Reproducing this ability with artificial agents is a challenge that requires learning relations and compositionality (Hu et al. 2017; Johnson et al. 2017b).\\
+The Visual Question Answering (VQA) task has been tailored to benchmark those reasoning performances.
+It is a complex semantic task requiring both natural language processing and visual recognition.
+It also put to the test the effective use of the short term memory.\\
 The recent CLEVR dataset (Johnson et al., 2017a) proposes a challenging multimodal task that requires to answer compositional questions about an image.
-Solving this problem involves a broad array of skills such as counting, comparison and understanding transitive reasoning (Hudson et al.
-2018) .
-CLEVR is a generated synthetic dataset that allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.
+The dataset is designed with the explicit goal of enabling detailed analysis of visual reasoning.
+Solving this problem involves a broad array of skills such as counting, comparison and understanding transitive reasoning.
+It also requires perceptual abilities such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge (Hudson et al. 2018).
+CLEVR is a generated synthetic dataset that allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.\\
+To solve this type of reasoning task, many deep learning approaches have been explored although they often struggle to perform well on tasks with a structured and compositional nature (Garnelo et al., 2016; Lake et al., 2017).
+More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection (Andreas et al., 2016a; Johnson et al., 2017b, Mascharka et al., 2018).
+However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes (Hudson et al.
+2018).
+These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.\\
 Recent work on CLEVR from Hudson et al.
@@
 Its ability to arbitrarily draw a complex reasoning graph while still featuring end-to-end differentiability made its sucess.
+MAC doesn’t use specific modules that would make it specifically tailored for the CLEVR dataset.
+The three general units working in tandem to perform a reasoning step make the robustness of the model.\\
 MAC achieves state-of-the-art accuracy on CLEVR and also on the most difficult CLEVR Humans dataset, were questions are written by humans. 
-Although the performance of MAC has been proven, does the model learn relations between objects?
+Although the performance of MAC has been proven, It appears difficult to understand what concepts the model is learning. 
+Does the model really learn relations between objects? 
 How does the model represent those relations and reasoning steps? 
-Is the model representing notions and concepts like objects attributes? 
+The interpretability of the MAC model seems yet to be fully defined.
+Is the model representing notions and concepts like objects attributes?\\
 In this work, we first question the complexity of the MAC model and explore simplification possibilities.
@@
 The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability.
-By mixing attributes other two sub-datasets, the CLEVR CoGenT allow us to see what relations and concepts the model has really learned.
-We show how MAC performs on CLEVR CoGenT
+By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned.
+We show how MAC performs on CLEVR CoGenT and compare it to state-of-the-art models.
 and propose a study about the model failures.

### 2018-10-26 2018_nips_vigil/mac.tex
no message

\section{Description of MAC model}

A MAC network is an end-to-end differentiable architecture primed to perform an explicit multi-step reasoning process, by stringing together p recurrent MAC cells, each responsible for performing one reasoning step. Given a knowledge base K (for VQA, an image) and a task description q (for VQA, a question), the model infers a decomposition into a series of p reasoning operations that interact with the knowledge base, iteratively aggregating and manipulating information to perform the task at hand. It consists of three components: (1) an input unit, (2) the core recurrent network, composed out of p MAC cells, and (3) an output unit, all described below.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.7\textwidth]{img/mac_cell.pdf}
	\caption{The Mac Cell. The MAC recurrent cell consists of a control unit, read unit, and write unit, that operate over dual control and memory hidden states. The control unit successively attends to different parts of the task description (question), updating the control state to represent at each timestep the reasoning operation the cell intends to perform. The read unit extracts information out of a knowledge base (here, image), guided by the control state. The write unit integrates the retrieved information into the memory state, yielding the new intermediate result that follows from applying the current reasoning operation.}
	\label{fig:core_concepts}
\end{figure}

### 2018-10-26 2018_nips_vigil/mac.tex
input unit

@@
 \end{figure}
+
+\textbf{\textit{Description of the input unit:}}
+
+The role of the input unit is to preprocess the raw images and questions. 
+The images are passed through a feature extractor (ResNet101 cut after layer \textbf{\textit{con4}} ) pre-trained on ImageNet.
+The output tensor is a feature map that is finally processed by two trainable CNN layers to obtain the knowledge base \textbf{\textit{K}}, the final image representation.
+
+The question first go through a word embedding method and then a bidirectional LSTM.
+The question preprocessing leads to two different outputs:
+
+\begin{description}
+	\item[$\bullet$] The question representation \textbf{\textit{q}} which is the concatenation of the final hidden states from the backward and forward LSTM passes
+	\item[$\bullet$] The contextual words \textbf{\textit{cw}} : a series of output states \textbf{\textit{cw1}}, . . . , \textbf{\textit{cwS}} that represent each word in the context of the question
+\end{description}

### 2018-10-29 2018_nips_vigil/introduction.tex
input unit
Mac and S-Mac

@@
 Reasoning over visual inputs is a fundamental characteristic of human intelligence.
-Reproducing this ability with artificial agents is a challenge that requires learning relations and compositionality (Hu et al. 2017; Johnson et al. 2017b).\\
+Reproducing this ability with artificial agents is a challenge that requires learning relations and compositionality (Hu et al. 2017; Johnson et al. 2017b).
+
 The Visual Question Answering (VQA) task has been tailored to benchmark those reasoning performances.
 It is a complex semantic task requiring both natural language processing and visual recognition.
-It also put to the test the effective use of the short term memory.\\
+It also put to the test the effective use of the short term memory.
+
 The recent CLEVR dataset (Johnson et al., 2017a) proposes a challenging multimodal task that requires to answer compositional questions about an image.
@@
 It also requires perceptual abilities such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge (Hudson et al. 2018).
-CLEVR is a generated synthetic dataset that allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.\\
+CLEVR is a generated synthetic dataset that allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.
+
 To solve this type of reasoning task, many deep learning approaches have been explored although they often struggle to perform well on tasks with a structured and compositional nature (Garnelo et al., 2016; Lake et al., 2017).
@@
 2018).
-These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.\\
+These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
+
 Recent work on CLEVR from Hudson et al.
@@
 Its ability to arbitrarily draw a complex reasoning graph while still featuring end-to-end differentiability made its sucess.
-MAC doesn’t use specific modules that would make it specifically tailored for the CLEVR dataset.
-The three general units working in tandem to perform a reasoning step make the robustness of the model.\\
+MAC doesn’t use specific modules that would make it specifically tailored for the CLEVR dataset. The three general units working in tandem to perform a reasoning step make the robustness of the model.
+
 MAC achieves state-of-the-art accuracy on CLEVR and also on the most difficult CLEVR Humans dataset, were questions are written by humans. 
@@
 The interpretability of the MAC model seems yet to be fully defined.
-Is the model representing notions and concepts like objects attributes?\\
+Is the model representing notions and concepts like objects attributes?
+
 In this work, we first question the complexity of the MAC model and explore simplification possibilities.

### 2018-10-29 2018_nips_vigil/mac.tex
output unit
Mac and S-Mac

--- 2018-10-26 2018_nips_vigil/mac.tex
@@
-\section{Description of MAC model}
+\section{MAC network and our proposed simplification}
 
-A MAC network is an end-to-end differentiable architecture primed to perform an explicit multi-step reasoning process, by stringing together p recurrent MAC cells, each responsible for performing one reasoning step.
-Given a knowledge base K (for VQA, an image) and a task description q (for VQA, a question), the model infers a decomposition into a series of p reasoning operations that interact with the knowledge base, iteratively aggregating and manipulating information to perform the task at hand.
-It consists of three components: (1) an input unit, (2) the core recurrent network, composed out of p MAC cells, and (3) an output unit, all described below.
+The MAC network~\cite{hudsonManning18} is a recurrent model that performs reasoning 
+using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
+At the end, a suitable answer is given based on this composite reasoning.
+To improve the accuracy of prediction, both the questions and images
+are preprocessed suitably. For the question,  a word-embedding is first used to
+transformed the question into a sequence of vectors which is then passed through
+a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
+corresponds to a unique word in the question and is called the 
+\emph{contextual embedding} for that word.
+Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.
 
@@
 	\includegraphics[width=0.7\textwidth]{img/mac_cell.pdf}
-	\caption{The Mac Cell.
-The MAC recurrent cell consists of a control unit, read unit, and write unit, that operate over dual control and memory hidden states.
-The control unit successively attends to different parts of the task description (question), updating the control state to represent at each timestep the reasoning operation the cell intends to perform.
-The read unit extracts information out of a knowledge base (here, image), guided by the control state.
-The write unit integrates the retrieved information into the memory state, yielding the new intermediate result that follows from applying the current reasoning operation.}
-	\label{fig:core_concepts}
+	\caption{The Mac Cell. The MAC recurrent cell consists of a control unit, read unit, and write unit, that operate over dual control and memory hidden states. }
+	\label{fig:mac_cell}
 \end{figure}

### 2018-10-29 2018_nips_vigil/smac.tex
Mac and S-Mac

@@
-\section{Simplified MAC model}
+\subsection{Simplified MAC network}
+Our proposed modification to the MAC network is based on two heuristic
+simplifications of the equations governing a MAC cell. 
+First, we observed that when looking at the equations of different units
+together as a whole, we notice that there are several affine transformations
+that are applied in sequence (with no activation in-between).
+Therefore they can actually be combined to form a single affine transformation.
+The second observation uses the following heuristic argument:
+suppose there is a single affine transformation which preserves the number
+of dimensions. Then one can assume that the transformation is invertible
+so as to avoid a loss in the information. Applying this principle to 
+equations in the read and write unit results in eliminating an affine
+operation of the knowledge base in the recurrent network. Instead we compute
+this operation on the knowledge base right after we apply the 2 
+trainable CNN layers (i.e. prior to the reasoning steps). This results
+in a significant savings in training time, as our experiments demonstrate
+below, without incurring too much drop in accuracy.
 
-Idealized equations:
 \subsection*{Control Unit}

### 2018-10-29 2018_nips_vigil/mac.tex

@@
 \end{figure}
+
+\textbf{\textit{Description of the input unit:}}
+
+The role of the input unit is to preprocess the raw images and questions. 
+The images are passed through a feature extractor (ResNet101 cut after layer \textbf{\textit{con4}} ) pre-trained on ImageNet.
+The output tensor is a feature map that is finally processed by two trainable CNN layers to obtain the knowledge base \textbf{\textit{K}}, the final image representation.
+
+The question first go through a word embedding method and then a bidirectional LSTM.
+The question preprocessing leads to two different outputs:
+
+\begin{description}
+	\item[$\bullet$] The question representation \textbf{\textit{q}} which is the concatenation of the final hidden states from the backward and forward LSTM passes
+	\item[$\bullet$] The contextual words \textbf{\textit{cw}} : a series of output states \textbf{\textit{cw1}}, . . . , \textbf{\textit{cwS}} that represent each word in the context of the question
+\end{description}
+
+\textbf{\textit{Description of the output unit:}}
+
+The output unit simply process the concatenation of the question representation  \textbf{\textit{q}} and the final memory  \textbf{\textit{mp}} to produce a final answer.
+For CLEVR it is a 2-layer fully-connected softmax classifier.

### 2018-10-29 2018_nips_vigil/introduction.tex
correct typo

@@
 It is a complex semantic task requiring both natural language processing and visual recognition.
-It also put to the test the effective use of the short term memory.
+It also puts to the test the effective use of the short term memory.
 
@@
 By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned.
-We show how MAC performs on CLEVR CoGenT and compare it to state-of-the-art models.
-and propose a study about the model failures.
+We show how MAC performs on CLEVR CoGenT and compare it to state-of-the-art models and propose a study about the model failures.
 This work points out some of the MAC model weaknesses, in particular its failure to differentiate concepts of colors and shape.

### 2018-10-29 2018_nips_vigil/smac.tex
S-mac with both equations side-by-side

@@
 
-\subsection*{Control Unit}
+In the description below, the original MAC cell equations are shown on the \emph{left}
+while our simplified equations are shown on the \emph{right}.
+(The equation numbering is the same as in~\cite{hudsonManning18}.)
 
+\setlength{\columnsep}{1cm}
+\setlength{\columnseprule}{0.5pt}
+%\def\columnseprulecolor{\color{blue}}
+
+\subsection*{Control Unit:}
+\newcommand{\cq}{cq}
+\newcommand{\ca}{ca}
+\newcommand{\cw}{\mathbf{cw}}
+\newcommand{\cc}{\mathbf{c}}
+
+\begin{multicols}{2}
+	\noindent
 	\begin{align*}
 	&q_i = U_i^{[d \times 2d]} q + b_i^{[d]}  \tag{c0} \\
+	\cline{1-2} \\[2pt]
+	&cq_i = W_{\cq}^{[d \times 2d]} [c_{i-1}, q_i] + b_{\cq}^{[d]}  \tag{c1} \\
+	&ca_{is} = W_{\ca}^{[1 \times d]} (cq_i \odot \cw_s) + b_{\ca}^{[1]}
+	\tag{c2.1}\\
+	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
+	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
+	\end{align*} 
+	\columnbreak
+	\begin{align*}
+	&q_i = U_i^{[d \times 2d]} q + b_i^{[d]}  \tag{c0} \\
+	\cline{1-2} \\[2pt]
+	&cq_i = W_{\cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
+	&ca_{is} = W_{\ca}^{[1 \times d]} (cq_i \odot \cw_s)  \tag{c2.1}\\
+	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
+	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
+    \end{align*} 
+\end{multicols}
+
+Above, $i$ refers to index/position of the reasoning step. Note that the weights/biases
+are \emph{shared} across reasoning steps except for eqn.~(c0) above, which 
+is \emph{position-aware}~\cite{hudsonManning18}, i.e. depends
+on $i$.
+
+\subsection*{Read and Write Unit:}
+\newcommand{\kb}{\mathbf{k}}
+\newcommand{\tkb}{\mathbf{\hat{k}}}
+\newcommand{\mi}{\textsf{I}}
+\newcommand{\mpi}{\textsf{I'}}
+\newcommand{\mem}{\mathbf{m}}
+\newcommand{\rr}{\mathbf{r}}
+
+\begin{multicols}{2}
+	\noindent
+	\begin{align*}
+	\\
 	\cline{1-2}
-	&cq_i = W_{\textsf{cq}}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
-	&ca_{is} = W_{\textsf{ca}}^{[1 \times d]} (cq_i \odot \mathbf{cw}_s)  \tag{c2.1}\\
-	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
-	&\mathbf{c}_i = \sum_s cv_{is} \, \mathbf{cw}_s  \tag{c2.3}
+	&I_{ihw} = (W_{m}^{[d \times d]} m_{i-1} + b_{m}^{[d]}) \\
+	           & \qquad \quad \odot (W_{k}^{[d \times d]} k_{i-1} + b_{m}^{[d]}) \tag{r1} \\
+	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
+	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
+	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
+	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
+	&\mem_i = W_{m}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{m}^{[d]} \tag{w1}	
 	\end{align*}
-Only eqn.~(c0) above is \emph{position dependent}
+	\columnbreak
+	\begin{align*}
+	&\tkb_{hw} = U_{\textsf{proj}}^{[d \times d]} \mathbf{k}_{hw} + b_{\textsf{proj}}^{[d]} \tag{r0} \\
+	\cline{1-2}
+	&I_{ihw} = \mem_{i-1} \odot \tkb_{hw} \tag{r1} \\ \\
+	&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \tkb_{hw} \tag{r2} \\
+	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
+	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
+	&\rr_i = \sum_s rv_{ihw} \, \tkb_{hw}  \tag{r3.3}\\
+	&\mem_i = W_{m}^{[d \times d]} \rr_i + b_{m}^{[d]} \tag{w1}
+	\end{align*}
+\end{multicols}
 
-\subsection*{Read Unit}
-
-\begin{align*}
-	&\mathbf{\tk}_{hw} = U_{\textsf{proj}}^{[d \times d]} \mathbf{k}_{hw} + b_{\textsf{proj}}^{[d]} \tag{r0} \\
-	\cline{1-2}
-	&I_{ihw} = \mathbf{m}_{i-1} \odot \mathbf{\tk}_{hw} \tag{r1} \\
-	&I'_{ihw} = \mathbf{\tk}_{hw}  + W_{\textsf{I}}^{[d \times d]} I_{ihw} + b_{\textsf{I}}^{[d]}  \tag{r2} \\
-	&ra_{ihw} = W_{\textsf{ra}}^{[1 \times d]} (\mathbf{c}_i \odot I'_{ihw})  \tag{r3.1}\\
-	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
-	&\mathbf{r}_i = \sum_s rv_{ihw} \, \mathbf{\tk}_{hw}  \tag{r3.3}
-\end{align*}
-
-Note that $\mathbf{\tk}_{hw}$ can be \emph{precomputed} before the reasoning steps.
-
-\subsection*{Write Unit}
-
-\begin{equation}
-\mathbf{m}_i = W_{\textsf{m}}^{[d \times d]} \mathbf{r}_i + b_{\textsf{m}}^{[d]} \tag{w1}
-\end{equation}
+Note that $\tkb_{hw}$ can be \emph{precomputed} before the reasoning steps.

### 2018-10-30 2018_nips_vigil/mac.tex
update on MAC part

--- 2018-10-29 2018_nips_vigil/mac.tex
@@
 \emph{contextual embedding} for that word.
-Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.
+Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.\\
+The core of network is a sequence of recurrent MAC cells.
+A MAC cell (Figure 1) is performing one reasoning step.
+At every step the network is driving the attention on one part of the question and a corresponding part of the image.
+This operation is made possible by the combination of 3 units working together, a control unit, a read and a write units.
+The control unit is updating the control state and drives the attention over the question.
+Given this control state, the read unit then retrieves information from the memory and drives the attention over the image.
+Finally, the write unit retrieves this visual information and update the memory state.
+The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.\\
+By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them. 
+MAC is performing state of the art accuracy on CLEVR....
 

### 2018-10-30 2018_nips_vigil/mac.tex
Update mac.tex
typos

@@
 Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.\\
-The core of network is a sequence of recurrent MAC cells.
+The core of the network is a sequence of recurrent MAC cells.
 A MAC cell (Figure 1) is performing one reasoning step.
-At every step the network is driving the attention on one part of the question and a corresponding part of the image.
+At every step the network is driving the attention on one part of the question and the corresponding part of the image.
 This operation is made possible by the combination of 3 units working together, a control unit, a read and a write units.
@@
 Given this control state, the read unit then retrieves information from the memory and drives the attention over the image.
-Finally, the write unit retrieves this visual information and update the memory state.
+Finally, the write unit retrieves this visual information and updates the memory state.
 The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.\\

### 2018-10-30 2018_nips_vigil/mac.tex
Update on description of MAC - perhaps too long

@@
 By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them.
-MAC is performing state of the art accuracy on CLEVR....
+MAC is performing state of the art accuracy on CLEVR and CLEVR Humans datasets.
+In contrast to modular approaches (Andreas et al., 2016a;b; Hu et al., 2017; Johnson et al., 2017b), MAC is fully
+differentiable and does not require additional supervision.
+It is making use of a single computational cell chained in sequence rather than a collection of custom modules deployed in a rigid tree structure.
+In contrast to augmented CNN approaches (Santoro et al., 2017; Perez et al., 2017),  the MAC model provides an ability for relational reasoning with better generalization capacity, higher
+computational efficiency and enhanced transparency.
 

### 2018-10-30 2018_nips_vigil/mac.tex
Wrapped figure in text. Modified equations to make it more readable.

@@
 \emph{contextual embedding} for that word.
-Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.\\
+Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.
+
+\begin{wrapfigure}{r}[5pt]{0.4\textwidth}
+	\vspace{-15pt}
+	\centering
+	\includegraphics[width=\textwidth]{img/mac_cell.pdf}
+	\caption{The MAC cell~\cite{hudsonManning18}}
+	\label{fig:mac_cell}
+	\vspace{-5pt}
+\end{wrapfigure}
+
 The core of the network is a sequence of recurrent MAC cells.
@@
 Finally, the write unit retrieves this visual information and updates the memory state.
-The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.\\
+The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.
+
 By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them.
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.7\textwidth]{img/mac_cell.pdf}
-	\caption{The Mac Cell. The MAC recurrent cell consists of a control unit, read unit, and write unit, that operate over dual control and memory hidden states. }
-	\label{fig:mac_cell}
-\end{figure}
+%\begin{figure}[htbp]
+%	\centering
+%	\includegraphics[width=0.4\textwidth]{img/mac_cell.pdf}
+%	\caption{The MAC cell~\cite{hudsonManning18}}
+%	\label{fig:mac_cell}
+%\end{figure}

### 2018-10-30 2018_nips_vigil/smac.tex
Wrapped figure in text. Modified equations to make it more readable.

--- 2018-10-29 2018_nips_vigil/smac.tex
@@
 
-\subsection*{Control Unit}
+In the description below, the original MAC cell equations are shown on the \emph{left}
+while our simplified equations are shown (in color) on the {\color{Plum} \emph{right}}.
+(The equation numbering is the same as in~\cite{hudsonManning18}.)
 
+\noindent\textit{Notation:} The index/position $i$ below denotes the reasoning step. 
+Unless mentioned otherwise, the weights/biases are invariant w.r.t $i$, 
+i.e., shared across all the reasoning steps.
+
+\noindent\textbf{Control unit:} 
+For both models, in the control unit, the question $q$ is first transformed in each step of 
+the reasoning using a \emph{position-aware}~\cite{hudsonManning18} 
+linear layer: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
+
+\begin{multicols}{2}
+	\noindent
 	\begin{align*}
-	&q_i = U_i^{[d \times 2d]} q + b_i^{[d]}  \tag{c0} \\
-	\cline{1-2}
-	&cq_i = W_{\textsf{cq}}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
-	&ca_{is} = W_{\textsf{ca}}^{[1 \times d]} (cq_i \odot \mathbf{cw}_s)  \tag{c2.1}\\
+	&cq_i = W_{cq}^{[d \times 2d]} [c_{i-1}, q_i] + b_{cq}^{[d]}  \tag{c1} \\
+	&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s) + b_{ca}^{[1]}
+	\tag{c2.1}\\
 	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
-	&\mathbf{c}_i = \sum_s cv_{is} \, \mathbf{cw}_s  \tag{c2.3}
+	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
 	\end{align*}
-Only eqn.~(c0) above is \emph{position dependent}
+	\columnbreak
+	{\color{Plum}
+	\begin{align*}
+	&cq_i = W_{cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
+	&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s)  \tag{c2.1}\\
+	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
+	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
+    \end{align*}}
+\end{multicols}
 
-\subsection*{Read Unit}
+\noindent\textbf{Read and write units:}
+For both models below, $\kb_{hw}$ denotes the \emph{knowledge base}~\cite{hudsonManning18}
+consisting of 3D tensors with dimension $H \times W \times d$ for each image
+in the data set. The difference in computing $\kb_{hw}$ is that the simplified MAC uses
+an additional linear layer on top of the 2 CNN layers present in the original MAC network.
+This circumvents the need for performing additional linear transformations on the 
+knowledge base, as is done by the original MAC network in \emph{each} reasoning step.
 
+\begin{multicols}{2}
+	\noindent
 	\begin{align*}
-	&\mathbf{\tk}_{hw} = U_{\textsf{proj}}^{[d \times d]} \mathbf{k}_{hw} + b_{\textsf{proj}}^{[d]} \tag{r0} \\
-	\cline{1-2}
-	&I_{ihw} = \mathbf{m}_{i-1} \odot \mathbf{\tk}_{hw} \tag{r1} \\
-	&I'_{ihw} = \mathbf{\tk}_{hw}  + W_{\textsf{I}}^{[d \times d]} I_{ihw} + b_{\textsf{I}}^{[d]}  \tag{r2} \\
-	&ra_{ihw} = W_{\textsf{ra}}^{[1 \times d]} (\mathbf{c}_i \odot I'_{ihw})  \tag{r3.1}\\
+	&I_{ihw} = (W_{m}^{[d \times d]} m_{i-1} + b_{m}^{[d]}) \\
+	           & \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{m}^{[d]}) \tag{r1} \\
+	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
+	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
 	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
-	&\mathbf{r}_i = \sum_s rv_{ihw} \, \mathbf{\tk}_{hw}  \tag{r3.3}
+	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
+	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
 	\end{align*}
-
-Note that $\mathbf{\tk}_{hw}$ can be \emph{precomputed} before the reasoning steps.
-
-\subsection*{Write Unit}
-
-\begin{equation}
-\mathbf{m}_i = W_{\textsf{m}}^{[d \times d]} \mathbf{r}_i + b_{\textsf{m}}^{[d]} \tag{w1}
-\end{equation}
+	\columnbreak
+	{\color{Plum}
+	\begin{align*}
+	&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
+	&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
+	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
+	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
+	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
+	&\mem_i = W_{rm}^{[d \times d]} \rr_i + b_{rm}^{[d]} \tag{w1}
+	\end{align*}}
+\end{multicols}

### 2018-10-30 2018_nips_vigil/experiments.tex
CoGenT intro

\section{Experiments}

We propose to further analyse MAC’s generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset. It is synthesized in the same way as CLEVR but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes. Both conditions contain spheres of all colors.

### 2018-10-30 2018_nips_vigil/experiments.tex
CoGenT intro +
correct typo
Started the experiments section.

@@
 
-We propose to further analyse MAC’s generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset.
+We propose to further analyze MAC's generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset.
 It is synthesized in the same way as CLEVR but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
 Both conditions contain spheres of all colors.
+We also evaluate the simplified model on this dataset for comparison.
+
+The training procedure is layed out as follows: we train the MAC model (and simplified MAC) for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
+We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets as test sets, given that the ground truth labels for the true test sets are not available.
+
+We implemented the models using PyTorch\footnote{\url{https://pytorch.org/}} (v0.4.0), and the code is available on GitHub\footnote{\url{https://github.com/IBM/mi-prometheus/}}.
+The system is based on Linux 16.04 and we used NVIDIA's GeForce GTX TITAN X.
+We followed the implementation details indicated in the original paper (Section A of the supplementary material), to ensure a faithful comparison.
+
+\begin{table}[]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|}
+		\hline
+		Model                 & Training set                & \multicolumn{1}{l|}{Training wall time} & Training statistics          & Test set & Test statistics \\ \hline
+		\multirow{3}{*}{MAC}  & CLEVR                       & 31h                                     & acc: 96.7\%                  & CLEVR    & 96.2\%          \\ \cline{2-6} 
+		& \multirow{2}{*}{CoGenT - A} & \multirow{2}{*}{31h}                    & \multirow{2}{*}{acc: 97.0\%} & CoGenT-A & 96.9\%          \\ \cline{5-6} 
+		&                             &                                         &                              & CoGenT-B & 79.5\%          \\ \hline
+		\multirow{3}{*}{SMAC} & CLEVR                       & 28h                                     & acc: 95.8.\%                 & CLEVR    & 95.3\%          \\ \cline{2-6} 
+		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28h}                    & \multirow{2}{*}{acc: 96.1\%} & CoGenT-A & 95.9\%          \\ \cline{5-6} 
+		&                             &                                         &                              & CogenT-B & 78.7\%          \\ \hline
+	\end{tabular}
+	\caption{CLEVR \& CLEVR-CoGenT accuracy for the MAC \& simplified MAC model.}
+	\label{results}
+\end{table}
+
+We report the obtained scores in \tableref{results}.
+Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31h of training.\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
+Evaluating MAC on CoGenT shows that, like previous work (\cite{johnson2017inferring}, \cite{mascharka2018transparency})], the performance is worse on Condition B than Condition A after training only using Condition A data.
+As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, which surpasses the previously 78.8\% reported in \cite{perez2017film}.
+The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.
+Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of ~10\% in wall time.
+This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.
+
+Following \cite{johnson2017inferring}, we then fine-tune both models using 3k images and 30k questions from the Condition B data.. \textit{To continue later on}.

### 2018-10-30 2018_nips_vigil/introduction.tex
Rewritten introduction, added several bibtex positions

--- 2018-10-29 2018_nips_vigil/introduction.tex
@@
 Reasoning over visual inputs is a fundamental characteristic of human intelligence.
-Reproducing this ability with artificial agents is a challenge that requires learning relations and compositionality (Hu et al. 2017; Johnson et al. 2017b).
+Reproducing this ability with artificial systems is a challenge that requires learning relations and compositionality~\citep{hu2017learning, johnson2017inferring}.
+The Visual Question Answering (VQA)~\citep{antol2015vqa,malinowski2014towards,wu2017visual} task has been tailored to benchmark those reasoning performances.
+VQA is a complex semantic task that combines natural language processing and visual recognition.
+In order to answer the questions the system  requires to master several perceptual abilities, such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge~\citep{hudson2018compositional}.
 
-The Visual Question Answering (VQA) task has been tailored to benchmark those reasoning performances.
-It is a complex semantic task requiring both natural language processing and visual recognition.
-It also put to the test the effective use of the short term memory.
+To solve this type of reasoning task, many approaches have been explored although they often appear to struggle performing well on tasks with a structured and compositional nature (Garnelo et al., 2016; Lake et al., 2017).
+\tk{I have no idea what those papers are...}
+More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection (andreas2016learning; johnson2017inferring, mascharka2018transparency).
+However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes
+These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
+\tk{Compositional models are one major direction of research in VQA...
+but there are 3 others (including e.g.
+attention) that we do not mention here, thus my concern is that the above is not well balanced...
+I can add more when we will understand how much space is left.}
 
-The recent CLEVR dataset (Johnson et al., 2017a) proposes a challenging multimodal task that requires to answer compositional questions about an image.
-The dataset is designed with the explicit goal of enabling detailed analysis of visual reasoning.
-Solving this problem involves a broad array of skills such as counting, comparison and understanding transitive reasoning.
-It also requires perceptual abilities such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge (Hudson et al. 2018).
-CLEVR is a generated synthetic dataset that allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.
+There are many datasets for VQA such as DAQUAR~\citep{malinowski2014multi} or VQA~\citep{antol2015vqa}.
+The problem is they contain several biases (e.g.
+unbalanced questions or answers) that are often exploited by systems during learning~\citep{goyal2017making}.
+The CLEVR dataset~\citep{johnson2017clevr} was designed to address that issue.
+And besides that, due to the synthetic nature of the images, it also enables detailed analysis of visual reasoning.
+CLEVR also allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.
 
-To solve this type of reasoning task, many deep learning approaches have been explored although they often struggle to perform well on tasks with a structured and compositional nature (Garnelo et al., 2016; Lake et al., 2017).
-More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection (Andreas et al., 2016a; Johnson et al., 2017b, Mascharka et al., 2018).
-However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes (Hudson et al.
-2018).
-These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
-
-Recent work on CLEVR from Hudson et al.
-2018;  has introduced  MAC ( Memory, Attention, and Composition).
+One of the most recent models aiming at solving VQA is called MAC (Memory, Attention, and Composition)~\citep{hudson2018compositional}.
 The MAC model has been deliberately designed to decompose the problem into a sequence of attention-based reasoning operations.
-Its ability to arbitrarily draw a complex reasoning graph while still featuring end-to-end differentiability made its sucess.
-MAC doesn’t use specific modules that would make it specifically tailored for the CLEVR dataset. The three general units working in tandem to perform a reasoning step make the robustness of the model.
-
-MAC achieves state-of-the-art accuracy on CLEVR and also on the most difficult CLEVR Humans dataset, were questions are written by humans. 
-Although the performance of MAC has been proven, It appears difficult to understand what concepts the model is learning. 
+MAC uses three general units working in tandem to perform a reasoning step make the robustness of the model.
+The MAC  model achieved state-of-the-art accuracy on CLEVR.
+The authors also tested in on the difficult CLEVR Humans dataset, were the questions (regarding synthetically generated images) were written by humans. 
+Although the performance of MAC has been proven, it appeared to have difficulties with understanding what concepts the model is learning. 
+So several questions appeared.
 Does the model really learn relations between objects? 
 How does the model represent those relations and reasoning steps? 
-The interpretability of the MAC model seems yet to be fully defined.
 Is the model representing notions and concepts like objects attributes?
+Those questions indicate that the interpretability of the MAC model seems yet to be fully defined.
 
-In this work, we first question the complexity of the MAC model and explore simplification possibilities.
-We propose a new set of equations that aims to simplify the model and improve training performance.
-We also put to proof the MAC model on the CLEVR CoGenT dataset.
+In this work we focus on that issue.
+First, we question the complexity of the MAC model and explore simplification possibilities.
+We propose a new set of equations that aims at simplification of the model and improvement of training performance.
+Second, we put to proof the MAC model on the CLEVR CoGenT dataset.
 The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability.
 By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned.
-We show how MAC performs on CLEVR CoGenT and compare it to state-of-the-art models.
-and propose a study about the model failures.
-This work points out some of the MAC model weaknesses, in particular its failure to differentiate concepts of colors and shape.
-We finally discuss some improvement possibilities.
+We show how MAC performs on CLEVR CoGenT and propose a study about the model failures.
+\tk{Finally, we also test MAC in a novel multi-step transfer learning setup -- if we will add it to the paper.} 
+%This work points out some of the MAC model weaknesses, in particular its failure to differentiate concepts of colors and shape. We finally discuss some improvement possibilities.

### 2018-10-30 2018_nips_vigil/mac.tex

@@
 
-The MAC network~\cite{hudsonManning18} is a recurrent model that performs reasoning 
+The MAC network~\cite{hudson2018compositional} is a recurrent model that performs reasoning 
 using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
@@
 	\includegraphics[width=\textwidth]{img/mac_cell.pdf}
-	\caption{The MAC cell~\cite{hudsonManning18}}
+	\caption{The MAC cell, reproduced on the basis of~\cite{hudson2018compositional}}
 	\label{fig:mac_cell}

### 2018-10-30 2018_nips_vigil/introduction.tex
adding references

@@
 \tk{I have no idea what those papers are...}
-More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection (andreas2016learning; johnson2017inferring, mascharka2018transparency).
+More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
 However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes

### 2018-10-30 2018_nips_vigil/smac.tex

@@
 	\begin{align*}
-	&I_{ihw} = (W_{m}^{[d \times d]} m_{i-1} + b_{m}^{[d]}) \\
-	           & \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{m}^{[d]}) \tag{r1} \\
+	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
+	           & \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
 	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\

### 2018-10-30 2018_nips_vigil/introduction.tex
references mac section

--- 2018-10-30 2018_nips_vigil/introduction.tex
@@
 
-To solve this type of reasoning task, many approaches have been explored although they often appear to struggle performing well on tasks with a structured and compositional nature (Garnelo et al., 2016; Lake et al., 2017).
-\tk{I have no idea what those papers are...}
-More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection (andreas2016learning; johnson2017inferring, mascharka2018transparency).
+To solve this type of reasoning task, many approaches have been explored although they often appear to struggle performing well on tasks with a structured and compositional nature \citep{hudson2018compositional}.
+More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
 However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes

### 2018-10-30 2018_nips_vigil/mac.tex
references mac section

@@
 MAC is performing state of the art accuracy on CLEVR and CLEVR Humans datasets.
-In contrast to modular approaches (Andreas et al., 2016a;b; Hu et al., 2017; Johnson et al., 2017b), MAC is fully
+In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully
 differentiable and does not require additional supervision.
 It is making use of a single computational cell chained in sequence rather than a collection of custom modules deployed in a rigid tree structure.
-In contrast to augmented CNN approaches (Santoro et al., 2017; Perez et al., 2017),  the MAC model provides an ability for relational reasoning with better generalization capacity, higher
-computational efficiency and enhanced transparency.
+In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher
+computational efficiency and enhanced transparency \cite{hudson2018compositional}.
 

### 2018-10-30 2018_nips_vigil/smac.tex
Fixed citation

@@
 while our simplified equations are shown (in color) on the {\color{Plum} \emph{right}}.
-(The equation numbering is the same as in~\cite{hudsonManning18}.)
+(The equation numbering is the same as in~\cite{hudson2018compositional}.)
 
@@
 For both models, in the control unit, the question $q$ is first transformed in each step of 
-the reasoning using a \emph{position-aware}~\cite{hudsonManning18} 
+the reasoning using a \emph{position-aware}~\cite{hudson2018compositional} 
 linear layer: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
@@
 \noindent\textbf{Read and write units:}
-For both models below, $\kb_{hw}$ denotes the \emph{knowledge base}~\cite{hudsonManning18}
+For both models below, $\kb_{hw}$ denotes the 
+\emph{knowledge base}~\cite{hudson2018compositional}
 consisting of 3D tensors with dimension $H \times W \times d$ for each image

### 2018-10-31 2018_nips_vigil/experiments.tex
Added MIP bib position, cleaned up the imported packages, refactored table so it is consistent with NIPS guidelines

@@
 
-We propose to further analyze MAC's generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset.
-It is synthesized in the same way as CLEVR but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
+We analyze MAC's generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset.
+It is synthesized in the same way as CLEVR, but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
 Both conditions contain spheres of all colors.
@@
 
-We implemented the models using PyTorch\footnote{\url{https://pytorch.org/}} (v0.4.0), and the code is available on GitHub\footnote{\url{https://github.com/IBM/mi-prometheus/}}.
-The system is based on Linux 16.04 and we used NVIDIA's GeForce GTX TITAN X.
-We followed the implementation details indicated in the original paper (Section A of the supplementary material), to ensure a faithful comparison.
+We implemented both versions of the MAC model using PyTorch v0.4.0~\cite{paszke2017automatic}.
+We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing of both models\footnote{The code of models along with training settings are available on \url{https://github.com/IBM/mi-prometheus/}}.
+For training we have used NVIDIA's GeForce GTX TITAN X.
+We followed the implementation details indicated in the original paper~\cite{hudson2018compositional} (Section A of the supplementary material), to ensure a faithful comparison.
 
 \begin{table}[]
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& simplified MAC models}
 	\centering
-	\begin{tabular}{|c|c|c|c|c|c|}
-		\hline
-		Model                 & Training set                & \multicolumn{1}{l|}{Training wall time} & Training statistics          & Test set & Test statistics \\ \hline
-		\multirow{3}{*}{MAC}  & CLEVR                       & 31h                                     & acc: 96.7\%                  & CLEVR    & 96.2\%          \\ \cline{2-6} 
-		& \multirow{2}{*}{CoGenT - A} & \multirow{2}{*}{31h}                    & \multirow{2}{*}{acc: 97.0\%} & CoGenT-A & 96.9\%          \\ \cline{5-6} 
-		&                             &                                         &                              & CoGenT-B & 79.5\%          \\ \hline
-		\multirow{3}{*}{SMAC} & CLEVR                       & 28h                                     & acc: 95.8.\%                 & CLEVR    & 95.3\%          \\ \cline{2-6} 
-		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28h}                    & \multirow{2}{*}{acc: 96.1\%} & CoGenT-A & 95.9\%          \\ \cline{5-6} 
-		&                             &                                         &                              & CogenT-B & 78.7\%          \\ \hline
+	\begin{tabular}{cccccc}
+		\toprule
+		Model                 & Training set                & Training time [h] & Training acc [\%]          & Test set & Test acc [\%] \\
+		\midrule
+		\multirow{3}{*}{MAC}  & CLEVR                       & 31                                   & acc: 96.7                  & CLEVR    & 96.2          \\
+		\cmidrule{2-6} 
+		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31}                    & \multirow{2}{*}{acc: 97.0} & CoGenT-A & 96.9         \\
+		\cmidrule{5-6} 
+		&                             &                                         &                              & CoGenT-B & 79.5          \\
+		\midrule
+		\multirow{3}{*}{SMAC} & CLEVR                       & 28                                     & acc: 95.8               & CLEVR    & 95.3          \\
+		\cmidrule{2-6} 
+		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28}                    & \multirow{2}{*}{acc: 96.1} & CoGenT-A & 95.9          \\
+		\cmidrule{5-6} 
+		&                             &                                         &                              & CogenT-B & 78.7          \\
+		\bottomrule
 	\end{tabular}
-	\caption{CLEVR \& CLEVR-CoGenT accuracy for the MAC \& simplified MAC model.}
 	\label{results}

### 2018-10-31 2018_nips_vigil/experiments.tex
experiments

@@
 We implemented both versions of the MAC model using PyTorch v0.4.0~\cite{paszke2017automatic}.
-We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing of both models\footnote{The code of models along with training settings are available on \url{https://github.com/IBM/mi-prometheus/}}.
+We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing of both models\footnote{Code along with training settings are available on \url{https://github.com/IBM/mi-prometheus/}}.
 For training we have used NVIDIA's GeForce GTX TITAN X.
-We followed the implementation details indicated in the original paper~\cite{hudson2018compositional} (Section A of the supplementary material), to ensure a faithful comparison.
+We followed the implementation details indicated in supplemental (Sec.
+A) of the original paper~\cite{hudson2018compositional}, to ensure a faithful comparison.
 
@@
 As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, which surpasses the previously 78.8\% reported in \cite{perez2017film}.
+\tk{not sure why we report this, is it state-of-the-art?}
 The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.

### 2018-10-31 2018_nips_vigil/smac.tex
simple table for parameters reduction
Typo fix

@@
 For both models, in the control unit, the question $q$ is first transformed in each step of 
-the reasoning using a \emph{position-aware}~\cite{hudson2018compositional} 
+%the reasoning using a \emph{position-aware}~\cite{hudson2018compositional} 
 linear layer: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.

### 2018-10-31 2018_nips_vigil/smac.tex
table number of parameters

--- 2018-10-30 2018_nips_vigil/smac.tex
@@
 \end{multicols}
+
+\begin{table}[]
+\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+		\hline
+		                & Read Unit               & Write Unit &  Control Unit       & Input Unit & Output Unit & Overall  \\ \hline
+		  MAC number of parameters  &  787,969 &  524,800        &    6,822,913          &   15,923,712   &   801,308  &       20,138,526           \\  \hline
+		  S-MAC number of arameters  & 263,168  & 262,656       &    6,560,256               &  15,923,712    & 801,308    &       19,089,436           \\  \hline
+		 \% parameters reduction  & -67\%  &   -50\%       &      -4\%               &  0\%    & 0\%    &     -5\%              \\  \hline
+
+	\end{tabular}
+	\caption{Percentage decrease of the number of parameters by unit between MAC and S-MAC models.}
+	\label{results}
+\end{table}

### 2018-10-31 2018_nips_vigil/smac.tex
typo

--- 2018-10-31 2018_nips_vigil/smac.tex
@@
 \end{multicols}
+
+\begin{table}[]
+\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+		\hline
+		                & Read Unit               & Write Unit &  Control Unit       & Input Unit & Output Unit & Overall  \\ \hline
+		  MAC number of parameters  &  787,969 &  524,800        &    6,822,913          &   15,923,712   &   801,308  &       20,138,526           \\  \hline
+		  S-MAC number of parameters  & 263,168  & 262,656       &    6,560,256               &  15,923,712    & 801,308    &       19,089,436           \\  \hline
+		 \% parameters reduction  & -67\%  &   -50\%       &      -4\%               &  0\%    & 0\%    &     -5\%              \\  \hline
+
+	\end{tabular}
+	\caption{Percentage decrease of the number of parameters by unit between MAC and S-MAC models.}
+	\label{results}
+\end{table}

### 2018-10-31 2018_nips_vigil/smac.tex
correct numbers

--- 2018-10-31 2018_nips_vigil/smac.tex
@@
 		                & Read Unit               & Write Unit &  Control Unit       & Input Unit & Output Unit & Overall  \\ \hline
-		  MAC number of parameters  &  787,969 &  524,800        &    6,822,913          &   15,923,712   &   801,308  &       20,138,526           \\  \hline
-		  S-MAC number of arameters  & 263,168  & 262,656       &    6,560,256               &  15,923,712    & 801,308    &       19,089,436           \\  \hline
+		  MAC number of parameters  &  787,969 &  524,800        &    6,822,913          &   11,200,509   &   801,308  &       20,138,526           \\  \hline
+		  S-MAC number of parameters  & 263,168  & 262,656       &    6,560,256               &  11,200,509   & 801,308    &       19,089,436           \\  \hline
 		 \% parameters reduction  & -67\%  &   -50\%       &      -4\%               &  0\%    & 0\%    &     -5\%              \\  \hline

### 2018-10-31 2018_nips_vigil/introduction.tex
Experiments - table with columns for finetuning. Missing dot in the intro

@@
 More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
-However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes
+However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes.
 These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.

### 2018-10-31 2018_nips_vigil/smac.tex
adding new table + new style

--- 2018-10-31 2018_nips_vigil/smac.tex
@@
 \begin{table}[]
+	\caption{Percentage decrease of the number of parameters by units in the MAC Cell between MAC and S-MAC models}
 	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|}
-		\hline
-		                & Read Unit               & Write Unit &  Control Unit       & Input Unit & Output Unit & Overall  \\ \hline
-		  MAC number of parameters  &  787,969 &  524,800        &    6,822,913          &   15,923,712   &   801,308  &       20,138,526           \\  \hline
-		  S-MAC number of arameters  & 263,168  & 262,656       &    6,560,256               &  15,923,712    & 801,308    &       19,089,436           \\  \hline
-		 \% parameters reduction  & -67\%  &   -50\%       &      -4\%               &  0\%    & 0\%    &     -5\%              \\  \hline
-
+	\begin{tabular}{ccccCcCc}
+		\toprule
+	             & Read Unit               & Write Unit &  Control Unit         \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		MAC number of parameters  &  787,969 &  524,800        &    6,822,913    \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
+	    S-MAC number of parameters  & 263,168  & 262,656       &    6,560,768 \\
+	    \cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
+	     \% parameters reduction  & -67\%  &   -50\%       &      -4\%  \\
+		\bottomrule
 	\end{tabular}
-	\caption{Percentage decrease of the number of parameters by unit between MAC and S-MAC models.}
 	\label{results}

### 2018-10-31 2018_nips_vigil/smac.tex
Table 1 explanation

@@
 \begin{table}[]
-	\caption{Percentage decrease of the number of parameters by units in the MAC Cell between MAC and S-MAC models}
+	\caption{Percentage decrease of the number of parameters by units in the MAC Cell between MAC and Simplified-MAC models}
 	\centering
@@
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
-	    S-MAC number of parameters  & 263,168  & 262,656       &    6,560,768 \\
+	    Simplified-MAC number of parameters  & 263,168  & 262,656       &    6,560,768 \\
 	    \cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
@@
 	\end{tabular}
-	\label{results}
 \end{table}
+
+As a result we could decrease the number of trainable parameters.
+Table 1 shows a significant decrease in the number of parameters in the Read and Write units as well as a small drop in the Control unit.
+Those three units combined together compose the MAC cell which is the core of the network.
+It is important to emphasize that the MAC cell is the recurrent part of the network as opposed to the Input and Output unit that are call only once.
+That is why this reduction in the number of parameters is particularly important for the three MAC cell units and why we decided to focus on simplifying those equations.

### 2018-10-31 2018_nips_vigil/mac.tex
Fixing MAC section

@@
 
-The MAC network~\cite{hudson2018compositional} is a recurrent model that performs reasoning 
-using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
+The MAC network~\cite{hudson2018compositional} is a recurrent model that performs
+sequential reasoning, where each step involves analyzing a part of the question following 
+which attention on the image is changed suitably.
 At the end, a suitable answer is given based on this composite reasoning.
-To improve the accuracy of prediction, both the questions and images
-are preprocessed suitably. For the question,  a word-embedding is first used to
-transformed the question into a sequence of vectors which is then passed through
-a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
-corresponds to a unique word in the question and is called the 
-\emph{contextual embedding} for that word.
-Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.
+Both the question and image are transformed suitably prior to the reasoning process. 
+For the question, a sequence of vectors obtained via word-embeddings is fed
+to a bidirectional LSTM to produce a sequence of hidden state pairs. Each pair 
+corresponds to a unique word in the question and denotes its 
+\emph{contextual embedding}. The final states in each direction 
+represent the \emph{global context} of that question.
+Similarly each image is initially processed using a pre-trained network (using ResNet~\cite{he2016resnet}) to obtain a feature map. 
+This is used as an input to a trainable neural network that consists of 
+two CNN layers followed by a single linear layer\footnote{%
+This minor reformulation saves computation time instead of applying it
+in \emph{every} reasoning step.}.
+This results in a 3D tensor for each image in the data set collectively called the
+\emph{knowledge base}~\cite{hudson2018compositional}.
 

### 2018-10-31 2018_nips_vigil/smac.tex
Polishing of table with parameters

@@
 \begin{table}[]
-	\caption{Percentage decrease of the number of parameters by units in the MAC Cell between MAC and Simplified-MAC models}
+	\caption{Numbers of trainable parameters in the units of MAC and simplified MAC cells}
 	\centering
@@
 		\toprule
-	             & Read Unit               & Write Unit &  Control Unit         \\
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		MAC number of parameters  &  787,969 &  524,800        &    6,822,913    \\
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
-	    Simplified-MAC number of parameters  & 263,168  & 262,656       &    6,560,768 \\
-	    \cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
-	     \% parameters reduction  & -67\%  &   -50\%       &      -4\%  \\
+	     Model        & Read Unit               & Write Unit &  Control Unit         \\
+		\midrule
+		MAC   &  787,969 &  524,800        &    6,822,913    \\
+		%\midrule
+	    simplified MAC & 263,168  & 262,656       &    6,560,768 \\
+	    \midrule
+	     Reduction [\%]  & -67\%  &   -50\%       &      -4\%  \\
 		\bottomrule

### 2018-10-31 2018_nips_vigil/smac.tex
Polishing of the paragraph regarding the # of params

@@
 
-\begin{table}[]
-	\caption{Numbers of trainable parameters in the units of MAC and simplified MAC cells}
+\begin{table}
 	\centering
@@
 	\end{tabular}
+	\caption{Numbers of trainable parameters in the units of MAC and simplified MAC cells}
+	\label{tab:parameters}
 \end{table}
 
-As a result we could decrease the number of trainable parameters.
-Table 1 shows a significant decrease in the number of parameters in the Read and Write units as well as a small drop in the Control unit.
-Those three units combined together compose the MAC cell which is the core of the network.
-It is important to emphasize that the MAC cell is the recurrent part of the network as opposed to the Input and Output unit that are call only once.
-That is why this reduction in the number of parameters is particularly important for the three MAC cell units and why we decided to focus on simplifying those equations.
+Our modifications resulted in a significant decrease in the number of parameters in the Read and Write units as well as a small drop in the Control unit, as presented in \tableref{tab:parameters}.
+Those three units combined together compose the MAC cell which is the core of the MAC network.
+It is important to emphasize that the MAC cell is the recurrent part of the network as opposed to the Input and Output units that are called only once.
+That is why we decided to focus on simplifying of those equations, whereas left the other two units unchanged.

### 2018-10-31 2018_nips_vigil/experiments.tex
Experiments - table with columns for finetuning. Missing dot in the intro
double --
tiny changes
Added precise training time.

@@
 	\centering
-	\begin{tabular}{cccccc}
+	\begin{tabular}{ccccCcCc}
 		\toprule
-		Model                 & Training set                & Training time [h] & Training acc [\%]          & Test set & Test acc [\%] \\
+		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& Dataset                & Time [h] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
 		\midrule
-		\multirow{3}{*}{MAC}  & CLEVR                       & 31                                   & acc: 96.7                  & CLEVR    & 96.2          \\
-		\cmidrule{2-6} 
-		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31}                    & \multirow{2}{*}{acc: 97.0} & CoGenT-A & 96.9         \\
-		\cmidrule{5-6} 
-		&                             &                                         &                              & CoGenT-B & 79.5          \\
+		\multirow{3}{*}{MAC}  & CLEVR                       & 31.86         &  --   & --                     & 96.7                  & CLEVR    & 96.2          \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31.86}     &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{97.0} & CoGenT-A & 96.9         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B & 79.5          \\
 		\midrule
-		\multirow{3}{*}{SMAC} & CLEVR                       & 28                                     & acc: 95.8               & CLEVR    & 95.3          \\
-		\cmidrule{2-6} 
-		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28}                    & \multirow{2}{*}{acc: 96.1} & CoGenT-A & 95.9          \\
-		\cmidrule{5-6} 
-		&                             &                                         &                              & CogenT-B & 78.7          \\
+		\multirow{3}{*}{SMAC} & CLEVR                       & 28.51      &   --   &   --                 & 95.8               & CLEVR    & 95.3          \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28.55}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{96.1} & CoGenT-A & 95.9          \\
+		\cmidrule{7-8} 
+		&                             &                                         &     &          &                & CogenT-B & 78.7          \\
 		\bottomrule
@@
 The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.
-Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of ~10\% in wall time.
+Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of 10.5\% in wall time.
 This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.

### 2018-10-31 2018_nips_vigil/experiments.tex
More on experiments section.

@@
 The training procedure is layed out as follows: we train the MAC model (and simplified MAC) for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
-We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets as test sets, given that the ground truth labels for the true test sets are not available.
+We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets as test sets.
+%given that the ground truth labels for the true test sets are not available.
 
 We implemented both versions of the MAC model using PyTorch v0.4.0~\cite{paszke2017automatic}.
-We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing of both models\footnote{Code along with training settings are available on \url{https://github.com/IBM/mi-prometheus/}}.
-For training we have used NVIDIA's GeForce GTX TITAN X.
-We followed the implementation details indicated in supplemental (Sec.
+We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing both variants\footnote{The code \& the training settings are available at \url{https://github.com/IBM/mi-prometheus/}}.
+For training, we used NVIDIA's GeForce GTX TITAN X.
+We followed the implementation details indicated in the  supplemental material (Sec.
 A) of the original paper~\cite{hudson2018compositional}, to ensure a faithful comparison.
@@
 We report the obtained scores in \tableref{results}.
-Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31h of training.\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
+Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31.9h of training.
+The training wall time is coherent with what is reported in the original paper (roughly 30h of training for 20 epochs)\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
 Evaluating MAC on CoGenT shows that, like previous work (\cite{johnson2017inferring}, \cite{mascharka2018transparency})], the performance is worse on Condition B than Condition A after training only using Condition A data.
-As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, which surpasses the previously 78.8\% reported in \cite{perez2017film}.
-\tk{not sure why we report this, is it state-of-the-art?}
+As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, and 96.9\% on Condition A.
 The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.
-Moreover, the simplified MAC presents the advantage to train faster, showing a decrease of 10.5\% in wall time.
+Moreover, it presents the advantage to train faster, showing a decrease of 10.5\% in wall time.
 This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.
+The scores obtained on both conditions are coherent with the ones of MAC, indicating that the simplifications did not hinder its generalization capability.
 
-Following \cite{johnson2017inferring}, we then fine-tune both models using 3k images and 30k questions from the Condition B data.. \textit{To continue later on}.
+Following (\cite{johnson2017inferring}, \cite{perez2017film}), we then fine-tune both models using 3k images and 30k questions from the Condition B data, and re-evaluate them on both conditions.

### 2018-10-31 2018_nips_vigil/mac.tex
Mac and S-Mac rewrite

@@
 Similarly each image is initially processed using a pre-trained network (using ResNet~\cite{he2016resnet}) to obtain a feature map. 
-This is used as an input to a trainable neural network that consists of 
-two CNN layers followed by a single linear layer\footnote{%
-This minor reformulation saves computation time instead of applying it
-in \emph{every} reasoning step.}.
-This results in a 3D tensor for each image in the data set collectively called the
-\emph{knowledge base}~\cite{hudson2018compositional}.
+This is given as an input to a trainable neural network that consists of 
+two CNN layers, resulting in a 3D tensor for each image in the data set. By viewing this
+tensor a collection of 1D vectors in the last dimension, we call this
+the \emph{knowledge base} of that image.
 
@@
 
-The core of the network is a sequence of recurrent MAC cells.
-A MAC cell (Figure 1) is performing one reasoning step.
+The core of the network is a sequence of recurrent MAC cells, each performing one reasoning step (see Figure~\ref{fig:mac_cell}).
 At every step the network is driving the attention on one part of the question and the corresponding part of the image.
-This operation is made possible by the combination of 3 units working together, a control unit, a read and a write units.
+This operation is made possible by the combination of 3 units working together: a control unit, a read unit and a write unit.
 The control unit is updating the control state and drives the attention over the question.
@@
 Finally, the write unit retrieves this visual information and updates the memory state.
-The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.
+The last part of the network is the output unit,  a simple classifier that process the concatenation of the global context  and the final memory state to produce a final answer.
 

### 2018-10-31 2018_nips_vigil/smac.tex
tiny changes
Mac and S-Mac rewrite

@@
 Our proposed modification to the MAC network is based on two heuristic
-simplifications of the equations governing a MAC cell. 
-First, we observed that when looking at the equations of different units
-together as a whole, we notice that there are several affine transformations
+simplifications of the MAC cell. 
+First, we observe that when looking at the equations of different units
+together as a whole, there are several linear layers
 that are applied in sequence (with no activation in-between).
-Therefore they can actually be combined to form a single affine transformation.
-The second observation uses the following heuristic argument:
-suppose there is a single affine transformation which preserves the number
+Therefore they can actually be combined to form a single linear layer.
+The second observation uses the following heuristic assumption:
+suppose there is an affine transformation that preserves the number
 of dimensions. Then one can assume that the transformation is invertible
 so as to avoid a loss in the information. Applying this principle to 
-equations in the read and write unit results in eliminating an affine
-operation of the knowledge base in the recurrent network. Instead we compute
-this operation on the knowledge base right after we apply the 2 
-trainable CNN layers (i.e. prior to the reasoning steps). This results
-in a significant savings in training time, as our experiments demonstrate
+equations in the MAC cell results in eliminating one of the linear layers applied to
+the knowledge base in the cell. With a careful reorganization, we in fact
+can compute this operation on the knowledge base right after we apply the 2 
+ CNN layers on the feature maps (i.e. prior to the reasoning steps). Thus, we can work purely
+with this \emph{projected} knowledge base, that yields
+noticeable savings in training time, as our experiments demonstrate
 below, without incurring too much drop in accuracy.
@@
 
-\noindent\textit{Notation:} The index/position $i$ below denotes the reasoning step. 
+\noindent\textit{Notation.}
+Let $q$ denote the global context of the question
+and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
+For each tensor of dimension $H \times W \times d$ corresponding to an image,
+its knowledge base $\{ \kb_{hw}\}$ is the set of $d$-dimensional vectors indexed by 
+$h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
+The index/position $i$ below denotes the reasoning step. 
 Unless mentioned otherwise, the weights/biases are invariant w.r.t $i$, 
@@
 For both models, in the control unit, the question $q$ is first transformed in each step of 
-%the reasoning using a \emph{position-aware}~\cite{hudson2018compositional} 
-linear layer: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
+the reasoning using a \emph{position-aware}
+linear layer depending on $i$: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
 
@@
 \noindent\textbf{Read and write units:}
-For both models below, $\kb_{hw}$ denotes the 
-\emph{knowledge base}~\cite{hudson2018compositional}
-consisting of 3D tensors with dimension $H \times W \times d$ for each image
-in the data set. The difference in computing $\kb_{hw}$ is that the simplified MAC uses
-an additional linear layer on top of the 2 CNN layers present in the original MAC network.
-This circumvents the need for performing additional linear transformations on the 
-knowledge base, as is done by the original MAC network in \emph{each} reasoning step.
-
 \begin{multicols}{2}
@@
 \end{multicols}
+For the original MAC model shown on the left above, eqn.~(r1) can be slightly optimized for time
+by computing the linear layer on the knowledge base \emph{prior} to the reasoning steps.
+This induces additional space due to storing this projected knowledge base throughout the
+reasoning steps.
 
@@
 	    \midrule
-	     Reduction [\%]  & -67\%  &   -50\%       &      -4\%  \\
+	     Reduction by [\%]  & 67\%  &   50\%       &      4\%  \\
 		\bottomrule

### 2018-10-31 2018_nips_vigil/experiments.tex
Table fixes - put the values of acc in the right place
Modified table with finetuning on CoGenT-B

@@
 \begin{table}[]
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& simplified MAC models}
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
 	\centering
@@
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& Dataset                & Time [h] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
+		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
 		\midrule
-		\multirow{3}{*}{MAC}  & CLEVR                       & 31.86         &  --   & --                     & 96.7                  & CLEVR    & 96.2          \\
+		\multirow{10}{*}{MAC} & \multirow{4}{*}{CLEVR}  & \multirow{4}{*}{30:52}  & \multirow{4}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
+		\cmidrule{7-8} 
+		 &                        &  &               &     &                                & CoGenT-A    &  96.22   \\
+		\cmidrule{7-8} 
+		  &                        &   &              &     &                               & CoGenT-B   & 96.27  \\
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{2}{*}{CoGenT-A} & \multirow{2}{*}{31.86}     &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{97.0} & CoGenT-A & 96.9         \\
+		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B & 79.5          \\
+		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
 		\midrule
-		\multirow{3}{*}{SMAC} & CLEVR                       & 28.51      &   --   &   --                 & 95.8               & CLEVR    & 95.3          \\
+		\multirow{10}{*}{S-MAC} & \multirow{3}{*}{CLEVR}  & \multirow{3}{*}{28:30}  & \multirow{3}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
+		\cmidrule{7-8} 
+		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
+		\cmidrule{7-8} 
+		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\		
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{2}{*}{CoGenT-A}   & \multirow{2}{*}{28.55}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & \multirow{2}{*}{96.1} & CoGenT-A & 95.9          \\
+		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
 		\cmidrule{7-8} 
-		&                             &                                         &     &          &                & CogenT-B & 78.7          \\
+		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  x         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    x       \\
 		\bottomrule

### 2018-10-31 2018_nips_vigil/appendix.tex
Template for appendices

\appendix

\section{Description of datasets}

\section{Full MAC and S-MAC comparison}

\section{Illustration of failures of MAC on CLEVR}

### 2018-10-31 2018_nips_vigil/appendix.tex
Description of content of appendix

@@
 
+\begin{enumerate}
+\item Some description (with link to the paper) about the datasets. Maybe we can "import" material from main paper, making it lighter...
+\item Table with attributes/feature combinations of CLEVR/CoGenT-A/CoGenT-B
+\item Some exemplary pictures?
+\end{enumerate}
+
 \section{Full MAC and S-MAC comparison}
 
+We think that in the main paper we should leave:
+\begin{itemize}
+\item first row - MAC - train on CLEVR, test on CLEVR 
+\item all rows regaring S-MAC
+\end{itemize}
+
+When we will fill the whole table we will copy the results in here.
+
 \section{Illustration of failures of MAC on CLEVR}
+
+\begin{itemize}
+\item one with color failure -- that the attention is pointing at the right object, whereas the answer is improper because he never saw this combination
+\item one with shape failure -- similarly	
+\end{itemize}
+Pictures with some description

### 2018-10-31 2018_nips_vigil/appendix.tex
table: colors/shapes combinations between CLEVR, CLEVR CoGenT-A and CLEVR CoGenT-B

@@
 \item Table with attributes/feature combinations of CLEVR/CoGenT-A/CoGenT-B
+
+\begin{table}
+	\centering
+	\begin{tabular}{ccccCcCc}
+		\toprule
+		Dataset        & Cubes              & Cylinders &  Spheres         \\
+		\midrule
+		CLEVR   &  any color &  any color        &    any color    \\
+		%\midrule
+		CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
+		CLEVR CoGenT B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
+		\bottomrule
+	\end{tabular}
+	\caption{Comparison of the different colors/shapes combinations between CLEVR, CLEVR CoGenT-A and CLEVR CoGenT-B  }
+	\label{tab:parameters}
+\end{table}
+
 \item Some exemplary pictures?

### 2018-11-01 2018_nips_vigil/appendix.tex

@@
 
-\begin{enumerate}
-\item Some description (with link to the paper) about the datasets. Maybe we can "import" material from main paper, making it lighter...
-\item Table with attributes/feature combinations of CLEVR/CoGenT-A/CoGenT-B
+Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input ~\cite{Santoro2017ASN}
+The CLEVR dataset ~\cite{johnson2017clevr}  was developed to address those issues and come back to the core challenge of visual QA which is reasoning  \href{url}{https://arxiv.org/pdf/1612.06890.pdf}.\\
+CLEVR contains images of 3D-rendered objects, such as spheres and cylinders.
+Each image is associated with a number of questions that fall into different categories.
+For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask “Is the cube the same material as the cylinder?
+”.
+The dataset consist of:
+\begin{itemize}
+\item 	A training set of 70k images and 700k questions
+\item	A test  set of 15k images and 150k questions about objects
+\item	A validation set of 15k images and 150k 
+\item	Answers, scene graphs and functional programs for all train and val images and questions
+
+\end{itemize}
+
+The dataset features unbiased, highly compositional questions that require an array of challenging reasoning skills, such as transitive and logical relations, counting and comparisons, without allowing any shortcuts around such reasoning ~\cite{hudson2018compositional}.
+
+To test how well models learn compositional concepts that generalize, CLEVR-CoGenT was introduced .
+This dataset is synthesized in the same way as CLEVR but contains two conditions.
+As shown in Table 3 in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
+Both conditions contain spheres of all colors.
+CLEVR-CoGenT thus indicates how a model answers CLEVR questions: by memorizing combinations of traits or by learning disentangled or general representations ~\cite{perez2017film}
+
+This dataset consists of:
+\begin{itemize}
+\item	A training set of 70,000 images and 699,960 questions in Condition A
+\item	A validation set of 15,000 images and 150,000 questions in Condition A
+\item	A validation set of 15,000 images and 149,991 questions in Condition B
+\item	A test set of 15,000 images and 149,980 questions in Condition B
+\item	A test set of 15,000 images and 149,992 questions in Condition B
+\item	Answers, scene graphs and functional programs for all train and val images and questions
+\end{itemize}
 
@@
 \end{table}
-
-\item Some exemplary pictures?
-\end{enumerate}
 

### 2018-11-01 2018_nips_vigil/conclusion.tex
conclusion - first draft

\section{Conclusion}
We have introduced SMAC, a simplified version on the MAC model. This version has simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model. As a result we could decrease training time by more than two hours while maintaining an equivalent test accuracy. 
We have also put to test the MAC and SMAC models on a novel task, the CLEVR CoGenT dataset.
It is a structured dataset especially designed to study transfer learning and generalization abilities. The results of our experiments first show that MAC and SMAC perform equally well on all the CoGenT task. Thus the simplifications did not alter SMAC generalization capability.
Furthermore, MAC and SMAC compare favorably with state-of-the-art models on the CoGenT taks. MAC and SMAC present competitive generalization and transfer learning capacities.
Nevertheless, CLEVR CoGenT remains an unsolved problem. The MAC model still struggles to learn distinct concepts. We could see that MAC sometimes fail to differentiate colors and shape as two distinct features of the same object.

+ Ppening on future work
+ Tomasz’s comment on finetuning

### 2018-11-01 2018_nips_vigil/appendix.tex
minor clean up
minor clean up 2

@@
 \item 	A training set of 70k images and 700k questions
-\item	A test  set of 15k images and 150k questions about objects
+\item	A test  set of 15k images and 150k questions 
 \item	A validation set of 15k images and 150k 
+ questions
 \item	Answers, scene graphs and functional programs for all train and val images and questions
@@
 \item	A validation set of 15,000 images and 149,991 questions in Condition B
-\item	A test set of 15,000 images and 149,980 questions in Condition B
+\item	A test set of 15,000 images and 149,980 questions in Condition A
 \item	A test set of 15,000 images and 149,992 questions in Condition B

### 2018-11-01 2018_nips_vigil/appendix.tex
typo

@@
 
-Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input ~\cite{Santoro2017ASN}
-The CLEVR dataset ~\cite{johnson2017clevr}  was developed to address those issues and come back to the core challenge of visual QA which is reasoning  \href{url}{https://arxiv.org/pdf/1612.06890.pdf}.\\
+Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input ~\cite{Santoro2017ASN}.
+The CLEVR dataset ~\cite{johnson2017clevr}  \href{url}{https://arxiv.org/pdf/1612.06890.pdf}  was developed to address those issues and come back to the core challenge of visual QA which is reasoning  .\\
 CLEVR contains images of 3D-rendered objects, such as spheres and cylinders.

### 2018-11-01 2018_nips_vigil/appendix.tex
Wrote appendix c.

--- 2018-11-01 2018_nips_vigil/appendix.tex
@@
 \section{Illustration of failures of MAC on CLEVR}
+Following the evaluation of MAC on CoGenT-B, we built a tool which helped us visualizing the attention of the model over the question words and the image, and thus provide insight on some cases of failure.
 
-\begin{itemize}
-\item one with color failure -- that the attention is pointing at the right object, whereas the answer is improper because he never saw this combination
-\item one with shape failure -- similarly	
-\end{itemize}
-Pictures with some description
+\begin{figure}[]
+	\centering
+	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_shape.png}
+	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
+	\label{fig:fail_mac_shape}
+\end{figure}
+
+\begin{figure}[]
+	\centering
+	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_color.png}
+	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
+	\label{fig:fail_mac_color}
+\end{figure}
+
+\fig{fig:fail_mac_shape} presents a question where the model is asked about the shape of the leftmost gray cylinder.
+The model correctly finds it, as we can see from its visual attention map, and appears to refer to it using its color (\textit{gray}), as we can see from the attention of the question words.
+Yet, it defaults to predicting the shape as \textit{cube}, because it never saw gray cylinders during training, but instead saw gray cubes.
+
+\fig{fig:fail_mac_color} presents a similar case, where the model is questioned about the color of the green cube at the back.
+MAC misses that object, and instead focuses on the nearby gray cylinder.
+We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus default to a combination that it knows.
+
+Those examples indicate that MAC did not correctly separate the concept of shape from the concept of color, but have a better understanding of the colors (as it found the object of interest in \fig{fig:fail_mac_shape} by its color).
+This could come from that fact that the shape \textit{sphere} is associated with all possible colors in the dataset.

### 2018-11-01 2018_nips_vigil/experiments.tex
Modified table with positions to ve filled
adding 1 result
Added more results in table.
More results.
Added more results to table.
Final table.
Wrote appendix c.

@@
 
-The training procedure is layed out as follows: we train the MAC model (and simplified MAC) for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
+The training procedure is as follows: we train the MAC model (and simplified MAC) for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
 We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets as test sets.
@@
 		\midrule
-		\multirow{10}{*}{MAC} & \multirow{4}{*}{CLEVR}  & \multirow{4}{*}{30:52}  & \multirow{4}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
+		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
 		\cmidrule{7-8} 
@@
 		  &                        &   &              &     &                               & CoGenT-B   & 96.27  \\
+
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    93.28       \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    94.44       \\
+
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
@@
 		\midrule
-		\multirow{10}{*}{S-MAC} & \multirow{3}{*}{CLEVR}  & \multirow{3}{*}{28:30}  & \multirow{3}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
+		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
 		\cmidrule{7-8} 
@@
 		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\
+
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    92.31       \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    92.95       \\
+
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
@@
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  x         \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24         \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    x       \\
+		&                             &                                         &       &         &                & CoGenT-B &    94.55       \\
 		\bottomrule
@@
 
-Following (\cite{johnson2017inferring}, \cite{perez2017film}), we then fine-tune both models using 3k images and 30k questions from the Condition B data, and re-evaluate them on both conditions.
+Following (\cite{johnson2017inferring}, \cite{perez2017film}), we then fine-tune both models using 3k images and 30k questions from the Condition B data (for 10 epochs), and re-evaluate them on both conditions.
+This enables both models to perform much better on CoGenT-B, as we observe a 15 points increase for the accuracy.
+Performance on CoGenT-A is slightly worse, dropping of ~4\%.
+This indicates that MAC is able to learn new combinations of shape \& color without forgetting the ones it learned during the initial training.
+
+Additionally, we have been able to diagnose interesting cases of failure on CoGenT-B. Please refer to Appendix B for more details.

### 2018-11-01 2018_nips_vigil/appendix.tex

@@
 Each image is associated with a number of questions that fall into different categories.
-For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask “Is the cube the same material as the cylinder?
+For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask "Is the cube the same material as the cylinder?
 ”.

### 2018-11-01 2018_nips_vigil/conclusion.tex

@@
 We have introduced SMAC, a simplified version on the MAC model.
-This version has simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model.
-As a result we could decrease training time by more than two hours while maintaining an equivalent test accuracy.
+This version proposes simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model.
+As a result we could decrease training time by more than two hours ( reduction by almost 10 \%)
+while maintaining an equivalent test accuracy. 
 We have also put to test the MAC and SMAC models on a novel task, the CLEVR CoGenT dataset.
@@
 
-+ Ppening on future work
++ Opening on future work/ideas
 + Tomasz’s comment on finetuning

### 2018-11-01 2018_nips_vigil/introduction.tex
clean up - intro + mac

@@
 VQA is a complex semantic task that combines natural language processing and visual recognition.
-In order to answer the questions the system  requires to master several perceptual abilities, such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge~\citep{hudson2018compositional}.
+In order to answer the questions, the system requires to master several perceptual abilities, such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge~\citep{hudson2018compositional}.
 
@@
 However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes.
-These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
+These models' structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
 \tk{Compositional models are one major direction of research in VQA...

### 2018-11-01 2018_nips_vigil/appendix.tex
work on appendix

--- 2018-11-01 2018_nips_vigil/appendix.tex
@@
 
-Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input ~\cite{Santoro2017ASN}.
-The CLEVR dataset ~\cite{johnson2017clevr}  \href{url}{https://arxiv.org/pdf/1612.06890.pdf}  was developed to address those issues and come back to the core challenge of visual QA which is reasoning  .\\
+Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input~\cite{Santoro2017ASN}.
+The CLEVR dataset~\cite{johnson2017clevr} was developed to address those issues and come back to the core challenge of visual QA which is reasoning.
 CLEVR contains images of 3D-rendered objects, such as spheres and cylinders.
-Each image is associated with a number of questions that fall into different categories.
-For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask “Is the cube the same material as the cylinder?
-”.
-The dataset consist of:
+Each image is associated with a number of highly compositional questions that fall into different categories.
+Those categories fall into 5 classes of tasks: Exist, Count, Compare Integer, Query Attribute and Compare Attribute. 
+For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask “Is the cube the same material as the cylinder? ”.
+The CLEVR dataset consists of:
 \begin{itemize}
-\item 	A training set of 70k images and 700k questions
-\item	A test  set of 15k images and 150k questions 
-\item	A validation set of 15k images and 150k 
- questions
-\item	Answers, scene graphs and functional programs for all train and val images and questions
+\item 	A training set of 70k images and 700k questions,
+\item	A validation set of 15k images and 150k questions,
+\item	A test  set of 15k images and 150k questions about objects,
+\item	Answers, scene graphs and functional programs for all train and val images and questions.
+\end{itemize}
+Each object present in the scene, aside of position, is characterized by a set of four attributes:
+\begin{itemize}
+\item 2 sizes: large, small,
+\item 3 shapes: square, cylinder, sphere,
+\item 2 material types: rubber, metal,
+\item 8 color types: gray, blue, brown, yellow, red, green, purple, cyan,
+\end{itemize}
+resulting in 96 unique combinations.
 
+Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of testing how well the models can learn and generalizer compositional concepts.
+This dataset is synthesized in the same way as CLEVR,, but contains two conditions.
+As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
+Both conditions contain spheres of all colors.
+CoGenT thus indicates how a model answers CLEVR questions: by memorizing combinations of traits or by learning disentangled or general representations.
+The CoGenT dataset contains:
+\begin{itemize}
+\item	A training set of 70,000 images and 699,960 questions in Condition A,
+\item	A validation set of 15,000 images and 150,000 questions in Condition A,
+\item	A validation set of 15,000 images and 149,991 questions in Condition B,
+\item	A test set of 15,000 images and 149,980 questions in Condition B,
+\item	A test set of 15,000 images and 149,992 questions in Condition B,
+\item	Answers, scene graphs and functional programs for all training and validation images and questions.
 \end{itemize}
 
-The dataset features unbiased, highly compositional questions that require an array of challenging reasoning skills, such as transitive and logical relations, counting and comparisons, without allowing any shortcuts around such reasoning ~\cite{hudson2018compositional}.
-
-To test how well models learn compositional concepts that generalize, CLEVR-CoGenT was introduced .
-This dataset is synthesized in the same way as CLEVR but contains two conditions.
-As shown in Table 3 in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
-Both conditions contain spheres of all colors.
-CLEVR-CoGenT thus indicates how a model answers CLEVR questions: by memorizing combinations of traits or by learning disentangled or general representations ~\cite{perez2017film}
-
-This dataset consists of:
-\begin{itemize}
-\item	A training set of 70,000 images and 699,960 questions in Condition A
-\item	A validation set of 15,000 images and 150,000 questions in Condition A
-\item	A validation set of 15,000 images and 149,991 questions in Condition B
-\item	A test set of 15,000 images and 149,980 questions in Condition A
-\item	A test set of 15,000 images and 149,992 questions in Condition B
-\item	Answers, scene graphs and functional programs for all train and val images and questions
-\end{itemize}
-
-\begin{table}
+\begin{table}[h!]
 	\centering
-	\begin{tabular}{ccccCcCc}
+	\begin{tabular}{cccc}
 		\toprule
@@
 	\end{tabular}
-	\caption{Comparison of the different colors/shapes combinations between CLEVR, CLEVR CoGenT-A and CLEVR CoGenT-B  }
-	\label{tab:parameters}
+	\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets}
+	\label{tab:cogent_conditions}
 \end{table}
@@
 
-We think that in the main paper we should leave:
-\begin{itemize}
-\item first row - MAC - train on CLEVR, test on CLEVR 
-\item all rows regaring S-MAC
-\end{itemize}
+In \tableref{tab:results_full} we present the full comparison between MAC and S-MAC models.
 
-When we will fill the whole table we will copy the results in here.
+\begin{table}
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
+	\centering
+	\begin{tabular}{ccccCcCc}
+		\toprule
+		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
+		\midrule
+		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
+		\cmidrule{7-8} 
+		&                        &  &               &     &                                & CoGenT-A    &  96.22   \\
+		\cmidrule{7-8} 
+		&                        &   &              &     &                               & CoGenT-B   & 96.27  \\
+
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    93.28       \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    94.44       \\
+
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
+		\midrule
+		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
+		\cmidrule{7-8} 
+		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
+		\cmidrule{7-8} 
+		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\
+
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    92.31       \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    92.95       \\
+
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
+		\cmidrule{7-8} 
+		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24         \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    94.55       \\
+		\bottomrule
+	\end{tabular}
+	\label{tab:results_full}
+\end{table}
+
+\section{Comparison of generalization capabilities}
+
+In this section we present comparison of MAC and S-MAC with selected state-of-the-art models as reported in~\cite{mascharka2018transparency} \tk{and? FiLM?}
+
+\begin{table}[!h]
+	\caption{Generalization capabilities of selected state-of-the-art models}
+	\centering
+	\begin{tabular}{cCcCcCc}
+		\toprule
+		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
+		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
+		(source)& CoGenT-A set & Acc [\%]  & CoGenT-B set & Acc [\%]  & CoGenT set~ & Acc [\%] \\
+
+\midrule				
+& \multirow{5}{*}{Training Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test?    &   96.6  \\
+\cmidrule{6-7} 
+PG+EE &   &    &   &    & B Test Full?    &   73.7  \\
+\cmidrule{4-5}\cmidrule{6-7}
+(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test?    &   76.1 \\
+\cmidrule{6-7} 
+&   &    &   &    & B Test Full?    &   92.7  \\
+
+\midrule				
+& \multirow{5}{*}{xxx}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   AAA    &     \\
+\cmidrule{6-7} 
+MAC &   &    &   &    & BBB    &     \\
+\cmidrule{4-5}\cmidrule{6-7}
+(\cite{hudson2018compositional}) &  &    & \multirow{2}{*}{CoGenT-B}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
+\cmidrule{6-7} 
+&   &    &   &    & CoGenT-B    &    \\
+
+\midrule				
+& \multirow{5}{*}{A Train 670k}   & \multirow{5}{*}{xx}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid 30k    &     \\
+\cmidrule{6-7} 
+MAC &   &    &   &    & CoGenT-B    &     \\
+\cmidrule{4-5}\cmidrule{6-7}
+(ours) &  &    & \multirow{2}{*}{CoGenT-B 30k}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
+\cmidrule{6-7} 
+&   &    &   &    & CoGenT-B    &    \\
+
+\midrule				
+& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   CoGenT-A    &     \\
+\cmidrule{6-7} 
+S-MAC &   &    &   &    & CoGenT-B    &     \\
+\cmidrule{4-5}\cmidrule{6-7}
+(ours) &  &    & \multirow{2}{*}{CoGenT-B 30k}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
+\cmidrule{6-7} 
+&   &    &   &    & CoGenT-B    &    \\
+
+		\bottomrule
+	\end{tabular}
+	\label{tab:generalization_comparison}
+\end{table}
+
+\subsection{The PG+EE model and training methodology}
+The PG+EE (Program Generator and Execution Engine)~\cite{johnson2017inferring}  model is composed of two main modules:
+a Program Generator constructing an explicit, graph-like representation of the reasoning process, and an Execution Engine executing that program and producing an answer. 
+Both modules are implemented by neural networks, and were trained using a combination of backpropagation and REINFORCE~\cite{williams1992simple}.
+
+The author inform that in the first step they trained their models on Condition A, and tested them on both Condition A and Condition B. 
+Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both Conditions.
+Sadly, it is not clear what sets exactly they used for fine-tuning (as Condition B contains only test set, thus lack training set) and testing on Condition A (as Condition A does not offer test set).
+One possibility, as they are the authors of CLEVR and CoGenT datasets, is that they actually generated the missing sets, but didn't share them publicly.
+
+\subsection{The FiLM model and training methodology}
+
+\subsection{The TbD model and training methodology}
+
+\subsection{Our MAC and S-MAC models and methodology}
+
+Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, the authors of~\cite{mascharka2018transparency} decided to split
+the CoGenT validation sets and use part of then for training, and part for testing. 
+We decided to follow that approach and ... \tk{Vincent, please proceed :)}
 

### 2018-11-01 2018_nips_vigil/introduction.tex
Updated intro.

--- 2018-10-31 2018_nips_vigil/introduction.tex
@@
 Reproducing this ability with artificial systems is a challenge that requires learning relations and compositionality~\citep{hu2017learning, johnson2017inferring}.
-The Visual Question Answering (VQA)~\citep{antol2015vqa,malinowski2014towards,wu2017visual} task has been tailored to benchmark those reasoning performances.
-VQA is a complex semantic task that combines natural language processing and visual recognition.
-In order to answer the questions the system  requires to master several perceptual abilities, such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge~\citep{hudson2018compositional}.
+The Visual Question Answering (VQA)~\citep{antol2015vqa,malinowski2014towards,wu2017visual} task has been tailored to benchmark this type of reasoning, combining natural language processing and visual recognition.
 
-To solve this type of reasoning task, many approaches have been explored although they often appear to struggle performing well on tasks with a structured and compositional nature \citep{hudson2018compositional}.
-More recent approaches adopt modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
-However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes.
-These models’ structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
-\tk{Compositional models are one major direction of research in VQA...
+%VQA is a complex semantic task that combines natural language processing and visual recognition.
+%In order to answer the questions the system  requires to master several perceptual abilities, such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge~\citep{hudson2018compositional}.
+
+Many approaches have been explored, 
+%although they often appear to struggle on tasks with a structured and compositional nature \citep{hudson2018compositional}.
+such as modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
+The attention mechanism (\cite{bahdanau2014neural}, \cite{xu2015show}) is also frequently used to guide the focus of the system over the image and the question words.
+Other approaches such as \vm{Ask Tomasz what he is thinking about.}.
+
+%However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes.
+%These models' structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
+%\tk{Compositional models are one major direction of research in VQA...
 but there are 3 others (including e.g.
@@
 
-There are many datasets for VQA such as DAQUAR~\citep{malinowski2014multi} or VQA~\citep{antol2015vqa}.
-The problem is they contain several biases (e.g.
+VQA datasets exist, such as DAQUAR~\citep{malinowski2014multi} or VQA~\citep{antol2015vqa}.
+Nonetheless, these datasets contain several biases (e.g.
 unbalanced questions or answers) that are often exploited by systems during learning~\citep{goyal2017making}.
-The CLEVR dataset~\citep{johnson2017clevr} was designed to address that issue.
-And besides that, due to the synthetic nature of the images, it also enables detailed analysis of visual reasoning.
-CLEVR also allows to introduce variations on a subset of data to test a particular ability such as generalization or transfer learning.
+The CLEVR dataset~\citep{johnson2017clevr} was designed to address those issues.
+The synthetic nature of its images enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning.
+In this direction, CLEVR-CoGenT is a constrained compositional generalization test, measuring if models learn separate representations for color and shape instead of memorizing all possible color/shape combinations.
 
-One of the most recent models aiming at solving VQA is called MAC (Memory, Attention, and Composition)~\citep{hudson2018compositional}.
-The MAC model has been deliberately designed to decompose the problem into a sequence of attention-based reasoning operations.
-MAC uses three general units working in tandem to perform a reasoning step make the robustness of the model.
-The MAC  model achieved state-of-the-art accuracy on CLEVR.
-The authors also tested in on the difficult CLEVR Humans dataset, were the questions (regarding synthetically generated images) were written by humans. 
-Although the performance of MAC has been proven, it appeared to have difficulties with understanding what concepts the model is learning. 
-So several questions appeared.
+One of the most recent models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\citep{hudson2018compositional}, which decomposes the problem into a sequence of attention-based reasoning operations.
+%MAC uses three general units working in tandem to perform a reasoning step make the robustness of the model.
+%The MAC  model achieved state-of-the-art accuracy on CLEVR.
+%The authors also tested in on the difficult CLEVR Humans dataset, were the questions (regarding synthetically generated images) were written by humans. 
+Although the performance of MAC has been proven, 
+%it appeared to have difficulties with understanding what concepts the model is learning. 
+several questions arose:
 Does the model really learn relations between objects? 
-How does the model represent those relations and reasoning steps? 
-Is the model representing notions and concepts like objects attributes?
-Those questions indicate that the interpretability of the MAC model seems yet to be fully defined.
+How does the model represent these relations in its reasoning steps? 
+Is the model representing notions and concepts like objects attributes(shape, color, size)?
+Those questions indicate that the interpretability of MAC can be further investigated.
 
@@
 Second, we put to proof the MAC model on the CLEVR CoGenT dataset. 
-The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability.
+%The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability.
 By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned.

### 2018-11-01 2018_nips_vigil/introduction.tex
Updates.

@@
 such as modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
-The attention mechanism (\cite{bahdanau2014neural}, \cite{xu2015show}) is also frequently used to guide the focus of the system over the image and the question words.
-Other approaches such as \vm{Ask Tomasz what he is thinking about.}.
+Attention mechanisms (\cite{bahdanau2014neural}, \cite{xu2015show}) are also frequently used to guide the focus of the system over the image and the question words.
+%Other approaches such as \vm{Ask Tomasz what he is thinking about.}.
 
@@
 
-VQA datasets exist, such as DAQUAR~\citep{malinowski2014multi} or VQA~\citep{antol2015vqa}.
-Nonetheless, these datasets contain several biases (e.g.
+Several VQA datasets have been proposed (e.g.
+DAQUAR~\citep{malinowski2014multi}, VQA~\citep{antol2015vqa}); nonetheless, these datasets contain several biases (e.g.
 unbalanced questions or answers) that are often exploited by systems during learning~\citep{goyal2017making}.
-The CLEVR dataset~\citep{johnson2017clevr} was designed to address those issues.
-The synthetic nature of its images enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning.
-In this direction, CLEVR-CoGenT is a constrained compositional generalization test, measuring if models learn separate representations for color and shape instead of memorizing all possible color/shape combinations.
+The CLEVR dataset~\citep{johnson2017clevr} was designed to address these issues.
+The synthetic nature of its images \& questions enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning.
+One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations.
 
-One of the most recent models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\citep{hudson2018compositional}, which decomposes the problem into a sequence of attention-based reasoning operations.
+One of the most recent exciting models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\citep{hudson2018compositional}, which performs a sequence of attention-based reasoning operations.
 %MAC uses three general units working in tandem to perform a reasoning step make the robustness of the model.
@@
 %it appeared to have difficulties with understanding what concepts the model is learning. 
-several questions arose:
+several questions arise:
 Does the model really learn relations between objects? 
 How does the model represent these relations in its reasoning steps? 
-Is the model representing notions and concepts like objects attributes(shape, color, size)?
-Those questions indicate that the interpretability of MAC can be further investigated.
+Is the model representing concepts like objects attributes (shape, color, size)?
 
-In this work we focus on that issue.
-First, we question the complexity of the MAC model and explore simplification possibilities.
-We propose a new set of equations that aims at simplification of the model and improvement of training performance.
-Second, we put to proof the MAC model on the CLEVR CoGenT dataset. 
+In this work, we further investigate the interpretability and generalization capabilities of the MAC model.
+We propose a new set of equations that simplifies the core of the model (S-MAC). It trains faster and achieves comparable accuracy on CLEVR. 
+Second, we evaluate the generalization capabilities of both MAC \& S-MAC on the CoGenT dataset. 
 %The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability.
 By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned.
-We show how MAC performs on CLEVR CoGenT and propose a study about the model failures.
+%We show how MAC performs on CLEVR CoGenT and propose a study about the model failures.
 \tk{Finally, we also test MAC in a novel multi-step transfer learning setup -- if we will add it to the paper.} 

### 2018-11-01 2018_nips_vigil/mac.tex
clean up - intro + mac
Shorteninf of MAC section, picked several experiment results from table 2

--- 2018-10-30 2018_nips_vigil/mac.tex
@@
 \section{MAC network and our proposed simplification}
-
-The MAC network~\cite{hudson2018compositional} is a recurrent model that performs reasoning 
-using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
-At the end, a suitable answer is given based on this composite reasoning.
-To improve the accuracy of prediction, both the questions and images
-are preprocessed suitably. For the question,  a word-embedding is first used to
-transformed the question into a sequence of vectors which is then passed through
-a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
-corresponds to a unique word in the question and is called the 
-\emph{contextual embedding} for that word.
-Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.
 
@@
 
-The core of the network is a sequence of recurrent MAC cells.
-A MAC cell (Figure 1) is performing one reasoning step.
-At every step the network is driving the attention on one part of the question and the corresponding part of the image.
-This operation is made possible by the combination of 3 units working together, a control unit, a read and a write units.
-The control unit is updating the control state and drives the attention over the question.
-Given this control state, the read unit then retrieves information from the memory and drives the attention over the image.
-Finally, the write unit retrieves this visual information and updates the memory state.
-The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.
+The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting of attention over the image.
+The core of the model is the MAC cell, supported with an input unit that processes question and image pair, and output unit which produces the answer.% (a two layer MLP).
+The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
+Besides, the input unit utilizes a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.
 
-By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them.
-MAC is performing state of the art accuracy on CLEVR and CLEVR Humans datasets.
-In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully
-differentiable and does not require additional supervision.
-It is making use of a single computational cell chained in sequence rather than a collection of custom modules deployed in a rigid tree structure.
-In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher
-computational efficiency and enhanced transparency \cite{hudson2018compositional}.
+The MAC cell consists of a control unit, a read unit and a write unit (\Fig{fig:mac_cell}).
+The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} $cw$ taking into account the \emph{question representation} $q$.
+Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $KB$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
+Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state.
+
+%The MAC network reached state-of-the-art accuracy on the CLEVR dataset.
+%In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher computational efficiency and enhanced transparency.
+
+%In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully differentiable and does not require additional supervision.
 

### 2018-11-01 2018_nips_vigil/mac.tex
symbols refinement

@@
 The MAC cell consists of a control unit, a read unit and a write unit (\Fig{fig:mac_cell}).
-The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} $cw$ taking into account the \emph{question representation} $q$.
-Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $KB$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
+The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} \textbf{cw} taking into account the \emph{question representation} $q$.
+Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} \textbf{k} and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
 Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state.

### 2018-11-01 2018_nips_vigil/mac.tex
update

--- 2018-11-01 2018_nips_vigil/mac.tex
@@
 The MAC cell consists of a control unit, a read unit and a write unit (\Fig{fig:mac_cell}).
-The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} $cw$ taking into account the \emph{question representation} $q$.
-Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $KB$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
+The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} $\cw$ taking into account the \emph{question representation} $q$.
+Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $\kb$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
 Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state.

### 2018-11-01 2018_nips_vigil/introduction.tex

@@
 %although they often appear to struggle on tasks with a structured and compositional nature \citep{hudson2018compositional}.
-such as modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
+such as modular networks, that combine modules coming from a predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
 Attention mechanisms (\cite{bahdanau2014neural}, \cite{xu2015show}) are also frequently used to guide the focus of the system over the image and the question words.

### 2018-11-01 2018_nips_vigil/mac.tex
Vincent's changes

@@
 
-The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting of attention over the image.
-The core of the model is the MAC cell, supported with an input unit that processes question and image pair, and output unit which produces the answer.% (a two layer MLP).
+The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting the attention over the image.
+The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
 The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
@@
 Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $\kb$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
-Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state.
-
-%The MAC network reached state-of-the-art accuracy on the CLEVR dataset.
-%In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher computational efficiency and enhanced transparency.
-
-%In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully differentiable and does not require additional supervision.
+Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state. Detailed equations are described in the next section.
 

### 2018-11-01 2018_nips_vigil/smac.tex
Shorteninf of MAC section, picked several experiment results from table 2
Vincent's changes

@@
 Therefore they can actually be combined to form a single linear layer.
-The second observation uses the following heuristic assumption:
+The second observation is:
 suppose there is an affine transformation that preserves the number
@@
 equations in the MAC cell results in eliminating one of the linear layers applied to
-the knowledge base in the cell. With a careful reorganization, we in fact
+the knowledge base in the cell. With a careful reorganization, we
 can compute this operation on the knowledge base right after we apply the 2 
@@
 while our simplified equations are shown (in color) on the {\color{Plum} \emph{right}}.
-(The equation numbering is the same as in~\cite{hudson2018compositional}.)
+The equation numbering is the same as in~\cite{hudson2018compositional}.
 

### 2018-11-01 2018_nips_vigil/appendix.tex

@@
 
-Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input~\cite{Santoro2017ASN}.
+Most of the VQA datasets have strong biases. This allow models to learn strategies without reasoning about the visual input~\cite{Santoro2017ASN}.
 The CLEVR dataset~\cite{johnson2017clevr} was developed to address those issues and come back to the core challenge of visual QA which is reasoning.
-CLEVR contains images of 3D-rendered objects, such as spheres and cylinders.
-Each image is associated with a number of highly compositional questions that fall into different categories.
+CLEVR contains images of 3D-rendered objects; each image comes with a number of highly compositional questions that fall into different categories.
 Those categories fall into 5 classes of tasks: Exist, Count, Compare Integer, Query Attribute and Compare Attribute. 
-For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask “Is the cube the same material as the cylinder? ”.
 The CLEVR dataset consists of:
@@
 
-Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of testing how well the models can learn and generalizer compositional concepts.
-This dataset is synthesized in the same way as CLEVR,, but contains two conditions.
+Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of testing how well the models can learn and generalize compositional concepts.
+This dataset is synthesized in the same way as CLEVR, but contains two conditions.
 As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.

### 2018-11-01 2018_nips_vigil/appendix.tex
Appendix A - cleaning

@@
 
-Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of testing how well the models can learn and generalize compositional concepts.
-This dataset is synthesized in the same way as CLEVR, but contains two conditions.
+Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
+This dataset is generated in the same way as CLEVR with two additional conditions.
 As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
-Both conditions contain spheres of all colors.
-CoGenT thus indicates how a model answers CLEVR questions: by memorizing combinations of traits or by learning disentangled or general representations.
+For both conditions spheres can be any colors.
+
+The CoGenT task give a sense on how the model solve CLEVR question. Is the model learning combination of attributes or general representations?
+
 The CoGenT dataset contains:

### 2018-11-02 2018_nips_vigil/appendix.tex
Comparison on CoGenT, external values

--- 2018-11-01 2018_nips_vigil/appendix.tex
@@
 \begin{itemize}
-\item	A training set of 70,000 images and 699,960 questions in Condition A,
-\item	A validation set of 15,000 images and 150,000 questions in Condition A,
-\item	A validation set of 15,000 images and 149,991 questions in Condition B,
-\item	A test set of 15,000 images and 149,980 questions in Condition B,
-\item	A test set of 15,000 images and 149,992 questions in Condition B,
+\item	Training set of 70,000 images and 699,960 questions in Condition A,
+\item	Validation set of 15,000 images and 149,991 questions in Condition A,
+\item	Test set of 15,000 images and 149,980 questions in Condition A (without answers),
+\item	Validation set of 15,000 images and 150,000 questions in Condition B,
+\item	Test set of 15,000 images and 149,992 questions in Condition B (without answers),
 \item	Answers, scene graphs and functional programs for all training and validation images and questions.
@@
 		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
-		(source)& CoGenT-A set & Acc [\%]  & CoGenT-B set & Acc [\%]  & CoGenT set~ & Acc [\%] \\
+		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\
 
 \midrule				
-& \multirow{5}{*}{Training Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test?    &   96.6  \\
+& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test Full    &   96.6  \\
 \cmidrule{6-7} 
@@
 \cmidrule{4-5}\cmidrule{6-7}
-(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test?    &   76.1 \\
+(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test Full    &   76.1 \\
 \cmidrule{6-7} 
@@
 \midrule				
-& \multirow{5}{*}{xxx}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   AAA    &     \\
+CNN+GRU+FiLM & \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full?    &  98.3   \\
 \cmidrule{6-7} 
-MAC &   &    &   &    & BBB    &     \\
+0-Shot &   &    &   &    & B Valid 120k    &   78.8  \\
 \cmidrule{4-5}\cmidrule{6-7}
-(\cite{hudson2018compositional}) &  &    & \multirow{2}{*}{CoGenT-B}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
+(\cite{perez2017film}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A Valid Full?    & 81.1  \\
 \cmidrule{6-7} 
-&   &    &   &    & CoGenT-B    &    \\
+&   &    &   &    & B Valid 120k    &  96.9  \\
 
 \midrule				
-& \multirow{5}{*}{A Train 670k}   & \multirow{5}{*}{xx}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid 30k    &     \\
+& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A ?    &  98.8   \\
 \cmidrule{6-7} 
-MAC &   &    &   &    & CoGenT-B    &     \\
+TbD + reg &   &    &   &    & B ?    &  75.4   \\
 \cmidrule{4-5}\cmidrule{6-7}
-(ours) &  &    & \multirow{2}{*}{CoGenT-B 30k}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
+(\cite{mascharka2018transparency}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A ?    &  96.9 \\
 \cmidrule{6-7} 
-&   &    &   &    & CoGenT-B    &    \\
+&   &    &   &    & B ?   &  96.3  \\
 
 \midrule				
-& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   CoGenT-A    &     \\
+& \multirow{5}{*}{A Train 630k}   & \multirow{5}{*}{97.02}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full    &     96.88 \\
 \cmidrule{6-7} 
-S-MAC &   &    &   &    & CoGenT-B    &     \\
+MAC &   &    &   &    & B Valid Full   &  79.54   \\
 \cmidrule{4-5}\cmidrule{6-7}
-(ours) &  &    & \multirow{2}{*}{CoGenT-B 30k}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
+(our results) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{97.91}     & A Valid Full    &  92.06 \\
 \cmidrule{6-7} 
-&   &    &   &    & CoGenT-B    &    \\
+&   &    &   &    & B Valid 120k    &   95.62 \\
+
+\midrule				
+& \multirow{5}{*}{A Train 630k}   & \multirow{5}{*}{96.09}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full    &     95.91 \\
+\cmidrule{6-7} 
+S-MAC &   &    &   &    & B Valid Full   &  78.71   \\
+\cmidrule{4-5}\cmidrule{6-7}
+(our results) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{96.85}     & A Valid Full    &  91.24 \\
+\cmidrule{6-7} 
+&   &    &   &    & B Valid 120k    &   94.55 \\
 
@@
 
+\cite{perez2017film})
+
+We train our best model architecture on Condition A and report accuracies on Conditions A and B, before and
+after fine-tuning on B, in Figure 9. Our results indicate FiLM
+surpasses other visual reasoning models at learning general
+concepts.
+
+FiLM ValB accuracy reported on ValB without the 30K fine-tuning samples 
+Accuracy before and after fine-tuning on 30K of ValB
+
+Training A
+
 \subsection{The TbD model and training methodology}
+
+Performance comparison against the current state-of-the-
+art model on the CoGenT dataset having trained only on Condition
+A data (middle column) and after fine-tuning on a small amount
+of data with novel attributes (right column).
+
+Like pre-
+vious  work  [14],  our  performance  is  worse  on  Condition
+B than Condition A after training only using Condition A
+data.  As Table 3 shows, our model achieves 98.8\% accu-
+racy on Condition A, but only 75.4\% on Condition B. Fol-
+lowing Johnson
+et al
+. [14], we then fine-tune our model us-
+ing 3k images and 30k questions from the Condition B data.
+Whereas other models see a significant drop in performance
+on the Condition A data after fine-tuning, our model main-
+tains high performance.  As Table 3 shows, our model can
+effectively learn from a small amount of Condition B data.
+We achieve 96.9\% accuracy on Condition A and 96.3\% ac-
+curacy on Condition B after fine-tuning, far surpassing the
+highest-reported 76.1\% Condition A and 92.7\% Condition
+B accuracy.
 

### 2018-11-02 2018_nips_vigil/appendix.tex
minor clean up

@@
 Most of the VQA datasets have strong biases. This allow models to learn strategies without reasoning about the visual input~\cite{Santoro2017ASN}.
-The CLEVR dataset~\cite{johnson2017clevr} was developed to address those issues and come back to the core challenge of visual QA which is reasoning.
+The CLEVR dataset~\cite{johnson2017clevr} was developed to address those issues and come back to the core challenge of visual QA which is testing reasoning abilities.
 CLEVR contains images of 3D-rendered objects; each image comes with a number of highly compositional questions that fall into different categories.
@@
 
-The CoGenT task give a sense on how the model solve CLEVR question. Is the model learning combination of attributes or general representations?
+The CoGenT task allow us to see whether the model learns combination of attributes or general representations.
 

### 2018-11-02 2018_nips_vigil/appendix.tex
Appendix, table with comparison of CoGenT results collected from different papers + explanation why and how we collected that data

--- 2018-11-02 2018_nips_vigil/appendix.tex
@@
 
-The CoGenT task give a sense on how the model solve CLEVR question. Is the model learning combination of attributes or general representations?
-
 The CoGenT dataset contains:
@@
 
+ \newpage
 \section{Full MAC and S-MAC comparison}
@@
 
-\begin{table}
+\begin{table}[!h]
 	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
@@
 
-In this section we present comparison of MAC and S-MAC with selected state-of-the-art models as reported in~\cite{mascharka2018transparency} \tk{and? FiLM?}
+In this section we present comparison of our results on generalization capabilities with selected state-of-the-art models.
+In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
+Deeper analysis of the papers revealed that it is most probable that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
+We find that the problems result from the fact that answers for the test sets aren't provided along with those sets, thus researchers started to use subsets of the validation set for testing. 
+The results of our research are presented in \tableref{tab:generalization_comparison}.
+In the table we had to shorten the names of the datasets.
+For example,  \textbf{A Test Full} means utilization of the whole \textbf{CoGenT Condition A Test set}, whereas  \textbf{B Valid 30k} indicates utilization of 30.000 samples from \textbf{CoGenT Condition B Validation set}.
+Question marks indicate that the paper does not provide enough information and those are the sets we assumed were used.
 
 \begin{table}[!h]
-	\caption{Generalization capabilities of selected state-of-the-art models}
 	\centering
@@
 	\end{tabular}
+	\caption{Generalization capabilities of selected state-of-the-art models}
 	\label{tab:generalization_comparison}
@@
 Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both Conditions.
-Sadly, it is not clear what sets exactly they used for fine-tuning (as Condition B contains only test set, thus lack training set) and testing on Condition A (as Condition A does not offer test set).
+Sadly, it is not clear what sets exactly they used for fine-tuning (as Condition B lacks the training set).
 One possibility, as they are the authors of CLEVR and CoGenT datasets, is that they actually generated the missing sets, but didn't share them publicly.
+Besides, as they posses answers for both CoGenT Condition A and Condition B test sets, we are almost sure that they reported the accuracies on both Condition A and Condition B test sets.
 
@@
 
-\cite{perez2017film})
+Feature-wise Linear Modulation (in short, FiLM)~\cite{perez2017film} is an optional enhancement of a neural network model.
+The idea is to influence the behavior of existing layer(s) by introducing a feature-wise affine transformations that are conditioned on the input.
+A model composed of FiLM enhanced CNN and GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing few percent of improvements over the PG+EE model.
 
-We train our best model architecture on Condition A and report accuracies on Conditions A and B, before and
-after fine-tuning on B, in Figure 9. Our results indicate FiLM
-surpasses other visual reasoning models at learning general
-concepts.
-
-FiLM ValB accuracy reported on ValB without the 30K fine-tuning samples 
-Accuracy before and after fine-tuning on 30K of ValB
-
-Training A
+The problem with the presented comparison is that the authors used different sets for collecting the results, i.e.
+in the paper they clearly indicate that accuracies reported for Condition B after fine-tuning were calculated on CoGenT Condition B Validation set, excluding the 30k samples that were used for that fine-tuning.
+This also suggests that they probably reported scores for CoGenT Condition A Validation set,
+whereas, as it was mentioned previously, the original PG+EE paper probably relied on test sets in both cases.
 
@@
 
-Performance comparison against the current state-of-the-
-art model on the CoGenT dataset having trained only on Condition
-A data (middle column) and after fine-tuning on a small amount
-of data with novel attributes (right column).
+The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
+TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composes a series of attention mask.
+The authors compare the accuracy of their model while tested on CLEVR  with several existing models, including mentioned PG + EE, CNN + GRU + FiLM and MAC, and once again indicate improvement.
 
-Like pre-
-vious  work  [14],  our  performance  is  worse  on  Condition
-B than Condition A after training only using Condition A
-data.  As Table 3 shows, our model achieves 98.8\% accu-
-racy on Condition A, but only 75.4\% on Condition B. Fol-
-lowing Johnson
-et al
-. [14], we then fine-tune our model us-
-ing 3k images and 30k questions from the Condition B data.
-Whereas other models see a significant drop in performance
-on the Condition A data after fine-tuning, our model main-
-tains high performance.  As Table 3 shows, our model can
-effectively learn from a small amount of Condition B data.
-We achieve 96.9\% accuracy on Condition A and 96.3\% ac-
-curacy on Condition B after fine-tuning, far surpassing the
-highest-reported 76.1\% Condition A and 92.7\% Condition
-B accuracy.
+They also compare accuracy on CoGenT, by comparison with PG+EE.
+Despite the results show clear improvement, the section clearly lacks the most important information, i.e. which sets were used for training, fine-tuning and testing. 
+The only provided information for sure is that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model following~\cite{johnson2017inferring}, but do not mention from which set they took the samples.
 
@@
 
-Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, the authors of~\cite{mascharka2018transparency} decided to split
-the CoGenT validation sets and use part of then for training, and part for testing. 
-We decided to follow that approach and ... \tk{Vincent, please proceed :)}
+Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, the authors of~\cite{perez2017film} decided to split
+the CoGenT A Validation sets and use 30k samples for fine-tuning and the remaining part for testing.
+When testing the model on CoGenT B, we used the whole Validation set.
+In the experiments when we were using Validation B for fine-tuning, we did it analogically.
+Besides that, as we were using Validation sets for testing, we also splitted the training set and used 90\% for training and remaining 10\% for validation during training.
 
@@
 
-\begin{figure}[]
+\fig{fig:fail_mac_shape} presents a question where the model is asked about the shape of the leftmost gray cylinder.
+The model correctly finds it, as we can see from its visual attention map, and appears to refer to it using its color (\textit{gray}), as we can see from the attention of the question words.
+Yet, it defaults to predicting the shape as \textit{cube}, because it never saw gray cylinders during training, but instead saw gray cubes.
+
+\fig{fig:fail_mac_color} presents a similar case, where the model is questioned about the color of the green cube at the back.
+MAC misses that object, and instead focuses on the nearby gray cylinder.
+We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus default to a combination that it knows.
+
+\begin{figure}[htbp]
 	\centering
@@
 
-\fig{fig:fail_mac_shape} presents a question where the model is asked about the shape of the leftmost gray cylinder.
-The model correctly finds it, as we can see from its visual attention map, and appears to refer to it using its color (\textit{gray}), as we can see from the attention of the question words.
-Yet, it defaults to predicting the shape as \textit{cube}, because it never saw gray cylinders during training, but instead saw gray cubes.
-
-\fig{fig:fail_mac_color} presents a similar case, where the model is questioned about the color of the green cube at the back.
-MAC misses that object, and instead focuses on the nearby gray cylinder.
-We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus default to a combination that it knows.
-
 Those examples indicate that MAC did not correctly separate the concept of shape from the concept of color, but have a better understanding of the colors (as it found the object of interest in \fig{fig:fail_mac_shape} by its color).

### 2018-11-02 2018_nips_vigil/experiments.tex
Shorteninf of MAC section, picked several experiment results from table 2
More work.

@@
 
-We analyze MAC's generalization and transfer learning abilities by testing it on the CLEVR-CoGenT dataset.
-It is synthesized in the same way as CLEVR, but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
+We analyze MAC's generalization and transfer learning abilities by testing it on the CoGenT dataset.
+%It is synthesized in the same way as CLEVR, but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
 Both conditions contain spheres of all colors.
@@
 
-We implemented both versions of the MAC model using PyTorch v0.4.0~\cite{paszke2017automatic}.
-We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing both variants\footnote{The code \& the training settings are available at \url{https://github.com/IBM/mi-prometheus/}}.
-For training, we used NVIDIA's GeForce GTX TITAN X.
-We followed the implementation details indicated in the supplemental material (Sec.
-A) of the original paper~\cite{hudson2018compositional}, to ensure a faithful comparison.
-
 \begin{table}[]
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
 	\centering
@@
 		\midrule
-		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
-		\cmidrule{7-8} 
-		 &                        &  &               &     &                                & CoGenT-A    &  96.22   \\
-		\cmidrule{7-8} 
-		  &                        &   &              &     &                               & CoGenT-B   & 96.27  \\
-
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    93.28       \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.44       \\
-
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
+		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17          \\
 		\midrule
-		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
+		\multirow{13}{*}{S-MAC} & \multirow{7}{*}{CLEVR}  & \multirow{7}{*}{28:30}  & \multirow{7}{*}{95.82} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 95.29           \\
 		\cmidrule{7-8} 
@@
 
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.31       \\
 		\cmidrule{5-6} \cmidrule{7-8} 
@@
 
+We implemented both versions of the MAC model using PyTorch (v0.4.0)~\cite{paszke2017automatic}.
+We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing both variants\footnote{The code \& the training settings are available at \url{https://github.com/IBM/mi-prometheus/}}.
+For training, we used NVIDIA's GeForce GTX TITAN X GPUs.
+We followed the implementation details indicated in the supplemental material (Sec.
+A) of the original paper~\cite{hudson2018compositional}, to ensure a faithful comparison.
+
 We report the obtained scores in \tableref{results}.
-Taking the evaluation of MAC on CLEVR as a reference experiment, it yields an accuracy of 96.2\%, obtained after 31.9h of training.
-The training wall time is coherent with what is reported in the original paper (roughly 30h of training for 20 epochs)\vmf{Not sure if we should explain in more details why there's a 3\% gap..}
-Evaluating MAC on CoGenT shows that, like previous work (\cite{johnson2017inferring}, \cite{mascharka2018transparency})], the performance is worse on Condition B than Condition A after training only using Condition A data.
+The evaluation of MAC on CLEVR yields an accuracy of 96.2\%, obtained after 31.9h of training, and is taken as a reference experiment.
+The training wall time is coherent with what is reported in the original paper (roughly 30h of training for 20 epochs).
+S-MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.
+Moreover, it presents the advantage to train faster, as supported by the reductions in the number of parameters, showing a decrease of 10.5\% in wall time.
+
+Evaluating MAC on CoGenT shows that, like previous work \cite{johnson2017inferring, mascharka2018transparency}, the performance is worse on Condition B than Condition A after training only sing Condition A data.
 As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, and 96.9\% on Condition A.
-The simplified MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.
-Moreover, it presents the advantage to train faster, showing a decrease of 10.5\% in wall time.
+S-MAC obtains comparable performance (78.71\%)
 This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.

### 2018-11-02 2018_nips_vigil/smac.tex
More work.

@@
 simplifications of the MAC cell. 
-First, we observe that when looking at the equations of different units
-together as a whole, there are several linear layers
-that are applied in sequence (with no activation in-between).
-Therefore they can actually be combined to form a single linear layer.
-The second observation is:
-suppose there is an affine transformation that preserves the number
-of dimensions. Then one can assume that the transformation is invertible
-so as to avoid a loss in the information. Applying this principle to 
-equations in the MAC cell results in eliminating one of the linear layers applied to
-the knowledge base in the cell. With a careful reorganization, we
-can compute this operation on the knowledge base right after we apply the 2 
- CNN layers on the feature maps (i.e. prior to the reasoning steps). Thus, we can work purely
-with this \emph{projected} knowledge base, that yields
-noticeable savings in training time, as our experiments demonstrate
-below, without incurring too much drop in accuracy.
+First, we observe that, taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
+Next, we assume that dimension-preserving linear layers are invertible
+so as to avoid information loss. 
+Applying this principle to the equations, with a careful reorganization,
+we can apply a single linear layer to the knowledge base \emph{prior}
+to all the reasoning steps and work with this \emph{projected} knowledge base
+as-is throughout the reasoning steps.
+
+%Applying this principle to 
+%equations in the MAC cell results in eliminating one of the linear layers applied to
+%the knowledge base.
+Having reduced the number of linear projections on the knowledge base to one, we can, with a careful reorganization, compute it prior to the reasoning steps.
+Thus, we can work purely
+%with this \emph{projected} knowledge base.
 
@@
 \noindent\textit{Notation.}
-Let $q$ denote the global context of the question
-and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
-For each tensor of dimension $H \times W \times d$ corresponding to an image,
-its knowledge base $\{ \kb_{hw}\}$ is the set of $d$-dimensional vectors indexed by 
+%Let $q$ denote the global context of the question
+%and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
+For each knowledge base $\kb$, a tensor of dimension $H \times W \times d$, let $\kb_{hw}$ be the $d$-dimensional vector indexed by 
 $h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
-The index/position $i$ below denotes the reasoning step. 
-Unless mentioned otherwise, the weights/biases are invariant w.r.t $i$, 
-i.e., shared across all the reasoning steps.
+Let $i$ denote the index (position) $i$ of the reasoning step.
 
@@
 
+\begin{table}[hb]
+	\centering
+	\begin{tabular}{ccccCcCc}
+		\toprule
+		Model        & Read Unit               & Write Unit &  Control Unit         \\
+		\midrule
+		MAC   &  787,969 &  524,800        &    525,313    \\
+		%\midrule
+		simplified MAC & 263,168  & 262,656       &    263,168 \\
+		\midrule
+		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
+		\bottomrule
+	\end{tabular}
+	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells. }
+	\label{tab:parameters}
+\end{table}
+
+\newpage
+
 \noindent\textbf{Read and write units:}
@@
 \end{multicols}
-For the original MAC model shown on the left above, eqn.~(r1) can be slightly optimized for time
-by computing the linear layer on the knowledge base \emph{prior} to the reasoning steps.
-This induces additional space due to storing this projected knowledge base throughout the
-reasoning steps.
 
-\begin{table}
-	\centering
-	\begin{tabular}{ccccCcCc}
-		\toprule
-	     Model        & Read Unit               & Write Unit &  Control Unit         \\
-		\midrule
-		MAC   &  787,969 &  524,800        &    6,822,913    \\
-		%\midrule
-	    simplified MAC & 263,168  & 262,656       &    6,560,768 \\
-	    \midrule
-	     Reduction by [\%]  & 67\%  &   50\%       &      4\%  \\
-		\bottomrule
-	\end{tabular}
-	\caption{Numbers of trainable parameters in the units of MAC and simplified MAC cells}
-	\label{tab:parameters}
-\end{table}
-
-Our modifications resulted in a significant decrease in the number of parameters in the Read and Write units as well as a small drop in the Control unit, as presented in \tableref{tab:parameters}.
-Those three units combined together compose the MAC cell which is the core of the MAC network.
-It is important to emphasize that the MAC cell is the recurrent part of the network as opposed to the Input and Output units that are called only once.
-That is why we decided to focus on simplifying of those equations, whereas left the other two units unchanged.
+As seen above, being noticeably simpler, the S-MAC obtains significant reduction in the number of position-independent parameters across all units (see~\tableref{tab:parameters}).
+Our experiments demonstrate that this gives us noticeable savings in the training time.
+However, since the computation time is also dominated by the position-aware layers in the control unit, as well as the input unit, the speedup is not as large as we desire.

### 2018-11-02 2018_nips_vigil/conclusion.tex

@@
 We have introduced SMAC, a simplified version on the MAC model.
-This version proposes simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model.
+Our version proposes simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model.
 As a result we could decrease training time by more than two hours ( reduction by almost 10 \%)
 while maintaining an equivalent test accuracy. 
-We have also put to test the MAC and SMAC models on a novel task, the CLEVR CoGenT dataset.
-It is a structured dataset especially designed to study transfer learning and generalization abilities.
-The results of our experiments first show that MAC and SMAC perform equally well on all the CoGenT task.
-Thus the simplifications did not alter SMAC generalization capability.
+We have also evaluated generalization capabilities of MAC and S-MAC on the CLEVR CoGenT dataset.
+The results of our experiments first show that MAC and SMAC perform equally well on all the CoGenT task. Thus the simplifications did not alter SMAC generalization capability.
 Furthermore, MAC and SMAC compare favorably with state-of-the-art models on the CoGenT taks. MAC and SMAC present competitive generalization and transfer learning capacities.
@@
 We could see that MAC sometimes fail to differentiate colors and shape as two distinct features of the same object.
-
-+ Opening on future work/ideas
-+ Tomasz’s comment on finetuning

### 2018-11-02 2018_nips_vigil/smac.tex

@@
 simplifications of the MAC cell. 
-First, we observe that, taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
+First, we observe that taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
 Next, we assume that dimension-preserving linear layers are invertible
@@
 Our experiments demonstrate that this gives us noticeable savings in the training time.
-However, since the computation time is also dominated by the position-aware layers in the control unit, as well as the input unit, the speedup is not as large as we desire.
+However, since the computation time is also dominated by the position-aware layers in the Control Unit as well as the input unit so the speedup is not as large as we desire.

### 2018-11-02 2018_nips_vigil/experiments.tex

@@
 As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, and 96.9\% on Condition A.
-S-MAC obtains comparable performance (78.71\%)
-This point also holds true when training on CoGenT: not only does the simplified model trains faster, it also presents comparable performance when evaluated on both conditions.
-The scores obtained on both conditions are coherent with the ones of MAC, indicating that the simplifications did not hinder its generalization capability.
+S-MAC obtains comparable performance (78.71\%), and still maintains the shorter training time.
+The comparable performance indicate that the simplifications did not hinder its generalization capability.
 
-Following (\cite{johnson2017inferring}, \cite{perez2017film}), we then fine-tune both models using 3k images and 30k questions from the Condition B data (for 10 epochs), and re-evaluate them on both conditions.
+Following \cite{johnson2017inferring, perez2017film}), we then fine-tune both models using 3k images and 30k questions from the Condition B data (for 10 epochs), and re-evaluate them on both conditions.
 This enables both models to perform much better on CoGenT-B, as we observe a 15 points increase for the accuracy.
 Performance on CoGenT-A is slightly worse, dropping of ~4\%.
-This indicates that MAC is able to learn new combinations of shape \& color without forgetting the ones it learned during the initial training.
+This seems to indicate that MAC is able to learn new combinations of shape \& color without forgetting the ones it learned during the initial training.
 
-Additionally, we have been able to diagnose interesting cases of failure on CoGenT-B. Please refer to Appendix B for more details.
+Nonetheless, MAC does not appear to separate the concepts of shape and color.
+We have analyzed cases of failure of MAC on CoGenT-B, which illustrate this point.
+Please refer to Appendix C for more details.

### 2018-11-02 2018_nips_vigil/experiments.tex
experi

@@
 \begin{table}[]
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.
+The [Training] column indicates wall time and final accuracy on the training set.
+For fine-tuning, we use 30k samples of the test set, and the remaining is kept for testing.
+The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracy on this sub-set during training.
+The [Test] column reports the used set and the obtained test accuracy.
+If no fine-tuning was done, the whole indicated set was used for testing.}
 	\centering
@@
 This seems to indicate that MAC is able to learn new combinations of shape \& color without forgetting the ones it learned during the initial training.
-
 Nonetheless, MAC does not appear to separate the concepts of shape and color.
@@
 Please refer to Appendix C for more details.
+
+We have conducted additional experiments to explore the

### 2018-11-02 2018_nips_vigil/appendix.tex

@@
 
-The author inform that in the first step they trained their models on Condition A, and tested them on both Condition A and Condition B. 
-Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both Conditions.
+The authors inform that in the first step they trained their models on Condition A, and tested them on both Condition A and Condition B. 
+Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
 Sadly, it is not clear what sets exactly they used for fine-tuning (as Condition B lacks the training set).
@@
 The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
-TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composes a series of attention mask.
-The authors compare the accuracy of their model while tested on CLEVR  with several existing models, including mentioned PG + EE, CNN + GRU + FiLM and MAC, and once again indicate improvement.
+TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing  attention masks.
+The authors compare the accuracy of their model while tested on CLEVR  with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM and MAC, and once again indicate improvement.
 
 They also compare accuracy on CoGenT, by comparison with PG+EE.
-Despite the results show clear improvement, the section clearly lacks the most important information, i.e. which sets were used for training, fine-tuning and testing. 
-The only provided information for sure is that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model following~\cite{johnson2017inferring}, but do not mention from which set they took the samples.
+Despite the results show improvement, the description clearly lacks the most important information, i.e. which sets were used for training, fine-tuning and testing. 
+The only provided information indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not mention from which set they took the samples.
+However, as they mention that they were following~\cite{johnson2017inferring}, it is possible that they used the test sets.
 
@@
 
-Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, the authors of~\cite{perez2017film} decided to split
-the CoGenT A Validation sets and use 30k samples for fine-tuning and the remaining part for testing.
-When testing the model on CoGenT B, we used the whole Validation set.
-In the experiments when we were using Validation B for fine-tuning, we did it analogically.
-Besides that, as we were using Validation sets for testing, we also splitted the training set and used 90\% for training and remaining 10\% for validation during training.
+Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, we decided to follow the approach proposed in~\cite{perez2017film} and split the CoGenT A Validation set.
+As a result we used 30k samples for fine-tuning and the remaining part for testing.
+When testing the model on CoGenT B, we used the whole validation set.
+In the experiments when we were using Validation B for fine-tuning, we did the analogical operations.
+Besides that, as we were using validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
 
@@
 MAC misses that object, and instead focuses on the nearby gray cylinder.
-We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus default to a combination that it knows.
+We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus defaulted to a combination that it knows.
 

### 2018-11-02 2018_nips_vigil/experiments.tex
more

@@
 
-We analyze MAC's generalization and transfer learning abilities by testing it on the CoGenT dataset.
-%It is synthesized in the same way as CLEVR, but contains two conditions: in Condition A, all cubes are gray, blue, brown, or yellow and all cylinders are red, green, purple, or cyan; in Condition B, cubes and cylinders swap color palettes.
-Both conditions contain spheres of all colors.
-We also evaluate the simplified model on this dataset for comparison.
+Our experiments were intended to understand MAC's and S-MAC's generalization as well as transfer learning abilities in different settings.
+We used the CLEVR and the CoGenT dataset(s) to address these different aspects.
+The first experiment studied the amount of training time and capability of the models to generalize on the same type of dataset that it was trained on.
+This was used mainly to both compare as a baseline for the further experiments that were intended to stuidy how well the transfer learning performed in comparision to the baseline.
+The second experiment studied the capability of the models to succeed in doing transfer learning from domain A to domain B when trained on different combinations of the training data from domain A and test data from domain B.
+The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
 
-The training procedure is as follows: we train the MAC model (and simplified MAC) for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
+For all the experiments the initial training procedure is as follows: we train the MAC model (and S-MAC) for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
 We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets as test sets.
@@
 
-We implemented both versions of the MAC model using PyTorch (v0.4.0)~\cite{paszke2017automatic}.
-We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework for training and testing both variants\footnote{The code \& the training settings are available at \url{https://github.com/IBM/mi-prometheus/}}.
-For training, we used NVIDIA's GeForce GTX TITAN X GPUs.
+Our implementation of both MAC models used PyTorch (v0.4.0)~\cite{paszke2017automatic}.
+We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework that enables fast experimentation of the cross product of models and datasets\footnote{Link available upon request, hidden here for reasons of anonymity.}.
+%The code \& experiment settings are available at \url{https://github.com/IBM/mi-prometheus/}}.
+We used NVIDIA's GeForce GTX TITAN X GPUs.
 We followed the implementation details indicated in the supplemental material (Sec.
@@
 
-We report the obtained scores in \tableref{results}.
-The evaluation of MAC on CLEVR yields an accuracy of 96.2\%, obtained after 31.9h of training, and is taken as a reference experiment.
-The training wall time is coherent with what is reported in the original paper (roughly 30h of training for 20 epochs).
+The entire set of results for both models are reported in˜\tableref{results}. 
+For the CLEVR dataset, the training wall time of MAC is consistent with what is reported in the original paper (roughly 30h of training for 20 epochs).
+S-MAC trains faster, showing a decrease of 10.5\% in wall time, due to the reductions in the 
+number of parameters as shown earlier.
+
+We now turn to the generalization performance. 
+The evaluation of MAC on CLEVR yields an accuracy of 96.2\%,
+
+ and is taken as a reference experiment. The training wall time is coherent with what is reported in the original paper (roughly 30h of training for 20 epochs).
 S-MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.
 Moreover, it presents the advantage to train faster, as supported by the reductions in the number of parameters, showing a decrease of 10.5\% in wall time.
+Training both models on CoGenT A
 

### 2018-11-02 2018_nips_vigil/experiments.tex
THE TABLEEEEE

@@
 
-Our experiments were intended to understand MAC's and S-MAC's generalization as well as transfer learning abilities in different settings.
-We used the CLEVR and the CoGenT dataset(s) to address these different aspects.
-The first experiment studied the amount of training time and capability of the models to generalize on the same type of dataset that it was trained on.
-This was used mainly to both compare as a baseline for the further experiments that were intended to stuidy how well the transfer learning performed in comparision to the baseline.
-The second experiment studied the capability of the models to succeed in doing transfer learning from domain A to domain B when trained on different combinations of the training data from domain A and test data from domain B.
+Our experiments were intended to study MAC's and S-MAC's generalization as well as transfer learning abilities in different settings. We used CLEVR and CoGenT to address these different aspects.
+The first experiment studied the training time and the capability of the models to generalize on the same type of dataset that it was trained on.
+This was used mainly as a baseline for the further experiments that were intended to study how well the transfer learning performed in comparison to the baseline results.
+The second experiment studied the capability of the models to succeed in doing transfer learning from domain A to domain B when trained on different combinations of the respective domains.
 The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
 
-For all the experiments the initial training procedure is as follows: we train the MAC model (and S-MAC) for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
+For all experiments, the initial training procedure is as follows: we train the given model  for 20 epochs on 90\% of the training sets of CLEVR \& CoGenT separately.
 We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets as test sets.
 %given that the ground truth labels for the true test sets are not available.
-
-\begin{table}[]
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.
-The [Training] column indicates wall time and final accuracy on the training set.
-For fine-tuning, we use 30k samples of the test set, and the remaining is kept for testing.
-The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracy on this sub-set during training.
-The [Test] column reports the used set and the obtained test accuracy.
-If no fine-tuning was done, the whole indicated set was used for testing.}
-	\centering
-	\begin{tabular}{ccccCcCc}
-		\toprule
-		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
-		\midrule
-		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17          \\
-		\midrule
-		\multirow{13}{*}{S-MAC} & \multirow{7}{*}{CLEVR}  & \multirow{7}{*}{28:30}  & \multirow{7}{*}{95.82} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 95.29           \\
-		\cmidrule{7-8} 
-		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
-		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\
-
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.95       \\
-
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
-		\cmidrule{7-8} 
-		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.55       \\
-		\bottomrule
-	\end{tabular}
-	\label{results}
-\end{table}
 
@@
 
+\begin{table}[t]
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.
+The [Training] column indicates wall time and final accuracy on the training set.
+For fine-tuning, we use 30k samples of the test set, and the remaining is kept for testing.
+The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracy on this sub-set during training.
+The [Test] column reports the used set and the obtained test accuracy.
+If no fine-tuning was done, the whole indicated set was used for testing.}
+	\centering
+	\begin{tabular}{cccccCcCC}
+		\toprule
+		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{N$^{o}$} \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
+		\midrule
+		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & A \\
+		\cmidrule{1-8}
+		\cmidrule{1-8}
+
+		 \multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29         & B  \\
+		 \cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
+
+		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91        & C  \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
+
+		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47  & D \\
+		\cmidrule{7-8} 
+		&                        &   &              &     &                               & CoGenT-B   &  95.58  & E\\
+
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71        & F  \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24        & G \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    94.55     & H  \\
+
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11       & I  \\
+\cmidrule{7-8} 
+&                             &                                         &       &         &                & CoGenT-B &    92.95    & J   \\
+
+		\bottomrule
+	\end{tabular}
+	\label{results}
+\end{table}
+
 The entire set of results for both models are reported in˜\tableref{results}. 
@@
 number of parameters as shown earlier.
+This was consistently observed across the other experiments as well.
 
-We now turn to the generalization performance. 
-The evaluation of MAC on CLEVR yields an accuracy of 96.2\%,
+Turning to the generalization performance,  MAC on CLEVR yields an accuracy of 96.2\%, which is 
+taken as a reference experiment. S-MAC reaches an accuracy of 95.3\% on CLEVR, indicating that 
+the simplifications did not hinder its generalization capability.
+Similar performances were observed for generalization on CoGenT-A.
 
- and is taken as a reference experiment. The training wall time is coherent with what is reported in the original paper (roughly 30h of training for 20 epochs).
-S-MAC reaches an accuracy of 95.3\% on CLEVR, which is close to the reference score.
-Moreover, it presents the advantage to train faster, as supported by the reductions in the number of parameters, showing a decrease of 10.5\% in wall time.
-Training both models on CoGenT A
+Before fine-tuning, we wanted to estimate the best upper bounds on accuracy that we could possibly get by doing transfer learning.
+As both CoGenT datasets contain complementary subsets of colors/shapes  combinations present in CLEVR, 
+we evaluated CLEVR-trained models on the CoGenT datasets.
+Even though the CoGenT datasets were generated using more restricted parameters, the models obtained nearly equal accuracy.
 
-Evaluating MAC on CoGenT shows that, like previous work \cite{johnson2017inferring, mascharka2018transparency}, the performance is worse on Condition B than Condition A after training only sing Condition A data.
-As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on Condition B, and 96.9\% on Condition A.
-S-MAC obtains comparable performance (78.71\%), and still maintains the shorter training time.
-The comparable performance indicate that the simplifications did not hinder its generalization capability.
+Evaluating MAC on CoGenT shows that, similar to~\cite{johnson2017inferring, mascharka2018transparency}, the score is worse on CoGenT-B than CoGenT-A after training on CoGenT-A data only. 
+As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on CoGenT-B compared to 78.71\% for S-MAC.
 
-Following \cite{johnson2017inferring, perez2017film}), we then fine-tune both models using 3k images and 30k questions from the Condition B data (for 10 epochs), and re-evaluate them on both conditions.
+We obtained comparable performances, which
+
+To that end,
+
+Following \cite{johnson2017inferring, perez2017film}), we then fine-tune both models using 3k images and 30k questions from the CoGenT-B data (for 10 epochs), and re-evaluate them on both conditions.
 This enables both models to perform much better on CoGenT-B, as we observe a 15 points increase for the accuracy.
@@
 Please refer to Appendix C for more details.
-
-We have conducted additional experiments to explore the

### 2018-11-02 2018_nips_vigil/experiments.tex
almot done

@@
 The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
+\tableref{results} presents the most important results, focusing on S-MAC in particular; see Appendix B for the entire set.
 
@@
 		\toprule
-		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{N$^{o}$} \\
+		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
@@
 		\midrule
-		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & A \\
+		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
 		\cmidrule{1-8}
@@
 
-		 \multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29         & B  \\
+		 \multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29         & (b)  \\
 		 \cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
 
-		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91        & C  \\
+		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91        & (c)  \\
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
 
-		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47  & D \\
+		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47  & (d) \\
 		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   &  95.58  & E\\
+		&                        &   &              &     &                               & CoGenT-B   &  95.58  & (e)\\
 
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71        & F  \\
+		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71        & (f)  \\
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24        & G \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24        & (g) \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.55     & H  \\
+		&                             &                                         &       &         &                & CoGenT-B &    94.55     & (h)  \\
 
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11       & I  \\
+& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11       & (i) \\
 \cmidrule{7-8} 
-&                             &                                         &       &         &                & CoGenT-B &    92.95    & J   \\
+&                             &                                         &       &         &                & CoGenT-B &    92.95    & (j)  \\
 
@@
 
-The entire set of results for both models are reported in˜\tableref{results}. 
-For the CLEVR dataset, the training wall time of MAC is consistent with what is reported in the original paper (roughly 30h of training for 20 epochs).
-S-MAC trains faster, showing a decrease of 10.5\% in wall time, due to the reductions in the 
+For the CLEVR dataset, the training wall time of MAC (row a) is consistent with what is reported in the original paper (roughly 30h of training for 20 epochs).
+S-MAC trains faster, showing a decrease of 10.5\% in wall time (row b), due to the reductions in the 
 number of parameters as shown earlier.
@@
 
-Turning to the generalization performance,  MAC on CLEVR yields an accuracy of 96.2\%, which is 
-taken as a reference experiment. S-MAC reaches an accuracy of 95.3\% on CLEVR, indicating that 
+Turning to the generalization performance (row a),  MAC on CLEVR yields an accuracy of 96.17\%, which is 
+taken as a reference experiment. S-MAC reaches an accuracy of 95.29\% on CLEVR (row b), indicating that 
 the simplifications did not hinder its generalization capability.
-Similar performances were observed for generalization on CoGenT-A.
+Similar performance was observed for generalization on CoGenT-A (row c).
 
@@
 we evaluated CLEVR-trained models on the CoGenT datasets.
-Even though the CoGenT datasets were generated using more restricted parameters, the models obtained nearly equal accuracy.
+Even though the CoGenT datasets were generated using more restricted parameters, the models obtained nearly equal accuracy (rows d-e).
 
-Evaluating MAC on CoGenT shows that, similar to~\cite{johnson2017inferring, mascharka2018transparency}, the score is worse on CoGenT-B than CoGenT-A after training on CoGenT-A data only. 
-As \tableref{results} shows, the MAC model achieves 79.5\% accuracy on CoGenT-B compared to 78.71\% for S-MAC.
+Evaluating S-MAC on CoGenT shows that, similar to~\cite{johnson2017inferring, mascharka2018transparency}, the score is worse on CoGenT-B (zero-shot learning, row f) than CoGenT-A after training on CoGenT-A data only (generalization, row c).
 
-We obtained comparable performances, which
+Following \cite{johnson2017inferring, perez2017film}), we then fine-tune S-MAC using 3k images and 30k questions from the CoGenT-B data (for 10 epochs), and re-evaluate it on both conditions.
+This enables much higher accuracy on CoGenT-B, of at least 15 points increase (row h).
+Performance on CoGenT-A is slightly worse, dropping by 4 points (row g).
+This seems to indicate that S-MAC is able to learn new combinations of shape \& color without forgetting the ones it learned during the initial training.
 
-To that end,
+To study the pitfalls of fine-tuning, we conducted a final set of experiments, where we fine-tuned a CLEVR-trained S-MAC model on CoGenT-B for 10 epochs, as before.
+Surprisingly, this operation handicapped the generalization of the model not only on CoGenT-A (row i), but also on CoGenT-B (row j, a 3 point drop compared to row e).
+This highlights the delicate nature of fine-tuning, with respect to the correlation between the datasets.
+This warrants further investigations.
 
-Following \cite{johnson2017inferring, perez2017film}), we then fine-tune both models using 3k images and 30k questions from the CoGenT-B data (for 10 epochs), and re-evaluate them on both conditions.
-This enables both models to perform much better on CoGenT-B, as we observe a 15 points increase for the accuracy.
-Performance on CoGenT-A is slightly worse, dropping of ~4\%.
-This seems to indicate that MAC is able to learn new combinations of shape \& color without forgetting the ones it learned during the initial training.
-Nonetheless, MAC does not appear to separate the concepts of shape and color.
-We have analyzed cases of failure of MAC on CoGenT-B, which illustrate this point.
-Please refer to Appendix C for more details.
+We have analyzed cases of failure on CoGenT-B to illustrate this point. Please refer to Appendix D for more details.

### 2018-11-02 2018_nips_vigil/introduction.tex
almot done

@@
 
-%VQA is a complex semantic task that combines natural language processing and visual recognition.
-%In order to answer the questions the system  requires to master several perceptual abilities, such as recognizing objects, attributes, and spatial relations as well as leveraging commonsense world knowledge~\citep{hudson2018compositional}.
-
-Many approaches have been explored, 
-%although they often appear to struggle on tasks with a structured and compositional nature \citep{hudson2018compositional}.
-such as modular networks, that combine modules coming from a predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
-Attention mechanisms (\cite{bahdanau2014neural}, \cite{xu2015show}) are also frequently used to guide the focus of the system over the image and the question words.
-%Other approaches such as \vm{Ask Tomasz what he is thinking about.}.
-
-%However, they rely on externally provided structured representations and functional programs, parsers or expert demonstration, and sometimes require reinforcement learning training schemes.
-%These models' structure is inherently rigid and the use of a range of specialized modules weaken their robustness and generalization capacities.
-%\tk{Compositional models are one major direction of research in VQA...
-but there are 3 others (including e.g.
-attention) that we do not mention here, thus my concern is that the above is not well balanced...
-I can add more when we will understand how much space is left.}
+Many approaches have been explored, such as modular networks, that combine modules coming from a predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}.
+Attention mechanisms (\cite{bahdanau2014neural}, \cite{xu2015show}) are also used to guide the focus of the system over the image and the question words.
 
@@
 One of the most recent exciting models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\citep{hudson2018compositional}, which performs a sequence of attention-based reasoning operations.
-%MAC uses three general units working in tandem to perform a reasoning step make the robustness of the model.
-%The MAC  model achieved state-of-the-art accuracy on CLEVR.
-%The authors also tested in on the difficult CLEVR Humans dataset, were the questions (regarding synthetically generated images) were written by humans. 
-Although the performance of MAC has been proven, 
-%it appeared to have difficulties with understanding what concepts the model is learning. 
-several questions arise:
+though the performance of MAC has been proven, several questions arise:
 Does the model really learn relations between objects? 
@@
 We propose a new set of equations that simplifies the core of the model (S-MAC). It trains faster and achieves comparable accuracy on CLEVR. 
-Second, we evaluate the generalization capabilities of both MAC \& S-MAC on the CoGenT dataset. 
-%The CoGenT dataset has been designed to highlight transfer learning abilities and give a better sense of interpretability.
-By mixing attributes over two sub-datasets, the CLEVR CoGenT task allow us to see what relations and concepts the model has really learned.
-%We show how MAC performs on CLEVR CoGenT and propose a study about the model failures.
-\tk{Finally, we also test MAC in a novel multi-step transfer learning setup -- if we will add it to the paper.} 
-%This work points out some of the MAC model weaknesses, in particular its failure to differentiate concepts of colors and shape. We finally discuss some improvement possibilities.
+Second, we show that both models achieve comparable performance with zero-shot learning, when trained on CoGenT-A and tested on CoGenT-B.
+With fine-tuning however, we obtained a significant 15 points increase in the accuracy, matching state-of-the-art results~\cite{perez2017film, mascharka2018transparency}.
+Last, we illustrate using CoGenT-B that, without adequate care, fine-tuning can actually reduce a model's accuracy.

### 2018-11-02 2018_nips_vigil/introduction.tex
Last fixes + list of authors

@@
 Reasoning over visual inputs is a fundamental characteristic of human intelligence.
-Reproducing this ability with artificial systems is a challenge that requires learning relations and compositionality~\citep{hu2017learning, johnson2017inferring}.
-The Visual Question Answering (VQA)~\citep{antol2015vqa,malinowski2014towards,wu2017visual} task has been tailored to benchmark this type of reasoning, combining natural language processing and visual recognition.
+Reproducing this ability with artificial systems is a challenge that requires learning relations and compositionality~\cite{hu2017learning, johnson2017inferring}.
+The Visual Question Answering (VQA)~\cite{antol2015vqa,malinowski2014towards,wu2017visual} task has been tailored to benchmark this type of reasoning, combining natural language processing and visual recognition.
 
@@
 Several VQA datasets have been proposed (e.g.
-DAQUAR~\citep{malinowski2014multi}, VQA~\citep{antol2015vqa}); nonetheless, these datasets contain several biases (e.g.
-unbalanced questions or answers) that are often exploited by systems during learning~\citep{goyal2017making}.
-The CLEVR dataset~\citep{johnson2017clevr} was designed to address these issues.
+DAQUAR~\cite{malinowski2014multi}, VQA~\cite{antol2015vqa}); nonetheless, these datasets contain several biases (e.g.
+unbalanced questions or answers) that are often exploited by systems during learning~\cite{goyal2017making}.
+The CLEVR dataset~\cite{johnson2017clevr} was designed to address these issues.
 The synthetic nature of its images \& questions enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning.
 One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations.
+For details, see Appendix~A (all appendices in supplementary material).
 
-One of the most recent exciting models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\citep{hudson2018compositional}, which performs a sequence of attention-based reasoning operations.
+One of the most recent exciting models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\cite{hudson2018compositional}, which performs a sequence of attention-based reasoning operations.
 though the performance of MAC has been proven, several questions arise:

### 2018-11-04 2018_nips_vigil/appendix.tex
Last fixes + list of authors
Fully read paper, added back appendices + cleanup/polishing.

@@
 
+ \newpage
 \section{Comparison of generalization capabilities}
 
-In this section we present comparison of our results on generalization capabilities with selected state-of-the-art models.
+In this section we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
 In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
-Deeper analysis of the papers revealed that it is most probable that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
-We find that the problems result from the fact that answers for the test sets aren't provided along with those sets, thus researchers started to use subsets of the validation set for testing. 
-The results of our research are presented in \tableref{tab:generalization_comparison}.
-In the table we had to shorten the names of the datasets.
-For example,  \textbf{A Test Full} means utilization of the whole \textbf{CoGenT Condition A Test set}, whereas  \textbf{B Valid 30k} indicates utilization of 30.000 samples from \textbf{CoGenT Condition B Validation set}.
-Question marks indicate that the paper does not provide enough information and those are the sets we assumed were used.
+Deeper analysis of the papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
+We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus researchers started to use subsets of the validation set for testing.
+The results of our research are presented in \tableref{tab:generalization_comparison}, where we shortened the names of the datasets.
+For instance, \textbf{A Test Full} means the use of the whole \textbf{CoGenT Condition A Test set}, whereas \textbf{B Valid 30k} indicates the use of 30.000 samples from \textbf{CoGenT Condition B Validation set}.
+Question marks indicate that the paper does not provide enough information; thus the indicated sets are the ones we assumed were used.
 
@@
 Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
-Sadly, it is not clear what sets exactly they used for fine-tuning (as Condition B lacks the training set).
-One possibility, as they are the authors of CLEVR and CoGenT datasets, is that they actually generated the missing sets, but didn't share them publicly.
-Besides, as they posses answers for both CoGenT Condition A and Condition B test sets, we are almost sure that they reported the accuracies on both Condition A and Condition B test sets.
+Sadly, it is not clear which sets they used for fine-tuning (as Condition B lacks a training set).
+Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets, but did not share them publicly.
+Additionally, as they own the ground truth answers for the test sets, it is very likely that they reported the accuracies on both Condition A and Condition B test sets.
 
@@
 Feature-wise Linear Modulation (in short, FiLM)~\cite{perez2017film} is an optional enhancement of a neural network model.
-The idea is to influence the behavior of existing layer(s) by introducing a feature-wise affine transformations that are conditioned on the input.
-A model composed of FiLM enhanced CNN and GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing few percent of improvements over the PG+EE model.
+The idea is to influence the behavior of existing layer(s) by introducing feature-wise affine transformations which are conditioned on the input.
+A model composed of FiLM enhanced by a CNN and a GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
 
-The problem with the presented comparison is that the authors used different sets for collecting the results, i.e.
-in the paper they clearly indicate that accuracies reported for Condition B after fine-tuning were calculated on CoGenT Condition B Validation set, excluding the 30k samples that were used for that fine-tuning.
-This also suggests that they probably reported scores for CoGenT Condition A Validation set,
-whereas, as it was mentioned previously, the original PG+EE paper probably relied on test sets in both cases.
+A problem with the presented comparison is that the authors used different sets for collecting the results.
+In the paper, they indicate that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples that were used for fine-tuning.
+This suggests that they probably reported scores for Condition A on the validation set.
 
@@
 TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing  attention masks.
-The authors compare the accuracy of their model while tested on CLEVR  with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM and MAC, and once again indicate improvement.
+The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM and MAC, and show improvement.
 
-They also compare accuracy on CoGenT, by comparison with PG+EE.
-Despite the results show improvement, the description clearly lacks the most important information, i.e. which sets were used for training, fine-tuning and testing. 
-The only provided information indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not mention from which set they took the samples.
-However, as they mention that they were following~\cite{johnson2017inferring}, it is possible that they used the test sets.
+They also compare performance on CoGenT, comparing to PG+EE.
+Nonetheless, the description lacks an important information, which is the used sets for training, fine-tuning and testing. 
+They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not mention from which set they took the samples.
 
@@
 When testing the model on CoGenT B, we used the whole validation set.
-In the experiments when we were using Validation B for fine-tuning, we did the analogical operations.
-Besides that, as we were using validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
+In the experiments when we were using Validation B for fine-tuning, we did a similar operation.
+Aside, as we were using validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
 
+\newpage
 \section{Illustration of failures of MAC on CLEVR}
@@
 
-\begin{figure}[]
+\begin{figure}[htbp]
 	\centering

### 2018-11-04 2018_nips_vigil/experiments.tex
Last fixes + list of authors
Fully read paper, added back appendices + cleanup/polishing.

@@
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
+		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
 		\midrule
@@
 Following \cite{johnson2017inferring, perez2017film}), we then fine-tune S-MAC using 3k images and 30k questions from the CoGenT-B data (for 10 epochs), and re-evaluate it on both conditions.
-This enables much higher accuracy on CoGenT-B, of at least 15 points increase (row h).
+This enables much higher accuracy on CoGenT-B, of at least a 15 points increase (row h).
 Performance on CoGenT-A is slightly worse, dropping by 4 points (row g).

### 2018-11-13 2018_nips_vigil/appendix.tex
Polishing of the main ViGIL paper and supplemental, split them into two files

@@
 	\end{tabular}
-	\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets}
+	\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
 	\label{tab:cogent_conditions}
@@
 \begin{table}[!h]
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
 	\centering
@@
 	\end{tabular}
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
 	\label{tab:results_full}
@@
 	\end{tabular}
-	\caption{Generalization capabilities of selected state-of-the-art models}
+	\caption{Generalization capabilities of selected state-of-the-art models.}
 	\label{tab:generalization_comparison}

### 2018-11-13 2018_nips_vigil/experiments.tex
Polishing of the main ViGIL paper and supplemental, split them into two files

@@
 Our implementation of both MAC models used PyTorch (v0.4.0)~\cite{paszke2017automatic}.
-We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework that enables fast experimentation of the cross product of models and datasets\footnote{Link available upon request, hidden here for reasons of anonymity.}.
-%The code \& experiment settings are available at \url{https://github.com/IBM/mi-prometheus/}}.
+We relied on the MI-Prometheus~\cite{kornuta2018accelerating} framework that enables fast experimentation of the cross product of models and datasets\footnote{To reproduce the presented research please follow:  \url{https://github.com/IBM/mi-prometheus/}}.
 We used NVIDIA's GeForce GTX TITAN X GPUs.
@@
 	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.
-The [Training] column indicates wall time and final accuracy on the training set.
-For fine-tuning, we use 30k samples of the test set, and the remaining is kept for testing.
-The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracy on this sub-set during training.
-The [Test] column reports the used set and the obtained test accuracy.
+The [Training] column indicates wall times and final accuracies on the training set.
+For fine-tuning, we use 30k samples of the test set, and kept the remainder for testing.
+The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training.
+The [Test] column reports the used set and the obtained test accuracies.
 If no fine-tuning was done, the whole indicated set was used for testing.}
@@
 
-We have analyzed cases of failure on CoGenT-B to illustrate this point. Please refer to Appendix D for more details.
+We have analyzed cases of failure on CoGenT-B to illustrate this point.
+Please refer to Appendix D for more details.
+Besides, Appendix C presents a comparison of results obtained by the S-MAC model and selected state-of-the-art models~\cite{johnson2017inferring,perez2017film,mascharka2018transparency}  on CoGenT.

### 2018-11-14 arxiv/comparison.tex
First draft of arxiv version of the paper

--- 2018-11-13 2018_nips_vigil/appendix.tex
@@
-\appendix
-
-\section{Description of datasets}
-
-Most of the VQA datasets have strong biases. This allow models to learn strategies without reasoning about the visual input~\cite{Santoro2017ASN}.
-The CLEVR dataset~\cite{johnson2017clevr} was developed to address those issues and come back to the core challenge of visual QA which is testing reasoning abilities.
-CLEVR contains images of 3D-rendered objects; each image comes with a number of highly compositional questions that fall into different categories.
-Those categories fall into 5 classes of tasks: Exist, Count, Compare Integer, Query Attribute and Compare Attribute. 
-The CLEVR dataset consists of:
-\begin{itemize}
-\item 	A training set of 70k images and 700k questions,
-\item	A validation set of 15k images and 150k questions,
-\item	A test  set of 15k images and 150k questions about objects,
-\item	Answers, scene graphs and functional programs for all train and val images and questions.
-\end{itemize}
-Each object present in the scene, aside of position, is characterized by a set of four attributes:
-\begin{itemize}
-\item 2 sizes: large, small,
-\item 3 shapes: square, cylinder, sphere,
-\item 2 material types: rubber, metal,
-\item 8 color types: gray, blue, brown, yellow, red, green, purple, cyan,
-\end{itemize}
-resulting in 96 unique combinations.
-
-Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
-This dataset is generated in the same way as CLEVR with two additional conditions.
-As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
-For both conditions spheres can be any colors.
-
-The CoGenT dataset contains:
-\begin{itemize}
-\item	Training set of 70,000 images and 699,960 questions in Condition A,
-\item	Validation set of 15,000 images and 149,991 questions in Condition A,
-\item	Test set of 15,000 images and 149,980 questions in Condition A (without answers),
-\item	Validation set of 15,000 images and 150,000 questions in Condition B,
-\item	Test set of 15,000 images and 149,992 questions in Condition B (without answers),
-\item	Answers, scene graphs and functional programs for all training and validation images and questions.
-\end{itemize}
-
-\begin{table}[h!]
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		Dataset        & Cubes              & Cylinders &  Spheres         \\
-		\midrule
-		CLEVR   &  any color &  any color        &    any color    \\
-		%\midrule
-		CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
-		CLEVR CoGenT B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
-		\bottomrule
-	\end{tabular}
-	\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
-	\label{tab:cogent_conditions}
-\end{table}
-
- \newpage
-\section{Full MAC and S-MAC comparison}
-
-In \tableref{tab:results_full} we present the full comparison between MAC and S-MAC models.
-
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{ccccCcCc}
-		\toprule
-		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
-		\midrule
-		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
-		\cmidrule{7-8} 
-		&                        &  &               &     &                                & CoGenT-A    &  96.22   \\
-		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   & 96.27  \\
-
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    93.28       \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.44       \\
-
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
-		\midrule
-		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
-		\cmidrule{7-8} 
-		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
-		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\
-
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.31       \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.95       \\
-
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
-		\cmidrule{7-8} 
-		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.55       \\
-		\bottomrule
-	\end{tabular}
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
-	\label{tab:results_full}
-\end{table}
-
- \newpage
-\section{Comparison of generalization capabilities}
+\subsection{Comparison of generalization capabilities with other models}
 
@@
 
-\subsection{The PG+EE model and training methodology}
+\subsubsection{The PG+EE model and training methodology}
 The PG+EE (Program Generator and Execution Engine)~\cite{johnson2017inferring} model is composed of two main modules:
@@
 
-\subsection{The FiLM model and training methodology}
+\subsubsection{The FiLM model and training methodology}
 
@@
 
-\subsection{The TbD model and training methodology}
+\subsubsection{The TbD model and training methodology}
 
@@
 
-\subsection{Our MAC and S-MAC models and methodology}
+\subsubsection{Our MAC and S-MAC models and methodology}
 
@@
 Aside, as we were using validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
-
-\newpage
-\section{Illustration of failures of MAC on CLEVR}
-Following the evaluation of MAC on CoGenT-B, we built a tool which helped us visualizing the attention of the model over the question words and the image, and thus provide insight on some cases of failure.
-
-\fig{fig:fail_mac_shape} presents a question where the model is asked about the shape of the leftmost gray cylinder.
-The model correctly finds it, as we can see from its visual attention map, and appears to refer to it using its color (\textit{gray}), as we can see from the attention of the question words.
-Yet, it defaults to predicting the shape as \textit{cube}, because it never saw gray cylinders during training, but instead saw gray cubes.
-
-\fig{fig:fail_mac_color} presents a similar case, where the model is questioned about the color of the green cube at the back.
-MAC misses that object, and instead focuses on the nearby gray cylinder.
-We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus defaulted to a combination that it knows.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_shape.png}
-	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
-	\label{fig:fail_mac_shape}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_color.png}
-	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
-	\label{fig:fail_mac_color}
-\end{figure}
-
-Those examples indicate that MAC did not correctly separate the concept of shape from the concept of color, but have a better understanding of the colors (as it found the object of interest in \fig{fig:fail_mac_shape} by its color).
-This could come from that fact that the shape \textit{sphere} is associated with all possible colors in the dataset.

### 2018-11-14 arxiv/conclusion.tex
First draft of arxiv version of the paper

\section{Conclusion}
\label{sec:conclusion}

We have introduced S-MAC, a simplified variant of the MAC model. Because it has nearly half the number of parameters in the recurrent portion MAC cell, it trains faster while maintaining an equivalent test accuracy.

Our experiments on zero-short learning show that the MAC model has poor performance in line with the other models in the literature. Thus, this remains an interesting problem to investigate how we can train it to disentangle the concepts of shape and color.

With fine-tuning, the MAC model indeed achieves much improved performance, matching state of the art. However, we have showed that correlation between the different domains must be taken into account when fine-tuning, otherwise potentially leading to decreased performance.

### 2018-11-14 arxiv/datasets.tex
First draft of arxiv version of the paper

--- 2018-11-13 2018_nips_vigil/appendix.tex
@@
-\appendix
-
 \section{Description of datasets}
+\label{sec:datasets}
 
@@
 \end{table}
-
- \newpage
-\section{Full MAC and S-MAC comparison}
-
-In \tableref{tab:results_full} we present the full comparison between MAC and S-MAC models.
-
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{ccccCcCc}
-		\toprule
-		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
-		\midrule
-		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
-		\cmidrule{7-8} 
-		&                        &  &               &     &                                & CoGenT-A    &  96.22   \\
-		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   & 96.27  \\
-
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    93.28       \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.44       \\
-
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
-		\midrule
-		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
-		\cmidrule{7-8} 
-		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
-		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\
-
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.31       \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.95       \\
-
-		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
-		\cmidrule{7-8} 
-		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
-		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24         \\
-		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.55       \\
-		\bottomrule
-	\end{tabular}
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
-	\label{tab:results_full}
-\end{table}
-
- \newpage
-\section{Comparison of generalization capabilities}
-
-In this section we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
-In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
-Deeper analysis of the papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
-We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus researchers started to use subsets of the validation set for testing.
-The results of our research are presented in \tableref{tab:generalization_comparison}, where we shortened the names of the datasets.
-For instance, \textbf{A Test Full} means the use of the whole \textbf{CoGenT Condition A Test set}, whereas \textbf{B Valid 30k} indicates the use of 30.000 samples from \textbf{CoGenT Condition B Validation set}.
-Question marks indicate that the paper does not provide enough information; thus the indicated sets are the ones we assumed were used.
-
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{cCcCcCc}
-		\toprule
-		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
-		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
-		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\
-
-\midrule				
-& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test Full    &   96.6  \\
-\cmidrule{6-7} 
-PG+EE &   &    &   &    & B Test Full?    &   73.7  \\
-\cmidrule{4-5}\cmidrule{6-7}
-(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test Full    &   76.1 \\
-\cmidrule{6-7} 
-&   &    &   &    & B Test Full?    &   92.7  \\
-
-\midrule				
-CNN+GRU+FiLM & \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full?    &  98.3   \\
-\cmidrule{6-7} 
-0-Shot &   &    &   &    & B Valid 120k    &   78.8  \\
-\cmidrule{4-5}\cmidrule{6-7}
-(\cite{perez2017film}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A Valid Full?    & 81.1  \\
-\cmidrule{6-7} 
-&   &    &   &    & B Valid 120k    &  96.9  \\
-
-\midrule				
-& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A ?    &  98.8   \\
-\cmidrule{6-7} 
-TbD + reg &   &    &   &    & B ?    &  75.4   \\
-\cmidrule{4-5}\cmidrule{6-7}
-(\cite{mascharka2018transparency}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A ?    &  96.9 \\
-\cmidrule{6-7} 
-&   &    &   &    & B ?   &  96.3  \\
-
-\midrule				
-& \multirow{5}{*}{A Train 630k}   & \multirow{5}{*}{97.02}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full    &     96.88 \\
-\cmidrule{6-7} 
-MAC &   &    &   &    & B Valid Full   &  79.54   \\
-\cmidrule{4-5}\cmidrule{6-7}
-(our results) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{97.91}     & A Valid Full    &  92.06 \\
-\cmidrule{6-7} 
-&   &    &   &    & B Valid 120k    &   95.62 \\
-
-\midrule				
-& \multirow{5}{*}{A Train 630k}   & \multirow{5}{*}{96.09}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full    &     95.91 \\
-\cmidrule{6-7} 
-S-MAC &   &    &   &    & B Valid Full   &  78.71   \\
-\cmidrule{4-5}\cmidrule{6-7}
-(our results) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{96.85}     & A Valid Full    &  91.24 \\
-\cmidrule{6-7} 
-&   &    &   &    & B Valid 120k    &   94.55 \\
-
-		\bottomrule
-	\end{tabular}
-	\caption{Generalization capabilities of selected state-of-the-art models.}
-	\label{tab:generalization_comparison}
-\end{table}
-
-\subsection{The PG+EE model and training methodology}
-The PG+EE (Program Generator and Execution Engine)~\cite{johnson2017inferring} model is composed of two main modules:
-a Program Generator constructing an explicit, graph-like representation of the reasoning process, and an Execution Engine executing that program and producing an answer. 
-Both modules are implemented by neural networks, and were trained using a combination of backpropagation and REINFORCE~\cite{williams1992simple}.
-
-The authors inform that in the first step they trained their models on Condition A, and tested them on both Condition A and Condition B. 
-Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
-Sadly, it is not clear which sets they used for fine-tuning (as Condition B lacks a training set).
-Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets, but did not share them publicly.
-Additionally, as they own the ground truth answers for the test sets, it is very likely that they reported the accuracies on both Condition A and Condition B test sets.
-
-\subsection{The FiLM model and training methodology}
-
-Feature-wise Linear Modulation (in short, FiLM)~\cite{perez2017film} is an optional enhancement of a neural network model.
-The idea is to influence the behavior of existing layer(s) by introducing feature-wise affine transformations which are conditioned on the input.
-A model composed of FiLM enhanced by a CNN and a GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
-
-A problem with the presented comparison is that the authors used different sets for collecting the results.
-In the paper, they indicate that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples that were used for fine-tuning.
-This suggests that they probably reported scores for Condition A on the validation set.
-
-\subsection{The TbD model and training methodology}
-
-The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
-TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing  attention masks.
-The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM and MAC, and show improvement.
-
-They also compare performance on CoGenT, comparing to PG+EE.
-Nonetheless, the description lacks an important information, which is the used sets for training, fine-tuning and testing. 
-They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not mention from which set they took the samples.
-
-\subsection{Our MAC and S-MAC models and methodology}
-
-Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, we decided to follow the approach proposed in~\cite{perez2017film} and split the CoGenT A Validation set.
-As a result we used 30k samples for fine-tuning and the remaining part for testing.
-When testing the model on CoGenT B, we used the whole validation set.
-In the experiments when we were using Validation B for fine-tuning, we did a similar operation.
-Aside, as we were using validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
-
-\newpage
-\section{Illustration of failures of MAC on CLEVR}
-Following the evaluation of MAC on CoGenT-B, we built a tool which helped us visualizing the attention of the model over the question words and the image, and thus provide insight on some cases of failure.
-
-\fig{fig:fail_mac_shape} presents a question where the model is asked about the shape of the leftmost gray cylinder.
-The model correctly finds it, as we can see from its visual attention map, and appears to refer to it using its color (\textit{gray}), as we can see from the attention of the question words.
-Yet, it defaults to predicting the shape as \textit{cube}, because it never saw gray cylinders during training, but instead saw gray cubes.
-
-\fig{fig:fail_mac_color} presents a similar case, where the model is questioned about the color of the green cube at the back.
-MAC misses that object, and instead focuses on the nearby gray cylinder.
-We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus defaulted to a combination that it knows.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_shape.png}
-	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
-	\label{fig:fail_mac_shape}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_color.png}
-	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
-	\label{fig:fail_mac_color}
-\end{figure}
-
-Those examples indicate that MAC did not correctly separate the concept of shape from the concept of color, but have a better understanding of the colors (as it found the object of interest in \fig{fig:fail_mac_shape} by its color).
-This could come from that fact that the shape \textit{sphere} is associated with all possible colors in the dataset.

### 2018-11-14 arxiv/experiments.tex
First draft of arxiv version of the paper

--- 2018-11-13 2018_nips_vigil/experiments.tex
@@
 \section{Experiments}
+\label{sec:experiments}
 
@@
 Besides, Appendix C presents a comparison of results obtained by the S-MAC model and selected state-of-the-art models~\cite{johnson2017inferring,perez2017film,mascharka2018transparency}  on CoGenT.
+
+\subsection{Illustration of failures of MAC on CLEVR}
+Following the evaluation of MAC on CoGenT-B, we built a tool which helped us visualizing the attention of the model over the question words and the image, and thus provide insight on some cases of failure.
+
+\fig{fig:fail_mac_shape} presents a question where the model is asked about the shape of the leftmost gray cylinder.
+The model correctly finds it, as we can see from its visual attention map, and appears to refer to it using its color (\textit{gray}), as we can see from the attention of the question words.
+Yet, it defaults to predicting the shape as \textit{cube}, because it never saw gray cylinders during training, but instead saw gray cubes.
+
+\fig{fig:fail_mac_color} presents a similar case, where the model is questioned about the color of the green cube at the back.
+MAC misses that object, and instead focuses on the nearby gray cylinder.
+We can hypothesize that MAC missed the green cube as it did not see this combination during training, and thus defaulted to a combination that it knows.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_shape.png}
+	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
+	\label{fig:fail_mac_shape}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_color.png}
+	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
+	\label{fig:fail_mac_color}
+\end{figure}
+
+Those examples indicate that MAC did not correctly separate the concept of shape from the concept of color, but have a better understanding of the colors (as it found the object of interest in \fig{fig:fail_mac_shape} by its color).
+This could come from that fact that the shape \textit{sphere} is associated with all possible colors in the dataset.

### 2018-11-14 2018_nips_vigil/appendix.tex
Moved images to folder 'above'
Polishing the appendices.

@@
 
-\section{Description of datasets}
+\section{Description of the datasets}
 
-Most of the VQA datasets have strong biases. This allow models to learn strategies without reasoning about the visual input~\cite{Santoro2017ASN}.
+Most of the VQA datasets have strong biases. This allow models to learn strategies without reasoning on the visual input~\cite{Santoro2017ASN}.
 The CLEVR dataset~\cite{johnson2017clevr} was developed to address those issues and come back to the core challenge of visual QA which is testing reasoning abilities.
-CLEVR contains images of 3D-rendered objects; each image comes with a number of highly compositional questions that fall into different categories.
-Those categories fall into 5 classes of tasks: Exist, Count, Compare Integer, Query Attribute and Compare Attribute. 
+CLEVR contains images of 3D-rendered objects; each image comes with a number of highly compositional questions which fall into different categories.
+These categories are divided into 5 classes of tasks: Exist, Count, Compare Integer, Query Attribute and Compare Attribute. 
 The CLEVR dataset consists of:
@@
 \end{itemize}
-Each object present in the scene, aside of position, is characterized by a set of four attributes:
+Each object present in the scene is characterized, aside its position, by a set of four attributes:
 \begin{itemize}
@@
 Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
-This dataset is generated in the same way as CLEVR with two additional conditions.
+This dataset is generated in the same way as CLEVR, with two conditions.
 As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
-For both conditions spheres can be any colors.
+For both conditions, spheres can be of any colors.
 
@@
 \item	Validation set of 15,000 images and 149,991 questions in Condition A,
-\item	Test set of 15,000 images and 149,980 questions in Condition A (without answers),
+\item	Test set of 15,000 images and 149,980 questions in Condition A,
 \item	Validation set of 15,000 images and 150,000 questions in Condition B,
-\item	Test set of 15,000 images and 149,992 questions in Condition B (without answers),
+\item	Test set of 15,000 images and 149,992 questions in Condition B,
 \item	Answers, scene graphs and functional programs for all training and validation images and questions.
@@
 
-In \tableref{tab:results_full} we present the full comparison between MAC and S-MAC models.
+In \tableref{tab:results_full}, we present the full comparison table between MAC and S-MAC models.
 
@@
  \newpage
-\section{Comparison of generalization capabilities}
+\section{Comparison of the generalization capabilities on CoGenT}
 
-In this section we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
+In this section, we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
 In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
 Deeper analysis of the papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
-We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus researchers started to use subsets of the validation set for testing.
+We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus subsets of the validation sets were sometimes used for testing. 
 The results of our research are presented in \tableref{tab:generalization_comparison}, where we shortened the names of the datasets.
@@
 		\toprule
-		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
-		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
+		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
+		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}\cmidrule{7-8} 
 		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\
@@
 
-The authors inform that in the first step they trained their models on Condition A, and tested them on both Condition A and Condition B. 
+The authors inform that in the first step they trained their models on Condition A, and tested them on both conditions. 
 Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
 Sadly, it is not clear which sets they used for fine-tuning (as Condition B lacks a training set).
-Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets, but did not share them publicly.
-Additionally, as they own the ground truth answers for the test sets, it is very likely that they reported the accuracies on both Condition A and Condition B test sets.
+Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets.
+Additionally, as they own the ground truth answers for the test sets, it is likely that they reported the accuracies on both Condition A and Condition B test sets.
 
@@
 The idea is to influence the behavior of existing layer(s) by introducing feature-wise affine transformations which are conditioned on the input.
-A model composed of FiLM enhanced by a CNN and a GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
+A model composed of FiLM layers enhanced by a CNN and a GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
 
-A problem with the presented comparison is that the authors used different sets for collecting the results.
-In the paper, they indicate that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples that were used for fine-tuning.
+Nonetheless, they indicate in the paper that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples which were used for fine-tuning.
 This suggests that they probably reported scores for Condition A on the validation set.
@@
 The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
-TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing  attention masks.
-The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM and MAC, and show improvement.
+TbD is composed of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing attention masks.
+The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM \& MAC, and show improvement.
 
-They also compare performance on CoGenT, comparing to PG+EE.
-Nonetheless, the description lacks an important information, which is the used sets for training, fine-tuning and testing. 
+They also compare their performance on CoGenT against PG+EE.
+Nonetheless, the description lacks information about the used sets for training, fine-tuning and testing. 
 They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not mention from which set they took the samples.
@@
 
-Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, we decided to follow the approach proposed in~\cite{perez2017film} and split the CoGenT A Validation set.
-As a result we used 30k samples for fine-tuning and the remaining part for testing.
-When testing the model on CoGenT B, we used the whole validation set.
-In the experiments when we were using Validation B for fine-tuning, we did a similar operation.
-Aside, as we were using validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
+Due to the fact that the test sets ground truth labels for both CLEVR and CoGenT aren't publicly available, we decided to follow the approach proposed in~\cite{perez2017film} and split the CoGenT B Validation set.
+As a result we used 30k samples for fine-tuning and the remaining ones for testing.
+When testing the model on CoGenT A, we used the whole validation set.
+
+Moreover, as we were using the validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_shape.png}
+	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_shape.png}
 	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
@@
 	\centering
-	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_color.png}
+	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_color.png}
 	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
@@
 
-Those examples indicate that MAC did not correctly separate the concept of shape from the concept of color, but have a better understanding of the colors (as it found the object of interest in \fig{fig:fail_mac_shape} by its color).
+These examples indicate that MAC did not correctly separate the concept of shape from the concept of color, but have a better understanding of the colors (as it found the object of interest in \fig{fig:fail_mac_shape} by its color).
 This could come from that fact that the shape \textit{sphere} is associated with all possible colors in the dataset.

### 2018-11-14 2018_nips_vigil/appendix.tex
Added row references to full table in App. B.

@@
 	\centering
-	\begin{tabular}{ccccCcCc}
+	\begin{tabular}{ccccCcCcc}
 		\toprule
-		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
+		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
-		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
+		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
 		\midrule
-		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
+		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17    & (a)      \\
 		\cmidrule{7-8} 
-		&                        &  &               &     &                                & CoGenT-A    &  96.22   \\
+		&                        &  &               &     &                                & CoGenT-A    &  96.22 &  \\
 		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   & 96.27  \\
+		&                        &   &              &     &                               & CoGenT-B   & 96.27 & \\
 
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	         \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	   &      \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    93.28       \\
+		&                             &                                         &       &         &                & CoGenT-B &    93.28   &    \\
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02         \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02    &     \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.44       \\
+		&                             &                                         &       &         &                & CoGenT-B &    94.44   &    \\
 
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
+		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88    &     \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
+		&                             &                                         &       &         &                & CoGenT-B & 79.54     &    \\
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06     &    \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
+		&                             &                                         &       &         &                & CoGenT-B &    95.62   &    \\
 		\midrule
-		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
+		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29     & (b)      \\
 		\cmidrule{7-8} 
-		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
+		&                        &  &               &     &                                & CoGenT-A    &  95.47 & (d)  \\
 		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\
+		&                        &   &              &     &                               & CoGenT-B   &  95.58 & (e) \\
 
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44         \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44      &   \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.31       \\
+		&                             &                                         &       &         &                & CoGenT-B &    92.31   &    \\
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11         \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11     & (i)    \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.95       \\
+		&                             &                                         &       &         &                & CoGenT-B &    92.95  & (j)     \\
 
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
+		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91    & (c)      \\
 		\cmidrule{7-8} 
-		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
+		&                             &                                         &     &          &                & CogenT-B & 78.71       & (f)   \\
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24         \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24   & (g)      \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.55       \\
+		&                             &                                         &       &         &                & CoGenT-B &    94.55   & (h)    \\
 		\bottomrule
@@
 		\toprule
-		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
-		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}\cmidrule{7-8} 
+		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
+		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
 		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\

### 2018-11-14 arxiv/introduction.tex
First draft of arxiv version of the paper
Intro and reformatting

--- 2018-11-02 2018_nips_vigil/introduction.tex
@@
 Last, we illustrate using CoGenT-B that, without adequate care, fine-tuning can actually reduce a model's accuracy.
+
+The paper is organized as follows.
+In \sec{datasets} we digest into details of both CLEVR and CoGenT datasets, emphasizing their differences.
+Next, in \sec{models}) we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
+\sec{experiments} discusses the most important findings when using transfer learning on CLEVR and both versions of CoGenT.
+In order to facilitate the lecture we cherry-picked a subset of experiments -- the whole table with comparison of both MAC and S-MAC models when training/fine-tuning/testing MAC and S-MAC models on different datasets can be found in Appendix A.
+Additionally, in \sec{failures} we present examples that support our hypotheses on lack of disentanglement of concepts in both models.
+\sec{comparison} presents 
+We conclude the paper in \sec{conclusion}.

### 2018-11-14 2018_nips_vigil/experiments.tex

@@
 The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
-\tableref{results} presents the most important results, focusing on S-MAC in particular; see Appendix B for the entire set.
+\tableref{results} presents the most important results, focusing on S-MAC in particular; see Appendix B for the entire table.
 
@@
 Please refer to Appendix D for more details.
-Besides, Appendix C presents a comparison of results obtained by the S-MAC model and selected state-of-the-art models~\cite{johnson2017inferring,perez2017film,mascharka2018transparency}  on CoGenT.
+Aside, Appendix C presents a comparison of results obtained by the S-MAC model and selected state-of-the-art models~\cite{johnson2017inferring,perez2017film,mascharka2018transparency} on CoGenT.

### 2018-11-14 2018_nips_vigil/appendix.tex
Polishing here and there

@@
 		CLEVR   &  any color &  any color        &    any color    \\
-		%\midrule
 		CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
@@
 
-In \tableref{tab:results_full}, we present the full comparison table between MAC and S-MAC models.
+In \tableref{tab:results_full} we present the full comparison between MAC and S-MAC models achieved with our implementations of both models.
+In the [Row] column we indicate the results that we have  analyzed and discussed in the experiments section of the main paper.
 
@@
 TbD is composed of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing attention masks.
-The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM \& MAC, and show improvement.
+The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models.
+In particular, they show improvement over the previously mentioned PG + EE, CNN + GRU + FiLM and MAC.
 
@@
 Nonetheless, the description lacks information about the used sets for training, fine-tuning and testing. 
-They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not mention from which set they took the samples.
+They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not explicitly point the set they used the samples from.
 
@@
 \newpage
-\section{Illustration of failures of MAC on CLEVR}
+\section{Illustration of failures of MAC/S-MAC on CLEVR}
 Following the evaluation of MAC on CoGenT-B, we built a tool which helped us visualizing the attention of the model over the question words and the image, and thus provide insight on some cases of failure.

### 2018-11-14 arxiv/comparison.tex
Polishing here and there

@@
 \subsection{Comparison of generalization capabilities with other models}
+\label{sec:comparison}
 
-In this section we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
+In this section, we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
 In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
 Deeper analysis of the papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
-We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus researchers started to use subsets of the validation set for testing.
+We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus subsets of the validation sets were sometimes used for testing. 
 The results of our research are presented in \tableref{tab:generalization_comparison}, where we shortened the names of the datasets.
@@
 The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
-TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing  attention masks.
-The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models, including the previously mentioned PG + EE, CNN + GRU + FiLM and MAC, and show improvement.
+TbD is composed of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composing attention masks.
+The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models.
+In particular, they show improvement over the previously mentioned PG + EE, CNN + GRU + FiLM and MAC.
 
-They also compare performance on CoGenT, comparing to PG+EE.
-Nonetheless, the description lacks an important information, which is the used sets for training, fine-tuning and testing. 
-They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not mention from which set they took the samples.
+They also compare their performance on CoGenT against PG+EE.
+Nonetheless, the description lacks information about the used sets for training, fine-tuning and testing. 
+They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not explicitly point the set they used the samples from.
 
@@
 
-Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, we decided to follow the approach proposed in~\cite{perez2017film} and split the CoGenT A Validation set.
-As a result we used 30k samples for fine-tuning and the remaining part for testing.
-When testing the model on CoGenT B, we used the whole validation set.
-In the experiments when we were using Validation B for fine-tuning, we did a similar operation.
-Aside, as we were using validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
+Due to the fact that the test sets ground truth labels for both CLEVR and CoGenT aren't publicly available, we decided to follow the approach proposed in~\cite{perez2017film} and split the CoGenT B Validation set.
+As a result we used 30k samples for fine-tuning and the remaining ones for testing.
+When testing the model on CoGenT A, we used the whole validation set.
+
+Moreover, as we were using the validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.

### 2018-11-14 arxiv/experiments.tex
Intro and reformatting
Polishing here and there

@@
 A) of the original paper~\cite{hudson2018compositional}, to ensure a faithful comparison.
+
+\subsection{Transfer Learning}
+\label{sec:transfer_learning}
 
@@
 \subsection{Illustration of failures of MAC on CLEVR}
+\label{sec:failures}
+
 Following the evaluation of MAC on CoGenT-B, we built a tool which helped us visualizing the attention of the model over the question words and the image, and thus provide insight on some cases of failure.

### 2018-11-14 arxiv/introduction.tex
Polishing here and there

--- 2018-11-02 2018_nips_vigil/introduction.tex
@@
 Last, we illustrate using CoGenT-B that, without adequate care, fine-tuning can actually reduce a model's accuracy.
+
+The paper is organized as follows.
+In \sec{datasets} we digest into details of both CLEVR and CoGenT datasets, emphasizing their differences.
+Next, in \sec{models}) we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
+\sec{experiments} discusses the most important findings when using transfer learning on CLEVR and both versions of CoGenT.
+In order to facilitate the lecture in \sec{transfer_learning} we cherry-picked a subset of experiments -- the whole table with comparison of both MAC and S-MAC models when training/fine-tuning/testing can be found in Appendix~\ref{sec:full_comparison}.
+In \sec{failures} we present examples that support hypothesis on the lack of disentanglement of concepts in both models.
+\sec{comparison} presents results obtained by other state-of-the-art models, and additionally indicates a problem with their reproducibility. 
+We conclude the paper in \sec{conclusion}.

### 2018-11-14 arxiv/experiments.tex
arvix - getting rid of references to appendices (aside of A, using references here)

@@
 The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
-\tableref{results} presents the most important results, focusing on S-MAC in particular; see Appendix B for the entire set.
+\tableref{results} presents the most important results, focusing on S-MAC in particular; see Appendix~\ref{sec:full_comparison} for the entire set.
 
@@
 
-We have analyzed cases of failure on CoGenT-B to illustrate this point.
-Please refer to Appendix D for more details.
-Besides, Appendix C presents a comparison of results obtained by the S-MAC model and selected state-of-the-art models~\cite{johnson2017inferring,perez2017film,mascharka2018transparency}  on CoGenT.
-
 \subsection{Illustration of failures of MAC on CLEVR}

### 2018-11-15 arxiv/introduction.tex
arvix - getting rid of references to appendices (aside of A, using references here)
Minor edits. Reworded a few sentences

--- 2018-11-02 2018_nips_vigil/introduction.tex
@@
 One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations.
-For details, see Appendix~A (all appendices in supplementary material).
 
@@
 Last, we illustrate using CoGenT-B that, without adequate care, fine-tuning can actually reduce a model's accuracy.
+
+The paper is organized as follows.
+In \sec{datasets} we delve into details of both CLEVR and CoGenT datasets, emphasizing their differences.
+Next, in \sec{models}) we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
+\sec{experiments} discusses the most important results of using transfer learning 
+on CLEVR and on both versions of CoGenT.
+\sec{transfer_learning} focuses on a cherry-picked subset of experiments to highlight our findings; 
+see~Appendix~\ref{sec:full_comparison} for the complete set of results comparing MAC and S-MAC models when training/fine-tuning/testing on various datasets.
+In \sec{failures} we present examples that support hypothesis on the lack of disentanglement of concepts in both models.
+\sec{comparison} presents results obtained by other state-of-the-art models, and discusses the challenges faced  
+with their reproducibility. 
+\sec{conclusion} concludes the paper.

### 2018-11-15 arxiv/comparison.tex
Minor edits. Reworded a few sentences
polishing

@@
 In this section, we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
-In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
-Deeper analysis of the papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
+In particular, we focused on three papers reporting state-of-the-art accuracies on CoGenT.
+Those papers introduce the following models: PG+EE~\cite{johnson2017inferring}, FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
+Deeper analysis of those papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
 We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus subsets of the validation sets were sometimes used for testing. 
@@
 		\cmidrule{6-7} 
-		&   &    &   &    & B Test Full?    &   92.7  \\
+		&   &    &   &    & B Test Full    &   92.7  \\
 
@@
 Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
-Sadly, it is not clear which sets they used for fine-tuning (as Condition B lacks a training set).
+We could not ascertain which sets they used for fine-tuning (as Condition B lacks a training set).
 Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets.
-Additionally, as they own the ground truth answers for the test sets, it is likely that they reported the accuracies on both Condition A and Condition B test sets.
+Additionally, as they own the ground truth answers for the test sets, we take as granted that they reported the accuracies on both Condition A and Condition B test sets, despite they explicitly didn't say that in the paper.
 
@@
 The idea is to influence the behavior of existing layer(s) by introducing feature-wise affine transformations which are conditioned on the input.
-A model composed of FiLM layers enhanced by a CNN and a GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
+A model composed of CNNs and a GRU with FiLM-enhanced layers achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
 
-Nonetheless, they indicate in the paper that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples which were used for fine-tuning.
-This suggests that they probably reported scores for Condition A on the validation set.
+Nonetheless, the authors indicate in the paper that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples which were used for fine-tuning.
+This suggests that they probably reported scores for Condition A on the validation, not test set as well.
 
@@
 The authors compare the accuracy of their model tested on CLEVR, alongside with several existing models.
-In particular, they show improvement over the previously mentioned PG + EE, CNN + GRU + FiLM and MAC.
+In particular, they show improvement over the previously mentioned PG + EE, CNN + GRU + FiLM and MAC models.
 
@@
 Moreover, as we were using the validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
+We used the same methodology for all the results presented in this paper, i.e. \tableref{tab:results}, \tableref{tab:generalization_comparison} and \tableref{tab:results_full}.

### 2018-11-15 arxiv/introduction.tex
polishing

@@
 In \sec{datasets} we delve into details of both CLEVR and CoGenT datasets, emphasizing their differences.
-Next, in \sec{models}) we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
+Next, in \sec{models} we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
 \sec{experiments} discusses the most important results of using transfer learning 
@@
 see~Appendix~\ref{sec:full_comparison} for the complete set of results comparing MAC and S-MAC models when training/fine-tuning/testing on various datasets.
-In \sec{failures} we present examples that support hypothesis on the lack of disentanglement of concepts in both models.
+In \sec{failures} we show examples supporting hypothesis on the lack of disentanglement of concepts in both models.
 \sec{comparison} presents results obtained by other state-of-the-art models, and discusses the challenges faced  

### 2018-11-15 2018_nips_vigil/appendix.tex
Cherry-picked changes: arXiv -> camera-ready.

@@
 In this section, we present a comparison of our results on generalization capabilities with selected state-of-the-art models.
-In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
-Deeper analysis of the papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
+In particular, we focused on three papers reporting state-of-the-art accuracies on CoGenT.
+These papers introduce the following models: PG+EE~\cite{johnson2017inferring}, FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
+Deeper analysis of these papers revealed that it is likely that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
 We find that the problem results from the fact that ground truth answers for the test sets are not provided along with these sets; thus subsets of the validation sets were sometimes used for testing. 
@@
 \cmidrule{6-7} 
-&   &    &   &    & B Test Full?    &   92.7  \\
+&   &    &   &    & B Test Full    &   92.7  \\
 
@@
 Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both conditions.
-Sadly, it is not clear which sets they used for fine-tuning (as Condition B lacks a training set).
++We could not ascertain which sets they used for fine-tuning (as Condition B lacks a training set).
 Being the authors of the CLEVR and CoGenT datasets, it is possible that they generated specific sets.
-Additionally, as they own the ground truth answers for the test sets, it is likely that they reported the accuracies on both Condition A and Condition B test sets.
+Additionally, as they own the ground truth answers for the test sets, it can be assumed that they reported the accuracies on both Condition A and Condition B test sets, although it is not indicated in the paper.
 
@@
 The idea is to influence the behavior of existing layer(s) by introducing feature-wise affine transformations which are conditioned on the input.
-A model composed of FiLM layers enhanced by a CNN and a GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
+A model composed of CNNs and a GRU with FiLM-enhanced layers achieved state-of-the-art results on both CLEVR and CoGenT, showing improvement over the PG+EE model.
 
-Nonetheless, they indicate in the paper that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples which were used for fine-tuning.
-This suggests that they probably reported scores for Condition A on the validation set.
+Nonetheless, the authors indicate in the paper that the accuracy reported for Condition B after fine-tuning was obtained on the CoGenT Condition B Validation set, excluding the 30k samples which were used for fine-tuning.
+This suggests that they probably reported scores for Condition A on the validation set, not the test set.
 
@@
 Moreover, as we were using the validation sets for testing, we also splitted the training set and used 90\% for training and the remaining 10\% for validation during training.
++We used the same methodology for all the results presented in this paper, i.e. Table 2 in the main paper, \tableref{tab:generalization_comparison} and \tableref{tab:results_full} here.
 

### 2018-11-20 2018_nips_vigil_poster/main.tex
nips vigil poster

\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.3]{baposter}
% NIPS Workshops format

% Encoding.
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx} % Required for including images
\usepackage{subfig}
\usepackage{booktabs} % for professional tables
\usepackage{floatrow}
\usepackage{float}

\usepackage{textgreek}
\usepackage{pstricks}
\usepackage{tikz}
\usepackage{pgf}
\usepackage{placeins} % For \FloatBarrier
\usetikzlibrary{positioning}
\usepackage{environ}
\makeatletter
\newsavebox{\measure@tikzpicture}
\NewEnviron{scaletikzpicturetowidth}[1]{%
	\def\tikz@width{#1}%
	\def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
		\BODY
	\end{lrbox}%
	\pgfmathparse{#1/\wd\measure@tikzpicture}%
	\edef\tikzscale{\pgfmathresult}%
	\BODY
}
\makeatother

\usepackage{amsmath} % For typesetting math
\usepackage{amssymb} % Adds new symbols to be used in math mode

\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{enumitem} % Used to reduce itemize/enumerate spacing
%\usepackage{palatino} % Use the Palatino font
\renewcommand{\familydefault}{\sfdefault}
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures

\usepackage{multicol} % Required for multiple columns
\setlength{\columnsep}{1.5em} % Slightly increase the space between columns
\setlength{\columnseprule}{0mm} % No horizontal rule between columns
\usepackage{multirow}

\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{itemize} or \begin{enumerate}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
}

% Defines the color used for content box headers
\definecolor{lightblue}{cmyk}{0.83,0.24,0,0.16}
%\definecolor{lightblue}{rgb}{0.145,0.6666,1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Begin of Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Pojedyncze spacje po kropce.
\frenchspacing

\begin{document}

\hyphenation{resolution occlusions}
%%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=false,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=lightblue,
  headerColorOne=black,
  headerColorTwo=lightblue,
  headerFontColor=white,
  boxColorOne=white,
  boxColorTwo=lightblue,
  % Format of textbox
  textborder=roundedleft,
%  textborder=faded,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  columns=2,
  headerheight=4cm,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\Large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}\large},
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=1pt
  } 
  { % Left Eye Catcher - IBM logo
\includegraphics[width=4cm]{../img/ibm_research.png}
  } 
  % Title
  	{\bf\textsc{Learning Beyond Simulated Physics}\vspace{0.2em}}
  % Authors
  {
	\textbf{Alexis Asseman, Tomasz Kornuta, Ahmet S. Ozcan}\\
	IBM Research AI, Almaden Research Center, San Jose, USA\\
	\texttt{alexis.asseman@ibm.com}, \texttt{\{tkornut, asozcan\}@us.ibm.com}\\
  }
  { % Left Eye Catcher
\includegraphics[width=4cm]{../img/arc_logo.png}
  }

% A coloured circle useful as a bullet with an adjustably strong filling
\newcommand{\colouredcircle}{%
\tikz{\useasboundingbox (-0.2em,-0.32em) rectangle(0.2em,0.32em); \draw[draw=black,fill=lightblue,line width=0.03em] (0,0) circle(0.16em);}}
\tikzstyle{block} = [draw,minimum size=2.5em, outer sep=2]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\headerbox{Abstract}{name=abstract,column=0,row=0}{
	Most advancements in terms of \textbf{time-series predictions of physical systems} is based on simulated physics.
	Thus we are proposing a \textbf{new dataset} based on videos of a real-world, \textbf{chaotic double pendulum}.
	We show baseline performance using an LSTM model, demonstrating the possibility of training directly on a real physical system.
} %headerbox

\headerbox{The Double Pendulum}{name=double-pendulum, column=0, below=abstract}{
	\begin{figure}[H]
		\centering
		\subfloat[]{{
				\includegraphics[width=0.27\textwidth]{../img/pendulum.jpg}
				\label{subfig:pendulum_picture}
		}}
		\quad\quad\quad
		\subfloat[]{{
				\def\svgwidth{0.3\textwidth}
				\footnotesize
				\input{../img/pendulum_dimensions.pdf_tex}
				\label{subfig:pendulum_dimensions}
		}}
		\caption{A picture \ref{subfig:pendulum_picture} and the dimensions \ref{subfig:pendulum_dimensions} of the double pendulum.}
		\label{fig:pendulum}
	\end{figure}

	The double pendulum is a \textbf{chaotic}\cite{levien1993} mechanical device. Even though it can be simulated, we chose to use a real one to create the Double Pendulum Chaotic Dataset. The behavior of the pendulum is influenced by environmental noise, i.e. air motion, coupling with the table, imperfections of the device, etc.
}

\headerbox{Data Acquisition}{name=data acquisition, column=0, below=double-pendulum}{
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\textwidth]{../img/camera_set_up.pdf}
		\caption{Camera set-up.}
		\label{fig:camera_set_up}
	\end{figure}
	\begin{table}[H]
		\centering
		\caption{Summary of the video settings}
		\begin{tabular}{ll}
			\toprule
			\multicolumn{2}{c}{Camera settings}\\
			\cmidrule{1-2}
			Resolution & 480x480 pixels\\
			Capture frame-rate & 400 Hz\\
			Frame exposure time & 90 \textmu s\\
			\cmidrule{1-2}
			\multicolumn{2}{c}{Data properties}\\
			\cmidrule{1-2}
			Sequence capture duration & $\approx$ 40 s\\
			Number of frames per sequence & $\approx$ 17500\\
			Number of sequences & 21\\
			\bottomrule
		\end{tabular}
		\label{tab:data_properties}
	\end{table}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.25\textwidth]{../img/0100.png}
		\caption{A video frame.}
		\label{fig:video_frame}
	\end{figure}
}

\headerbox{The Dataset}{name=dataset, column=1}{
	The dataset is available as:
	\vspace{-4pt}
	\begin{itemize}
		\itemsep0em 
		\item Full length, high quality videos
		\item Corresponding CSV files of the positions through time
	\end{itemize}
	And the ones above, precut as a train/test dataset, such that:
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.7\textwidth]{../img/dataset_split_2.pdf}
		\caption{Split of the dataset (To scale).}
		\label{fig:dataset_split}
	\end{figure}
	\vspace{-4pt}
	Where the testing data is cut in sequences of \textbf{4 input frames and 200 prediction ground-truth frames}.
}

\headerbox{ML baseline with LSTM}{name=baseline, column=1, below=dataset}{
	{
	\begin{minipage}[H]{0.4\textwidth}
		\begin{figure}[H]
			\centering
			\caption{Diagram of the LSTM\cite{lstm-paper}-based recurrent neural network used. It takes one time-step as input and predicts the next one.}
			\label{fig:lstm_diag}
			\small
			\def\svgwidth{4cm}
			\input{../img/lstm.pdf_tex}
		\end{figure}
	\end{minipage}
	\hfill
	\begin{minipage}[H]{0.4\textwidth}
		\begin{figure}[H]
			\centering
			\scalebox{0.72}{\input{../plots/lstm_sample_good.pgf}}
			\centering
			\caption{Example of a predicted sequence.}
			\label{fig:lstm_result_good}
		\end{figure}
	\end{minipage}
	\hfill
	}

		{
		\begin{minipage}[H]{0.4\textwidth}
			\begin{figure}[H]
				\centering
				\caption{Training convergence, using Adam\cite{adam-paper} as optimizer.}
				\scalebox{0.72}{\input{../plots/lstm_loss.pgf}}
				\label{fig:lstm_loss}
			\end{figure}
		\end{minipage}
		\hfill
		\begin{minipage}[H]{0.4\textwidth}
			\begin{figure}[H]
				\centering
   				\scalebox{0.72}{\input{../plots/lstm_se.pgf}}
				\label{fig:lstm_se}
				\centering
				\caption{Square error per time-step, averaged over all the test samples. $RMSE = 0.30$}
			\end{figure}
		\end{minipage}
		\hfill
	}
}

\headerbox{References}{name=references, column=1, below=baseline}{
	\small
	\vspace{-8pt}
	\renewcommand{\refname}{}
	\bibliographystyle{abbrv}
	\bibliography{sample}
	\normalsize
	\textsl{}
	\begin{center}
		The Double Pendulum Chaotic Dataset:
		\large
		\texttt{\color{blue} https://ibm.github.io/double-pendulum-chaotic-dataset/}
	\end{center}
}

\end{poster}

\end{document}

### 2018-11-21 2018_nips_vigil_poster/main.tex
adding all necessary files
begining nips poster

@@
   % Title
-  	{\bf\textsc{Learning Beyond Simulated Physics}\vspace{0.2em}}
+  	{\bf\textsc{On transfer learning using a MAC model variant}\vspace{0.2em}}
   % Authors
   {
-	\textbf{Alexis Asseman, Tomasz Kornuta, Ahmet S. Ozcan}\\
-	IBM Research AI, Almaden Research Center, San Jose, USA\\
-	\texttt{alexis.asseman@ibm.com}, \texttt{\{tkornut, asozcan\}@us.ibm.com}\\
+	\textbf{Vincent Marois, T.S. Jayram, Vincent Albouy, Tomasz Kornuta, \\Younes Bouhadjar, Ahmet S. Ozcan}\\
+
+	\texttt{\{vmarois,jayram,tkornut,byounes,asozcan\}@us.ibm.com},{\{vincent.albouy\}@ibm.com}\\
   }
@@
 \headerbox{Abstract}{name=abstract,column=0,row=0}{
-	Most advancements in terms of \textbf{time-series predictions of physical systems} is based on simulated physics.
-	Thus we are proposing a \textbf{new dataset} based on videos of a real-world, \textbf{chaotic double pendulum}.
-	We show baseline performance using an LSTM model, demonstrating the possibility of training directly on a real physical system.
+We introduce a variant of the MAC model (Hudson and Manning, ICLR 2018) with a simplified set of equations that achieves comparable accuracy, while training faster.
+We evaluate both models on CLEVR and CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.
+Finally, in contrast, we demonstrate that improper fine-tuning can actually reduce a model's accuracy as well.
 } %headerbox
 
-\headerbox{The Double Pendulum}{name=double-pendulum, column=0, below=abstract}{
+\headerbox{The MAC Model}{name=double-pendulum, column=0, below=abstract}{
 	\begin{figure}[H]
@@
 		\subfloat[]{{
-				\includegraphics[width=0.27\textwidth]{../img/pendulum.jpg}
+				\includegraphics[width=0.60\textwidth]{../img/mac_cell.pdf}
 				\label{subfig:pendulum_picture}
 		}}
-		\quad\quad\quad
-		\subfloat[]{{
-				\def\svgwidth{0.3\textwidth}
-				\footnotesize
-				\input{../img/pendulum_dimensions.pdf_tex}
-				\label{subfig:pendulum_dimensions}
-		}}
-		\caption{A picture \ref{subfig:pendulum_picture} and the dimensions \ref{subfig:pendulum_dimensions} of the double pendulum.}
+
+		\caption{The MAC cell}
 		\label{fig:pendulum}
@@
 
-	The double pendulum is a \textbf{chaotic}\cite{levien1993} mechanical device.
-Even though it can be simulated, we chose to use a real one to create the Double Pendulum Chaotic Dataset.
-The behavior of the pendulum is influenced by environmental noise, i.e.
-air motion, coupling with the table, imperfections of the device, etc.
+The MAC network is a recurrent model that performs sequential reasoning,  where each step involves analyzing a part of the question followed by shifting the attention over the image.
+The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
+The input unit uses an LSTM to process the question in a word-by-word manner producing a sequence of contextual words and a final question representation.
+Besides, the input unit utilizes a pre-trained ResNet followed by two CNN layers to extract a feature map (referred to as knowledge base) from the image.
 }
 
-\headerbox{Data Acquisition}{name=data acquisition, column=0, below=double-pendulum}{
-	\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.8\textwidth]{../img/camera_set_up.pdf}
-		\caption{Camera set-up.}
-		\label{fig:camera_set_up}
-	\end{figure}
-	\begin{table}[H]
-		\centering
-		\caption{Summary of the video settings}
-		\begin{tabular}{ll}
-			\toprule
-			\multicolumn{2}{c}{Camera settings}\\
-			\cmidrule{1-2}
-			Resolution & 480x480 pixels\\
-			Capture frame-rate & 400 Hz\\
-			Frame exposure time & 90 \textmu s\\
-			\cmidrule{1-2}
-			\multicolumn{2}{c}{Data properties}\\
-			\cmidrule{1-2}
-			Sequence capture duration & $\approx$ 40 s\\
-			Number of frames per sequence & $\approx$ 17500\\
-			Number of sequences & 21\\
-			\bottomrule
-		\end{tabular}
-		\label{tab:data_properties}
-	\end{table}
-	\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.25\textwidth]{../img/0100.png}
-		\caption{A video frame.}
-		\label{fig:video_frame}
-	\end{figure}
+\headerbox{Simplified Mac Model}{name=data acquisition, column=0, below=double-pendulum}{
+
 }
 
-\headerbox{The Dataset}{name=dataset, column=1}{
-	The dataset is available as:
-	\vspace{-4pt}
-	\begin{itemize}
-		\itemsep0em 
-		\item Full length, high quality videos
-		\item Corresponding CSV files of the positions through time
-	\end{itemize}
-	And the ones above, precut as a train/test dataset, such that:
-	\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.7\textwidth]{../img/dataset_split_2.pdf}
-		\caption{Split of the dataset (To scale).}
-		\label{fig:dataset_split}
-	\end{figure}
-	\vspace{-4pt}
-	Where the testing data is cut in sequences of \textbf{4 input frames and 200 prediction ground-truth frames}.
+\headerbox{Transfer Learning - Experiments}{name=dataset, column=1}{
 }
 
-\headerbox{ML baseline with LSTM}{name=baseline, column=1, below=dataset}{
+\headerbox{MAC failures examples on CLEVR}{name=baseline, column=1, below=dataset}{
 	{
-	\begin{minipage}[H]{0.4\textwidth}
-		\begin{figure}[H]
-			\centering
-			\caption{Diagram of the LSTM\cite{lstm-paper}-based recurrent neural network used. It takes one time-step as input and predicts the next one.}
-			\label{fig:lstm_diag}
-			\small
-			\def\svgwidth{4cm}
-			\input{../img/lstm.pdf_tex}
-		\end{figure}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[H]{0.4\textwidth}
-		\begin{figure}[H]
-			\centering
-			\scalebox{0.72}{\input{../plots/lstm_sample_good.pgf}}
-			\centering
-			\caption{Example of a predicted sequence.}
-			\label{fig:lstm_result_good}
-		\end{figure}
-	\end{minipage}
-	\hfill
 	}
@@
 		{
-		\begin{minipage}[H]{0.4\textwidth}
-			\begin{figure}[H]
-				\centering
-				\caption{Training convergence, using Adam\cite{adam-paper} as optimizer.}
-				\scalebox{0.72}{\input{../plots/lstm_loss.pgf}}
-				\label{fig:lstm_loss}
-			\end{figure}
-		\end{minipage}
-		\hfill
-		\begin{minipage}[H]{0.4\textwidth}
-			\begin{figure}[H]
-				\centering
-   				\scalebox{0.72}{\input{../plots/lstm_se.pgf}}
-				\label{fig:lstm_se}
-				\centering
-				\caption{Square error per time-step, averaged over all the test samples. $RMSE = 0.30$}
-			\end{figure}
-		\end{minipage}
-		\hfill
+
 	}

### 2018-11-26 2018_nips_vigil_poster/main.tex
update VIGIL poster

@@
 \usepackage{pgf}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{multicol}
 \usepackage{placeins} % For \FloatBarrier
@@
 \usepackage{multirow}
+
+% For gap between cmidrules.
+\usepackage{array}
+\newcolumntype{C}{@{\extracolsep{0.1cm}}c@{\extracolsep{0pt}}}%
+
+\setlength{\columnsep}{1cm}
+\setlength{\columnseprule}{0.5pt}
+\def\columnseprulecolor{\color{Plum}}
 
@@
 
+	Our proposed modification to the MAC network is based on two heuristic simplifications of the
+	MAC cell. First, we observe that, taking the MAC cell equations as a whole, consecutive linear
+	layers (with no activation in-between) can be combined as one linear layer. Next, we assume that
+	dimension-preserving linear layers are invertible so as to avoid information loss. Applying this
+	principle to the equations, with a careful reorganization, we can apply a single linear layer to the
+	knowledge base prior to all the reasoning steps and work with this projected knowledge base as-is
+	throughout the reasoning steps.
+
+	\begin{table}[H]
+		\centering
+		\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
+		\begin{tabular}{llll}
+			\toprule
+			Model        & Read Unit               & Write Unit &  Control Unit         \\
+			\midrule
+			MAC   &  787,969 &  524,800        &    525,313    \\
+			%\midrule
+			simplified MAC & 263,168  & 262,656       &    263,168 \\
+			\midrule
+			Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
+			\bottomrule
+		\end{tabular}
+		\label{tab:data_properties}
+	\end{table}
 }
@@
 \headerbox{Transfer Learning - Experiments}{name=dataset, column=1}{
+	\begin{table}[H]
+	\centering
+	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
+	\begin{tabular}{lllllllll}
+		\toprule
+		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
+		\midrule
+		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
+		\cmidrule{1-8}
+		\cmidrule{1-8}
+
+		\multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29         & (b)  \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
+
+		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91        & (c)  \\
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
+
+		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47  & (d) \\
+		\cmidrule{7-8} 
+		&                        &   &              &     &                               & CoGenT-B   &  95.58  & (e)\\
+
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71        & (f)  \\
+		\cmidrule{5-6} \cmidrule{7-8} 
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24        & (g) \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    94.55     & (h)  \\
+
+		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
+		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11       & (i) \\
+		\cmidrule{7-8} 
+		&                             &                                         &       &         &                & CoGenT-B &    92.95    & (j)  \\
+
+		\bottomrule
+
+	\end{tabular}
+	\label{tab:data_properties}
+\end{table}
 }

### 2018-11-26 2018_nips_vigil_poster/main.tex
new update VIGIL poster

@@
 \headerbox{MAC failures examples on CLEVR}{name=baseline, column=1, below=dataset}{
-	{
-	}
 
-		{
+	\begin{figure}[H]
+	\centering
+	\subfloat[]{{
+			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_shape.png}
+			\label{subfig:pendulum_picture}
+	}}
 
-	}
+	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
+	\label{fig:fail_mac_shape}
+\end{figure}
+	\begin{figure}[H]
+	\centering
+	\subfloat[]{{
+			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_color.png}
+			\label{subfig:pendulum_picture}
+	}}
+
+	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
+    \label{fig:fail_mac_color}
+\end{figure}
+
 }

### 2018-11-28 2018_nips_vigil_poster/main.tex
mino clean up
resizing table 2
last update poster vigil

@@
-\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.3]{baposter}
+\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.35]{baposter}
 % NIPS Workshops format
@@
 \usepackage{multirow}
+\usepackage{graphicx}
 
@@
 \headerbox{Abstract}{name=abstract,column=0,row=0}{
-We introduce a variant of the MAC model (Hudson and Manning, ICLR 2018) with a simplified set of equations that achieves comparable accuracy, while training faster.
-We evaluate both models on CLEVR and CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.
-Finally, in contrast, we demonstrate that improper fine-tuning can actually reduce a model's accuracy as well.
+\begin{description}
+
+	\item[$\bullet$] 	We introduce a variant of the MAC model (Hudson and Manning, ICLR 2018) with a simplified set of equations that achieves comparable accuracy, while training faster
+
+	\item[$\bullet$] We evaluate both models on CLEVR and CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.
+
+	\item[$\bullet$] We demonstrate that improper fine-tuning can reduce a model's accuracy as well.
+
+\end{description}
+
 } %headerbox
@@
 		\subfloat[]{{
-				\includegraphics[width=0.60\textwidth]{../img/mac_cell.pdf}
+				\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
 				\label{subfig:pendulum_picture}
@@
 
-The MAC network is a recurrent model that performs sequential reasoning,  where each step involves analyzing a part of the question followed by shifting the attention over the image.
-The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
-The input unit uses an LSTM to process the question in a word-by-word manner producing a sequence of contextual words and a final question representation.
-Besides, the input unit utilizes a pre-trained ResNet followed by two CNN layers to extract a feature map (referred to as knowledge base) from the image.
+\begin{description}
+	\item[$\bullet$] The MAC network is a recurrent model that performs sequential reasoning; at each step the model analyzes the question and shifts the attention over the image
+	\item[$\bullet$] The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
+	\item[$\bullet$] The input unit uses an LSTM to process the question in a word-by-word manner producing a sequence of contextual words and a final question representation.
+	\item[$\bullet$] The input unit utilizes a pre-trained ResNet followed by two CNN layers to extract a feature map  from the image.
+
+\end{description}
+
 }
 
-\headerbox{Simplified Mac Model}{name=data acquisition, column=0, below=double-pendulum}{
+\headerbox{Simplified Mac Model (S-MAC)}{name=data acquisition, column=0, below=double-pendulum}{
 
 	Our proposed modification to the MAC network is based on two heuristic simplifications of the
-	MAC cell. First, we observe that, taking the MAC cell equations as a whole, consecutive linear
-	layers (with no activation in-between) can be combined as one linear layer. Next, we assume that
-	dimension-preserving linear layers are invertible so as to avoid information loss. Applying this
-	principle to the equations, with a careful reorganization, we can apply a single linear layer to the
-	knowledge base prior to all the reasoning steps and work with this projected knowledge base as-is
-	throughout the reasoning steps.
+	MAC cell:
+
+	\begin{description}
+
+    \item[$\bullet$] 	First, we observe that, taking the MAC cell equations as a whole, consecutive linear
+	layers (with no activation in-between) can be combined as one linear layer.
+
+	\item[$\bullet$] Secondly, we assume that
+	dimension-preserving linear layers are invertible so as to avoid information loss.
+
+   \end{description}
+
+\makebox[\textwidth]{MAC  \\[5cm] S-MAC}\\
+\noindent\textbf{Control unit:} 
+For both models, the question $q$ is first transformed in each step of 
+the reasoning using a \emph{position-aware}
+linear layer depending on $i$: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
+
+\begin{multicols}{2}
+	\noindent
+	\begin{align*}
+	&cq_i = W_{cq}^{[d \times 2d]} [c_{i-1}, q_i] + b_{cq}^{[d]}  \tag{c1} \\
+	&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s) + b_{ca}^{[1]}
+	\tag{c2.1}\\
+	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
+	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
+	\end{align*}
+	\columnbreak
+	{\color{Plum}
+		\begin{align*}
+		&cq_i = W_{cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
+		&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s)  \tag{c2.1}\\
+		&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
+		&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
+		\end{align*}}
+\end{multicols}
+
+\vskip -0.6cm
+
+\noindent\textbf{Read and write units:}
+\begin{multicols}{2}
+	\noindent
+	\begin{align*}
+	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
+	& \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
+	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
+	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
+	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
+	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
+	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
+	\end{align*}
+	\columnbreak
+	{\color{Plum}
+		\begin{align*}
+		&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
+		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
+		&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
+		&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
+		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
+		&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
+		\end{align*}}
+\end{multicols}
 
@@
 \end{table}
+
 }
@@
 \headerbox{Transfer Learning - Experiments}{name=dataset, column=1}{
+
+Along with CLEVR, the authors~\cite{hudson2018compositional} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
+This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.
+
 	\begin{table}[H]
 		\centering
-	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
+		\begin{tabular}{llll}
+			\toprule
+			Dataset        & Cubes              & Cylinders &  Spheres         \\
+			\midrule
+			CLEVR   &  any color &  any color        &    any color    \\
+			CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
+			CLEVR CoGenT B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
+			\bottomrule
+		\end{tabular}
+		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
+		\label{tab:cogent_conditions}
+	\end{table}
+
+	\begin{table}[H]
+	\centering
+	\scalebox{0.9}{
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.
+The [Training] column indicates wall times and final accuracies on the training set.
+For fine-tuning, we use 30k samples of the test set, and kept the remainder for testing.
+The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training.
+The [Test] column reports the used set and the obtained test accuracies.
+If no fine-tuning was done, the whole indicated set was used for testing.}
 	\begin{tabular}{lllllllll}
@@
 
-	\end{tabular}
+	\end{tabular}}
 	\label{tab:data_properties}
@@
 
-\headerbox{MAC failures examples on CLEVR}{name=baseline, column=1, below=dataset}{
+\headerbox{MAC limitations on CLEVR}{name=baseline, column=1, below=dataset}{
 
@@
 	\subfloat[]{{
-			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_shape.png}
+			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_shape.png}
 			\label{subfig:pendulum_picture}
@@
 	\subfloat[]{{
-			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_color.png}
+			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_color.png}
 			\label{subfig:pendulum_picture}
@@
 \headerbox{References}{name=references, column=1, below=baseline}{
-	\small
-	\vspace{-8pt}
-	\renewcommand{\refname}{}
-	\bibliographystyle{abbrv}
-	\bibliography{sample}
-	\normalsize
-	\textsl{}
-	\begin{center}
-		The Double Pendulum Chaotic Dataset:
-		\large
-		\texttt{\color{blue} https://ibm.github.io/double-pendulum-chaotic-dataset/}
-	\end{center}
+\bibliographystyle{alpha}
+\bibliography{vigil_bibliograph}
 }

### 2018-11-28 2018_nips_vigil_poster/main.tex
update poster vigil

@@
 
-\headerbox{The MAC Model}{name=double-pendulum, column=0, below=abstract}{
+\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=double-pendulum, column=0, below=abstract}{
 	\begin{figure}[H]
@@
 
-		\caption{The MAC cell}
+		\caption{The MAC cell ~\cite{hudson2018compositional}}
 		\label{fig:pendulum}
@@
 
-Along with CLEVR, the authors~\cite{hudson2018compositional} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
+Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
 This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.
@@
 \headerbox{References}{name=references, column=1, below=baseline}{
+	\small
+	\vspace{-8pt}
+	\renewcommand{\refname}{}
 	\bibliographystyle{alpha}
-\bibliography{vigil_bibliograph}
+	\bibliography{vigil_bibliography}
+	\normalsize
+	\textsl{}
 }

### 2018-11-28 2018_nips_vigil_poster/main.tex
update vigil poster

@@
 		\centering
-		\subfloat[]{{
+
 		\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
 		\label{subfig:pendulum_picture}
-		}}
-
 		\caption{The MAC cell ~\cite{hudson2018compositional}}
@@
 
+\begin{description}
+
+	\item[$\bullet$] Simplifications results in a 10\% speed up in training time.
+
+\end{description}
+
 \begin{table}[H]
@@
 
-\headerbox{Transfer Learning - Experiments}{name=dataset, column=1}{
+\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
+The CLEVR task:
+		\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.33\textwidth]{../img/teaser.jpg}
+	    \end{figure}
 
-Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
-This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.
+    \begin{description}
+    	\centering
+    	\item[$\cdot$] \textit{How many objects are either small cylinders or red things?}
+
+    \end{description}
+
+   \begin{description}
+   	\item[$\bullet$]Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT 
+   	\item[$\bullet$] The goal is to evaluate how well the models can generalize, learn relations and compositional concepts.
+   	\item[$\bullet$] This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.
+
+   \end{description}
 
@@
 
+}
+
+\headerbox{Transfer Learning - Experiments}{name=transfer, column=1, below=dataset}{
+
+CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
 	\begin{table}[H]
@@
 	\scalebox{0.9}{
-	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.
-The [Training] column indicates wall times and final accuracies on the training set.
-For fine-tuning, we use 30k samples of the test set, and kept the remainder for testing.
-The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training.
-The [Test] column reports the used set and the obtained test accuracies.
-If no fine-tuning was done, the whole indicated set was used for testing.}
 	\begin{tabular}{lllllllll}
@@
 \end{table}
+
+\begin{description}
+	\item[$\bullet$] The [Training] column indicates wall times and final accuracies on the training set.
+	\item[$\bullet$] The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training
+	\item[$\bullet$] Experiments can be reproduced by following the \textbf{mi-prometheus}  documentation
+\end{description}
+
 }
 
-\headerbox{MAC limitations on CLEVR}{name=baseline, column=1, below=dataset}{
+\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=transfer}{
 
@@
 	}}
+	\label{fig:fail_mac_shape}
 
-	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
-	\label{fig:fail_mac_shape}
 \end{figure}
-	\begin{figure}[H]
-	\centering
-	\subfloat[]{{
-			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_color.png}
-			\label{subfig:pendulum_picture}
-	}}
 
-	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
-    \label{fig:fail_mac_color}
-\end{figure}
+\begin{description}
+	\item[$\bullet$] The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?
+Predicted answer: Cylinder - Truth: Cube}
+
+\end{description}
 

### 2018-11-29 2018_nips_vigil_poster/main.tex
final update vigil

@@
-\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.35]{baposter}
+\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.36]{baposter}
 % NIPS Workshops format
@@
   { % Left Eye Catcher
+
 \includegraphics[width=4cm]{../img/arc_logo.png}
+
   }
@@
 
-		\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
+		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
 		\label{subfig:pendulum_picture}
@@
 	\item[$\bullet$] The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
-	\item[$\bullet$] The input unit uses an LSTM to process the question in a word-by-word manner producing a sequence of contextual words and a final question representation.
-	\item[$\bullet$] The input unit utilizes a pre-trained ResNet followed by two CNN layers to extract a feature map  from the image.
+	\item[$\bullet$] The input unit uses an LSTM to process the question  and CNN layers to extract a feature map  from the image.
 
@@
 
-	Our proposed modification to the MAC network is based on two heuristic simplifications of the
-	MAC cell:
+	Our proposed modification to the MAC network is based on two heuristic simplifications:
 
@@
 		\begin{align*}
-		&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
+		&I_{ihw} = m _{i-1} \odot k _{hw} \tag{r1} \\ 
 		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
@@
 
+\headerbox{Links}{name=links,column=0,below=data acquisition}{
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{cc} 
+			\includegraphics[height=1.6 cm]{../img/github_repo_qr_code.png} &
+			\includegraphics[height=1.6 cm]{../img/doc_qr_code.png}  &
+			Github &  Reproducibility \\
+			repository & documentation
+		\end{tabular}
+	\end{center}
+}
+
+}
+
 \headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
@@
 		\centering
-		\includegraphics[width=0.33\textwidth]{../img/teaser.jpg}
+		\includegraphics[width=0.35\textwidth]{../img/teaser.jpg}
 	    \end{figure}
@@
 	\centering
-	\scalebox{0.9}{
+	\scalebox{1}{
 	\begin{tabular}{lllllllll}
@@
 	\centering
-	\subfloat[]{{
-			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_shape.png}
-			\label{subfig:pendulum_picture}
-	}}
-	\label{fig:fail_mac_shape}
+				\includegraphics[width=0.65\textwidth]{../img/fail_mac_cogent_b_shape.png}
 

### 2018-11-29 2018_nips_vigil_poster/main.tex
vigil last update

@@
 
-}
-
 \headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
@@
 		\centering
-		\includegraphics[width=0.35\textwidth]{../img/teaser.jpg}
+		\includegraphics[width=0.31\textwidth]{../img/teaser.jpg}
 	    \end{figure}
@@
 \begin{description}
-	\item[$\bullet$] The [Training] column indicates wall times and final accuracies on the training set.
-	\item[$\bullet$] The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training
+	\item[$\bullet$] Our experiments on zero-short learning show that the MAC model has poor performance in line with
+	the other models in the literature.
+	\item[$\bullet$] With fine-tuning, the MAC model matches state of
+	the art accuracy
+	\item[$\bullet$]Remains an interesting problem to investigate how we can train it to disentangle the concepts of shape and color.
 	\item[$\bullet$] Experiments can be reproduced by following the \textbf{mi-prometheus}  documentation
@@
 	\centering
-				\includegraphics[width=0.65\textwidth]{../img/fail_mac_cogent_b_shape.png}
+				\includegraphics[width=0.60\textwidth]{../img/fail_mac_cogent_b_shape.png}
 

### 2018-11-29 2018_nips_vigil_poster/main.tex
Remove Plum color + add macros for equations.
Removed more unnecessary files.

@@
 \setlength{\columnseprule}{0.5pt}
-\def\columnseprulecolor{\color{Plum}}
 
@@
 }
+
+% macros for the equations
+\newcommand{\cw}{\mathbf{cw}}
+\newcommand{\cc}{\mathbf{c}}
+\newcommand{\kb}{\mathbf{k}}
+\newcommand{\mem}{\mathbf{m}}
+\newcommand{\rr}{\mathbf{r}}
 
@@
 	\columnbreak
-	{\color{Plum}
+	{
 		\begin{align*}
@@
 \headerbox{Links}{name=links,column=0,below=data acquisition}{
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{cc} 
-			\includegraphics[height=1.6 cm]{../img/github_repo_qr_code.png} &
-			\includegraphics[height=1.6 cm]{../img/doc_qr_code.png}  &
-			Github &  Reproducibility \\
-			repository & documentation
-		\end{tabular}
-	\end{center}
+	\vspace{-15pt}
+	\begin{minipage}[H]{0.4\textwidth}
+		\begin{figure}[H]
+			\includegraphics[width=0.4\textwidth]{../img/doc_qr_code.png}
+			\vspace{-10pt}
+			\caption{Documentation.}
+			\label{fig:qr_doc}
+		\end{figure}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[H]{0.4\textwidth}
+		\begin{figure}[H]
+			\includegraphics[width=0.4\textwidth]{../img/github_repo_qr_code.png}
+			\vspace{-10pt}
+			\caption{GitHub repo.}
+			\label{fig:qr_github}
+		\end{figure}
+	\end{minipage}
 }
@@
 	\bibliographystyle{alpha}
-	\bibliography{vigil_bibliography}
+	\bibliography{../vigil_bibliography}
 	\normalsize

### 2018-11-29 2018_nips_vigil_poster/main.tex
Removed unnecessary packages.

@@
 \usepackage{graphicx} % Required for including images
-\usepackage{subfig}
 \usepackage{booktabs} % for professional tables
 \usepackage{floatrow}
-\usepackage{float}
-
-\usepackage{textgreek}
-\usepackage{pstricks}
-\usepackage{tikz}
-\usepackage{pgf}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{multicol}
-\usepackage{placeins} % For \FloatBarrier
-\usetikzlibrary{positioning}
-\usepackage{environ}
-\makeatletter
-\newsavebox{\measure@tikzpicture}
-\NewEnviron{scaletikzpicturetowidth}[1]{%
-	\def\tikz@width{#1}%
-	\def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
-		\BODY
-	\end{lrbox}%
-	\pgfmathparse{#1/\wd\measure@tikzpicture}%
-	\edef\tikzscale{\pgfmathresult}%
-	\BODY
-}
-\makeatother
-
 \usepackage{amsmath} % For typesetting math
-\usepackage{amssymb} % Adds new symbols to be used in math mode
-
-\usepackage{booktabs} % Top and bottom rules for tables
-\usepackage{enumitem} % Used to reduce itemize/enumerate spacing
-%\usepackage{palatino} % Use the Palatino font
-\renewcommand{\familydefault}{\sfdefault}
 \usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
@@
 \usepackage{multicol} % Required for multiple columns
-\setlength{\columnsep}{1.5em} % Slightly increase the space between columns
-\setlength{\columnseprule}{0mm} % No horizontal rule between columns
+\setlength{\columnsep}{1cm}
+\setlength{\columnseprule}{0.5pt}
 \usepackage{multirow}
@@
 
-\setlength{\columnsep}{1cm}
-\setlength{\columnseprule}{0.5pt}
-
 \newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{itemize} or \begin{enumerate}
@@
 
+% Defines the color used for content box headers
+\definecolor{lightblue}{cmyk}{0.83,0.24,0,0.16}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % macros for the equations
@@
 \newcommand{\rr}{\mathbf{r}}
-
-% Defines the color used for content box headers
-\definecolor{lightblue}{cmyk}{0.83,0.24,0,0.16}
-%\definecolor{lightblue}{rgb}{0.145,0.6666,1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% Pojedyncze spacje po kropce.
 \frenchspacing

### 2018-11-29 2018_nips_vigil_poster/main.tex
Reduce text to gain space + better description of MAC cell & simplifications.

@@
 \usepackage{amsmath} % For typesetting math
-\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
+\usepackage[font=small,labelfont=bf, justification=centering]{caption} % Required for specifying captions to tables and figures
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \frenchspacing
@@
   columns=2,
-  headerheight=4cm,
+  headerheight=3cm,
 %  textfont=\sc, An example of changing the text font
@@
   {
-	\textbf{Vincent Marois, T.S. Jayram, Vincent Albouy, Tomasz Kornuta, \\Younes Bouhadjar, Ahmet S. Ozcan}\\
-
-	\texttt{\{vmarois,jayram,tkornut,byounes,asozcan\}@us.ibm.com},{\{vincent.albouy\}@ibm.com}\\
+	\textbf{\null\hfill Vincent Marois \hfill T.S. Jayram \hfill Vincent Albouy \hfill Tomasz Kornuta \hfill\null}\\
+	\textbf{\null\hfill Younes Bouhadjar \hfill Ahmet S. Ozcan \hfill\null}\\
+	\texttt{\{vmarois,jayram,tkornut,byounes,asozcan\}@us.ibm.com, \{vincent.albouy\}@ibm.com}
   }
   { % Left Eye Catcher
-
   	\includegraphics[width=4cm]{../img/arc_logo.png}
-
   }
 
-% A coloured circle useful as a bullet with an adjustably strong filling
-\newcommand{\colouredcircle}{%
-\tikz{\useasboundingbox (-0.2em,-0.32em) rectangle(0.2em,0.32em); \draw[draw=black,fill=lightblue,line width=0.03em] (0,0) circle(0.16em);}}
-\tikzstyle{block} = [draw,minimum size=2.5em, outer sep=2]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\headerbox{Summary}{name=summary,column=0,row=0}{
+\begin{itemize}
+	\compresslist
+	\item[$\bullet$] We introduce a simplified variant of the MAC model (\textit{Hudson and Manning, ICLR 2018}), which achieves comparable accuracy while training faster.
+	\item[$\bullet$] We evaluate both models on CLEVR \& CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.
+	\item[$\bullet$] We also demonstrate that improper fine-tuning can reduce a model's accuracy.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\headerbox{Abstract}{name=abstract,column=0,row=0}{
-\begin{description}
-
-	\item[$\bullet$] 	We introduce a variant of the MAC model (Hudson and Manning, ICLR 2018) with a simplified set of equations that achieves comparable accuracy, while training faster
-
-	\item[$\bullet$] We evaluate both models on CLEVR and CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.
-
-	\item[$\bullet$] We demonstrate that improper fine-tuning can reduce a model's accuracy as well.
-
-\end{description}
+\end{itemize}
 
@@
 
-\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=double-pendulum, column=0, below=abstract}{
+\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=mac-model, column=0, below=summary}{
+	\vspace{-10pt}
 	\begin{figure}[H]
 		\centering
-
 		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
-		\label{subfig:pendulum_picture}
-		\caption{The MAC cell ~\cite{hudson2018compositional}}
-		\label{fig:pendulum}
+		\caption{The MAC cell ~\cite{hudson2018compositional}.}
+		\label{fig:mac_cell}
 	\end{figure}
-
-\begin{description}
-	\item[$\bullet$] The MAC network is a recurrent model that performs sequential reasoning; at each step the model analyzes the question and shifts the attention over the image
-	\item[$\bullet$] The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
-	\item[$\bullet$] The input unit uses an LSTM to process the question  and CNN layers to extract a feature map  from the image.
-
-\end{description}
-
+	\vspace{-20pt}
+	\begin{itemize}
+		\compresslist
+		\item[$\bullet$] MAC network: a recurrent model performing sequential reasoning. At each step, it analyzes the question and shifts the attention over the image.
+		\item[$\bullet$] Recurrent MAC cell: consists of a control unit, a read unit \& a write unit. The control unit updates the control state $c_i$ \& drives the attention over the question words.
+		\item[$\bullet$] The read unit, guided by $c_i$ extracts information from the image. The write unit uses this information to update the memory state $m_i$.
+	\end{itemize}
 }
 
-\headerbox{Simplified Mac Model (S-MAC)}{name=data acquisition, column=0, below=double-pendulum}{
+\headerbox{Simplified Mac Model (S-MAC)}{name=s-mac, column=0, below=mac-model}{
 
-	Our proposed modification to the MAC network is based on two heuristic simplifications:
+	Based on two heuristic simplifications:
 
-	\begin{description}
+	\begin{itemize}
+		\compresslist
+	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
+		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
+    \end{itemize}
 
-    \item[$\bullet$] 	First, we observe that, taking the MAC cell equations as a whole, consecutive linear
-	layers (with no activation in-between) can be combined as one linear layer.
-
-	\item[$\bullet$] Secondly, we assume that
-	dimension-preserving linear layers are invertible so as to avoid information loss.
-
-   \end{description}
+	This allows, with a careful reorganization, to apply a single linear layer to the \textit{knowledge base} (feature map extracted from the image) prior to all the reasoning steps and work with this projection throughout the reasoning steps.\\
 
 \makebox[\textwidth]{MAC  \\[5cm] S-MAC}\\
-\noindent\textbf{Control unit:} 
-For both models, the question $q$ is first transformed in each step of 
-the reasoning using a \emph{position-aware}
-linear layer depending on $i$: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
+\noindent\textbf{Control unit:} The question $q$ is first made \emph{position-aware} in each reasoning step using an $i$-dependent projection: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
 
@@
 
-\begin{description}
-
-	\item[$\bullet$] Simplifications results in a 10\% speed up in training time.
-
-\end{description}
-
 \begin{table}[H]
@@
 	\end{tabular}
-	\label{tab:data_properties}
+	\label{tab:mac_cell_parameters}
 \end{table}
@@
 
-\headerbox{Links}{name=links,column=0,below=data acquisition}{
+\headerbox{Links}{name=links,column=0,below=s-mac}{
 	\vspace{-15pt}

### 2018-11-29 2018_nips_vigil_poster/main.tex
Finalize Equations & Datasets section.

@@
-\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.36]{baposter}
+\documentclass[paperwidth=36in,paperheight=48in,portrait,fontscale=0.36]{baposter}
 % NIPS Workshops format
@@
 \usepackage{amsmath} % For typesetting math
-\usepackage[font=small,labelfont=bf, justification=centering]{caption} % Required for specifying captions to tables and figures
+\usepackage[labelfont=bf, justification=centering]{caption} % Required for specifying captions to tables and figures
 
@@
 	\compresslist
-	\item[$\bullet$] We introduce a simplified variant of the MAC model (\textit{Hudson and Manning, ICLR 2018}), which achieves comparable accuracy while training faster.
-	\item[$\bullet$] We evaluate both models on CLEVR \& CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.
-	\item[$\bullet$] We also demonstrate that improper fine-tuning can reduce a model's accuracy.
+	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model (\textit{Hudson and Manning, ICLR 2018}), which achieves comparable accuracy while training \emph{\textbf{faster}}.
+	\item[$\bullet$] We evaluate both models on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
+	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can reduce a model's accuracy.
 
@@
 
-\makebox[\textwidth]{MAC  \\[5cm] S-MAC}\\
+\makebox[\textwidth]{\textbf{MAC \\[5cm] S-MAC}}\\
+\vspace{-5pt}
+\hrule
+\vspace{10pt}
 \noindent\textbf{Control unit:} The question $q$ is first made \emph{position-aware} in each reasoning step using an $i$-dependent projection: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.
@@
 	\columnbreak
-	{
-		\begin{align*}
+	{\begin{align*}
 		&cq_i = W_{cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
@@
 	\columnbreak
-	{
-		\begin{align*}
+	{\begin{align*}
 		&I_{ihw} = m _{i-1} \odot k _{hw} \tag{r1} \\ 
@@
 
+\vspace{-15pt}
 \begin{table}[H]
@@
 		MAC   &  787,969 &  524,800        &    525,313    \\
-		%\midrule
-		simplified MAC & 263,168  & 262,656       &    263,168 \\
+		S-MAC & 263,168  & 262,656       &    263,168 \\
 		\midrule
@@
 
-\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
-The CLEVR task:
+\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
+	\vspace{-10pt}
 	\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.31\textwidth]{../img/teaser.jpg}
+		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
+		\caption{\textit{How many objects are either small cylinders or red things?}}
+		\label{fig:clevr_task}
 	\end{figure}
-
-    \begin{description}
-    	\centering
-    	\item[$\cdot$] \textit{How many objects are either small cylinders or red things?}
-
-    \end{description}
-
-   \begin{description}
-   	\item[$\bullet$]Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT 
-   	\item[$\bullet$] The goal is to evaluate how well the models can generalize, learn relations and compositional concepts.
-   	\item[$\bullet$] This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.
-
-   \end{description}
-
+	\vspace{-10pt}
+	\begin{itemize}
+	  	\compresslist
+	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
+	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
+	\end{itemize}
+	\vspace{-10pt}
 	\begin{table}[H]
@@
 			CLEVR   &  any color &  any color        &    any color    \\
-			CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
-			CLEVR CoGenT B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
+			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
+			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
 			\bottomrule
@@
 
-\headerbox{Transfer Learning - Experiments}{name=transfer, column=1, below=dataset}{
+\headerbox{Experiments \& Results}{name=experiments, column=1, below=datasets}{
 
@@
 	\scalebox{1}{
-	\begin{tabular}{lllllllll}
+	\begin{tabular}{cccccccc}
 		\toprule
-		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
+		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} \\
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
+		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
 		\midrule
-		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
+		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17 \\
 		\cmidrule{1-8}
@@
 
-		\multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29         & (b)  \\
+		\multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29 \\
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
 
-		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91        & (c)  \\
+		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91 \\
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
 
-		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47  & (d) \\
+		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47 \\
 		\cmidrule{7-8} 
-		&                        &   &              &     &                               & CoGenT-B   &  95.58  & (e)\\
+		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\
 
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71        & (f)  \\
+		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71 \\
 		\cmidrule{5-6} \cmidrule{7-8} 
-		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24        & (g) \\
+		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24 \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    94.55     & (h)  \\
+		&                             &                                         &       &         &                & CoGenT-B &    94.55 \\
 
 		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
-		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11       & (i) \\
+		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11 \\
 		\cmidrule{7-8} 
-		&                             &                                         &       &         &                & CoGenT-B &    92.95    & (j)  \\
+		&                             &                                         &       &         &                & CoGenT-B &    92.95 \\
 
@@
 
-\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=transfer}{
+\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=experiments}{
 

### 2018-11-29 2018_nips_vigil_poster/main.tex
Add better QR codes & finalize poster.

@@
 		\begin{figure}[H]
-			\includegraphics[width=0.4\textwidth]{../img/doc_qr_code.png}
+			\includegraphics[width=0.4\textwidth]{../img/arxiv_paper_qr_code.png}
 			\vspace{-10pt}
-			\caption{Documentation.}
-			\label{fig:qr_doc}
+			\caption{Paper on arXiv.}
+			\label{fig:qr_arxiv}
 		\end{figure}
@@
 		\begin{figure}[H]
-			\includegraphics[width=0.4\textwidth]{../img/github_repo_qr_code.png}
+			\includegraphics[width=0.4\textwidth]{../img/reproducible_research_qr_code.png}
 			\vspace{-10pt}
-			\caption{GitHub repo.}
-			\label{fig:qr_github}
+			\caption{\textbf{How to reproduce the experiments.}}
+			\label{fig:qr_repro_research}
 		\end{figure}
@@
 	\end{figure}
-	\vspace{-10pt}
+	\vspace{-20pt}
 	\begin{itemize}
@@
 \headerbox{Experiments \& Results}{name=experiments, column=1, below=datasets}{
-
-CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
+	\vspace{-10pt}
 	\begin{table}[H]
@@
 		\bottomrule
-
 	\end{tabular}}
+	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
 	\label{tab:data_properties}
 \end{table}
+\vspace{-20pt}
 
-\begin{description}
-	\item[$\bullet$] Our experiments on zero-short learning show that the MAC model has poor performance in line with
+\begin{itemize}
+	\compresslist
+	\item[$\bullet$] Our experiments on \emph{zero-shot learning} show that both models have poor performance, in line with
 	the other models in the literature.
-	\item[$\bullet$] With fine-tuning, the MAC model matches state of
-	the art accuracy
-	\item[$\bullet$]Remains an interesting problem to investigate how we can train it to disentangle the concepts of shape and color.
-	\item[$\bullet$] Experiments can be reproduced by following the \textbf{mi-prometheus}  documentation
-\end{description}
+	\item[$\bullet$] With fine-tuning, both MAC models match state-of-the-art accuracy (a 15pts increase).
+	\item[$\bullet$] \textbf{S-MAC presents a 10\% speed-up in training time and comparable accuracy.}
+	\item[$\bullet$] Finetuning CLEVR-trained models on CoGenT-A or -B hurts their generalization capabilities.
+	\item[$\rightarrow$] \emph{Zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) remains an interesting problem to solve.
+\end{itemize}
 
@@
 
-\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=experiments}{
-
+\headerbox{MAC drawbacks on CLEVR}{name=mac-failures, column=1, below=experiments}{
+	\vspace{-10pt}
 	\begin{figure}[H]
-	\centering
 		\includegraphics[width=0.60\textwidth]{../img/fail_mac_cogent_b_shape.png}
-
+		\caption{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}
+		\label{fig:mac_failure}
 	\end{figure}
-
-\begin{description}
-	\item[$\bullet$] The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?
-Predicted answer: Cylinder - Truth: Cube}
-
-\end{description}
-
+	\vspace{-20pt}
+	\begin{itemize}
+		\compresslist
+		\item[$\bullet$] Asked about the shape of the leftmost gray cylinder, the model correctly finds it, (cf.
+\emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
+		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \emph{gray cylinders} during training, but saw \emph{gray cubes}.
+		\item[$\rightarrow$] Indicate that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
+	\end{itemize}
 }
 
-\headerbox{References}{name=references, column=1, below=baseline}{
+\headerbox{References}{name=references, column=1, below=mac-failures}{
 	\small
@@
 	\bibliography{../vigil_bibliography}
-	\normalsize
-	\textsl{}
 }
@@
 \end{poster}
-
 \end{document}

### 2018-11-29 2018_nips_vigil_poster/main.tex
Better section name.

@@
 
-\headerbox{MAC drawbacks on CLEVR}{name=mac-failures, column=1, below=experiments}{
+\headerbox{Compositional generalization of the MAC model}{name=mac-failures, column=1, below=experiments}{
 	\vspace{-10pt}
@@
 		\compresslist
-		\item[$\bullet$] Asked about the shape of the leftmost gray cylinder, the model correctly finds it, (cf.
+		\item[$\bullet$] Asked about the shape of the leftmost \textbf{gray cylinder}, the model correctly finds it, (cf.
 \emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
-		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \emph{gray cylinders} during training, but saw \emph{gray cubes}.
+		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \textbf{gray cylinders} during training, but saw \textbf{gray cubes}.
 		\item[$\rightarrow$] Indicate that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).

### 2018-11-29 2018_nips_vigil_poster/main.tex
Change font.
Integrated Tomasz's remarks.

@@
 \usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-
+\renewcommand{\familydefault}{\sfdefault}
 \usepackage{graphicx} % Required for including images
@@
 \newcommand{\rr}{\mathbf{r}}
+
+\newcommand{\vm}[1]{\textcolor{red}{VM: #1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   % Title
-  	{\bf\textsc{On transfer learning using a MAC model variant}\vspace{0.2em}}
+  	{\bf\textsc{ On Transfer Learning using a MAC model variant}\vspace{0.2em}}
   % Authors
@@
 	\compresslist
-	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model (\textit{Hudson and Manning, ICLR 2018}), which achieves comparable accuracy while training \emph{\textbf{faster}}.
-	\item[$\bullet$] We evaluate both models on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
+	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
+	\item[$\bullet$] We evaluate the MAC model and the simplified variant on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
 	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can reduce a model's accuracy.
@@
 		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
-		\caption{The MAC cell ~\cite{hudson2018compositional}.}
+		\caption{The MAC cell, based on~\cite{hudson2018compositional}.}
 		\label{fig:mac_cell}
@@
 
-\headerbox{Simplified Mac Model (S-MAC)}{name=s-mac, column=0, below=mac-model}{
+\headerbox{Simplified MAC Model (S-MAC)}{name=s-mac, column=0, below=mac-model}{
 
-	Based on two heuristic simplifications:
+	The simplifications are based on two heuristics:
 
@@
 	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
-		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
+		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss. \vm{To reformulate?}
     \end{itemize}
@@
 		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
-		&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}
+		&\mem_i = W_{rm}^{[d \times 2d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}
 	\end{align*}
@@
 	{\begin{align*}
-		&I_{ihw} = m _{i-1} \odot k _{hw} \tag{r1} \\ 
+		&\\
+		&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ 
 		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
@@
 		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
-		&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
+		&\mem_i = W_{rm}^{[d \times d]} \rr_i + b_{rm}^{[d]} \tag{w1}
 	\end{align*}}
@@
 	\vspace{-15pt}
-	\begin{minipage}[H]{0.4\textwidth}
+	\null\hfill
+	\begin{minipage}[H]{0.3\textwidth}
 		\begin{figure}[H]
-			\includegraphics[width=0.4\textwidth]{../img/arxiv_paper_qr_code.png}
-			\vspace{-10pt}
-			\caption{Paper on arXiv.}
+			\includegraphics[width=0.6\textwidth]{../img/reproducible_research_qr_code.png}
+			\vspace{-15pt}
+			\caption*{\textbf{How to reproduce the experiments.}}
+			\label{fig:qr_repro_research}
+		\end{figure}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[H]{0.3\textwidth}
+		\begin{figure}[H]
+			\includegraphics[width=0.7\textwidth]{../img/arxiv_paper_qr_code.png}
+			\vspace{-15pt}
+			\caption*{Paper on arXiv.}
 			\label{fig:qr_arxiv}
@@
 	\hfill
-	\begin{minipage}[H]{0.4\textwidth}
+	\begin{minipage}[H]{0.3\textwidth}
 		\begin{figure}[H]
-			\includegraphics[width=0.4\textwidth]{../img/reproducible_research_qr_code.png}
-			\vspace{-10pt}
-			\caption{\textbf{How to reproduce the experiments.}}
-			\label{fig:qr_repro_research}
+			\includegraphics[width=0.7\textwidth]{../img/clevr_qr_code.png}
+			\vspace{-15pt}
+			\caption*{CLEVR Dataset.}
+			\label{fig:qr_clevr}
 		\end{figure}
 	\end{minipage}
+	\hfill\null
 }
@@
 		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
-		\caption{\textit{How many objects are either small cylinders or red things?}}
+		\caption{\textit{How many objects are either small cylinders or red things?} -- Answer: 5.}
 		\label{fig:clevr_task}
@@
 	\compresslist
-	\item[$\bullet$] Our experiments on \emph{zero-shot learning} show that both models have poor performance, in line with
+	\item[$\bullet$] Our experiments on \emph{zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) show that both models have poor performance, in line with
 	the other models in the literature.
@@
 	\item[$\bullet$] Finetuning CLEVR-trained models on CoGenT-A or -B hurts their generalization capabilities.
-	\item[$\rightarrow$] \emph{Zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) remains an interesting problem to solve.
+	\item[$\rightarrow$] \emph{Zero-shot learning} remains an interesting problem to solve.
 \end{itemize}
@@
 		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \textbf{gray cylinders} during training, but saw \textbf{gray cubes}.
-		\item[$\rightarrow$] Indicate that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
+		\item[$\rightarrow$] This indicates that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
 	\end{itemize}

### 2018-11-29 2018_nips_vigil_poster/main.tex
Rename Summary to Contributions.
Increased size of Fig. 3.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\headerbox{Summary}{name=summary,column=0,row=0}{
+\headerbox{Contributions}{name=contributions,column=0,row=0}{
 \begin{itemize}
@@
 
-\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=mac-model, column=0, below=summary}{
+\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=mac-model, column=0, below=contributions}{
 	\vspace{-10pt}
@@
 		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
-		\caption{\textit{How many objects are either small cylinders or red things?} -- Answer: 5.}
+		\caption{\textbf{Q}: \textit{How many objects are either small cylinders or red things?} -- \textbf{A}: 5.}
 		\label{fig:clevr_task}
@@
 	\begin{figure}[H]
-		\includegraphics[width=0.60\textwidth]{../img/fail_mac_cogent_b_shape.png}
+		\includegraphics[width=0.71\textwidth]{../img/fail_mac_cogent_b_shape.png}
 		\caption{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}

### 2018-11-29 2018_nips_vigil_poster/main.tex
Small precision.

@@
 \newcommand{\rr}{\mathbf{r}}
-
-\newcommand{\vm}[1]{\textcolor{red}{VM: #1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		\compresslist
-	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
-		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss. \vm{To reformulate?}
+	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no non-linear activation in-between) can be combined as one linear layer.
+		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
     \end{itemize}

### 2018-11-30 2018_nips_vigil_poster/main.tex
Emphasize some terms in the Summary.

@@
 	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
-	\item[$\bullet$] We evaluate the MAC model and the simplified variant on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
-	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can reduce a model's accuracy.
+	\item[$\bullet$] We evaluate the MAC model and the simplified variant on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a \emph{\textbf{15 point increase}} in accuracy, matching the state of the art.
+	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can \emph{\textbf{reduce a model's accuracy}}.
 

### 2019-01-02 arxiv/comparison.tex
Updated table accoriding to David comments, added acknowledgement section

@@
 		\midrule				
-		& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A ?    &  98.8   \\
+		& \multirow{5}{*}{A Train Full}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test Full    &  98.8   \\
 		\cmidrule{6-7} 
-		TbD + reg &   &    &   &    & B ?    &  75.4   \\
+		TbD + reg &   &    &   &    & B Test Full    &  75.4   \\
 		\cmidrule{4-5}\cmidrule{6-7}
-		(\cite{mascharka2018transparency}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A ?    &  96.9 \\
+		(\cite{mascharka2018transparency}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A Test Full    &  96.9 \\
 		\cmidrule{6-7} 
-		&   &    &   &    & B ?   &  96.3  \\
+		&   &    &   &    & B Test Full   &  96.3  \\
 
@@
 They also compare their performance on CoGenT against PG+EE.
-Nonetheless, the description lacks information about the used sets for training, fine-tuning and testing. 
+The authors (in a separate conversation) explained that they trained their models on Condition A training set and tested on Condition A and Condition B test sets respectively.
+For fine-tuning on CoGenT-B the authors used the first 3k images (Val-B indices 0-2999) in the CoGenT-B validation dataset and all of their corresponding questions.
+
 They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not explicitly point the set they used the samples from.

### 2019-08-29 2019_neurips_vigil/intro.tex
Venkatesh paper + restructurization of the paper

\section{Introduction}

Intro + related work

\subsection{Contributions}

\begin{itemize}
\item \textbf{Time aspect}:
\begin{itemize}
\item Learning the temporal association - grounding the time-related words with meaning
\item Learning the concept of time
\item time context being by-product of gates
\end{itemize}

\item Visual Grounding:
\begin{itemize}
\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
\item 
\end{itemize}
\item \textbf{Selective Attention Memory}:
\begin{itemize}
\item updating the memory content only with relevant visual information depending on the temporal context
\item content based and location based addressing for reading and writing
\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way

\end{itemize}
\end{itemize}

### 2019-08-29 2019_neurips_vigil/model.tex
Venkatesh paper + restructurization of the paper

\section{Model}

Selective Attention Memory Network (SAMNet)

### 2019-08-30 2019_neurips_vigil/appendix_model.tex

\section{Appendix}

\section{VWM model}

\begin{notation}
Treat 1D tensors as column vectors and 2D tensors as matrices, where appropriate.
We use lower case to represent both 1D and 2D tensors but occasionally use upper case
for 2D tensors where matrix operations are involved.

\begin{enumerate}
	\item Let 
	$\Delta^d = \{ (x_0, x_1, \dots, x_d) : x_0 + x_1 + \dots + x_d = 1, x_i \ge 0, i = 0, 1, \dots, d\}$ denote the standard $d$-simplex.

	\item  Let $\circ$ denote concatenation of two tensors with identical shape except possibly
	for their last dimensions $d_1$ and $d_2$, respectively,  
	resulting in a tensor with last dimension of $d_1+d_2$.

	\item Let $\odot$ denote  element-wise product of two tensors of same shape,
	i.e., Hadamard product for vectors/matrices.

	\item Let $\otimes$ denote tensor product of two tensors, 
	i.e. Kronecker product for vectors/matrices.
\end{enumerate}
\end{notation}

\section{Basic layers/modules}

\colorbx{Linear (Affine) Layer}

\begin{description}
	\item[Inputs:] A tensor $x$ with last dimension $n$.
	\item[Parameter:] An affine function $\cG: \Reals^n \to \Reals^m$ with 
	weight and bias parameters.

	\item[Output:] A tensor $y$ with last dimension $m$, and remaining dimensions
	same as that of $x$, obtained by applying $\cG$ to each 1D slice of $x$
	along the last dimension.
	\end{description}

\colorbx{Attention Module}

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Query: $q \in \Reals^d$
		\item Keys: $K \in \Reals^{N \times d}$	
		\item Values: $V \in \Reals^{N \times d}$. By default $V=K$, unless mentioned explicitly.	
	\end{enumerate}

	\item[Parameter:] Weight $w \in \Reals^d$

	\item[Outputs:] 
	\begin{enumerate}
		\item[]
		\item Content vector: $h =  V^{\T} u \in \Reals^d$
		\item Attention vector:  $w = \softmax(K(w \odot q)) \in \Reals^N$
	\end{enumerate}
\end{description}

\colorbx{Interaction Module}

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Base object: $b \in \Reals^d$
		\item Feature objects: $f \in \Reals^{M \times d}$	
	\end{enumerate}

	\item[Parameters:] 
	\begin{enumerate}
	\item[]
	\item Base object projection linear layer: $\cG: \Reals^d \to \Reals^d$
	\item Feature objects projection linear layer : $\cK: \Reals^{M \times d} \to \Reals^{M \times d}$
	\item Modifier linear layer:  $\cH: \Reals^{M \times 2d} \to \Reals^{M \times d}$	
\end{enumerate}

	\item[Output:] Modified feature objects 
	$f' =  \cH( \cK(f) \odot ( \vone \otimes \cG(b))) \in  \Reals^{M \times d}$
\end{description}

\hrulefill

\section{VWM cell}

The VWM recurrent cell is executed for $T$ reasoning steps for every frame in
the temporal order.  Within a single frame, the cell state at the end of each reasoning step 
$t=1,2, \dots, T$ is denoted by $(c_t, M_t, o_t)$, where: 
\begin{enumerate}
	\item $c_t \in \Reals^d$ is the control state;
	\item $M_t \in  \Reals^{N \times d}$ is the visual working memory with $N$ slots;
	\item $w_t \in  \Reals^N$ is the write head; and
	\item $so_t  \in \Reals^d$ is the summary visual object.
\end{enumerate} 
The initial state is such that both $c_0$ and $so_0$ are initialized
to a fixed value at the start of each frame. However $M_0$ is initialized only once at
the start of the first frame and otherwise taken to be the value of $M_T$ at the
end of the previous frame.

%The number of slots $N$ for the VWM $M_t$ is not fixed because the neural network 
%parameters do not depend on it. It can be variable across the different datasets used
%for training, validation and test as well as within each dataset. This, for example, enables a 
%form of transfer learning where we can train on an easy dataset for one value of $N$
%and study its generalization to a hard dataset using a larger value of $N$.

\colorbx{Question-driven Controller}

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Reasoning step $t = 1,2, \dots, T$
		\item Previous control state: $c_{t-1} \in \Reals^d$	
		\item Contextual words: $cw \in \Reals^{L \times d}$
		\item Question encoding: $q \in \Reals^d$
	\end{enumerate}

	\item[Parameters:] 
	\begin{enumerate}
		\item[]
		\item Reasoning step-dependent linear layer: $\cG_t: \Reals^d \to \Reals^d$, depending on $s$
		\item Concatenation linear layer: $\cH: \Reals^{2d} \to \Reals^d$
		\item Attention module $\cA$
		\item Temporal classifier:  $\cK: \Reals^d \to \Delta^3$. A two-layer feedforward
		network with ELU activation in the hidden layer of $d$ units.	
		The classes for the temporal context are labeled ``last'', ``latest'', ``now'', as well as 
		a fourth class label ``none`` indicating no temporal context.
		If $\tau \in \Delta^3$ is the output of the classifier, we denote the components by
		$\tlast$, $\tlatest$, $\tnow$ and $\tnone$.
	\end{enumerate}

	\item[Outputs:] 
	\begin{enumerate}
		\item[]
		\item Control state $c_t \in \Reals^d$
		\item Control attention $ca_t \in \Reals^L$
		\item Temporal class weights $\tau_t \in \Reals^4$
    \end{enumerate}

	\item[Equations:] 
	\begin{enumerate}
		\item[]
		\item Modulation: $y = \cH\bigl([c_{t-1}, \cG_t(q)]\bigr)$
		\item Control state and attention: $c_t,  ca_t= \cA(y, cw)$
		\item Temporal classification: $\tau_t = \cK(c_t)$
\end{enumerate}
\end{description}

\colorbx{Visual Retrieval Unit}

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Control state: $c_t \in \Reals^d$	
		\item Previous summary object: $so_{t-1} \in \Reals^d$
		\item Feature map of current frame: $F \in \Reals^{H \times W \times d}$
	\end{enumerate}

	\item[Parameters:] 
	\begin{enumerate}
		\item[]
		\item Interaction module $\cI$
		\item Attention module $\cA$
	\end{enumerate}

	\item[Outputs:] 
	\begin{enumerate}
		\item[]
		\item Visual object: $vo_t \in  \Reals^d$
		\item Visual attention: $va_t  \in \Reals^{H \times W \times d}$
	\end{enumerate}

	\item[Equations:]
	\begin{enumerate}
		\item[]
		\item Modified feature map: $\hat{F} = \cI(so_{t-1}, F)$
		\item Visual object and attention: $vo_t, va_t = \cA(y, \hat{F}, M_{t-1})$
	\end{enumerate}
\end{description}

\begin{note}
	Appropriate flatten/unflatten operations are performed to match the signature 
	of the modules.
\end{note}

\colorbx{Memory Retrieval Unit}

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Control state: $c_t \in \Reals^d$	
		\item Previous summary object: $so_{t-1} \in  \Reals^d$
		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
	\end{enumerate}

	\item[Parameters:] 
	\begin{enumerate}
		\item[]
		\item Interaction module $\cI$
		\item Attention module $\cA$
	\end{enumerate}

	\item[Outputs:] 
	\begin{enumerate}
		\item[]
		\item Memory object: $mo_t \in \Reals^d$
		\item Read head: $\rhead_t \in \Reals^N$
	\end{enumerate}

	\item[Equations:]
	\begin{enumerate}
		\item[]
		\item Modified VWM: $\hat{M}_t = \cI(so_{t-1}, M_{t-1})$
		\item Memory object and attention: $mo_t, \rhead_t = \cA(y, \hat{M}_t, M_{t-1})$
	\end{enumerate}
\end{description}

\colorbx{Reasoning Unit}

%control_state, visual_object, memory_object, temporal_class_weights

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Control state: $c_t \in \Reals^d$
		\item Visual object: $vo_t \in \Reals^d$
		\item Memory object: $mo_t \in \Reals^d$
		\item Temporal class weights $\tau \in \Delta^3$
	\end{enumerate}

	\item[Parameters:] Validator modules $\cG, \cK: \Reals^{2d} \to \Reals$.
	Both $\cG, \cK$ are two-layer networks of $2d$ hidden units,
	using ELU activation in the hidden layer, and sigmoid in the output layer.

	\item[Output:] Predicate gates for the current reasoning step
	\begin{enumerate}
    	\item Object match predicate gates (i) image: $\imatch_t \in [0,1]$ and 
    	(ii) memory: $\mmatch_t \in [0,1]$.

		\item Memory update predicate gates (i) add: $\doadd_t \in [0,1]$ and
		(ii) replace: $\doreplace_t \in [0,1]$
    \end{enumerate}

	\item[Equations:]
	\begin{enumerate}
		\item[]
		\item $\imatch_t \in [0,1]$:
		It's true if there is a valid visual object. This assumes that
		the current reasoning step refers to either ```now''  or ``latest''.

		\item$\mmatch_t \in [0,1]$:
		It's true if there is a valid memory object. This assumes that
		the current reasoning step refers to either ``last'',  or alternatively ``latest'' 
		but there is no matching visual object.

		\item $\doadd_t$:

		\item $\doreplace_t$: 
\end{enumerate}
\end{description}

\colorbx{Memory Update Unit}
% visual_object, visual_working_memory, read_head, write_head, do_replace, do_add_new

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Visual object: $vo_t \in \Reals^d$
		\item Memory object: $mo_t \in \Reals^d$
		\item Memory update predicate gates:  $\doadd_t, \doreplace_t \in [0,1]$
		\item Read head: $\rhead_t \in \Reals^N$
		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
		\item Previous write head: $\whead_{t-1} \in \Reals^N$
	\end{enumerate}

	\item[Outputs:] 
	\begin{enumerate}
		\item[]
		\item VWM $M_t \in \Reals^{N \times d}$
		\item Read head: $\rhead_t \in \Reals^N$
		\item Write head: $\whead_t \in \Reals^N$
	\end{enumerate}

\end{description}

\colorbx{Summary Object Update Unit}

\begin{description}
	\item[Inputs:] 
	\begin{enumerate}
		\item[]
		\item Previous summary object: $so_{t-1} \in \Reals^d$
		\item Visual object: $vo_t \in \Reals^d$
		\item Memory object: $mo_t \in \Reals^d$
		\item Object predicate gates: $\imatch_t, \mmatch_t \in [0,1]$
	\end{enumerate}

	\item[Parameters:] Concatenation linear layer $\cH$

	\item[Output:] 
     New summary object:
	             $so_t = \cH\bigl([so_{t-1}, (\imatch_t * vo_t + \mmatch_t * mo_t)]\bigr) \in \Reals^d$

\end{description}

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

\begin{figure}[b]
	\centering
	\includegraphics[width=\textwidth]{img/model}
	\caption{Testing}
	\label{fig:model}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{img/visualization}
	\caption{Testing}
	\label{fig:visualization}
\end{figure}

### 2019-09-05 2019_neurips_vigil/intro.tex
intro + bibiography

@@
 
-Intro + related work
+\begin{itemize}
+\item bAbI:  MemNets~\cite{weston2014memory} have access to the whole story at once
+\item the same goes to SoftPats~\cite{haurilet2019s} - they build graph per frame and then frame number is treated as one dimensions, so at the end the \textit{Traveler} can access all of them at the same time
+\item The paper~\cite{le2019learning} focuses on SVQA and TGIF-QA -  they access all frames at once, i.e.
+cut the video into clips, process each frame with CNNs and then aggregate feature representations of equal-size clips obtained by a temporal attention mechanism.
+So in fact the model has access to all frames all the time.
+\end{itemize}
+so the time aspect is really... not dealt with?
+
+Additionally, in~\cite{song2018explore} the authors introduced a large-scale dataset caled SVQA (Synthetic Video Question Answering) consisting of (Total QA pairs: 83160/11760/23760 and Total Videos 8400/1200/2400).
+As "using all frames is time-consuming.
+Thus we divide each video into clips (segments) of 16 frames, with 80\% overlap between successive clips (segments)" and "We extract feature from each clip and aggregate features of all clips from one video to form a sequential video representation." -- which means that they identified the problem that you "cannot extract features from all frames" at the beginning and pass that to the model.
+But instead of proposing a solution that will deal with the video on per-frame basis, they "cheated".
+;)
+
+IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie}, so there is no need for cutting video into cuts etc.
 

### 2019-09-11 2019_neurips_vigil/experiments.tex
experiments section first draft

\section{Experiments}

Our experiments were intended to study SAMNET's performances as well as generalizations abilities in different settings. For this purpose, we use two different versions of the COG data set, an easy one (canonical) and a hard version to explore two different level of difficulties. The canonical setting represents 4 frames input sequences, a maximum memory duration of 3, and only one distractor object per frame. Whereas the hard setting has 8 frames, a maximum memory duration of 7 and 10 distractors. We compare our model to the original COG model.

\underline {Hard dataset}:

Our first goal is to improve the accuracy on the hard data set. In order to do this, we have tried different approaches.

The first approach is to train a model on the hard version only and test it on the hard version. We achieve a test accuracy of … which represent a major improvement from the COG model score.

The second approach is to see if we can generalize from easy to hard setting. We train a model on the canonical data set and test it on the hard data set. Doing so we can achieve comparable results than the first approach. It shows that SAMNET has good generalizations abilities. It can adapt well to different sequence lengths and number of distractors.

Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard data set. We can observe a significant improvement from 91.6\%  to 96.5\%  which represent the state of the art accuracy for the hard setting (classification tasks).

\underline {Canonical dataset}:

For the canonical setting, we also could achieve a small improvement in accuracy, from 97.6\% for the COG model to 98\% for SAMNET.

\underline {Hard tasks}:

We can also notice a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor. Those two tasks represent a higher level of difficulties due to the number of objects to be remembered in order to answer the question correctly.
We could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard data set.
We see that the external memory plays an important role in remembering objects from the past and this affects the test scores significantly.

\begin{table}[t]
	\tiny

	\centering
	\begin{tabular}{ccccccccccc}
		\toprule
		Model & & SAMNET & && &&& COG& \\
		\cmidrule{2-5} \cmidrule{7-11} 
		&&&&&& ours & paper & ours & ours & paper\\
		\cmidrule{7-9} \cmidrule{10-11}
		Trained on       & canonical & canonical & canonical & hard &            & canonical &  canonical  & canonical  & canonical & hard \\ 
		Fine tuned on  & - & - & hard  & - &           &- & -   & - & hard & - \\ 
		Tested on        & canonical & hard & hard & hard &           & canonical  &  canonical  & hard & hard & hard  \\ 
		\midrule

		Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 96.7 & 97.6  & 65.9 & running& 80.1 \\

		\midrule

		AndCompareColor	&	93.5		&	82.7	&	89.2	&&	&	79.0	&81.9	&53.1&&	51.4
\\ 
		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	77.5&	80.0	&57.1	&&50.7\\ 
		AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&&	99.0	&99.7&	53.4&&	78.2\\ 
		AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	99.3&	100.0	&56.7&&	77.9\\ 
		CompareColor	&	98.1		&	89.3	&	95.9	&&	&	98.4	&99.2&	56.1&&	50.1\\ 
		CompareShape	&	98.0	&		89.7	&	95.9	&&&	98.9	&99.4	&66.8	&&50.5
\\ 
		Exist	&	100.0	&		99.7	&	99.8		&&	&99.90&	100.0&	63.5&&	99.3\\ 
		ExistColor	&	100.0		&	99.6	&	99.9	&&	&	97.6&	99.0&	70.9&&	89.8\\ 
		ExistColorOf	&	99.9	&		95.5	&	99.7		& &&	98.9 &	99.7&	51.5&&	73.1\\ 
		ExistColorSpace	&94.1		&	88.8	&	91.0	&&	&	97.9&	98.9	&72.8	&&89.2\\ 
		ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&	&	95.6	&100.0	&65.0&&	50.4
\\ 
		ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	93.3&	98.0&	77.5	&&60.2\\ 
		ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	96.9&	100.0&	87.8&&	50.3\\ 
		ExistShape	&	100.0	&	99.5	&	100.0	&&&	98.4&	100.0&	77.1	&&92.5\\ 
		ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&		99.6	&100.0	&52.7&&89.8\\ 
		ExistSpace	&	95.3	&	89.7	&	93.2	&&		&98.5&	98.9	&71.1	&&92.8\\ 
		GetColor	&	100.0		&	95.8&	99.9	&&&	99.70&	100.0&	71.4&&	97.9\\ 
		GetColorSpace	&	98.0		&	90.0	&	95.0&	&&		97.8&	98.2	&71.8&&	92.3\\ 
		GetShape	&	100.0		&	97.3&	99.9&	&	&	99.5&	100.0  &83.5&&	97.1
\\ 
		GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	96.8&	98.1  &78.7	&&	90.3\\ 
		SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	99.8&	100.0 & 67.7&&	99.3\\ 
		SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	99.7&	100.0&	64.2&&	99.3	  \\

		\bottomrule
	\end{tabular}
	\label{results}
\end{table}

### 2019-09-11 2019_neurips_vigil/intro.tex
work on intro, proposition of new title

@@
 \section{Introduction}
+
+In recent years there has been substantial progress in sys-tems  that  can  find  factual  answers  in  text,  starting  withIBM’s Watson system~\cite{ferrucci2010building}
+
+, and now withhigh-performing neural systems that can answer short ques-tions provided they are given a text that contains the answer(e.g., Seo et al., 2016; Wang et al., 2018).
+
+AI  has  achieved  remarkable  mastery  over  games  such  asChess, Go, and Poker, and evenJeopardy!, but the rich variety of standardized exams has remained a landmark chal-lenge.
+Even  in  2016,  the  best  AI  system  achieved  merely 59.3\% on an 8th Grade science exam challenge (Schoenicket al., 2016).
+
+Playing Atari Games~\cite{mnih2015human}
+
+Despite several successes across many domains Deep learning~\cite{lecun2015deep} still struggles with
+
+learning algoritms
+learning reasoning~\cite{graves2016hybrid}
+
+visual reasoning~\cite{mogadala2019trends} - datasets such as COG~\cite{yang2018dataset} and 
+SVQA (Synthetic Video Question Answering)~\cite{song2018explore}
+
+ARISTO project~\cite{clark2019f} - based on RoBERTa~\cite{liu2019roberta} contextual word embeddings
+
+transformer-based solutions~\cite{vaswani2017attention} using self-attention
+
+“The current neural network approaches will find it difficult to determine which combinations of ‘later’, ‘earlier’, ‘more’, and ‘less’ constitute ‘increase’ and which constitute ‘decrease,'” Davis says.
+“Neural networks have no inherent idea of magnitude or of time.”
+~\cite{davis2016write}
+
+Visual Dialog~\cite{das2017visual} - the same, they keep the whole history of the dialog in memory
 
@@
 
-IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie}, so there is no need for cutting video into cuts etc.
+IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie/number of distractionts}, so there is no need for cutting video into cuts etc.
 

### 2019-09-11 2019_neurips_vigil/experiments.tex
experiments section + update bib

@@
 
-Our experiments were intended to study SAMNET's performances as well as generalizations abilities in different settings.
+Our experiments were intended to study SAMNet's performances as well as generalization abilities in different settings.
 For this purpose, we use two different versions of the COG data set, an easy one (canonical) and a hard version to explore two different level of difficulties.
@@
 Whereas the hard setting has 8 frames, a maximum memory duration of 7 and 10 distractors.
-We compare our model to the original COG model.
+We compare our model to the original COG model~\cite{cog2018}
 
@@
 
-The first approach is to train a model on the hard version only and test it on the hard version. We achieve a test accuracy of … which represent a major improvement from the COG model score.
+The first approach is to train a model on the hard train set only and test it on the test set.
+It is the same approach used by the original COG paper ~\cite{cog2018} to evaluate performance on the hard data set.
+We achieve a test accuracy of … which represents a major improvement from the COG model score.
 
@@
 Doing so we can achieve comparable results than the first approach.
-It shows that SAMNET has good generalizations abilities.
+It shows that SAMNet has good generalizations abilities.
 It can adapt well to different sequence lengths and number of distractors.
@@
 Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard data set.
-We can observe a significant improvement from 91.6\%  to 96.5\%  which represent the state of the art accuracy for the hard setting (classification tasks).
+Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represent the state of the art accuracy for the hard setting (classification tasks).
+After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy from the first approach.
 
@@
 We could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard data set.
-We see that the external memory plays an important role in remembering objects from the past and this affects the test scores significantly.
+We see that the SAMNet's external memory plays an important role in remembering objects from the past and this affects the test scores significantly.
 
@@
 
+	\caption{COG test set accuracies for  SAMNet \& COG models.
+For the COG section, the results marked as 'paper' comes from the original COG paper ~\cite{cog2018}, wheras the results marked as 'ours' come from our own experiments using the following implementation: https://github.com/google/cog }
+
 	\centering
@@
 		\toprule
-		Model & & SAMNET & && &&& COG& \\
+		Model & & SAMNet & && &&& COG& \\
 		\cmidrule{2-5} \cmidrule{7-11} 

### 2019-09-12 2019_neurips_vigil/intro.tex
added some additional references to intro

@@
 
-, and now withhigh-performing neural systems that can answer short ques-tions provided they are given a text that contains the answer(e.g., Seo et al., 2016; Wang et al., 2018).
+, and now with high-performing neural systems that can answer short ques-tions provided they are given a text that contains the answer e.g.~\cite{wang2018glue}
 
@@
 
+\cite{levesque2012winograd}
+
 visual reasoning~\cite{mogadala2019trends} - datasets such as COG~\cite{yang2018dataset} and 
@@
 ~\cite{davis2016write}
+
+bAbI~\cite{weston2015towards}
 

### 2019-09-12 2019_neurips_vigil/experiments.tex

@@
 
-The first approach is to train a model on the hard train set only and test it on the test set.
+The first approach is to train a model on the hard train set only and test it on the hard test set.
 It is the same approach used by the original COG paper ~\cite{cog2018} to evaluate performance on the hard data set.
@@
 Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represent the state of the art accuracy for the hard setting (classification tasks).
-After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy from the first approach.
+After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy obtained in the first approach.
 

### 2019-09-12 2019_neurips_vigil/intro.tex
fluid intelligence

@@
 \section{Introduction}
+
+Fluid Intelligence:
+
+IQ may be viewed as a composite comprising multiple elements: In many theories of intelligence, a distinction is made between fluid and crystallized intelligence (8).
+Fluid intelligence comprises the set of abilities involved in coping with novel environments and especially in abstract reasoning; crystallized intelligence is the product of the application of these processes.
+Fluid intelligence is often measured by tests such as figural analogy, classification, and matrix problems, whereas crystallized intelligence is measured by tests of vocabulary and general information (9).
+~\cite{sternberg2008increasing}
+
+Cognitively, gF is thought to be related to metacognition6(knowing about and reflecting upon one’s own ongoing mentalprocesses) and to working memory4,5,7–9(the active maintenanceof domain-specific information plus domain-general attention-al or ‘executive’ control of ongoing processing).
+One componentof attentional control is the ability to overcome interference thatwould otherwise disrupt performance by compromising taskgoals or information held active in working memory.
+Individualdifferences in gF are most pronounced in behavioral measureswhen attentional control is required4,8,10.
+For this reason, gF isthought to be related to attentional control specifically~\cite{gray2003neural}
 
@@
 
-\cite{levesque2012winograd}
+Wingrad Scheme challenge~\cite{levesque2012winograd}
 

### 2019-09-12 2019_neurips_vigil/experiments.tex
experiment section revisited

@@
 Our experiments were intended to study SAMNet's performances as well as generalization abilities in different settings.
-For this purpose, we use two different versions of the COG data set, an easy one (canonical) and a hard version to explore two different level of difficulties.
-The canonical setting represents 4 frames input sequences, a maximum memory duration of 3, and only one distractor object per frame.
-Whereas the hard setting has 8 frames, a maximum memory duration of 7 and 10 distractors.
-We compare our model to the original COG model~\cite{cog2018}
+For this purpose, we use two different versions of the COG dataset, an easy one (canonical) and a hard version to explore a wide range of difficulties.
+The following parameters control the difficulty level: the number of frames in the input sequence, the maximum memory duration (how far is the last object to be remembered), and the number of distractors.
+These parameters are detailed in Table 1 for each setting.
+The table also shows the size of the training/validation/test split used for our experiments.
+The COG dataset is composed of 44 tasks that have equal number of samples.
+We compare our model SAMNet's to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
+We also use the exact same training parameters detailed in the original paper.
 
-\underline {Hard dataset}:
+On the other side we trained SAMNet using IBM's Mi-Prometheus, a framework based on Pytorch.
+We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
+We trained  SAMNet for 6 epochs using 8 reasoning steps SAMCells and a hidden state size of 128.
+The external memory has 128-bit slots.
 
-Our first goal is to improve the accuracy on the hard data set. In order to do this, we have tried different approaches.
+\begin{table}[!t]
+	\centering
+	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
+	\begin{tabular}{ccc}
+		\toprule
+		Dataset       &    Canonical setting   & Hard setting   \\
 
-The first approach is to train a model on the hard train set only and test it on the hard test set.
-It is the same approach used by the original COG paper ~\cite{cog2018} to evaluate performance on the hard data set.
-We achieve a test accuracy of … which represents a major improvement from the COG model score.
+		\midrule
+
+		number of frames      &    4  &  8      \\
+
+		\midrule
+
+		maximum memory duration      &    3   & 7      \\
+
+		\midrule
+
+		number of distractors     &    1   & 10    \\
+
+		\midrule
+
+		size of training set    &    10000320  & 10000320      \\
+
+		\midrule
+
+		size of validation/test set    &    500016   & 500016      \\
+
+		\midrule
+
+		tasks per family  training set   &    227280  & 227280    \\
+
+		\midrule
+
+		tasks per family  validation/test set   &    11364   & 11364      \\
+
+	   \bottomrule
+
+	\end{tabular}
+
+	\label{tab:parameters}
+\end{table}
+
+\subsection{Training and testing Methodology}
+
+First we evaluate SAMNet's performance on the canonical setting and compare it with the COG Model.
+As shown in Table 2 we could achieve a small improvement in accuracy, from 97.6\% for the COG model to 98\% for SAMNet.
+
+Our second goal is to improve the accuracy on the hard dataset. In order to do this, we have tried three different approaches.
+
+The first approach is to train a model on the hard training set only and test it on the hard test set.
+It is the same approach used by the original COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset.
+We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 2).
+It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more objects to remember.
 
 The second approach is to see if we can generalize from easy to hard setting.
-We train a model on the canonical data set and test it on the hard data set.
+We train a model on the canonical dataset and test it on the hard dataset.
 Doing so we can achieve comparable results than the first approach.
@@
 After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy obtained in the first approach.
-
-\underline {Canonical dataset}:
-
-For the canonical setting, we also could achieve a small improvement in accuracy, from 97.6\% for the COG model to 98\% for SAMNET.
-
-\underline {Hard tasks}:
+We note that the third approach is two time faster than the first one and more effective.
 
 We can also notice a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor.
-Those two tasks represent a higher level of difficulties due to the number of objects to be remembered in order to answer the question correctly.
-We could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard data set.
+Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
+As we can see in Table 2 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
 We see that the SAMNet's external memory plays an important role in remembering objects from the past and this affects the test scores significantly.
+
+\subsection{Results}
 
@@
 	\caption{COG test set accuracies for  SAMNet \& COG models.
-For the COG section, the results marked as 'paper' comes from the original COG paper ~\cite{cog2018}, wheras the results marked as 'ours' come from our own experiments using the following implementation: https://github.com/google/cog }
+For the COG section, the results marked as 'paper' comes from the original COG paper ~\cite{yang2018dataset}, whereas the results marked as 'ours' come from our own experiments using the following implementation: https://github.com/google/cog }
 

### 2019-09-12 2019_neurips_vigil/experiments.tex
minor clean up

@@
 
-On the other side we trained SAMNet using IBM's Mi-Prometheus, a framework based on Pytorch.
+On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018acceleratingo}, a framework for research based on Pytorch.
 We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
@@
 We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 2).
-It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more objects to remember.
+It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.
 
-The second approach is to see if we can generalize from easy to hard setting.
+The second approach is to see if we can generalize from the easy to the hard setting.
 We train a model on the canonical dataset and test it on the hard dataset.
@@
 
-Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard data set.
-Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represent the state of the art accuracy for the hard setting (classification tasks).
+Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard dataset.
+Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represents the state of the art accuracy for the hard setting (classification tasks).
 After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy obtained in the first approach.

### 2019-09-13 2019_neurips_vigil/model.tex
model first words

@@
 
-Selective Attention Memory Network (SAMNet)
+Selective Attention Memory Network (SAMNet) is a end-to-end differentiable model made for video reasoning.
+It is a model based on attention mechanisms but also on a Selective Attention Memory which is able to store selected entities.
+This memory enables SAMNet to reason across multiple frames and perform spatio-temporal reasoning.
+The core of SAMNet is based a recurrent cell called SAMCell.
+By aligning together a series of k SAMCells, the network can perform k reasoning steps.
+At every reasoning step the attention on the image and the question is updated.
+This section describes the model and the different units that composed a SAMCell.
+They are called the Question-driven Controller, the Visual Retrievial Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
+The model is also composed of an Image Encoder and a Question Encoder both responsible to pre-process the visual and textual inputs. The output unit is a classifier.
+All those modules are described below.
+
+\subsection{Question-driven Controller}
+\subsection{Visual Retrievial Unit}
+\subsection{Reasoning unit}
+\subsection{Memory update}
+\subsection{Summary Object Udpate Unit}
+\subsection{Question Encoder}
+\subsection{Image Encoder}
+\subsection{Output Unit}

### 2019-09-13 2019_neurips_vigil/model.tex
Update model.tex

@@
 This section describes the model and the different units that composed a SAMCell.
-They are called the Question-driven Controller, the Visual Retrievial Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
+They are called the Question-driven Controller, the Visual Retrievial unit, the Memory Retrieval unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate unit.
 The model is also composed of an Image Encoder and a Question Encoder both responsible to pre-process the visual and textual inputs. The output unit is a classifier.
@@
 \subsection{Visual Retrievial Unit}
-\subsection{Reasoning unit}
-\subsection{Memory update}
+\subsection{Reasoning Unit}
+\subsection{Memory update Unit}
 \subsection{Summary Object Udpate Unit}

### 2019-09-13 2019_neurips_vigil/model.tex

--- 2019-09-13 2019_neurips_vigil/model.tex
@@
 The core of SAMNet is based a recurrent cell called SAMCell.
-By aligning together a series of k SAMCells, the network can perform k reasoning steps.
-At every reasoning step the attention on the image and the question is updated.
+By aligning together a series of k SAMCells per frame, the network can perform k reasoning steps over a frame.
+At every new frame, a new series of k SAMCells is initiated.
+The SAMCell can read and write to memory at every frame using a content addressable mechanism.
 This section describes the model and the different units that composed a SAMCell.

### 2019-09-13 2019_neurips_vigil/model.tex
visual retrievial unit + memory retrievial unit

@@
 \subsection{Visual Retrievial Unit}
+
+The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
+It is first projecting the past summary object and the feature maps together using the interaction module.
+It is then using the attention module as follow.
+The query are the control states and the keys and are the feature maps coming from the image encoder.
+The results of this attention is applied on the modified features maps coming from the interaction module.
+This unit outputs the extracted object and the visual attention.
+
+\subsection{Memory Retrievial Unit}
+
+The role of the memory retrievial unit is to read and extract object from memory (Selective AttentionMemory).
+As the Visual Retrievial Unit, it uses a combination of two following submodules.
+The interaction module responsible to blend the extracted object and the content of the memory.
+The attention module then extract the corresponding object in memory if present.
+
 \subsection{Reasoning Unit}
@@
 \subsection{Summary Object Udpate Unit}
-\subsection{Question Encoder}
-\subsection{Image Encoder}
-\subsection{Output Unit}
+
+The image encoder, question encoder and output unit are described in the appendix.

### 2019-09-13 2019_neurips_vigil/model.tex
Question driven controller first draft

@@
 This section describes the model and the different units that composed a SAMCell.
-They are called the Question-driven Controller, the Visual Retrievial Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
+They are called the Question-driven Controller, the Visual Retrieval Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
 The model is also composed of an Image Encoder and a Question Encoder both responsible to pre-process the visual and textual inputs. The output unit is a classifier.
@@
 \subsection{Question-driven Controller}
-\subsection{Visual Retrievial Unit}
+
+The Question-driven Controller plays an important role in the reasoning process.
+it drives the attention over the question and produces the new control states.
+Each new control state defines a new reasoning operation.
+The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit).
+It uses the dot product attention between the contextual words
+and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
+
+This unit also output the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words. (last,latest,now, none temporal)
+
+\subsection{Visual Retrieval Unit}
 
@@
 
-\subsection{Memory Retrievial Unit}
+\subsection{Memory Retrieval Unit}
 

### 2019-09-13 2019_neurips_vigil/experiments.tex
minor clean up
change subsection title
new plot

@@
 The COG dataset is composed of 44 tasks that have equal number of samples.
-We compare our model SAMNet's to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
+We chose to focus our effort only on the the 22 classification tasks.
+We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
 We also use the exact same training parameters detailed in the original paper.
 
-On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018acceleratingo}, a framework for research based on Pytorch.
+On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
 We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
-We trained  SAMNet for 6 epochs using 8 reasoning steps SAMCells and a hidden state size of 128.
+We trained  SAMNet using 8 reasoning steps SAMCells and a hidden state size of 128.
 The external memory has 128-bit slots.
+We trained our model until convergence but we also have set a training time limit of 80 hours.
 
@@
 
-\subsection{Results}
+\begin{figure}
+	\centering
+	\caption{This plot compares SAMNet and COG on their abilities to generalize from the canonical to the hard dataset.
+We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical,fine tuned on hard, tested on hard }
+
+\begin{tikzpicture}
+
+\tiny
+
+\begin{axis}[
+ybar,
+enlargelimits=0.15,
+legend style={at={(0.5,-0.15)},
+	anchor=north,legend columns=-1},
+ylabel={COG test accuracy in \% },
+symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
+xtick=data,
+nodes near coords,
+nodes near coords align={vertical},
+]
+\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
+\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
+\legend{SAMNet ,COG Model}
+\end{axis}
+\end{tikzpicture}
+\end{figure}
 
@@
 		\toprule
-		Model & & SAMNet & && &&& COG& \\
+		Model & & SAMNet & && && COG&& \\
 		\cmidrule{2-5} \cmidrule{7-11} 
-		&&&&&& ours & paper & ours & ours & paper\\
+		&&&&& & paper & ours & ours & paper&\\
 		\cmidrule{7-9} \cmidrule{10-11}
-		Trained on       & canonical & canonical & canonical & hard &            & canonical &  canonical  & canonical  & canonical & hard \\ 
-		Fine tuned on  & - & - & hard  & - &           &- & -   & - & hard & - \\ 
-		Tested on        & canonical & hard & hard & hard &           & canonical  &  canonical  & hard & hard & hard  \\ 
+		Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
+		Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
+		Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
 		\midrule
 
-		Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 96.7 & 97.6  & 65.9 & running& 80.1 \\
+		Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & running& 80.1 \\
 
@@
 
-		AndCompareColor	&	93.5		&	82.7	&	89.2	&&	&	79.0	&81.9	&53.1&&	51.4
+		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&53.1&&	51.4
 \\ 
-		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	77.5&	80.0	&57.1	&&50.7\\ 
-		AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&&	99.0	&99.7&	53.4&&	78.2\\ 
-		AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	99.3&	100.0	&56.7&&	77.9\\ 
-		CompareColor	&	98.1		&	89.3	&	95.9	&&	&	98.4	&99.2&	56.1&&	50.1\\ 
-		CompareShape	&	98.0	&		89.7	&	95.9	&&&	98.9	&99.4	&66.8	&&50.5
+		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&57.1	&&50.7\\ 
+		AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&&	78.2\\ 
+		AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	100.0	&56.7&&	77.9\\ 
+		CompareColor	&	98.1		&	89.3	&	95.9	&&		&99.2&	56.1&&	50.1\\ 
+		CompareShape	&	98.0	&		89.7	&	95.9	&&	&99.4	&66.8	&&50.5
 \\ 
-		Exist	&	100.0	&		99.7	&	99.8		&&	&99.90&	100.0&	63.5&&	99.3\\ 
-		ExistColor	&	100.0		&	99.6	&	99.9	&&	&	97.6&	99.0&	70.9&&	89.8\\ 
-		ExistColorOf	&	99.9	&		95.5	&	99.7		& &&	98.9 &	99.7&	51.5&&	73.1\\ 
-		ExistColorSpace	&94.1		&	88.8	&	91.0	&&	&	97.9&	98.9	&72.8	&&89.2\\ 
-		ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&	&	95.6	&100.0	&65.0&&	50.4
+		Exist	&	100.0	&		99.7	&	99.8		&&	&	100.0&	63.5&&	99.3\\ 
+		ExistColor	&	100.0		&	99.6	&	99.9	&&	&	99.0&	70.9&&	89.8\\ 
+		ExistColorOf	&	99.9	&		95.5	&	99.7		& & &	99.7&	51.5&&	73.1\\ 
+		ExistColorSpace	&94.1		&	88.8	&	91.0	&& &	98.9	&72.8	&&89.2\\ 
+		ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&		&100.0	&65.0&&	50.4
 \\ 
-		ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	93.3&	98.0&	77.5	&&60.2\\ 
-		ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	96.9&	100.0&	87.8&&	50.3\\ 
-		ExistShape	&	100.0	&	99.5	&	100.0	&&&	98.4&	100.0&	77.1	&&92.5\\ 
-		ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&		99.6	&100.0	&52.7&&89.8\\ 
-		ExistSpace	&	95.3	&	89.7	&	93.2	&&		&98.5&	98.9	&71.1	&&92.8\\ 
-		GetColor	&	100.0		&	95.8&	99.9	&&&	99.70&	100.0&	71.4&&	97.9\\ 
-		GetColorSpace	&	98.0		&	90.0	&	95.0&	&&		97.8&	98.2	&71.8&&	92.3\\ 
-		GetShape	&	100.0		&	97.3&	99.9&	&	&	99.5&	100.0  &83.5&&	97.1
+		ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	98.0&	77.5	&&60.2\\ 
+		ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	100.0&	87.8&&	50.3\\ 
+		ExistShape	&	100.0	&	99.5	&	100.0	&&&	100.0&	77.1	&&92.5\\ 
+		ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&100.0	&52.7&&89.8\\ 
+		ExistSpace	&	95.3	&	89.7	&	93.2	&&		&	98.9	&71.1	&&92.8\\ 
+		GetColor	&	100.0		&	95.8&	99.9	&& &	100.0&	71.4&&	97.9\\ 
+		GetColorSpace	&	98.0		&	90.0	&	95.0&	& &	98.2	&71.8&&	92.3\\ 
+		GetShape	&	100.0		&	97.3&	99.9&	&	&	100.0  &83.5&&	97.1
 \\ 
-		GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	96.8&	98.1  &78.7	&&	90.3\\ 
-		SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	99.8&	100.0 & 67.7&&	99.3\\ 
-		SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	99.7&	100.0&	64.2&&	99.3	  \\
+		GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	98.1  &78.7	&&	90.3\\ 
+		SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	100.0 & 67.7&&	99.3\\ 
+		SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	100.0&	64.2&&	99.3	  \\
 

### 2019-09-13 2019_neurips_vigil/intro.tex

--- 2019-09-11 2019_neurips_vigil/intro.tex
@@
 
-In recent years there has been substantial progress in sys-tems  that  can  find  factual  answers  in  text,  starting  withIBM’s Watson system~\cite{ferrucci2010building}
+Integration of vision and language in deep neural network models allows learning joint representations of objects, concepts, and relations.
+In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{}.
 
-, and now withhigh-performing neural systems that can answer short ques-tions provided they are given a text that contains the answer(e.g., Seo et al., 2016; Wang et al., 2018).
+Starting with the VQA dataset \cite{}, many tasks have emerged in the past several years\cite{mogadala2019trends}.
+Since the conception of the VQA benchmark, visual reasoning is the main emphasis in these tasks, which can be expressed in language.
+Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.
+In contrast to VQA, which comes with static image and question pairs, an emerging field is Video QA \cite{} that introduced the temporal aspect in the visual input.
+Video input provides another opportunity to test system's ability to deal with temporal relations and reasoning.
+As evident from human cognition, attention and memory are the key components that are required to solve these problems, which need to process spatial and temporal information.
 
-AI  has  achieved  remarkable  mastery  over  games  such  asChess, Go, and Poker, and evenJeopardy!, but the rich variety of standardized exams has remained a landmark chal-lenge.
+The ability to deal with time is also challenge for natural language processing (NLP), for example in question answering (QA) systems and in dialog.
+The current QA solutions, in certain problem settings, can work around this challenge by processing the whole text input and reason over the text using attention or other mechanisms.
+For example the Memory Networks \cite{weston2015towards}, solves the bAbI reasoning task by processing all the facts at once, which reside in memory and available to provide answers.
+Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.
+In real-time dialog or video QA, there may not be such opportunity or the system may be forced to record the whole history which is not always feasible.
+Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore}, TGIF-QA, and COG \cite{yang2018dataset}
+and 
+Humans have the ability to selectively pay attention and store important items or events in memory based on their goals.
+Working memory and episodic memory systems are responsible for this remarkable ability.
+
+%Fluid Intelligence:
+%
+%IQ may be viewed as a composite comprising multiple elements: In many theories of intelligence, a distinction is made between fluid and crystallized intelligence (8).
+Fluid intelligence comprises the set of abilities involved in coping with novel environments and especially in abstract reasoning; crystallized intelligence is the product of the application of these processes.
+Fluid intelligence is often measured by tests such as figural analogy, classification, and matrix problems, whereas crystallized intelligence is measured by tests of vocabulary and general information (9).
+%~\cite{sternberg2008increasing}
+%
+%Cognitively, gF is thought to be related to metacognition6(knowing about and reflecting upon one’s own ongoing mentalprocesses) and to working memory4,5,7–9(the active maintenanceof domain-specific information plus domain-general attention-al or ‘executive’ control of ongoing processing).
+One componentof attentional control is the ability to overcome interference thatwould otherwise disrupt performance by compromising taskgoals or information held active in working memory.
+Individualdifferences in gF are most pronounced in behavioral measureswhen attentional control is required4,8,10.
+For this reason, gF isthought to be related to attentional control specifically~\cite{gray2003neural}
+
+%In recent years there has been substantial progress in systems  that  can  find  factual  answers  in  text,  starting  with IBM’s Watson system~\cite{ferrucci2010building}, and now with high-performing neural systems that can answer short questions provided they are given a text that contains the answer e.g.~\cite{wang2018glue}
+%
+%
+%AI  has  achieved  remarkable  mastery  over  games  such  asChess, Go, and Poker, and evenJeopardy!, but the rich variety of standardized exams has remained a landmark chal-lenge.
 Even  in  2016,  the  best  AI  system  achieved  merely 59.3\% on an 8th Grade science exam challenge (Schoenicket al., 2016).
-
-Playing Atari Games~\cite{mnih2015human}
-
-Despite several successes across many domains Deep learning~\cite{lecun2015deep} still struggles with
-
-learning algoritms
-learning reasoning~\cite{graves2016hybrid}
+%
+%Playing Atari Games~\cite{mnih2015human}
+%
+%
+%Despite several successes across many domains Deep learning~\cite{lecun2015deep} still struggles with
+%
+%learning algoritms
+%learning reasoning~\cite{graves2016hybrid}
+%
+%
+%Wingrad Scheme challenge~\cite{levesque2012winograd}
 
@@
 ~\cite{davis2016write}
-
-Visual Dialog~\cite{das2017visual} - the same, they keep the whole history of the dialog in memory
 

### 2019-09-14 2019_neurips_vigil/intro.tex

@@
 Integration of vision and language in deep neural network models allows learning joint representations of objects, concepts, and relations.
-In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{}.
+In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.
 
@@
 
-The ability to deal with time is also challenge for natural language processing (NLP), for example in question answering (QA) systems and in dialog.
-The current QA solutions, in certain problem settings, can work around this challenge by processing the whole text input and reason over the text using attention or other mechanisms.
-For example the Memory Networks \cite{weston2015towards}, solves the bAbI reasoning task by processing all the facts at once, which reside in memory and available to provide answers.
+The ability to deal with time is a challenge also for natural language processing (NLP), for example in question answering (QA) systems and in dialog applications.
+The current NLP solutions, in certain problem settings, can work around this challenge by processing the entire text input and reason over it using attention \cite{vaswani2017attention} or other mechanisms.
+For example, Memory Networks \cite{weston2015towards}, solves the bAbI reasoning task by processing the supporting facts all at once, which reside in memory and available to provide answers.
 Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.
 In real-time dialog or video QA, there may not be such opportunity or the system may be forced to record the whole history which is not always feasible.
-Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore}, TGIF-QA, and COG \cite{yang2018dataset}
-and 
+Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG \cite{yang2018dataset} have limited number of frames (e.g.
+4-16 frames), and therefore manageable by the neural net models to process and represent all of the visual information.
+According to\cite{song2018explore} the authors extracted visual features from each clip and aggregated features of all clips from one video to form a sequential video representation.
+These solutions may demonstrate high accuracy and apply to specific problems, however, generalization to arbitrary length video sequences will be problematic.
+Such approaches also differ from the human cognitive strategies.
 Humans have the ability to selectively pay attention and store important items or events in memory based on their goals.
@@
 
-visual reasoning~\cite{mogadala2019trends} - datasets such as COG~\cite{yang2018dataset} and 
-SVQA (Synthetic Video Question Answering)~\cite{song2018explore}
+%visual reasoning~\cite{mogadala2019trends} - datasets such as COG~\cite{yang2018dataset} and 
+%SVQA (Synthetic Video Question Answering)~\cite{song2018explore}
+%
+%
+%ARISTO project~\cite{clark2019f} - based on RoBERTa~\cite{liu2019roberta} contextual word embeddings
+%
+%transformer-based solutions~\cite{vaswani2017attention} using self-attention
+%
+%
+%“The current neural network approaches will find it difficult to determine which combinations of ‘later’, ‘earlier’, ‘more’, and ‘less’ constitute ‘increase’ and which constitute ‘decrease,'” Davis says.
+“Neural networks have no inherent idea of magnitude or of time.”
+%~\cite{davis2016write}
 
-ARISTO project~\cite{clark2019f} - based on RoBERTa~\cite{liu2019roberta} contextual word embeddings
-
-transformer-based solutions~\cite{vaswani2017attention} using self-attention
-
-“The current neural network approaches will find it difficult to determine which combinations of ‘later’, ‘earlier’, ‘more’, and ‘less’ constitute ‘increase’ and which constitute ‘decrease,'” Davis says.
-“Neural networks have no inherent idea of magnitude or of time.”
-~\cite{davis2016write}
-
-\begin{itemize}
-\item bAbI:  MemNets~\cite{weston2014memory} have access to the whole story at once
-\item the same goes to SoftPats~\cite{haurilet2019s} - they build graph per frame and then frame number is treated as one dimensions, so at the end the \textit{Traveler} can access all of them at the same time
-\item The paper~\cite{le2019learning} focuses on SVQA and TGIF-QA -  they access all frames at once, i.e.
+%\begin{itemize}
+%\item bAbI:  MemNets~\cite{weston2014memory} have access to the whole story at once
+%\item the same goes to SoftPats~\cite{haurilet2019s} - they build graph per frame and then frame number is treated as one dimensions, so at the end the \textit{Traveler} can access all of them at the same time
+%\item The paper~\cite{le2019learning} focuses on SVQA and TGIF-QA -  they access all frames at once, i.e.
 cut the video into clips, process each frame with CNNs and then aggregate feature representations of equal-size clips obtained by a temporal attention mechanism.
 So in fact the model has access to all frames all the time.
-\end{itemize}
-so the time aspect is really... not dealt with?
-
-Additionally, in~\cite{song2018explore} the authors introduced a large-scale dataset caled SVQA (Synthetic Video Question Answering) consisting of (Total QA pairs: 83160/11760/23760 and Total Videos 8400/1200/2400).
-As "using all frames is time-consuming.
+%\end{itemize}
+%so the time aspect is really... not dealt with?
+%
+%Additionally, in~\cite{song2018explore} the authors introduced a large-scale dataset caled SVQA (Synthetic Video Question Answering) consisting of (Total QA pairs: 83160/11760/23760 and Total Videos 8400/1200/2400).
+%As "using all frames is time-consuming.
 Thus we divide each video into clips (segments) of 16 frames, with 80\% overlap between successive clips (segments)" and "We extract feature from each clip and aggregate features of all clips from one video to form a sequential video representation." -- which means that they identified the problem that you "cannot extract features from all frames" at the beginning and pass that to the model.
@@
 ;)
-
-IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie/number of distractionts}, so there is no need for cutting video into cuts etc.
+%
+%IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie/number of distractionts}, so there is no need for cutting video into cuts etc.
 

### 2019-09-14 2019_neurips_vigil/model.tex
Question driven controller first draft

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{../img/architecture/samnet_architecture}
+	\caption{}
+	\label{fig:samnetarchitecture}
+\end{figure}
+
 \subsection{Question-driven Controller}
@@
 The Question-driven Controller plays an important role in the reasoning process.
-it drives the attention over the question and produces the new control states.
+It drives the attention over the question and produces the new control states.
 Each new control state defines a new reasoning operation.
@@
 
-This unit also output the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words. (last,latest,now, none temporal)
+This unit also output the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words. (last, latest, now, none temporal)
 
@@
 
-The role of the memory retrievial unit is to read and extract object from memory (Selective AttentionMemory).
-As the Visual Retrievial Unit, it uses a combination of two following submodules.
+The role of the memory retrieval unit is to read and extract object from memory (Selective Attention Memory).
+As the Visual Retrieval Unit, it uses a combination of two following submodules.
 The interaction module responsible to blend the extracted object and the content of the memory.
@@
 \subsection{Reasoning Unit}
+
 \subsection{Memory update Unit}
-\subsection{Summary Object Udpate Unit}
+
+This unit is meant to update the content of the memory. It is controlled by two booleans that decides if the object needs to be added to a new position, or replaced somewhere. 
+It also updated the position of the write head.
+If a new object as been added to the current write head position, the right head shifts right to a new empty slot.
+If the object has been replaced, the write head doesn't move.
+
+\subsection{Summary Object  Unit}
+
+The goal of the Summary Object
 

### 2019-09-14 2019_neurips_vigil/intro.tex
intro

@@
 
-Integration of vision and language in deep neural network models allows learning joint representations of objects, concepts, and relations.
-In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.
+Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
+Potentially, this approach can address Harnad's "symbol grounding problem" \cite{harnad2003symbol} and lead to visually grounded language learning.
+%In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.
 
-Starting with the VQA dataset \cite{}, many tasks have emerged in the past several years\cite{mogadala2019trends}.
-Since the conception of the VQA benchmark, visual reasoning is the main emphasis in these tasks, which can be expressed in language.
+Starting with the Visual Question Answering (VQA) dataset \cite{}, many tasks that integrate vision and language have emerged in the past several years\cite{mogadala2019trends}.
+As a departure from the simpler vision tasks like classification and object detection, visual reasoning has become the core emphasis in these tasks.
 Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.
-In contrast to VQA, which comes with static image and question pairs, an emerging field is Video QA \cite{} that introduced the temporal aspect in the visual input.
-Video input provides another opportunity to test system's ability to deal with temporal relations and reasoning.
-As evident from human cognition, attention and memory are the key components that are required to solve these problems, which need to process spatial and temporal information.
 
-The ability to deal with time is a challenge also for natural language processing (NLP), for example in question answering (QA) systems and in dialog applications.
-The current NLP solutions, in certain problem settings, can work around this challenge by processing the entire text input and reason over it using attention \cite{vaswani2017attention} or other mechanisms.
-For example, Memory Networks \cite{weston2015towards}, solves the bAbI reasoning task by processing the supporting facts all at once, which reside in memory and available to provide answers.
+In contrast to VQA, which comes with static image and question pairs, another emerging direction is Video QA \cite{}, which introduces the aspect of time.
+In addition to spatial reasoning, video input provides an opportunity to work on temporal relations and reasoning.
+As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
+
+The ability to deal with time can pose a challenge for natural language processing (NLP) as well; for instance, in question answering (QA) and dialog applications.
+The current NLP solutions, in certain problem settings, can work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
+For example, solutions to the bAbI reasoning task (e.g.
+Memory Networks \cite{weston2015towards}), typically involve processing the supporting facts all at once, which reside in memory and available to provide answers.
 Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.
-In real-time dialog or video QA, there may not be such opportunity or the system may be forced to record the whole history which is not always feasible.
+In real-time dialog or video QA, there may not be such an opportunity to have the question and entire input all at once in the beginning.
+
 Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG \cite{yang2018dataset} have limited number of frames (e.g.
 4-16 frames), and therefore manageable by the neural net models to process and represent all of the visual information.
-According to\cite{song2018explore} the authors extracted visual features from each clip and aggregated features of all clips from one video to form a sequential video representation.
-These solutions may demonstrate high accuracy and apply to specific problems, however, generalization to arbitrary length video sequences will be problematic.
+As an example, according to\cite{song2018explore} the authors extracted visual features from each frame and aggregated features of all clips from one video to form a sequential video representation.
+These solutions may demonstrate high accuracy, however, generalization to arbitrary length video sequences will be problematic.
 Such approaches also differ from the human cognitive strategies.
-Humans have the ability to selectively pay attention and store important items or events in memory based on their goals.
+Humans have the ability to selectively pay attention and store salient items or events in memory based on their goals.
 Working memory and episodic memory systems are responsible for this remarkable ability.
@@
 \subsection{Contributions}
-
-\begin{itemize}
-\item \textbf{Time aspect}:
+This work have attempted to address the issues mentioned above and propose a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.
+We have tested this model on the COG dataset \cite{yang2018dataset} and compared to the baseline results.
+Our results indicate that the model is capable of:
+%\begin{itemize}
+%\item \textbf{Time aspect}:
 \begin{itemize}
 \item Learning the temporal association - grounding the time-related words with meaning
-\item Learning the concept of time
-\item time context being by-product of gates
-\end{itemize}
+%\item Learning the concept of time
+%\item time context being by-product of gates
+%\end{itemize}
 
-\item Visual Grounding:
-\begin{itemize}
-\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
-\item 
-\end{itemize}
-\item \textbf{Selective Attention Memory}:
-\begin{itemize}
-\item updating the memory content only with relevant visual information depending on the temporal context
-\item content based and location based addressing for reading and writing
-\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way
+\item Learning complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes
+%\begin{itemize}
+%\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
+\item Selectively control the flow of information to and from the memory to answer questions
+%\end{itemize}
+%\item \textbf{Selective Attention Memory}:
+%\begin{itemize}
+\item Updating the memory content only with relevant visual information depending on the temporal context
+%\item content based and location based addressing for reading and writing
+%\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way
 
 \end{itemize}
-\end{itemize}
+%\end{itemize}

### 2019-09-14 2019_neurips_vigil/intro.tex
intro

@@
 
-Starting with the Visual Question Answering (VQA) dataset \cite{}, many tasks that integrate vision and language have emerged in the past several years\cite{mogadala2019trends}.
-As a departure from the simpler vision tasks like classification and object detection, visual reasoning has become the core emphasis in these tasks.
+Starting with the Visual Question Answering (VQA) dataset \cite{}, a variety of tasks that integrate vision and language have emerged in the past several years\cite{mogadala2019trends}.
+As a departure from the simpler vision problems like classification and object detection, visual reasoning has become the core emphasis in these tasks.
 Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.

### 2019-09-14 2019_neurips_vigil/experiments.tex
cleaning model section

@@
 
-\begin{figure}
-	\centering
-	\caption{This plot compares SAMNet and COG on their abilities to generalize from the canonical to the hard dataset.
-We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical,fine tuned on hard, tested on hard }
-
-\begin{tikzpicture}
-
-\tiny
-
-\begin{axis}[
-ybar,
-enlargelimits=0.15,
-legend style={at={(0.5,-0.15)},
-	anchor=north,legend columns=-1},
-ylabel={COG test accuracy in \% },
-symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
-xtick=data,
-nodes near coords,
-nodes near coords align={vertical},
-]
-\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
-\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
-\legend{SAMNet ,COG Model}
-\end{axis}
-\end{tikzpicture}
-\end{figure}
-
 \begin{table}[t]
@@
 \end{table}
+
+\begin{figure}
+	\centering
+	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset.
+We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard.
+}
+
+	\begin{tikzpicture}
+
+	\tiny
+
+	\begin{axis}[
+	ybar,
+	enlargelimits=0.15,
+	legend style={at={(0.5,-0.15)},
+		anchor=north,legend columns=-1},
+	ylabel={COG test accuracy in \% },
+	symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
+	xtick=data,
+	nodes near coords,
+	nodes near coords align={vertical},
+	]
+	\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
+	\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
+	\legend{SAMNet ,COG Model}
+	\end{axis}
+	\end{tikzpicture}
+\end{figure}

### 2019-09-14 2019_neurips_vigil/model.tex
cleaning model section

@@
 
-The role of the memory retrieval unit is to read and extract object from memory (Selective Attention Memory).
-As the Visual Retrieval Unit, it uses a combination of two following submodules.
-The interaction module responsible to blend the extracted object and the content of the memory.
+The role of the memory retrieval unit is to read and extract object from memory).
+As the Visual Retrieval Unit, it uses the combination of the two following submodules.
+The interaction module blends together the extracted object and the content of the memory.
 The attention module then extract the corresponding object in memory if present.
+This unit outputs the extracted object and its corresponding location, we call it the "read head".
 
@@
 
-This unit is meant to update the content of the memory. It is controlled by two booleans that decides if the object needs to be added to a new position, or replaced somewhere. 
-It also updated the position of the write head.
+This unit is meant to update the content of the memory.
+
+Three actions can happen:
+
+\begin{itemize}
+	\item There is no object to be added to memory, the memory remains unchanged
+	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
+
+	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
+\end{itemize}
+
+This module also updates the position of the write head.
 If a new object as been added to the current write head position, the right head shifts right to a new empty slot.

### 2019-09-14 2019_neurips_vigil/model.tex
summary output unit

@@
 
-This unit also output the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words. (last, latest, now, none temporal)
+This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
 
@@
 
-\subsection{Summary Object  Unit}
+\subsection{Summary  Unit}
 
-The goal of the Summary Object
+The  Summary Unit is the last unit of the SAMCell.
+It is responsible to output the new summary object.
+It first picks which object is relevant between the object extracted from memory and the visual object extracted from the image.
+Once the relevant object is picked, it is combined with the former summary object through a linear layer to become the new summary object.
+It is the final step of the SAMCell reasoning cycle.
 

### 2019-09-15 2019_neurips_vigil/appendix_model.tex
Fixed errors
results
new table size

@@
 
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=\textwidth]{img/model}
-	\caption{Testing}
+\begin{figure}
+	\includegraphics[width=\textwidth]{img/model2}
 	\label{fig:model}
@@
 
-\begin{figure}[ht]
+\begin{figure}
+	\includegraphics[width=\textwidth]{img/image}
+	\label{fig:model}
+\end{figure}
+
+\colorbx{Image Encoder}
+
+\colorbx{Question Encoder}
+
+\colorbx{Output Unit}
+
+\section{Results}
+
+\begin{table}[t]
+	\tiny
+
+	\caption{COG test set accuracies for  SAMNet \& COG models.
+For the COG section, the results marked as 'paper' comes from the original COG paper ~\cite{yang2018dataset}, whereas the results marked as 'ours' come from our own experiments using the following implementation: https://github.com/google/cog }
+
 	\centering
-	\includegraphics[width=\textwidth]{img/visualization}
-	\caption{Testing}
-	\label{fig:visualization}
-\end{figure}
+	\begin{tabular}{ccccccccccc}
+		\toprule
+		Model & & SAMNet & && && COG&& \\
+		\cmidrule{2-5} \cmidrule{7-11} 
+		&&&&& & paper & ours & ours & paper&\\
+		\cmidrule{7-9} \cmidrule{10-11}
+		Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
+		Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
+		Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
+		\midrule
+
+		Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & running& 80.1 \\
+
+		\midrule
+
+		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&53.1&&	51.4
+		\\ 
+		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&57.1	&&50.7\\ 
+		AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&&	78.2\\ 
+		AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	100.0	&56.7&&	77.9\\ 
+		CompareColor	&	98.1		&	89.3	&	95.9	&&		&99.2&	56.1&&	50.1\\ 
+		CompareShape	&	98.0	&		89.7	&	95.9	&&	&99.4	&66.8	&&50.5
+		\\ 
+		Exist	&	100.0	&		99.7	&	99.8		&&	&	100.0&	63.5&&	99.3\\ 
+		ExistColor	&	100.0		&	99.6	&	99.9	&&	&	99.0&	70.9&&	89.8\\ 
+		ExistColorOf	&	99.9	&		95.5	&	99.7		& & &	99.7&	51.5&&	73.1\\ 
+		ExistColorSpace	&94.1		&	88.8	&	91.0	&& &	98.9	&72.8	&&89.2\\ 
+		ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&		&100.0	&65.0&&	50.4
+		\\ 
+		ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	98.0&	77.5	&&60.2\\ 
+		ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	100.0&	87.8&&	50.3\\ 
+		ExistShape	&	100.0	&	99.5	&	100.0	&&&	100.0&	77.1	&&92.5\\ 
+		ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&100.0	&52.7&&89.8\\ 
+		ExistSpace	&	95.3	&	89.7	&	93.2	&&		&	98.9	&71.1	&&92.8\\ 
+		GetColor	&	100.0		&	95.8&	99.9	&& &	100.0&	71.4&&	97.9\\ 
+		GetColorSpace	&	98.0		&	90.0	&	95.0&	& &	98.2	&71.8&&	92.3\\ 
+		GetShape	&	100.0		&	97.3&	99.9&	&	&	100.0  &83.5&&	97.1
+		\\ 
+		GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	98.1  &78.7	&&	90.3\\ 
+		SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	100.0 & 67.7&&	99.3\\ 
+		SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	100.0&	64.2&&	99.3	  \\
+
+		\bottomrule
+	\end{tabular}
+	\label{results}
+\end{table}

### 2019-09-15 2019_neurips_vigil/experiments.tex
new table size

@@
 		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&57.1	&&50.7\\
-		AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&&	78.2\\ 
-		AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	100.0	&56.7&&	77.9\\ 
-		CompareColor	&	98.1		&	89.3	&	95.9	&&		&99.2&	56.1&&	50.1\\ 
-		CompareShape	&	98.0	&		89.7	&	95.9	&&	&99.4	&66.8	&&50.5
-\\ 
-		Exist	&	100.0	&		99.7	&	99.8		&&	&	100.0&	63.5&&	99.3\\ 
-		ExistColor	&	100.0		&	99.6	&	99.9	&&	&	99.0&	70.9&&	89.8\\ 
-		ExistColorOf	&	99.9	&		95.5	&	99.7		& & &	99.7&	51.5&&	73.1\\ 
-		ExistColorSpace	&94.1		&	88.8	&	91.0	&& &	98.9	&72.8	&&89.2\\ 
-		ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&		&100.0	&65.0&&	50.4
-\\ 
-		ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	98.0&	77.5	&&60.2\\ 
-		ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	100.0&	87.8&&	50.3\\ 
-		ExistShape	&	100.0	&	99.5	&	100.0	&&&	100.0&	77.1	&&92.5\\ 
-		ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&100.0	&52.7&&89.8\\ 
-		ExistSpace	&	95.3	&	89.7	&	93.2	&&		&	98.9	&71.1	&&92.8\\ 
-		GetColor	&	100.0		&	95.8&	99.9	&& &	100.0&	71.4&&	97.9\\ 
-		GetColorSpace	&	98.0		&	90.0	&	95.0&	& &	98.2	&71.8&&	92.3\\ 
-		GetShape	&	100.0		&	97.3&	99.9&	&	&	100.0  &83.5&&	97.1
-\\ 
-		GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	98.1  &78.7	&&	90.3\\ 
-		SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	100.0 & 67.7&&	99.3\\ 
-		SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	100.0&	64.2&&	99.3	  \\
 

### 2019-09-15 2019_neurips_vigil/intro.tex
intro

@@
 \subsection{Contributions}
-This work have attempted to address the issues mentioned above and propose a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.
-We have tested this model on the COG dataset \cite{yang2018dataset} and compared to the baseline results.
-Our results indicate that the model is capable of:
+This work introduces a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.
+Our results based on the COG dataset \cite{yang2018dataset} indicate that the model is capable of:
 %\begin{itemize}

### 2019-09-16 2019_neurips_vigil/model.tex
SAM Cell reasoning + supporting figures
samnet architecture v4
Model section

@@
-\section{Model}
+\section{Selective Attention Memory Network (SAMNet)}
 
-Selective Attention Memory Network (SAMNet) is a end-to-end differentiable model made for video reasoning.
+\begin{figure}[!b]
+\begin{minipage}{0.43\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
+\end{minipage}\hfill
+\begin{minipage}{0.55\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+\end{minipage}\hfill
+\caption{General architecture of SAMNet (left) and a single reasoning step in SAMCell (right)}
+\label{fig:samnet}
+\end{figure}
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
+	\caption{General architecture of SAMNet}
+	\label{fig:samneta}
+\end{figure}
+
+\begin{figure}[!b]
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+	\caption{Single reasoning step in SAMCell}
+	\label{fig:samneta}
+\end{figure}
+
+%Selective Attention Memory Network (SAMNet) is a end-to-end differentiable model made for video reasoning.
 It is a model based on attention mechanisms but also on a Selective Attention Memory which is able to store selected entities.
 This memory enables SAMNet to reason across multiple frames and perform spatio-temporal reasoning.
-The core of SAMNet is based a recurrent cell called SAMCell.
+%The core of SAMNet is based a recurrent cell called SAMCell.
 By aligning together a series of k SAMCells per frame, the network can perform k reasoning steps over a frame.
@@
 They are called the Question-driven Controller, the Visual Retrieval Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
+%The model is also composed of an Image Encoder and a Question Encoder both responsible to pre-process the visual and textual inputs. The output unit is a classifier.
+%All those modules are described below.
+
+SAMNet is a recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
+The memory is used to store relevant objects representing contextual information about words in text and feature vectors in video frames. The memory 
+can be accessed through either content-addressing, via dot-product attention, or location-based addressing. 
+Coupled with gating mechanisms to be described later, this enables correct objects to be retrieved 
+in order to perform spatio-temporal reasoning on frames and text. Each address of the memory stores
+a $d$-dimensional vector, where $d$ is a global parameter.
+SAMNet is end-to-end differentiable including its memory update procedures. 
+%A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
+%testing to fit the characteristics of data.
+
+The core of SAMNet is a recurrent cell called SAMCell (\cref{fig:samnet}). 
+By aligning together a new series of $k$ SAMCells per frame, the network can perform $k$ 
+reasoning steps over each frame; the only flow of information between frames is through the external memory. 
+For $t=1,2, \dots, k$, SAMCell maintains the following information as part of its recurrent state:
+(a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
+(b) $so_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
+Let $M_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
+Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
+in a trained model, $\whead_t$ points to the location of first empty slot in memory for adding new objects.
+
+This section describes the model and the different units that composed a SAMCell.
+They are called the Question-driven Controller, the Visual Retrieval Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
 The model is also composed of an Image Encoder and a Question Encoder both responsible to pre-process the visual and textual inputs. The output unit is a classifier.
 All those modules are described below.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{../img/architecture/samnet_architecture}
-	\caption{}
-	\label{fig:samnetarchitecture}
-\end{figure}
 

### 2019-09-16 2019_neurips_vigil/model.tex

@@
 
-\begin{figure}[!b]
-\begin{minipage}{0.43\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
-\end{minipage}\hfill
-\begin{minipage}{0.55\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
-\end{minipage}\hfill
-\caption{General architecture of SAMNet (left) and a single reasoning step in SAMCell (right)}
-\label{fig:samnet}
-\end{figure}
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
-	\caption{General architecture of SAMNet}
-	\label{fig:samneta}
-\end{figure}
-
-\begin{figure}[!b]
-	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
-	\caption{Single reasoning step in SAMCell}
-	\label{fig:samneta}
-\end{figure}
+%\begin{figure}[!b]
+%\begin{minipage}{0.43\textwidth}
+%	\centering
+%	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
+%\end{minipage}\hfill
+%\begin{minipage}{0.55\textwidth}
+%	\centering
+%	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+%\end{minipage}\hfill
+%\caption{General architecture of SAMNet (left) and a single reasoning step in SAMCell (right)}
+%\label{fig:samnet}
+%\end{figure}
 
@@
 
-SAMNet is a recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
-The memory is used to store relevant objects representing contextual information about words in text and feature vectors in video frames. The memory 
-can be accessed through either content-addressing, via dot-product attention, or location-based addressing. 
+\begin{figure}[hbtp]
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
+	\caption{General architecture of SAMNet}
+	\label{fig:samnet}
+\end{figure}
+
+SAMNet is an end-to-end differentiable recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
+The memory is used to store relevant objects representing contextual information about words in text and visual objects in video frames. 
+Each address of the memory stores a $d$-dimensional vector, where $d$ is a global parameter.
+The memory  can be accessed through either content-addressing, via dot-product attention, or location-based addressing. 
 Coupled with gating mechanisms to be described later, this enables correct objects to be retrieved 
-in order to perform spatio-temporal reasoning on frames and text. Each address of the memory stores
-a $d$-dimensional vector, where $d$ is a global parameter.
-SAMNet is end-to-end differentiable including its memory update procedures. 
+in order to perform spatio-temporal reasoning on frames and text. 
 %A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
@@
 
-The core of SAMNet is a recurrent cell called SAMCell (\cref{fig:samnet}). 
+\begin{figure}[hbtp]
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+	\caption{Single reasoning step in SAMCell}
+	\label{fig:samcell}
+\end{figure}
+
+The core of SAMNet is a recurrent cell called SAMCell (\cref{fig:samcell}). 
 By aligning together a new series of $k$ SAMCells per frame, the network can perform $k$ 
-reasoning steps over each frame; the only flow of information between frames is through the external memory. 
-For $t=1,2, \dots, k$, SAMCell maintains the following information as part of its recurrent state:
+reasoning steps over each frame, with information flowing between frames through the external memory. 
+While processing a single frame, for $t=1,2, \dots, k$, SAMCell maintains the following information as part of its recurrent state:
 (a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and

### 2019-09-16 2019_neurips_vigil/appendix_model.tex
training details to appendix

@@
 
+\section{Training and Implementation Details}
+
+SAMNet is implemented on IBM's Mi-Prometheus~\cite{kornuta2018accelerating} framework based on Pytorch. 
+We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
+SAMNet was trained using 8 reasoning steps and a hidden state size of 128.
+The external memory has 128-bit slots for all experiments.
+We trained our model until convergence but we also have set a training time limit of 80 hours.
+
 \section{Results}
@@
 
+	\resizebox{\textwidth}{!}{
 	\centering
@@
 
-		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&53.1&&	51.4
+		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1&&	51.4
 		\\ 
-		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&57.1	&&50.7\\ 
+		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&&50.7\\ 
 		AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&&	78.2\\ 
@@
 	\end{tabular}
+}
+
 	\label{results}

### 2019-09-16 2019_neurips_vigil/experiments.tex
table 1, 2 3
training details to appendix

@@
 
-Our experiments were intended to study SAMNet's performances as well as generalization abilities in different settings.
+We evaluated SAMNet on the COG dataset and compared our results to the baseline model described in ~\cite{yang2018dataset}.
+To test the generalization ability of both models, we used the canonical (easy) and hard settings that alter the number of distractors and sequence length.
+Since there was no baseline for these tests (train on canonical, test on hard), we ran our own experiments using the COG model provided by the authors.
+SAMNet achieves the highest overall scores for all categories of experiments (Table 2), especially for the tests run on the hard dataset.
+Among the 22 classification tasks, we highlighted the two most difficult tasks that affect the overall score.
+More detailed results are provided in the Appendix.
+
+We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence.
+The mechanisms introduced in SAMCell (e.g., Memory retrieval and update units) learn to operate independent of the total number of frames and allow to generalize to longer video lengths.
+The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
+Therefore, the memory is updated efficiently instead of storing all information across all frames.
+
+%Our experiments were intended to study SAMNet's performances as well as generalization abilities in different settings.
 For this purpose, we use two different versions of the COG dataset, an easy one (canonical) and a hard version to explore a wide range of difficulties.
@@
 The COG dataset is composed of 44 tasks that have equal number of samples.
-We chose to focus our effort only on the the 22 classification tasks.
-We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
+%We chose to focus our effort only on the the 22 classification tasks.
+%We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
 We also use the exact same training parameters detailed in the original paper.
-
-On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
+%
+%On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
 We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
@@
 	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
-	\begin{tabular}{ccc}
+	\resizebox{\textwidth}{!}{
+
+	\begin{tabular}{ccccccc}
 		\toprule
-		Dataset       &    Canonical setting   & Hard setting   \\
 
+		Dataset    &  	number of frames  &  	maximum memory duration & number of distractors & size of training set & size of validation/test set    \\ 
           \midrule
 
-		number of frames      &    4  &  8      \\
-
+		 Canonical setting & 4 & 3 & 1 & 10000320 & 500016 &   \\
 		 \midrule
 
-		maximum memory duration      &    3   & 7      \\
-
-		\midrule
-
-		number of distractors     &    1   & 10    \\
-
-		\midrule
-
-		size of training set    &    10000320  & 10000320      \\
-
-		\midrule
-
-		size of validation/test set    &    500016   & 500016      \\
-
-		\midrule
-
-		tasks per family  training set   &    227280  & 227280    \\
-
-		\midrule
-
-		tasks per family  validation/test set   &    11364   & 11364      \\
-
+		 Hard  setting & 8 & 7& 10 & 10000320 & 500016  \\
 		 \bottomrule
@@
 	\end{tabular}
+}
 
@@
 
-First we evaluate SAMNet's performance on the canonical setting and compare it with the COG Model.
+We compared our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores provided by the authors through personal communications.
+We used the same training parameters detailed in the original paper and reproduced their results.
+For the generalization experiments from canonical to hard, we used the verified model and obtained new results that were not reported in the reference paper.
+In Table 2 COG section shows 4 columns divided into two parts: "paper" and "ours" which distinguish between the results reported in the paper vs.
+our own experiments.
+
+Our experiments focused on the 22 classification tasks provided by the COG dataset.
+First we evaluated SAMNet's performance on the canonical setting and compared it with the COG Model.
 As shown in Table 2 we could achieve a small improvement in accuracy, from 97.6\% for the COG model to 98\% for SAMNet.
+Next we focused on the hard setting of the dataset which increases the number of distractors from 1 to 10 and the number of frames from 4 to 8.
 
-Our second goal is to improve the accuracy on the hard dataset. In order to do this, we have tried three different approaches.
+The first approach was to train a model on the hard training set, and test it on the hard test set.
+This is the same approach used by the COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset.
+We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 2).
+%It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.
 
-The first approach is to train a model on the hard training set only and test it on the hard test set.
-It is the same approach used by the original COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset.
-We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 2).
-It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.
+The second approach was to see if the models can generalize from the easy to the hard setting.
+For this experiment, we trained a model on the canonical dataset, and directly tested on the hard dataset.
+This experiment highlighted the most significant difference between SAMNet and the baseline COG model.
 
-The second approach is to see if we can generalize from the easy to the hard setting.
-We train a model on the canonical dataset and test it on the hard dataset.
-Doing so we can achieve comparable results than the first approach.
-It shows that SAMNet has good generalizations abilities.
-It can adapt well to different sequence lengths and number of distractors.
+Finally we trained a model on the canonical data set, fine-tuned it on the hard data set using only 25k iterations, and tested on the hard dataset.
+Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represents the state of the art accuracy for the hard setting (classification tasks).
+After a short fine-tuning process, the transferred model could generalize well to harder tasks and even surpass the accuracy obtained in the first approach.
+We note that the third approach is also twice faster than the first one, and it is more effective in terms of accuracy.
 
-Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard dataset.
-Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represents the state of the art accuracy for the hard setting (classification tasks).
-After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy obtained in the first approach.
-We note that the third approach is two time faster than the first one and more effective.
-
-We can also notice a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor.
+A more granular analysis of accuracy per task shows a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor.
 Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
 As we can see in Table 2 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
-We see that the SAMNet's external memory plays an important role in remembering objects from the past and this affects the test scores significantly.
+The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
+The training and implementation details are in appendix.
 
 \begin{table}[t]
-	\tiny
 
@@
 	\centering
+	\resizebox{\textwidth}{!}{
 	\begin{tabular}{ccccccccccc}
@@
 
-		Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & running& 80.1 \\
+		Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & & 80.1 \\
 
@@
 
-		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&53.1&&	51.4
+		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1&  &	51.4
 \\ 
-		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&57.1	&&50.7\\
+		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	& &50.7\\
 
@@
 	\end{tabular}
+}
 	\label{results}
@@
 }
+	\resizebox{6cm}{3.5cm}{%
 
@@
 	\end{tikzpicture}
+}
 \end{figure}

### 2019-09-16 2019_neurips_vigil/appendix_model.tex
move models subsections to appendix

@@
 
+The Question-driven Controller plays an important role in the reasoning process.
+It drives the attention over the question and produces the new control states.
+Each new control state defines a new reasoning operation.
+The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit).
+It uses the dot product attention between the contextual words
+and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
+
+This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
+
 \begin{description}
@@
 
+The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
+It is first projecting the past summary object and the feature maps together using the interaction module.
+It is then using the attention module as follow.
+The query are the control states and the keys and are the feature maps coming from the image encoder.
+The results of this attention is applied on the modified features maps coming from the interaction module.
+This unit outputs the extracted object and the visual attention.
+
 \begin{description}
@@
 \colorbx{Memory Retrieval Unit}
+
+The role of the memory retrieval unit is to read and extract object from memory).
+As the Visual Retrieval Unit, it uses the combination of the two following submodules.
+The interaction module blends together the extracted object and the content of the memory.
+The attention module then extract the corresponding object in memory if present.
+This unit outputs the extracted object and its corresponding location, we call it the "read head".
 
@@
 \colorbx{Memory Update Unit}
+
+This unit is meant to update the content of the memory.
+
+Three actions can happen:
+
+\begin{itemize}
+	\item There is no object to be added to memory, the memory remains unchanged
+	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
+
+	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
+\end{itemize}
+
+This module also updates the position of the write head.
+If a new object as been added to the current write head position, the right head shifts right to a new empty slot.
+If the object has been replaced, the write head doesn't move.
 % visual_object, visual_working_memory, read_head, write_head, do_replace, do_add_new
@@
 \colorbx{Summary Object Update Unit}
+
+The  Summary Unit is the last unit of the SAMCell.
+It is responsible to output the new summary object.
+It first picks which object is relevant between the object extracted from memory and the visual object extracted from the image.
+Once the relevant object is picked, it is combined with the former summary object through a linear layer to become the new summary object.
+It is the final step of the SAMCell reasoning cycle.
+
+The image encoder, question encoder and output unit are described in the appendix.
 

### 2019-09-16 2019_neurips_vigil/model.tex
move models subsections to appendix

@@
 
-\subsection{Question-driven Controller}
-
-The Question-driven Controller plays an important role in the reasoning process.
-It drives the attention over the question and produces the new control states.
-Each new control state defines a new reasoning operation.
-The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit).
-It uses the dot product attention between the contextual words
-and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
-
-This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
-
-\subsection{Visual Retrieval Unit}
-
-The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
-It is first projecting the past summary object and the feature maps together using the interaction module.
-It is then using the attention module as follow.
-The query are the control states and the keys and are the feature maps coming from the image encoder.
-The results of this attention is applied on the modified features maps coming from the interaction module.
-This unit outputs the extracted object and the visual attention.
-
-\subsection{Memory Retrieval Unit}
-
-The role of the memory retrieval unit is to read and extract object from memory).
-As the Visual Retrieval Unit, it uses the combination of the two following submodules.
-The interaction module blends together the extracted object and the content of the memory.
-The attention module then extract the corresponding object in memory if present.
-This unit outputs the extracted object and its corresponding location, we call it the "read head".
-
-\subsection{Reasoning Unit}
-
-\subsection{Memory update Unit}
-
-This unit is meant to update the content of the memory.
-
-Three actions can happen:
-
-\begin{itemize}
-	\item There is no object to be added to memory, the memory remains unchanged
-	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
-
-	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
-\end{itemize}
-
-This module also updates the position of the write head.
-If a new object as been added to the current write head position, the right head shifts right to a new empty slot.
-If the object has been replaced, the write head doesn't move.
-
-\subsection{Summary  Unit}
-
 The  Summary Unit is the last unit of the SAMCell.

### 2019-09-16 2019_neurips_vigil/experiments.tex
experiments

@@
 	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
-	\resizebox{\textwidth}{!}{
+	\begin{tabular}{ccc}
+		\toprule
+		Dataset       &    Canonical setting   & Hard setting   \\
 
-	\begin{tabular}{ccccccc}
-		\toprule
-
-		Dataset    &  	number of frames  &  	maximum memory duration & number of distractors & size of training set & size of validation/test set    \\ 
 		\midrule
 
-		 Canonical setting & 4 & 3 & 1 & 10000320 & 500016 &   \\
+		number of frames      &    4  &  8      \\
+
 		\midrule
 
-		 Hard  setting & 8 & 7& 10 & 10000320 & 500016  \\
+		maximum memory duration      &    3   & 7      \\
+
+		\midrule
+
+		number of distractors     &    1   & 10    \\
+
+		\midrule
+
+		size of training set    &    10000320  & 10000320      \\
+
+		\midrule
+
+		size of validation/test set    &    500016   & 500016      \\
+
+		\midrule
+
+		tasks per family  training set   &    227280  & 227280    \\
+
+		\midrule
+
+		tasks per family  validation/test set   &    11364   & 11364      \\
+
 	   \bottomrule
@@
 	\end{tabular}
-}
 
@@
 
-\subsection{Training and testing Methodology}
+\subsection{Training and Implementation Details}
+
+SAMNet is implmented on IBM's Mi-Prometheus~\cite{kornuta2018accelerating} framework based on Pytorch. 
+We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
+SAMNet was trained using 8 reasoning steps and a hidden state size of 128.
+The external memory has 128-bit slots for all experiments.
+We trained our model until convergence but we also have set a training time limit of 80 hours.
 
@@
 The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results.
-The training and implementation details are in appendix.
 
 \begin{table}[t]
+	\tiny
 
@@
 	\centering
-	\resizebox{\textwidth}{!}{
 	\begin{tabular}{ccccccccccc}
@@
 
-		Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & & 80.1 \\
+		Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & running& 80.1 \\
 
@@
 
-		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1&  &	51.4
+		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&53.1&&	51.4
 \\ 
-		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	& &50.7\\
+		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&57.1	&&50.7\\
 
@@
 	\end{tabular}
-}
 	\label{results}
@@
 }
-	\resizebox{6cm}{3.5cm}{%
 
@@
 	\end{tikzpicture}
-}
 \end{figure}

### 2019-09-16 2019_neurips_vigil/model.tex
no message

--- 2019-09-16 2019_neurips_vigil/model.tex
@@
-\section{Selective Attention Memory Network (SAMNet)}
+\section{Selective Attention Memory (SAM) Network}
 
@@
 
-SAMNet is an end-to-end differentiable recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
-The memory is used to store relevant objects representing contextual information about words in text and visual objects in video frames. 
-Each address of the memory stores a $d$-dimensional vector, where $d$ is a global parameter.
-The memory  can be accessed through either content-addressing, via dot-product attention, or location-based addressing. 
+SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
+The model makes a single pass over the frames in temporal order, accessing one frame at a time.
+The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video. 
+Each location of the memory stores a $d$-dimensional vector. %, where $d$ is a global parameter.
+The memory  can be accessed through either content-based addressing, via dot-product attention, or location-based addressing. 
 Coupled with gating mechanisms to be described later, this enables correct objects to be retrieved 
@@
 
-The core of SAMNet is a recurrent cell called SAMCell (\cref{fig:samcell}). 
-By aligning together a new series of $k$ SAMCells per frame, the network can perform $k$ 
+The core of SAMNet is a recurrent cell called a SAM Cell (\cref{fig:samcell}). 
+By aligning together a new series of $k$ SAM Cells per frame, the network can perform $k$ 
 reasoning steps over each frame, with information flowing between frames through the external memory. 
@@
 
+\paragraph{Question-driven Controller.}
+
+%The Question-driven Controller plays an important role in the reasoning process.
+%It drives the attention over the question and produces the new control states.
+Each new control state defines a new reasoning operation.
+The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit).
+It uses the dot product attention between the contextual words
+%and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
+%
+%This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
+
+This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
+The control state $c_t$ at step $t$ is then fed to temporal classifier, a two-layer feedforward network with ELU activation in the hidden layer of $d$ units.
+The output $\tau_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
+For example in case of the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
+
+\paragraph{Reasoning Unit}
+This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory as well as determining whether the relevant object for reasoning is supposed to be retrieved from the current frame or from the external memory.
+
 This section describes the model and the different units that composed a SAMCell.
@@
 All those modules are described below.
-
-\subsection{Question-driven Controller}
-
-The Question-driven Controller plays an important role in the reasoning process.
-It drives the attention over the question and produces the new control states.
-Each new control state defines a new reasoning operation.
-The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit).
-It uses the dot product attention between the contextual words
-and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
-
-This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
 

### 2019-09-16 2019_neurips_vigil/model.tex

@@
 
-\subsection{Visual Retrieval Unit}
-
-The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
-It is first projecting the past summary object and the feature maps together using the interaction module.
-It is then using the attention module as follow.
-The query are the control states and the keys and are the feature maps coming from the image encoder.
-The results of this attention is applied on the modified features maps coming from the interaction module.
-This unit outputs the extracted object and the visual attention.
-
-\subsection{Memory Retrieval Unit}
-
-The role of the memory retrieval unit is to read and extract object from memory).
-As the Visual Retrieval Unit, it uses the combination of the two following submodules.
-The interaction module blends together the extracted object and the content of the memory.
-The attention module then extract the corresponding object in memory if present.
-This unit outputs the extracted object and its corresponding location, we call it the "read head".
-
-\subsection{Reasoning Unit}
-
-\subsection{Memory update Unit}
-
-This unit is meant to update the content of the memory.
-
-Three actions can happen:
-
-\begin{itemize}
-	\item There is no object to be added to memory, the memory remains unchanged
-	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
-
-	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
-\end{itemize}
-
-This module also updates the position of the write head.
-If a new object as been added to the current write head position, the right head shifts right to a new empty slot.
-If the object has been replaced, the write head doesn't move.
-
-\subsection{Summary  Unit}
-
 The  Summary Unit is the last unit of the SAMCell.

### 2019-09-16 2019_neurips_vigil/experiments.tex
revert to good version

--- 2019-09-16 2019_neurips_vigil/experiments.tex
@@
 We trained our model until convergence but we also have set a training time limit of 80 hours.
-
-\begin{table}[!t]
-	\centering
-	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
-	\resizebox{\textwidth}{!}{
-
-	\begin{tabular}{ccccccc}
-		\toprule
-
-		Dataset    &  	number of frames  &  	maximum memory duration & number of distractors & size of training set & size of validation/test set    \\ 
-          \midrule
-
-		 Canonical setting & 4 & 3 & 1 & 10000320 & 500016 &   \\
-		 \midrule
-
-		 Hard  setting & 8 & 7& 10 & 10000320 & 500016  \\
-		 \bottomrule
-
-	\end{tabular}
-}
-
-	\label{tab:parameters}
-\end{table}
-
-\subsection{Training and testing Methodology}
-
-We compared our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores provided by the authors through personal communications.
-We used the same training parameters detailed in the original paper and reproduced their results.
-For the generalization experiments from canonical to hard, we used the verified model and obtained new results that were not reported in the reference paper.
-In Table 2 COG section shows 4 columns divided into two parts: "paper" and "ours" which distinguish between the results reported in the paper vs.
-our own experiments.
-
-Our experiments focused on the 22 classification tasks provided by the COG dataset.
-First we evaluated SAMNet's performance on the canonical setting and compared it with the COG Model.
-As shown in Table 2 we could achieve a small improvement in accuracy, from 97.6\% for the COG model to 98\% for SAMNet.
-Next we focused on the hard setting of the dataset which increases the number of distractors from 1 to 10 and the number of frames from 4 to 8.
-
-The first approach was to train a model on the hard training set, and test it on the hard test set.
-This is the same approach used by the COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset.
-We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 2).
-%It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.
-
-The second approach was to see if the models can generalize from the easy to the hard setting.
-For this experiment, we trained a model on the canonical dataset, and directly tested on the hard dataset.
-This experiment highlighted the most significant difference between SAMNet and the baseline COG model.
-
-Finally we trained a model on the canonical data set, fine-tuned it on the hard data set using only 25k iterations, and tested on the hard dataset.
-Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represents the state of the art accuracy for the hard setting (classification tasks).
-After a short fine-tuning process, the transferred model could generalize well to harder tasks and even surpass the accuracy obtained in the first approach.
-We note that the third approach is also twice faster than the first one, and it is more effective in terms of accuracy.
-
-A more granular analysis of accuracy per task shows a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor.
-Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
-As we can see in Table 2 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
-The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
-The training and implementation details are in appendix.
 

### 2019-09-16 2019_neurips_vigil/appendix_model.tex

@@
 
+\subsection{Training and testing Methodology}
+
 SAMNet is implemented on IBM's Mi-Prometheus~\cite{kornuta2018accelerating} framework based on Pytorch. 
@@
 
-\section{Results}
+We compared our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores provided by the authors through personal communications.
+We used the same training parameters detailed in the original paper and reproduced their results.
+For the generalization experiments from canonical to hard, we used the verified model and obtained new results that were not reported in the reference paper.
+In Table 1 COG section shows 4 columns divided into two parts: "paper" and "ours" which distinguish between the results reported in the paper vs.
+our own experiments.
+
+Our experiments focused on the 22 classification tasks provided by the COG dataset.
+First we evaluated SAMNet's performance on the canonical setting and compared it with the COG Model.
+As shown in Table 1 we could achieve a small improvement in accuracy, from 97.6\% for the COG model to 98\% for SAMNet.
+Next we focused on the hard setting of the dataset which increases the number of distractors from 1 to 10 and the number of frames from 4 to 8.
+
+The first approach was to train a model on the hard training set, and test it on the hard test set.
+This is the same approach used by the COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset.
+We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 1).
+%It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.
+
+The second approach was to see if the models can generalize from the easy to the hard setting.
+For this experiment, we trained a model on the canonical dataset, and directly tested on the hard dataset.
+This experiment highlighted the most significant difference between SAMNet and the baseline COG model.
+
+Finally we trained a model on the canonical data set, fine-tuned it on the hard data set using only 25k iterations, and tested on the hard dataset.
+Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represents the state of the art accuracy for the hard setting (classification tasks).
+After a short fine-tuning process, the transferred model could generalize well to harder tasks and even surpass the accuracy obtained in the first approach.
+We note that the third approach is also twice faster than the first one, and it is more effective in terms of accuracy.
+
+A more granular analysis of accuracy per task shows a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor.
+Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
+As we can see in Table 2 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
+The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
+The training and implementation details are in appendix.
 
@@
 \end{table}
+
+\begin{table}[!t]
+	\centering
+	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
+	\resizebox{\textwidth}{!}{
+
+		\begin{tabular}{ccccccc}
+			\toprule
+
+			Dataset    &  	number of frames  &  	maximum memory duration & number of distractors & size of training set & size of validation/test set    \\ 
+			\midrule
+
+			Canonical setting & 4 & 3 & 1 & 10000320 & 500016 &   \\
+			\midrule
+
+			Hard  setting & 8 & 7& 10 & 10000320 & 500016  \\
+			\bottomrule
+
+		\end{tabular}
+	}
+
+	\label{tab:parameters}
+\end{table}

### 2019-09-16 2019_neurips_vigil/model.tex

@@
 The core of SAMNet is a recurrent cell called a SAM Cell (\cref{fig:samcell}). 
-By aligning together a new series of $k$ SAM Cells per frame, the network can perform $k$ 
+By aligning together a new series of $T$ cells per frame, the network can perform $k$ 
 reasoning steps over each frame, with information flowing between frames through the external memory. 
-While processing a single frame, for $t=1,2, \dots, k$, SAMCell maintains the following information as part of its recurrent state:
+While processing a single frame, for $t=1,2, \dots, T$, SAMCell maintains the following information as part of its recurrent state:
 (a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and

### 2019-09-16 2019_neurips_vigil/experiments.tex
polishing experiment section

@@
 The mechanisms introduced in SAMCell (e.g., Memory retrieval and update units) learn to operate independent of the total number of frames and allow to generalize to longer video lengths.
-The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
+As shown in Figure 3, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
 Therefore, the memory is updated efficiently instead of storing all information across all frames.
@@
 }
-	\resizebox{6cm}{3.5cm}{%
+	\resizebox{6cm}{4.5cm}{%
 

### 2019-09-16 2019_neurips_vigil/model.tex
polishing experiment section
Current version of Model section

@@
 The core of SAMNet is a recurrent cell called a SAM Cell (\cref{fig:samcell}). 
-By aligning together a new series of $T$ cells per frame, the network can perform $k$ 
-reasoning steps over each frame, with information flowing between frames through the external memory. 
-While processing a single frame, for $t=1,2, \dots, T$, SAMCell maintains the following information as part of its recurrent state:
+By unrolling a new series of $T$ cells for every frame, the network can perform $k$ steps of compositional
+reasoning over every frame, with information flowing between frames through the external memory. 
+While processing a single frame, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
 (a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
@@
 
+The visual (resp. memory) retrieval unit uses the information generated above to extract a relevant object from the frame (resp. memory)
+along with an attention vector over the feature vectors of that frame (resp. over memory addresses). Note that the returned object may not be valid, 
+e.g., if the current reasoning step focuses on the phrase ``last red square'', the returned object from the current frame
+will be invalid even if it contains a red square. The attention vector over the memory $rh_t$ is also called the \emph{read head} since it will be used 
+for memory updates later.
+
 \paragraph{Reasoning Unit}
-This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory as well as determining whether the relevant object for reasoning is supposed to be retrieved from the current frame or from the external memory.
+This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, postponing the actual updates
+themselves to the memory update unit. It also determines whether the relevant object for reasoning is supposed to be retrieved from the current frame or from external memory.
 
-This section describes the model and the different units that composed a SAMCell.
-They are called the Question-driven Controller, the Visual Retrieval Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
-The model is also composed of an Image Encoder and a Question Encoder both responsible to pre-process the visual and textual inputs. The output unit is a classifier.
-All those modules are described below.
+To determine whether we have a valid object from frame (and similarly for memory), we execute the following reasoning procedure.
+First, we take the visual attention vector $va_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
+and compute a simple aggregate $vs_t = \sum_{i=1}^L [va_t(i)]^2$. It can be shown mathematically that the more localized the attention
+vector is, the higher is the aggregate value.
+We perform a similar computation on the read head attention vector over memory locations.
+We feed these 2 values along with the temporal class weights $\tau_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
+in $[0,1]$ modulated for the current reasoning step:
+(a) $\imatch_t$, which determines whether there is a valid visual object;
+(b) $\mmatch_t$, which determines whether there is a valid memory object. 
+(c) $\doreplace_t$, which determines whether the memory should be updated by replacing a previously stored object with a new one; and
+(d) $\doadd_t$, which determines whether a new object should be added to memory.
+We stress that the network has to learn via training how to correctly implement these behaviors.
 
-The  Summary Unit is the last unit of the SAMCell.
+\paragraph{Memory Update Unit.}
+
+%# get attention on the correct slot in memory based on the 2 predicates
+%# attention defaults to 0 if neither condition holds
+%wt = do_replace * read_head + do_add_new * write_head
+%
+%# Update visual_working_memory
+%new_visual_working_memory = (visual_working_memory * (1 - wt)[..., None]
+%+ wt[..., None] * visual_object[..., None, :])
+%
+%# compute shifted sequential head to right
+%shifted_write_head = torch.roll(write_head, shifts=1, dims=-1)
+%
+%# new sequential attention
+%new_write_head = ((shifted_write_head * do_add_new)
+%+ (write_head * (1 - do_add_new)))
+
+TO BE WRITTEN
+
+The  Summary Unit is the last unit of the SAM Cell.
 It is responsible to output the new summary object.
@@
 Once the relevant object is picked, it is combined with the former summary object through a linear layer to become the new summary object.
-It is the final step of the SAMCell reasoning cycle.
+It is the final step of the SAM Cell reasoning cycle.
 
-The image encoder, question encoder and output unit are described in the appendix.
+The details of the modules image encoder, question encoder and output unit are described in the appendix.

### 2019-09-17 2019_neurips_vigil/appendix_model.tex
appendix + tables

@@
 
+\begin{description}
+	\item[Inputs:] 
+	Images
+
+	\item[Output:] 
+	Features maps:
+	$F_k$
+\end{description}
+
+The Image Encoder unit is responsible to preprocess the sequence of images one at the time.
+It is a 4 layer convolutional neural network.
+Every layer is composed of the following sequence of operations:
+
+\begin{enumerate}
+	\item 2D convolution ($stride=1$) 
+	\item 2D max pooling
+	\item 2D batch normalization
+	\item Relu (only for the first 3 layers)
+\end{enumerate}
+
+The first layer has 3 inputs channels and 32 output channels. Layer 2 has 32 and 64. Layer 3 has 64 and 64. Finally, layer 4 has 64 inputs channels and 128 output channels .
+The resulting tensor (feature maps) are of dimensions [batch size, $H*W =7*7$, $dim$=128].
+
 \colorbx{Question Encoder}
 
+\begin{description}
+	\item[Inputs:] 
+	\begin{enumerate}
+		\item question string $question$
+		\item question lengths $question_l$
+
+	\end{enumerate}
+
+	\item[Output:] 
+	\begin{enumerate}
+		\item contextual word embeddingg $cw$
+		\item question encoding $q$
+
+	\end{enumerate}
+
+\end{description}
+
+The strings questions are first embedded ($torch.NN.Embeddings$) and then passed through a $d$-dimensional biLSTM ($d$=128).
+The final hidden state of the biLSTM becomes the question encoding representation $q$.
+Whereas the biLSTM outputs are projected via a linear layer to become the final words encodings named contextual words $cw$.
+
 \colorbx{Output Unit}
+
+\begin{description}
+	\item[Inputs:] 
+	\begin{enumerate}
+		\item question encoding $q$
+		\item summary object $so_t$
+
+	\end{enumerate}
+
+	\item[Output:] 
+	prediction 
+\end{description}
+
+The output unit predicts the final answer to the question.
+It is a 2-linear-layer-ELU classifier that produces a distribution over the possible candidates.
+It is based on two inputs, the final summary object $so_t$ and the question encoding $q$ that are concatenated together.
 
@@
 
-			Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & running& 80.1 \\
+			Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & 78.1& 80.1 \\
 
@@
 
-			AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1&&	51.4
+			AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1& 60.7&	51.4
 			\\ 
-			AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&&50.7\\ 
-			AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&&	78.2\\ 
-			AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	100.0	&56.7&&	77.9\\ 
-			CompareColor	&	98.1		&	89.3	&	95.9	&&		&99.2&	56.1&&	50.1\\ 
-			CompareShape	&	98.0	&		89.7	&	95.9	&&	&99.4	&66.8	&&50.5
+			AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&50.3&50.7\\ 
+			AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&77.1&	78.2\\ 
+			AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	100.0	&56.7&79.3&	77.9\\ 
+			CompareColor	&	98.1		&	89.3	&	95.9	&&		&99.2&	56.1&67.9&	50.1\\ 
+			CompareShape	&	98.0	&		89.7	&	95.9	&&	&99.4	&66.8	&65.4&50.5
 			\\ 
-			Exist	&	100.0	&		99.7	&	99.8		&&	&	100.0&	63.5&&	99.3\\ 
-			ExistColor	&	100.0		&	99.6	&	99.9	&&	&	99.0&	70.9&&	89.8\\ 
-			ExistColorOf	&	99.9	&		95.5	&	99.7		& & &	99.7&	51.5&&	73.1\\ 
-			ExistColorSpace	&94.1		&	88.8	&	91.0	&& &	98.9	&72.8	&&89.2\\ 
-			ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&		&100.0	&65.0&&	50.4
+			Exist	&	100.0	&		99.7	&	99.8		&&	&	100.0&	63.5&96.1&	99.3\\ 
+			ExistColor	&	100.0		&	99.6	&	99.9	&&	&	99.0&	70.9&99&	89.8\\ 
+			ExistColorOf	&	99.9	&		95.5	&	99.7		& & &	99.7&	51.5&76.1&	73.1\\ 
+			ExistColorSpace	&94.1		&	88.8	&	91.0	&& &	98.9	&72.8	&77.3&89.2\\ 
+			ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&		&100.0	&65.0&62.5&	50.4
 			\\ 
-			ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	98.0&	77.5	&&60.2\\ 
-			ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	100.0&	87.8&&	50.3\\ 
-			ExistShape	&	100.0	&	99.5	&	100.0	&&&	100.0&	77.1	&&92.5\\ 
-			ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&100.0	&52.7&&89.8\\ 
-			ExistSpace	&	95.3	&	89.7	&	93.2	&&		&	98.9	&71.1	&&92.8\\ 
-			GetColor	&	100.0		&	95.8&	99.9	&& &	100.0&	71.4&&	97.9\\ 
-			GetColorSpace	&	98.0		&	90.0	&	95.0&	& &	98.2	&71.8&&	92.3\\ 
-			GetShape	&	100.0		&	97.3&	99.9&	&	&	100.0  &83.5&&	97.1
+			ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	98.0&	77.5	&61.7&60.2\\ 
+			ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	100.0&	87.8&60.4&	50.3\\ 
+			ExistShape	&	100.0	&	99.5	&	100.0	&&&	100.0&	77.1	&98.2&92.5\\ 
+			ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&100.0	&52.7&74.7&72.70\\ 
+			ExistShapeSpace &	93.4		&	87.5	&	91.1	&&&97.7 &70	&89.8&89.80& \\
+			ExistSpace	&	95.3	&	89.7	&	93.2	&&		&	98.9	&71.1	&88.1&92.8\\ 
+			GetColor	&	100.0		&	95.8&	99.9	&& &	100.0&	71.4&83.1&	97.9\\ 
+			GetColorSpace	&	98.0		&	90.0	&	95.0&	& &	98.2	&71.8&73.&	92.3\\ 
+			GetShape	&	100.0		&	97.3&	99.9&	&	&	100.0  &83.5&89.2&	97.1
 			\\ 
-			GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	98.1  &78.7	&&	90.3\\ 
-			SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	100.0 & 67.7&&	99.3\\ 
-			SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	100.0&	64.2&&	99.3	  \\
+			GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	98.1  &78.7	&77.3&	90.3\\ 
+			SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	100.0 & 67.7&96.7&	99.3\\ 
+			SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	100.0&	64.2&90.4&	99.3	  \\
 

### 2019-09-17 2019_neurips_vigil/model.tex
Updated model section. Cosmetic changes to other sections.

@@
 
-\begin{figure}[hbtp]
+\begin{wrapfigure}{R}{0.8\textwidth}
 	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
+	\includegraphics[width=0.78\textwidth]{../img/architecture/samnet_architecture4}
 	\caption{General architecture of SAMNet}
 	\label{fig:samnet}
-\end{figure}
+\end{wrapfigure}
+
+%\begin{figure}[hbtp]
+%	\centering
+%	\includegraphics[width=0.7\textwidth]{../img/architecture/samnet_architecture4}
+%	\caption{General architecture of SAMNet}
+%	\label{fig:samnet}
+%\end{figure}
 
@@
 
-\begin{figure}[hbtp]
+\begin{wrapfigure}{R}{0.8\textwidth}
 	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+	\includegraphics[width=0.78\textwidth]{../img/architecture/samcell_reasoning}
 	\caption{Single reasoning step in SAMCell}
 	\label{fig:samcell}
-\end{figure}
+\end{wrapfigure}
+
+%\begin{figure}[hbtp]
+%	\centering
+%	\includegraphics[width=0.7\textwidth]{../img/architecture/samcell_reasoning}
+%	\caption{Single reasoning step in SAMCell}
+%	\label{fig:samcell}
+%\end{figure}
 
@@
 
-\paragraph{Question-driven Controller.}
-
-%The Question-driven Controller plays an important role in the reasoning process.
-%It drives the attention over the question and produces the new control states.
-Each new control state defines a new reasoning operation.
-The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit).
-It uses the dot product attention between the contextual words
-%and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
-%
-%This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
-
+\noindent{\textbf{Question-driven Controller.}}
 This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
@@
 
-The visual (resp. memory) retrieval unit uses the information generated above to extract a relevant object from the frame (resp. memory)
+The visual (resp. memory) retrieval unit uses the information generated above to extract a relevant object $vo_t$ from the frame (resp. $mo_t$ from memory)
 along with an attention vector over the feature vectors of that frame (resp. over memory addresses). Note that the returned object may not be valid, 
@@
 
-\paragraph{Reasoning Unit}
+\noindent{\textbf{Reasoning Unit.}}
+%\paragraph{Reasoning Unit.}
 This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, postponing the actual updates
@@
 
-\paragraph{Memory Update Unit.}
+\noindent{\textbf{Memory Update Unit.}}
+We first determine the exact location where an object could be added to the memory using the following equation:
+\[ w_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
+Above, $w_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
+The sum of components of $w$ is at most equal to 1; and $w_t$ can even equal 0 whenever neither condition
+of adding a new object nor replacing an existing object holds true.
+We then update the memory accordingly as:
+\[ M_t = M_{t-1} \odot (J - w_t \otimes \mathbf{1}) + w_t \otimes vo_t,\]
+where $vo_t$ denotes the object returned by the visual retrieval unit. 
+Here $J$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product. 
+Note that the memory is unchanged in the case where $w_t = 0$, i.e., $M_t = M_{t-1}$.
+We finally update the write head so that it points to the succeeding address if an object was added to memory or otherwise stay the same.
+Let $\whead'_{t-1}$ denote the circular shift to the right of $\whead_{t-1}$ which corresponds to the soft version of this operation.
+Then we update the write head according to the equation:
+\[ \whead_t = \doadd \cdot \whead'_{t-1} + (1-\doadd) \cdot \whead_{t-1} \]
 
-%# get attention on the correct slot in memory based on the 2 predicates
-%# attention defaults to 0 if neither condition holds
-%wt = do_replace * read_head + do_add_new * write_head
-%
-%# Update visual_working_memory
-%new_visual_working_memory = (visual_working_memory * (1 - wt)[..., None]
-%+ wt[..., None] * visual_object[..., None, :])
-%
-%# compute shifted sequential head to right
-%shifted_write_head = torch.roll(write_head, shifts=1, dims=-1)
-%
-%# new sequential attention
-%new_write_head = ((shifted_write_head * do_add_new)
-%+ (write_head * (1 - do_add_new)))
+\noindent{\textbf{Summary Update Unit.}}
+%\paragraph{Summary Update Unit.}
+This unit updates the summary object to be the outcome of the $t$-th reasoning step.
+We first determine whether the relevant object $ro_t$ should be obtained from memory or the frame according to:
+\[ ro_t = \imatch_t \cdot vo_t + \mmatch_t \cdot mo_t \]
+Note that $ro_t$ could be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
+Finally, $so_t$ is the output of a simple linear layer whose inputs are $ro_t$ and the previous summary object $so_{t-1}$.
+This serves to retain additional information that was in $so_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
 
-TO BE WRITTEN
-
-The  Summary Unit is the last unit of the SAM Cell.
-It is responsible to output the new summary object.
-It first picks which object is relevant between the object extracted from memory and the visual object extracted from the image.
-Once the relevant object is picked, it is combined with the former summary object through a linear layer to become the new summary object.
-It is the final step of the SAM Cell reasoning cycle.
-
-The details of the modules image encoder, question encoder and output unit are described in the appendix.
+For more details of the various modules, please see the appendix.

### 2019-09-17 2019_neurips_vigil/experiments.tex
appendix + tables
Tightening the content

@@
 Since there was no baseline for these tests (train on canonical, test on hard), we ran our own experiments using the COG model provided by the authors.
-SAMNet achieves the highest overall scores for all categories of experiments (Table 2), especially for the tests run on the hard dataset.
+SAMNet achieves the highest overall scores for all categories of experiments (\cref{tab:results}), especially for the tests run on the hard dataset.
 Among the 22 classification tasks, we highlighted the two most difficult tasks that affect the overall score.
@@
 \begin{table}[t]
-
-	\caption{COG test set accuracies for  SAMNet \& COG models.
-For the COG section, the results marked as 'paper' comes from the original COG paper ~\cite{yang2018dataset}, whereas the results marked as 'ours' come from our own experiments using the following implementation: https://github.com/google/cog }
+\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
+	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
 
 \centering
-	\resizebox{\textwidth}{!}{
+\begin{adjustbox}{width=\textwidth}
 \begin{tabular}{ccccccccccc}
@@
 	\cmidrule{2-5} \cmidrule{7-11} 
-			&&&&& & paper & ours & ours & paper&\\
+	&&&&& & paper & code & code & paper&\\
 	\cmidrule{7-9} \cmidrule{10-11}
@@
 	\midrule	
-
-			Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & & 80.1 \\
-
+	Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & 78.1& 80.1 \\ 	
 	\midrule 	
-
-			AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1&  &	51.4
-			\\ 
-			AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	& &50.7\\
-
+	AndCompareColor	&	93.5		&	82.7	&	89.2	& &		&81.9	&57.1&60.7  &	51.4 \\ 
+	AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&50.3 &50.7 \\ 
 	\bottomrule
 \end{tabular}
-	}
-	\label{results}
+\end{adjustbox}
+%\resizebox{\textwidth}{!}{
+%	}
+\label{tab:results}
 \end{table}
 
-\begin{figure}
-	\centering
-	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset.
+%\begin{figure}
+%	\centering
+%	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset.
 We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard.
 }
-	\resizebox{6cm}{4.5cm}{%
-
-		\begin{tikzpicture}
-
-		\tiny
-
-		\begin{axis}[
-		ybar,
-		enlargelimits=0.15,
-		legend style={at={(0.5,-0.15)},
-			anchor=north,legend columns=-1},
-		ylabel={COG test accuracy in \% },
-		symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
-		xtick=data,
-		nodes near coords,
-		nodes near coords align={vertical},
-		]
-		\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
-		\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
-		\legend{SAMNet ,COG Model}
-		\end{axis}
-		\end{tikzpicture}
-	}
-\end{figure}
+%	\resizebox{6cm}{4.5cm}{%
+%		
+%		\begin{tikzpicture}
+%		
+%		
+%		
+%		\tiny
+%		
+%		\begin{axis}[
+%		ybar,
+%		enlargelimits=0.15,
+%		legend style={at={(0.5,-0.15)},
+%			anchor=north,legend columns=-1},
+%		ylabel={COG test accuracy in \% },
+%		symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
+%		xtick=data,
+%		nodes near coords,
+%		nodes near coords align={vertical},
+%		]
+%		\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
+%		\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
+%		\legend{SAMNet ,COG Model}
+%		\end{axis}
+%		\end{tikzpicture}
+%	}
+%\end{figure}

### 2019-09-17 2019_neurips_vigil/intro.tex
Tightening the content

@@
 Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
-Potentially, this approach can address Harnad's "symbol grounding problem" \cite{harnad2003symbol} and lead to visually grounded language learning.
+Potentially, this approach can address Harnad's ``symbol grounding problem''~\cite{harnad2003symbol} and lead to visually grounded language learning.
 %In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.
 
-Starting with the Visual Question Answering (VQA) dataset \cite{}, a variety of tasks that integrate vision and language have emerged in the past several years\cite{mogadala2019trends}.
-As a departure from the simpler vision problems like classification and object detection, visual reasoning has become the core emphasis in these tasks.
-Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.
+Starting with the Visual Question Answering (VQA) dataset~\cite{antol2015}, a variety of tasks that integrate vision and language have emerged in the past several years~\cite{mogadala2019trends}.
+Going beyond classification and object detection, the core emphasis in these tasks is
+\emph{visual reasoning} that tackles spatial aspects such as comparison of object attributes, counting and other relational questions.
 
-In contrast to VQA, which comes with static image and question pairs, another emerging direction is Video QA \cite{}, which introduces the aspect of time.
-In addition to spatial reasoning, video input provides an opportunity to work on temporal relations and reasoning.
+In contrast to VQA, which comes with static image and question pairs, another emerging direction is Video QA \cite{}, that 
+provides an additional opportunity to work on \emph{temporal} relations and reasoning.
 As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
 
-The ability to deal with time can pose a challenge for natural language processing (NLP) as well; for instance, in question answering (QA) and dialog applications.
-The current NLP solutions, in certain problem settings, can work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
+The ability to deal with time can pose a challenge for natural language processing (NLP), e.g. in question answering (QA) and dialog applications.  
+Current NLP solutions, in certain problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
 For example, solutions to the bAbI reasoning task (e.g.
@@
 Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.
-In real-time dialog or video QA, there may not be such an opportunity to have the question and entire input all at once in the beginning.
+In real-time dialog or video QA, there may not be such an opportunity to have the question and entire visual data all at once in the beginning.
 
-Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG \cite{yang2018dataset} have limited number of frames (e.g.
+Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG~\cite{yang2018dataset} have limited number of frames (e.g.
 4-16 frames), and therefore manageable by the neural net models to process and represent all of the visual information.
-As an example, according to\cite{song2018explore} the authors extracted visual features from each frame and aggregated features of all clips from one video to form a sequential video representation.
-These solutions may demonstrate high accuracy, however, generalization to arbitrary length video sequences will be problematic.
-Such approaches also differ from the human cognitive strategies.
+As an example, according to~\cite{song2018explore} the authors extracted visual features from each frame and aggregated features of all clips from one video to form a sequential video representation.
+%Such approaches also differ from the human cognitive strategies.
 Humans have the ability to selectively pay attention and store salient items or events in memory based on their goals.
@@
 
-\subsection{Contributions}
-This work introduces a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.
+\paragraph{Contributions.}
+%Such approaches also differ from the human cognitive strategies.
+Humans have the ability to selectively pay attention and store salient items or events in memory based on their goals.
+Working memory and episodic memory systems are responsible for this remarkable ability.
+
+Inspired by human cognitive capacity to selectively pay attention and store salient information in memory,
+we introduce a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.
 Our results based on the COG dataset \cite{yang2018dataset} indicate that the model is capable of:
-%\begin{itemize}
-%\item \textbf{Time aspect}:
-\begin{itemize}
-\item Learning the temporal association - grounding the time-related words with meaning
+(1) learning the temporal association, i.e., grounding the time-related words with meaning;
 	%\item Learning the concept of time
@@
 	%\end{itemize}
-
-\item Learning complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes
+(2) learning complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes;
+(3) selectively control the flow of information to and from the memory to answer questions; and
+(4) updating the memory only with relevant visual information depending on the temporal context.
 %\begin{itemize}
-%\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
-\item Selectively control the flow of information to and from the memory to answer questions
+%\item \textbf{Time aspect}:
+%\begin{itemize}
+%\item Learning the temporal association - grounding the time-related words with meaning
+%%\item Learning the concept of time
+%%\item time context being by-product of gates
+%%\end{itemize}
+%
+%\item Learning complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes
+%%\begin{itemize}
+%%\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
+%\item Selectively control the flow of information to and from the memory to answer questions
+%%\end{itemize}
+%%\item \textbf{Selective Attention Memory}:
+%%\begin{itemize}
+%\item Updating the memory only with relevant visual information depending on the temporal context
+%%\item content based and location based addressing for reading and writing
+%%\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way
+%
 %\end{itemize}
-%\item \textbf{Selective Attention Memory}:
-%\begin{itemize}
-\item Updating the memory content only with relevant visual information depending on the temporal context
-%\item content based and location based addressing for reading and writing
-%\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way
-
-\end{itemize}
 %\end{itemize}

### 2019-09-17 2019_neurips_vigil/model.tex
Tightening the content

@@
 
-\begin{wrapfigure}{R}{0.8\textwidth}
+\begin{wrapfigure}{r}{0.78\textwidth}
 	\centering
-	\includegraphics[width=0.78\textwidth]{../img/architecture/samnet_architecture4}
+	\includegraphics[width=0.76\textwidth]{../img/architecture/samnet_architecture4}
 	\caption{General architecture of SAMNet}
@@
 
-SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory for enabling multi-step reasoning over text and video (\cref{fig:samnet}).
+SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}).
 The model makes a single pass over the frames in temporal order, accessing one frame at a time.
@@
 The memory can be accessed through either content-based addressing, via dot-product attention, or location-based addressing. 
-Coupled with gating mechanisms to be described later, this enables correct objects to be retrieved 
-in order to perform spatio-temporal reasoning on frames and text. 
+Using gating mechanisms, correct objects can be retrieved 
+in order to perform multi-step spatio-temporal reasoning over text and video.  
 %A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
@@
 
-\begin{wrapfigure}{R}{0.8\textwidth}
+\begin{wrapfigure}{r}{0.8\textwidth}
 	\centering
@@
 The core of SAMNet is a recurrent cell called a SAM Cell (\cref{fig:samcell}). 
-By unrolling a new series of $T$ cells for every frame, the network can perform $k$ steps of compositional
-reasoning over every frame, with information flowing between frames through the external memory. 
-While processing a single frame, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
+Unrolling a new series of $T$ cells for every frame enables $T$ steps of compositional
+reasoning.
+Information flows between frames through the external memory. 
+During the $t$-th reasoning step, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
 (a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
@@
 This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
-The control state $c_t$ at step $t$ is then fed to temporal classifier, a two-layer feedforward network with ELU activation in the hidden layer of $d$ units.
+The control state $c_t$ at step $t$ is then fed to a \emph{temporal classifier}, 
+a two-layer feedforward network with ELU activation used in the hidden layer of $d$ units.
 The output $\tau_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
-For example in case of the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
+For the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
 
-The visual (resp. memory) retrieval unit uses the information generated above to extract a relevant object $vo_t$ from the frame (resp. $mo_t$ from memory)
-along with an attention vector over the feature vectors of that frame (resp. over memory addresses). Note that the returned object may not be valid, 
-e.g., if the current reasoning step focuses on the phrase ``last red square'', the returned object from the current frame
-will be invalid even if it contains a red square. The attention vector over the memory $rh_t$ is also called the \emph{read head} since it will be used 
-for memory updates later.
+The visual retrieval unit uses the information generated above to extract a relevant object $vo_t$ from the frame.
+A similar operation on memory yields the object $mo_t$. The memory operation is based on an attention mechanism,
+and resembles content-based addressing on memory. Therefore, we obtain an attention vector over memory addresses
+that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
+Note that the returned objects may be invalid, 
+e.g., if the current reasoning step focuses on the phrase ``last red square'', $vo_t$ is invalid 
+even if the current frame contains a red square.
 
@@
 %\paragraph{Reasoning Unit.}
-This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, postponing the actual updates
-themselves to the memory update unit. It also determines whether the relevant object for reasoning is supposed to be retrieved from the current frame or from external memory.
+This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, as well as
+determining the location of the correct object for reasoning.
 
@@
 vector is, the higher is the aggregate value.
-We perform a similar computation on the read head attention vector over memory locations.
+We perform a similar computation on the read head $rh_t$ over memory locations.
 We feed these 2 values along with the temporal class weights $\tau_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
@@
 We finally update the write head so that it points to the succeeding address if an object was added to memory or otherwise stay the same.
-Let $\whead'_{t-1}$ denote the circular shift to the right of $\whead_{t-1}$ which corresponds to the soft version of this operation.
-Then we update the write head according to the equation:
+Let $\whead'_{t-1}$ denote the circular shift to the right of $\whead_{t-1}$ which corresponds to the soft version of the head update.
+Then:
 \[ \whead_t = \doadd \cdot \whead'_{t-1} + (1-\doadd) \cdot \whead_{t-1} \]
@@
 %\paragraph{Summary Update Unit.}
-This unit updates the summary object to be the outcome of the $t$-th reasoning step.
+This unit updates the (recurrent) summary object to equal the outcome of the $t$-th reasoning step.
 We first determine whether the relevant object $ro_t$ should be obtained from memory or the frame according to:
 \[ ro_t = \imatch_t \cdot vo_t + \mmatch_t \cdot mo_t \]
-Note that $ro_t$ could be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
+Note that $ro_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
 Finally, $so_t$ is the output of a simple linear layer whose inputs are $ro_t$ and the previous summary object $so_{t-1}$.

### 2019-09-17 2019_neurips_vigil/experiments.tex
Visualization. Misc edits.

--- 2019-09-16 2019_neurips_vigil/experiments.tex
@@
 	\midrule	
-
-			Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & & 80.1 \\
-
+	Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & 78.1& 80.1 \\ 	
 	\midrule 	
-
-			AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1&  &	51.4
-			\\ 
-			AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	& &50.7\\
-
+	AndCompareColor	&	93.5		&	82.7	&	89.2	& &		&81.9	&57.1&60.7  &	51.4 \\ 
+	AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&50.3 &50.7 \\ 
 	\bottomrule
 \end{tabular}
-	}
-	\label{results}
+\end{adjustbox}
+%\resizebox{\textwidth}{!}{
+%	}
+\label{tab:results}
 \end{table}

### 2019-09-17 2019_neurips_vigil/appendix_model.tex
Updated model section. Cosmetic changes to other sections.
Table in appendix

@@
 	\includegraphics[width=\textwidth]{img/model2}
-	\label{fig:model}
+	\label{fig:model2}
 \end{figure}
@@
 \begin{table}[t]
-	\tiny
-
-	\caption{COG test set accuracies for  SAMNet \& COG models.
-For the COG section, the results marked as 'paper' comes from the original COG paper ~\cite{yang2018dataset}, whereas the results marked as 'ours' come from our own experiments using the following implementation: https://github.com/google/cog }
-
+\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
+	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
 \resizebox{\textwidth}{!}{
@@
 
-			Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & 78.1& 80.1 \\
+	Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\
 
@@
 
-			AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1& 60.7&	51.4
-			\\ 
-			AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&50.3&50.7\\ 
-			AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&77.1&	78.2\\ 
-			AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	100.0	&56.7&79.3&	77.9\\ 
-			CompareColor	&	98.1		&	89.3	&	95.9	&&		&99.2&	56.1&67.9&	50.1\\ 
-			CompareShape	&	98.0	&		89.7	&	95.9	&&	&99.4	&66.8	&65.4&50.5
-			\\ 
-			Exist	&	100.0	&		99.7	&	99.8		&&	&	100.0&	63.5&96.1&	99.3\\ 
-			ExistColor	&	100.0		&	99.6	&	99.9	&&	&	99.0&	70.9&99&	89.8\\ 
-			ExistColorOf	&	99.9	&		95.5	&	99.7		& & &	99.7&	51.5&76.1&	73.1\\ 
-			ExistColorSpace	&94.1		&	88.8	&	91.0	&& &	98.9	&72.8	&77.3&89.2\\ 
-			ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&		&100.0	&65.0&62.5&	50.4
-			\\ 
-			ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	98.0&	77.5	&61.7&60.2\\ 
-			ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	100.0&	87.8&60.4&	50.3\\ 
-			ExistShape	&	100.0	&	99.5	&	100.0	&&&	100.0&	77.1	&98.2&92.5\\ 
-			ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&100.0	&52.7&74.7&72.70\\ 
-			ExistShapeSpace &	93.4		&	87.5	&	91.1	&&&97.7 &70	&89.8&89.80& \\
-			ExistSpace	&	95.3	&	89.7	&	93.2	&&		&	98.9	&71.1	&88.1&92.8\\ 
-			GetColor	&	100.0		&	95.8&	99.9	&& &	100.0&	71.4&83.1&	97.9\\ 
-			GetColorSpace	&	98.0		&	90.0	&	95.0&	& &	98.2	&71.8&73.&	92.3\\ 
-			GetShape	&	100.0		&	97.3&	99.9&	&	&	100.0  &83.5&89.2&	97.1
-			\\ 
-			GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	98.1  &78.7	&77.3&	90.3\\ 
-			SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	100.0 & 67.7&96.7&	99.3\\ 
-			SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	100.0&	64.2&90.4&	99.3	  \\
-
+	AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
+	AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
+	AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
+	AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
+	CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
+	CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
+	Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
+	ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
+	ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
+	ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
+	ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
+	ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
+	ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
+	ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
+	ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
+	ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
+	ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
+	GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
+	GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
+	GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
+	GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
+	SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
+	SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
 	\bottomrule

### 2019-09-17 2019_neurips_vigil/experiments.tex
Table in appendix
Fix table
progress on experiments - images with performance

@@
 	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
-
 \centering
@@
 	\midrule	
-	Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & 78.1& 80.1 \\ 	
+	Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &         & 97.6  & 65.9 & 78.1& 80.1 \\ 	
 	\midrule 	
-	AndCompareColor	&	93.5		&	82.7	&	89.2	& &		&81.9	&57.1&60.7  &	51.4 \\ 
-	AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&50.3 &50.7 \\ 
+	AndCompareColor	&	93.5		&	82.7	&	89.2	&  80.6 &		&81.9	&57.1&60.7  &	51.4 \\ 
+	AndCompareShape	&	93.2 		&	83.7	&	89.7	& 80.1 &	&	80.0	&53.1	&50.3 &50.7 \\ 
 	\bottomrule
@@
 \end{table}
+
+\begin{figure}
+	\centering
+  \begin{subfigure}{\textwidth}
+    \includegraphics[width=0.99\textwidth]{results/samnet_cog_orig_canonical_no_labels.png}
+  \end{subfigure}%
+  \newline
+  \begin{subfigure}{\textwidth}
+	\includegraphics[width=\textwidth]{results/samnet_cog_orig_hard.png}
+  \end{subfigure}%
+\caption{Comparison of performances of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+\label{fig:samnet}
+\end{figure}
 

### 2019-09-17 2019_neurips_vigil/experiments.tex
overall accuracy comparison

@@
 \section{Experiments}
-
-We evaluated SAMNet on the COG dataset and compared our results to the baseline model described in ~\cite{yang2018dataset}.
-To test the generalization ability of both models, we used the canonical (easy) and hard settings that alter the number of distractors and sequence length.
-Since there was no baseline for these tests (train on canonical, test on hard), we ran our own experiments using the COG model provided by the authors.
-SAMNet achieves the highest overall scores for all categories of experiments (\cref{tab:results}), especially for the tests run on the hard dataset.
-Among the 22 classification tasks, we highlighted the two most difficult tasks that affect the overall score.
-More detailed results are provided in the Appendix.
-
-We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence.
-The mechanisms introduced in SAMCell (e.g., Memory retrieval and update units) learn to operate independent of the total number of frames and allow to generalize to longer video lengths.
-As shown in Figure 3, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
-Therefore, the memory is updated efficiently instead of storing all information across all frames.
-
-%Our experiments were intended to study SAMNet's performances as well as generalization abilities in different settings.
-For this purpose, we use two different versions of the COG dataset, an easy one (canonical) and a hard version to explore a wide range of difficulties.
-The following parameters control the difficulty level: the number of frames in the input sequence, the maximum memory duration (how far is the last object to be remembered), and the number of distractors.
-These parameters are detailed in Table 1 for each setting.
-The table also shows the size of the training/validation/test split used for our experiments.
-The COG dataset is composed of 44 tasks that have equal number of samples.
-%We chose to focus our effort only on the the 22 classification tasks.
-%We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
-We also use the exact same training parameters detailed in the original paper.
-%
-%On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
-We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
-We trained  SAMNet using 8 reasoning steps SAMCells and a hidden state size of 128.
-The external memory has 128-bit slots.
-We trained our model until convergence but we also have set a training time limit of 80 hours.
 
@@
 
-\begin{figure}
+\begin{wrapfigure}{r}{0.5\textwidth}
 	\centering
-	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset.
-We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard.
-}
-	\resizebox{6cm}{4.5cm}{%
+	\includegraphics[width=0.5\textwidth]{results/samnet_cog_overall_transfer.png}
+	\caption{Comparison of SAMNet (blue) and COG model (gray) on their abilities to generalize from the canonical to the hard dataset.
+Light gray indicates original results, whereas right gray indicates the accuracy of COG models that we have trained on our own using the original code.}
+	\label{fig:samcell}
+\end{wrapfigure}
 
-		\begin{tikzpicture}
+We evaluated SAMNet on the COG dataset and compared our results to the baseline model described in ~\cite{yang2018dataset}.
+To test the generalization ability of both models, we used the canonical (easy) and hard settings that alter the number of distractors and sequence length.
+Since there was no baseline for these tests (train on canonical, test on hard), we ran our own experiments using the COG model provided by the authors.
+SAMNet achieves the highest overall scores for all categories of experiments (\cref{tab:results}), especially for the tests run on the hard dataset.
+Among the 22 classification tasks, we highlighted the two most difficult tasks that affect the overall score.
+More detailed results are provided in the Appendix.
 
-		\tiny
+We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence.
+The mechanisms introduced in SAMCell (e.g., Memory retrieval and update units) learn to operate independent of the total number of frames and allow to generalize to longer video lengths.
+As shown in Figure 3, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
+Therefore, the memory is updated efficiently instead of storing all information across all frames.
 
-		\begin{axis}[
-		ybar,
-		enlargelimits=0.15,
-		legend style={at={(0.5,-0.15)},
-			anchor=north,legend columns=-1},
-		ylabel={COG test accuracy in \% },
-		symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
-		xtick=data,
-		nodes near coords,
-		nodes near coords align={vertical},
-		]
-		\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
-		\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
-		\legend{SAMNet ,COG Model}
-		\end{axis}
-		\end{tikzpicture}
-	}
-\end{figure}
+%Our experiments were intended to study SAMNet's performances as well as generalization abilities in different settings.
+For this purpose, we use two different versions of the COG dataset, an easy one (canonical) and a hard version to explore a wide range of difficulties.
+The following parameters control the difficulty level: the number of frames in the input sequence, the maximum memory duration (how far is the last object to be remembered), and the number of distractors.
+These parameters are detailed in Table 1 for each setting.
+The table also shows the size of the training/validation/test split used for our experiments.
+The COG dataset is composed of 44 tasks that have equal number of samples.
+%We chose to focus our effort only on the the 22 classification tasks.
+%We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
+We also use the exact same training parameters detailed in the original paper.
+%
+%On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
+We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
+We trained  SAMNet using 8 reasoning steps SAMCells and a hidden state size of 128.
+The external memory has 128-bit slots.
+We trained our model until convergence but we also have set a training time limit of 80 hours.

### 2019-09-17 2019_neurips_vigil/experiments.tex
Experiments chapter

@@
 
-\begin{table}[t]
-\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
-	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
-\centering
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{ccccccccccc}
-	\toprule
-	Model & & SAMNet & && && COG&& \\
-	\cmidrule{2-5} \cmidrule{7-11} 
-	&&&&& & paper & code & code & paper&\\
-	\cmidrule{7-9} \cmidrule{10-11}
-	Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
-	Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
-	Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
-	\midrule	
-	Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &         & 97.6  & 65.9 & 78.1& 80.1 \\ 	
-	\midrule 	
-	AndCompareColor	&	93.5		&	82.7	&	89.2	&  80.6 &		&81.9	&57.1&60.7  &	51.4 \\ 
-	AndCompareShape	&	93.2 		&	83.7	&	89.7	& 80.1 &	&	80.0	&53.1	&50.3 &50.7 \\ 
-	\bottomrule
-\end{tabular}
-\end{adjustbox}
-%\resizebox{\textwidth}{!}{
-%	}
-\label{tab:results}
-\end{table}
+We evaluated SAMNet on the COG dataset~\cite{yang2018dataset}.
+Our experiments were intended to study SAMNet's performance as well as generalization abilities in different settings.
+For this purpose, we used two different variants of the COG dataset: an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
+The main differences are: the number of frames in the input sequence (4 vs 8) and the maximum number of distractors (i.e.
+objects not important from the point of view of the answer) per frame (1 vs 10).
+%More details on the dataset, its variants and tasks can be found in the Appendix.
 
-\begin{figure}
+%
+%We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
+We also use the exact same training parameters detailed in the original paper.
+%
+%On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
+We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
+We trained  SAMNet using 8 reasoning steps SAMCells and a hidden state size of 128.
+The external memory has 128-bit slots.
+We trained our model until convergence but we also have set a training time limit of 80 hours.
+
+\begin{figure}[htbp]
 	\centering
@@
   \end{subfigure}%
-\caption{Comparison of performances of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-\label{fig:samnet}
+\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+\label{fig:samnet_cog_detailed}
 \end{figure}
 
-\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{wrapfigure}{r}{0.4\textwidth}
 	\centering
-	\includegraphics[width=0.5\textwidth]{results/samnet_cog_overall_transfer.png}
-	\caption{Comparison of SAMNet (blue) and COG model (gray) on their abilities to generalize from the canonical to the hard dataset.
-Light gray indicates original results, whereas right gray indicates the accuracy of COG models that we have trained on our own using the original code.}
-	\label{fig:samcell}
+	\includegraphics[width=0.4\textwidth]{results/samnet_cog_overall_transfer.png}
+	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\label{fig:samnet_cog_overall_transfer}
 \end{wrapfigure}
 
-We evaluated SAMNet on the COG dataset and compared our results to the baseline model described in ~\cite{yang2018dataset}.
-To test the generalization ability of both models, we used the canonical (easy) and hard settings that alter the number of distractors and sequence length.
+We have implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
+In our experiments we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.
+For the Canonical variant (top row), we have achieved similar accuracies for majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with big improvements (around 13 points) for \textit{AndCompare} tasks.
+As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
+Despite there are some tasks in which our model reached slightly lower accuracies,
+% (between 0.2 and 1.8 points)
+when comparing performances on the Hard variant, it clearly dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
+
+The goal of the next set of experiments was to test the generalization ability when it comes to both length of sequence and number of distractors.
+For that purpose we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
+As the original paper haven't included such experiments, we have performed them on our own---light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have achieved by training (finetuning/testing) them on our own using the original code provided by the authors.
+For sanity check, in the first column we report both best achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning (N/A in the second row from the bottom).
+In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on test set.
+We have also tested both models in a setup where model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on Hard variant (third column).
+In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested on exclusively on Hard variant.
+Summarizing, the achieved results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
+
+%we used the canonical (easy) and hard settings that alter the number of distractors and sequence length.
 Since there was no baseline for these tests (train on canonical, test on hard), we ran our own experiments using the COG model provided by the authors.
-SAMNet achieves the highest overall scores for all categories of experiments (\cref{tab:results}), especially for the tests run on the hard dataset.
+SAMNet achieves the highest overall scores for all categories of experiments (\cref{fig:samnet_cog_overall_transfer}), especially for the tests run on the hard dataset.
 Among the 22 classification tasks, we highlighted the two most difficult tasks that affect the overall score.
-More detailed results are provided in the Appendix.
-
-We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence.
-The mechanisms introduced in SAMCell (e.g., Memory retrieval and update units) learn to operate independent of the total number of frames and allow to generalize to longer video lengths.
-As shown in Figure 3, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
+%We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence. 
+%The mechanisms introduced in SAMCell learn to operate independently of the total number of frames and allow to generalize to longer video lengths.
+%As shown in \cref{fig:samnet_cog_overall_transfer}, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
 Therefore, the memory is updated efficiently instead of storing all information across all frames.
-
-%Our experiments were intended to study SAMNet's performances as well as generalization abilities in different settings.
-For this purpose, we use two different versions of the COG dataset, an easy one (canonical) and a hard version to explore a wide range of difficulties.
-The following parameters control the difficulty level: the number of frames in the input sequence, the maximum memory duration (how far is the last object to be remembered), and the number of distractors.
-These parameters are detailed in Table 1 for each setting.
-The table also shows the size of the training/validation/test split used for our experiments.
-The COG dataset is composed of 44 tasks that have equal number of samples.
-%We chose to focus our effort only on the the 22 classification tasks.
-%We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
-We also use the exact same training parameters detailed in the original paper.
-%
-%On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
-We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
-We trained  SAMNet using 8 reasoning steps SAMCells and a hidden state size of 128.
-The external memory has 128-bit slots.
-We trained our model until convergence but we also have set a training time limit of 80 hours.

### 2019-09-17 2019_neurips_vigil/experiments.tex
polished text

@@
 We evaluated SAMNet on the COG dataset~\cite{yang2018dataset}.
-Our experiments were intended to study SAMNet's performance as well as generalization abilities in different settings.
+Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
 For this purpose, we used two different variants of the COG dataset: an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
-The main differences are: the number of frames in the input sequence (4 vs 8) and the maximum number of distractors (i.e.
-objects not important from the point of view of the answer) per frame (1 vs 10).
+The main differences are the number of frames in the input sequence (4 vs. 8) and the maximum number of distractors (i.e., objects not relevant for the answer) per frame (1 vs. 10).
 %More details on the dataset, its variants and tasks can be found in the Appendix.
@@
 We have implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
-In our experiments we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.
-For the Canonical variant (top row), we have achieved similar accuracies for majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with big improvements (around 13 points) for \textit{AndCompare} tasks.
+In our experiments, we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.
+For the Canonical variant (top row), we have achieved similar accuracies for the majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
 As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
@@
 % (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it clearly dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
+when comparing performances on the Hard variant, it dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
 
-The goal of the next set of experiments was to test the generalization ability when it comes to both length of sequence and number of distractors.
-For that purpose we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
-As the original paper haven't included such experiments, we have performed them on our own---light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have achieved by training (finetuning/testing) them on our own using the original code provided by the authors.
-For sanity check, in the first column we report both best achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning (N/A in the second row from the bottom).
-In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on test set.
-We have also tested both models in a setup where model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on Hard variant (third column).
-In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested on exclusively on Hard variant.
-Summarizing, the achieved results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
+The goal of the next set of experiments was to test the generalization ability concerning the sequence length and number of distractors.
+For that purpose, we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
+As the original paper does not include such experiments, we have performed them on our own.
+The light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have trained (fine-tuning/testing) using the original code provided by the authors.
+For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning (N/A in the second row from the bottom).
+In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
+We have also tested both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
+In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested exclusively on the Hard variant.
+In summary, the results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
 

### 2019-09-17 2019_neurips_vigil/appendix_model.tex
Fix table
polishing appendix

@@
 Our experiments focused on the 22 classification tasks provided by the COG dataset.
+More details about the dataset are given in Table 2.
 First we evaluated SAMNet's performance on the canonical setting and compared it with the COG Model.
@@
 Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
-As we can see in Table 2 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
+As we can see in Table 1 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
 The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
@@
 	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
-\resizebox{\textwidth}{!}{
 \centering
-\begin{tabular}{ccccccccccc}
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{lcccccccccc}
 	\toprule
@@
 \end{tabular}
-}
-
+\end{adjustbox}
 \label{results}
@@
 \begin{table}[!t]
+\caption{COG Dataset parameters for the canonical setting and the hard setting  }
 \centering
-	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
-	\resizebox{\textwidth}{!}{
-
+\begin{adjustbox}{width=\textwidth}
 \begin{tabular}{ccccccc}
@@
 	\bottomrule	
-
 \end{tabular}
-	}
-
+\end{adjustbox}
 \label{tab:parameters}

### 2019-09-17 2019_neurips_vigil/intro.tex

@@
 Potentially, this approach can address Harnad's ``symbol grounding problem''~\cite{harnad2003symbol} and lead to visually grounded language learning.
-%In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.
+Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have emerged in the past several years~\cite{mogadala2019trends}.
+Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g.
+appearing or disappearing of objects).
+To deal with the temporal aspect people typically employ cutting the whole video into clips, e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over the whole video to form a single video representation.
+Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
+%As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
+%The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
+%Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
+%For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2015towards}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
+Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.
+However, in real-time dialog or video monitoring, it is impossible to keep the entire history of conversation nor all frames from the beginning of the recording.  
+In this paper we focus on Visual Reasoning, however, instead of enabling the system to access all input frames at every reasoning step, we decided to follow a totally different, nevertheless more natural approach: we enable the model to access each frame only once in order to extract and remember only the  objects that are relevant from the point of view of the task.
 
-Starting with the Visual Question Answering (VQA) dataset~\cite{antol2015}, a variety of tasks that integrate vision and language have emerged in the past several years~\cite{mogadala2019trends}.
-Going beyond classification and object detection, the core emphasis in these tasks is
-\emph{visual reasoning} that tackles spatial aspects such as comparison of object attributes, counting and other relational questions.
-
-In contrast to VQA, which comes with static image and question pairs, another emerging direction is Video QA \cite{}, that 
-provides an additional opportunity to work on \emph{temporal} relations and reasoning.
-As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
-
-The ability to deal with time can pose a challenge for natural language processing (NLP), e.g. in question answering (QA) and dialog applications.  
-Current NLP solutions, in certain problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
-For example, solutions to the bAbI reasoning task (e.g.
-Memory Networks \cite{weston2015towards}), typically involve processing the supporting facts all at once, which reside in memory and available to provide answers.
-Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.
-In real-time dialog or video QA, there may not be such an opportunity to have the question and entire visual data all at once in the beginning.
-
-Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG~\cite{yang2018dataset} have limited number of frames (e.g.
-4-16 frames), and therefore manageable by the neural net models to process and represent all of the visual information.
-As an example, according to~\cite{song2018explore} the authors extracted visual features from each frame and aggregated features of all clips from one video to form a sequential video representation.
 %Such approaches also differ from the human cognitive strategies.

### 2019-09-17 2019_neurips_vigil/model.tex
Visualization. Misc edits.

@@
 
-\begin{wrapfigure}{r}{0.78\textwidth}
+\begin{wrapfigure}{r}{0.80\textwidth}
 	\centering
-	\includegraphics[width=0.76\textwidth]{../img/architecture/samnet_architecture4}
+	\includegraphics[width=0.78\textwidth]{../img/architecture/samnet_architecture4}
 	\caption{General architecture of SAMNet}
@@
 	\includegraphics[width=0.78\textwidth]{../img/architecture/samcell_reasoning}
-	\caption{Single reasoning step in SAMCell}
+	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
 	\label{fig:samcell}
@@
 determining the location of the correct object for reasoning.
-
 To determine whether we have a valid object from frame (and similarly for memory), we execute the following reasoning procedure.
@@
 \noindent{\textbf{Memory Update Unit.}}
-We first determine the exact location where an object could be added to the memory using the following equation:
+Unit first determines the memory location where an object could be added:
 \[ w_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
@@
 
-For more details of the various modules, please see the appendix.
+%For more details of the various modules, please see the appendix.

### 2019-09-17 2019_neurips_vigil/intro.tex
polished intro, model, fit all into 4 pages

@@
 Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
-Potentially, this approach can address Harnad's ``symbol grounding problem''~\cite{harnad2003symbol} and lead to visually grounded language learning.
+Potentially, this approach can address Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} and lead to visually grounded language learning.
 Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have emerged in the past several years~\cite{mogadala2019trends}.
 Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g.
-appearing or disappearing of objects).
-To deal with the temporal aspect people typically employ cutting the whole video into clips, e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over the whole video to form a single video representation.
+object disappearance).
+To deal with the temporal aspect people typically employ cutting the whole video into clips, e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
 Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
@@
 %For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2015towards}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
-Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.
+Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
 However, in real-time dialog or video monitoring, it is impossible to keep the entire history of conversation nor all frames from the beginning of the recording.
-In this paper we focus on Visual Reasoning, however, instead of enabling the system to access all input frames at every reasoning step, we decided to follow a totally different, nevertheless more natural approach: we enable the model to access each frame only once in order to extract and remember only the  objects that are relevant from the point of view of the task.
 
@@
 Working memory and episodic memory systems are responsible for this remarkable ability.
-
+In this paper we focus on Visual Reasoning, however, however, instead of enabling the system to access all input frames at every reasoning step, we decided to follow a totally different, nevertheless more natural approach.
 Inspired by human cognitive capacity to selectively pay attention and store salient information in memory,
-we introduce a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.
+we introduce a new model that can dynamically processes video input frame-by-frame, reasons over a given image and remembers the salient concepts to answer questions.
 Our results based on the COG dataset \cite{yang2018dataset} indicate that the model is capable of:

### 2019-09-17 2019_neurips_vigil/appendix_model.tex
reorganizing appendix

@@
 
-\section{VWM model}
+\subsection{VWM model}
 
@@
 
-\section{Basic layers/modules}
+\subsection{Basic layers/modules}
 
@@
 
-\section{VWM cell}
+\subsection{VWM cell}
 
@@
 
-\begin{figure}
-	\includegraphics[width=\textwidth]{img/model2}
-	\label{fig:model2}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\textwidth]{img/image}
-	\label{fig:model}
-\end{figure}
-
 \colorbx{Image Encoder}
@@
 
-\section{Training and Implementation Details}
+\subsection{Training and Implementation Details}
 
-\subsection{Training and testing Methodology}
+\subsubsection{Implementation Details}
 
@@
 We trained our model until convergence but we also have set a training time limit of 80 hours.
+
+\subsubsection{Training and testing Methodology}
 
@@
 This is the same approach used by the COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset.
-We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 1).
+We achieve a test accuracy of 96.1 \% which represents a 16\% improvement from the COG model score (see Table 1).
 %It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.
@@
 Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
-As we can see in Table 1 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
+As we can see in Table 1 we could achieve a 12\% improvement for the canonical data set and almost a 30\% improvement for the hard dataset.
 The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
@@
 
-\begin{table}[t]
+\begin{table}[htb]
 \caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
@@
 
-\begin{table}[!t]
+\begin{table}[htb]
 \caption{COG Dataset parameters for the canonical setting and the hard setting  }
@@
 \end{table}
+
+\subsection{Visualization}
+
+\begin{figure}[!htb]
+	\includegraphics[width=\textwidth]{img/model2}
+	\label{fig:model2}
+\end{figure}
+
+\begin{figure}[!htb]
+	\includegraphics[width=\textwidth]{img/image}
+	\label{fig:model}
+\end{figure}

### 2019-09-18 2019_neurips_vigil/experiments.tex
interpretability

@@
   \begin{subfigure}{\textwidth}
-    \includegraphics[width=0.99\textwidth]{results/samnet_cog_orig_canonical_no_labels.png}
+    \includegraphics[width=0.92\textwidth]{results/samnet_cog_orig_canonical_no_labels.png}
   \end{subfigure}%
@@
   \begin{subfigure}{\textwidth}
-	\includegraphics[width=\textwidth]{results/samnet_cog_orig_hard.png}
+	\includegraphics[width=0.93\textwidth]{results/samnet_cog_orig_hard.png}
   \end{subfigure}%
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth}
+\begin{wrapfigure}{r}{0.36\textwidth}
 	\centering
@@
 In summary, the results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
+One other strength of SAMNet is its interpretability.
+Observing attention maps (see Appendix 4.5) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
+It also accurately classify temporal contexts as designed.
+However we notice that the model can sometime discover alternative strategies that were not in the intended design but the answers are still correct.
+More details are given in Appendix 4.5
 

### 2019-09-18 2019_neurips_vigil/model.tex
Minor

@@
 Unrolling a new series of $T$ cells for every frame enables $T$ steps of compositional
-reasoning.
+reasoning, similar to~\cite{hudson2018compositional}.
 Information flows between frames through the external memory. 
@@
 First, we take the visual attention vector $va_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
-and compute a simple aggregate $vs_t = \sum_{i=1}^L [va_t(i)]^2$. It can be shown mathematically that the more localized the attention
+and compute a simple aggregate\footnote{%
+	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.}: %
+$vs_t = \sum_{i=1}^L [va_t(i)]^2$. It can be shown mathematically that the more localized the attention
 vector is, the higher is the aggregate value.

### 2019-09-18 2019_neurips_vigil/experiments.tex
title
figures with black fonts

@@
 
-\begin{wrapfigure}{r}{0.36\textwidth}
+\begin{wrapfigure}{r}{0.45\textwidth}
 	\centering
-	\includegraphics[width=0.4\textwidth]{results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.45\textwidth]{results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 The light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have trained (fine-tuning/testing) using the original code provided by the authors.
-For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning (N/A in the second row from the bottom).
+For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning.
 In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
@@
 Observing attention maps (see Appendix 4.5) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
-It also accurately classify temporal contexts as designed.
+It also accurately classifies temporal contexts as designed.
 However we notice that the model can sometime discover alternative strategies that were not in the intended design but the answers are still correct.

### 2019-09-18 2019_neurips_vigil/appendix_model.tex
Visualization detailed example.

@@
 
-The Question-driven Controller plays an important role in the reasoning process.
-It drives the attention over the question and produces the new control states.
+%The Question-driven Controller plays an important role in the reasoning process.
+%It drives the attention over the question and produces the new control states.
 Each new control state defines a new reasoning operation.
@@
 It uses the dot product attention between the contextual words
-and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
-
-This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
+%and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
+%
+%This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
 
@@
 
-The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
+%The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
 It is first projecting the past summary object and the feature maps together using the interaction module.
-It is then using the attention module as follow.
+%It is then using the attention module as follow.
 The query are the control states and the keys and are the feature maps coming from the image encoder.
 The results of this attention is applied on the modified features maps coming from the interaction module.
-This unit outputs the extracted object and the visual attention.
+%This unit outputs the extracted object and the visual attention.
 
@@
 
-The role of the memory retrieval unit is to read and extract object from memory).
-As the Visual Retrieval Unit, it uses the combination of the two following submodules.
+%The role of the memory retrieval unit is to read and extract object from memory).
+%As the Visual Retrieval Unit, it uses the combination of the two following submodules.
 The interaction module blends together the extracted object and the content of the memory.
@@
 
-	\item[Equations:]
-	\begin{enumerate}
-		\item[]
-		\item $\imatch_t \in [0,1]$:
-		It's true if there is a valid visual object. This assumes that
-		the current reasoning step refers to either ```now''  or ``latest''.
-
-		\item$\mmatch_t \in [0,1]$:
-		It's true if there is a valid memory object. This assumes that
-		the current reasoning step refers to either ``last'',  or alternatively ``latest'' 
-		but there is no matching visual object.
-
-		\item $\doadd_t$:
-
-		\item $\doreplace_t$: 
-	\end{enumerate}
+%	\item[Equations:]
+%	\begin{enumerate}
+%		\item[]
+%		\item $\imatch_t \in [0,1]$:
+%		It's true if there is a valid visual object in the current temporal context.
+%		
+%		\item $\mmatch_t \in [0,1]$:
+%		It's true if there is a valid memory object in the current temporal context.
+%		
+%		\item $\doadd_t \in [0,1]$: 
+%		It's true if the current visual object should be added as a new object to memory.
+%		
+%		\item $\doreplace_t \in [0,1]$: 
+%		It's true if the current visual object should replace an existing object in memory.
+%	\end{enumerate}
 \end{description}
@@
 
-This unit is meant to update the content of the memory.
-
-Three actions can happen:
-
-\begin{itemize}
-	\item There is no object to be added to memory, the memory remains unchanged
-	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
-
-	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
-\end{itemize}
-
-This module also updates the position of the write head.
+%This unit is meant to update the content of the memory. 
+%
+%Three actions can happen:
+%
+%\begin{itemize}
+%	\item There is no object to be added to memory, the memory remains unchanged
+%	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
+%	
+%	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
+%\end{itemize}
+%
+%
+%This module also updates the position of the write head.
 If a new object as been added to the current write head position, the right head shifts right to a new empty slot.
@@
 
-The  Summary Unit is the last unit of the SAMCell.
+%The  Summary Unit is the last unit of the SAMCell.
 It is responsible to output the new summary object.
@@
 It is the final step of the SAMCell reasoning cycle.
-
-The image encoder, question encoder and output unit are described in the appendix.
+%
+%The image encoder, question encoder and output unit are described in the appendix.
 
@@
 
-\begin{figure}[!htb]
-	\includegraphics[width=\textwidth]{img/model2}
-	\label{fig:model2}
+We illustrate the key reasoning steps taken by the model with the following example.
+Let the question be: ``Does color of u now equal the color of the latest circle?''
+and let the frames be as shown in~\cref{fig:frame-seq}.
+The answer is true in the last frame because the latest circle can be found in Frame 2. 
+\begin{figure}[!h]
+\begin{minipage}{0.25\textwidth}
+\centering
+\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
+\label{fig:frame-1}
+\end{minipage}\hfill
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
+	\label{fig:frame-1}
+\end{minipage}\hfill
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
+	\label{fig:frame-1}
+\end{minipage}\hfill
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
+		\label{fig:frame-1}
+\end{minipage}
+\caption{Sample sequence of input frames} 
+\label{fig:frame-seq}
 \end{figure}
 
-\begin{figure}[!htb]
-	\includegraphics[width=\textwidth]{img/image}
-	\label{fig:model}
+SAMNet gives the correct answer for this example and we can interpret its reasoning process via a movie that we can generate.
+The key steps in that reasoning process are shown below. Working backwards, the following shows what happens in the key steps
+of the reasoning process.
+In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
+is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
+\begin{figure}[!h]
+\centering
+  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
+\caption{State of SAMNet in a particular reasoning step} 
+\label{fig:frame-4-step-1}
 \end{figure}
+
+Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
+as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
+and the temporal classification is ``latest'', there
+is no valid visual attention.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
+	\caption{State of SAMNet in a particular reasoning step} 
+	\label{fig:frame-4-step-6}
+\end{figure}
+
+But in Step 6 of processing Frame 2 (see~\cref{fig:frame-2-step-6}), 
+we see that the object representing the circle is where the attention is.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+	\caption{State of SAMNet in a particular reasoning step} 
+	\label{fig:frame-2-step-6}
+\end{figure}
+Moreover, the ``Add New`` gate value is high enough that the valid object representing
+the visual encoding of the circle is stored in memory. Note that this is not perfect:
+this value should have been close to 1 but the model is still able to use it for 
+correct prediction.

### 2019-09-18 2019_neurips_vigil/experiments.tex
Visualization detailed example.

@@
 One other strength of SAMNet is its interpretability.
-Observing attention maps (see Appendix 4.5) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
+Observing attention maps (see Appendix) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
 It also accurately classifies temporal contexts as designed.
 However we notice that the model can sometime discover alternative strategies that were not in the intended design but the answers are still correct.
-More details are given in Appendix 4.5
+More details are given in the Appendix.
 

### 2019-09-18 2019_neurips_vigil/intro.tex
minor edits

@@
 object disappearance).
-To deal with the temporal aspect people typically employ cutting the whole video into clips, e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
+To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
 Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
@@
 Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
-However, in real-time dialog or video monitoring, it is impossible to keep the entire history of conversation nor all frames from the beginning of the recording.
+However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
 

### 2019-09-18 2019_neurips_vigil/model.tex
Visualization detailed example.
minor edits

@@
 %\paragraph{Reasoning Unit.}
-This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, as well as
+This module is the backbone of SAMNet that determines what gating operations need to be performed on the external memory, as well as
 determining the location of the correct object for reasoning.
-To determine whether we have a valid object from frame (and similarly for memory), we execute the following reasoning procedure.
+To determine whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
 First, we take the visual attention vector $va_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
@@
 We perform a similar computation on the read head $rh_t$ over memory locations.
-We feed these 2 values along with the temporal class weights $\tau_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
+We feed these two values along with the temporal class weights $\tau_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
 in $[0,1]$ modulated for the current reasoning step:
@@
 
-%For more details of the various modules, please see the appendix.
+For details of the modules not covered here, please see the appendix.

### 2019-09-19 2019_neurips_kr2ml/experiments.tex
KR2ML - start

--- 2019-09-18 2019_neurips_vigil/experiments.tex
@@
 
-We evaluated SAMNet on the COG dataset~\cite{yang2018dataset}.
+We have implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
+We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning.
 Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
-For this purpose, we used two different variants of the COG dataset: an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
-The main differences are the number of frames in the input sequence (4 vs. 8) and the maximum number of distractors (i.e., objects not relevant for the answer) per frame (1 vs. 10).
+For this purpose, we used two different variants of the COG dataset (\cref{fig:cog_variants}): an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
+The main differences are the number of frames in the input sequence (4 vs. 8) and the maximum number of distractors (i.e., objects not relevant for the answer) per a single frame (1 vs. 10).
+
+\begin{table}[htb]
+\caption{Details of the Canonical and Hard variants of the COG dataset}
+\centering
+\begin{tabular}{ccccccc}
+	\toprule
+	Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
+	& of   & memory & number of & of & of & of  \\
+	& frames & duration & distractors & training set & validation set & test set \\
+	\midrule
+	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 422400? \\	
+	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 422400? \\
+	\bottomrule	
+\end{tabular}
+\label{tab:cog_variants}
+\end{table}
+
 %More details on the dataset, its variants and tasks can be found in the Appendix.
@@
 
+\subsection{Performance comparison with COG baseline}
+
 \begin{figure}[htbp]
@@
   \begin{subfigure}{\textwidth}
-    \includegraphics[width=0.92\textwidth]{results/samnet_cog_orig_canonical_no_labels.png}
+    \includegraphics[width=0.92\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
   \end{subfigure}%
@@
   \begin{subfigure}{\textwidth}
-	\includegraphics[width=0.93\textwidth]{results/samnet_cog_orig_hard.png}
+	\includegraphics[width=0.93\textwidth]{../results/samnet_cog_orig_hard.png}
   \end{subfigure}%
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.45\textwidth]{../results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 
-We have implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
 In our experiments, we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.

### 2019-09-19 2019_neurips_kr2ml/experiments.tex
analysis of the results strategy - start

@@
 \centering
-\begin{tabular}{ccccccc}
+\begin{tabular}{lcccccc}
 	\toprule
@@
 
-\subsection{Performance comparison with COG baseline}
+\subsection{Performance comparison with the COG baseline}
 
@@
 
+In our experiments, we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.
+For the Canonical variant (top row), we have achieved similar accuracies for the majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
+As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
+Despite there are some tasks in which our model reached slightly lower accuracies,
+% (between 0.2 and 1.8 points)
+when comparing performances on the Hard variant, it dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
+
+\begin{table}[htb]
+\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~
+	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
+\centering
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{lcccccccccc}
+	\toprule
+	Model & & SAMNet & && && COG&& \\
+	\cmidrule{2-5} \cmidrule{7-11} 
+	&&&&& & paper & ours & ours & paper&\\
+	\cmidrule{7-9} \cmidrule{10-11}
+	Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
+	Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
+	Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
+	\midrule
+
+	Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\
+
+	\midrule
+
+	AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
+	AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
+	AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
+	AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
+	CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
+	CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
+	Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
+	ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
+	ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
+	ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
+	ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
+	ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
+	ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
+	ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
+	ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
+	ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
+	ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
+	GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
+	GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
+	GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
+	GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
+	SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
+	SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
+	\bottomrule
+\end{tabular}
+\end{adjustbox}
+\label{results}
+\end{table}
+
 \begin{wrapfigure}{r}{0.45\textwidth}
@@
 \end{wrapfigure}
-
-In our experiments, we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.
-For the Canonical variant (top row), we have achieved similar accuracies for the majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
-Despite there are some tasks in which our model reached slightly lower accuracies,
-% (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
 
@@
 Therefore, the memory is updated efficiently instead of storing all information across all frames.
+
+\subsection{Analysis of the reasoning strategy}
+
+We illustrate the key reasoning steps taken by the model with the following example.
+Let the question be: ``Does color of u now equal the color of the latest circle?''
+and let the frames be as shown in~\cref{fig:frame-seq}.
+The answer is true in the last frame because the latest circle can be found in Frame 2. 
+\begin{figure}[!h]
+\begin{minipage}{0.25\textwidth}
+\centering
+\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
+\label{fig:frame-1}
+\end{minipage}\hfill
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
+	\label{fig:frame-1}
+\end{minipage}\hfill
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
+	\label{fig:frame-1}
+\end{minipage}\hfill
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
+		\label{fig:frame-1}
+\end{minipage}
+\caption{Sample sequence of input frames} 
+\label{fig:frame-seq}
+\end{figure}
+
+SAMNet gives the correct answer for this example and we can interpret its reasoning process via a movie that we can generate.
+The key steps in that reasoning process are shown below. Working backwards, the following shows what happens in the key steps
+of the reasoning process.
+In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
+is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
+\begin{figure}[!h]
+\centering
+  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
+\caption{State of SAMNet in a particular reasoning step} 
+\label{fig:frame-4-step-1}
+\end{figure}
+
+Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
+as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
+and the temporal classification is ``latest'', there
+is no valid visual attention.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
+	\caption{State of SAMNet in a particular reasoning step} 
+	\label{fig:frame-4-step-6}
+\end{figure}
+
+But in Step 6 of processing Frame 2 (see~\cref{fig:frame-2-step-6}), 
+we see that the object representing the circle is where the attention is.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+	\caption{State of SAMNet in a particular reasoning step} 
+	\label{fig:frame-2-step-6}
+\end{figure}
+Moreover, the ``Add New`` gate value is high enough that the valid object representing
+the visual encoding of the circle is stored in memory. Note that this is not perfect:
+this value should have been close to 1 but the model is still able to use it for 
+correct prediction.

### 2019-09-19 2019_neurips_kr2ml/experiments.tex
work in progress - experiments

@@
 Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
-For this purpose, we used two different variants of the COG dataset (\cref{fig:cog_variants}): an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
+For this purpose, we used two different variants of the COG dataset (\cref{tab:cog_variants}): an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
 The main differences are the number of frames in the input sequence (4 vs. 8) and the maximum number of distractors (i.e., objects not relevant for the answer) per a single frame (1 vs. 10).
@@
 
+In our experiments we have trained SAMNet using 8 reasoning steps and external memory having 8 address locations, each being a vector of 128 floats.
+We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
+In here, we have focused on 22 classification tasks and compared our results with the baseline model.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}, whereas full comparison is presented in \cref{tab:results-full}.
+
 \begin{figure}[htbp]
@@
   \begin{subfigure}{\textwidth}
-    \includegraphics[width=0.92\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
+    \includegraphics[width=0.99\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
   \end{subfigure}%
@@
   \begin{subfigure}{\textwidth}
-	\includegraphics[width=0.93\textwidth]{../results/samnet_cog_orig_hard.png}
+	\includegraphics[width=\textwidth]{../results/samnet_cog_orig_hard.png}
   \end{subfigure}%
@@
 
-In our experiments, we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.
 For the Canonical variant (top row), we have achieved similar accuracies for the majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
@@
 
-\begin{table}[htb]
+\begin{table}[t!]
 \caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~
@@
 \end{adjustbox}
-\label{results}
+\label{tab:results-full}
 \end{table}
 
-\begin{wrapfigure}{r}{0.45\textwidth}
+\begin{wrapfigure}{r}{0.5\textwidth}
 	\centering
-	\includegraphics[width=0.45\textwidth]{../results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.5\textwidth]{../results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 \subsection{Analysis of the reasoning strategy}
+As a result of training the SAMNet developed a quite complex reasoning.
+We illustrate the key reasoning steps taken by the model with the following example.
 
-We illustrate the key reasoning steps taken by the model with the following example.
-Let the question be: ``Does color of u now equal the color of the latest circle?''
+Let the question be: ``'
 and let the frames be as shown in~\cref{fig:frame-seq}.
 The answer is true in the last frame because the latest circle can be found in Frame 2.
+
+\captionsetup[subfigure]{labelformat=empty}
 \begin{figure}[!h]
-\begin{minipage}{0.25\textwidth}
-\centering
+  \begin{center}
+  Question: \textbf{Does color of u now equal the color of the latest circle?}
+  \end{center}
+  \vskip -0.4cm
+  \null\hfill
+  \begin{subfigure}{0.25\textwidth}
 	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
+	\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{invalid}}
 	\label{fig:frame-1}
-\end{minipage}\hfill
-\begin{minipage}{0.25\textwidth}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}{0.25\textwidth}
 	\centering
 	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
-	\label{fig:frame-1}
-\end{minipage}\hfill
-\begin{minipage}{0.25\textwidth}
+	\caption{Frame: \textbf{2}\newline Ground Truth: \textbf{false}}
+	\label{fig:frame-2}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}{0.25\textwidth}
 	\centering
 	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
-	\label{fig:frame-1}
-\end{minipage}\hfill
-\begin{minipage}{0.25\textwidth}
+	\caption{Frame: \textbf{3}\newline Ground Truth: \textbf{true}}
+	\label{fig:frame-3}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}{0.25\textwidth}
 	\centering
 	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
-		\label{fig:frame-1}
-\end{minipage}
-\caption{Sample sequence of input frames} 
+	\caption{Frame: \textbf{4}\newline Ground Truth: \textbf{true}}
+	\label{fig:frame-4}
+  \end{subfigure}%
+  \hfill\null
+  \newline
+  \centering
+\caption{The video-question pair selected for analysis.} 
 \label{fig:frame-seq}  

### 2019-09-19 2019_neurips_kr2ml/intro.tex

--- 2019-09-18 2019_neurips_vigil/intro.tex
@@
 Potentially, this approach can address Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} and lead to visually grounded language learning.
-Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have emerged in the past several years~\cite{mogadala2019trends}.
+
+Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \citep{}.
+These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.
+Furthermore, symbolic priors (e.g., domain knowledge) and integration of logic depend on hand-crafted modules.
+In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability).
+However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols.
+
+Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have appeared in the past several years~\cite{mogadala2019trends}.
 Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g.
@@
 Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
-%As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
-%The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
-%Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
-%For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2015towards}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
 Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
 However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
+
+As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
+The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
+Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
+For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2015towards}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
 

### 2019-09-19 2019_neurips_kr2ml/intro.tex
bib

@@
 
-Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \citep{}.
+Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \citep{mao2019neurosymbolic}.
 These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.
 Furthermore, symbolic priors (e.g., domain knowledge) and integration of logic depend on hand-crafted modules.
-In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability).
-However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols.
+In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability)\citep{vedantam2019probabilistic}.
+However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols \citep{taniguchi2018symbol}.
 
@@
 Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
-For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2015towards}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
+For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2014memory}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
 

### 2019-09-19 2019_neurips_kr2ml/appendix_model.tex
KR2ML - start
progress on experiments, new title

--- 2019-09-18 2019_neurips_vigil/appendix_model.tex
@@
 
-\subsection{VWM model}
+\subsection{VWM Network model}
 
@@
 
-\subsection{VWM cell}
+\subsection{SAM cell}
 
-The VWM recurrent cell is executed for $T$ reasoning steps for every frame in
+The SAM recurrent cell is executed for $T$ reasoning steps for every frame in
 the temporal order.  Within a single frame, the cell state at the end of each reasoning step 
@@
 
-%The number of slots $N$ for the VWM $M_t$ is not fixed because the neural network 
+%The number of slots $N$ for the SAM $M_t$ is not fixed because the neural network 
 %parameters do not depend on it. It can be variable across the different datasets used
@@
 		\item Previous summary object: $so_{t-1} \in  \Reals^d$
-		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
+		\item Previous SAM $M_{t-1} \in \Reals^{N \times d}$
 	\end{enumerate}
@@
 		\item[]
-		\item Modified VWM: $\hat{M}_t = \cI(so_{t-1}, M_{t-1})$
+		\item Modified SAM: $\hat{M}_t = \cI(so_{t-1}, M_{t-1})$
 		\item Memory object and attention: $mo_t, \rhead_t = \cA(y, \hat{M}_t, M_{t-1})$
@@
 		\item Read head: $\rhead_t \in \Reals^N$
-		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
+		\item Previous SAM $M_{t-1} \in \Reals^{N \times d}$
 		\item Previous write head: $\whead_{t-1} \in \Reals^N$
@@
 		\item[]
-		\item VWM $M_t \in \Reals^{N \times d}$
+		\item SAM $M_t \in \Reals^{N \times d}$
 		\item Read head: $\rhead_t \in \Reals^N$
@@
 
-SAMNet is implemented on IBM's Mi-Prometheus~\cite{kornuta2018accelerating} framework based on Pytorch. 
+SAMNet is implemented using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch. 
 We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
@@
 \end{table}
-
-\subsection{Visualization}
-
-We illustrate the key reasoning steps taken by the model with the following example.
-Let the question be: ``Does color of u now equal the color of the latest circle?''
-and let the frames be as shown in~\cref{fig:frame-seq}.
-The answer is true in the last frame because the latest circle can be found in Frame 2. 
-\begin{figure}[!h]
-\begin{minipage}{0.25\textwidth}
-\centering
-\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
-\label{fig:frame-1}
-\end{minipage}\hfill
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
-	\label{fig:frame-1}
-\end{minipage}\hfill
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
-	\label{fig:frame-1}
-\end{minipage}\hfill
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
-		\label{fig:frame-1}
-\end{minipage}
-\caption{Sample sequence of input frames} 
-\label{fig:frame-seq}
-\end{figure}
-
-SAMNet gives the correct answer for this example and we can interpret its reasoning process via a movie that we can generate.
-The key steps in that reasoning process are shown below. Working backwards, the following shows what happens in the key steps
-of the reasoning process.
-In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
-is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
-\begin{figure}[!h]
-\centering
-  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
-\caption{State of SAMNet in a particular reasoning step} 
-\label{fig:frame-4-step-1}
-\end{figure}
-
-Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
-as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
-and the temporal classification is ``latest'', there
-is no valid visual attention.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
-	\caption{State of SAMNet in a particular reasoning step} 
-	\label{fig:frame-4-step-6}
-\end{figure}
-
-But in Step 6 of processing Frame 2 (see~\cref{fig:frame-2-step-6}), 
-we see that the object representing the circle is where the attention is.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
-	\caption{State of SAMNet in a particular reasoning step} 
-	\label{fig:frame-2-step-6}
-\end{figure}
-Moreover, the ``Add New`` gate value is high enough that the valid object representing
-the visual encoding of the circle is stored in memory. Note that this is not perfect:
-this value should have been close to 1 but the model is still able to use it for 
-correct prediction.

### 2019-09-19 2019_neurips_kr2ml/experiments.tex
work on experiments, changed figure placement
progress on experiments, new title

@@
 	\midrule
-	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 422400? \\	
-	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 422400? \\
+	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 500016? \\	
+	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 500016? \\
 	\bottomrule	
@@
 
+\subsection{Generalization capabilities}
+
 \begin{wrapfigure}{r}{0.5\textwidth}
@@
 
-\subsection{Analysis of the reasoning strategy}
-As a result of training the SAMNet developed a quite complex reasoning.
-We illustrate the key reasoning steps taken by the model with the following example.
-
-Let the question be: ``'
-and let the frames be as shown in~\cref{fig:frame-seq}.
-The answer is true in the last frame because the latest circle can be found in Frame 2.
-
 \captionsetup[subfigure]{labelformat=empty}
-\begin{figure}[!h]
+\begin{figure}[!b]
   \begin{center}
@@
 	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
-	\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{invalid}}
+	\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{false}}
 	\label{fig:frame-1}
@@
   \centering
-\caption{The video-question pair selected for analysis.} 
-\label{fig:frame-seq}  
+\caption{A sample from the COG dataset selected for the following analysis.} 
+\label{fig:example}  
 \end{figure}
 
-SAMNet gives the correct answer for this example and we can interpret its reasoning process via a movie that we can generate.
-The key steps in that reasoning process are shown below. Working backwards, the following shows what happens in the key steps
-of the reasoning process.
-In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
-is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
+\subsection{Analysis of the reasoning strategy}
+As a result of training the SAMNet developed a quite complex reasoning.
+We illustrate the key reasoning steps taken by the model with the example presented in \cref{fig:example}.
+First let us analyze, independently of SAMNet, what are the key operations that need to be performed in order to provide the answers. 
+As the question concerns \textbf{latest} in the \textbf{Frame 1}, one should look for both \textbf{u} and \textbf{circle} objects and look at their colors (different), thus provide answer: \textbf{false}.
+Next one should also memorize the presence of \textbf{pink circle} and move to next Frame.
+Analogically, in \textbf{Frame 2} there are both objects present, both with different colors, so the answer is once again \textbf{false}.
+Besides, from that point we do not care anymore about the \textbf{pink circle} and remember the presence of \textbf{yellow circle} instead.
+This is of utmost importance for the following two frames, as there are no circles down there at all.
+So when analyzing \textbf{Frames 3} and \textbf{4} one need to recall the \textbf{yellow circle} from the memory and compare its color with the color of \textbf{u}'s -- as in both cases they are yellow, thus  both answers should be \textbf{true}.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 1"}
+	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
+	\label{fig:frame-2-step-1}
+\end{figure}
+
+As full step-by-step analysis would significantly exceed the page limits, we have cherry picked three steps of reasoning performed by our SAMNet model.
+Let us start from \textbf{1}-st reasoning step on Frame \textbf{2}, as visualized in \cref{fig:frame-2-step-1}.
+First thing worth noting is that there is already an object stored in memory address 1 (write head is always pointing at "free memory slot", in this case the 2nd slot seems to be partially "polluted" by the object from slot 1).
+Second, the attention over both the question and image is clearly focusing over \textbf{u} -- despite we have never trained the system with "word \textbf{u}"-"visual object \textbf{u}" pairs, the SAM Network managed to develop visual grounding on its own.
+Third, the time context is clearly focused on \text{Now} -- once again, during the training we have never indicated that the system should pay attention to this (or any other) particular word and the system learned to catch that context on its own (i.e.
+learned to use the provided mechanisms in the correct way).
+
+\begin{figure}[!h]
+\centering
+  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+\caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
+\label{fig:frame-2-step-6}
+\end{figure}
+
+Next let us analyze \textbf{6}-th reasoning step presented~\cref{fig:frame-2-step-6}.
+At that point the system focuses its attention on the second object important from the point of view of the question: \textbf{yellow circle}.
+Analogically, the question and visual attention are almost perfectly aligned with the word and object, and, besides, the system caught that the time context of the object is \textbf{Latest}.
+Additionally, the "Add New" gate is on, the memory address 2 has a different content and write head moved to the next address -- sadly in here we also observe the "pollution" of addresses 3 and 4.
+But despite that, those are still clear indicators that the system has stored the \textbf{yellow circle} in the external memory.
+
 \begin{figure}[!h]
@@
 
-Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
-as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
-and the temporal classification is ``latest'', there
-is no valid visual attention.
+Let us now fast-forward to analogical reasoning steps in Frame \textbf{6}.
+In the \textbf{1}-st reasoning step (\cref{fig:frame-4-step-1}) we can once again that  system correctly grounded visual object and temporal context.
+
 \begin{figure}[!h]
@@
 
-But in Step 6 of processing Frame 2 (see~\cref{fig:frame-2-step-6}), 
 we see that the object representing the circle is where the attention is.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
-	\caption{State of SAMNet in a particular reasoning step} 
-	\label{fig:frame-2-step-6}
-\end{figure}
 Moreover, the ``Add New`` gate value is high enough that the valid object representing
@@
 correct prediction.
+
+In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
+is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
+
+Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
+as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
+and the temporal classification is ``latest'', there
+is no valid visual attention.
+
+Summarizing, the system has learned to reason using neural representations similarly as a human would operate on abstract symbols when solving the same task, including objects that are memorized and recalled from the memory.

### 2019-09-20 2019_neurips_kr2ml/experiments.tex
experiments more or less done

--- 2019-09-19 2019_neurips_kr2ml/experiments.tex
@@
 In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested exclusively on the Hard variant.
-In summary, the results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
-One other strength of SAMNet is its interpretability.
-Observing attention maps (see Appendix) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
-It also accurately classifies temporal contexts as designed.
-However we notice that the model can sometime discover alternative strategies that were not in the intended design but the answers are still correct.
-More details are given in the Appendix.
 
@@
   \centering
-\caption{The video-question pair selected for analysis.} 
-\label{fig:frame-seq}  
+\caption{A sample from the COG dataset selected for the following analysis.} 
+\label{fig:example}  
 \end{figure}
 
-SAMNet gives the correct answer for this example and we can interpret its reasoning process via a movie that we can generate.
-The key steps in that reasoning process are shown below. Working backwards, the following shows what happens in the key steps
-of the reasoning process.
-In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
-is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
+\subsection{Analysis of the reasoning strategy}
+As a result of training the SAMNet developed a quite complex reasoning strategy.
+We will illustrate the key reasoning steps taken by the model on the example presented in \cref{fig:example}.
+We have decided to pick the sample from the "AndCompareColor" task, as, despite the clear improvement over the COG baseline model, our SAMNet model seems to still struggle with those type of questions.
+
+First, let us analyze, independently of SAMNet, what are the key operations that one would need to perform in order to provide the correct answers. 
+As the question concerns both the \textbf{now} and \textbf{latest} temporal contexts, in the Frame \textbf{1} one should look for both \textbf{u} and \textbf{circle} objects, look at their colors (different), and provide the answer \textbf{false}.
+Next, one should also memorize the \textbf{pink circle} and move to next Frame.
+Analogically, in Frame \textbf{2} there are both objects present, both with different colors, so the answer is once again \textbf{false}.
+However, from that point we do not care anymore about the \textbf{pink circle} and should remember the \textbf{yellow circle} instead.
+This is of utmost importance for the following two frames, as there are no circles present there.
+So when analyzing Frames \textbf{3} and \textbf{4} one need to recall the \textbf{yellow circle} from the memory and compare its color with the color of \textbf{u}'s -- as in both cases they are yellow, thus  both answers should be \textbf{true}.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 1"}
+	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
+	\label{fig:frame-2-step-1}
+\end{figure}
+
+As full step-by-step analysis (8 reasoning steps for each of 4 frames) would significantly exceed the page limits, we have cherry picked four steps of reasoning performed by our SAMNet model.
+Let us start from \textbf{1}-st reasoning step on Frame \textbf{2}, as visualized in \cref{fig:frame-2-step-1} and focus on different aspects of the model.
+First, the attention over both the question and image is clearly focusing over the \textbf{u} -- despite we have never trained the system with "word \textbf{u}"-"visual object \textbf{u}" pairs, the SAM Network managed to develop visual grounding on its own.
+Second, the time context is clearly focused on \text{Now} -- once again, during the training we have never instructed that the system should pay attention to this (or any other) particular word and the system learned to catch the temporal context on its own (i.e.
+learned to use the provided mechanisms in the correct way).
+Third, as write head is always pointing at "free memory slot", we can notice that there is an object already stored in memory under address 1.
+This is the \textbf{pink circle} object memorized during the analysis of the Frame \textbf{1}.
+However, we can also notice that the 2nd slot seems to be partially "polluted" by the object from slot 1, which indicates that the write head was not perfectly focused on a single memory address (similarly to the current state).
+
+\begin{figure}[!h]
+\centering
+  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+\caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
+\label{fig:frame-2-step-6}
+\end{figure}
+
+Next, let us analyze the \textbf{6}-th reasoning step presented~\cref{fig:frame-2-step-6}.
+Here the system clearly focuses its attention on the second object important from the point of view of the question: the \textbf{yellow circle}.
+Analogically, the question and visual attention are almost perfectly aligned with the word and object, and, besides, the system  properly caught the time context of the object: \textbf{Latest}.
+Additionally, the "Add New" gate is on, the memory address 2 has a different content and write head moved to the next address.
+Those are clear indicators that the system has stored the \textbf{yellow circle} in the external memory.
+Sadly, also  in here we observe the "pollution" of addresses 3 and 4.
+
 \begin{figure}[!h]
@@
 
-Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
-as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
-and the temporal classification is ``latest'', there
-is no valid visual attention.
+Let us now fast-forward to analogical reasoning steps in Frame \textbf{6}.
+In the \textbf{1}-st reasoning step (\cref{fig:frame-4-step-1}) we can once again observe that  system correctly grounded the visual object \textbf{u} and detected the correct temporal context \textbf{Now}.
+Besides that, we can notice that memory content remained more or less unchanged, despite the fact that write head shifted to the next memory address (it also became more soft, pointing at addresses 4 and 5).
+
 \begin{figure}[!h]
@@
 
-But in Step 6 of processing Frame 2 (see~\cref{fig:frame-2-step-6}), 
-we see that the object representing the circle is where the attention is.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
-	\caption{State of SAMNet in a particular reasoning step} 
-	\label{fig:frame-2-step-6}
-\end{figure}
-Moreover, the ``Add New`` gate value is high enough that the valid object representing
-the visual encoding of the circle is stored in memory. Note that this is not perfect:
-this value should have been close to 1 but the model is still able to use it for 
-correct prediction.
+In \textbf{6}-th reasoning step (\cref{fig:frame-4-step-6}) there are several things worth discussing.
+First, question attention is pointing at the word \textbf{circle}, but the visual attention is clearly avoiding all the objects. 
+This is because there is no circle.
+However, as the system properly identified the temporal context as \textbf{Latest}, instead of using the visual object, it uses the object retrieved from the memory -- please notice that the read head, despite not being perfectly crisp, is pointing at addresses 3-5, where it previously stored the \textbf{yellow circle} during the analysis of Frame \textbf{2}.
+Moreover, the ``Add New`` gate value is high enough so it once again updates the memory, with void object. 
+But please notice that the content of those memory addresses is negligible, and at the end the SAMNet model is still able return the correct prediction.

### 2019-09-20 2019_neurips_kr2ml/summary.tex
experiments more or less done

--- 2019-09-18 2019_neurips_vigil/experiments.tex
@@
-\section{Experiments}
+\section{Conclusions}
 
-We evaluated SAMNet on the COG dataset~\cite{yang2018dataset}.
-Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
-For this purpose, we used two different variants of the COG dataset: an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
-The main differences are the number of frames in the input sequence (4 vs. 8) and the maximum number of distractors (i.e., objects not relevant for the answer) per frame (1 vs. 10).
-%More details on the dataset, its variants and tasks can be found in the Appendix.
-
-%
-%We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
-We also use the exact same training parameters detailed in the original paper.
-%
-%On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
-We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
-We trained  SAMNet using 8 reasoning steps SAMCells and a hidden state size of 128.
-The external memory has 128-bit slots.
-We trained our model until convergence but we also have set a training time limit of 80 hours.
-
-\begin{figure}[htbp]
-	\centering
-  \begin{subfigure}{\textwidth}
-    \includegraphics[width=0.92\textwidth]{results/samnet_cog_orig_canonical_no_labels.png}
-  \end{subfigure}%
-  \newline
-  \begin{subfigure}{\textwidth}
-	\includegraphics[width=0.93\textwidth]{results/samnet_cog_orig_hard.png}
-  \end{subfigure}%
-\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-\label{fig:samnet_cog_detailed}
-\end{figure}
-
-\begin{wrapfigure}{r}{0.45\textwidth}
-	\centering
-	\includegraphics[width=0.45\textwidth]{results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
-	\label{fig:samnet_cog_overall_transfer}
-\end{wrapfigure}
-
-We have implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
-In our experiments, we have focused on 22 classification tasks and compared our results with the baseline model, as presented in \cref{fig:samnet_cog_detailed}.
-For the Canonical variant (top row), we have achieved similar accuracies for the majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
-Despite there are some tasks in which our model reached slightly lower accuracies,
-% (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
-
-The goal of the next set of experiments was to test the generalization ability concerning the sequence length and number of distractors.
-For that purpose, we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
-As the original paper does not include such experiments, we have performed them on our own.
-The light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have trained (fine-tuning/testing) using the original code provided by the authors.
-For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning.
-In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
-We have also tested both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
-In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested exclusively on the Hard variant.
 In summary, the results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
@@
 
-%we used the canonical (easy) and hard settings that alter the number of distractors and sequence length.
-Since there was no baseline for these tests (train on canonical, test on hard), we ran our own experiments using the COG model provided by the authors.
-SAMNet achieves the highest overall scores for all categories of experiments (\cref{fig:samnet_cog_overall_transfer}), especially for the tests run on the hard dataset.
-Among the 22 classification tasks, we highlighted the two most difficult tasks that affect the overall score.
-%We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence. 
-%The mechanisms introduced in SAMCell learn to operate independently of the total number of frames and allow to generalize to longer video lengths.
-%As shown in \cref{fig:samnet_cog_overall_transfer}, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
-Therefore, the memory is updated efficiently instead of storing all information across all frames.
+Summarizing, the system has learned to reason using neural representations similarly as a human would operate on abstract symbols when solving the same task, including objects that are memorized and recalled from the memory.

### 2019-09-20 2019_neurips_kr2ml/experiments.tex
summary, paragraph about MANNs and compositional reasoning

@@
 In here, we have focused on 22 classification tasks and compared our results with the baseline model.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}, whereas full comparison is presented in \cref{tab:results-full}.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}, whereas full comparison with all accuracies can be found in the table in the Appendix.
 
@@
 when comparing performances on the Hard variant, it dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
-
-\begin{table}[t!]
-\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~
-	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
-\centering
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{lcccccccccc}
-	\toprule
-	Model & & SAMNet & && && COG&& \\
-	\cmidrule{2-5} \cmidrule{7-11} 
-	&&&&& & paper & ours & ours & paper&\\
-	\cmidrule{7-9} \cmidrule{10-11}
-	Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
-	Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
-	Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
-	\midrule
-
-	Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\
-
-	\midrule
-
-	AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
-	AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
-	AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
-	AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
-	CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
-	CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
-	Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
-	ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
-	ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
-	ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
-	ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
-	ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
-	ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
-	ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
-	ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
-	ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
-	ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
-	GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
-	GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
-	GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
-	GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
-	SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
-	SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
-	\bottomrule
-\end{tabular}
-\end{adjustbox}
-\label{tab:results-full}
-\end{table}
 
@@
 \captionsetup[subfigure]{labelformat=empty}
-\begin{figure}[!b]
+\begin{figure}[htbp]
   \begin{center}
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 1"}
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 2 Step 1"}
 	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
@@
 \centering
-  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+  \includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
 \caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
 	\caption{State of SAMNet in a particular reasoning step} 
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
 	\caption{State of SAMNet in a particular reasoning step} 

### 2019-09-20 2019_neurips_kr2ml/summary.tex
summary, paragraph about MANNs and compositional reasoning

@@
 
-In summary, the results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
-One other strength of SAMNet is its interpretability.
-Observing attention maps (see Appendix) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
-It also accurately classifies temporal contexts as designed.
-However we notice that the model can sometime discover alternative strategies that were not in the intended design but the answers are still correct.
-More details are given in the Appendix.
+In this paper we have introduced a novel Memory-Augmented Neural Network model called SAMNet.
+SAMNet was designed with the goal of learning reasoning over video sequences and answering the questions on the content of the frames.
+When applied to the COG video reasoning dataset, the model achieved over-performed the baseline model, showing significant improvements on the Hard variant of the dataset.
+The results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
 
-Summarizing, the system has learned to reason using neural representations similarly as a human would operate on abstract symbols when solving the same task, including objects that are memorized and recalled from the memory.
+One other strengths of SAMNet is its interpretability.
+Observing attention maps shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended. 
+Despite being trained only on image-question pairs with complex, compositional questions, SAMNet clearly learned to associate visual symbols with words and accurately classify temporal contexts as designed.
+Besides, when the system has learned to reason using neural representations similarly as a human would operate on abstract symbols when solving the same task, including memorizing and recalling symbols (object embeddings) from the memory when needed.
+
+Despite the model clearly is not storing all objects present in the scene, sometimes it is not working in a way that we intended when designing the gating and reasoning mechanisms.
+We have cherry-picked a sample from the "AndCompareColor" task that the model seems to be struggling (when looking at pure accuracies).
+Despite in the example all answers were still correct, we have observed that the model seems to struggle with the utilization of the memory in the correct way, that sometimes results in adding the same object under two or more addresses or adding "void" objects.
+This indicates at least two directions for possible further improvements.
+First is fixing content-based addressing with masking, similarly to the improvements to addressing in DNC proposed in~\cite{csordas2019improved}.
+Second is using variable number of reasoning steps instead of hard-coded 8 steps.
+One of the possible solutions to that problem is incorporation of Adaptive Computation Time (ACT)~\cite{graves2016adaptive}.

### 2019-09-20 2019_neurips_kr2ml/summary.tex

--- 2019-09-20 2019_neurips_kr2ml/summary.tex
@@
 
-In summary, the results clearly indicate that the mechanisms introduced in SAMNet  enable it to learn to operate independently of the total number of frames or number of distractions, and allow it to generalize to longer videos and more complex scenes.
-One other strength of SAMNet is its interpretability.
-Observing attention maps (see Appendix) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
-It also accurately classifies temporal contexts as designed.
-However we notice that the model can sometime discover alternative strategies that were not in the intended design but the answers are still correct.
-More details are given in the Appendix.
+In this paper we have introduced a novel Memory-Augmented Neural Network model called SAMNet.
+SAMNet was designed with the goal of learning to reason over video sequences and to answer questions about the content of the frames.
+When applied to the COG video reasoning dataset, the model outperformed the baseline model, showing significant improvements on the Hard variant of the dataset.
+The results indicate that the mechanisms introduced in SAMNet  enable it to operate independent of the total number of frames or the number of distractions, and allow it to generalize to longer videos and more complex scenes.
 
-Summarizing, the system has learned to reason using neural representations similarly as a human would operate on abstract symbols when solving the same task, including objects that are memorized and recalled from the memory.
+Another strength of SAMNet is its interpretability.
+Observing attention maps shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended. 
+Despite being trained only on image-question pairs with complex, compositional questions, SAMNet clearly learned to associate visual symbols with words and accurately classify temporal contexts as designed.
+Besides, the model's reasoning using neural representations appears to be similar to how a human would operate on abstract symbols when solving the same task, including memorizing and recalling symbols (object embeddings) from the memory when needed.
+
+Even though the model is not storing all objects present in the scene, sometimes it is not working in the way we intended with the gating and reasoning mechanisms.
+We have hand-picked a sample from the "AndCompareColor" task that the model seems to be struggling (based on accuracy).
+Despite giving correct answers, we have observed that the model seems to struggle with the utilization of the memory in the intended way, which sometimes results in adding the same object under two or more addresses or adding "void" objects.
+This indicates at least two directions for possible further improvements.
+First is ameliorating content-based addressing with masking, similar to the improvements made for DNC proposed by ~\cite{csordas2019improved}.
+Second is implementing variable number of reasoning steps instead of hard-coded 8 steps, which could utilize Adaptive Computation Time (ACT)~\cite{graves2016adaptive}.

### 2019-09-20 2019_neurips_kr2ml/experiments.tex
Epoch 7 hard-na-hard

@@
 	\midrule
-	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 500016? \\	
-	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 500016? \\
+	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 500016 \\	
+	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 500016 \\
 	\bottomrule	
@@
   \begin{subfigure}{0.25\textwidth}
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 1"}
 	\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{false}}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2"}
 	\caption{Frame: \textbf{2}\newline Ground Truth: \textbf{false}}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 3"}
 	\caption{Frame: \textbf{3}\newline Ground Truth: \textbf{true}}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4"}
 	\caption{Frame: \textbf{4}\newline Ground Truth: \textbf{true}}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 2 Step 1"}
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 1"}
 	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
@@
 \centering
-  \includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+  \includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 6"}
 \caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
-	\caption{State of SAMNet in a particular reasoning step} 
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 1"}
+	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 4.} 
 	\label{fig:frame-4-step-1}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
-	\caption{State of SAMNet in a particular reasoning step} 
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 6"}
+	\caption{State of the SAM Cell after 6-th step of reasoning on Frame 4.} 
 	\label{fig:frame-4-step-6}

### 2019-09-20 2019_neurips_kr2ml/experiments.tex
Copied reasoning to appendix

--- 2019-09-20 2019_neurips_kr2ml/experiments.tex
@@
 	\midrule
-	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 500016? \\	
-	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 500016? \\
+	Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
+	Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
 	\bottomrule	
@@
 In here, we have focused on 22 classification tasks and compared our results with the baseline model.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}, whereas full comparison is presented in \cref{tab:results-full}.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}, whereas full comparison with all accuracies can be found in~\cref{tab:all-results} at the end of the section.
 
@@
 
-\begin{table}[t!]
-\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~
+\subsection{Generalization capabilities}
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\centering
+	\includegraphics[width=0.5\textwidth]{../results/samnet_cog_overall_transfer.png}
+	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\label{fig:samnet_cog_overall_transfer}
+\end{wrapfigure}
+
+The goal of the next set of experiments was to test the generalization ability concerning the sequence length and number of distractors.
+For that purpose, we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
+As the original paper does not include such experiments, we have performed them on our own.
+The light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have trained (fine-tuning/testing) using the original code provided by the authors.
+For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning.
+In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
+We have also tested both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
+In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested exclusively on the Hard variant.
+
+\begin{table}[htb]
+	\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
 		while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
@@
 	\end{adjustbox}
-\label{tab:results-full}
+	\label{tab:all-results}
 \end{table}
-
-\subsection{Generalization capabilities}
-
-\begin{wrapfigure}{r}{0.5\textwidth}
-	\centering
-	\includegraphics[width=0.5\textwidth]{../results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
-	\label{fig:samnet_cog_overall_transfer}
-\end{wrapfigure}
-
-The goal of the next set of experiments was to test the generalization ability concerning the sequence length and number of distractors.
-For that purpose, we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
-As the original paper does not include such experiments, we have performed them on our own.
-The light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have trained (fine-tuning/testing) using the original code provided by the authors.
-For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning.
-In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
-We have also tested both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
-In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested exclusively on the Hard variant.
 
@@
 
-\subsection{Analysis of the reasoning strategy}
-As a result of training the SAMNet developed a quite complex reasoning strategy.
-We will illustrate the key reasoning steps taken by the model on the example presented in \cref{fig:example}.
+\subsection{Illustrating the multi-step reasoning and grounding of concepts including time}
+To illustrate the reasoning strategy developed by SAMNet including the grounding of concepts, we consider the example
+presented in \cref{fig:example}. For more details on this example, please see~
 We have decided to pick the sample from the "AndCompareColor" task, as, despite the clear improvement over the COG baseline model, our SAMNet model seems to still struggle with those type of questions.
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 1"}
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 1"}
 	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
@@
 \centering
-  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+  \includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 6"}
 \caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
-	\caption{State of SAMNet in a particular reasoning step} 
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 1"}
+	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 4.} 
 	\label{fig:frame-4-step-1}
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
-	\caption{State of SAMNet in a particular reasoning step} 
+	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 6"}
+	\caption{State of the SAM Cell after 6-th step of reasoning on Frame 4.} 
 	\label{fig:frame-4-step-6}

### 2019-09-20 2019_neurips_kr2ml/experiments.tex
Rearranged main body of paper.

@@
 
+\subsection{Illustrating the multi-step reasoning and grounding of concepts including time}
+
+To illustrate the reasoning strategy developed by SAMNet including the grounding of concepts, we consider the example
+of \textbf{CompareColor} presented in \cref{fig:example}. 
+As a full step-by-step analysis (8 reasoning steps for each of 4 frames) would be tedious, we picked the four key steps
+of reasoning performed by SAMNet for the same example that are important for Frame~\textbf{4}.
+For more details on this example, please see~\cref{sec:append}.
+
 \captionsetup[subfigure]{labelformat=empty}
@@
 
-\subsection{Illustrating the multi-step reasoning and grounding of concepts including time}
-To illustrate the reasoning strategy developed by SAMNet including the grounding of concepts, we consider the example
-presented in \cref{fig:example}. For more details on this example, please see~
-We have decided to pick the sample from the "AndCompareColor" task, as, despite the clear improvement over the COG baseline model, our SAMNet model seems to still struggle with those type of questions.
-
-First, let us analyze, independently of SAMNet, what are the key operations that one would need to perform in order to provide the correct answers. 
-As the question concerns both the \textbf{now} and \textbf{latest} temporal contexts, in the Frame \textbf{1} one should look for both \textbf{u} and \textbf{circle} objects, look at their colors (different), and provide the answer \textbf{false}.
-Next, one should also memorize the \textbf{pink circle} and move to next Frame.
-Analogically, in Frame \textbf{2} there are both objects present, both with different colors, so the answer is once again \textbf{false}.
-However, from that point we do not care anymore about the \textbf{pink circle} and should remember the \textbf{yellow circle} instead.
-This is of utmost importance for the following two frames, as there are no circles present there.
-So when analyzing Frames \textbf{3} and \textbf{4} one need to recall the \textbf{yellow circle} from the memory and compare its color with the color of \textbf{u}'s -- as in both cases they are yellow, thus  both answers should be \textbf{true}.
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 1"}
-	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
-	\label{fig:frame-2-step-1}
-\end{figure}
-
-As full step-by-step analysis (8 reasoning steps for each of 4 frames) would significantly exceed the page limits, we have cherry picked four steps of reasoning performed by our SAMNet model.
-Let us start from \textbf{1}-st reasoning step on Frame \textbf{2}, as visualized in \cref{fig:frame-2-step-1} and focus on different aspects of the model.
-First, the attention over both the question and image is clearly focusing over the \textbf{u} -- despite we have never trained the system with "word \textbf{u}"-"visual object \textbf{u}" pairs, the SAM Network managed to develop visual grounding on its own.
-Second, the time context is clearly focused on \text{Now} -- once again, during the training we have never instructed that the system should pay attention to this (or any other) particular word and the system learned to catch the temporal context on its own (i.e.
-learned to use the provided mechanisms in the correct way).
-Third, as write head is always pointing at "free memory slot", we can notice that there is an object already stored in memory under address 1.
-This is the \textbf{pink circle} object memorized during the analysis of the Frame \textbf{1}.
-However, we can also notice that the 2nd slot seems to be partially "polluted" by the object from slot 1, which indicates that the write head was not perfectly focused on a single memory address (similarly to the current state).
-
+First, we analyze the \textbf{6}-th reasoning step of Frame~\textbf{2}, presented~\cref{fig:frame-2-step-6}.
+Here the system clearly focuses its attention on the second object important from the point of view of the question: the \textbf{yellow circle}.
+Analogously, the question and visual attention are almost perfectly aligned with the word and object, besides, 
+the system does a decent job of capturing the time context \textbf{Latest} of the object.
+Finally, the ``Add New'' gate is on, indicating that the system has stored the \textbf{yellow circle} in external memory.
 \begin{figure}[!h]
@@
 
-Next, let us analyze the \textbf{6}-th reasoning step presented~\cref{fig:frame-2-step-6}.
-Here the system clearly focuses its attention on the second object important from the point of view of the question: the \textbf{yellow circle}.
-Analogically, the question and visual attention are almost perfectly aligned with the word and object, and, besides, the system  properly caught the time context of the object: \textbf{Latest}.
-Additionally, the "Add New" gate is on, the memory address 2 has a different content and write head moved to the next address.
-Those are clear indicators that the system has stored the \textbf{yellow circle} in the external memory.
-Sadly, also  in here we observe the "pollution" of addresses 3 and 4.
-
+Next, in the \textbf{1}-st reasoning step of Frame~\textbf{4}, presented in~\cref{fig:frame-4-step-1}, 
+we can once again observe that  system correctly grounded the visual object \textbf{u} and detected the most likely temporal context \textbf{Now} (still not extremely high indicating that the distinction may not be significant for this example).
+Besides that, we can notice that memory content remained more or less unchanged.
 \begin{figure}[!h]
@@
 
-Let us now fast-forward to analogical reasoning steps in Frame \textbf{6}.
-In the \textbf{1}-st reasoning step (\cref{fig:frame-4-step-1}) we can once again observe that  system correctly grounded the visual object \textbf{u} and detected the correct temporal context \textbf{Now}.
-Besides that, we can notice that memory content remained more or less unchanged, despite the fact that write head shifted to the next memory address (it also became more soft, pointing at addresses 4 and 5).
+In \textbf{6}-th reasoning step (\cref{fig:frame-4-step-6}) there are several things worth discussing.
+First, question attention is pointing at the word \textbf{circle}, but the visual attention is clearly avoiding all the objects. 
+This is because there is no circle.
+However, as the system properly identified the temporal context as \textbf{Latest}, instead of using the visual object, it uses the object retrieved from the memory---notice that the read head, despite not being perfectly crisp, is pointing at addresses 3-5, where it previously stored the \textbf{yellow circle} during the analysis of Frame \textbf{2}.
+Moreover, the ``Add New`` gate value is high enough so it once again updates the memory, with a void object. 
+(This would have been considered for future frames if they were to be present. 
+Because the content of those memory addresses is negligible, SAMNet  will still able return the correct prediction).
 
@@
 \end{figure}
-
-In \textbf{6}-th reasoning step (\cref{fig:frame-4-step-6}) there are several things worth discussing.
-First, question attention is pointing at the word \textbf{circle}, but the visual attention is clearly avoiding all the objects. 
-This is because there is no circle.
-However, as the system properly identified the temporal context as \textbf{Latest}, instead of using the visual object, it uses the object retrieved from the memory -- please notice that the read head, despite not being perfectly crisp, is pointing at addresses 3-5, where it previously stored the \textbf{yellow circle} during the analysis of Frame \textbf{2}.
-Moreover, the ``Add New`` gate value is high enough so it once again updates the memory, with void object. 
-But please notice that the content of those memory addresses is negligible, and at the end the SAMNet model is still able return the correct prediction.

### 2019-09-20 2019_neurips_kr2ml/summary.tex
Rearranged main body of paper.

@@
 The results indicate that the mechanisms introduced in SAMNet  enable it to operate independent of the total number of frames or the number of distractions, and allow it to generalize to longer videos and more complex scenes.
-
-Another strength of SAMNet is its interpretability.
 Observing attention maps shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended. 
-Despite being trained only on image-question pairs with complex, compositional questions, SAMNet clearly learned to associate visual symbols with words and accurately classify temporal contexts as designed.
+Despite being trained only on image-question pairs with complex, compositional questions, SAMNet clearly learns
+to associate visual symbols with words and accurately classify temporal contexts as designed.
 Besides, the model's reasoning using neural representations appears to be similar to how a human would operate on abstract symbols when solving the same task, including memorizing and recalling symbols (object embeddings) from the memory when needed.
-
-Even though the model is not storing all objects present in the scene, sometimes it is not working in the way we intended with the gating and reasoning mechanisms.
-We have hand-picked a sample from the "AndCompareColor" task that the model seems to be struggling (based on accuracy).
-Despite giving correct answers, we have observed that the model seems to struggle with the utilization of the memory in the intended way, which sometimes results in adding the same object under two or more addresses or adding "void" objects.
+This is not perfect however and the system can sometimes store spurious objects despite the gating and reasoning mechanisms,
+but still give correct answers.
 This indicates at least two directions for possible further improvements.
-First is ameliorating content-based addressing with masking, similar to the improvements made for DNC proposed by ~\cite{csordas2019improved}.
-Second is implementing variable number of reasoning steps instead of hard-coded 8 steps, which could utilize Adaptive Computation Time (ACT)~\cite{graves2016adaptive}.
+The first is to ameliorate content-based addressing with masking, similar to the improvements made for DNC proposed by ~\cite{csordas2019improved}.
+Second is to implement variable number of reasoning steps, instead of hard-coded 8 steps, which could utilize Adaptive Computation Time (ACT)~\cite{graves2016adaptive}.

### 2019-10-21 2019_neurips_kr2ml/appendix.tex

\appendix

\section{More details on the reasoning strategy}
\label{sec:append}

\captionsetup[subfigure]{labelformat=empty}
\begin{figure}[htbp]
	\begin{center}
		Question: \textbf{Does color of u now equal the color of the latest circle?}
	\end{center}
	\vskip -0.4cm
	\null\hfill
	\begin{subfigure}{0.25\textwidth}
		\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 1"}
		\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{false}}
		\label{fig:frame-1}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.25\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2"}
		\caption{Frame: \textbf{2}\newline Ground Truth: \textbf{false}}
		\label{fig:frame-2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.25\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 3"}
		\caption{Frame: \textbf{3}\newline Ground Truth: \textbf{true}}
		\label{fig:frame-3}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.25\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4"}
		\caption{Frame: \textbf{4}\newline Ground Truth: \textbf{true}}
		\label{fig:frame-4}
	\end{subfigure}%
	\hfill\null
	\newline
	\centering
	\caption{A sample from the COG dataset selected for the following analysis.} 
	\label{fig:example-app}  
\end{figure}

As a result of training the SAMNet developed a quite complex reasoning strategy.
We will illustrate the key reasoning steps taken by the model on the example presented in \cref{fig:example-app}.
We have decided to pick the sample from the \textbf{CompareColor} task.

First, let us analyze, independently of SAMNet, what are the key operations that one would need to perform in order to provide the correct answers. 
As the question concerns both the \textbf{now} and \textbf{latest} temporal contexts, in the Frame \textbf{1} one should look for both \textbf{u} and \textbf{circle} objects, look at their colors (different), and provide the answer \textbf{false}.
Next, one should also memorize the \textbf{pink circle} and move to next Frame.
Analogically, in Frame \textbf{2} there are both objects present, both with different colors, so the answer is once again \textbf{false}.
However, from that point we do not care anymore about the \textbf{pink circle} and should remember the \textbf{yellow circle} instead.
This is of utmost importance for the following two frames, as there are no circles present there.
So when analyzing Frames \textbf{3} and \textbf{4} one need to recall the \textbf{yellow circle} from the memory and compare its color with the color of \textbf{u}'s -- as in both cases they are yellow, thus  both answers should be \textbf{true}.

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 1"}
	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
	\label{fig:frame-2-step-1-app}
\end{figure}

As full step-by-step analysis (8 reasoning steps for each of 4 frames) would significantly exceed the page limits, we have cherry picked four steps of reasoning performed by our SAMNet model.
Let us start from \textbf{1}-st reasoning step on Frame \textbf{2}, as visualized in \cref{fig:frame-2-step-1-app} and focus on different aspects of the model.
First, the attention over both the question and image is clearly focusing over the \textbf{u} -- despite we have never trained the system with "word \textbf{u}"-"visual object \textbf{u}" pairs, the SAM Network managed to develop visual grounding on its own.
Second, the time context is clearly focused on \text{Now} -- once again, during the training we have never instructed that the system should pay attention to this (or any other) particular word and the system learned to catch the temporal context on its own (i.e. learned to use the provided mechanisms in the correct way).
Third, as write head is always pointing at "free memory slot", we can notice that there is an object already stored in memory under address 1.
This is the \textbf{pink circle} object memorized during the analysis of the Frame \textbf{1}.
However, we can also notice that the 2nd slot seems to be partially "polluted" by the object from slot 1, which indicates that the write head was not perfectly focused on a single memory address (similarly to the current state).

\begin{figure}[!h]
\centering
  \includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 6"}
\caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
\label{fig:frame-2-step-6-app}
\end{figure}

Next, let us analyze the \textbf{6}-th reasoning step presented~\cref{fig:frame-2-step-6-app}.
Here the system clearly focuses its attention on the second object important from the point of view of the question: the \textbf{yellow circle}.
Analogically, the question and visual attention are almost perfectly aligned with the word and object, and, besides, the system  properly caught the time context of the object: \textbf{Latest}.
Additionally, the "Add New" gate is on, the memory address 2 has a different content and write head moved to the next address.
Those are clear indicators that the system has stored the \textbf{yellow circle} in the external memory.
Sadly, also  in here we observe the "pollution" of addresses 3 and 4.

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 1"}
	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 4.} 
	\label{fig:frame-4-step-1-app}
\end{figure}

Let us now fast-forward to analogical reasoning steps in Frame \textbf{6}.
In the \textbf{1}-st reasoning step (\cref{fig:frame-4-step-1-app}) we can once again observe that  system correctly grounded the visual object \textbf{u} and detected the correct temporal context \textbf{Now}.
Besides that, we can notice that memory content remained more or less unchanged, despite the fact that write head shifted to the next memory address (it also became more soft, pointing at addresses 4 and 5).

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 6"}
	\caption{State of the SAM Cell after 6-th step of reasoning on Frame 4.} 
	\label{fig:frame-4-step-6-app}
\end{figure}

In \textbf{6}-th reasoning step (\cref{fig:frame-4-step-6-app}) there are several things worth discussing.
First, question attention is pointing at the word \textbf{circle}, but the visual attention is clearly avoiding all the objects. 
This is because there is no circle.
However, as the system properly identified the temporal context as \textbf{Latest}, instead of using the visual object, it uses the object retrieved from the memory -- please notice that the read head, despite not being perfectly crisp, is pointing at addresses 3-5, where it previously stored the \textbf{yellow circle} during the analysis of Frame \textbf{2}.
Moreover, the ``Add New`` gate value is high enough so it once again updates the memory, with void object. 
But please notice that the content of those memory addresses is negligible, and at the end the SAMNet model is still able return the correct prediction.

### 2019-10-21 2019_neurips_kr2ml/model.tex
KR2ML - start
work in progress - experiments
work on experiments, changed figure placement

--- 2019-09-18 2019_neurips_vigil/model.tex
@@
 
-\begin{wrapfigure}{r}{0.80\textwidth}
+\begin{figure}[b!]
 	\centering
-	\includegraphics[width=0.78\textwidth]{../img/architecture/samnet_architecture4}
+	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
 	\caption{General architecture of SAMNet}
 	\label{fig:samnet}
-\end{wrapfigure}
-
-%\begin{figure}[hbtp]
-%	\centering
-%	\includegraphics[width=0.7\textwidth]{../img/architecture/samnet_architecture4}
-%	\caption{General architecture of SAMNet}
-%	\label{fig:samnet}
-%\end{figure}
+\end{figure}
 
 SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}).
-The model makes a single pass over the frames in temporal order, accessing one frame at a time.
+At the conceptual level SAMNet draws from two core ideas:
+compositional reasoning as proposed e.g. in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer}
+and utilization of external memory in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
+
+A distinctive feature of the SAM Network is that it makes a single pass over the frames in temporal order, accessing one frame at a time.
 The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video. 
@@
 in order to perform multi-step spatio-temporal reasoning over text and video.  
-%A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
-%testing to fit the characteristics of data.
+A notable feature of this design is that the number of addresses $N$ can be set to different values during training and testing to fit the characteristics of data.
 
-\begin{wrapfigure}{r}{0.8\textwidth}
+\begin{figure}[t!]
 	\centering
-	\includegraphics[width=0.78\textwidth]{../img/architecture/samcell_reasoning}
+	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
 	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
 	\label{fig:samcell}
-\end{wrapfigure}
-
-%\begin{figure}[hbtp]
-%	\centering
-%	\includegraphics[width=0.7\textwidth]{../img/architecture/samcell_reasoning}
-%	\caption{Single reasoning step in SAMCell}
-%	\label{fig:samcell}
-%\end{figure}
+\end{figure}
 
@@
 
-For details of the modules not covered here, please see the appendix.
+%For details of the modules not covered here, please see the appendix.

### 2019-10-21 2019_neurips_vigil/appendix_model.tex

@@
 \centering
-\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
+\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 1"}
 \label{fig:frame-1}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2"}
 	\label{fig:frame-1}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 3"}
 	\label{fig:frame-1}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
+	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4"}
 		\label{fig:frame-1}
@@
 \centering
-  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
+  \includegraphics[width=\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 1"}
 \caption{State of SAMNet in a particular reasoning step} 
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
+	\includegraphics[width=\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 6"}
 	\caption{State of SAMNet in a particular reasoning step} 
@@
 	\centering
-	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
+	\includegraphics[width=\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 6"}
 	\caption{State of SAMNet in a particular reasoning step} 

### 2019-10-21 COG_publications/2019_neurips_kr2ml/intro.tex
Move COG publications files into subdir

--- 2019-09-19 2019_neurips_kr2ml/intro.tex
@@
 Working memory and episodic memory systems are responsible for this remarkable ability.
-In this paper we focus on Visual Reasoning, however, however, instead of enabling the system to access all input frames at every reasoning step, we decided to follow a totally different, nevertheless more natural approach.
+In this paper we focus on Visual Reasoning, however, instead of enabling the system to access all input frames at every reasoning step, we decided to follow a totally different, nevertheless more natural approach.
 Inspired by human cognitive capacity to selectively pay attention and store salient information in memory,
-we introduce a new model that can dynamically processes video input frame-by-frame, reasons over a given image and remembers the salient concepts to answer questions.
+we introduce a new model that can dynamically processes video input frame-by-frame, reasons over a given image and remembers the salient concepts required for answering the questions.
 Our results based on the COG dataset \cite{yang2018dataset} indicate that the model is capable of:

### 2019-10-21 2018_nips_vigil/conclusion.tex

@@
 \section{Conclusion}
-We have introduced SMAC, a simplified version on the MAC model.
-Our version proposes simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model.
-As a result we could decrease training time by more than two hours ( reduction by almost 10 \%)
-while maintaining an equivalent test accuracy. 
-We have also evaluated generalization capabilities of MAC and S-MAC on the CLEVR CoGenT dataset.
-The results of our experiments first show that MAC and SMAC perform equally well on all the CoGenT task. Thus the simplifications did not alter SMAC generalization capability.
-Furthermore, MAC and SMAC compare favorably with state-of-the-art models on the CoGenT taks. MAC and SMAC present competitive generalization and transfer learning capacities.
-Nevertheless, CLEVR CoGenT remains an unsolved problem.
-The MAC model still struggles to learn distinct concepts.
-We could see that MAC sometimes fail to differentiate colors and shape as two distinct features of the same object.
+We have introduced S-MAC, a simplified variant of the MAC model.
+Because it has nearly half the number of parameters in the recurrent portion MAC cell, it trains faster while maintaining an equivalent test accuracy.
+
+Our experiments on zero-short learning show that the MAC model has poor performance in line with the other models in the literature.
+Thus, this remains an interesting problem to investigate how we can train it to disentangle the concepts of shape and color.
+
+With fine-tuning, the MAC model indeed achieves much improved performance, matching state of the art.
+However, we have showed that correlation between the different domains must be taken into account when fine-tuning, otherwise potentially leading to decreased performance.

### 2019-10-21 arxiv/experiments.tex
polishing

@@
 The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
-\tableref{results} presents the most important results, focusing on S-MAC in particular; see Appendix~\ref{sec:full_comparison} for the entire set.
+\tableref{tab:results} presents the most important results, focusing on S-MAC in particular; see Appendix~\ref{sec:full_comparison} for the entire set.
 
@@
 	\end{tabular}
-	\label{results}
+	\label{tab:results}
 \end{table}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_shape.png}
+	\includegraphics[width=\textwidth]{\dir/img/fail_mac_cogent_b_shape.png}
 	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_color.png}
+	\includegraphics[width=\textwidth]{\dir/img/fail_mac_cogent_b_color.png}
 	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}

### 2019-10-21 MAC_publications/2018_nips_vigil/introduction.tex
Move MAC publications files into subdir

--- 2018-11-15 arxiv/introduction.tex
@@
 One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations.
+For details, see Appendix~A (all appendices are in the supplementary material).
 
 One of the most recent exciting models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\cite{hudson2018compositional}, which performs a sequence of attention-based reasoning operations.
-though the performance of MAC has been proven, several questions arise:
+Although the performance of MAC has been proven, several questions arise:
 Does the model really learn relations between objects? 
@@
 Last, we illustrate using CoGenT-B that, without adequate care, fine-tuning can actually reduce a model's accuracy.
-
-The paper is organized as follows.
-In \sec{datasets} we delve into details of both CLEVR and CoGenT datasets, emphasizing their differences.
-Next, in \sec{models} we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
-\sec{experiments} discusses the most important results of using transfer learning 
-on CLEVR and on both versions of CoGenT.
-\sec{transfer_learning} focuses on a cherry-picked subset of experiments to highlight our findings; 
-see~Appendix~\ref{sec:full_comparison} for the complete set of results comparing MAC and S-MAC models when training/fine-tuning/testing on various datasets.
-In \sec{failures} we show examples supporting hypothesis on the lack of disentanglement of concepts in both models.
-\sec{comparison} presents results obtained by other state-of-the-art models, and discusses the challenges faced  
-with their reproducibility. 
-\sec{conclusion} concludes the paper.

### 2019-10-21 MAC_publications/2018_nips_vigil/mac.tex
Move MAC publications files into subdir

--- 2018-11-01 2018_nips_vigil/mac.tex
@@
 	\centering
-	\includegraphics[width=\textwidth]{img/mac_cell.pdf}
-	\caption{The MAC cell, reproduced on the basis of~\cite{hudson2018compositional}}
+	\includegraphics[width=\textwidth]{../img/mac_cell.pdf}
+	\caption{The MAC cell, reproduced on the basis of~\cite{hudson2018compositional}.}
 	\label{fig:mac_cell}
@@
 The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
-Besides, the input unit utilizes a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.
+Additionally, the input unit uses a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.
 

### 2019-10-21 MAC_publications/2018_nips_vigil/smac.tex
Move MAC publications files into subdir

--- 2018-11-02 2018_nips_vigil/smac.tex
@@
 
+\begin{table}[!t]
+	\centering
+	\begin{tabular}{ccccCcCc}
+		\toprule
+		Model        & Read Unit               & Write Unit &  Control Unit         \\
+		\midrule
+		MAC   &  787,969 &  524,800        &    525,313    \\
+		%\midrule
+		simplified MAC & 263,168  & 262,656       &    263,168 \\
+		\midrule
+		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
+		\bottomrule
+	\end{tabular}
+	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
+	\label{tab:parameters}
+\end{table}
+
 %Applying this principle to 
@@
 
+\noindent\textit{Notation.}
+%Let $q$ denote the global context of the question
+%and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
+For each knowledge base $\kb$ of dimension $H \times W \times d$, let $\kb_{hw}$ be the $d$-dimensional vector indexed by 
+$h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
+Let $i$ denote the index (position) $i$ of the reasoning step.
+
 In the description below, the original MAC cell equations are shown on the \emph{left}
@@
 The equation numbering is the same as in~\cite{hudson2018compositional}.
-
-\noindent\textit{Notation.}
-%Let $q$ denote the global context of the question
-%and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
-For each knowledge base $\kb$, a tensor of dimension $H \times W \times d$, let $\kb_{hw}$ be the $d$-dimensional vector indexed by 
-$h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
-Let $i$ denote the index (position) $i$ of the reasoning step.
 
@@
 
-\begin{table}[hb]
-	\centering
-	\begin{tabular}{ccccCcCc}
-		\toprule
-		Model        & Read Unit               & Write Unit &  Control Unit         \\
-		\midrule
-		MAC   &  787,969 &  524,800        &    525,313    \\
-		%\midrule
-		simplified MAC & 263,168  & 262,656       &    263,168 \\
-		\midrule
-		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
-		\bottomrule
-	\end{tabular}
-	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells. }
-	\label{tab:parameters}
-\end{table}
-
-\newpage
+\vskip -0.6cm
 
@@
 	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
-	&\mem_i = W_{rm}^{[d \times d]} \rr_i + b_{rm}^{[d]} \tag{w1}
+	&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
 	\end{align*}}

### 2019-10-21 MAC_publications/2018_nips_vigil_poster/main.tex
Move MAC publications files into subdir

--- 2018-11-29 2018_nips_vigil_poster/main.tex
@@
 	\compresslist
-	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
-	\item[$\bullet$] We evaluate the MAC model and the simplified variant on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
-	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can reduce a model's accuracy.
+	\item We introduce a \emph{\textbf{simplified}} variant of the MAC (Memory,  Attention,
+	and Composition) model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
+	\item We evaluate both the original MAC model and the simplified variant on CLEVR \& CoGenT datasets, and show that \emph{\textbf{transfer learning with fine-tuning}} results in a \emph{\textbf{15 point increase}} in accuracy, matching the state of the art.
+	\item We also demonstrate that \emph{\textbf{improper}} fine-tuning can \emph{\textbf{reduce a model's accuracy}}.
 
@@
 
-\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=mac-model, column=0, below=contributions}{
-	\vspace{-10pt}
+\headerbox{The MAC model~\cite{hudson2018compositional}}{name=mac-model, column=0, below=contributions}{
+\textbf{MAC network}: a recurrent neural network performing sequential reasoning. At each step, it analyzes the question and shifts the attention over the image.
+	\vspace{-3pt}
 	\begin{figure}[H]
 		\centering
-		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
-		\caption{The MAC cell, based on~\cite{hudson2018compositional}.}
+		\includegraphics[width=0.4\textwidth]{../img/mac_cell.pdf}
+		\caption{\textbf{MAC cell} consists of a control unit, a read unit \& a write unit.}
 		\label{fig:mac_cell}
@@
 	\compresslist
-		\item[$\bullet$] MAC network: a recurrent model performing sequential reasoning. At each step, it analyzes the question and shifts the attention over the image.
-		\item[$\bullet$] Recurrent MAC cell: consists of a control unit, a read unit \& a write unit. The control unit updates the control state $c_i$ \& drives the attention over the question words.
-		\item[$\bullet$] The read unit, guided by $c_i$ extracts information from the image. The write unit uses this information to update the memory state $m_i$.
+		\item \textbf{Control unit} updates the control state $c_i$ \& shifts the attention over question words.
+		\item \textbf{Read unit}, guided by $c_i$, extracts information from the image.
+		\item \textbf{Write unit} uses this information to update the memory state $m_i$.
 	\end{itemize}
@@
 
-\headerbox{Simplified MAC Model (S-MAC)}{name=s-mac, column=0, below=mac-model}{
+\headerbox{The Simplified MAC model (S-MAC)}{name=s-mac, column=0, below=mac-model}{
 
@@
 		\compresslist
-	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no non-linear activation in-between) can be combined as one linear layer.
-		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
+	    \item Taking the MAC cell equations as a whole, all consecutive linear layers (with no non-linear activation in-between) can be combined into a single linear layer.
+		\item We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
+		\item[$\Rightarrow$] This allows, with a careful reorganization, to apply a single linear layer to the \textit{knowledge base} (feature map extracted from the image) prior to all the reasoning steps and work with this projection throughout the reasoning steps.
 \end{itemize}
-
-	This allows, with a careful reorganization, to apply a single linear layer to the \textit{knowledge base} (feature map extracted from the image) prior to all the reasoning steps and work with this projection throughout the reasoning steps.\\
 
@@
 	\centering
-	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
+	\caption{Comparison of numbers of position-independent parameters between MAC \& S-MAC cells.}
 	\begin{tabular}{llll}
@@
 		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
-		\caption{\textbf{Q}: \textit{How many objects are either small cylinders or red things?} -- \textbf{A}: 5.}
+		\caption{\textbf{Q}: \textit{How many objects are either small cylinders or red things?} \textbf{A}: 5.}
 		\label{fig:clevr_task}
@@
 	  	\compresslist
-	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
-	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
+	  	\item The authors of CLEVR~\cite{johnson2017clevr} also introduced a variant called CLEVR-CoGenT, aiming at evaluation of how well models can learn compositional concepts.
+	  	\item Similar to CLEVR, but with two conditions, as follows:
 	\end{itemize}
@@
 
-\headerbox{Experiments \& Results}{name=experiments, column=1, below=datasets}{
+\headerbox{Experiments \& results}{name=experiments, column=1, below=datasets}{
 	\vspace{-10pt}
@@
 	\compresslist
-	\item[$\bullet$] Our experiments on \emph{zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) show that both models have poor performance, in line with
+	\item Our experiments on \emph{zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) show that both models have poor performance, in line with
 	the other models in the literature.
-	\item[$\bullet$] With fine-tuning, both MAC models match state-of-the-art accuracy (a 15pts increase).
-	\item[$\bullet$] \textbf{S-MAC presents a 10\% speed-up in training time and comparable accuracy.}
-	\item[$\bullet$] Finetuning CLEVR-trained models on CoGenT-A or -B hurts their generalization capabilities.
-	\item[$\rightarrow$] \emph{Zero-shot learning} remains an interesting problem to solve.
+	\item With fine-tuning, both MAC models match state-of-the-art accuracy (a 15pts increase).
+	\item \textbf{S-MAC presents a 10\% speed-up in training time and comparable accuracy.}
+	\item Finetuning CLEVR-trained models on CoGenT-A or -B hurts their generalization capabilities.
+	\item[$\Rightarrow$] \emph{Zero-shot learning} remains an interesting problem to solve.
 \end{itemize}
@@
 		\compresslist
-		\item[$\bullet$] Asked about the shape of the leftmost \textbf{gray cylinder}, the model correctly finds it, (cf.
+		\item Asked about the shape of the leftmost \textbf{gray cylinder}, the model correctly finds it, (cf.
 \emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
-		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \textbf{gray cylinders} during training, but saw \textbf{gray cubes}.
-		\item[$\rightarrow$] This indicates that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
+		\item As it never saw \textbf{gray cylinders} during training, whereas learned the \textbf{gray cubes} compositional concept, the model predicts the shape as a \textbf{cube}.
+		\item[$\Rightarrow$] This indicates that MAC does not separate shape from color, but has a better understanding of color cues (as it found the object by its color).
 	\end{itemize}

### 2019-10-21 MAC_publications/arxiv/smac.tex
Move MAC publications files into subdir

--- 2018-11-02 2018_nips_vigil/smac.tex
@@
 
+\noindent\textit{Notation.}
+%Let $q$ denote the global context of the question
+%and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
+For each knowledge base $\kb$ of dimension $H \times W \times d$, let $\kb_{hw}$ be the $d$-dimensional vector indexed by 
+$h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
+Let $i$ denote the index of the reasoning steps.
+
 In the description below, the original MAC cell equations are shown on the \emph{left}
@@
 
-\begin{table}[hb]
-	\centering
-	\begin{tabular}{ccccCcCc}
-		\toprule
-		Model        & Read Unit               & Write Unit &  Control Unit         \\
-		\midrule
-		MAC   &  787,969 &  524,800        &    525,313    \\
-		%\midrule
-		simplified MAC & 263,168  & 262,656       &    263,168 \\
-		\midrule
-		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
-		\bottomrule
-	\end{tabular}
-	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells. }
-	\label{tab:parameters}
-\end{table}
-
-\newpage
-
+\vskip -0.6cm
 \noindent\textbf{Read and write units:}
@@
 	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
-	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
+	&\mem_i = W_{rm}^{[d \times 2d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
 	\end{align*}
@@
 However, since the computation time is also dominated by the position-aware layers in the control unit, as well as the input unit, the speedup is not as large as we desire.
+
+\begin{table}[!t]
+	\centering
+	\begin{tabular}{ccccCcCc}
+		\toprule
+		Model        & Read Unit               & Write Unit &  Control Unit         \\
+		\midrule
+		MAC   &  787,969 &  524,800        &    525,313    \\
+		%\midrule
+		simplified MAC & 263,168  & 262,656       &    263,168 \\
+		\midrule
+		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
+		\bottomrule
+	\end{tabular}
+	\caption{Comparison of the number of position-independent parameters in MAC \& S-MAC cells.}
+	\label{tab:parameters}
+\end{table}

### 2019-11-05 COG_publications/2019_neurips_kr2ml/experiments.tex
Camera ready versions of kr2ml and vigil

--- 2019-09-20 2019_neurips_kr2ml/experiments.tex
@@
 
-\begin{figure}[htbp]
+\begin{figure}[!t]
 	\centering
@@
 As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
-Despite there are some tasks in which our model reached slightly lower accuracies,
+Despite there being some tasks in which our model reached slightly lower accuracies,
 % (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
+when comparing performances on the Hard variant, it improves upon the COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
 
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{figure}[!b]
 	\centering
-	\includegraphics[width=0.5\textwidth]{../results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.75\textwidth]{../results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
 	\label{fig:samnet_cog_overall_transfer}
-\end{wrapfigure}
+\end{figure}
 

### 2019-11-05 COG_publications/2019_neurips_kr2ml/intro.tex
Camera ready versions of kr2ml and vigil

--- 2019-09-19 2019_neurips_kr2ml/intro.tex
@@
 Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
-Potentially, this approach can address Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} and lead to visually grounded language learning.
+Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.
 
@@
 Working memory and episodic memory systems are responsible for this remarkable ability.
-In this paper we focus on Visual Reasoning, however, however, instead of enabling the system to access all input frames at every reasoning step, we decided to follow a totally different, nevertheless more natural approach.
-Inspired by human cognitive capacity to selectively pay attention and store salient information in memory,
-we introduce a new model that can dynamically processes video input frame-by-frame, reasons over a given image and remembers the salient concepts to answer questions.
-Our results based on the COG dataset \cite{yang2018dataset} indicate that the model is capable of:
-(1) learning the temporal association, i.e., grounding the time-related words with meaning;
+In this paper, we introduce a new model for visual reasoning that can dynamically process video input frame-by-frame, reason over each frame and store the salient concepts in memory so as to order to answer questions.
+Our experiments based on the COG dataset \cite{yang2018dataset} indicate that the model can:
+(1) form temporal associations, i.e., grounding the time-related words with meaning;
 %\item Learning the concept of time
@@
 %\end{itemize}
-(2) learning complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes;
+(2) learn complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes;
 (3) selectively control the flow of information to and from the memory to answer questions; and
-(4) updating the memory only with relevant visual information depending on the temporal context.
+(4) update the memory only with relevant visual information depending on the temporal context.
 %\begin{itemize}

### 2019-11-05 COG_publications/2019_neurips_kr2ml/model.tex
Camera ready versions of kr2ml and vigil

--- 2019-10-21 2019_neurips_kr2ml/model.tex
@@
 During the $t$-th reasoning step, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
-(a) $c_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
-(b) $so_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
-Let $M_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
+(a) $\vec{c}_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
+(b) $\vec{so}_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
+Let $\vec{M}_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
 Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
@@
 This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
-The control state $c_t$ at step $t$ is then fed to a \emph{temporal classifier}, 
+The control state $\vec{c}_t$ at step $t$ is then fed to a \emph{temporal classifier}, 
 a two-layer feedforward network with ELU activation used in the hidden layer of $d$ units.
-The output $\tau_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
+The output $\vec{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
 For the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
 
-The visual retrieval unit uses the information generated above to extract a relevant object $vo_t$ from the frame.
-A similar operation on memory yields the object $mo_t$. The memory operation is based on an attention mechanism,
+The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
+A similar operation on memory yields the object $\vec{mo}_t$. The memory operation is based on an attention mechanism,
 and resembles content-based addressing on memory. Therefore, we obtain an attention vector over memory addresses
@@
 Note that the returned objects may be invalid, 
-e.g., if the current reasoning step focuses on the phrase ``last red square'', $vo_t$ is invalid 
+e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid 
 even if the current frame contains a red square.
@@
 To determine whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
-First, we take the visual attention vector $va_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
+First, we take the visual attention vector $\vec{va}_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
 and compute a simple aggregate\footnote{%
 	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.}: %
-$vs_t = \sum_{i=1}^L [va_t(i)]^2$. It can be shown mathematically that the more localized the attention
+$vs_t = \sum_{i=1}^L [\vec{va}_t(i)]^2$. It can be shown that the more localized the attention
 vector is, the higher is the aggregate value.
-We perform a similar computation on the read head $rh_t$ over memory locations.
-We feed these two values along with the temporal class weights $\tau_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
+We perform a similar computation on the read head $\rhead_t$ over memory locations.
+We feed these two values along with the temporal class weights $\vec{\tau}_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
 in $[0,1]$ modulated for the current reasoning step:
@@
 Unit first determines the memory location where an object could be added:
-\[ w_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
-Above, $w_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
-The sum of components of $w$ is at most equal to 1; and $w_t$ can even equal 0 whenever neither condition
+\[ \vec{w}_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
+Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
+The sum of components of $\vec{w}_t$ is at most equal to 1; and $\vec{w}_t$ can even equal 0, e.g., whenever neither condition
 of adding a new object nor replacing an existing object holds true.
 We then update the memory accordingly as:
-\[ M_t = M_{t-1} \odot (J - w_t \otimes \mathbf{1}) + w_t \otimes vo_t,\]
-where $vo_t$ denotes the object returned by the visual retrieval unit. 
-Here $J$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product. 
-Note that the memory is unchanged in the case where $w_t = 0$, i.e., $M_t = M_{t-1}$.
+\[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t,\]
+where $\vec{vo}_t$ denotes the object returned by the visual retrieval unit. 
+Here $\vec{J}$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product. 
+Note that the memory is unchanged in the case where $\vec{w}_t = 0$, i.e., $\vec{M}_t = \vec{M}_{t-1}$.
 We finally update the write head so that it points to the succeeding address if an object was added to memory or otherwise stay the same.
@@
 This unit updates the (recurrent) summary object to equal the outcome of the $t$-th reasoning step.
-We first determine whether the relevant object $ro_t$ should be obtained from memory or the frame according to:
-\[ ro_t = \imatch_t \cdot vo_t + \mmatch_t \cdot mo_t \]
-Note that $ro_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
-Finally, $so_t$ is the output of a simple linear layer whose inputs are $ro_t$ and the previous summary object $so_{t-1}$.
-This serves to retain additional information that was in $so_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
+We first determine whether the relevant object $\vec{ro}_t$ should be obtained from memory or the frame according to:
+\[ \vec{ro}_t = \imatch_t \cdot \vec{vo}_t + \mmatch_t \cdot \vec{mo}_t \]
+Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
+Finally, $\vec{so}_t$ is the output of a simple linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
+This serves to retain additional information that was in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
 

### 2019-11-05 COG_publications/2019_neurips_vigil/appendix_model.tex
Camera ready versions of kr2ml and vigil

--- 2019-10-21 2019_neurips_vigil/appendix_model.tex
@@
-\section{Appendix}
+\section{Supplementary Material}
 
-\subsection{VWM model}
-
-\begin{notation}
-	Treat 1D tensors as column vectors and 2D tensors as matrices, where appropriate.
-	We use lower case to represent both 1D and 2D tensors but occasionally use upper case
-	for 2D tensors where matrix operations are involved.
-
-	\begin{enumerate}
-		\item Let 
-		$\Delta^d = \{ (x_0, x_1, \dots, x_d) : x_0 + x_1 + \dots + x_d = 1, x_i \ge 0, i = 0, 1, \dots, d\}$ denote the standard $d$-simplex.
-
-		\item  Let $\circ$ denote concatenation of two tensors with identical shape except possibly
-		for their last dimensions $d_1$ and $d_2$, respectively,  
-		resulting in a tensor with last dimension of $d_1+d_2$.
-
-		\item Let $\odot$ denote  element-wise product of two tensors of same shape,
-		i.e., Hadamard product for vectors/matrices.
-
-		\item Let $\otimes$ denote tensor product of two tensors, 
-		i.e. Kronecker product for vectors/matrices.
-	\end{enumerate}
-\end{notation}
-
-\subsection{Basic layers/modules}
-
-\colorbx{Linear (Affine) Layer}
-
-\begin{description}
-	\item[Inputs:] A tensor $x$ with last dimension $n$.
-	\item[Parameter:] An affine function $\cG: \Reals^n \to \Reals^m$ with 
-	weight and bias parameters.
-
-	\item[Output:] A tensor $y$ with last dimension $m$, and remaining dimensions
-	same as that of $x$, obtained by applying $\cG$ to each 1D slice of $x$
-	along the last dimension.
-\end{description}
-
-\colorbx{Attention Module}
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Query: $q \in \Reals^d$
-		\item Keys: $K \in \Reals^{N \times d}$	
-		\item Values: $V \in \Reals^{N \times d}$. By default $V=K$, unless mentioned explicitly.	
-	\end{enumerate}
-
-	\item[Parameter:] Weight $w \in \Reals^d$
-
-	\item[Outputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Content vector: $h =  V^{\T} u \in \Reals^d$
-		\item Attention vector:  $w = \softmax(K(w \odot q)) \in \Reals^N$
-	\end{enumerate}
-\end{description}
-
-\colorbx{Interaction Module}
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Base object: $b \in \Reals^d$
-		\item Feature objects: $f \in \Reals^{M \times d}$	
-	\end{enumerate}
-
-	\item[Parameters:] 
-	\begin{enumerate}
-		\item[]
-		\item Base object projection linear layer: $\cG: \Reals^d \to \Reals^d$
-		\item Feature objects projection linear layer : $\cK: \Reals^{M \times d} \to \Reals^{M \times d}$
-		\item Modifier linear layer:  $\cH: \Reals^{M \times 2d} \to \Reals^{M \times d}$	
-	\end{enumerate}
-
-	\item[Output:] Modified feature objects 
-	$f' =  \cH( \cK(f) \odot ( \vone \otimes \cG(b))) \in  \Reals^{M \times d}$
-\end{description}
-
-\hrulefill
-
-\subsection{VWM cell}
-
-The VWM recurrent cell is executed for $T$ reasoning steps for every frame in
-the temporal order.  Within a single frame, the cell state at the end of each reasoning step 
-$t=1,2, \dots, T$ is denoted by $(c_t, M_t, o_t)$, where: 
-\begin{enumerate}
-	\item $c_t \in \Reals^d$ is the control state;
-	\item $M_t \in  \Reals^{N \times d}$ is the visual working memory with $N$ slots;
-	\item $w_t \in  \Reals^N$ is the write head; and
-	\item $so_t  \in \Reals^d$ is the summary visual object.
-\end{enumerate} 
-The initial state is such that both $c_0$ and $so_0$ are initialized
-to a fixed value at the start of each frame. However $M_0$ is initialized only once at
-the start of the first frame and otherwise taken to be the value of $M_T$ at the
-end of the previous frame.
-
-%The number of slots $N$ for the VWM $M_t$ is not fixed because the neural network 
-%parameters do not depend on it. It can be variable across the different datasets used
-%for training, validation and test as well as within each dataset. This, for example, enables a 
-%form of transfer learning where we can train on an easy dataset for one value of $N$
-%and study its generalization to a hard dataset using a larger value of $N$.
-
-\colorbx{Question-driven Controller}
-
-%The Question-driven Controller plays an important role in the reasoning process.
-%It drives the attention over the question and produces the new control states.
+%
+%\subsection{VWM model}
+%
+%\begin{notation}
+%	Treat 1D tensors as column vectors and 2D tensors as matrices, where appropriate.
+%	We use lower case to represent both 1D and 2D tensors but occasionally use upper case
+%	for 2D tensors where matrix operations are involved.
+%	
+%	\begin{enumerate}
+%		\item Let 
+%		$\Delta^d = \{ (x_0, x_1, \dots, x_d) : x_0 + x_1 + \dots + x_d = 1, x_i \ge 0, i = 0, 1, \dots, d\}$ denote the standard $d$-simplex.	
+%		
+%		\item  Let $\circ$ denote concatenation of two tensors with identical shape except possibly
+%		for their last dimensions $d_1$ and $d_2$, respectively,  
+%		resulting in a tensor with last dimension of $d_1+d_2$. 
+%		
+%		\item Let $\odot$ denote  element-wise product of two tensors of same shape,
+%		i.e., Hadamard product for vectors/matrices.
+%		
+%		\item Let $\otimes$ denote tensor product of two tensors, 
+%		i.e. Kronecker product for vectors/matrices.
+%	\end{enumerate}
+%\end{notation}	
+%
+%\subsection{Basic layers/modules}
+%
+%\colorbx{Linear (Affine) Layer}
+%
+%\begin{description}
+%	\item[Inputs:] A tensor $x$ with last dimension $n$.
+%	\item[Parameter:] An affine function $\cG: \Reals^n \to \Reals^m$ with 
+%	weight and bias parameters.
+%	
+%	\item[Output:] A tensor $y$ with last dimension $m$, and remaining dimensions
+%	same as that of $x$, obtained by applying $\cG$ to each 1D slice of $x$
+%	along the last dimension.
+%\end{description}
+%
+%
+%\colorbx{Attention Module}
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Query: $q \in \Reals^d$
+%		\item Keys: $K \in \Reals^{N \times d}$	
+%		\item Values: $V \in \Reals^{N \times d}$. By default $V=K$, unless mentioned explicitly.	
+%	\end{enumerate}
+%	
+%	\item[Parameter:] Weight $w \in \Reals^d$
+%	
+%	\item[Outputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Content vector: $h =  V^{\T} u \in \Reals^d$
+%		\item Attention vector:  $w = \softmax(K(w \odot q)) \in \Reals^N$
+%	\end{enumerate}
+%\end{description}
+%
+%
+%\colorbx{Interaction Module}
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Base object: $b \in \Reals^d$
+%		\item Feature objects: $f \in \Reals^{M \times d}$	
+%	\end{enumerate}
+%	
+%	\item[Parameters:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Base object projection linear layer: $\cG: \Reals^d \to \Reals^d$
+%		\item Feature objects projection linear layer : $\cK: \Reals^{M \times d} \to \Reals^{M \times d}$
+%		\item Modifier linear layer:  $\cH: \Reals^{M \times 2d} \to \Reals^{M \times d}$	
+%	\end{enumerate}
+%	
+%	\item[Output:] Modified feature objects 
+%	$f' =  \cH( \cK(f) \odot ( \vone \otimes \cG(b))) \in  \Reals^{M \times d}$
+%\end{description}
+%
+%\hrulefill
+%
+%\subsection{VWM cell}
+%
+%The VWM recurrent cell is executed for $T$ reasoning steps for every frame in
+%the temporal order.  Within a single frame, the cell state at the end of each reasoning step 
+%$t=1,2, \dots, T$ is denoted by $(c_t, M_t, o_t)$, where: 
+%\begin{enumerate}
+%	\item $\vec{c}_t \in \Reals^d$ is the control state;
+%	\item $\vec{M}_t \in  \Reals^{N \times d}$ is the visual working memory with $N$ slots;
+%	\item $\vec{w}_t \in  \Reals^N$ is the write head; and
+%	\item $\vec{so}_t  \in \Reals^d$ is the summary visual object.
+%\end{enumerate} 
+%The initial state is such that both $\vec{c}_0$ and $\vec{so}_0$ are initialized
+%to a fixed value at the start of each frame. However $\vec{M}_0$ is initialized only once at
+%the start of the first frame and otherwise taken to be the value of $\vec{M}_T$ at the
+%end of the previous frame.
+%
+%%The number of slots $N$ for the VWM $M_t$ is not fixed because the neural network 
+%%parameters do not depend on it. It can be variable across the different datasets used
+%%for training, validation and test as well as within each dataset. This, for example, enables a 
+%%form of transfer learning where we can train on an easy dataset for one value of $N$
+%%and study its generalization to a hard dataset using a larger value of $N$.
+%
+%\colorbx{Question-driven Controller}
+%
+%%The Question-driven Controller plays an important role in the reasoning process.
+%%It drives the attention over the question and produces the new control states.
 Each new control state defines a new reasoning operation.
@@
 It uses the dot product attention between the contextual words
-%and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
+%%and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
+%%
+%%This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
 %
-%This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Reasoning step $t = 1,2, \dots, T$
-		\item Previous control state: $c_{t-1} \in \Reals^d$	
-		\item Contextual words: $cw \in \Reals^{L \times d}$
-		\item Question encoding: $q \in \Reals^d$
-	\end{enumerate}
-
-	\item[Parameters:] 
-	\begin{enumerate}
-		\item[]
-		\item Reasoning step-dependent linear layer: $\cG_t: \Reals^d \to \Reals^d$, depending on $s$
-		\item Concatenation linear layer: $\cH: \Reals^{2d} \to \Reals^d$
-		\item Attention module $\cA$
-		\item Temporal classifier:  $\cK: \Reals^d \to \Delta^3$. A two-layer feedforward
-		network with ELU activation in the hidden layer of $d$ units.	
-		The classes for the temporal context are labeled ``last'', ``latest'', ``now'', as well as 
-		a fourth class label ``none`` indicating no temporal context.
-		If $\tau \in \Delta^3$ is the output of the classifier, we denote the components by
-		$\tlast$, $\tlatest$, $\tnow$ and $\tnone$.
-	\end{enumerate}
-
-	\item[Outputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Control state $c_t \in \Reals^d$
-		\item Control attention $ca_t \in \Reals^L$
-		\item Temporal class weights $\tau_t \in \Reals^4$
-	\end{enumerate}
-
-	\item[Equations:] 
-	\begin{enumerate}
-		\item[]
-		\item Modulation: $y = \cH\bigl([c_{t-1}, \cG_t(q)]\bigr)$
-		\item Control state and attention: $c_t,  ca_t= \cA(y, cw)$
-		\item Temporal classification: $\tau_t = \cK(c_t)$
-	\end{enumerate}
-\end{description}
-
-\colorbx{Visual Retrieval Unit}
-
-%The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Reasoning step $t = 1,2, \dots, T$
+%		\item Previous control state: $\vec{c}_{t-1} \in \Reals^d$	
+%		\item Contextual words: $\vec{cw} \in \Reals^{L \times d}$
+%		\item Question encoding: $q \in \Reals^d$
+%	\end{enumerate}
+%	
+%	\item[Parameters:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Reasoning step-dependent linear layer: $\cG_t: \Reals^d \to \Reals^d$, depending on $s$
+%		\item Concatenation linear layer: $\cH: \Reals^{2d} \to \Reals^d$
+%		\item Attention module $\cA$
+%		\item Temporal classifier:  $\cK: \Reals^d \to \Delta^3$. A two-layer feedforward
+%		network with ELU activation in the hidden layer of $d$ units.	
+%		The classes for the temporal context are labeled ``last'', ``latest'', ``now'', as well as 
+%		a fourth class label ``none`` indicating no temporal context.
+%		If $\tau \in \Delta^3$ is the output of the classifier, we denote the components by
+%		$\tlast$, $\tlatest$, $\tnow$ and $\tnone$.
+%	\end{enumerate}
+%	
+%	\item[Outputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Control state $\vec{c}_t \in \Reals^d$
+%		\item Control attention $\vec{ca}_t \in \Reals^L$
+%		\item Temporal class weights $\tau_t \in \Reals^4$
+%	\end{enumerate}
+%	
+%	\item[Equations:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Modulation: $y = \cH\bigl([c_{t-1}, \cG_t(q)]\bigr)$
+%		\item Control state and attention: $c_t,  ca_t= \cA(y, cw)$
+%		\item Temporal classification: $\tau_t = \cK(c_t)$
+%	\end{enumerate}
+%\end{description}
+%
+%
+%\colorbx{Visual Retrieval Unit}
+%
+%%The visual retrievial unit is responsible to extract visual information from the current image given a control state coming from the Question-driven Controller.
 It is first projecting the past summary object and the feature maps together using the interaction module.
-%It is then using the attention module as follow.
+%%It is then using the attention module as follow.
 The query are the control states and the keys and are the feature maps coming from the image encoder.
 The results of this attention is applied on the modified features maps coming from the interaction module.
-%This unit outputs the extracted object and the visual attention.
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Control state: $c_t \in \Reals^d$	
-		\item Previous summary object: $so_{t-1} \in \Reals^d$
-		\item Feature map of current frame: $F \in \Reals^{H \times W \times d}$
-	\end{enumerate}
-
-	\item[Parameters:] 
-	\begin{enumerate}
-		\item[]
-		\item Interaction module $\cI$
-		\item Attention module $\cA$
-	\end{enumerate}
-
-	\item[Outputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Visual object: $vo_t \in  \Reals^d$
-		\item Visual attention: $va_t  \in \Reals^{H \times W \times d}$
-	\end{enumerate}
-
-	\item[Equations:]
-	\begin{enumerate}
-		\item[]
-		\item Modified feature map: $\hat{F} = \cI(so_{t-1}, F)$
-		\item Visual object and attention: $vo_t, va_t = \cA(y, \hat{F}, M_{t-1})$
-	\end{enumerate}
-\end{description}
-
-\begin{note}
-	Appropriate flatten/unflatten operations are performed to match the signature 
-	of the modules.
-\end{note}
-
-\colorbx{Memory Retrieval Unit}
-
-%The role of the memory retrieval unit is to read and extract object from memory).
-%As the Visual Retrieval Unit, it uses the combination of the two following submodules.
+%%This unit outputs the extracted object and the visual attention.
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Control state: $c_t \in \Reals^d$	
+%		\item Previous summary object: $so_{t-1} \in \Reals^d$
+%		\item Feature map of current frame: $F \in \Reals^{H \times W \times d}$
+%	\end{enumerate}
+%	
+%	\item[Parameters:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Interaction module $\cI$
+%		\item Attention module $\cA$
+%	\end{enumerate}
+%	
+%	\item[Outputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Visual object: $vo_t \in  \Reals^d$
+%		\item Visual attention: $va_t  \in \Reals^{H \times W \times d}$
+%	\end{enumerate}
+%	
+%	\item[Equations:]
+%	\begin{enumerate}
+%		\item[]
+%		\item Modified feature map: $\hat{F} = \cI(so_{t-1}, F)$
+%		\item Visual object and attention: $vo_t, va_t = \cA(y, \hat{F}, M_{t-1})$
+%	\end{enumerate}
+%\end{description}
+%
+%\begin{note}
+%	Appropriate flatten/unflatten operations are performed to match the signature 
+%	of the modules.
+%\end{note}
+%
+%
+%\colorbx{Memory Retrieval Unit}
+%
+%%The role of the memory retrieval unit is to read and extract object from memory).
+%%As the Visual Retrieval Unit, it uses the combination of the two following submodules.
 The interaction module blends together the extracted object and the content of the memory.
@@
 This unit outputs the extracted object and its corresponding location, we call it the "read head".
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Control state: $c_t \in \Reals^d$	
-		\item Previous summary object: $so_{t-1} \in  \Reals^d$
-		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
-	\end{enumerate}
-
-	\item[Parameters:] 
-	\begin{enumerate}
-		\item[]
-		\item Interaction module $\cI$
-		\item Attention module $\cA$
-	\end{enumerate}
-
-	\item[Outputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Memory object: $mo_t \in \Reals^d$
-		\item Read head: $\rhead_t \in \Reals^N$
-	\end{enumerate}
-
-	\item[Equations:]
-	\begin{enumerate}
-		\item[]
-		\item Modified VWM: $\hat{M}_t = \cI(so_{t-1}, M_{t-1})$
-		\item Memory object and attention: $mo_t, \rhead_t = \cA(y, \hat{M}_t, M_{t-1})$
-	\end{enumerate}
-\end{description}
-
-\colorbx{Reasoning Unit}
-
-%control_state, visual_object, memory_object, temporal_class_weights
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Control state: $c_t \in \Reals^d$
-		\item Visual object: $vo_t \in \Reals^d$
-		\item Memory object: $mo_t \in \Reals^d$
-		\item Temporal class weights $\tau \in \Delta^3$
-	\end{enumerate}
-
-	\item[Parameters:] Validator modules $\cG, \cK: \Reals^{2d} \to \Reals$.
-	Both $\cG, \cK$ are two-layer networks of $2d$ hidden units,
-	using ELU activation in the hidden layer, and sigmoid in the output layer.
-
-	\item[Output:] Predicate gates for the current reasoning step
-	\begin{enumerate}
-		\item Object match predicate gates (i) image: $\imatch_t \in [0,1]$ and 
-		(ii) memory: $\mmatch_t \in [0,1]$.
-
-		\item Memory update predicate gates (i) add: $\doadd_t \in [0,1]$ and
-		(ii) replace: $\doreplace_t \in [0,1]$
-	\end{enumerate}
-
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Control state: $c_t \in \Reals^d$	
+%		\item Previous summary object: $so_{t-1} \in  \Reals^d$
+%		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
+%	\end{enumerate}
+%	
+%	\item[Parameters:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Interaction module $\cI$
+%		\item Attention module $\cA$
+%	\end{enumerate}
+%	
+%	\item[Outputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Memory object: $mo_t \in \Reals^d$
+%		\item Read head: $\rhead_t \in \Reals^N$
+%	\end{enumerate}
+%	
 %	\item[Equations:]
@@
 %		\item[]
-%		\item $\imatch_t \in [0,1]$:
-%		It's true if there is a valid visual object in the current temporal context.
-%		
-%		\item $\mmatch_t \in [0,1]$:
-%		It's true if there is a valid memory object in the current temporal context.
-%		
-%		\item $\doadd_t \in [0,1]$: 
-%		It's true if the current visual object should be added as a new object to memory.
-%		
-%		\item $\doreplace_t \in [0,1]$: 
-%		It's true if the current visual object should replace an existing object in memory.
+%		\item Modified VWM: $\hat{M}_t = \cI(so_{t-1}, M_{t-1})$
+%		\item Memory object and attention: $mo_t, \rhead_t = \cA(y, \hat{M}_t, M_{t-1})$
 %	\end{enumerate}
-\end{description}
-
-\colorbx{Memory Update Unit}
-
-%This unit is meant to update the content of the memory. 
-%
-%Three actions can happen:
-%
-%\begin{itemize}
-%	\item There is no object to be added to memory, the memory remains unchanged
-%	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
-%	
-%	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
-%\end{itemize}
+%\end{description}
 %
 %
-%This module also updates the position of the write head.
+%\colorbx{Reasoning Unit}
+%
+%%control_state, visual_object, memory_object, temporal_class_weights
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Control state: $c_t \in \Reals^d$
+%		\item Visual object: $vo_t \in \Reals^d$
+%		\item Memory object: $mo_t \in \Reals^d$
+%		\item Temporal class weights $\tau \in \Delta^3$
+%	\end{enumerate}
+%	
+%	\item[Parameters:] Validator modules $\cG, \cK: \Reals^{2d} \to \Reals$.
+%	Both $\cG, \cK$ are two-layer networks of $2d$ hidden units,
+%	using ELU activation in the hidden layer, and sigmoid in the output layer.
+%	
+%	\item[Output:] Predicate gates for the current reasoning step
+%	\begin{enumerate}
+%		\item Object match predicate gates (i) image: $\imatch_t \in [0,1]$ and 
+%		(ii) memory: $\mmatch_t \in [0,1]$.
+%		
+%		\item Memory update predicate gates (i) add: $\doadd_t \in [0,1]$ and
+%		(ii) replace: $\doreplace_t \in [0,1]$
+%	\end{enumerate}
+%	
+%%	\item[Equations:]
+%%	\begin{enumerate}
+%%		\item[]
+%%		\item $\imatch_t \in [0,1]$:
+%%		It's true if there is a valid visual object in the current temporal context.
+%%		
+%%		\item $\mmatch_t \in [0,1]$:
+%%		It's true if there is a valid memory object in the current temporal context.
+%%		
+%%		\item $\doadd_t \in [0,1]$: 
+%%		It's true if the current visual object should be added as a new object to memory.
+%%		
+%%		\item $\doreplace_t \in [0,1]$: 
+%%		It's true if the current visual object should replace an existing object in memory.
+%%	\end{enumerate}
+%\end{description}
+%
+%
+%\colorbx{Memory Update Unit}
+%
+%%This unit is meant to update the content of the memory. 
+%%
+%%Three actions can happen:
+%%
+%%\begin{itemize}
+%%	\item There is no object to be added to memory, the memory remains unchanged
+%%	\item There is one object that needs to be added to memory, but a similar object is already in memory at a given location. The new object will replace the old object at this location
+%%	
+%%	\item There is one object that needs to be added to memory, and  it is a new object. It is added at the write head location.
+%%\end{itemize}
+%%
+%%
+%%This module also updates the position of the write head.
 If a new object as been added to the current write head position, the right head shifts right to a new empty slot.
 If the object has been replaced, the write head doesn't move.
-% visual_object, visual_working_memory, read_head, write_head, do_replace, do_add_new
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Visual object: $vo_t \in \Reals^d$
-		\item Memory object: $mo_t \in \Reals^d$
-		\item Memory update predicate gates:  $\doadd_t, \doreplace_t \in [0,1]$
-		\item Read head: $\rhead_t \in \Reals^N$
-		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
-		\item Previous write head: $\whead_{t-1} \in \Reals^N$
-	\end{enumerate}
-
-	\item[Outputs:] 
-	\begin{enumerate}
-		\item[]
-		\item VWM $M_t \in \Reals^{N \times d}$
-		\item Read head: $\rhead_t \in \Reals^N$
-		\item Write head: $\whead_t \in \Reals^N$
-	\end{enumerate}
-
-\end{description}
-
-\colorbx{Summary Object Update Unit}
-
-%The  Summary Unit is the last unit of the SAMCell.
+%% visual_object, visual_working_memory, read_head, write_head, do_replace, do_add_new
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Visual object: $vo_t \in \Reals^d$
+%		\item Memory object: $mo_t \in \Reals^d$
+%		\item Memory update predicate gates:  $\doadd_t, \doreplace_t \in [0,1]$
+%		\item Read head: $\rhead_t \in \Reals^N$
+%		\item Previous VWM $M_{t-1} \in \Reals^{N \times d}$
+%		\item Previous write head: $\whead_{t-1} \in \Reals^N$
+%	\end{enumerate}
+%	
+%	\item[Outputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item VWM $M_t \in \Reals^{N \times d}$
+%		\item Read head: $\rhead_t \in \Reals^N$
+%		\item Write head: $\whead_t \in \Reals^N$
+%	\end{enumerate}
+%	
+%\end{description}
+%
+%
+%
+%\colorbx{Summary Object Update Unit}
+%
+%%The  Summary Unit is the last unit of the SAMCell.
 It is responsible to output the new summary object.
@@
 It is the final step of the SAMCell reasoning cycle.
+%%
+%%The image encoder, question encoder and output unit are described in the appendix.
 %
-%The image encoder, question encoder and output unit are described in the appendix.
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item[]
-		\item Previous summary object: $so_{t-1} \in \Reals^d$
-		\item Visual object: $vo_t \in \Reals^d$
-		\item Memory object: $mo_t \in \Reals^d$
-		\item Object predicate gates: $\imatch_t, \mmatch_t \in [0,1]$
-	\end{enumerate}
-
-	\item[Parameters:] Concatenation linear layer $\cH$
-
-	\item[Output:] 
-	New summary object:
-	$so_t = \cH\bigl([so_{t-1}, (\imatch_t * vo_t + \mmatch_t * mo_t)]\bigr) \in \Reals^d$
-
-\end{description}
-
-\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}
-
-\colorbx{Image Encoder}
-
-\begin{description}
-	\item[Inputs:] 
-	Images
-
-	\item[Output:] 
-	Features maps:
-	$F_k$
-\end{description}
-
-The Image Encoder unit is responsible to preprocess the sequence of images one at the time.
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item[]
+%		\item Previous summary object: $so_{t-1} \in \Reals^d$
+%		\item Visual object: $vo_t \in \Reals^d$
+%		\item Memory object: $mo_t \in \Reals^d$
+%		\item Object predicate gates: $\imatch_t, \mmatch_t \in [0,1]$
+%	\end{enumerate}
+%	
+%	\item[Parameters:] Concatenation linear layer $\cH$ 
+%	
+%	\item[Output:] 
+%	New summary object:
+%	$so_t = \cH\bigl([so_{t-1}, (\imatch_t * vo_t + \mmatch_t * mo_t)]\bigr) \in \Reals^d$ 
+%	
+%\end{description}
+%
+%
+%\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}
+%
+%
+%
+%
+%
+%\colorbx{Image Encoder}
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	Images
+%	
+%	\item[Output:] 
+%	Features maps:
+%	$F_k$
+%\end{description}
+%
+%The Image Encoder unit is responsible to preprocess the sequence of images one at the time.
 It is a 4 layer convolutional neural network.
 Every layer is composed of the following sequence of operations:
-
-\begin{enumerate}
-	\item 2D convolution ($stride=1$) 
-	\item 2D max pooling
-	\item 2D batch normalization
-	\item Relu (only for the first 3 layers)
-\end{enumerate}
-
-The first layer has 3 inputs channels and 32 output channels. Layer 2 has 32 and 64. Layer 3 has 64 and 64. Finally, layer 4 has 64 inputs channels and 128 output channels .
-The resulting tensor (feature maps) are of dimensions [batch size, $H*W =7*7$, $dim$=128].
-
-\colorbx{Question Encoder}
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item question string $question$
-		\item question lengths $question_l$
-
-	\end{enumerate}
-
-	\item[Output:] 
-	\begin{enumerate}
-		\item contextual word embeddingg $cw$
-		\item question encoding $q$
-
-	\end{enumerate}
-
-\end{description}
-
-The strings questions are first embedded ($torch.NN.Embeddings$) and then passed through a $d$-dimensional biLSTM ($d$=128).
-The final hidden state of the biLSTM becomes the question encoding representation $q$.
+%
+%\begin{enumerate}
+%	\item 2D convolution ($stride=1$) 
+%	\item 2D max pooling
+%	\item 2D batch normalization
+%	\item Relu (only for the first 3 layers)
+%\end{enumerate}
+%
+%The first layer has 3 inputs channels and 32 output channels. Layer 2 has 32 and 64. Layer 3 has 64 and 64. Finally, layer 4 has 64 inputs channels and 128 output channels .
+%The resulting tensor (feature maps) are of dimensions [batch size, $H*W =7*7$, $dim$=128]. 
+%
+%
+%\colorbx{Question Encoder}
+%
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item question string $question$
+%		\item question lengths $question_l$
+%		
+%	\end{enumerate}
+%	
+%	
+%	\item[Output:] 
+%	\begin{enumerate}
+%		\item contextual word embeddingg $cw$
+%		\item question encoding $q$
+%		
+%	\end{enumerate}
+%	
+%\end{description}
+%
+%The strings questions are first embedded ($torch.NN.Embeddings$) and then passed through a $d$-dimensional biLSTM ($d$=128).
+%The final hidden state of the biLSTM becomes the question encoding representation $q$.
 Whereas the biLSTM outputs are projected via a linear layer to become the final words encodings named contextual words $cw$.
-
-\colorbx{Output Unit}
-
-\begin{description}
-	\item[Inputs:] 
-	\begin{enumerate}
-		\item question encoding $q$
-		\item summary object $so_t$
-
-	\end{enumerate}
-
-	\item[Output:] 
-	prediction 
-\end{description}
-
-The output unit predicts the final answer to the question.
+%
+%\colorbx{Output Unit}
+%
+%\begin{description}
+%	\item[Inputs:] 
+%	\begin{enumerate}
+%		\item question encoding $q$
+%		\item summary object $so_t$
+%
+%	\end{enumerate}
+%	
+%	
+%	\item[Output:] 
+%	prediction 
+%\end{description}
+%
+%The output unit predicts the final answer to the question.
 It is a 2-linear-layer-ELU classifier that produces a distribution over the possible candidates.
 It is based on two inputs, the final summary object $so_t$ and the question encoding $q$ that are concatenated together.
+%
 
 \subsection{Training and Implementation Details}
-
-\subsubsection{Implementation Details}
 
@@
 
-We compared our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores provided by the authors through personal communications.
+We compared our model to the original COG model~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores provided by the authors through personal communications.
 We used the same training parameters detailed in the original paper and reproduced their results.

### 2019-11-05 COG_publications/2019_neurips_vigil/experiments.tex
Camera ready versions of kr2ml and vigil

--- 2019-10-21 2019_neurips_vigil/experiments.tex
@@
 
-\begin{wrapfigure}{r}{0.45\textwidth}
+\begin{figure}
 	\centering
-	\includegraphics[width=0.45\textwidth]{../results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.75\textwidth]{../results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
 	\label{fig:samnet_cog_overall_transfer}
-\end{wrapfigure}
+\end{figure}
 
@@
 As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
-Despite there are some tasks in which our model reached slightly lower accuracies,
+Despite there being some tasks in which our model reached slightly lower accuracies,
 % (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it dominates COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
+when comparing performances on the Hard variant, it improves upon the  COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
 
@@
 One other strength of SAMNet is its interpretability.
-Observing attention maps (see Appendix) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
+Observing attention maps (see supplementary material) shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
 It also accurately classifies temporal contexts as designed.
 However we notice that the model can sometime discover alternative strategies that were not in the intended design but the answers are still correct.
-More details are given in the Appendix.
 

### 2019-11-05 COG_publications/2019_neurips_vigil/model.tex
Camera ready versions of kr2ml and vigil

--- 2019-11-05 COG_publications/2019_neurips_kr2ml/model.tex
@@
 
-\begin{figure}[b!]
+\begin{figure}[!t]
 	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
+	\includegraphics[width=0.9\textwidth]{../img/architecture/samnet_architecture4}
 	\caption{General architecture of SAMNet}
@@
 
+%\begin{figure}[hbtp]
+%	\centering
+%	\includegraphics[width=0.7\textwidth]{../img/architecture/samnet_architecture4}
+%	\caption{General architecture of SAMNet}
+%	\label{fig:samnet}
+%\end{figure}
+
 SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}).
-At the conceptual level SAMNet draws from two core ideas:
-compositional reasoning as proposed e.g. in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer}
-and utilization of external memory in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
-
-A distinctive feature of the SAM Network is that it makes a single pass over the frames in temporal order, accessing one frame at a time.
+The model makes a single pass over the frames in temporal order, accessing one frame at a time.
 The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video. 
@@
 in order to perform multi-step spatio-temporal reasoning over text and video.  
-A notable feature of this design is that the number of addresses $N$ can be set to different values during training and testing to fit the characteristics of data.
+%A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
+%testing to fit the characteristics of data.
 
-\begin{figure}[t!]
+\begin{figure}[!b]
 	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+	\includegraphics[width=0.9\textwidth]{../img/architecture/samcell_reasoning}
 	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
@@
 \end{figure}
+
+%\begin{figure}[hbtp]
+%	\centering
+%	\includegraphics[width=0.7\textwidth]{../img/architecture/samcell_reasoning}
+%	\caption{Single reasoning step in SAMCell}
+%	\label{fig:samcell}
+%\end{figure}
 
@@
 This serves to retain additional information that was in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
-
-%For details of the modules not covered here, please see the appendix.

### 2019-11-06 cvpr_submission/experiments.tex
Added folder & empty template for cvpr submission.

--- 2019-11-05 COG_publications/2019_neurips_kr2ml/experiments.tex
@@
 
-We have implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
-We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning.
-Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
-For this purpose, we used two different variants of the COG dataset (\cref{tab:cog_variants}): an easy one (Canonical) and a Hard version to explore a wide range of difficulties.
-The main differences are the number of frames in the input sequence (4 vs. 8) and the maximum number of distractors (i.e., objects not relevant for the answer) per a single frame (1 vs. 10).
-
-\begin{table}[htb]
-\caption{Details of the Canonical and Hard variants of the COG dataset}
-\centering
-\begin{tabular}{lcccccc}
-	\toprule
-	Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
-	& of   & memory & number of & of & of & of  \\
-	& frames & duration & distractors & training set & validation set & test set \\
-	\midrule
-	Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
-	Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
-	\bottomrule	
-\end{tabular}
-\label{tab:cog_variants}
-\end{table}
-
-%More details on the dataset, its variants and tasks can be found in the Appendix.
-
-%
-%We compare our model to the original COG model  ~\cite{yang2018dataset} using their implementation (https://github.com/google/cog) and scores given by the authors.
-We also use the exact same training parameters detailed in the original paper.
-%
-%On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018accelerating}, a framework for research based on Pytorch.
-We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs.
-We trained  SAMNet using 8 reasoning steps SAMCells and a hidden state size of 128.
-The external memory has 128-bit slots.
-We trained our model until convergence but we also have set a training time limit of 80 hours.
-
-\subsection{Performance comparison with the COG baseline}
-
-In our experiments we have trained SAMNet using 8 reasoning steps and external memory having 8 address locations, each being a vector of 128 floats.
-We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
-In here, we have focused on 22 classification tasks and compared our results with the baseline model.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}, whereas full comparison with all accuracies can be found in~\cref{tab:all-results} at the end of the section.
-
-\begin{figure}[!t]
-	\centering
-  \begin{subfigure}{\textwidth}
-    \includegraphics[width=0.99\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
-  \end{subfigure}%
-  \newline
-  \begin{subfigure}{\textwidth}
-	\includegraphics[width=\textwidth]{../results/samnet_cog_orig_hard.png}
-  \end{subfigure}%
-\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-\label{fig:samnet_cog_detailed}
-\end{figure}
-
-For the Canonical variant (top row), we have achieved similar accuracies for the majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
-Despite there being some tasks in which our model reached slightly lower accuracies,
-% (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it improves upon the COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
-
 \subsection{Generalization capabilities}
-
-\begin{figure}[!b]
-	\centering
-	\includegraphics[width=0.75\textwidth]{../results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
-	\label{fig:samnet_cog_overall_transfer}
-\end{figure}
-
-The goal of the next set of experiments was to test the generalization ability concerning the sequence length and number of distractors.
-For that purpose, we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
-As the original paper does not include such experiments, we have performed them on our own.
-The light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have trained (fine-tuning/testing) using the original code provided by the authors.
-For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning.
-In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
-We have also tested both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
-In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested exclusively on the Hard variant.
-
-\begin{table}[htb]
-	\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
-		while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
-	\centering
-	\begin{adjustbox}{width=\textwidth}
-		\begin{tabular}{lcccccccccc}
-			\toprule
-			Model & & SAMNet & && && COG&& \\
-			\cmidrule{2-5} \cmidrule{7-11} 
-			&&&&& & paper & ours & ours & paper&\\
-			\cmidrule{7-9} \cmidrule{10-11}
-			Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
-			Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
-			Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
-			\midrule
-
-			Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\
-
-			\midrule
-
-			AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
-			AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
-			AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
-			AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
-			CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
-			CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
-			Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
-			ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
-			ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
-			ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
-			ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
-			ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
-			ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
-			ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
-			ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
-			ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
-			ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
-			GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
-			GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
-			GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
-			GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
-			SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
-			SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\label{tab:all-results}
-\end{table}
-
-%we used the canonical (easy) and hard settings that alter the number of distractors and sequence length.
-Since there was no baseline for these tests (train on canonical, test on hard), we ran our own experiments using the COG model provided by the authors.
-SAMNet achieves the highest overall scores for all categories of experiments (\cref{fig:samnet_cog_overall_transfer}), especially for the tests run on the hard dataset.
-Among the 22 classification tasks, we highlighted the two most difficult tasks that affect the overall score.
-%We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence. 
-%The mechanisms introduced in SAMCell learn to operate independently of the total number of frames and allow to generalize to longer video lengths.
-%As shown in \cref{fig:samnet_cog_overall_transfer}, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.
-Therefore, the memory is updated efficiently instead of storing all information across all frames.
-
-\subsection{Illustrating the multi-step reasoning and grounding of concepts including time}
-
-To illustrate the reasoning strategy developed by SAMNet including the grounding of concepts, we consider the example
-of \textbf{CompareColor} presented in \cref{fig:example}. 
-As a full step-by-step analysis (8 reasoning steps for each of 4 frames) would be tedious, we picked the four key steps
-of reasoning performed by SAMNet for the same example that are important for Frame~\textbf{4}.
-For more details on this example, please see~\cref{sec:append}.
-
-\captionsetup[subfigure]{labelformat=empty}
-\begin{figure}[htbp]
-  \begin{center}
-  Question: \textbf{Does color of u now equal the color of the latest circle?}
-  \end{center}
-  \vskip -0.4cm
-  \null\hfill
-  \begin{subfigure}{0.25\textwidth}
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 1"}
-	\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{false}}
-	\label{fig:frame-1}
-  \end{subfigure}%
-  \hfill
-  \begin{subfigure}{0.25\textwidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2"}
-	\caption{Frame: \textbf{2}\newline Ground Truth: \textbf{false}}
-	\label{fig:frame-2}
-  \end{subfigure}%
-  \hfill
-  \begin{subfigure}{0.25\textwidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 3"}
-	\caption{Frame: \textbf{3}\newline Ground Truth: \textbf{true}}
-	\label{fig:frame-3}
-  \end{subfigure}%
-  \hfill
-  \begin{subfigure}{0.25\textwidth}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4"}
-	\caption{Frame: \textbf{4}\newline Ground Truth: \textbf{true}}
-	\label{fig:frame-4}
-  \end{subfigure}%
-  \hfill\null
-  \newline
-  \centering
-\caption{A sample from the COG dataset selected for the following analysis.} 
-\label{fig:example}  
-\end{figure}
-
-First, we analyze the \textbf{6}-th reasoning step of Frame~\textbf{2}, presented~\cref{fig:frame-2-step-6}.
-Here the system clearly focuses its attention on the second object important from the point of view of the question: the \textbf{yellow circle}.
-Analogously, the question and visual attention are almost perfectly aligned with the word and object, besides, 
-the system does a decent job of capturing the time context \textbf{Latest} of the object.
-Finally, the ``Add New'' gate is on, indicating that the system has stored the \textbf{yellow circle} in external memory.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 6"}
-	\caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
-	\label{fig:frame-2-step-6}
-\end{figure}
-
-Next, in the \textbf{1}-st reasoning step of Frame~\textbf{4}, presented in~\cref{fig:frame-4-step-1}, 
-we can once again observe that  system correctly grounded the visual object \textbf{u} and detected the most likely temporal context \textbf{Now} (still not extremely high indicating that the distinction may not be significant for this example).
-Besides that, we can notice that memory content remained more or less unchanged.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 1"}
-	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 4.} 
-	\label{fig:frame-4-step-1}
-\end{figure}
-
-In \textbf{6}-th reasoning step (\cref{fig:frame-4-step-6}) there are several things worth discussing.
-First, question attention is pointing at the word \textbf{circle}, but the visual attention is clearly avoiding all the objects. 
-This is because there is no circle.
-However, as the system properly identified the temporal context as \textbf{Latest}, instead of using the visual object, it uses the object retrieved from the memory---notice that the read head, despite not being perfectly crisp, is pointing at addresses 3-5, where it previously stored the \textbf{yellow circle} during the analysis of Frame \textbf{2}.
-Moreover, the ``Add New`` gate value is high enough so it once again updates the memory, with a void object. 
-(This would have been considered for future frames if they were to be present. 
-Because the content of those memory addresses is negligible, SAMNet  will still able return the correct prediction).
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 6"}
-	\caption{State of the SAM Cell after 6-th step of reasoning on Frame 4.} 
-	\label{fig:frame-4-step-6}
-\end{figure}

### 2019-11-06 cvpr_submission/related_work.tex
Added folder & empty template for cvpr submission.

\section{Introduction}

\subsection{Subsection 1}

\subsection{Subsection 2}

\subsection{Subsection 3}

### 2019-11-06 cvpr_submission/introduction.tex
Added COG bibliography and copied introduction section.

--- 2019-11-05 COG_publications/2019_neurips_kr2ml/intro.tex
@@
 
-Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \citep{mao2019neurosymbolic}.
+Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \cite{mao2019neurosymbolic}.
 These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.
 Furthermore, symbolic priors (e.g., domain knowledge) and integration of logic depend on hand-crafted modules.
-In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability)\citep{vedantam2019probabilistic}.
-However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols \citep{taniguchi2018symbol}.
+In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability)\cite{vedantam2019probabilistic}.
+However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols \cite{taniguchi2018symbol}.
 
@@
 
-%Such approaches also differ from the human cognitive strategies.
-Humans have the ability to selectively pay attention and store salient items or events in memory based on their goals.
-Working memory and episodic memory systems are responsible for this remarkable ability.
-
-%Fluid Intelligence:
-%
-%IQ may be viewed as a composite comprising multiple elements: In many theories of intelligence, a distinction is made between fluid and crystallized intelligence (8).
-Fluid intelligence comprises the set of abilities involved in coping with novel environments and especially in abstract reasoning; crystallized intelligence is the product of the application of these processes.
-Fluid intelligence is often measured by tests such as figural analogy, classification, and matrix problems, whereas crystallized intelligence is measured by tests of vocabulary and general information (9).
-%~\cite{sternberg2008increasing}
-%
-%Cognitively, gF is thought to be related to metacognition6(knowing about and reflecting upon one’s own ongoing mentalprocesses) and to working memory4,5,7–9(the active maintenanceof domain-specific information plus domain-general attention-al or ‘executive’ control of ongoing processing).
-One componentof attentional control is the ability to overcome interference thatwould otherwise disrupt performance by compromising taskgoals or information held active in working memory.
-Individualdifferences in gF are most pronounced in behavioral measureswhen attentional control is required4,8,10.
-For this reason, gF isthought to be related to attentional control specifically~\cite{gray2003neural}
-
-%In recent years there has been substantial progress in systems  that  can  find  factual  answers  in  text,  starting  with IBM’s Watson system~\cite{ferrucci2010building}, and now with high-performing neural systems that can answer short questions provided they are given a text that contains the answer e.g.~\cite{wang2018glue}
-%
-%
-%AI  has  achieved  remarkable  mastery  over  games  such  asChess, Go, and Poker, and evenJeopardy!, but the rich variety of standardized exams has remained a landmark chal-lenge.
-Even  in  2016,  the  best  AI  system  achieved  merely 59.3\% on an 8th Grade science exam challenge (Schoenicket al., 2016).
-%
-%Playing Atari Games~\cite{mnih2015human}
-%
-%
-%Despite several successes across many domains Deep learning~\cite{lecun2015deep} still struggles with
-%
-%learning algoritms
-%learning reasoning~\cite{graves2016hybrid}
-%
-%
-%Wingrad Scheme challenge~\cite{levesque2012winograd}
-
-%visual reasoning~\cite{mogadala2019trends} - datasets such as COG~\cite{yang2018dataset} and 
-%SVQA (Synthetic Video Question Answering)~\cite{song2018explore}
-%
-%
-%ARISTO project~\cite{clark2019f} - based on RoBERTa~\cite{liu2019roberta} contextual word embeddings
-%
-%transformer-based solutions~\cite{vaswani2017attention} using self-attention
-%
-%
-%“The current neural network approaches will find it difficult to determine which combinations of ‘later’, ‘earlier’, ‘more’, and ‘less’ constitute ‘increase’ and which constitute ‘decrease,'” Davis says.
-“Neural networks have no inherent idea of magnitude or of time.”
-%~\cite{davis2016write}
-
-%\begin{itemize}
-%\item bAbI:  MemNets~\cite{weston2014memory} have access to the whole story at once
-%\item the same goes to SoftPats~\cite{haurilet2019s} - they build graph per frame and then frame number is treated as one dimensions, so at the end the \textit{Traveler} can access all of them at the same time
-%\item The paper~\cite{le2019learning} focuses on SVQA and TGIF-QA -  they access all frames at once, i.e.
-cut the video into clips, process each frame with CNNs and then aggregate feature representations of equal-size clips obtained by a temporal attention mechanism.
-So in fact the model has access to all frames all the time.
-%\end{itemize}
-%so the time aspect is really... not dealt with?
-%
-%Additionally, in~\cite{song2018explore} the authors introduced a large-scale dataset caled SVQA (Synthetic Video Question Answering) consisting of (Total QA pairs: 83160/11760/23760 and Total Videos 8400/1200/2400).
-%As "using all frames is time-consuming.
-Thus we divide each video into clips (segments) of 16 frames, with 80\% overlap between successive clips (segments)" and "We extract feature from each clip and aggregate features of all clips from one video to form a sequential video representation." -- which means that they identified the problem that you "cannot extract features from all frames" at the beginning and pass that to the model.
-But instead of proposing a solution that will deal with the video on per-frame basis, they "cheated".
-;)
-%
-%IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie/number of distractionts}, so there is no need for cutting video into cuts etc.
-
-\paragraph{Contributions.}
-%Such approaches also differ from the human cognitive strategies.
-Humans have the ability to selectively pay attention and store salient items or events in memory based on their goals.
-Working memory and episodic memory systems are responsible for this remarkable ability.
-In this paper, we introduce a new model for visual reasoning that can dynamically process video input frame-by-frame, reason over each frame and store the salient concepts in memory so as to order to answer questions.
-Our experiments based on the COG dataset \cite{yang2018dataset} indicate that the model can:
-(1) form temporal associations, i.e., grounding the time-related words with meaning;
-%\item Learning the concept of time
-%\item time context being by-product of gates
-%\end{itemize}
-(2) learn complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes;
-(3) selectively control the flow of information to and from the memory to answer questions; and
-(4) update the memory only with relevant visual information depending on the temporal context.
-%\begin{itemize}
-%\item \textbf{Time aspect}:
-%\begin{itemize}
-%\item Learning the temporal association - grounding the time-related words with meaning
-%%\item Learning the concept of time
-%%\item time context being by-product of gates
-%%\end{itemize}
-%
-%\item Learning complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes
-%%\begin{itemize}
-%%\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
-%\item Selectively control the flow of information to and from the memory to answer questions
-%%\end{itemize}
-%%\item \textbf{Selective Attention Memory}:
-%%\begin{itemize}
-%\item Updating the memory only with relevant visual information depending on the temporal context
-%%\item content based and location based addressing for reading and writing
-%%\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way
-%
-%\end{itemize}
-%\end{itemize}
+\paragraph{Contributions}

### 2019-11-08 cvpr_submission/introduction.tex
intro + references - core dump

@@
 
+Deep Learning~\cite{lecun2015deep}
+
+An assumption of traditional machine learning methodologies is the training data and testing data are taken from the same domain, such that the input feature space and data distribution characteristics are the same.
+However, in some real-world machine learning scenarios, this assumption does not hold.
+There are cases where training data is expensive or difficult to collect.
+
+Transfer learning is used to improve a learner from one domain by transferring information from a related domain~\cite{pan2009survey}.
+
+There can be  different types of transfer learnings in deep learning,
+most popular being
+
+In Computer Vision:
+
+It became a standard to pretrain an image encoder or feature detector on ImageNet~\cite{deng2009imagenet} which is image classification task, and transfer it to unrelated domains and applications, such as e.g.
+visual question answering in medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}
+
+Transfer learning is a cornerstone of computer vision,
+yet little work has been done to evaluate the relationship
+between architecture and transfer~\cite{kornblith2019better}.
+Here, we compare the performance of 16 classification networks on 12 image classification datasets.
+We find that, when networks are used as fixed feature extractors or fine-tuned, there is a strong correlation between ImageNet accuracy and transfer accuracy.
+
+The tremendous success of ImageNet-trained deep features on a wide range of transfer tasks raises the question:
+what is it about the ImageNet dataset that makes the learnt
+features as good as they are?~\cite{huh2016makes}
+
+We proposes a fully computational approach for modeling the structure of space of visual tasks. This is done via
+finding (first and higher-order) transfer learning dependencies across a dictionary of twenty six 2D, 2.5D, 3D, and
+semantic tasks in a latent space. The product is a computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}
+
+In Language:
+
+Analogically, the NLP community was using shallow word embeddings such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}.
+The latter work came with a repository of pretrained models that became a standard for several years.
+Recently, we can observe an explosion of deep contextualized word representations such as ELMo (based on bidirectional LSTM)~\cite{peters2018deep} or BERT (based on Transformer)~\cite{devlin2018bert}
+
+Repositories with dozens of pretrained BERT variations such as HugginFace~\cite{wolf2019transformers} -- a new standard
+
+Conclusion:
+TL for image, video(?) and language engoders are standard.
+Are widely used for Visual Reasoning. But those tasks require some kind of fusion/higher level reasoning.
+
+Lack of studies of impact of transfer learning for higher-level, abstract reasoning?
+
+From one point, some preliminary results:
+ - CLEVR showing results on CoGenT-a/b~\cite{johnson2017clevr} - this is more "object generalization"
+ - COG paper showing interesting results with "task generalization" when training on all tasks excluding the one used for test~\cite{yang2018dataset}
+
+\subsection{old}
 Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.

### 2019-11-08 cvpr_submission/experiments.tex
Added table of CoGenT experiments results.
Added some details about the CoGenT experiments.

@@
 \subsection{Generalization capabilities}
+
+\subsubsection{CoGenT tasks}
+
+We have reimplemented and trained the MAC model~\cite{hudson2018compositional} using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}.
+For all experiments, the training procedure is as follows: we train the MAC model for 20 epochs on 90\% of the training set of CoGenT.
+We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets (CoGenT-A  \& -B) as test sets.
+We used NVIDIA's GeForce GTX TITAN X GPUs.
+We followed the implementation details indicated in the supplemental material (Sec.
+A) of the original paper~\cite{hudson2018compositional}, to ensure a faithful comparison.
+
+\begin{table}[htb]
+	\centering
+	\noindent
+	\begin{adjustbox}{width=0.5\textwidth}
+	\begin{tabular}{c c c c c c c }\toprule
+		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
+		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
+		\cmidrule(lr){2-7}
+		\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-7}
+		\multicolumn{1}{ c }{All tasks} & 95.32 & 98.4 	& 86.75	& 96.0	& 98.65	& 98.02 \\ 
+		\cmidrule(lr){1-7}
+		\multicolumn{1}{ c }{All tasks but Exist} & 90.33 	& 60.42	& 86.12	& 96.18	& 98.52 & 98.60 \\ 
+		\multicolumn{1}{ c }{All tasks but Count} & 74.59 	& 97.51	& 0.0	& 94.37	& 98.42 & 98.47 \\ 
+		\multicolumn{1}{ c }{All tasks but CompareInteger} & 91.53 	& 98.22	& 86.09	& 56.35	& 98.78 & 98.40 \\ 
+		\multicolumn{1}{ c }{All tasks but CompareAttribute} & 81.92 	& 98.32	& 86.36	& 95.86	& 23.18 & 98.44 \\ 
+		\multicolumn{1}{ c }{All tasks but QueryAttribute} & 42.17 	& 76.79	& 54.64	& 79.87 & 64.13 & 0.0 \\ 
+		\cmidrule(lr){1-7}
+		\multicolumn{1}{ c }{Exist only} & 26.07 & 74.20	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
+	    \multicolumn{1}{ c }{Count only} & 14.89  & 0.0	& 62.78	& 0.0 & 0.0 & 0.0 \\ 
+	    \multicolumn{1}{ c }{CompareInteger only} & 23.44 & 48.15	& 0.0	& 77.98	& 54.08 & 0.0 \\ 
+	    \multicolumn{1}{ c }{CompareAttribute only} & 23.50 & 51.93	& 0.0 & 59.06 & 61.73 & 0.0 \\ 
+	\multicolumn{1}{ c }{QueryAttribute only} & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & 97.08 \\ 
+		\bottomrule
+	\end{tabular}
+    \end{adjustbox}
+	\caption{CoGenT accuracies for all tasks when training on one task only or all but one task.}
+	\label{tab:CoGenT_results}
+\end{table}
+
+We first ran a control experiment, where the model is trained, then tested on all tasks.
+We take the results as references for the following experiments.
+The accuracy per task is coherent with the human performance~\cite{johnson2017clevr}, where we observe that \textit{Count} is the most challenging task.
+
+The next set of experiments excludes one task from the training set, and tests the model on all.
+Comparing these experiments against the reference one allows to observe whether the model is able to solve the held-out task using information from the other tasks.
+We observe here a first distinction between the five tasks: 
+\begin{itemize}
+	\item \textit{Exist}, \textit{CompareInteger}, \textit{CompareAttribute}: Even with no training data for these tasks, the model is able to answer correctly the majority of the questions for \textit{Exist} \& \textit{CompareInteger} and one-quarter of the \textit{CompareAttribute} questions.
+	\item \textit{Count} \& \textit{QueryAttribute}: When not present in the training data, the model cannot answer any of these questions correctly.
+\end{itemize}
+
+This first observation hints at a transfer of information between tasks -- to a limited degree.
+A subsequent set of experiments is then to train on only one task at a time and test on all.
+This will allow us to quantify what is the benefit provided by training on a certain task when solving others.
+
+The last section of \tableref{tab:CoGenT_results} contains the results of this set of experiments.
+We note the following:
+\begin{itemize}
+	\item A distinction between tasks is again observed: \{\textit{Exist}, \textit{CompareInteger}, \textit{CompareAttribute}\}, \{\textit{Count}\}, \{\textit{QueryAttribute}\},
+	\item The tasks \{\textit{Exist}, \textit{CompareInteger}, \textit{CompareAttribute}\} seem to be benefiting from one another: When trained on one, the model is able to answer correctly the majority of questions in the two other tasks.
+	\item \textit{QueryAttribute} and \textit{Count} are very distinct: the model is able to answer these questions correctly only when it was trained on them.
+Additionally, training solely on these tasks do not appear to benefit the other 3 tasks.
+	\item Nevertheless, not including \textit{QueryAttribute} results in a test accuracy drop of 17 to 30+ pts on the other tasks.
+\textit{QueryAttribute} could thus be qualified as a "necessary but not sufficient" training task.
+This could be mitigated by the fact that \textit{QueryAttribute} is the largest task (by number of questions).
+Hence, removing it from the training set reduces the number of samples by a third.
+\end{itemize}

### 2019-11-10 cvpr_submission/introduction.tex
wip on intro

@@
 \section{Introduction}
+During recent year neural networks, being the core of the so-called Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  speech recognition~\cite{graves2013speech}, to image classification~\cite{krizhevsky2012imagenet} to object detection~\cite{redmon2016you} to question answering~\cite{weston2014memory} to machine translation~\cite{bahdanau2014neural}.
+At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing data are sampled from the same domain, i.e.
+operating in the same input space and with similar data distribution characteristics.
+However, in many real-world scenarios, this assumption does not hold and besides, as modern neural models often have  milions of trainable parameters (weights), their trainng reguires a vaist amount of data, which for some domains (e.g.
+medical) can be very expensive and/or extremely difficult to collect.
+One of the widely accepted solutions for the mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique that enables improving of a model by transferring \emph{information} from one domain to the other.
 
-Deep Learning~\cite{lecun2015deep}
+%pan2009survey: we categorize transfer learning under three sub-settings: inductive transfer learning, transductive transfer learning and unsupervised transfer learning,
 
-An assumption of traditional machine learning methodologies is the training data and testing data are taken from the same domain, such that the input feature space and data distribution characteristics are the same.
-However, in some real-world machine learning scenarios, this assumption does not hold.
-There are cases where training data is expensive or difficult to collect.
+In Computer Vision, it became a standard to pretrain an image encoder (such as VGG~\cite{simonyan2014very}) on a large scale dataset (like ImageNet~\cite{deng2009imagenet}), and transfer its weights to unrelated domains and tasks, such as e.g.
+Visual Question Answering (VQA) in medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+The fact that such a transfer improves performance is quite fascinating taking into account that both domain (natural images vs medical or images with cars) and task (image classification vs VQA or image segmentation) change (inductive transfer learning according to the taxonomy from~\cite{pan2009survey}).
 
-Transfer learning is used to improve a learner from one domain by transferring information from a related domain~\cite{pan2009survey}.
+Similarly, NLP...
 
-There can be  different types of transfer learnings in deep learning,
-most popular being
+Analogically, the NLP community was using shallow word embeddings such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}.
+The latter work came with a repository of pretrained models that became a standard for several years.
+Recently, we can observe an explosion of deep contextualized word representations such as ELMo (based on bidirectional LSTM)~\cite{peters2018deep} or BERT (based on Transformer)~\cite{devlin2018bert}
 
-In Computer Vision:
+Repositories with dozens of pretrained BERT variations such as HugginFace~\cite{wolf2019transformers} -- a new standard
 
-It became a standard to pretrain an image encoder or feature detector on ImageNet~\cite{deng2009imagenet} which is image classification task, and transfer it to unrelated domains and applications, such as e.g.
-visual question answering in medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}
+The tremendous success of ImageNet-trained deep features on a wide range of transfer tasks raises the question:
+what is it about the ImageNet dataset that makes the learnt
+features as good as they are?~\cite{huh2016makes}
 
@@
 
-The tremendous success of ImageNet-trained deep features on a wide range of transfer tasks raises the question:
-what is it about the ImageNet dataset that makes the learnt
-features as good as they are?~\cite{huh2016makes}
-
 We proposes a fully computational approach for modeling the structure of space of visual tasks. This is done via
@@
 
-In Language:
-
-Analogically, the NLP community was using shallow word embeddings such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}.
-The latter work came with a repository of pretrained models that became a standard for several years.
-Recently, we can observe an explosion of deep contextualized word representations such as ELMo (based on bidirectional LSTM)~\cite{peters2018deep} or BERT (based on Transformer)~\cite{devlin2018bert}
-
-Repositories with dozens of pretrained BERT variations such as HugginFace~\cite{wolf2019transformers} -- a new standard
+Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa} is a new exciting problem domain, where the system is expected to answer questions expressed in natural language by taking into account the content of the image.
 

### 2019-11-11 cvpr_submission/introduction.tex
introduction

--- 2019-11-06 cvpr_submission/introduction.tex
@@
 \section{Introduction}
+During recent year neural networks, being the core of the so-called Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  speech recognition~\cite{graves2013speech}, to image classification~\cite{krizhevsky2012imagenet} to object detection~\cite{redmon2016you} to question answering~\cite{weston2014memory} to machine translation~\cite{bahdanau2014neural}.
+At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing data are sampled from the same domain, i.e.
+operating in the same input space and with similar data distribution characteristics.
+However, in many real-world scenarios, this assumption does not hold and besides, as modern neural models often have  milions of trainable parameters (weights), their trainng reguires a vaist amount of data, which for some domains (e.g.
+medical) can be very expensive and/or extremely difficult to collect.
+One of the widely accepted solutions for the mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique that enables improving of a model by transferring \emph{information} from one domain to the other.
 
-Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
+%pan2009survey: we categorize transfer learning under three sub-settings: inductive transfer learning, transductive transfer learning and unsupervised transfer learning,
+
+In Computer Vision, it became a standard to pretrain an image encoder (such as VGG~\cite{simonyan2014very}) on large scale datasets (like ImageNet~\cite{deng2009imagenet}), and transfer its weights to unrelated domains and tasks, such as e.g.
+Visual Question Answering (VQA) in medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+The fact that such a transfer improves performance is quite fascinating, taking into account that both domain (natural images vs medical or images with cars) and task (image classification vs VQA or image segmentation) change (inductive transfer learning according to the taxonomy from~\cite{pan2009survey}).
+
+A similar development can be observed in the Natural Language Processing (NLP) community.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on several large corpuses coming from e.g.
+Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks.
+Recently, we can observe an explosion of deep contextualized word representations such as ELMo (based on bidirectional LSTM)~\cite{peters2018deep} or BERT (based on the Transformer architecture)~\cite{devlin2018bert}.
+Analogically to the pretrained image encoders, the community made an effort to ease the access to repositories with dozens of pretrained BERT variations, HugginFace~\cite{wolf2019transformers} being one of most notable examples.
+
+The success of transfer learning raises several questions, such as specifics of datasets used for the pretraining (in particular, ImageNet~\cite{huh2016makes}), or correlation of performances of models with different architectures in the source and target domains~\cite{kornblith2019better}.
+One of most systematic works analysing the impact of transfer learning in Computer Vision is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies across a dictionary of twenty six 2D, 2.5D, 3D, and
+semantic tasks.
+
+The impact of transfer learning is even more important in the case of multi-modal tasks~\cite{mogadala2019trends} combining both of the mentioned modalities (i.e. vision and language).
+One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer questions expressed in natural language by taking into account the content of a single image (Image Question Answering) or a video (Video Question Answering).
+In a typical VQA model, disregarding whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encode and word embeddings is de facto standard, proven empirically its dominance over the models trained from the scratch.
+
+In this paper, however, we decided to focus on a slightly different  aspect of transfer learning.
+As both Image and Video QA can be seen as meta-problems, where the system has to develop a different reasoning process depending on the type/family of question (task), we asked ourselves whether mastering one task type/family can help with mastering others.
+
+\paragraph{Contributions}
+
+The contributions of this paper are as follows.
+We propose a new model called SAMNet, that achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning.
+Next we show how different tasks impact when transfering the whole pretrained model in three main setups.
+In the first one focus on transfer learning within the Image QA domain and perform experiment similar to Taskonomy~\cite{zamir2018taskonomy} and analyse how training exclusively on one task family helps with mastering other family, with once but crucial difference: we transfer and fine-tune the whole model (not only the encoder).
+In the second we show a complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
+Finally, we present a set of experiments aimed at analysis of the impact of transfer learning in Video QA, when domain changes drastically and system has to deal with longer videos with higher complexity (understood as number of distractors present in each frame).
+%Surprisingly, our model with only small fine-tuning, managed to the master Hard variant and achieved higher accuracy than the model trained explicitly on Hard variant from the scratch.
+
+\tk{Have I addressed that correctly? I am not sure whether I have covered TL with CoGenT-A and CoGenT-B variants...}
+%A) Task generalization
+%- answers (CLEVR)
+%B) Domain adaptation
+%- CoGenT A -> CoGenT B (CLEVR)
+%- sequence lenght  (COG)
+%- image complexity (distractors) (COG)
+
+%All those experiments in fact analyse different aspects
+
+%Lack of studies of impact of transfer learning for higher-level, abstract reasoning?
+
+%From one point, some preliminary results:
+% - CLEVR showing results on CoGenT-a/b~\cite{johnson2017clevr} - this is more "object generalization"
+ %- COG paper showing interesting results with "task generalization" when training on all tasks excluding the one used for test~\cite{yang2018dataset}
+
+%I want to claim that therer are three different approaches to "master count".
+%1) Train and test only on count
+%2) Train on alll the tasks including count
+%3) Do not train on count at all and then test on count
+
+%conclusions:
+%when you are doing transfer make sure that the target answers are the same!
+%otherwise: binary y/n vs numers 0-7 vs names of attributes
+
+\section{Related work -- import}
+%Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
 Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.
 
-Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \cite{mao2019neurosymbolic}.
+%Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \cite{mao2019neurosymbolic}.
 These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.
@@
 For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2014memory}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
-
-\paragraph{Contributions}

### 2019-11-11 cvpr_submission/experiments.tex
Rewrote CLEVR subsection in the Experiments section.

--- 2019-11-06 cvpr_submission/experiments.tex
@@
 
-\subsection{Generalization capabilities}
+\subsection{Multi-task learning}
+
+\subsubsection{CLEVR tasks}
+\vm{Will have to rephrase this in accordance with Jayram's definition.}
+
+We have trained SAMNet using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}, on the training set of the condition A of the CLEVR dataset (CLEVR-CoGenT)~\cite{johnson2017clevr}.
+For all experiments, the training procedure is as follows: we train the model for 20 epochs on 90\% of the training set of CoGenT.
+We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets (CoGenT-A  \& -B) as test sets.
+We used NVIDIA's GeForce GTX TITAN X GPUs.
+
+We consider as task groups the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+In order to investigate the potential benefits of multi-task learning, we conducted the following experiments:
+
+\begin{itemize}
+	\item We first trained SAMNet on a single task group, and tested on this same task group.
+These 5 experiments (one per task group) fit into the traditional Deep Learning procedure of training and testing on the same task, or on samples drawn from the same distribution over an input domain (single-task learning).
+	\item Following, we trained SAMNet on all task groups jointly, and evaluated its performance on each group separately.
+The underlying hypothesis for this experiment is that learning jointly on all task groups would improve the performance on each task group.
+	\item Finally, we finetuned a model, trained on all task groups jointly, on each of the task groups separately.
+We are interested in two observations here: how significant is the performance gain, if any, on the finetuned task?
+And complementary, how significant is the performance drop, if any, on the other tasks?
+\end{itemize}
+
+The results of these experiments are available in \Tab{tab:CoGenT_results}. 
+\begin{table}[htb]
+	\centering
+	\noindent
+	\caption{CLEVR-CoGenT accuracies for all 5 tasks when training on solely one task, jointly training on all tasks and finetuning on each task.
+For all experiments, the validation and test sets are identical.}\label{tab:CoGenT_results}
+	\begin{adjustbox}{width=0.5\textwidth}
+	\begin{tabular}{c c c c c c c }\toprule
+		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
+		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
+		\cmidrule(lr){2-7}
+		\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-7}
+		\multicolumn{1}{ c }{Exist only} & 26.07 & 74.20	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
+		\multicolumn{1}{ c }{Count only} & 14.89  & 0.0	& 62.78	& 0.0 & 0.0 & 0.0 \\ 
+		\multicolumn{1}{ c }{CompareInteger only} & 23.44 & 48.15	& 0.0	& 77.98	& 54.08 & 0.0 \\ 
+		\multicolumn{1}{ c }{CompareAttribute only} & 23.50 & 51.93	& 0.0 & 59.06 & 61.73 & 0.0 \\ 
+		\multicolumn{1}{ c }{QueryAttribute only} & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & 97.08 \\ 		
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-7}
+
+		\multicolumn{1}{ c }{All tasks} & 95.32 & 98.4 	& 86.75	& 96.0	& 98.65	& 98.02 \\ 
+		\cmidrule(lr){1-1}
+		\cmidrule(lr){2-7}
+
+		\multicolumn{1}{ c }{\textit{Trained on all tasks -- Finetune on $t$}} & &  & &  & &\\ 
+		\multicolumn{1}{ c }{Exist} &  & & & & & \\ 
+		\multicolumn{1}{ c }{Count} &  & & & & & \\
+		\multicolumn{1}{ c }{CompareInteger} &  & & & & & \\
+		\multicolumn{1}{ c }{CompareAttribute} &  & & & & & \\
+		\multicolumn{1}{ c }{QueryAttribute} &  & & & & & \\
+
+		\bottomrule
+	\end{tabular}
+    \end{adjustbox}
+\end{table}
+
+Looking at the first section of \tab{tab:CoGenT_results}, we observe, unsurprisingly, that a model trained on a single task will do better on this task than on the others when being tested.
+Nevertheless, we also note that a model, trained on \textit{Exist} only, obtains a score slightly better than random on \textit{CompareInteger} \& \textit{CompareAttribute}.
+This is due to the fact that these 3 task groups share the same labels space ('yes', 'no').
+\textit{Count} and \textit{QueryAttribute} have isolated labels space (('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10') and the set of object attributes values respectively) and we thus observe an accuracy of zero for these tasks, except when trained on these.
+
+Training SAMNet on all tasks jointly, then testing it on each task, shows significant improvement on 4 out of 5 tasks, ranging from 18 points to 37 points.
+\textit{QueryAttribute} does not benefit from such an improvement, only seeing an increase of one point in terms of test accuracy.
+This suggests that \textit{QueryAttribute} is \textit{self-sufficient}, as the model is performing similarly between single-task learning and multi-task learning.
+
+Finally, we finetuned the model trained on all tasks on each task separately, for up to one epoch.
+The interest here is to observe if finetuning on a specific task can further boost the accuracy on this particular, while preserving the performance on other tasks (and thus the overall performance as well) similar.
+
+\begin{table}[htb]
+	\centering
+	\noindent
+	\begin{adjustbox}{width=0.5\textwidth}
+		\begin{tabular}{c c c c c c c }\toprule
+			\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
+			\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
+			\cmidrule(lr){2-7}
+			\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
+			\cmidrule(lr){1-1}
+			\cmidrule(lr){2-7}
+			\multicolumn{1}{ c }{All tasks but Exist} & 90.33 	& 60.42	& 86.12	& 96.18	& 98.52 & 98.60 \\ 
+			\multicolumn{1}{ c }{All tasks but Count} & 74.59 	& 97.51	& 0.0	& 94.37	& 98.42 & 98.47 \\ 
+			\multicolumn{1}{ c }{All tasks but CompareInteger} & 91.53 	& 98.22	& 86.09	& 56.35	& 98.78 & 98.40 \\ 
+			\multicolumn{1}{ c }{All tasks but CompareAttribute} & 81.92 	& 98.32	& 86.36	& 95.86	& 23.18 & 98.44 \\ 
+			\multicolumn{1}{ c }{All tasks but QueryAttribute} & 42.17 	& 76.79	& 54.64	& 79.87 & 64.13 & 0.0 \\
+
+			\cmidrule(lr){1-1}
+			\cmidrule(lr){2-7}
+			\multicolumn{1}{ c }{\textbf{Trained on all tasks but $t$ -- Finetune on $t$ }} & &  & &  & &\\ 
+			\multicolumn{1}{ c }{Exist} & 86.24 & 98.04 & 56.59 & 87.99 & 94.17 & 97.14 \\ 
+			\multicolumn{1}{ c }{Count} & 46.97 & 2.80 & 78.73 & 15.60 & 35.06 & 56.60 \\
+			\multicolumn{1}{ c }{CompareInteger} & 73.46 & 72.89 & 42.42 & 92.07 & 68.32 & 91.90 \\
+			\multicolumn{1}{ c }{CompareAttribute} & 48.16 & 85.77 & 30.84 & 77.20 & 97.72 & 13.21 \\
+			\multicolumn{1}{ c }{QueryAttribute} & 35.26 & 38.65 & 4.22 & 31.56 & 5.08 & 70.67 \\
+		\bottomrule
+	\end{tabular}
+\end{adjustbox}
+\caption{CoGenT accuracies with finetuning.}\label{tab:CoGenT_finetuning_results}
+\end{table}
+
+End of section

### 2019-11-11 cvpr_submission/introduction.tex
Correcting typos in the introduction.

@@
 \section{Introduction}
-During recent year neural networks, being the core of the so-called Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  speech recognition~\cite{graves2013speech}, to image classification~\cite{krizhevsky2012imagenet} to object detection~\cite{redmon2016you} to question answering~\cite{weston2014memory} to machine translation~\cite{bahdanau2014neural}.
-At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing data are sampled from the same domain, i.e.
+In recent years, neural networks, at the heart of the Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural}.
+At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independant and identically distributed (iid); i.e they are sampled from the same domain, i.e.
 operating in the same input space and with similar data distribution characteristics.
-However, in many real-world scenarios, this assumption does not hold and besides, as modern neural models often have  milions of trainable parameters (weights), their trainng reguires a vaist amount of data, which for some domains (e.g.
-medical) can be very expensive and/or extremely difficult to collect.
-One of the widely accepted solutions for the mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique that enables improving of a model by transferring \emph{information} from one domain to the other.
+However, in many real-world scenarios, this assumption does not hold.
+Moreover, as modern neural models often have  millions of trainable parameters, training them requires a vast amount of data, which for some domains (notably medical) can be very expensive and/or extremely difficult to collect.
+One of the widely accepted solutions for the problems mentioned above is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enables improving a model by transferring \emph{information} from one domain to another.
 
@@
 
-In Computer Vision, it became a standard to pretrain an image encoder (such as VGG~\cite{simonyan2014very}) on large scale datasets (like ImageNet~\cite{deng2009imagenet}), and transfer its weights to unrelated domains and tasks, such as e.g.
-Visual Question Answering (VQA) in medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
-The fact that such a transfer improves performance is quite fascinating, taking into account that both domain (natural images vs medical or images with cars) and task (image classification vs VQA or image segmentation) change (inductive transfer learning according to the taxonomy from~\cite{pan2009survey}).
+In Computer Vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very}, or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as e.g.
+Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+The fact that such transfer improves performance is appealing, knowing that both the domain (natural images vs.
+medical ones or images with cars) and the task (image classification vs.
+VQA or image segmentation) can change significantly.
+This type of Transfer Learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
 
-A similar development can be observed in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on several large corpuses coming from e.g.
-Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks.
-Recently, we can observe an explosion of deep contextualized word representations such as ELMo (based on bidirectional LSTM)~\cite{peters2018deep} or BERT (based on the Transformer architecture)~\cite{devlin2018bert}.
-Analogically to the pretrained image encoders, the community made an effort to ease the access to repositories with dozens of pretrained BERT variations, HugginFace~\cite{wolf2019transformers} being one of most notable examples.
+A similar development can be noted in the Natural Language Processing (NLP) community.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.
+Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, for some where labeled data is less accessible.
+Recently, we can denote an exponential development of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amount of data.
+Analogically to the pretrained image encoders, the community made an effort to facilitate access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
+HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
 
-The success of transfer learning raises several questions, such as specifics of datasets used for the pretraining (in particular, ImageNet~\cite{huh2016makes}), or correlation of performances of models with different architectures in the source and target domains~\cite{kornblith2019better}.
-One of most systematic works analysing the impact of transfer learning in Computer Vision is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies across a dictionary of twenty six 2D, 2.5D, 3D, and
-semantic tasks.
+The success of transfer learning raises several questions, such as which characteristics make a dataset eligible to be used for pretraining (in particular, ImageNet~\cite{huh2016makes}), or the correlation observed in the performances of models with different architectures between the source and target domains~\cite{kornblith2019better}.
+One of the most systematic publications studying the impact of Transfer Learning in Computer Vision is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies across a dictionary of twenty six 2D, 2.5D, 3D, and semantic tasks.
 
-The impact of transfer learning is even more important in the case of multi-modal tasks~\cite{mogadala2019trends} combining both of the mentioned modalities (i.e. vision and language).
+The impact of Transfer Learning is even more crucial in the case of multi-modal tasks~\cite{mogadala2019trends} combining both of the modalities mentioned above (i.e. vision and language).
 One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer questions expressed in natural language by taking into account the content of a single image (Image Question Answering) or a video (Video Question Answering).

### 2019-11-12 cvpr_submission/related_work.tex
Related work

@@
-\section{Introduction}
+\section{Related work}
+Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.
+Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
+Prior work generally relied on dense visual features produced by either CNNs \cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \citep{teney2017graph,santoro2017simple}.
 
-\subsection{Subsection 1}
+Another research focus area has been multimodal fusion and
+attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
+features \citep{zhou2015simple,antol2015}.
+Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \citep{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .
+Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \citep{yang2016stacked, chen2015abc, ilievski2016focused}.
+Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \citep{hudson2018compositional, song2018explore}.
+Visualization of attention steps also provide interpretability, which is an increasingly important aspect.
+The MAC model \citep{hudson2018compositional} is a great example of such an approach.
+The follow-on model by the same authors  \citep{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
+Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \citep{haurilet2019s, teney2017graph, kim2018dynamic}.
 
-\subsection{Subsection 2}
-
-\subsection{Subsection 3}
+Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .
+Early works \citep{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.
+These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.
+Learning long-term dependencies is also another challenge that LSTMs may struggle with.
+Yin et al.
+2019 \citep{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+Our work is mostly related to the MAC and MANN type models.
+An important distinction of our approach is the frame-by-frame processing of the video input.
+Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
+Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.
+Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
+However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

### 2019-11-12 cvpr_submission/related_work.tex
Update related_work.tex

--- 2019-11-06 cvpr_submission/related_work.tex
@@
-\section{Introduction}
+\section{Related work}
+Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.
+Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
+Prior work generally relied on dense visual features produced by either CNNs \cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph,santoro2017simple}.
 
-\subsection{Subsection 1}
+Another research focus area has been multimodal fusion and
+attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
+features \cite{zhou2015simple,antol2015}.
+Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .
+Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
+Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.
+Visualization of attention steps also provide interpretability, which is an increasingly important aspect.
+The MAC model \cite{hudson2018compositional} is a great example of such an approach.
+The follow-on model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
+Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.
 
-\subsection{Subsection 2}
-
-\subsection{Subsection 3}
+Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .
+Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.
+These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.
+Learning long-term dependencies is also another challenge that LSTMs may struggle with.
+Yin et al.
+2019 \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+Our work is mostly related to the MAC and MANN type models.
+An important distinction of our approach is the frame-by-frame processing of the video input.
+Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
+Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.
+Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
+However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

### 2019-11-12 cvpr_submission/related_work.tex
bib and related work updates

@@
 Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
-Prior work generally relied on dense visual features produced by either CNNs \cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph,santoro2017simple}.
+Prior work generally relied on dense visual features produced by either CNNs \cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.
 
@@
 attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
-features \cite{zhou2015simple,antol2015}.
+features \cite{zhou2015simple, antol2015}.
 Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .

### 2019-11-12 cvpr_submission/introduction.tex
More corrections & references in the introduction.

@@
 \section{Introduction}
-In recent years, neural networks, at the heart of the Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural}.
-At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independant and identically distributed (iid); i.e they are sampled from the same domain, i.e.
-operating in the same input space and with similar data distribution characteristics.
+In recent years, neural networks, at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
+At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.
+sampled from a common input space under similar data distribution characteristics.
 However, in many real-world scenarios, this assumption does not hold.
-Moreover, as modern neural models often have  millions of trainable parameters, training them requires a vast amount of data, which for some domains (notably medical) can be very expensive and/or extremely difficult to collect.
-One of the widely accepted solutions for the problems mentioned above is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enables improving a model by transferring \emph{information} from one domain to another.
+Moreover, as modern neural models often have  millions of trainable parameters, training them requires vast amount of data, which for some domains (notably medical) can be very expensive and/or extremely difficult to collect.
+One of the widely accepted solutions for the problems mentioned above is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enables model - and thus performance - improvements by transferring \emph{information} from one domain to another.
 
@@
 
-In Computer Vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very}, or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as e.g.
-Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
-The fact that such transfer improves performance is appealing, knowing that both the domain (natural images vs.
-medical ones or images with cars) and the task (image classification vs.
+In computer vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+That such transfer improves performance is appealing, knowing that both the domain (e.g.
+realistic images vs.
+medical ones or images with cars) and the task (e.g.
+image classification vs.
 VQA or image segmentation) can change significantly.
-This type of Transfer Learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
+This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
 
 A similar development can be noted in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.
-Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, for some where labeled data is less accessible.
-Recently, we can denote an exponential development of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amount of data.
-Analogically to the pretrained image encoders, the community made an effort to facilitate access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, some where labeled data is less accessible.
+Recently, we can denote an accelerated development of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amount of data.
+Analogically to the pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
 HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
 
-The success of transfer learning raises several questions, such as which characteristics make a dataset eligible to be used for pretraining (in particular, ImageNet~\cite{huh2016makes}), or the correlation observed in the performances of models with different architectures between the source and target domains~\cite{kornblith2019better}.
-One of the most systematic publications studying the impact of Transfer Learning in Computer Vision is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies across a dictionary of twenty six 2D, 2.5D, 3D, and semantic tasks.
+The success of transfer learning raises several questions, such as which characteristics make a dataset favorable for use in pretraining (notably ImageNet~\cite{huh2016makes}), or what explains the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
+One of the most systematic work studying the impact of transfer learning in computer vision is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.
 
-The impact of Transfer Learning is even more crucial in the case of multi-modal tasks~\cite{mogadala2019trends} combining both of the modalities mentioned above (i.e. vision and language).
-One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer questions expressed in natural language by taking into account the content of a single image (Image Question Answering) or a video (Video Question Answering).
-In a typical VQA model, disregarding whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encode and word embeddings is de facto standard, proven empirically its dominance over the models trained from the scratch.
+The impact of transfer learning is even more central in the case of multi-modal tasks~\cite{mogadala2019trends}, combining both of the modalities mentioned above (i.e. vision and language).
+One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
+In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
 
-In this paper, however, we decided to focus on a slightly different  aspect of transfer learning.
-As both Image and Video QA can be seen as meta-problems, where the system has to develop a different reasoning process depending on the type/family of question (task), we asked ourselves whether mastering one task type/family can help with mastering others.
+In this work, we are focusing on a parallel aspect of transfer learning.
+As both Image and Video QA can be seen as meta-problems, where the model has to develop a different reasoning process depending on the type/family of question (task, e.g.
+counting objects or finding the value of a specific object's attribute), we asked ourselves whether mastering one task type/family can help with mastering others.
+This work is thus also deeply related to multi-task learning~\cite{caruana1997multitask}.
 

### 2019-11-12 cvpr_submission/introduction.tex
Made contributions paragraph more readable + added comment.

@@
 The contributions of this paper are as follows.
-We propose a new model called SAMNet, that achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning.
-Next we show how different tasks impact when transfering the whole pretrained model in three main setups.
-In the first one focus on transfer learning within the Image QA domain and perform experiment similar to Taskonomy~\cite{zamir2018taskonomy} and analyse how training exclusively on one task family helps with mastering other family, with once but crucial difference: we transfer and fine-tune the whole model (not only the encoder).
-In the second we show a complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
-Finally, we present a set of experiments aimed at analysis of the impact of transfer learning in Video QA, when domain changes drastically and system has to deal with longer videos with higher complexity (understood as number of distractors present in each frame).
-%Surprisingly, our model with only small fine-tuning, managed to the master Hard variant and achieved higher accuracy than the model trained explicitly on Hard variant from the scratch.
+We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
+We show the impact of the different tasks when transferring the whole pretrained model in three main setups.
+\begin{itemize}
+	\item We first focus on transfer learning within the Image QA domain and perform experiments similar to Taskonomy~\cite{zamir2018taskonomy}.
+We analyze how training exclusively on one task family helps with mastering the others, with one notable difference: we transfer and fine-tune the whole model (not only the encoder or input layer).
+	\item Next, we show complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
+	\item Finally, we present a set of experiments aimed at analyzing of the impact of transfer learning in Video QA, when domain changes drastically and the model is forced to handle longer videos with higher complexity (i.e.
+a higher number of distractor objects present in each frame).
+\end{itemize}
+Surprisingly, our model with only small fine-tuning, managed to the master Hard variant and achieved higher accuracy than the model trained explicitly on Hard variant from the scratch.
 
 \tk{Have I addressed that correctly? I am not sure whether I have covered TL with CoGenT-A and CoGenT-B variants...}
+
+\vm{I think the contributions should be: 1.
+A new model with SotA results on COG |  2.
+transfer  / multitask learning  in COG | 3.
+transfer  / multitask learning  in CLEVR | 4.
+Ablation study ("all-but-one") in CLEVR and the limitations of transfer learning (e.g.
+the labels domains should be aligned)}.
+
 %A) Task generalization
@@
 %otherwise: binary y/n vs numers 0-7 vs names of attributes
-
-\section{Related work -- import}
-%Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
-Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.
-
-%Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \cite{mao2019neurosymbolic}.
-These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.
-Furthermore, symbolic priors (e.g., domain knowledge) and integration of logic depend on hand-crafted modules.
-In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability)\cite{vedantam2019probabilistic}.
-However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols \cite{taniguchi2018symbol}.
-
-Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have appeared in the past several years~\cite{mogadala2019trends}.
-Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g.
-object disappearance).
-To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
-Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
-Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
-However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
-
-As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
-The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
-Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
-For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2014memory}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.

### 2019-11-12 cvpr_submission/related_work.tex
Made contributions paragraph more readable + added comment.

@@
+\section{Related work -- import}
+%Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
+Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.
+
+%Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \cite{mao2019neurosymbolic}.
+These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.
+Furthermore, symbolic priors (e.g., domain knowledge) and integration of logic depend on hand-crafted modules.
+In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability)\cite{vedantam2019probabilistic}.
+However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols \cite{taniguchi2018symbol}.
+
+Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have appeared in the past several years~\cite{mogadala2019trends}.
+Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g.
+object disappearance).
+To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
+Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
+Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
+However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
+
+As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
+The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
+Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
+For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2014memory}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
+
 \section{Related work}

### 2019-11-12 cvpr_submission/related_work.tex
Merged the "imported" related work section with the newer one.

@@
-\section{Related work -- import}
+\section{Related work}
 %Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
@@
 
-Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have appeared in the past several years~\cite{mogadala2019trends}.
-Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g.
+Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.
+Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, most datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
+Prior work generally relied on dense visual features produced by either CNNs~\cite{xiong2016dynamic,yang2016stacked} or object detection modules~\cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings~\cite{teney2017graph, santoro2017simple}.
+
+A variety of new tasks integrating vision and language have appeared in the past several years~\cite{mogadala2019trends}.
+Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) as well as temporal aspects and relations (e.g.
 object disappearance).
-To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
-Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
-Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
-However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
+Earlier work~\cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video.
+These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.
+Learning long-term dependencies is also another challenge that LSTMs may struggle with.
+Yin et al.~\cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+
+% Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
+Another research focus area has been multimodal fusion and attention for VQA.
+For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal features \cite{zhou2015simple, antol2015}.
+Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard}.
+Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
+Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.
+Visualization of attention steps also provide interpretability, which is an increasingly important aspect.
+The MAC model \cite{hudson2018compositional} is a great example of such an approach.
+The follow-up model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
+Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.
 
@@
 
-\section{Related work}
-Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.
-Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
-Prior work generally relied on dense visual features produced by either CNNs \cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.
-
-Another research focus area has been multimodal fusion and
-attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
-features \cite{zhou2015simple, antol2015}.
-Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .
-Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
-Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.
-Visualization of attention steps also provide interpretability, which is an increasingly important aspect.
-The MAC model \cite{hudson2018compositional} is a great example of such an approach.
-The follow-on model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
-Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.
-
-Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .
-Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.
-These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.
-Learning long-term dependencies is also another challenge that LSTMs may struggle with.
-Yin et al.
-2019 \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
-Our work is mostly related to the MAC and MANN type models.
-An important distinction of our approach is the frame-by-frame processing of the video input.
+%Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .  
+Our work is mostly related to the MAC and MANN type models. An important distinction of our approach is the frame-by-frame processing of the video input.
 Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.

### 2019-11-12 cvpr_submission/experiments.tex
Changed table label to avoid formatting issue.

@@
 
-The results of these experiments are available in \Tab{tab:CoGenT_results}. 
+The results of these experiments are available in \Tab{tab:CoGenT-results}. 
 \begin{table}[htb]
@@
 	\caption{CLEVR-CoGenT accuracies for all 5 tasks when training on solely one task, jointly training on all tasks and finetuning on each task.
-For all experiments, the validation and test sets are identical.}\label{tab:CoGenT_results}
+For all experiments, the validation and test sets are identical.}\label{tab:CoGenT-results}
 	\begin{adjustbox}{width=0.5\textwidth}
@@
 
-Looking at the first section of \tab{tab:CoGenT_results}, we observe, unsurprisingly, that a model trained on a single task will do better on this task than on the others when being tested.
+Looking at the first section of \tab{tab:CoGenT-results}, we observe, unsurprisingly, that a model trained on a single task will do better on this task than on the others when being tested.
 Nevertheless, we also note that a model, trained on \textit{Exist} only, obtains a score slightly better than random on \textit{CompareInteger} \& \textit{CompareAttribute}.
@@
 \end{adjustbox}
-\caption{CoGenT accuracies with finetuning.}\label{tab:CoGenT_finetuning_results}
+\caption{CoGenT accuracies with finetuning.}\label{tab:CoGenT-finetuning-results}
 \end{table}

### 2019-11-12 cvpr_submission/samnet.tex
Moved all images into cvpr folder. Added model section.

--- 2019-11-05 COG_publications/2019_neurips_kr2ml/model.tex
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
+	\includegraphics[width=\textwidth]{img/architecture/samnet_architecture4}
 	\caption{General architecture of SAMNet}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+	\includegraphics[width=\textwidth]{img/architecture/samcell_reasoning}
 	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
@@
 a two-layer feedforward network with ELU activation used in the hidden layer of $d$ units.
-The output $\vec{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
+The output $\bm{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
 For the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
@@
 We perform a similar computation on the read head $\rhead_t$ over memory locations.
-We feed these two values along with the temporal class weights $\vec{\tau}_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
+We feed these two values along with the temporal class weights $\bm{\tau}_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
 in $[0,1]$ modulated for the current reasoning step:

### 2019-11-12 cvpr_submission/experiments.tex
Rewrote CLEVR experiments section.

@@
 
-We have trained SAMNet using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}, on the training set of the condition A of the CLEVR dataset (CLEVR-CoGenT)~\cite{johnson2017clevr}.
+We have trained SAMNet using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}, using the training set of the condition A of the CLEVR dataset (CLEVR-CoGenT)~\cite{johnson2017clevr}.
 For all experiments, the training procedure is as follows: we train the model for 20 epochs on 90\% of the training set of CoGenT.
@@
 \begin{itemize}
-	\item We first trained SAMNet on a single task group, and tested on this same task group.
-These 5 experiments (one per task group) fit into the traditional Deep Learning procedure of training and testing on the same task, or on samples drawn from the same distribution over an input domain (single-task learning).
-	\item Following, we trained SAMNet on all task groups jointly, and evaluated its performance on each group separately.
+	\item We first trained SAMNet on a single task group $t$, and tested on this same task group.
+These 5 experiments (one per task group) fit into the traditional Deep Learning procedure of training and testing on the same task, or on samples drawn from the same distribution over a common input domain (single-task learning).
+	\item Following, we trained SAMNet on all task groups jointly, and evaluated its performance on each group $t$ separately.
 The underlying hypothesis for this experiment is that learning jointly on all task groups would improve the performance on each task group.
-	\item Finally, we finetuned a model, trained on all task groups jointly, on each of the task groups separately.
-We are interested in two observations here: how significant is the performance gain, if any, on the finetuned task?
-And complementary, how significant is the performance drop, if any, on the other tasks?
+	\item Finally, for each task group $t$, we trained SAMNet on all tasks but $t$, and tested its performance on $t$.
+These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
 \end{itemize}
 
-The results of these experiments are available in \Tab{tab:CoGenT-results}. 
-\begin{table}[htb]
+\begin{figure}[!t]
 	\centering
-	\noindent
-	\caption{CLEVR-CoGenT accuracies for all 5 tasks when training on solely one task, jointly training on all tasks and finetuning on each task.
-For all experiments, the validation and test sets are identical.}\label{tab:CoGenT-results}
-	\begin{adjustbox}{width=0.5\textwidth}
-	\begin{tabular}{c c c c c c c }\toprule
-		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
-		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
-		\cmidrule(lr){2-7}
-		\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-7}
-		\multicolumn{1}{ c }{Exist only} & 26.07 & 74.20	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
-		\multicolumn{1}{ c }{Count only} & 14.89  & 0.0	& 62.78	& 0.0 & 0.0 & 0.0 \\ 
-		\multicolumn{1}{ c }{CompareInteger only} & 23.44 & 48.15	& 0.0	& 77.98	& 54.08 & 0.0 \\ 
-		\multicolumn{1}{ c }{CompareAttribute only} & 23.50 & 51.93	& 0.0 & 59.06 & 61.73 & 0.0 \\ 
-		\multicolumn{1}{ c }{QueryAttribute only} & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & 97.08 \\ 		
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-7}
+	\includegraphics[width=0.5\textwidth]{img/charts/CoGenT_results.pdf}
+	\caption{CLEVR-CoGenT accuracies for all 5 tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.
+For all experiments, the validation and test sets are identical.}
+	\label{fig:CoGenT-results}
+\end{figure}
 
-		\multicolumn{1}{ c }{All tasks} & 95.32 & 98.4 	& 86.75	& 96.0	& 98.65	& 98.02 \\ 
-		\cmidrule(lr){1-1}
-		\cmidrule(lr){2-7}
+The results of these experiments are available in \Fig{fig:CoGenT-results}. The complete set of results is available in Appendix \ref{sec:full-cogent-results}.
 
-		\multicolumn{1}{ c }{\textit{Trained on all tasks -- Finetune on $t$}} & &  & &  & &\\ 
-		\multicolumn{1}{ c }{Exist} &  & & & & & \\ 
-		\multicolumn{1}{ c }{Count} &  & & & & & \\
-		\multicolumn{1}{ c }{CompareInteger} &  & & & & & \\
-		\multicolumn{1}{ c }{CompareAttribute} &  & & & & & \\
-		\multicolumn{1}{ c }{QueryAttribute} &  & & & & & \\
+Looking at \Fig{fig:CoGenT-results}, we observe that single-task learning results in better-than-average performance on the same task.
+\textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks (\textit{yes} or \textit{no}); \textit{Count} has for corresponding labels the digits 0 through 10 (11 labels in total, hence a random agent would obtain ~9.1\% accuracy) and \textit{QueryAttribute} has for labels the set of object attributes values (15 labels, hence an an accuracy of 6.7\% would be associated with chance).
+In that perspective, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks.
 
-		\bottomrule
-	\end{tabular}
-    \end{adjustbox}
-\end{table}
+Nonetheless, significant accuracy gains are observed when training jointly on all 5 tasks.
+We indeed observe improvements ranging from 18 points to 37 points on 4 out of 5 tasks.
+\textit{QueryAttribute} does not benefit from such an improvement, only seeing an increase of one point in terms of test accuracy.
+One could qualify this task as \textit{self-sufficient}, as single- and multi-task learning performance are close.
+These accuracy improvements thus suggest that related tasks benefit from joint training, i.e.
+\emph{the whole is greater than the sum of the parts}.
+One further set of experiments here could favor the granularity of the observed improvements, by jointly training on $t$ and all possible subsets of the remaining 4 tasks.
+We hypothesize that the improvements on e.g.
+\textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e.
+labels domain).
+% 5 x 2^4 = 80 experiments to get that granularity.
 
-Looking at the first section of \tab{tab:CoGenT-results}, we observe, unsurprisingly, that a model trained on a single task will do better on this task than on the others when being tested.
-Nevertheless, we also note that a model, trained on \textit{Exist} only, obtains a score slightly better than random on \textit{CompareInteger} \& \textit{CompareAttribute}.
-This is due to the fact that these 3 task groups share the same labels space ('yes', 'no').
-\textit{Count} and \textit{QueryAttribute} have isolated labels space (('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10') and the set of object attributes values respectively) and we thus observe an accuracy of zero for these tasks, except when trained on these.
+Finally, the "all-tasks-but-$t$" experiments demonstrate that while task groups are related, one does not subsume another in terms of learning.
+Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
+We also observe accuracy of zero for \textit{Count} and \textit{QueryAttribute}.
+This is due to these tasks having distinct labels domains, which do not overlap with the other tasks labels domain.
+Thus, if holding out samples from \textit{Count} during training, a model will not be able to learn to predict the corresponding labels ('0' through '10').
 
-Training SAMNet on all tasks jointly, then testing it on each task, shows significant improvement on 4 out of 5 tasks, ranging from 18 points to 37 points.
-\textit{QueryAttribute} does not benefit from such an improvement, only seeing an increase of one point in terms of test accuracy.
-This suggests that \textit{QueryAttribute} is \textit{self-sufficient}, as the model is performing similarly between single-task learning and multi-task learning.
-
-Finally, we finetuned the model trained on all tasks on each task separately, for up to one epoch.
-The interest here is to observe if finetuning on a specific task can further boost the accuracy on this particular, while preserving the performance on other tasks (and thus the overall performance as well) similar.
-
-\begin{table}[htb]
-	\centering
-	\noindent
-	\begin{adjustbox}{width=0.5\textwidth}
-		\begin{tabular}{c c c c c c c }\toprule
-			\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
-			\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
-			\cmidrule(lr){2-7}
-			\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
-			\cmidrule(lr){1-1}
-			\cmidrule(lr){2-7}
-			\multicolumn{1}{ c }{All tasks but Exist} & 90.33 	& 60.42	& 86.12	& 96.18	& 98.52 & 98.60 \\ 
-			\multicolumn{1}{ c }{All tasks but Count} & 74.59 	& 97.51	& 0.0	& 94.37	& 98.42 & 98.47 \\ 
-			\multicolumn{1}{ c }{All tasks but CompareInteger} & 91.53 	& 98.22	& 86.09	& 56.35	& 98.78 & 98.40 \\ 
-			\multicolumn{1}{ c }{All tasks but CompareAttribute} & 81.92 	& 98.32	& 86.36	& 95.86	& 23.18 & 98.44 \\ 
-			\multicolumn{1}{ c }{All tasks but QueryAttribute} & 42.17 	& 76.79	& 54.64	& 79.87 & 64.13 & 0.0 \\
-
-			\cmidrule(lr){1-1}
-			\cmidrule(lr){2-7}
-			\multicolumn{1}{ c }{\textbf{Trained on all tasks but $t$ -- Finetune on $t$ }} & &  & &  & &\\ 
-			\multicolumn{1}{ c }{Exist} & 86.24 & 98.04 & 56.59 & 87.99 & 94.17 & 97.14 \\ 
-			\multicolumn{1}{ c }{Count} & 46.97 & 2.80 & 78.73 & 15.60 & 35.06 & 56.60 \\
-			\multicolumn{1}{ c }{CompareInteger} & 73.46 & 72.89 & 42.42 & 92.07 & 68.32 & 91.90 \\
-			\multicolumn{1}{ c }{CompareAttribute} & 48.16 & 85.77 & 30.84 & 77.20 & 97.72 & 13.21 \\
-			\multicolumn{1}{ c }{QueryAttribute} & 35.26 & 38.65 & 4.22 & 31.56 & 5.08 & 70.67 \\
-		\bottomrule
-	\end{tabular}
-\end{adjustbox}
-\caption{CoGenT accuracies with finetuning.}\label{tab:CoGenT-finetuning-results}
-\end{table}
-
-End of section
+A final set of experiment, for which the results are available in Appendix \ref{sec:full-cogent-results}, finetuned the model trained on all tasks on each task $t$ respectively.
+Given that the initial pretraining on all tasks, we were interested in the tradeoff between the significance of the performance gain, if any, on the finetuned task and the performance drop, if any, on the other tasks.
+Finetuning did not demonstrate a statistically meaningful benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
+Nevertheless, these experiments leave open the possibility that the training method for multi-task training could potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups.
+Recent work~\cite{guo2018dynamic, kendall2018multi} in this direction has been done, although seems to weigh the tasks rather than the samples.

### 2019-11-12 cvpr_submission/introduction.tex
Reverted modifications to the Related Work section.
Corrected some typos.

@@
 
-In computer vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+In Computer Vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
 That such transfer improves performance is appealing, knowing that both the domain (e.g.
 realistic images vs.
-medical ones or images with cars) and the task (e.g.
+medical or cars ones) and the task (e.g.
 image classification vs.
@@
 \end{itemize}
-Surprisingly, our model with only small fine-tuning, managed to the master Hard variant and achieved higher accuracy than the model trained explicitly on Hard variant from the scratch.
+Surprisingly, our model, with only small fine-tuning, managed to master the Hard variant of the COG dataset and achieved higher accuracy than the model trained solely on the Hard variant.
 
@@
 
-\vm{I think the contributions should be: 1.
-A new model with SotA results on COG |  2.
-transfer  / multitask learning  in COG | 3.
-transfer  / multitask learning  in CLEVR | 4.
-Ablation study ("all-but-one") in CLEVR and the limitations of transfer learning (e.g.
-the labels domains should be aligned)}.
+\vm{I think the contributions should be: 1. A new model with SotA results on COG |  2. transfer  / multitask learning  in COG | 3.  transfer  / multitask learning  in CLEVR}.
 

### 2019-11-12 cvpr_submission/related_work.tex
Corrected some typos.

--- 2019-11-12 cvpr_submission/related_work.tex
@@
+%\section{Related work -- import}
+%Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.
+Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.
+
+%Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \cite{mao2019neurosymbolic}.
+These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.
+Furthermore, symbolic priors (e.g., domain knowledge) and integration of logic depend on hand-crafted modules.
+In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability)\cite{vedantam2019probabilistic}.
+However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols \cite{taniguchi2018symbol}.
+
+%Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have appeared in the past several years~\cite{mogadala2019trends}.
+%Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g.
+object disappearance).
+%To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
+%Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
+%Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
+%However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
+
+%As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
+%The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
+%Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
+%For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2014memory}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
+
 \section{Related work}
@@
 features \cite{zhou2015simple, antol2015}.
-Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .
-Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
+Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard}.
+Attention  research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
 Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.
@@
 The MAC model \cite{hudson2018compositional} is a great example of such an approach.
-The follow-on model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
+The follow-on model by the same authors~\cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
 Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.
 
-Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .
-Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.
-These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.
+Video Question Answering, aside from spatial queries, also focuses on questions that require \emph{temporal} reasoning.
+Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video.
+These approaches might be sufficient for action-recognition type of tasks but fall short when spatio-temporal reasoning is required.
 Learning long-term dependencies is also another challenge that LSTMs may struggle with.
 Yin et al.
-2019 \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+\cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
 Our work is mostly related to the MAC and MANN type models.
 An important distinction of our approach is the frame-by-frame processing of the video input.
-Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
-Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.
+Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by an aggregation over clips to form a single video representation.
+Nevertheless, when reasoning and producing the answer, the system has \emph{access to all frames}.
 Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.

### 2019-11-13 cvpr_submission/introduction.tex
Update introduction.tex

--- 2019-11-12 cvpr_submission/introduction.tex
@@
 \section{Introduction}
-In recent years, neural networks, at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
+In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from  Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
 At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.
@@
 However, in many real-world scenarios, this assumption does not hold.
-Moreover, as modern neural models often have  millions of trainable parameters, training them requires vast amount of data, which for some domains (notably medical) can be very expensive and/or extremely difficult to collect.
-One of the widely accepted solutions for the problems mentioned above is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enables model - and thus performance - improvements by transferring \emph{information} from one domain to another.
+Moreover, as modern neural models often have  millions of trainable parameters, training them requires vast amounts of data, which for some domains (e.g., medical) can be very expensive and/or extremely difficult to collect.
+One of the widely used solutions for the above mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances the  model performance by transferring \emph{information} from one domain to another.
 
@@
 
-In computer vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
-That such transfer improves performance is appealing, knowing that both the domain (e.g.
+In computer vision, it is now a standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+Such performance improvements are appealing, especially for cases that both the domain (e.g.
 realistic images vs.
@@
 
-A similar development can be noted in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, some where labeled data is less accessible.
-Recently, we can denote an accelerated development of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amount of data.
-Analogically to the pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
+A similar development has emerged in the Natural Language Processing (NLP) community.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, especially when labeled data is less accessible.
+Recently, we observe a growing utilization of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amounts of data.
+In analogy to the pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
 HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
 
-The success of transfer learning raises several questions, such as which characteristics make a dataset favorable for use in pretraining (notably ImageNet~\cite{huh2016makes}), or what explains the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
-One of the most systematic work studying the impact of transfer learning in computer vision is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.
+The success of transfer learning raises several questions for research, such as the characteristics which make a dataset more favorable to use in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
+One of the most systematic in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aim to discover the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.
 
-The impact of transfer learning is even more central in the case of multi-modal tasks~\cite{mogadala2019trends}, combining both of the modalities mentioned above (i.e. vision and language).
-One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
-In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
-
-In this work, we are focusing on a parallel aspect of transfer learning.
+The impact of transfer learning is even more essential in the case of multi-modal tasks, \cite{mogadala2019trends}, which combine both modalities mentioned above (i.e. vision and language).
+%One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
+%In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
+In this work, we focus on a parallel aspect of transfer learning.
 As both Image and Video QA can be seen as meta-problems, where the model has to develop a different reasoning process depending on the type/family of question (task, e.g.
-counting objects or finding the value of a specific object's attribute), we asked ourselves whether mastering one task type/family can help with mastering others.
-This work is thus also deeply related to multi-task learning~\cite{caruana1997multitask}.
+counting objects or finding the value of a specific object's attribute), we investigated  whether mastering one task type/family can help to master others.
+Thus, this work is also deeply related to multi-task learning~\cite{caruana1997multitask}.
 

### 2019-11-13 cvpr_submission/experiments.tex
Ported the Experiments subsections over from the kr2ml version.

@@
 
-\subsection{Multi-task learning}
+We have implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
+We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning.
+We have also evaluated the model's performance on the CLEVR dataset~\cite{johnson2017clevr}, designed for Image Question Answering.
+Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
+For this purpose, we used two variants of the COG dataset: an easy one (Canonical) and a Hard version.
+The main differences are the number of frames in the input sequence (4 vs.
+8) and the maximum number of distractors (i.e., objects not relevant for the answer) per single frame (1 vs.
+10).
+For CLEVR, we considered the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
+More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
 
-\subsubsection{CLEVR tasks}
+\subsection{Performance comparison with the COG baseline}
+
+In our experiments, we have trained SAMNet using 8 reasoning steps and the external memory having 8 address locations, each being a vector of 128 floats.
+%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
+We focused on 22 classification tasks and compared our results with the baseline model.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}, whereas full comparison can be found in Appendix~\ref{sec:cog-all-results}.
+
+\begin{figure*}[!t]
+	\centering
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_canonical_no_labels.png}
+	\end{subfigure}%
+	\newline
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_hard.png}
+	\end{subfigure}%
+	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+	\label{fig:samnet_cog_detailed}
+\end{figure*}
+
+For the Canonical variant (top row), we have achieved similar accuracies for the majority of tasks (with the total average accuracy of 98.0\% in comparison of 97.6\% achieved by the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
+As those tasks focus on compositional questions referring to two objects, we hypothesize that our model achieved better accuracy due to the ability to selectively pick and store the relevant objects from the past frames in the memory.
+Despite there being some tasks in which our model reached slightly lower accuracies,
+% (between 0.2 and 1.8 points)
+when comparing performances on the Hard variant, it improves upon the COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
+
+\subsection{Temporal generalization capabilities}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{img/results/samnet_cog_overall_transfer.png}
+	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\label{fig:samnet_cog_overall_transfer}
+\end{figure}
+
+The goal of the next set of experiments was to test the generalization ability concerning the sequence length and number of distractors.
+For that purpose, we have compared the accuracies of both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
+As the original paper does not include such experiments, we have performed them on our own.
+The light gray color indicates the original results, whereas dark gray indicates the accuracies of COG models that we have trained (fine-tuning/testing) using the original code provided by the authors.
+For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning.
+In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
+We have also tested both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
+In this case, the SAMNet model also reached much better performance, and, interestingly, achieved better scores from the model trained and tested exclusively on the Hard variant.
+
+\subsection{Multi-task learning on the CLEVR and COG tasks}
 \vm{Will have to rephrase this in accordance with Jayram's definition.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{img/charts/CoGenT_results.pdf}
+	\includegraphics[width=0.5\textwidth]{img/results/CoGenT_results.pdf}
 	\caption{CLEVR-CoGenT accuracies for all 5 tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.
@@
 Recent work~\cite{guo2018dynamic, kendall2018multi} in this direction has been done, although seems to weigh the tasks rather than the samples.
+
+\subsection{Domain Adaptation}
+
+\vm{todo...}

### 2019-11-13 cvpr_submission/related_work.tex

@@
 features \cite{zhou2015simple, antol2015}.
-Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard}.
-Attention  research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
+Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .
+Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
 Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.
@@
 The MAC model \cite{hudson2018compositional} is a great example of such an approach.
-The follow-on model by the same authors~\cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
+The follow-on model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
 Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.
 
-Video Question Answering, aside from spatial queries, also focuses on questions that require \emph{temporal} reasoning.
-Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video.
-These approaches might be sufficient for action-recognition type of tasks but fall short when spatio-temporal reasoning is required.
+Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .
+Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.
+These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.
 Learning long-term dependencies is also another challenge that LSTMs may struggle with.
 Yin et al.
-\cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+2019 \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
 Our work is mostly related to the MAC and MANN type models.
 An important distinction of our approach is the frame-by-frame processing of the video input.
-Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by an aggregation over clips to form a single video representation.
-Nevertheless, when reasoning and producing the answer, the system has \emph{access to all frames}.
+Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
+Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.
 Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.

### 2019-11-13 cvpr_submission/experiments.tex
Several corrections throughout the paper.

@@
 We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning.
-We have also evaluated the model's performance on the CLEVR dataset~\cite{johnson2017clevr}, designed for Image Question Answering.
+We have also evaluated the model's performance on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
 Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[htb]
 	\centering
@@
 
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{img/results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
-	\label{fig:samnet_cog_overall_transfer}
-\end{figure}
-
 The goal of the next set of experiments was to test the generalization ability concerning the sequence length and number of distractors.
@@
 For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on Canonical variant, without any fine-tuning.
-In a pure \textit{transfer learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
+In a pure \textit{zero-shot learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
 We have also tested both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
@@
 
-\subsection{Multi-task learning on the CLEVR and COG tasks}
-\vm{Will have to rephrase this in accordance with Jayram's definition.}
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{img/results/samnet_cog_overall_transfer.png}
+	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\label{fig:samnet_cog_overall_transfer}
+\end{figure}
 
-We have trained SAMNet using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}, using the training set of the condition A of the CLEVR dataset (CLEVR-CoGenT)~\cite{johnson2017clevr}.
-For all experiments, the training procedure is as follows: we train the model for 20 epochs on 90\% of the training set of CoGenT.
+\subsection{Multi-task learning on CLEVR and COG tasks}
+
+%We have trained SAMNet using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}, using the training set of the condition A of the CLEVR dataset (CLEVR-CoGenT)~\cite{johnson2017clevr}.
+%For all experiments, the training procedure is as follows: we train the model for 20 epochs on 90\% of the training set of CoGenT.
 We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets (CoGenT-A  \& -B) as test sets.
@@
 
-We consider as task groups the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+For the CLEVR dataset, we consider as task groups the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
 In order to investigate the potential benefits of multi-task learning, we conducted the following experiments:
@@
 \begin{itemize}
-	\item We first trained SAMNet on a single task group $t$, and tested on this same task group.
-These 5 experiments (one per task group) fit into the traditional Deep Learning procedure of training and testing on the same task, or on samples drawn from the same distribution over a common input domain (single-task learning).
-	\item Following, we trained SAMNet on all task groups jointly, and evaluated its performance on each group $t$ separately.
-The underlying hypothesis for this experiment is that learning jointly on all task groups would improve the performance on each task group.
+	\compresslist
+	\item We first trained SAMNet on a single task group $t$, and tested on this same task group. These 5 experiments fit into the traditional Deep Learning procedure of single-task learning.
+	\item Following, we trained SAMNet on all task groups jointly, and evaluated its performance on each task $t$ separately.
 	\item Finally, for each task group $t$, we trained SAMNet on all tasks but $t$, and tested its performance on $t$.
@@
 	\includegraphics[width=0.5\textwidth]{img/results/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all 5 tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.
+	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.
 For all experiments, the validation and test sets are identical.}
@@
 Looking at \Fig{fig:CoGenT-results}, we observe that single-task learning results in better-than-average performance on the same task.
-\textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks (\textit{yes} or \textit{no}); \textit{Count} has for corresponding labels the digits 0 through 10 (11 labels in total, hence a random agent would obtain ~9.1\% accuracy) and \textit{QueryAttribute} has for labels the set of object attributes values (15 labels, hence an an accuracy of 6.7\% would be associated with chance).
+\textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $\sim$9.1\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
 In that perspective, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks.
@@
 We indeed observe improvements ranging from 18 points to 37 points on 4 out of 5 tasks.
-\textit{QueryAttribute} does not benefit from such an improvement, only seeing an increase of one point in terms of test accuracy.
-One could qualify this task as \textit{self-sufficient}, as single- and multi-task learning performance are close.
-These accuracy improvements thus suggest that related tasks benefit from joint training, i.e.
-\emph{the whole is greater than the sum of the parts}.
-One further set of experiments here could favor the granularity of the observed improvements, by jointly training on $t$ and all possible subsets of the remaining 4 tasks.
+\textit{QueryAttribute} does not benefit from such an improvement, only seeing an increase of one point.
+One could qualify it as \textit{self-sufficient}, as single- and multi-task learning performance are close.
+These accuracy improvements thus suggest that related tasks benefit from joint training. % i.e. \emph{the whole is greater than the sum of the parts}.
+To increase the granularity of the observed improvements, we plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks.
 We hypothesize that the improvements on e.g.
@@
 We also observe accuracy of zero for \textit{Count} and \textit{QueryAttribute}.
-This is due to these tasks having distinct labels domains, which do not overlap with the other tasks labels domain.
-Thus, if holding out samples from \textit{Count} during training, a model will not be able to learn to predict the corresponding labels ('0' through '10').
+This is due to these tasks having distinct labels domains, which do not overlap with the other tasks.
+Thus, if holding out samples from \textit{Count} during training, a model will not be able to learn to predict the corresponding labels.
 
 A final set of experiment, for which the results are available in Appendix \ref{sec:full-cogent-results}, finetuned the model trained on all tasks on each task $t$ respectively.
-Given that the initial pretraining on all tasks, we were interested in the tradeoff between the significance of the performance gain, if any, on the finetuned task and the performance drop, if any, on the other tasks.
+Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the finetuned task and the drop, if any, on the other tasks.
 Finetuning did not demonstrate a statistically meaningful benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
 Nevertheless, these experiments leave open the possibility that the training method for multi-task training could potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups.
-Recent work~\cite{guo2018dynamic, kendall2018multi} in this direction has been done, although seems to weigh the tasks rather than the samples.
+Recent work~\cite{guo2018dynamic, kendall2018multi} in this direction has been done, although seems to weigh the tasks rather than samples.
 

### 2019-11-13 cvpr_submission/introduction.tex
Several corrections throughout the paper.

@@
 In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
-At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.
-sampled from a common input space under similar data distribution characteristics.
+At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.\ sampled from a common input space under similar data distribution characteristics.
 However, in many real-world scenarios, this assumption does not hold.
@@
 
-In computer vision, it is now a standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
-Such performance improvements are appealing, especially for cases that both the domain (e.g.
+In Computer Vision, it is now a standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+Such performance improvements are appealing, especially for cases where both the domain (e.g.
 realistic images vs.
-medical ones or images with cars) and the task (e.g.
+medical or cars ones) and the task (e.g.
 image classification vs.
@@
 The success of transfer learning raises several questions for research, such as the characteristics which make a dataset more favorable to use in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
-One of the most systematic in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aim to discover the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.
+One of the most systematic work in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aim to discover the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.
 

### 2019-11-13 cvpr_submission/related_work.tex
Several corrections throughout the paper.

--- 2019-11-12 cvpr_submission/related_work.tex
@@
 Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
-Prior work generally relied on dense visual features produced by either CNNs \cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.
+Prior work generally relied on dense visual features produced by either CNNs~\cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.
 
-Another research focus area has been multimodal fusion and
-attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
-features \cite{zhou2015simple, antol2015}.
-Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard}.
-Attention  research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.
-Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.
+Another research focus area has been multimodal fusion and attention for VQA.
+For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal features~\cite{zhou2015simple, antol2015}.
+Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions~\cite{fukui2016multimodal, kim2016hadamard}.
+Attention research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach~\cite{yang2016stacked, chen2015abc, ilievski2016focused}.
+Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods~\cite{hudson2018compositional, song2018explore}.
 Visualization of attention steps also provide interpretability, which is an increasingly important aspect.
@@
 The follow-on model by the same authors~\cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.
-Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.
+Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction~\cite{haurilet2019s, teney2017graph, kim2018dynamic}.
 
-Video Question Answering, aside from spatial queries, also focuses on questions that require \emph{temporal} reasoning.
-Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video.
+Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning.
+Early works~\cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video.
 These approaches might be sufficient for action-recognition type of tasks but fall short when spatio-temporal reasoning is required.
 Learning long-term dependencies is also another challenge that LSTMs may struggle with.
-Yin et al.
-\cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+Yin et al.~\cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+
 Our work is mostly related to the MAC and MANN type models.
 An important distinction of our approach is the frame-by-frame processing of the video input.
-Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by an aggregation over clips to form a single video representation.
-Nevertheless, when reasoning and producing the answer, the system has \emph{access to all frames}.
+Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore}, the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
+Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.
 Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.

### 2019-11-13 cvpr_submission/samnet.tex
Fixed figure
Several corrections throughout the paper.

@@
 
-\begin{figure}[b!]
+\begin{figure*}[!t]
 	\centering
-	\includegraphics[width=\textwidth]{img/architecture/samnet_architecture4}
+	\includegraphics[width=\textwidth]{img/architecture/SAMNETmodel}
 	\caption{General architecture of SAMNet}
 	\label{fig:samnet}
-\end{figure}
+\end{figure*}
 
-SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}).
-At the conceptual level SAMNet draws from two core ideas:
-compositional reasoning as proposed e.g. in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer}
-and utilization of external memory in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
+SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level SAMNet draws from two core ideas:
+compositional reasoning as proposed e.g.
+in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and utilization of external memory in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
 
@@
 The memory can be accessed through either content-based addressing, via dot-product attention, or location-based addressing.
-Using gating mechanisms, correct objects can be retrieved 
-in order to perform multi-step spatio-temporal reasoning over text and video.  
+Using gating mechanisms, correct objects can be retrieved in order to perform multi-step spatio-temporal reasoning over text and video.
 A notable feature of this design is that the number of addresses $N$ can be set to different values during training and testing to fit the characteristics of data.
 
-\begin{figure}[t!]
-	\centering
-	\includegraphics[width=\textwidth]{img/architecture/samcell_reasoning}
-	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
-	\label{fig:samcell}
-\end{figure}
+%\begin{figure}[t!]
+%	\centering
+%	\includegraphics[width=\textwidth]{img/architecture/samcell_reasoning}
+%	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
+%	\label{fig:samcell}
+%\end{figure}
 
-The core of SAMNet is a recurrent cell called a SAM Cell (\cref{fig:samcell}). 
-Unrolling a new series of $T$ cells for every frame enables $T$ steps of compositional
-reasoning, similar to~\cite{hudson2018compositional}.
+The core of SAMNet is a recurrent cell called a SAM Cell.
+Unrolling a new series of $T$ cells for every frame enables $T$ steps of compositional reasoning, similar to~\cite{hudson2018compositional}.
 Information flows between frames through the external memory.
@@
 The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
-A similar operation on memory yields the object $\vec{mo}_t$. The memory operation is based on an attention mechanism,
-and resembles content-based addressing on memory. Therefore, we obtain an attention vector over memory addresses
-that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
-Note that the returned objects may be invalid, 
-e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid 
-even if the current frame contains a red square.
+A similar operation on memory yields the object $\vec{mo}_t$.
+The memory operation is based on an attention mechanism, and resembles content-based addressing on memory.
+Therefore, we obtain an attention vector over memory addresses that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
+Note that the returned objects may be invalid, e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid even if the current frame contains a red square.
 
@@
 %\paragraph{Reasoning Unit.}
-This module is the backbone of SAMNet that determines what gating operations need to be performed on the external memory, as well as
-determining the location of the correct object for reasoning.
+This module is the backbone of SAMNet that determines what gating operations need to be performed on the external memory, as well as determining the location of the correct object for reasoning.
 To determine whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
@@
 \noindent{\textbf{Memory Update Unit.}}
-Unit first determines the memory location where an object could be added:
+The unit first determines the memory location where an object could be added:
 \[ \vec{w}_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
 Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
-The sum of components of $\vec{w}_t$ is at most equal to 1; and $\vec{w}_t$ can even equal 0, e.g., whenever neither condition
-of adding a new object nor replacing an existing object holds true.
+The sum of components of $\vec{w}_t$ is at most equal to 1; and $\vec{w}_t$ can even equal 0, e.g., whenever neither condition of adding a new object nor replacing an existing object holds true.
 We then update the memory accordingly as:

### 2019-11-13 cvpr_submission/experiments.tex
Several improvements to the Experiments sections. Clearer CLEVR barcharts, Shorter sentences.

--- 2019-11-12 cvpr_submission/experiments.tex
@@
 \section{Experiments}
+We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}.
+We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
+Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
+For this purpose, we used two variants of both datasets.
+For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence (4 vs.
+8) and the maximum number of distractors (i.e., objects not relevant for the answer) per single frame (1 vs.
+10).
+For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
+More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
 
-\subsection{Multi-task learning}
+\subsection{Performance comparison with the COG baseline}
 
-\subsubsection{CLEVR tasks}
-\vm{Will have to rephrase this in accordance with Jayram's definition.}
+We trained SAMNet using 8 reasoning steps and external memory of 8 128-floats address locations.
+%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
+We focused on 22 classification tasks and compared our results with the baseline model.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in Appendix~\ref{sec:cog-all-results}.
 
-We have trained SAMNet using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}, using the training set of the condition A of the CLEVR dataset (CLEVR-CoGenT)~\cite{johnson2017clevr}.
-For all experiments, the training procedure is as follows: we train the model for 20 epochs on 90\% of the training set of CoGenT.
-We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets (CoGenT-A  \& -B) as test sets.
-We used NVIDIA's GeForce GTX TITAN X GPUs.
+\begin{figure*}[htb]
+	\centering
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_canonical_no_labels.png}
+	\end{subfigure}%
+	\newline
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_hard.png}
+	\end{subfigure}%
+	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+	\label{fig:samnet_cog_detailed}
+\end{figure*}
 
-We consider as task groups the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-In order to investigate the potential benefits of multi-task learning, we conducted the following experiments:
+For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, compared to 97.6\% for the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
+As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
+Despite there being some tasks in which our model reached slightly lower accuracies,
+% (between 0.2 and 1.8 points)
+when comparing performances on the Hard variant, it improves upon the COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
 
+\subsection{Temporal generalization capabilities on COG}
+
+The goal here is to test the generalization ability concerning the sequence length and number of distractors.
+For that purpose, we compare both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
+As the original paper does not include these experiments, we performed them.
+The light gray color indicates original results, whereas dark gray indicates the accuracies of COG models which we trained (fine-tuning/testing) using the original code provided by the authors.
+For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on the Canonical variant, without any fine-tuning.
+In a pure \textit{zero-shot learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
+We also test both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
+In this case, the SAMNet model also reaches much better performance and, interestingly, performs better than the model trained solely on the Hard variant.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{img/results/samnet_cog_overall_transfer.png}
+	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\label{fig:samnet_cog_overall_transfer}
+\end{figure}
+
+\subsection{Multi-task learning on CLEVR and COG}
+In these experiments, we focus on analyzing the impact of each task relatively to others when training jointly.
+
+\subsubsection{CLEVR}
+For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute} and conducted the following experiments:
 \begin{itemize}
-	\item We first trained SAMNet on a single task group $t$, and tested on this same task group.
-These 5 experiments (one per task group) fit into the traditional Deep Learning procedure of training and testing on the same task, or on samples drawn from the same distribution over a common input domain (single-task learning).
-	\item Following, we trained SAMNet on all task groups jointly, and evaluated its performance on each group $t$ separately.
-The underlying hypothesis for this experiment is that learning jointly on all task groups would improve the performance on each task group.
-	\item Finally, for each task group $t$, we trained SAMNet on all tasks but $t$, and tested its performance on $t$.
-These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
+	\compresslist
+	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional Deep Learning procedure of single-task learning,
+	\item Train SAMNet on all task groups jointly, and evaluate its performance on each task $t$ separately,
+	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$.
+%These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
 \end{itemize}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{img/charts/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all 5 tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.
-For all experiments, the validation and test sets are identical.}
+	\includegraphics[width=0.5\textwidth]{img/results/CoGenT_results.pdf}
+	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
 	\label{fig:CoGenT-results}
@@
 
-The results of these experiments are available in \Fig{fig:CoGenT-results}. The complete set of results is available in Appendix \ref{sec:full-cogent-results}.
+Noticeable results are shown in \Fig{fig:CoGenT-results}, while the complete set is available in Appendix \ref{sec:full-cogent-results}.
 
-Looking at \Fig{fig:CoGenT-results}, we observe that single-task learning results in better-than-average performance on the same task.
-\textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks (\textit{yes} or \textit{no}); \textit{Count} has for corresponding labels the digits 0 through 10 (11 labels in total, hence a random agent would obtain ~9.1\% accuracy) and \textit{QueryAttribute} has for labels the set of object attributes values (15 labels, hence an an accuracy of 6.7\% would be associated with chance).
-In that perspective, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks.
+Looking at \Fig{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (dark blue).
+Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
 
-Nonetheless, significant accuracy gains are observed when training jointly on all 5 tasks.
-We indeed observe improvements ranging from 18 points to 37 points on 4 out of 5 tasks.
-\textit{QueryAttribute} does not benefit from such an improvement, only seeing an increase of one point in terms of test accuracy.
-One could qualify this task as \textit{self-sufficient}, as single- and multi-task learning performance are close.
-These accuracy improvements thus suggest that related tasks benefit from joint training, i.e.
-\emph{the whole is greater than the sum of the parts}.
-One further set of experiments here could favor the granularity of the observed improvements, by jointly training on $t$ and all possible subsets of the remaining 4 tasks.
+Nevertheless, significant accuracy gains are noted when training jointly on all tasks (light gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
+\textit{QueryAttribute} only sees an increase of one point.
+One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
+These improvements suggest that related tasks benefit from joint training.
+We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
 We hypothesize that the improvements on e.g.
@@
 labels domain).
-% 5 x 2^4 = 80 experiments to get that granularity.
 
-Finally, the "all-tasks-but-$t$" experiments demonstrate that while task groups are related, one does not subsume another in terms of learning.
+Finally, the "all-tasks-but-$t$" experiments (cyan) demonstrate that while tasks are related, one does not subsume another in terms of learning.
 Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
-We also observe accuracy of zero for \textit{Count} and \textit{QueryAttribute}.
-This is due to these tasks having distinct labels domains, which do not overlap with the other tasks labels domain.
-Thus, if holding out samples from \textit{Count} during training, a model will not be able to learn to predict the corresponding labels ('0' through '10').
+We also observe no learning for \textit{Count} and \textit{QueryAttribute}, caused by these tasks having distinct labels domains, which do not overlap with the other tasks.
+Thus, if holding out samples from \textit{Count} during training, a model will not be able to predict the corresponding labels.
 
-A final set of experiment, for which the results are available in Appendix \ref{sec:full-cogent-results}, finetuned the model trained on all tasks on each task $t$ respectively.
-Given that the initial pretraining on all tasks, we were interested in the tradeoff between the significance of the performance gain, if any, on the finetuned task and the performance drop, if any, on the other tasks.
-Finetuning did not demonstrate a statistically meaningful benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
-Nevertheless, these experiments leave open the possibility that the training method for multi-task training could potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups.
-Recent work~\cite{guo2018dynamic, kendall2018multi} in this direction has been done, although seems to weigh the tasks rather than the samples.
+An supplementary set of experiments, for which results are available in Appendix \ref{sec:full-cogent-results}, finetune the model trained on all tasks on each task $t$ respectively.
+Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the finetuned task and the drop, if any, on other tasks.
+Finetuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
+Nevertheless, these experiments leave open the possibility that the multi-task learning training method may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups.
+Recent work~\cite{guo2018dynamic, kendall2018multi} in this direction has been done, although seems to weigh tasks rather than samples.
+
+\subsubsection{COG}
+\tsj{todo}
+
+\subsection{Domain Adaptation}
+
+The final set of experiments we consider is related to \emph{Domain Adaptation}.
+According to \cite{pan2009survey}, this settings considers different but related source and target domains, under a common task.
+\subsubsection{CLEVR-CoGenT}
+The CoGenT-A \& -B sets of CLEVR differ by the available combinations of object attributes.
+If we consider the input domain to be the set of objects with all attributes values, both sets differ by the data distribution they are sampled from.
+We thus consider 2 experiments with SAMNet trained on CoGenT-A: A direct generalization test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following the procedure of~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}.
+The results are available in \Fig{fig:CoGenT-B-results}.
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.3\textwidth]{img/results/CoGenT_B_results.pdf}
+	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.}
+	\label{fig:CoGenT-B-results}
+\end{figure}
+Evaluating SAMNet on CoGenT shows that performance is worse on CoGenT-B than CoGenT-A, in line with~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.
+Finetuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A, also observed in other models.
+
+\subsubsection{COG}
+\tsj{todo}

### 2019-11-13 cvpr_submission/transfer_learning.tex
no message

\section{Transfer Learning}

\begin{figure*}
	\caption{Transfer learning taxonomy}
	\label{fig:taskonomy}
	\includegraphics[width=0.8\textwidth]{img/architecture/transfer_taxo}
\end{figure*}

We follow the notations in the survey by~\cite{pan-yang}.
A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
For visual reasoning problems considered in this paper, 
$\cX$ will consist of purely visual inputs, i.e., either images or videos, in some cases, or 
a combination of both visual inputs and questions in other cases. 
A \emph{task} is a pair $\cT= (\cY,f(X))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the 
question\footnote{%
	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas for typical video answering datasets,
	only a single answer is needed for the entire video.}. % 
If the domain elements consist of just the visual inputs, then the task is defined by the question so that each question 
defines a separate task.
\begin{definition}[\cite{pan-yang}]
	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 
	learning of the target predictive function $f_T(\cdot)$ in $\cD_T$ using the knowledge  in $\cD_S$ and $\cT_S$, where $\cD_S \ne \cD_T$, or $\cT_S \ne \cT_T$.
\end{definition}
In all our applications, $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the marginal distributions $P_S$ and $P_T$ are different.
Similarly, $\cT_S \ne \cT_T$ means that either $Y_S \ne Y_T$ or that the associated prediction functions are different.

While the above definition is quite general, they do not adequately capture all the artifacts present in the visual reasoning.
For example, consider \emph{domain adaptation}, defined  in the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
but the marginal distributions $P_S$ and $P_T$ are different.
One setting is the case of static images, where this could be due to having different feature combinations in the source and
target but a different setting is in the context of video reasoning where the number of frames can be small in one case and 
large in another.
These require possibly very different methods, one involving building disentangled feature representations that can generalize across 
domains and another in which we might need memory-augmented neural networks that can generalize across frame lengths.
Another situation is when the  the questions themselves can be grouped in to families which entails studying transfer learning
in the context of different groups of questions, perhaps even all of them simultaneously.
This requires a slightly modifying the above definition.

Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
\begin{description}
	\item[Feature Transfer:] In this setting of domain adaptation $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on $v$.
	The marginal distributions $P_S$ and $P_T$ differ in the just the feature attributes such as shape, color, and size, or their combinations
	thereof.
	\item[Temporal Transfer:] This setting is similar to attribute adaptation in that $\cX_S = \cX_T \subseteq \cQ \times \cV$.
	The key difference is that we introduce a notion of complexity $C(v) = (n, m)$ for a visual input $v$,
	where $n$ equals the maximum number of objects $n$ in an image, and $m$
	equals  the number of frames in a vide. 
	For any visual input $v_S$ coming from $X_S$ with $C(v_S) = (n_S, m_S)$
	and for any visual input $v_T$ coming from $X_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and 
	$m_T \ge m_S$ which at least one inequality being a strict one. 
	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.
	\item[Reasoning Transfer:]
\end{description}

### 2019-11-13 cvpr_submission/transfer_learning.tex
Removed duplicate entries in bib + corrected crop of taxonomy image.

@@
 \begin{figure*}
+	\centering
 	\caption{Transfer learning taxonomy}
@@
 
-We follow the notations in the survey by~\cite{pan-yang}.
+We follow the notations in the survey by~\cite{pan2009survey}.
 A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
@@
 defines a separate task.
-\begin{definition}[\cite{pan-yang}]
+\begin{definition}[\cite{pan2009survey}]
 	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 

### 2019-11-13 cvpr_submission/transfer_learning.tex
Finished section on transfer learning

--- 2019-11-13 cvpr_submission/transfer_learning.tex
@@
 a combination of both visual inputs and questions in other cases. 
-A \emph{task} is a pair $\cT= (\cY,f(X))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
+A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
 When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the 
@@
 defines a separate task.
-\begin{definition}[\cite{pan-yang}]
+\begin{definition}[\cite{pan-yang}] \label{defn:transfer}
 	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 
@@
 
-While the above definition is quite general, they do not adequately capture all the artifacts present in the visual reasoning.
-For example, consider \emph{domain adaptation}, defined  in the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
-but the marginal distributions $P_S$ and $P_T$ are different.
+Although~\cref{defn:transfer} is quite general, it does not adequately capture all the artifacts present in the visual reasoning.
+For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
+but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
 One setting is the case of static images, where this could be due to having different feature combinations in the source and
@@
 domains and another in which we might need memory-augmented neural networks that can generalize across frame lengths.
-Another situation is when the  the questions themselves can be grouped in to families which entails studying transfer learning
-in the context of different groups of questions, perhaps even all of them simultaneously.
-This requires a slightly modifying the above definition.
+Another situation is when the questions themselves can be grouped into families such as count-based queries, 
+comparison of objects, or existence of objects with certain features etc.
+This entails studying transfer learning between families of tasks which requires extending the above definition.
 
@@
 	\item[Feature Transfer:] In this setting of domain adaptation $\cX_S = \cX_T \subseteq \cQ \times \cV$
-	and the task $f(q,v)$ is just the answer to the question $q$ on $v$.
+	and the task $f(q,v)$ is just the answer to the question $q$ on $v$. The output set $\cY$ is the union of legitimate answers
+	over all questions in $\cQ$.
 	The marginal distributions $P_S$ and $P_T$ differ in the just the feature attributes such as shape, color, and size, or their combinations
 	thereof.
-	\item[Temporal Transfer:] This setting is similar to attribute adaptation in that $\cX_S = \cX_T \subseteq \cQ \times \cV$.
+
+	\item[Temporal Transfer:] This setting is similar to attribute adaptation in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
+	and there is a single task.
 	The key difference is that we introduce a notion of complexity $C(v) = (n, m)$ for a visual input $v$,
@@
 	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.
+
 	\item[Reasoning Transfer:]
+	This setting requires an extension of~\cref{defn:transfer} given above to investigate transfer learning when
+	grouping questions into families. Let $\cV$ be the feature space consisting of visual inputs only, shared by
+	all tasks, with a common marginal distribution $P(X)$. For each question $q \in \cQ$, we define the task 
+	$\cT_q = (\cY_q, f_q(\cdot))$ where
+	the output set $\cY_q$ is the set of legitimate answers to $q$ and $f_q(v)$, for a visual input $v$, 
+	is the answer to question $q$ on visual input $v$.
+	Thus tasks are in a 1-1 correspondence with questions.
+	A \emph{task family} is a probability distribution on tasks which our case can be obtained by defining the distribution on $\cQ$. 
+	Given a task family, the goal is to learn a prediction function that gives an answer to $f_q(v)$ for $v \in \cV$ chosen according 
+	to the feature space distribution and $q$ chosen according to the task probability distribution.
+	Suppose $\cF_S$ is the source task family and $\cF_T$ is the target task family.
+	Transfer learning aims to help improve the learning of the predictive function for the target task family 
+	using the knowledge in the source task family.
+
 \end{description}

### 2019-11-13 cvpr_submission/transfer_learning.tex

@@
 defines a separate task.
-\begin{definition}[\cite{pan-yang}] \label{defn:transfer}
+\begin{definition}[\cite{pan2009survey}]
 	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 

### 2019-11-14 cvpr_submission/transfer_learning.tex
Add \label for Def 1 + fix minor typos.

@@
 \begin{definition}[\cite{pan2009survey}]
+	\label{defn:transfer}
 	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 
@@
 	over all questions in $\cQ$.
-	The marginal distributions $P_S$ and $P_T$ differ in the just the feature attributes such as shape, color, and size, or their combinations
+	The marginal distributions $P_S$ and $P_T$ differ in just the feature attributes such as shape, color, and size, or their combinations
 	thereof.
@@
 	where $n$ equals the maximum number of objects $n$ in an image, and $m$
-	equals  the number of frames in a vide. 
+	equals  the number of frames in a video. 
 	For any visual input $v_S$ coming from $X_S$ with $C(v_S) = (n_S, m_S)$
 	and for any visual input $v_T$ coming from $X_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and 
-	$m_T \ge m_S$ which at least one inequality being a strict one. 
+	$m_T \ge m_S$ with at least one inequality being a strict one. 
 	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.
@@
 	is the answer to question $q$ on visual input $v$.
-	Thus tasks are in a 1-1 correspondence with questions.
-	A \emph{task family} is a probability distribution on tasks which our case can be obtained by defining the distribution on $\cQ$. 
+	Thus, tasks are in a 1-1 correspondence with questions.
+	A \emph{task family} is a probability distribution on tasks which in our case can be obtained by defining the distribution on $\cQ$. 
 	Given a task family, the goal is to learn a prediction function that gives an answer to $f_q(v)$ for $v \in \cV$ chosen according 

### 2019-11-14 cvpr_submission/introduction.tex
Taking another shot at the contributions paragraph. The older one is just commented out.

@@
 VQA or image segmentation) can change significantly.
-This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
+%This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
 
@@
 \paragraph{Contributions}
+The contributions of this work are as follows.
+\begin{itemize}
+	\compresslist
+	\item We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
+	\item We propose a taxonomy of transfer learning, inspired from~\cite{pan2009survey}, applied to the domain of visual reasoning.
+Articulated around 3 main axis, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
+	\item Following, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: Feature transfer, temporal transfer and reasoning transfer.
+This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants.
+Several of these experiments show the significant generalization capabilities of SAMNet.
+\end{itemize}
 
-The contributions of this paper are as follows.
-We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
-We show the impact of the different tasks when transferring the whole pretrained model in three main setups.
-\begin{itemize}
-	\item We first focus on transfer learning within the Image QA domain and perform experiments similar to Taskonomy~\cite{zamir2018taskonomy}.
+% ===========================
+%The contributions of this paper are as follows.
+%We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
+%We show the impact of the different tasks when transferring the whole pretrained model in three main setups.
+%\begin{itemize}
+%	\item We first focus on transfer learning within the Image QA domain and perform experiments similar to Taskonomy~\cite{zamir2018taskonomy}.
 We analyze how training exclusively on one task family helps with mastering the others, with one notable difference: we transfer and fine-tune the whole model (not only the encoder or input layer).
-	\item Next, we show complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
-	\item Finally, we present a set of experiments aimed at analyzing of the impact of transfer learning in Video QA, when domain changes drastically and the model is forced to handle longer videos with higher complexity (i.e.
+%	\item Next, we show complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
+%	\item Finally, we present a set of experiments aimed at analyzing of the impact of transfer learning in Video QA, when domain changes drastically and the model is forced to handle longer videos with higher complexity (i.e.
 a higher number of distractor objects present in each frame).
-\end{itemize}
-Surprisingly, our model, with only small fine-tuning, managed to master the Hard variant of the COG dataset and achieved higher accuracy than the model trained solely on the Hard variant.
+%\end{itemize}
+%Surprisingly, our model, with only small fine-tuning, managed to master the Hard variant of the COG dataset and achieved higher accuracy than the model trained solely on the Hard variant.
 
-\tk{Have I addressed that correctly? I am not sure whether I have covered TL with CoGenT-A and CoGenT-B variants...}
-
-\vm{I think the contributions should be: 1. A new model with SotA results on COG |  2. transfer  / multitask learning  in COG | 3.  transfer  / multitask learning  in CLEVR}.
+%\tk{Have I addressed that correctly? I am not sure whether I have covered TL with CoGenT-A and CoGenT-B variants...}
+%
+%\vm{I think the contributions should be: 1. A new model with SotA results on COG |  2. transfer  / multitask learning  in COG | 3.  transfer  / multitask learning  in CLEVR}.
 

### 2019-11-14 cvpr_submission/introduction.tex
Fix typo.

@@
 	\item We propose a taxonomy of transfer learning, inspired from~\cite{pan2009survey}, applied to the domain of visual reasoning.
-Articulated around 3 main axis, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
+Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
 	\item Following, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: Feature transfer, temporal transfer and reasoning transfer.
@@
 %\vm{I think the contributions should be: 1. A new model with SotA results on COG |  2. transfer  / multitask learning  in COG | 3.  transfer  / multitask learning  in CLEVR}.
+% ===========================
 

### 2019-11-14 cvpr_submission/introduction.tex
Reformulate last paragraph of introduction to better link it with the contributions.

@@
 Moreover, as modern neural models often have millions of trainable parameters, training them requires vast amounts of data, which for some domains (e.g., medical) can be very expensive and/or extremely difficult to collect.
-One of the widely used solutions for the above mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances the  model performance by transferring \emph{information} from one domain to another.
+One of the widely used solutions for the above mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances model performance by transferring \emph{information} from one domain to another.
 
@@
 
-In Computer Vision, it is now a standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+In Computer Vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
 Such performance improvements are appealing, especially for cases where both the domain (e.g.
@@
 Recently, we observe a growing utilization of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amounts of data.
-In analogy to the pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
+In analogy to pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
 HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
@@
 
-The impact of transfer learning is even more essential in the case of multi-modal tasks, \cite{mogadala2019trends}, which combine both modalities mentioned above (i.e. vision and language).
+The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above (i.e. vision and language).
 %One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
 %In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
-In this work, we focus on a parallel aspect of transfer learning.
-As both Image and Video QA can be seen as meta-problems, where the model has to develop a different reasoning process depending on the type/family of question (task, e.g.
-counting objects or finding the value of a specific object's attribute), we investigated whether mastering one task type/family can help to master others.
-Thus, this work is also deeply related to multi-task learning~\cite{caruana1997multitask}.
+In this work, we focus on a parallel aspect of transfer learning in Image and Video QA.
+Both can be seen as meta-problems, where models have to develop different reasoning processes, associated to the type of questions (e.g., objects count queries, objects attribute queries etc.).
+We investigate, with a new model, whether mastering one task helps to master others.
+This is thus connected to multi-task learning~\cite{caruana1997multitask}.
 
@@
 Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
-	\item Following, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: Feature transfer, temporal transfer and reasoning transfer.
+	\item Following, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer.
 This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants.

### 2019-11-14 cvpr_submission/related_work.tex
Minor corrections.

@@
 Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods~\cite{hudson2018compositional, song2018explore}.
-Visualization of attention steps also provide interpretability, which is an increasingly important aspect.
+Visualization of attention maps also provides interpretability, which is an increasingly important aspect.
 The MAC model \cite{hudson2018compositional} is a great example of such an approach.
@@
 Learning long-term dependencies is also another challenge that LSTMs may struggle with.
-Yin et al.~\cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
+Yin et al.~\cite{yin2019memory} recently proposed a Memory-Augmented Neural Network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling long-term visual-textual dependencies.
 
@@
 Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore}, the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
-Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.
-Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
+Nevertheless, when reasoning and producing the answer, the system has \emph{access to all frames}.
+Similarly, in Visual Dialog~\cite{das2017visual}, the system memorizes the whole dialog history.
 However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

### 2019-11-14 cvpr_submission/introduction.tex
Minor corrections. Add or remove commas, Add \compresslist option for transfer learning section.

@@
 
-The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above (i.e. vision and language).
+The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above (i.e., vision and language).
 %One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).

### 2019-11-14 cvpr_submission/transfer_learning.tex
Minor corrections. Add or remove commas, Add \compresslist option for transfer learning section.

@@
 	\centering
-	\caption{Transfer learning taxonomy}
-	\label{fig:taskonomy}
 	\includegraphics[width=0.8\textwidth]{img/architecture/transfer_taxo}
+	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
 \end{figure*}
@@
 For visual reasoning problems considered in this paper, 
-$\cX$ will consist of purely visual inputs, i.e., either images or videos, in some cases, or 
+$\cX$ will consist of purely visual inputs, i.e., either images or videos in some cases, or 
 a combination of both visual inputs and questions in other cases. 
@@
 
-Although~\cref{defn:transfer} is quite general, it does not adequately capture all the artifacts present in the visual reasoning.
+Although~\cref{defn:transfer} is quite general, it does not adequately capture all the artifacts present in visual reasoning.
 For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
@@
 \begin{description}
-	\item[Feature Transfer:] In this setting of domain adaptation $\cX_S = \cX_T \subseteq \cQ \times \cV$
+	\compresslist % used to reduce spacing
+	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
 	and the task $f(q,v)$ is just the answer to the question $q$ on $v$. The output set $\cY$ is the union of legitimate answers
@@
 	\item[Reasoning Transfer:]
-	This setting requires an extension of~\cref{defn:transfer} given above to investigate transfer learning when
+	This setting requires an extension of~\cref{defn:transfer} above to investigate transfer learning when
 	grouping questions into families. Let $\cV$ be the feature space consisting of visual inputs only, shared by

### 2019-11-14 cvpr_submission/experiments.tex
Made modifications to Experiments section as discussed with Jayram.

@@
 \section{Experiments}
+\label{sec:experiments}
 We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}.
@@
 Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
-For this purpose, we used two variants of both datasets.
-For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence (4 vs.
-8) and the maximum number of distractors (i.e., objects not relevant for the answer) per single frame (1 vs.
-10).
+For the temporal and feature transfer experiments, we used two variants of both datasets.
+For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence and number of distractors. See \Sec{sec:temporal} for more information.
 For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
-More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
+See \Sec{sec:feature} for additional details.
+For the reasoning transfer experiments, we consider 22 classification tasks in COG and the 5 original question categories in CLEVR.
+%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
 
 \subsection{Performance comparison with the COG baseline}
+\label{sec:cog-baseline-compare}
 
@@
 We focused on 22 classification tasks and compared our results with the baseline model.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in Appendix~\ref{sec:cog-all-results}.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
 
@@
 
-\subsection{Temporal generalization capabilities on COG}
-
-The goal here is to test the generalization ability concerning the sequence length and number of distractors.
-For that purpose, we compare both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
-As the original paper does not include these experiments, we performed them.
-The light gray color indicates original results, whereas dark gray indicates the accuracies of COG models which we trained (fine-tuning/testing) using the original code provided by the authors.
-For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on the Canonical variant, without any fine-tuning.
-In a pure \textit{zero-shot learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
-We also test both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
-In this case, the SAMNet model also reaches much better performance and, interestingly, performs better than the model trained solely on the Hard variant.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{img/results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
-	\label{fig:samnet_cog_overall_transfer}
-\end{figure}
-
-\subsection{Multi-task learning on CLEVR and COG}
+\subsection{Reasoning transfer on CLEVR and COG}
+\label{sec:reasoning}
 In these experiments, we focus on analyzing the impact of each task relatively to others when training jointly.
@@
 \subsubsection{CLEVR}
+\label{sec:reasoning-clevr}
 For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute} and conducted the following experiments:
@@
 
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.5\textwidth]{img/results/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
-	\label{fig:CoGenT-results}
-\end{figure}
-
-Noticeable results are shown in \Fig{fig:CoGenT-results}, while the complete set is available in Appendix \ref{sec:full-cogent-results}.
+Noticeable results are shown in \Fig{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
 
@@
 We hypothesize that the improvements on e.g.
-\textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e.
-labels domain).
+\textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e., labels domain).
 
@@
 
-An supplementary set of experiments, for which results are available in Appendix \ref{sec:full-cogent-results}, finetune the model trained on all tasks on each task $t$ respectively.
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.5\textwidth]{img/results/CoGenT_results.pdf}
+	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
+	\label{fig:CoGenT-results}
+\end{figure}
+
+An supplementary set of experiments, for which results are available in the supplementary material,
+%Appendix \ref{sec:full-cogent-results}
+finetune the model trained on all tasks on each task $t$ respectively.
 Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the finetuned task and the drop, if any, on other tasks.
@@
 \subsubsection{COG}
+\label{sec:reasoning-cog}
 \tsj{todo}
 
-\subsection{Domain Adaptation}
+\subsection{Temporal transfer on COG}
+\label{sec:temporal}
 
-The final set of experiments we consider is related to \emph{Domain Adaptation}.
-According to \cite{pan2009survey}, this settings considers different but related source and target domains, under a common task.
-\subsubsection{CLEVR-CoGenT}
-The CoGenT-A \& -B sets of CLEVR differ by the available combinations of object attributes.
+The goal here is to test the generalization ability concerning the sequence length and number of distractors.
+For that purpose, we compare both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
+
+\begin{table}[ht]
+	\centering
+	\begin{adjustbox}{width=0.45\textwidth}
+		\begin{tabular}{lccc}
+			\toprule
+			Variant	&	Number of frames	&	Max. memory duration	&	Max. number of distractors \\ 
+			\midrule
+			Canonical & 4 & 3 & 1\\	
+			Hard  & 8 & 7 & 10\\
+			\bottomrule	
+		\end{tabular}
+	\end{adjustbox}
+	\caption{Details of the Canonical and Hard variants of the COG dataset.}
+	\label{tab:cog_variants}
+\end{table}\vspace{5pt}
+
+As the original paper does not include these experiments, we performed them.
+The light gray color indicates original results, whereas dark gray indicates the accuracies of COG models which we trained (fine-tuning/testing) using the original code provided by the authors.
+For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on the Canonical variant, without any fine-tuning.
+The observed close scores underline the faithfulness of the model reproducibility.
+In a pure \textit{zero-shot learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
+We also test both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
+In this case, the SAMNet model again reaches exemplary performance, at 96.7\% accuracy, and, interestingly, performs better than the model trained solely on the Hard variant.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{img/results/samnet_cog_overall_transfer.png}
+	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\label{fig:samnet_cog_overall_transfer}
+\end{figure}
+
+\subsection{Feature transfer on CLEVR-CoGenT}
+\label{sec:feature}
+\begin{table}[ht]
+	\label{tab:cogent_conditions}
+	\centering
+	\begin{adjustbox}{width=0.45\textwidth}
+		\begin{tabular}{cccc}
+			\toprule
+			Dataset	& Cubes	& Cylinders &	Spheres	\\
+			\midrule
+			CoGenT A & Gray / Blue / Brown / Yellow  & Red / Green / Purple / Cyan	&	Any color  \\
+			CoGenT B	&	Red / Green / Purple / Cyan &	Gray / Blue / Brown / Yellow	&	Any color \\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
+\end{table}
+
+The final set of experiments we consider is related to domain adaptation.
+%According to \cite{pan2009survey}, this settings considers different but related source and target domains, under a common task.
+
+The CoGenT-A \& -B sets of CLEVR differ by the available combinations of object attributes (\Tab{tab:cogent_conditions}).
 If we consider the input domain to be the set of objects with all attributes values, both sets differ by the data distribution they are sampled from.
@@
 
-\begin{figure}[!t]
+\begin{figure}[!t]\vspace{5pt}
 	\centering
@@
 Finetuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A, also observed in other models.
-
-\subsubsection{COG}
-\tsj{todo}

### 2019-11-14 cvpr_submission/summary.tex
Started to write Summary. WIP.

\section{Summary}

%In this paper we have introduced a novel Memory-Augmented Neural Network model called SAMNet. SAMNet was designed with the goal of learning to reason over video sequences and to answer questions about the content of the frames. When applied to the COG video reasoning dataset, the model outperformed the baseline model, showing significant improvements on the Hard variant of the dataset. The results indicate that the mechanisms introduced in SAMNet enable it to operate independent of the total number of frames or the number of distractions, and allow it to generalize to longer videos and more complex scenes. Observing attention maps shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended. Despite being trained only on image-question pairs with complex, compositional questions, SAMNet clearly learns to associate visual symbols with words and accurately classify temporal contexts as designed. Besides, the model’s reasoning using neural representations appears to be similar to how a human would operate on abstract symbols when solving the same task, including memorizing and recalling symbols (object embeddings) from the memory when needed. This is not perfect however and the system can sometimes store spurious objects despite the gating and reasoning mechanisms, but still give correct answers. This indicates at least two directions for possible further improvements. The first is to ameliorate content-based addressing with masking, similar to the improvements made for DNC proposed by [2]. Second is to implement variable number of reasoning steps, instead of hard-coded 8 steps, which could utilize Adaptive Computation Time (ACT) [5].

In this paper, through the introduction of a novel Memory-Augmented Neural Network model, SAMNet, we have quantified the impact of Transfer Learning in Visual Reasoning. Designed to learn to reason over sequences of frames (i.e., static images), SAMNet shows significant improvements, on the video reasoning dataset COG, over the corresponding baseline. Analysis of the results highlights the ability of the model to operate independently of the number of frames and generalize to samples with higher complexity, characterized by longer sequences or more complex scenes.
We also introduce a new taxonomy of transfer learning for visual reasoning, articulated around three axes: feature transfer, temporal transfer and reasoning transfer. To highlight the robustness of this taxonomy, we realize an extensive set of experiments with SAMNet over two datasets: COG and CLEVR, a diagnostic dataset for Question Answering over static images. SAMNet

### 2019-11-15 cvpr_submission/experiments.tex
no message

@@
 We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
-Our experiments were designed to study SAMNet's performance as well as its generalization abilities in different settings.
+Our experiments were designed to study SAMNet's performance as well as its generalization and transfer learning abilities in different settings.
 For the temporal and feature transfer experiments, we used two variants of both datasets.
-For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence and number of distractors. See \Sec{sec:temporal} for more information.
+For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence and number of 
+distractors (see~\cref{tab:cog_variants}).
+\begin{table}[ht]
+	\centering
+	\begin{adjustbox}{width=0.45\textwidth}
+		\begin{tabular}{lccc}
+			\toprule
+			Variant	&	Number of frames	&	Max. memory duration	&	Max. number of distractors \\ 
+			\midrule
+			Canonical & 4 & 3 & 1\\	
+			Hard  & 8 & 7 & 10\\
+			\bottomrule	
+		\end{tabular}
+	\end{adjustbox}
+	\caption{Details of the Canonical and Hard variants of the COG dataset.}
+	\label{tab:cog_variants}
+\end{table}
+This experiment is described in~\cref{sec:temporal}.
 For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
-See \Sec{sec:feature} for additional details.
-For the reasoning transfer experiments, we consider 22 classification tasks in COG and the 5 original question categories in CLEVR.
+\Cref{sec:feature} describes this experiment.
+For the reasoning transfer experiments, we consider 23 classification tasks in COG and the 5 original question categories in CLEVR.
 %More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
 
-\subsection{Performance comparison with the COG baseline}
+\subsection{Performance of SAMNet vs baseline model~\cite{yang2018dataset}}
 \label{sec:cog-baseline-compare}
 
-We trained SAMNet using 8 reasoning steps and external memory of 8 128-floats address locations.
+We trained SAMNet using 8 reasoning steps and external memory of 8 address locations, each storing an array of 128 floats. 
 %We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
-We focused on 22 classification tasks and compared our results with the baseline model.
+We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
 The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
@@
 	\end{subfigure}%
-	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
+		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
 	\label{fig:samnet_cog_detailed}
@@
 
-For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, compared to 97.6\% for the COG model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
-Despite there being some tasks in which our model reached slightly lower accuracies,
+For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, 
+compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
+As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better 
+accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
+For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating
+that our model can adapt to larger number of frames and distractors.
+Despite there being some tasks in the canonical variant where SAMNet achieved slightly lower accuracies,
 % (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it improves upon the COG baseline on all tasks, with improvements varying from 0.5 to more than 30 points.
+when comparing performances on the Hard variant, it improves upon the baseline model on all tasks, 
+with improvements varying from 0.5 to more than 30 points, and especially on the more complex tasks in the dataset.
 
@@
 \label{sec:reasoning}
-In these experiments, we focus on analyzing the impact of each task relatively to others when training jointly.
+In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
+of each task relatively to others when training jointly.
 
@@
 
-Noticeable results are shown in \Fig{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
+Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
 
-Looking at \Fig{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (dark blue).
+Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (dark blue).
 Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
@@
 
-Finally, the "all-tasks-but-$t$" experiments (cyan) demonstrate that while tasks are related, one does not subsume another in terms of learning.
+Finally, the ``all-tasks-but-$t$'' experiments (cyan) demonstrate that while tasks are related, one does not subsume another in terms of learning.
 Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
@@
 \label{sec:reasoning-cog}
-\tsj{todo}
+For the COG dataset, the number of tasks (23) is large, so we decided  there is no a priori grouping of tasks
 
-\subsection{Temporal transfer on COG}
+\subsection{Temporal transfer in COG}
 \label{sec:temporal}
 
-The goal here is to test the generalization ability concerning the sequence length and number of distractors.
-For that purpose, we compare both models when trained on the Canonical variant and tested on Hard (\cref{fig:samnet_cog_overall_transfer}).
+The goal here is to test the transfer learning ability concerning the sequence length and number of distractors.
+For that purpose, we compare both models when trained on the Canonical variant but tested on the 
+Hard variant (\cref{fig:samnet_cog_overall_transfer}).
 
@@
 
-The CoGenT-A \& -B sets of CLEVR differ by the available combinations of object attributes (\Tab{tab:cogent_conditions}).
+The CoGenT-A \& -B sets of CLEVR differ by the available combinations of object attributes (\cref{tab:cogent_conditions}).
 If we consider the input domain to be the set of objects with all attributes values, both sets differ by the data distribution they are sampled from.
 We thus consider 2 experiments with SAMNet trained on CoGenT-A: A direct generalization test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following the procedure of~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}.
-The results are available in \Fig{fig:CoGenT-B-results}.
+The results are available in~\cref{fig:CoGenT-B-results}.
 

### 2019-11-15 cvpr_submission/experiments.tex
Changes in experiments

@@
 For the temporal and feature transfer experiments, we used two variants of both datasets.
-For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence and number of 
+For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence,
+the maximum amount of look-back in frame history with the relevant information for each frame,  and number of 
 distractors (see~\cref{tab:cog_variants}).
@@
 	\centering
-	\begin{adjustbox}{width=0.45\textwidth}
+	%\begin{adjustbox}{width=0.45\textwidth}
 		\begin{tabular}{lccc}
 			\toprule
-			Variant	&	Number of frames	&	Max. memory duration	&	Max. number of distractors \\ 
+			Variant	& Frames & History	& Distractors \\ 
 			\midrule
@@
 		\end{tabular}
-	\end{adjustbox}
-	\caption{Details of the Canonical and Hard variants of the COG dataset.}
+	%\end{adjustbox}
+	\caption{Details of the Canonical and Hard variants of COG}
 	\label{tab:cog_variants}
@@
 of each task relatively to others when training jointly.
+For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
+appropriate experiments to study the effectiveness of transfer learning across task families.
 
@@
 \begin{itemize}
-	\compresslist
-	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional Deep Learning procedure of single-task learning,
-	\item Train SAMNet on all task groups jointly, and evaluate its performance on each task $t$ separately,
+	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
+	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
+	This is a transfer learning setting where for the source task family, the task is sampled from all questions,
+	while for the target task family, the samples consist of questions from group $t$ only;
 	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$.
+	This can also be viewed as a transfer learning setting similar to the previous case.
 	%These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
@@
 \label{sec:reasoning-cog}
-For the COG dataset, the number of tasks (23) is large, so we decided  there is no a priori grouping of tasks
+For the COG dataset, the number of task groups (23) is large, so we designed a 2-level hierarchy of the task groups motivated by the
+description of these tasks.
 
@@
 Hard variant (\cref{fig:samnet_cog_overall_transfer}).
-
-\begin{table}[ht]
-	\centering
-	\begin{adjustbox}{width=0.45\textwidth}
-		\begin{tabular}{lccc}
-			\toprule
-			Variant	&	Number of frames	&	Max. memory duration	&	Max. number of distractors \\ 
-			\midrule
-			Canonical & 4 & 3 & 1\\	
-			Hard  & 8 & 7 & 10\\
-			\bottomrule	
-		\end{tabular}
-	\end{adjustbox}
-	\caption{Details of the Canonical and Hard variants of the COG dataset.}
-	\label{tab:cog_variants}
-\end{table}\vspace{5pt}
 

### 2019-11-15 cvpr_submission/experiments.tex
Some minor typo corrections.

@@
 For the temporal and feature transfer experiments, we used two variants of both datasets.
-For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence,
-the maximum amount of look-back in frame history with the relevant information for each frame,  and number of 
-distractors (see~\cref{tab:cog_variants}).
+For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence, the maximum amount of look-back in frame history with the relevant information for each frame, and number of distractors (see~\cref{tab:cog_variants}).
 \begin{table}[ht]
@@
 	\label{tab:cog_variants}
-\end{table}
+\end{table}\vspace{5pt}
 This experiment is described in~\cref{sec:temporal}.
@@
 that our model can adapt to larger number of frames and distractors.
-Despite there being some tasks in the canonical variant where SAMNet achieved slightly lower accuracies,
+Despite there being some tasks in the Canonical variant where SAMNet achieved slightly lower accuracies,
 % (between 0.2 and 1.8 points)
@@
 
-An supplementary set of experiments, for which results are available in the supplementary material,
+An additional set of experiments, for which results are available in the supplementary material,
 %Appendix \ref{sec:full-cogent-results}
@@
 If we consider the input domain to be the set of objects with all attributes values, both sets differ by the data distribution they are sampled from.
-We thus consider 2 experiments with SAMNet trained on CoGenT-A: A direct generalization test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following the procedure of~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}.
+We thus consider 2 experiments with SAMNet trained on CoGenT-A: A direct generalization test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following the procedure of~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
 The results are available in~\cref{fig:CoGenT-B-results}.
@@
 	\includegraphics[width=0.3\textwidth]{img/results/CoGenT_B_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.}
+	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and finetuning on CoGenT-B (gray).}
 	\label{fig:CoGenT-B-results}

### 2019-11-15 cvpr_submission/paper_main.tex
Removed unnecessary packages + slightly reformulated abstract. Abstract probably needs a little more work.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
%\usepackage{epsfig}
\usepackage{graphicx}
\usepackage[font=small]{subcaption}
\captionsetup[figure]{skip=5pt}
\captionsetup[table]{skip=5pt}
\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
\usepackage{amsmath, amssymb, amsfonts,bm}
\usepackage{amsthm}

% Include other packages here, before hyperref.
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{tabularx}

\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{7813} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\usepackage{cleveref}
\crefname{section}{Section}{Sections}
\crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\crefname{appendix}{Appendix}{Appendices}
\crefname{definition}{Definition}{Definitions}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}

\theoremstyle{remark}
\newtheorem*{notation}{Notation}
%\newtheorem*{remark}{Remark}
\newtheorem*{note}{Note}

\newtheorem{fact}{Fact}
\newtheorem*{observation}{Observation}
\newtheorem*{condition}{Condition}
\newtheorem*{claim}{Claim}
\newtheorem*{example}{Example}
\newtheorem*{question}{Question}

\usepackage{enumitem}
\setlist{leftmargin=*}

%% User's macros %%
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cF}{\mathcal{F}}

\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\vc}{\vec{c}}
\newcommand{\vso}{\vec{so}}
\newcommand{\vone}{\vec{1}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\vx}{\vec{x}}
\newcommand{\vy}{\vec{y}}

\newcommand{\imatch}{g^{\mathrm{v}}}
\newcommand{\mmatch}{g^{\mathrm{m}}}

\newcommand{\doadd}{h^{\mathrm{a}}}
\newcommand{\doreplace}{h^{\mathrm{r}}}

\newcommand{\tlast}{\tau^{\mathrm{last}}}
\newcommand{\tlatest}{\tau^{\mathrm{latest}}}
\newcommand{\tnow}{\tau^{\mathrm{now}}}
\newcommand{\tnone}{\tau^{\mathrm{none}}}

\newcommand{\rhead}{\vec{rh}}
\newcommand{\whead}{\vec{wh}}

\newcommand{\tk}[1]{\textcolor{red}{TK: #1}}
\newcommand{\ao}[1]{\textcolor{green}{AO: #1}}
\newcommand{\tsj}[1]{\textcolor{magenta}{TSJ: #1}}
\newcommand{\vm}[1]{\textcolor{blue}{VM: #1}}

\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{enumerate} or \begin{enumerate}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}}

%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%% TITLE
\title{Transfer Learning in Multimodal Compositional and Relational Reasoning}

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{T.S. Jayram \and  Vincent Marois \and Vincent Albouy \and Tomasz Kornuta  \and Emre Sevgen \and Ahmet Ozcan\\
IBM Research AI\\
Almaden Research Center, San Jose, CA 95120, USA\\
Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
{\tt\small {jayram,  asozcan}@us.ibm.com}
{\tt\small {tkornuta, sesevgen}@gmail.com}
{\tt\small vincent.marois@ibm.com}
}

\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  Transfer learning is becoming the de facto solution for vision and text encoders in the front-end processing of machine learning solutions. Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited. In this paper, we analyze the efficiency of transfer learning in multimodal (vision and language) reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.  Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline. We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer. Based on extensive experimentation on transfer learning on the two datasets, we show the performance of the new model along each axis.
\end{abstract}

%%%%%%%%% BODY TEXT
\input{introduction}

\input{related_work}

\input{transfer_learning}

\input{samnet}

\input{experiments}

\input{summary}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{bibliography}
}

\clearpage
\input{appendix}

\end{document}

### 2019-11-15 cvpr_submission/experiments.tex
Enhanced CLEVR barcharts images.
Experiments

--- 2019-11-15 cvpr_submission/experiments.tex
@@
 \label{sec:reasoning-cog}
-For the COG dataset, the number of task groups (23) is large, so we designed a 2-level hierarchy of the task groups motivated by the
-description of these tasks.
+Since the number of task classes (=23) in the COG dataset is large, we designed a 2-level hierarchy of task groups using the
+description of these tasks, as shown in~\cref{fig:task-groups}.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\columnwidth]{img/architecture/hierarchy}
+	\caption{Hierarchy of Task Groups}
+	\label{fig:task-groups}
+\end{figure}
+
+\bigskip
+
+For the groups at the lowest level, we chose the following task classes to be placed in those groups:
+\begin{description}
+	\item[Basic:] \textit{ExistShape}, \textit{GetShape},
+\textit{GetColor}, \textit{ExistColor}, \textit{Exist}
+	\item[Compare Obj-Attr:] \emph{SimpleCompareColor}, \textit{SimpleCompareShape}, \textit{AndSimpleCompareShape}, 
+	\textit{AndSimpleCompareColor};
+	\item[Compare 2 Obj:] \textit{CompareColor}, \textit{CompareShape},  \textit{AndCompareColor}, \textit{AndCompareShape}, 
+	\textit{ExistColorOf}, \textit{ExistShapeOf};
+	\item[Spatial:] \textit{ExistSpace}, \textit{ExistColorSpace}, \textit{ExistShapeSpace}, \textit{GetColorSpace}, \textit{GetShapeSpace};
+	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor}, \textit{ExistLastObjectSameObjectdescription}
+\end{description}
+
+We then conducted the following experiments using the Canonical variant of the COG dataset, to study 
+whether transfer learning was effective in leveraging information gained by training a group at a higher level
+of the hierarchy to learning the constituent task groups below that group at the leaf level.
+ \begin{itemize}
+	\item Train and test SAMNet on a single task group $t$ for the 5 groups at the lowest level of the hierarchy. 
+	These 5 experiments fit into the traditional ML setup of single-task learning;
+	\item Train on \textbf{Group A} and test separately on \textbf{Basic}, \textbf{Compare Obj-Attr} and \textbf{Compare 2 Obj};
+	\item Train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
+	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
+	can be viewed as training on \textbf{All} and testing on each group at the lowest level separately.
+\end{itemize}
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{img/results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=\columnwidth]{img/results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 \begin{table}[ht]
-	\label{tab:cogent_conditions}
 	\centering
@@
 	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
+	\label{tab:cogent_conditions}
 \end{table}

### 2019-11-15 cvpr_submission/experiments.tex

@@
 	\centering
-	\includegraphics[width=0.3\textwidth]{img/results/CoGenT_B_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.}
+	\includegraphics[width=0.2\textwidth]{img/results/CoGenT_B_results.pdf}
+	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and finetuning on CoGenT-B (gray).}
 	\label{fig:CoGenT-B-results}

### 2019-11-15 cvpr_submission/summary.tex

@@
 
-%In this paper we have introduced a novel Memory-Augmented Neural Network model called SAMNet.
-SAMNet was designed with the goal of learning to reason over video sequences and to answer questions about the content of the frames.
-When applied to the COG video reasoning dataset, the model outperformed the baseline model, showing significant improvements on the Hard variant of the dataset.
-The results indicate that the mechanisms introduced in SAMNet enable it to operate independent of the total number of frames or the number of distractions, and allow it to generalize to longer videos and more complex scenes.
-Observing attention maps shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
+%Observing attention maps shows that SAMNet can effectively perform multi-step reasoning over questions and frames as intended.
 Despite being trained only on image-question pairs with complex, compositional questions, SAMNet clearly learns to associate visual symbols with words and accurately classify temporal contexts as designed.
@@
 Designed to learn to reason over sequences of frames (i.e., static images), SAMNet shows significant improvements, on the video reasoning dataset COG, over the corresponding baseline.
-Analysis of the results highlights the ability of the model to operate independently of the number of frames and generalize to samples with higher complexity, characterized by longer sequences or more complex scenes.
+Analysis of the results highlights the model's ability to operate independently of the number of frames and generalize to samples with higher complexity, characterized by longer sequences and more complex scenes.
+However, SAMNet can sporadically store spurious objects in the memory, despite its mechanisms.
+This doesn't prevent the model to produce accurate predictions.
+
 We also introduce a new taxonomy of transfer learning for visual reasoning, articulated around three axes: feature transfer, temporal transfer and reasoning transfer.
 To highlight the robustness of this taxonomy, we realize an extensive set of experiments with SAMNet over two datasets: COG and CLEVR, a diagnostic dataset for Question Answering over static images.
-SAMNet
+SAMNet demonstrates clear generalization capabilities along certain axes and, through the cautious use of finetuning, further advances performance in visual reasoning.
+
+We hope these contributions can bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.

### 2019-11-15 cvpr_submission/experiments.tex
Finished reasoning trasnfer

--- 2019-11-15 cvpr_submission/experiments.tex
@@
 Our experiments were designed to study SAMNet's performance as well as its generalization and transfer learning abilities in different settings.
+In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
+involving \emph{finetuning}.
+Recall that the former involves evaluating the trained model of the source directly on the target while for the latter we do additional lightweight 
+training on the target labeled data before evaluating its performance.
+
 For the temporal and feature transfer experiments, we used two variants of both datasets.
 For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence, the maximum amount of look-back in frame history with the relevant information for each frame, and number of distractors (see~\cref{tab:cog_variants}).
+This experiment is described in~\cref{sec:temporal}.
 \begin{table}[ht]
 	\centering
-	%\begin{adjustbox}{width=0.45\textwidth}
 		\begin{tabular}{lccc}
@@
 		\end{tabular}
-	%\end{adjustbox}
 	\caption{Details of the Canonical and Hard variants of COG}
@@
 \end{table}\vspace{5pt}
-This experiment is described in~\cref{sec:temporal}.
+
 For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
 \Cref{sec:feature} describes this experiment.
-For the reasoning transfer experiments, we consider 23 classification tasks in COG and the 5 original question categories in CLEVR.
+For the reasoning transfer experiments, we consider 23 classification task classes in COG and the 5 original question categories in CLEVR.
 %More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
@@
 In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
-of each task relatively to others when training jointly.
-For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
-appropriate experiments to study the effectiveness of transfer learning across task families.
+of each task relative to others using appropriate groupings of tasks.
+%For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
+%appropriate experiments to study the effectiveness of transfer learning across task families.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{img/results/CoGenT_results.pdf}
+	\includegraphics[width=\columnwidth]{img/results/CoGenT_results.pdf}
 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
@@
 \label{sec:reasoning-cog}
-For the COG dataset, the number of task groups (23) is large, so we designed a 2-level hierarchy of the task groups motivated by the
-description of these tasks.
+Since the number of task classes (=23) in the COG dataset is large, we designed a 2-level hierarchy of task groups using the
+description of these tasks, as shown in~\cref{fig:task-groups}.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\columnwidth]{img/architecture/hierarchy}
+	\caption{Hierarchy of Task Groups}
+	\label{fig:task-groups}
+\end{figure}
+
+\bigskip
+
+For groups at the lowest level, we chose the following task classes to be placed in those groups.
+Below, substitute each of \textit{Shape} and \textit{Color} for  \uX{} to obtain the task class.
+\begin{description}
+	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist};
+	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX;
+	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of};
+	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space};
+	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject}
+\end{description}
+
+We then conducted the following experiments using the Canonical variant of COG to study 
+whether transfer learning was effective in leveraging information gained by training a task family at a higher level
+of the hierarchy.
+ \begin{itemize}
+	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (standard ML). 
+	\item Train on \textbf{Group A} and test on \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare} each;
+	\item Train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
+	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
+	can be viewed as training on \textbf{All} and testing on each group at the leaf level separately.
+\end{itemize}
+
+The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
+
+First notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases 
+suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
+With \textbf{Spatial} we see a small improvement showing that there is some benefit due to joint training with other task families.
+Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
+The former saw an accuracy jump from 68.6\% by training on samples from that family alone
+to 97.0\% while training on all samples. To furthe rdrill down on this behavior, notice that 
+just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
+In hindsight, this is not surprising because the questions in \textbf{Compare} are composed
+of fragments in the questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
+Lastly, for the  \textbf{Spatial} family we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
+is a slight loss incurred by including everything.
+As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in the accuracy (97.1\%).
+To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.
+
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer}
+ 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
+ 	\label{fig:COG-reasoning-results}
+ \end{figure}
 
@@
 \begin{table}[ht]
-	\label{tab:cogent_conditions}
 	\centering
-	\begin{adjustbox}{width=0.45\textwidth}
+	%\begin{adjustbox}{width=0.45\textwidth}
 		\begin{tabular}{cccc}
@@
 			\midrule
-			CoGenT A & Gray / Blue / Brown / Yellow  & Red / Green / Purple / Cyan	&	Any color  \\
-			CoGenT B	&	Red / Green / Purple / Cyan &	Gray / Blue / Brown / Yellow	&	Any color \\
+			CoGenT A &  Family A  & Family B 	&	Any color  \\
+			CoGenT B	&	Family B  &	Family A	&	Any color \\
 			\bottomrule
 		\end{tabular}
-	\end{adjustbox}
-	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
+	%\end{adjustbox}
+	\caption{Color restrictions in CoGenT-A \& -B datasets.}
+	\label{tab:cogent_conditions}
 \end{table}
 
-The final set of experiments we consider is related to domain adaptation.
-%According to \cite{pan2009survey}, this settings considers different but related source and target domains, under a common task.
-
-The CoGenT-A \& -B sets of CLEVR differ by the available combinations of object attributes (\cref{tab:cogent_conditions}).
+The final set of experiments we consider is related to feature transfer.
+The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color attributes.
+The colors are partitioned into two complementary families: 
+Gray, Blue, Brown and Yellow in Family A and Red, Green, Purple, Cyan in Family B. 
+The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while
+the spheres can take any color. This is summarized in~\cref{tab:cogent_conditions}. 
 If we consider the input domain to be the set of objects with all attributes values, both sets differ by the data distribution they are sampled from.
@@
 
-\begin{figure}[!t]\vspace{5pt}
+\begin{figure}[!t]
 	\centering
-	\includegraphics[width=0.3\textwidth]{img/results/CoGenT_B_results.pdf}
+	\includegraphics[width=0.4\columnwidth]{img/results/CoGenT_B_results.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and finetuning on CoGenT-B (gray).}

### 2019-11-15 cvpr_submission/experiments.tex
Redo CLEVR barcharts in new style -- more compact and readable.

@@
 
-Finally, the ``all-tasks-but-$t$'' experiments (cyan) demonstrate that while tasks are related, one does not subsume another in terms of learning.
+Finally, the ``all-tasks-but-$t$'' experiments (yellow) demonstrate that while tasks are related, one does not subsume another in terms of learning.
 Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
@@
  	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer}
- 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
+ 	\caption{COG accuracies for all task groups $t$ when training on $t$ only, training on Group A or B and training on all tasks.}
  	\label{fig:COG-reasoning-results}
@@
 	\centering
-	\includegraphics[width=0.4\columnwidth]{img/results/CoGenT_B_results.pdf}
+	\includegraphics[width=0.8\columnwidth]{img/results/CoGenT_B_results.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and finetuning on CoGenT-B (gray).}

### 2019-11-15 cvpr_submission/transfer_learning.tex
Change to new taxonomy image.
no message
updated image name
Some minor typo corrections.
Finished reasoning trasnfer
Add distinction between zero-shot learning and finetuning at end of transfer learning section.

@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{img/architecture/transfer_taxo}
+	\includegraphics[width=\textwidth]{img/architecture/transfer_taxo}
 	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
@@
 
-Although~\cref{defn:transfer} is quite general, it does not adequately capture all the artifacts present in visual reasoning.
+Although~\cref{defn:transfer} is quite general, it does not adequately capture all artifacts present in visual reasoning.
 For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
@@
 	over all questions in $\cQ$.
-	The marginal distributions $P_S$ and $P_T$ differ in just the feature attributes such as shape, color, and size, or their combinations
+	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
 	thereof.
@@
 	equals  the number of frames in a video. 
-	For any visual input $v_S$ coming from $X_S$ with $C(v_S) = (n_S, m_S)$
-	and for any visual input $v_T$ coming from $X_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and 
+	For any visual input $v_S$ coming from $\cX_S$ with $C(v_S) = (n_S, m_S)$
+	and for any visual input $v_T$ coming from $\cX_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and 
 	$m_T \ge m_S$ with at least one inequality being a strict one. 
@@
 \end{description}
+
+If labeled data is available for $\cX_T$, a final distinction we make is between \emph{zero-shot learning} and \emph{finetuning}.
+Finetuning entails the use of labeled data in the target domain $\cD_T$, foreseeing performance gain on the target task $\cX_T$ will improve, after initial training on $\cX_S$ and additional training on $\cX_T$.
+Zero-shot learning thus refers to immediate test on $\cX_T$ after initial training on $\cX_S$.

### 2019-11-15 cvpr_submission/experiments.tex
Commented 2 sentences in CLEVR section + 1 sentence in  summary to reduce space. Also reduced size of transfer taxonomy by 10%.

@@
 		\end{tabular}
-	\caption{Details of the Canonical and Hard variants of COG}
+	\caption{Details of the Canonical and Hard variants of COG.}
 	\label{tab:cog_variants}
@@
 \begin{itemize}
+	\compresslist
 	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
@@
 These improvements suggest that related tasks benefit from joint training.
-We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
+%We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
 We hypothesize that the improvements on e.g.
@@
 finetune the model trained on all tasks on each task $t$ respectively.
-Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the finetuned task and the drop, if any, on other tasks.
+%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the finetuned task and the drop, if any, on other tasks.
 Finetuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
@@
 	\includegraphics[width=\columnwidth]{img/architecture/hierarchy}
-	\caption{Hierarchy of Task Groups}
+	\caption{Hierarchy of Task Groups.}
 	\label{fig:task-groups}
@@
 \begin{description}
+	\compresslist
 	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist};
@@
  \begin{itemize}
+ 	\compresslist
 	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (standard ML). 

### 2019-11-15 cvpr_submission/experiments.tex
Typo.
Some minor typo corrections in COG section 5.2.2.

@@
 
-Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (dark blue).
+Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
 Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
 
-Nevertheless, significant accuracy gains are noted when training jointly on all tasks (light gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
+Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
 \textit{QueryAttribute} only sees an increase of one point.
@@
 whether transfer learning was effective in leveraging information gained by training a task family at a higher level
-of the hierarchy.
+of the hierarchy:
  \begin{itemize}
@@
 
-First notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases 
-suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
-With \textbf{Spatial} we see a small improvement showing that there is some benefit due to joint training with other task families.
+First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
+With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
 Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
 The former saw an accuracy jump from 68.6\% by training on samples from that family alone
-to 97.0\% while training on all samples. To furthe rdrill down on this behavior, notice that 
+to 97.0\% when training on all samples. To further emphasize this behavior, notice that 
 just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
-In hindsight, this is not surprising because the questions in \textbf{Compare} are composed
-of fragments in the questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
-Lastly, for the  \textbf{Spatial} family we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
+In hindsight, this is not surprising as the questions in \textbf{Compare} are composed
+of fragments of the questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
+Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
 is a slight loss incurred by including everything.
-As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in the accuracy (97.1\%).
+As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%).
 To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.
@@
 Evaluating SAMNet on CoGenT shows that performance is worse on CoGenT-B than CoGenT-A, in line with~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.
-Finetuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A, also observed in other models.
+Finetuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A, also observed with other models.

### 2019-11-15 cvpr_submission/experiments.tex
Slight rephrasing of last experiments subsection to respect page limit.

@@
 just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
-In hindsight, this is not surprising as the questions in \textbf{Compare} are composed
-of fragments of the questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
+In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed
+of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
 Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
@@
 The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while
-the spheres can take any color. This is summarized in~\cref{tab:cogent_conditions}. 
-If we consider the input domain to be the set of objects with all attributes values, both sets differ by the data distribution they are sampled from.
-We thus consider 2 experiments with SAMNet trained on CoGenT-A: A direct generalization test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following the procedure of~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+the spheres can take any color (See~\cref{tab:cogent_conditions}). 
+Considering the input domain to be the set of objects with all attributes values, both sets differ by their marginal distributions $P_S$ and $P_T$.
+We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
 The results are available in~\cref{fig:CoGenT-B-results}.

### 2019-11-15 cvpr_submission/experiments.tex
Specify distinction of finetuning + comment paragraph in experiments.

@@
 The colors are partitioned into two complementary families: 
-Gray, Blue, Brown and Yellow in Family A and Red, Green, Purple, Cyan in Family B. 
+Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
 The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while

### 2019-11-15 cvpr_submission/experiments.tex
Comment paragraph in experiments.

@@
 Our experiments were designed to study SAMNet's performance as well as its generalization and transfer learning abilities in different settings.
-In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
-involving \emph{finetuning}.
-Recall that the former involves evaluating the trained model of the source directly on the target while for the latter we do additional lightweight 
-training on the target labeled data before evaluating its performance.
+%In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
+%involving \emph{finetuning}.
+%Recall that the former involves evaluating the trained model of the source directly on the target while for the latter we do additional lightweight 
+%training on the target labeled data before evaluating its performance.
 

### 2019-11-15 cvpr_submission/experiments.tex
Replaced COG_reasoning_transfer.png with a pdf version. Printer-friendly.
Add 2 sentences in section 5.2.1 about memory update & reasoning unit in SAMNet for CLEVR.

@@
 \label{sec:reasoning-clevr}
-For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute} and conducted the following experiments:
+For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+Given that the frame length is one (static image), the Memory Update unit of SAMNet does not impact the loss function.
+Following, in the Reasoning Unit, most of the useful information should originate from the image.
+We conduct the following experiments:
 \begin{itemize}
@@
  	\centering
- 	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer}
+ 	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer.pdf}
  	\caption{COG accuracies for all task groups $t$ when training on $t$ only, training on Group A or B and training on all tasks.}

### 2019-11-15 cvpr_submission/experiments.tex
Temporal transfer cleanup

--- 2019-11-15 cvpr_submission/experiments.tex
@@
 We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
-Our experiments were designed to study SAMNet's performance as well as its generalization and transfer learning abilities in different settings.
+There are 23 classification question categories in COG and the 5 original question categories in CLEVR.
+Our experiments were designed to study SAMNet's performance in terms of generalization and transfer learning abilities in different settings,
+and involved incorporating variants of both datasets.  
+For COG, the Canonical (easy) and Hard variant differ mainly on the number of frames in the video, 
+the maximum amount of look-back in frame history containing relevant information for reasoning, 
+and the number of object distractors (see~\cref{tab:cog_variants}).
+For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values (details in~\cref{sec:temporal}).
 %In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
@@
 %training on the target labeled data before evaluating its performance. 
-
-For the temporal and feature transfer experiments, we used two variants of both datasets.
-For COG, an easy one (Canonical) and a Hard variant, differ mainly on the number of frames in the input sequence, the maximum amount of look-back in frame history with the relevant information for each frame, and number of distractors (see~\cref{tab:cog_variants}).
-This experiment is described in~\cref{sec:temporal}.
 \begin{table}[ht]
@@
 			\midrule
-			Canonical & 4 & 3 & 1\\	
+			Canonical (Easy) & 4 & 3 & 1\\	
 			Hard  & 8 & 7 & 10\\
@@
 
-For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values.
-\Cref{sec:feature} describes this experiment.
-For the reasoning transfer experiments, we consider 23 classification task classes in COG and the 5 original question categories in CLEVR.
 %More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
@@
 
-The goal here is to test the transfer learning ability concerning the sequence length and number of distractors.
+The goal here is to test the transfer learning ability concerning the frame sequence length, frame history required
+for reasoning, and the number of object distractors.
 For that purpose, we compare both models when trained on the Canonical variant but tested on the 
 Hard variant (\cref{fig:samnet_cog_overall_transfer}).
-
-As the original paper does not include these experiments, we performed them.
-The light gray color indicates original results, whereas dark gray indicates the accuracies of COG models which we trained (fine-tuning/testing) using the original code provided by the authors.
-For sanity check, in the first column, we report both the best-achieved score and the score reported in the paper when training and testing on the Canonical variant, without any fine-tuning.
-The observed close scores underline the faithfulness of the model reproducibility.
-In a pure \textit{zero-shot learning} setup (second column), our model shows enormous generalization ability, reaching 91.6\% accuracy on the test set.
-We also test both models in a setup where the model trained on a Canonical variant underwent additional fine-tuning (for a single epoch) on the Hard variant (third column).
-In this case, the SAMNet model again reaches exemplary performance, at 96.7\% accuracy, and, interestingly, performs better than the model trained solely on the Hard variant.
+The light gray color indicates original accuracies of the baseline model from paper, 
+whereas dark gray indicates accuracies of the baseline model
+obtained by running the original code provided by the authors~\cite{yang2018implement}.
+The first column displays the scores when training and testing on the Canonical variant, without any finetuning. 
+The observed close scores in light and dark gray underscore the baseline model reproducibility.
+For both cases of zero-shot learning (second column--91.6\% vs 65.9\%) and finetuning for a single epoch 
+(third column--96.7\% vs. 78.1\%), SAMNET outperforms the baseline model significantly.
+Interestingly, finetuning gets a modest boost (96.7\%) on the earlier reported accuracy in~\cref{sec:cog-baseline-compare}
+of SAMNet using the pure ML setup.
+These results suggest that it suffices to train SAMNet on video samples with small complexity 
+and achieve comparable, if not better, performance on more complex videos.
 
@@
 	\includegraphics[width=\columnwidth]{img/results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
 	\label{fig:samnet_cog_overall_transfer}

### 2019-11-15 cvpr_submission/experiments.tex
Changed sentence about SAMNet for CLEVR.

--- 2019-11-15 cvpr_submission/experiments.tex
@@
 For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-Given that the frame length is one (static image), the Memory Update unit of SAMNet does not impact the loss function.
-Following, in the Reasoning Unit, most of the useful information should originate from the image.
+For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
 We conduct the following experiments:

### 2019-11-15 cvpr_submission/experiments.tex
Temporal trasnfer cleanup

--- 2019-11-15 cvpr_submission/experiments.tex
@@
 obtained by running the original code provided by the authors~\cite{yang2018implement}.
-The first column displays the scores when training and testing on the Canonical variant, without any finetuning. 
+
+The first column displays the scores of the traditional ML setup when training and testing on the Canonical variant. 
 The observed close scores in light and dark gray underscore the baseline model reproducibility.
-For both cases of zero-shot learning (second column--91.6\% vs 65.9\%) and finetuning for a single epoch 
+For both cases of zero-shot learning (second column--91.6\% vs 65.9\%) and finetuning using a single epoch 
 (third column--96.7\% vs. 78.1\%), SAMNET outperforms the baseline model significantly.
-Interestingly, finetuning gets a modest boost (96.7\%) on the earlier reported accuracy in~\cref{sec:cog-baseline-compare}
-of SAMNet using the pure ML setup.
-These results suggest that it suffices to train SAMNet on video samples with small complexity 
-and achieve comparable, if not better, performance on more complex videos.
+Interestingly, this finetuning yields a mild boost of +0.6\% on the earlier reported accuracy 
+in~\cref{sec:cog-baseline-compare} (fourth column).
+These results suggest that it suffices to train SAMNet on simpler videos 
+to enable learning of good memory usage and attention on relevant entities  
+in order to achieve comparable, if not better, 
+performance on longer video frames with more complex scenes.
 

### 2019-11-15 cvpr_submission/transfer_learning.tex
Commented 2 sentences in CLEVR section + 1 sentence in  summary to reduce space. Also reduced size of transfer taxonomy by 10%.
Specify distinction of finetuning + comment paragraph in experiments.
Fix typo.

@@
 	\centering
-	\includegraphics[width=\textwidth]{img/architecture/transfer_taxo}
+	\includegraphics[width=0.9\textwidth]{img/architecture/transfer_taxo}
 	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
@@
 
-If labeled data is available for $\cX_T$, a final distinction we make is between \emph{zero-shot learning} and \emph{finetuning}.
-Finetuning entails the use of labeled data in the target domain $\cD_T$, foreseeing performance gain on the target task $\cX_T$ will improve, after initial training on $\cX_S$ and additional training on $\cX_T$.
+If labeled data is available for $\cX_T$, a training algorithm distinction we make is between \emph{zero-shot learning} and \emph{finetuning}.
+Finetuning entails the use of labeled data in the target domain $\cD_T$, foreseeing performance gain on the target task $\cX_T$, after initial training on $\cX_S$ and additional training on $\cX_T$.
 Zero-shot learning thus refers to immediate test on $\cX_T$ after initial training on $\cX_S$.

### 2019-11-15 cvpr_submission/introduction.tex
Intro minor edits

--- 2019-11-14 cvpr_submission/introduction.tex
@@
 A similar development has emerged in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, especially when labeled data is less accessible.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, has become a standard procedure when working with different NLP domains and tasks,
+especially when labeled data is less accessible.
 Recently, we observe a growing utilization of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amounts of data.
@@
 
-The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above (i.e. vision and language).
+The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above, i.e., vision and language.
 %One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
@@
 In this work, we focus on a parallel aspect of transfer learning in Image and Video QA.
-Both can be seen as meta-problems, where models have to develop different reasoning processes, associated to the type of questions (e.g., objects count queries, objects attribute queries etc.).
+Both can be seen as meta-problems, where models have to develop different reasoning processes, associated to the type of questions, such as object-count and object-attribute queries.
 We investigate, with a new model, whether mastering one task helps to master others.

### 2019-11-15 cvpr_submission/samnet.tex
Transfer learning
no message

@@
 
-\begin{figure*}[!t]
-	\centering
-	\includegraphics[width=\textwidth]{img/architecture/SAMNETmodel}
-	\caption{General architecture of SAMNet}
-	\label{fig:samnet}
-\end{figure*}
+SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
+compositional reasoning as proposed e.g.
+in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and use of an external memory, as in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
 
-SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level SAMNet draws from two core ideas:
-compositional reasoning as proposed e.g.
-in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and utilization of external memory in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
-
-A distinctive feature of the SAM Network is that it makes a single pass over the frames in temporal order, accessing one frame at a time.
+A distinctive feature of the SAM Network is its frame-by-frame temporal processing approach, where a single frame can be accessed at once.
+This is a notable difference from~\cite{haurilet2019s}, which uses graph traversal reasoning.
+The recurrent nature of SAMNet does not prevent frame sequences longer than those used for training.
 The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video. 
@@
 Using gating mechanisms, correct objects can be retrieved in order to perform multi-step spatio-temporal reasoning over text and video.
-A notable feature of this design is that the number of addresses $N$ can be set to different values during training and testing to fit the characteristics of data.
+A notable feature of this design is that the number of addresses $N$ can be changed between training and testing, to fit the data characteristics.
 
@@
 
-The core of SAMNet is a recurrent cell called a SAM Cell.
-Unrolling a new series of $T$ cells for every frame enables $T$ steps of compositional reasoning, similar to~\cite{hudson2018compositional}.
+SAMNet's core is a recurrent cell called the SAM Cell.
+Unrolling a new series of $T$ cells for each frame allows $T$ steps of compositional reasoning, similar to~\cite{hudson2018compositional}.
 Information flows between frames through the external memory.
 During the $t$-th reasoning step, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
-(a) $\vec{c}_t \in \Reals^d$, the control state used to drive the reasoning over objects in the frame and memory; and
+(a) $\vec{c}_t \in \Reals^d$, the control state used to drive reasoning over objects in the frame and memory; and
 (b) $\vec{so}_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
@@
 Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
-in a trained model, $\whead_t$ points to the location of first empty slot in memory for adding new objects.
+in a trained model, $\whead_t$ points to the location of the first empty slot in memory for adding new objects.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{img/architecture/SAMNETmodel}
+	\caption{General architecture of SAMNet.}
+	\label{fig:samnet}
+\end{figure*}
 
@@
 The control state $\vec{c}_t$ at step $t$ is then fed to a \emph{temporal classifier}, 
-a two-layer feedforward network with ELU activation used in the hidden layer of $d$ units.
-The output $\bm{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
-For the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
+a two-layer feedforward network with ELU activation in the hidden layer of $d$ units.
+The output $\bm{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that reasoning step.	
+For the COG dataset, we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
 
@@
 A similar operation on memory yields the object $\vec{mo}_t$.
-The memory operation is based on an attention mechanism, and resembles content-based addressing on memory.
+The memory operation is based on an attention mechanism, and resembles content-based addressing.
 Therefore, we obtain an attention vector over memory addresses that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
-Note that the returned objects may be invalid, e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid even if the current frame contains a red square.
+%Note that the returned objects may be invalid, e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid even if the current frame contains a red square.
 
@@
 %\paragraph{Reasoning Unit.}
-This module is the backbone of SAMNet that determines what gating operations need to be performed on the external memory, as well as determining the location of the correct object for reasoning.
-To determine whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
-First, we take the visual attention vector $\vec{va}_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
-and compute a simple aggregate\footnote{%
-	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.}: %
+This module is the backbone of SAMNet, which determines the gating operations to be performed on the external memory, as well as determining the correct object's location for reasoning.
+To resolve whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
+First, we compute a simple aggregate\footnote{%
+	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.} of the visual attention vector $\vec{va}_t$ of dimension $L$ ($L$ denotes the number of feature vectors for the frame):
 $vs_t = \sum_{i=1}^L [\vec{va}_t(i)]^2$. It can be shown that the more localized the attention
-vector is, the higher is the aggregate value.
+vector, the higher the aggregate value.
 We perform a similar computation on the read head $\rhead_t$ over memory locations.
-We feed these two values along with the temporal class weights $\bm{\tau}_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
-in $[0,1]$ modulated for the current reasoning step:
+We input these two values, along with the temporal class weights $\bm{\tau}_t$, into a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values (in $[0,1]$) for the current reasoning step:
 (a) $\imatch_t$, which determines whether there is a valid visual object;
@@
 Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
-The sum of components of $\vec{w}_t$ is at most equal to 1; and $\vec{w}_t$ can even equal 0, e.g., whenever neither condition of adding a new object nor replacing an existing object holds true.
+$\vec{w}_t$ sums up to at most equal to 1; and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
 We then update the memory accordingly as:

### 2019-11-15 cvpr_submission/samnet.tex
Finish polishing Model section.

@@
 Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
-$\vec{w}_t$ sums up to at most equal to 1; and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
+$\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
 We then update the memory accordingly as:
@@
 Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
-Finally, $\vec{so}_t$ is the output of a simple linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
-This serves to retain additional information that was in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
+Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
+This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
 

### 2019-11-15 cvpr_submission/introduction.tex
Rewrite final paragraph of introduction. WIP.

@@
 
-The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above, i.e., vision and language.
-%One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
-%In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
-In this work, we focus on a parallel aspect of transfer learning in Image and Video QA.
-Both can be seen as meta-problems, where models have to develop different reasoning processes, associated to the type of questions, such as object-count and object-attribute queries.
-We investigate, with a new model, whether mastering one task helps to master others.
-This is thus connected to multi-task learning~\cite{caruana1997multitask}.
+How to acutely employ transfer learning in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above, i.e., vision and language, is another engaging research question.
+While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, there is no obvious approach to combine both and hope to perform well on, say, Visual Question Answering.
+New models and mechanisms, such as attention~\cite{bahdanau2014neural}, are appropriate to handle the intricate relations between two (or more) modalities.
 
@@
 \end{itemize}
-
-% ===========================
-%The contributions of this paper are as follows.
-%We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
-%We show the impact of the different tasks when transferring the whole pretrained model in three main setups.
-%\begin{itemize}
-%	\item We first focus on transfer learning within the Image QA domain and perform experiments similar to Taskonomy~\cite{zamir2018taskonomy}.
-We analyze how training exclusively on one task family helps with mastering the others, with one notable difference: we transfer and fine-tune the whole model (not only the encoder or input layer).
-%	\item Next, we show complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
-%	\item Finally, we present a set of experiments aimed at analyzing of the impact of transfer learning in Video QA, when domain changes drastically and the model is forced to handle longer videos with higher complexity (i.e.
-a higher number of distractor objects present in each frame).
-%\end{itemize}
-%Surprisingly, our model, with only small fine-tuning, managed to master the Hard variant of the COG dataset and achieved higher accuracy than the model trained solely on the Hard variant.
-
-%\tk{Have I addressed that correctly? I am not sure whether I have covered TL with CoGenT-A and CoGenT-B variants...}
-%
-%\vm{I think the contributions should be: 1. A new model with SotA results on COG |  2. transfer  / multitask learning  in COG | 3.  transfer  / multitask learning  in CLEVR}.
-% ===========================
-
-%A) Task generalization
-%- answers (CLEVR)
-%B) Domain adaptation
-%- CoGenT A -> CoGenT B (CLEVR)
-%- sequence lenght  (COG)
-%- image complexity (distractors) (COG)
-
-%All those experiments in fact analyse different aspects
-
-%Lack of studies of impact of transfer learning for higher-level, abstract reasoning?
-
-%From one point, some preliminary results:
-% - CLEVR showing results on CoGenT-a/b~\cite{johnson2017clevr} - this is more "object generalization"
- %- COG paper showing interesting results with "task generalization" when training on all tasks excluding the one used for test~\cite{yang2018dataset}
-
-%I want to claim that therer are three different approaches to "master count".
-%1) Train and test only on count
-%2) Train on alll the tasks including count
-%3) Do not train on count at all and then test on count
-
-%conclusions:
-%when you are doing transfer make sure that the target answers are the same!
-%otherwise: binary y/n vs numers 0-7 vs names of attributes

### 2019-11-15 cvpr_submission/experiments.tex
Small corrections in experiments.

@@
 Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareInteger} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
+Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
 
@@
 
-First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
+First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive tasks and therefore do not benefit from training with other task families.
 With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.

### 2019-11-15 cvpr_submission/supplementary_material.tex
Made Supplementary Material its own file.

--- 2019-11-15 cvpr_submission/paper_main.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\documentclass[10pt,letterpaper]{article}
 
@@
 \usepackage{times}
-%\usepackage{epsfig}
 \usepackage{graphicx}
-\usepackage[font=small]{subcaption}
-\captionsetup[figure]{skip=5pt}
-\captionsetup[table]{skip=5pt}
-\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
-\usepackage{amsmath, amssymb, amsfonts,bm}
-\usepackage{amsthm}
-
-% Include other packages here, before hyperref.
+\usepackage{subcaption}
 \usepackage{booktabs}
@@
 \usepackage{tabularx}
-
-\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage{xcolor}
+\usepackage{url}
+\usepackage{enumitem}
+\setlist{leftmargin=*}
 
@@
 
-\def\cvprPaperID{7813} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{7813} 
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
 \ifcvprfinal\pagestyle{empty}\fi
-
-\usepackage{cleveref}
-\crefname{section}{Section}{Sections}
-\crefname{figure}{Figure}{Figures}
-\crefname{table}{Table}{Tables}
-\crefname{appendix}{Appendix}{Appendices}
-\crefname{definition}{Definition}{Definitions}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{definition}[theorem]{Definition}
-
-\theoremstyle{remark}
-\newtheorem*{notation}{Notation}
-%\newtheorem*{remark}{Remark}
-\newtheorem*{note}{Note}
-
-\newtheorem{fact}{Fact}
-\newtheorem*{observation}{Observation}
-\newtheorem*{condition}{Condition}
-\newtheorem*{claim}{Claim}
-\newtheorem*{example}{Example}
-\newtheorem*{question}{Question}
-
-\usepackage{enumitem}
-\setlist{leftmargin=*}
-
-%% User's macros %%
-\newcommand{\Reals}{\mathbb{R}}
-\newcommand{\cD}{\mathcal{D}}
-\newcommand{\cT}{\mathcal{T}}
-\newcommand{\cX}{\mathcal{X}}
-\newcommand{\cY}{\mathcal{Y}}
-\newcommand{\cQ}{\mathcal{Q}}
-\newcommand{\cV}{\mathcal{V}}
-\newcommand{\cF}{\mathcal{F}}
-
-\renewcommand{\vec}[1]{\mathbf{#1}}
-\newcommand{\vc}{\vec{c}}
-\newcommand{\vso}{\vec{so}}
-\newcommand{\vone}{\vec{1}}
-\newcommand{\proj}{\mathrm{proj}}
-\newcommand{\vx}{\vec{x}}
-\newcommand{\vy}{\vec{y}}
-
-\newcommand{\imatch}{g^{\mathrm{v}}}
-\newcommand{\mmatch}{g^{\mathrm{m}}}
-
-\newcommand{\doadd}{h^{\mathrm{a}}}
-\newcommand{\doreplace}{h^{\mathrm{r}}}
-
-\newcommand{\tlast}{\tau^{\mathrm{last}}}
-\newcommand{\tlatest}{\tau^{\mathrm{latest}}}
-\newcommand{\tnow}{\tau^{\mathrm{now}}}
-\newcommand{\tnone}{\tau^{\mathrm{none}}}
-
-\newcommand{\rhead}{\vec{rh}}
-\newcommand{\whead}{\vec{wh}}
-
-\newcommand{\tk}[1]{\textcolor{red}{TK: #1}}
-\newcommand{\ao}[1]{\textcolor{green}{AO: #1}}
-\newcommand{\tsj}[1]{\textcolor{magenta}{TSJ: #1}}
-\newcommand{\vm}[1]{\textcolor{blue}{VM: #1}}
-
-\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{enumerate} or \begin{enumerate}
-\setlength{\itemsep}{1pt}
-\setlength{\parskip}{0pt}
-\setlength{\parsep}{0pt}}
-
-%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%% TITLE
-\title{Transfer Learning in Multimodal Compositional and Relational Reasoning}
+\title{Transfer Learning in Multimodal Compositional and Relational Reasoning:\\Supplementary Material}
 
@@
 
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  Transfer learning is becoming the de facto solution for vision and text encoders in the front-end processing of machine learning solutions.
-Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited.
-In this paper, we analyze the efficiency of transfer learning in multimodal (vision and language) reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.
-Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline.
-We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer.
-Based on extensive experimentation on transfer learning on the two datasets, we show the performance of the new model along each axis.
-\end{abstract}
+\input{appendix}
 
-%%%%%%%%% BODY TEXT
-\input{introduction}
-
-\input{related_work}
-
-\input{transfer_learning}
-
-\input{samnet}
-
-\input{experiments}
-
-\input{summary}
-
+\clearpage
 {\small
@@
 
-\clearpage
-\input{appendix}
-
 \end{document}

### 2019-11-15 cvpr_submission/introduction.tex
transfer learning para

@@
 
-How to acutely employ transfer learning in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above, i.e., vision and language, is another engaging research question.
-While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, there is no obvious approach to combine both and hope to perform well on, say, Visual Question Answering.
-New models and mechanisms, such as attention~\cite{bahdanau2014neural}, are appropriate to handle the intricate relations between two (or more) modalities.
+In this work, we focus on multi-modal learning~\cite{mogadala2019trends} combining vision and language,
+and in particular, transfer learning for visual reasoning tasks with a rich logical structure, e.g., see~\cite{johnson2017clevr,yang2018dataset}. 
+While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
+once the modalities have been fused.
+For example, in compositional reasoning problems that involve objects with multiple attributes,
+feature representations in the source domain may be entangled and not easily transfer over to the target domain~\cite{johnson2017clevr}.
+In video reasoning, an additional challenge in the temporal dimension is whether a model that is trained on shorter video sequences will 
+transfer over to longer sequences~\cite{yang2018dataset,song2018explore}.
+To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
+and external memory~\cite{graves2014neural, graves2016hybrid,weston2014memory} 
+which facilitate higher-level abstractions, seem more promising.
 
-\paragraph{Contributions}
-The contributions of this work are as follows.
+Our main contributions are:
 \begin{itemize}

### 2019-11-15 cvpr_submission/experiments.tex

@@
 Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has for corresponding labels the digits 0 through 10 (a random agent would thus obtain $<$10\% accuracy) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
+Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
 
 Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
+These improvements suggest that related tasks benefit from joint training.
 \textit{QueryAttribute} only sees an increase of one point.
 One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
-These improvements suggest that related tasks benefit from joint training.
 %We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
@@
 Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
-We also observe no learning for \textit{Count} and \textit{QueryAttribute}, caused by these tasks having distinct labels domains, which do not overlap with the other tasks.
-Thus, if holding out samples from \textit{Count} during training, a model will not be able to predict the corresponding labels.
+We also observe no learning for \textit{Count} and \textit{QueryAttribute}. As these categories have labels that do not overlap with other categories, the model cannot predict these labels.
 
@@
 Finetuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
-Nevertheless, these experiments leave open the possibility that the multi-task learning training method may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups.
-Recent work~\cite{guo2018dynamic, kendall2018multi} in this direction has been done, although seems to weigh tasks rather than samples.
+Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
 

### 2019-11-15 cvpr_submission/introduction.tex

@@
 feature representations in the source domain may be entangled and not easily transfer over to the target domain~\cite{johnson2017clevr}.
-In video reasoning, an additional challenge in the temporal dimension is whether a model that is trained on shorter video sequences will 
+In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
 transfer over to longer sequences~\cite{yang2018dataset,song2018explore}.

### 2019-11-15 cvpr_submission/introduction.tex
Dummy change

@@
 \section{Introduction}
+%dummy
 In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.

### 2019-11-16 cvpr_submission/paper_main.tex
Finished reasoning trasnfer
Remove Appendix from main paper. Will make it a separate file.
New title + remove "compositional".

@@
 \usepackage{tabularx}
+\usepackage{xcolor}
 
-\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
-
+\usepackage{hyperref}
+\hypersetup{
+	pagebackref,
+	colorlinks,
+	breaklinks,
+	bookmarks=false,
+	linkcolor={red!50!black},
+	citecolor={blue!50!black},
+	urlcolor={blue!80!black},
+	%linkcolor=OliveGreen,
+	%citecolor=Blue,
+}
 %\cvprfinalcopy % *** Uncomment this line for the final submission
@@
 
+\newcommand{\uX}{\underline{X}}
+
 \newcommand{\tk}[1]{\textcolor{red}{TK: #1}}
@@
 %%%%%%%%% TITLE
-\title{Transfer Learning in Multimodal Compositional and Relational Reasoning}
+\title{Transfer Learning in Visual and Relational Reasoning}
 
@@
 
+\clearpage
 {\small
@@
 
-\clearpage
-\input{appendix}
+%\clearpage
+%\input{appendix}
 

### 2019-11-16 cvpr_submission/samnet.tex
New title + remove "compositional".

@@
 SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
-compositional reasoning as proposed e.g.
+iterative reasoning as proposed e.g.
 in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and use of an external memory, as in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
@@
 SAMNet's core is a recurrent cell called the SAM Cell.
-Unrolling a new series of $T$ cells for each frame allows $T$ steps of compositional reasoning, similar to~\cite{hudson2018compositional}.
+Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}.
 Information flows between frames through the external memory.

### 2019-11-16 cvpr_submission/introduction.tex
Removing other occurences of "compositional".

@@
 once the modalities have been fused.
-For example, in compositional reasoning problems that involve objects with multiple attributes,
+For example, in visual reasoning problems that involve objects with multiple attributes,
 feature representations in the source domain may be entangled and not easily transfer over to the target domain~\cite{johnson2017clevr}.

### 2019-11-16 cvpr_submission/related_work.tex
Minor corrections. Add or remove commas, Add \compresslist option for transfer learning section.
Removing other occurences of "compositional".

@@
 Attention research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach~\cite{yang2016stacked, chen2015abc, ilievski2016focused}.
-Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods~\cite{hudson2018compositional, song2018explore}.
+Visual reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods~\cite{hudson2018compositional, song2018explore}.
 Visualization of attention maps also provides interpretability, which is an increasingly important aspect.
@@
 
-Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning.
+Video question answering, aside from spatial queries, also focuses on questions that require \emph{temporal} reasoning.
 Early works~\cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video.

### 2019-11-16 cvpr_submission/paper_main.tex
Correct abstract.

@@
 Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited.
-In this paper, we analyze the efficiency of transfer learning in multimodal (vision and language) reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.
+In this paper, we analyze the efficiency of transfer learning in visual reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.
 Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline.

### 2019-11-16 cvpr_submission/experiments.tex
Modified Intro and related work

@@
 Considering the input domain to be the set of objects with all attributes values, both sets differ by their marginal distributions $P_S$ and $P_T$.
-We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (zero-shot learning) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
 The results are available in~\cref{fig:CoGenT-B-results}.

### 2019-11-16 cvpr_submission/introduction.tex
Modified Intro and related work

@@
 once the modalities have been fused.
-For example, in visual reasoning problems that involve objects with multiple attributes,
-feature representations in the source domain may be entangled and not easily transfer over to the target domain~\cite{johnson2017clevr}.
+For example, the CoGenT (Constrained Generalization Test) variant of the CLEVR~\cite{johnson2017clevr}  
+contains two datasets with similar questions, but differing on combinations of object-attribute values in images 
+(\cref{sec:feature}).
+In this case, training on the first dataset might yield entangled feature representations that may fail reasoning tasks
+on the second dataset.
 In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
-transfer over to longer sequences~\cite{yang2018dataset,song2018explore}.
+transfer over to longer sequences, e.g., the Canonical and the Hard variants of the 
+COG dataset~\cite{yang2018dataset} (\cref{sec:temporal}).
 To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
@@
 \begin{itemize}
-	\compresslist
+	%\compresslist
 	\item We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on COG~\cite{yang2018dataset}, a Video QA reasoning dataset.

### 2019-11-16 cvpr_submission/related_work.tex
Modified Intro and related work

@@
 
-Our work is mostly related to the MAC and MANN type models.
+Our work is mostly related to the MAC~\cite{hudson2018compositional} as well as neural network models with
+external memory~\cite{graves2014neural, graves2016hybrid} that support flexible addressing mechanisms 
+including sequential- and content-based addressing. 
 An important distinction of our approach is the frame-by-frame processing of the video input.

### 2019-11-16 cvpr_submission/experiments.tex
Spell checking the files. Minor edits.

@@
 and the number of object distractors (see~\cref{tab:cog_variants}).
-For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attributes values (details in~\cref{sec:temporal}).
+For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attribute values (details in~\cref{sec:temporal}).
 %In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
@@
 Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object attributes values (15 labels).
+Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object-attribute values (15 labels).
 
@@
 The final set of experiments we consider is related to feature transfer.
-The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color attributes.
+The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color-attributes.
 The colors are partitioned into two complementary families: 
@@
 the spheres can take any color (See~\cref{tab:cogent_conditions}). 
-Considering the input domain to be the set of objects with all attributes values, both sets differ by their marginal distributions $P_S$ and $P_T$.
+Considering the input domain to be the set of objects with all attribute values, both sets differ by their marginal distributions $P_S$ and $P_T$.
 We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (zero-shot learning) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).

### 2019-11-16 cvpr_submission/introduction.tex
Spell checking the files. Minor edits.

@@
 
-In Computer Vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
+In Computer Vision, it is now standard practice to pretrain an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
 Such performance improvements are appealing, especially for cases where both the domain (e.g.
@@
 In this work, we focus on multi-modal learning~\cite{mogadala2019trends} combining vision and language,
-and in particular, transfer learning for visual reasoning tasks with a rich logical structure, e.g., see~\cite{johnson2017clevr,yang2018dataset}. 
+and in particular, transfer learning for visual reasoning tasks that have a ``nice'' logical structure, e.g., 
+see~\cite{johnson2017clevr,yang2018dataset,song2018explore}. 
 While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
@@
 
-Our main contributions are:
-\begin{itemize}
+\smallskip
+
+\noindent Motivated by these considerations:
+%Consequently:
+\begin{enumerate}
 	%\compresslist
@@
 Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
-	\item Following, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer.
+	\item Subsequently, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer.
 This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants.
-Several of these experiments show the significant generalization capabilities of SAMNet.
-\end{itemize}
+Several of these experiments show significant transfer learning capabilities of SAMNet.
+\end{enumerate}

### 2019-11-16 cvpr_submission/related_work.tex
Spell checking the files. Minor edits.

--- 2019-11-16 cvpr_submission/related_work.tex
@@
 
-Our work is mostly related to the MAC and MANN type models.
+Our work is mostly related to the MAC~\cite{hudson2018compositional} as well as neural networks with
+external memory~\cite{graves2014neural, graves2016hybrid} that support flexible addressing mechanisms 
+including sequential and content-based addressing. 
 An important distinction of our approach is the frame-by-frame processing of the video input.

### 2019-11-16 cvpr_submission/transfer_learning.tex
Fix weird bug.
Spell checking the files. Minor edits.

@@
 defines a separate task.
+
 \begin{definition}[\cite{pan2009survey}]
@@
 but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
-One setting is the case of static images, where this could be due to having different feature combinations in the source and
-target but a different setting is in the context of video reasoning where the number of frames can be small in one case and 
-large in another.
-These require possibly very different methods, one involving building disentangled feature representations that can generalize across 
-domains and another in which we might need memory-augmented neural networks that can generalize across frame lengths.
+As mentioned in the introduction, one setting is the case of static images, 
+where this could be due to having different feature combinations in the source and target.
+A different setting is in the context of video reasoning where the number of frames can increase significantly going from source to target.
+These require possibly very different methods: the first involves building disentangled feature representations that can generalize across 
+domains; the second might need external memory to remember relevant objects to generalize across frame lengths.
 Another situation is when the questions themselves can be grouped into families such as count-based queries, 
@@
 \begin{description}
-	\compresslist % used to reduce spacing
+	%\compresslist % used to reduce spacing
 	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$

### 2019-11-16 cvpr_submission/introduction.tex
introduction polishing, added LSTM reference, minor fixes in transfer learning and samnet sections

@@
 
-In Computer Vision, it is now standard practice to pretrain an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
-Such performance improvements are appealing, especially for cases where both the domain (e.g.
-realistic images vs.
-medical or cars ones) and the task (e.g.
-image classification vs.
-VQA or image segmentation) can change significantly.
+In Computer Vision, it is now standard practice to pretrain an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as segmentation of cars~\cite{iglovikov2018ternausnet} or Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging}.
+Such performance improvements are appealing, especially in cases where both the domain (natural vs.
+medical images) and the task (image classification vs.
+image segmentation vs VQA) change significantly.
 %This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
 
-A similar development has emerged in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, has become a standard procedure when working with different NLP domains and tasks,
-especially when labeled data is less accessible.
-Recently, we observe a growing utilization of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amounts of data.
-In analogy to pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations.
+Similar developments have emerged in the Natural Language Processing (NLP) community.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, has become a standard procedure when working with different NLP domains and tasks.
+Recently, there is a clear, growing trend of utilization of deep contextualized word representations such as ELMo~\cite{peters2018deep} (based on bidirectional LSTMs~\cite{hochreiter1997long}) or BERT~\cite{devlin2018bert} (based on the Transformer~\cite{vaswani2017attention} architecture), where entire deep networks (not just the input layer) are pretrained on very large corporas.
+In analogy to pretrained image encoders, the NLP community has also started to create model repositories, some with dozens of pretrained models ready to be downloaded and used.
 HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
 
-The success of transfer learning raises several questions for research, such as the characteristics which make a dataset more favorable to use in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
-One of the most systematic work in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aim to discover the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.
+The success of transfer learning raises several research questions, such as the characteristics which make a dataset more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
+One of the most systematic works in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aimed at discovering the dependencies between twenty-six 2D, 2.5D, 3D, and semantic computer vision tasks.
 
-In this work, we focus on multi-modal learning~\cite{mogadala2019trends} combining vision and language,
-and in particular, transfer learning for visual reasoning tasks that have a ``nice'' logical structure, e.g., 
-see~\cite{johnson2017clevr,yang2018dataset,song2018explore}. 
+In this work we focus on transfer learning in multi-modal tasks combining vision and language~\cite{mogadala2019trends} .
+More precisely, we narrow the scope to transfer learning between visual reasoning tasks that have a ``nice'' logical structure, e.g.,~\cite{johnson2017clevr,yang2018dataset,song2018explore}. 
 While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
@@
 (\cref{sec:feature}).
-In this case, training on the first dataset might yield entangled feature representations that may fail reasoning tasks
-on the second dataset.
+In this case, training on the first variant might yield entangled feature representations that may fail reasoning tasks
+on the second one.
 In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
-transfer over to longer sequences, e.g., the Canonical and the Hard variants of the 
+transfer over to longer ones, e.g., the Canonical and the Hard variants of the 
 COG dataset~\cite{yang2018dataset} (\cref{sec:temporal}).

### 2019-11-16 cvpr_submission/experiments.tex

@@
 
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer_v3}
+	\caption{COG accuracies for all task groups $t$ when training on $t$ only, training on Group A or B and training on all tasks.}
+	\label{fig:COG-reasoning-results}
+\end{figure}
+
 We then conducted the following experiments using the Canonical variant of COG to study 
@@
 	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (standard ML). 
-	\item Train on \textbf{Group A} and test on \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare} each;
-	\item Train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
+	\item Jointly train on \textbf{Group A} and test separately on \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare};
+	\item Jointly train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
 	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
-	can be viewed as training on \textbf{All} and testing on each group at the leaf level separately.
+	can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately.
 \end{itemize}
@@
 To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.
-
- \begin{figure}
- 	\centering
- 	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer.pdf}
- 	\caption{COG accuracies for all task groups $t$ when training on $t$ only, training on Group A or B and training on all tasks.}
- 	\label{fig:COG-reasoning-results}
- \end{figure}
 

### 2019-11-16 cvpr_submission/experiments.tex
polishing last section of experiments

@@
 %Appendix \ref{sec:full-cogent-results}
-finetune the model trained on all tasks on each task $t$ respectively.
-%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the finetuned task and the drop, if any, on other tasks.
-Finetuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
+fine-tune the model trained on all tasks on each task $t$ respectively.
+%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the fine-tuned task and the drop, if any, on other tasks.
+Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
 Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
@@
 	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer_v3}
-	\caption{COG accuracies for all task groups $t$ when training on $t$ only, training on Group A or B and training on all tasks.}
+	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
 	\label{fig:COG-reasoning-results}
@@
  	\compresslist
-	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (standard ML). 
-	\item Jointly train on \textbf{Group A} and test separately on \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare};
-	\item Jointly train on \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
+	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (Single-task training);
+	\item Jointly train on:
+	\begin{itemize}
+		\item 	 \textbf{Group A} and test on each task from the lowest groups (i.e. \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare}) separately;
+		\item \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
+	\end{itemize}
 	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
-	can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately.
+	can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately (All-task training).
 \end{itemize}
@@
 The observed close scores in light and dark gray underscore the baseline model reproducibility.
-For both cases of zero-shot learning (second column--91.6\% vs 65.9\%) and finetuning using a single epoch 
+For both cases of zero-shot learning (second column--91.6\% vs 65.9\%) and fine-tuning using a single epoch 
 (third column--96.7\% vs. 78.1\%), SAMNET outperforms the baseline model significantly.
-Interestingly, this finetuning yields a mild boost of +0.6\% on the earlier reported accuracy 
+Interestingly, this fine-tuning yields a mild boost of +0.6\% on the earlier reported accuracy 
 in~\cref{sec:cog-baseline-compare} (fourth column).
@@
 	%\end{adjustbox}
-	\caption{Color restrictions in CoGenT-A \& -B datasets.}
+	\caption{Restrictions on feature combinations in A \& B conditions of the CoGenT variant of the CLEVR dataset.}
 	\label{tab:cogent_conditions}
@@
 The final set of experiments we consider is related to feature transfer.
-The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color-attributes.
+The CoGenT-A \& -B variants of CLEVR differ by the available combinations of 8 object color-attributes.
 The colors are partitioned into two complementary families: 
 Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
-The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while
-the spheres can take any color (See~\cref{tab:cogent_conditions}). 
-Considering the input domain to be the set of objects with all attribute values, both sets differ by their marginal distributions $P_S$ and $P_T$.
-We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (zero-shot learning) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
-The results are available in~\cref{fig:CoGenT-B-results}.
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}). 
+As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
+We conduct 2 experiments with SAMNet trained on CoGenT-A:
+\begin{itemize}
+\item an immediate test (zero-shot learning) from A to B; and 
+\item fine-tuning for a single epoch on 30k samples from CoGenT-B (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+\end{itemize}
 
@@
 	\includegraphics[width=0.8\columnwidth]{img/results/CoGenT_B_results.pdf}
-	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and finetuning on CoGenT-B (gray).}
+	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
 	\label{fig:CoGenT-B-results}
 \end{figure}
-Evaluating SAMNet on CoGenT shows that performance is worse on CoGenT-B than CoGenT-A, in line with~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.
-Finetuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A, also observed with other models.
+
+Performance of SAMNet on CoGenT (\cref{fig:CoGenT-B-results}) is clearly worse on CoGenT-B than CoGenT-A.
+Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
+Both are consistent with findings from the literature~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.

### 2019-11-16 cvpr_submission/summary.tex
Commented 2 sentences in CLEVR section + 1 sentence in  summary to reduce space. Also reduced size of transfer taxonomy by 10%.
polish of summary

@@
 
-In this paper, through the introduction of a novel Memory-Augmented Neural Network model, SAMNet, we have quantified the impact of Transfer Learning in Visual Reasoning.
-Designed to learn to reason over sequences of frames (i.e., static images), SAMNet shows significant improvements, on the video reasoning dataset COG, over the corresponding baseline.
-Analysis of the results highlights the model's ability to operate independently of the number of frames and generalize to samples with higher complexity, characterized by longer sequences and more complex scenes.
-However, SAMNet can sporadically store spurious objects in the memory, despite its mechanisms.
-This doesn't prevent the model to produce accurate predictions.
+In this paper we quantified the impact of Transfer Learning on Visual Reasoning. 
+We have proposed a new taxonomy of transfer learning for Visual Reasoning, articulated around three axes: feature, temporal and reasoning transfer. 
+We have also introduced a novel Memory-Augmented Neural Network model called SAMNet.
+SAMNet, designed to learn to reason over sequences of frames, shows significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieves comparable performances on the CLEVR dataset for Image Resoning.
 
-We also introduce a new taxonomy of transfer learning for visual reasoning, articulated around three axes: feature transfer, temporal transfer and reasoning transfer.
-To highlight the robustness of this taxonomy, we realize an extensive set of experiments with SAMNet over two datasets: COG and CLEVR, a diagnostic dataset for Question Answering over static images.
-SAMNet demonstrates clear generalization capabilities along certain axes and, through the cautious use of finetuning, further advances performance in visual reasoning.
+Taking that as a starting point and leveraging on the proposed taxonomy, we  have conducted an extensive set of experiments, with focus on impact of transfer learning in areas that might be considered as higher-level reasoning.
+SAMNet demonstrated very good generalization capabilities along certain axes and, through the cautious use of fine-tuning, we have managed to eleviate its performance even further.
 
-We hope these contributions can bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.
+Finally, we note that some of the proposed tasks (e.g.
+Train on all but \textit{t}) are complementary to the ones already well established in the literature, e.g.
+in taskonomy~\cite{zamir2018taskonomy}.
+We hope these contributions will bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.

### 2019-11-16 cvpr_submission/summary.tex
Minor typo corrections.

@@
 
-In this paper we quantified the impact of Transfer Learning on Visual Reasoning. 
+In this paper, we quantified the impact of Transfer Learning on Visual Reasoning. 
 We have proposed a new taxonomy of transfer learning for Visual Reasoning, articulated around three axes: feature, temporal and reasoning transfer. 
 We have also introduced a novel Memory-Augmented Neural Network model called SAMNet.
-SAMNet, designed to learn to reason over sequences of frames, shows significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieves comparable performances on the CLEVR dataset for Image Resoning.
+SAMNet, designed to learn to reason over sequences of frames, shows significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieves comparable performance on the CLEVR dataset for Image Reasoning.
 
-Taking that as a starting point and leveraging on the proposed taxonomy, we  have conducted an extensive set of experiments, with focus on impact of transfer learning in areas that might be considered as higher-level reasoning.
-SAMNet demonstrated very good generalization capabilities along certain axes and, through the cautious use of fine-tuning, we have managed to eleviate its performance even further.
+Taking that as a starting point and leveraging the proposed taxonomy, we have conducted an extensive set of experiments, focusing on the impact of transfer learning in areas that might be considered as higher-level reasoning.
+SAMNet demonstrates very good generalization capabilities along certain axes and, through the cautious use of fine-tuning, can see its performance advanced even further.
 
-Finally, we note that some of the proposed tasks (e.g.
-Train on all but \textit{t}) are complementary to the ones already well established in the literature, e.g.
-in taskonomy~\cite{zamir2018taskonomy}.
+Finally, we note that some of the proposed tasks (e.g. Train on all but \textit{t}) are complementary to ones already well established in the literature, e.g. in Taskonomy~\cite{zamir2018taskonomy}.
 We hope these contributions will bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.

### 2019-11-20 Transfer_Learning/arxiv_version/introduction.tex
Rearranging folders because of arxiv version

--- 2019-11-16 cvpr_submission/introduction.tex
@@
 
-In this work we focus on transfer learning in multi-modal tasks combining vision and language~\cite{mogadala2019trends} .
+In this work we focus on transfer learning in multi-modal tasks combining vision and language~\cite{mogadala2019trends}.
 More precisely, we narrow the scope to transfer learning between visual reasoning tasks that have a ``nice'' logical structure, e.g.,~\cite{johnson2017clevr,yang2018dataset,song2018explore}. 
@@
 once the modalities have been fused.
-For example, the CoGenT (Constrained Generalization Test) variant of the CLEVR~\cite{johnson2017clevr}  
-contains two datasets with similar questions, but differing on combinations of object-attribute values in images 
+For example, the CoGenT (Constrained Generalization Test) variant of the CLEVR dataset~\cite{johnson2017clevr}  
+contains two sets with similar questions, but differing on combinations of object-attribute values in images 
 (\cref{sec:feature}).

### 2019-11-20 Transfer_Learning/arxiv_version/paper_main.tex
Rearranging folders because of arxiv version

--- 2019-11-16 cvpr_submission/paper_main.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\documentclass[11pt]{article}
 
-\usepackage{cvpr}
-\usepackage{times}
+\usepackage[letterpaper,margin=1in]{geometry}
+%\usepackage{cvpr}
+%\usepackage{times}
 %\usepackage{epsfig}
@@
 }
-%\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{7813} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
 
@@
 % WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
-\author{T.S. Jayram \and  Vincent Marois \and Vincent Albouy \and Tomasz Kornuta  \and Emre Sevgen \and Ahmet Ozcan\\
+\author{T.S. Jayram \and  Vincent Marois \and \and Tomasz Kornuta \and Vincent Albouy \and Emre Sevgen \and Ahmet Ozcan\\
 IBM Research AI\\
@@
 Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
-{\tt\small {jayram,  asozcan}@us.ibm.com}
-{\tt\small {tkornuta, sesevgen}@gmail.com}
+{\tt\small \{jayram,  asozcan\}@us.ibm.com}
+{\tt\small \{tkornuta, sesevgen\}@gmail.com}
 {\tt\small vincent.marois@ibm.com}
@@
 We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer.
-Based on extensive experimentation on transfer learning on the two datasets, we show the performance of the new model along each axis.
+Based on extensive experimentation of transfer learning on each of the two datasets, we show the performance of the new model along each axis.
 \end{abstract}
@@
 
-\clearpage
-{\small
-\bibliographystyle{ieee_fullname}
+\bibliographystyle{alpha}
 \bibliography{bibliography}
-}
 
-%\clearpage
-%\input{appendix}
+\newpage
+\input{appendix}
 

### 2019-11-20 Transfer_Learning/arxiv_version/transfer_learning.tex
Rearranging folders because of arxiv version

--- 2019-11-16 cvpr_submission/transfer_learning.tex
@@
 	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
-	and the task $f(q,v)$ is just the answer to the question $q$ on $v$. The output set $\cY$ is the union of legitimate answers
+	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
 	over all questions in $\cQ$.

### 2019-11-20 Transfer_Learning/cvpr_submission/samnet.tex
Rearranging folders because of arxiv version

--- 2019-11-16 cvpr_submission/samnet.tex
@@
 A similar operation on memory yields the object $\vec{mo}_t$.
-The memory operation is based on an attention mechanism, and resembles content-based addressing.
+The memory operation is based on attention mechanism, and resembles content-based addressing.
 Therefore, we obtain an attention vector over memory addresses that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
@@
 First, we compute a simple aggregate\footnote{%
-	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.} of the visual attention vector $\vec{va}_t$ of dimension $L$ ($L$ denotes the number of feature vectors for the frame):
+	This is closely related to R\'{e}nyi entropy and Tsallis entropy of order~2.} of the visual attention vector $\vec{va}_t$ of dimension $L$ ($L$ denotes the number of feature vectors for the frame):
 $vs_t = \sum_{i=1}^L [\vec{va}_t(i)]^2$. It can be shown that the more localized the attention

### 2019-11-20 Transfer_Learning/cvpr_submission/experiments.tex
Rearranging folders and references

--- 2019-11-16 cvpr_submission/experiments.tex
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_canonical_no_labels.png}
+		\includegraphics[width=0.9\textwidth]{../img/results/samnet_cog_orig_canonical_no_labels.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_hard.png}
+		\includegraphics[width=0.9\textwidth]{../img/results/samnet_cog_orig_hard.png}
 	\end{subfigure}%
@@
 	\centering
-	\includegraphics[width=\columnwidth]{img/results/CoGenT_results.pdf}
+	\includegraphics[width=\columnwidth]{../img/results/CoGenT_results.pdf}
 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{img/architecture/hierarchy}
+	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
 	\caption{Hierarchy of Task Groups.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer_v3}
+	\includegraphics[width=\columnwidth]{../img/results/COG_reasoning_transfer_v3}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{img/results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=\columnwidth]{../img/results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{img/results/CoGenT_B_results.pdf}
+	\includegraphics[width=0.8\columnwidth]{../img/results/CoGenT_B_results.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}

### 2019-11-20 Transfer_Learning/arxiv_version/experiments.tex
Minor changes

--- 2019-11-16 cvpr_submission/experiments.tex
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_canonical_no_labels.png}
+		\includegraphics[width=\textwidth]{../img/results/samnet_cog_orig_canonical_no_labels.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_hard.png}
+		\includegraphics[width=\textwidth]{../img/results/samnet_cog_orig_hard.png}
 	\end{subfigure}%
@@
 \begin{itemize}
-	\compresslist
 	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
@@
 Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../img/results/CoGenT_results.pdf}
+	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
+	\label{fig:CoGenT-results}
+\end{figure}
 
@@
 
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth]{img/results/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
-	\label{fig:CoGenT-results}
-\end{figure}
-
 An additional set of experiments, for which results are available in the supplementary material,
@@
 
-\begin{figure}[htb]
+\begin{figure}[!t]
 	\centering
-	\includegraphics[width=\columnwidth]{img/architecture/hierarchy}
+	\includegraphics[width=0.8\textwidth]{../img/architecture/hierarchy}
 	\caption{Hierarchy of Task Groups.}
@@
 \begin{description}
-	\compresslist
 	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist};
@@
 	\centering
-	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer_v3}
+	\includegraphics[width=0.85\textwidth]{../img/results/COG_reasoning_transfer_v3}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
@@
  \begin{itemize}
- 	\compresslist
 	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (Single-task training);
@@
 	\centering
-	\includegraphics[width=\columnwidth]{img/results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.8\textwidth]{../img/results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{img/results/CoGenT_B_results.pdf}
+	\includegraphics[width=0.6\textwidth]{../img/results/CoGenT_B_results.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}

### 2019-11-20 Transfer_Learning/arxiv_version/paper_main.tex
Minor changes

@@
 % WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
-\author{T.S. Jayram \and  Vincent Marois \and \and Tomasz Kornuta \and Vincent Albouy \and Emre Sevgen \and Ahmet Ozcan\\
-IBM Research AI\\
-Almaden Research Center, San Jose, CA 95120, USA\\
-Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
-{\tt\small \{jayram,  asozcan\}@us.ibm.com}
-{\tt\small \{tkornuta, sesevgen\}@gmail.com}
-{\tt\small vincent.marois@ibm.com}
+\author{%
+	T.S. Jayram\thanks{IBM Research AI.
+		\textit{Location}: Almaden Research Center, San Jose, CA, USA.} \and  
+	Vincent Marois\thanks{IBM Research AI. 
+		\textit{Location}: Thomas J. Watson Research Center, Yorktown Heights, NY, USA.} \and 
+	Tomasz Kornuta\thanks{Nvidia Research. 
+		\textit{Location}: Santa Clara, CA, USA.
+		Work done while employed at IBM Research AI.} \and 
+	Vincent Albouy  \and 
+	Emre Sevgen \and 
+	Ahmet Ozcan\footnotemark[1]
 }
+
+%\author{ABC\thanks{XYZ} \and DEF\thanks{UVW} \and GHI\footnotemark[1]}
 

### 2019-11-20 Transfer_Learning/arxiv_version/experiments.tex
rearranging again

@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/results/samnet_cog_orig_canonical_no_labels.png}
+		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/results/samnet_cog_orig_hard.png}
+		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_hard.png}
 	\end{subfigure}%
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../img/results/CoGenT_results.pdf}
+	\includegraphics[width=0.8\textwidth]{../results/CoGenT_results.pdf}
 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{../img/results/COG_reasoning_transfer_v3}
+	\includegraphics[width=0.85\textwidth]{../results/COG_reasoning_transfer_v3}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../img/results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.8\textwidth]{../results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{../img/results/CoGenT_B_results.pdf}
+	\includegraphics[width=0.6\textwidth]{../results/CoGenT_B_results.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}

### 2019-11-20 Transfer_Learning/cvpr_submission/experiments.tex
Bugfix

@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{../img/results/samnet_cog_orig_canonical_no_labels.png}
+		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{../img/results/samnet_cog_orig_hard.png}
+		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_hard.png}
 	\end{subfigure}%
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/results/CoGenT_results.pdf}
+	\includegraphics[width=\columnwidth]{../results/CoGenT_results.pdf}
 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/results/COG_reasoning_transfer_v3}
+	\includegraphics[width=\columnwidth]{../results/COG_reasoning_transfer_v3}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=\columnwidth]{../results/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{../img/results/CoGenT_B_results.pdf}
+	\includegraphics[width=0.8\columnwidth]{../results/CoGenT_B_results.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}

### 2019-11-21 Transfer_Learning/arxiv_version/paper_main.tex
Fixing appendix

--- 2019-11-20 Transfer_Learning/arxiv_version/paper_main.tex
@@
 \usepackage[letterpaper,margin=1in]{geometry}
-%\usepackage{cvpr}
-%\usepackage{times}
-%\usepackage{epsfig}
+\usepackage{times}
 \usepackage{graphicx}
-\usepackage[font=small]{subcaption}
-\captionsetup[figure]{skip=5pt}
-\captionsetup[table]{skip=5pt}
-\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
+\usepackage{subcaption}
 \usepackage{amsmath, amssymb, amsfonts,bm}
@@
 \usepackage{booktabs}
-\usepackage{multirow}
 \usepackage{adjustbox}
-\usepackage{tabularx}
 \usepackage{xcolor}
@@
 \hypersetup{
-	pagebackref,
 	colorlinks,
 	breaklinks,
-	bookmarks=false,
 	linkcolor={red!50!black},
@@
 	urlcolor={blue!80!black},
-	%linkcolor=OliveGreen,
-	%citecolor=Blue,
 }
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{definition}[theorem]{Definition}
-
-\theoremstyle{remark}
-\newtheorem*{notation}{Notation}
-%\newtheorem*{remark}{Remark}
-\newtheorem*{note}{Note}
-
-\newtheorem{fact}{Fact}
-\newtheorem*{observation}{Observation}
-\newtheorem*{condition}{Condition}
-\newtheorem*{claim}{Claim}
-\newtheorem*{example}{Example}
-\newtheorem*{question}{Question}
+\newtheorem*{definition}{Definition}
 
@@
 
-\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{enumerate} or \begin{enumerate}
-\setlength{\itemsep}{1pt}
-\setlength{\parskip}{0pt}
-\setlength{\parsep}{0pt}}
-
 %%%%%%%%%%%%%%%
@@
 %%%%%%%%% TITLE
-\title{Transfer Learning in Visual and Relational Reasoning}
+\title{Transfer Learning in Visual and Relational Reasoning\footnote{%
+		Major portion of this work was done when all the authors were at IBM Research AI (Almaden)}}
 
@@
 % WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
-\author{T.S. Jayram \and  Vincent Marois \and \and Tomasz Kornuta \and Vincent Albouy \and Emre Sevgen \and Ahmet Ozcan\\
-IBM Research AI\\
-Almaden Research Center, San Jose, CA 95120, USA\\
-Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
-{\tt\small \{jayram,  asozcan\}@us.ibm.com}
-{\tt\small \{tkornuta, sesevgen\}@gmail.com}
-{\tt\small vincent.marois@ibm.com}
+\author{%
+	T.S. Jayram\thanks{IBM Research AI.
+		Location: \textit{Almaden Research Center, San Jose, CA, USA}.} \and  
+	Vincent Marois\thanks{IBM Research AI. 
+		Location: \textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \and 
+	Tomasz Kornuta\thanks{Nvidia Research. 
+		Location: \textit{Santa Clara, CA, USA}.} \and 
+	Vincent Albouy\thanks{} \and 
+	Emre Sevgen\thanks{University of Chicago.}  \and 
+	Ahmet Ozcan\footnotemark[2]
 }
+
+\date{}
 

### 2019-11-21 Transfer_Learning/cvpr_submission/appendix.tex
Fixing appendix

\section{Datasets: CLEVR-CoGenT and COG}
\label{sec:datasets-desc}
%Here are the details of the COG dataset.
%
The CoGenT dataset~\cite{johnson2017clevr} contains:
\begin{itemize}
	\def\labelitemi{--}
	\item Training set of 70,000 images and 699,960 questions in Condition A,
	\item Validation set of 15,000 images and 149,991 questions in Condition A,
	\item Test set of 15,000 images and 149,980 questions in Condition A (without answers),
	\item Validation set of 15,000 images and 150,000 questions in Condition B,
	\item Test set of 15,000 images and 149,992 questions in Condition B (without answers),
	\item Scene graphs and functional programs for all training/validation images/questions.
\end{itemize}

The combinations of attributes in CoGenT-A and CoGenT-B are shown in~\cref{tab:cogent_conditions_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{cccc}
		\toprule
		Dataset	&	Cubes	&	Cylinders	&	Spheres	\\
		\midrule
		CoGenT-A	&	Gray / Blue / Brown / Yellow	&	Red / Green / Purple / Cyan	&	Any color	\\
		CoGenT-B	&	Red / Green / Purple / Cyan	&	Gray / Blue / Brown / Yellow	&	Any color 	\\
		\bottomrule
	\end{tabular}
	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
	\label{tab:cogent_conditions_supplement}
\end{table}

The Canonical and Hard variants of the COG dataset~\cite{yang2018dataset} are contrasted in~\cref{tab:cog_variants_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{lcccccc}
		\toprule
		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
		& of   & memory & number of & of & of & of  \\
		& frames & duration & distractors & training set & validation set & test set \\
		\midrule
		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
		\bottomrule	
	\end{tabular}
	\caption{Details of the Canonical and Hard variants of the COG dataset.}
	\label{tab:cog_variants_supplement}
\end{table}
%
%\begin{table}[ht]
%	\centering
%	\begin{tabular}{lcccccc}.
%		\toprule
%		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
%		& of   & memory & number of & of & of & of 
%%		& frames & duration & distractors & training set & validation set & test set \\
%		\midrule
%		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
%		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
%		\bottomrule	
%	\end{tabular}
%	\caption{Details of the Canonical and Hard variants of the COG dataset.}
%	\label{tab:cog_variants_supplement}
%\end{table}

\clearpage
\section{Complete COG results}
\label{sec:cog-all-results}

\begin{table*}[htb]
\centering
	\begin{adjustbox}{width=\columnwidth}
	\begin{tabular}{lcccccccccc}
		\toprule
		Model & & SAMNet & && && Baseline Model&& \\
		\cmidrule{2-5} \cmidrule{7-11} 
		&&&&& & paper & code & code & paper&\\
		\cmidrule{7-9} \cmidrule{10-11}
		Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
		Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
		Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
		\midrule

		Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\

		\midrule

		AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
		AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
		AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
		AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
		CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
		CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
		Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
		ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
		ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
		ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
		ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
		ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
		ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
		ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
		ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
		ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
		ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
		GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
		GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
		GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
		GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
		SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
		SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
		\bottomrule
		\end{tabular}
		\end{adjustbox}
	\caption{COG test set accuracies for SAMNet and baseline model~\cite{yang2018dataset}. Below `paper' denotes results from~\cite{yang2018dataset} with further author clarifications (private communication) while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}.}
	\label{tab:all-results}
\end{table*}

\clearpage
\section{Complete CLEVR-CoGenT results}
\label{sec:full-cogent-results}

\begin{table*}[htb]
	\centering
	\begin{adjustbox}{width=\columnwidth}
	\begin{tabular}{c c c c c c c }\toprule
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{Exist only} & 26.07 & \emph{74.20}	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
		\multicolumn{1}{ c }{Count only} & 14.89  & 0.0	& \emph{62.78}	& 0.0 & 0.0 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareInteger only} & 23.44 & 48.15	& 0.0	& \emph{77.98}	& 54.08 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareAttribute only} & 23.50 & 51.93	& 0.0 & 59.06 & \emph{61.73} & 0.0 \\ 
		\multicolumn{1}{ c }{QueryAttribute only} & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & \emph{97.08} \\ 		
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		\multicolumn{1}{ c }{All tasks} & 95.32 & 98.4 	& 86.75	& 96.0	& 98.65	& 98.02 \\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		\multicolumn{1}{ c }{All tasks but Exist} & 90.33 	& \emph{60.42}	& 86.12	& 96.18	& 98.52 & 98.60 \\ 
		\multicolumn{1}{ c }{All tasks but Count} & 74.59 	& 97.51	& \emph{0.0}	& 94.37	& 98.42 & 98.47 \\ 
		\multicolumn{1}{ c }{All tasks but CompareInteger} & 91.53 	& 98.22	& 86.09	& \emph{56.35}	& 98.78 & 98.40 \\ 
		\multicolumn{1}{ c }{All tasks but CompareAttribute} & 81.92 	& 98.32	& 86.36	& 95.86	& \emph{23.18} & 98.44 \\ 
		\multicolumn{1}{ c }{All tasks but QueryAttribute} & 42.17 	& 76.79	& 54.64	& 79.87 & 64.13 & \emph{0.0} \\

		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		\multicolumn{1}{ c }{\textit{Trained on all tasks -- Finetune on $t$}} & &  & &  & &\\ 
		\multicolumn{1}{ c }{Exist} & 94.16 & \emph{98.04} & 82.96 & 95.02 & 98.12 & 97.97 \\ 
		\multicolumn{1}{ c }{Count} & 95.10 & 96.46 & \emph{88.28} & 94.78 & 97.01 & 98.26 \\
		\multicolumn{1}{ c }{CompareInteger} & 95.31 & 98.39 & 86.56 & \emph{96.07} & 98.70 & 98.09 \\
		\multicolumn{1}{ c }{CompareAttribute} & 95.31 & 98.40 & 86.78 & 96.00 & \emph{98.66} & 98.04 \\
		\multicolumn{1}{ c }{QueryAttribute} & 93.49 & 97.45 & 82.09 & 92.23 & 97.85& \emph{97.76} \\

		\bottomrule
	\end{tabular}
	\end{adjustbox}
	\caption{Complete set of results for SAMNet on CLEVR-CoGenT.}
	\label{tab:CoGenT-results}
\end{table*}

### 2019-11-21 Transfer_Learning/cvpr_submission/supplementary_material.tex
Fixing appendix

--- 2019-11-15 cvpr_submission/paper_main.tex
@@
 \usepackage{times}
-%\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage[font=small]{subcaption}
-\captionsetup[figure]{skip=5pt}
-\captionsetup[table]{skip=5pt}
-\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
-\usepackage{amsmath, amssymb, amsfonts,bm}
-\usepackage{amsthm}
 
-% Include other packages here, before hyperref.
 \usepackage{booktabs}
-\usepackage{multirow}
 \usepackage{adjustbox}
-\usepackage{tabularx}
+\usepackage{xcolor}
 
-\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks,
+	breaklinks,
+	linkcolor={red!50!black},
+	citecolor={blue!50!black},
+	urlcolor={blue!80!black},
+}
+
+\usepackage{cleveref}
+\crefname{table}{Table}{Tables}
 
@@
 %%%%%%%%% TITLE
-\title{Transfer Learning in Multimodal Compositional and Relational Reasoning}
+\title{Transfer Learning in Visual and Relational Reasoning\\ (Supplementary Material)}
 
 %%%%%%%%% AUTHORS
-% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
 \author{T.S. Jayram \and  Vincent Marois \and Vincent Albouy \and Tomasz Kornuta  \and Emre Sevgen \and Ahmet Ozcan\\
@@
 
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  Transfer learning is becoming the de facto solution for vision and text encoders in the front-end processing of machine learning solutions.
-Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited.
-In this paper, we analyze the efficiency of transfer learning in multimodal (vision and language) reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.
-Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline.
-We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer.
-Based on extensive experimentation on transfer learning on the two datasets, we show the performance of the new model along each axis.
-\end{abstract}
+\input{appendix}
 
-%%%%%%%%% BODY TEXT
-\input{introduction}
+\bigskip
 
-\input{related_work}
-
-\input{transfer_learning}
-
-\input{samnet}
-
-\input{experiments}
-
-\input{summary}
-
-{\small
+\clearpage
 \bibliographystyle{ieee_fullname}
 \bibliography{bibliography}
-}
-
-\clearpage
-\input{appendix}
 

### 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Fixed appendix in both supplementary and arxiv. Added results from SoftPaths to the arxiv version. Added a comment in the main body as well.

--- 2019-11-21 Transfer_Learning/arxiv_version/paper_main.tex
@@
 \title{Transfer Learning in Visual and Relational Reasoning\footnote{%
-		Major portion of this work was done when all the authors were at IBM Research AI (Almaden)}}
+		This work was primarily done at IBM Research AI.}}
 
@@
 \author{%
-	T.S. Jayram\thanks{IBM Research AI.
-		Location: \textit{Almaden Research Center, San Jose, CA, USA}.} \and  
-	Vincent Marois\thanks{IBM Research AI. 
-		Location: \textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \and 
-	Tomasz Kornuta\thanks{Nvidia Research. 
-		Location: \textit{Santa Clara, CA, USA}.} \and 
+	T.S. Jayram\thanks{IBM Research AI. \textit{Almaden Research Center, San Jose, CA, USA}.} \and  
+	Vincent Marois\thanks{IBM Research AI. \textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \and 
+	Tomasz Kornuta\thanks{Nvidia Research. \textit{Santa Clara, CA, USA}.} \and 
 	Vincent Albouy\thanks{} \and 
-	Emre Sevgen\thanks{University of Chicago.}  \and 
+	Emre Sevgen\thanks{Citrine Informatics}  \and 
 	Ahmet Ozcan\footnotemark[2]
@@
 \bibliographystyle{alpha}
-\bibliography{bibliography}
+\bibliography{../bibliography}
 
 \newpage
+\appendix
+
 \input{appendix}

### 2019-11-22 Transfer_Learning/arxiv_version/experiments.tex
Fixed appendix in both supplementary and arxiv. Added results from SoftPaths to the arxiv version. Added a comment in the main body as well.

@@
 
-%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
+More details on the composition of these datasets is available in Appendix~\ref{sec:datasets-desc}.
 
@@
 We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in 
+Appendix~\ref{sec:cog-all-results}.
 
@@
 
+Appendix~\ref{sec:cog-all-results} also includes the task-by-task performance of ``SoftPaths'' model~\cite{haurilet2019s} on the Canonical variant of the COG dataset, on which it achieves on overall accuracy of 96.1\%.
+This model is however not recurrent, therefore, it is unsuitable for temporal transfer learning, in contrast to SAMNet or the baseline model of~\cite{yang2018dataset}.
+
 \subsection{Reasoning transfer on CLEVR and COG}
@@
 
-Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
+Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in Appendix~\ref{sec:full-cogent-results}.
 
@@
 
-An additional set of experiments, for which results are available in the supplementary material,
-%Appendix \ref{sec:full-cogent-results}
+An additional set of experiments, for which results are available in Appendix~\ref{sec:full-cogent-results},
 fine-tune the model trained on all tasks on each task $t$ respectively.

### 2019-11-22 Transfer_Learning/cvpr_submission/appendix.tex
Fixed appendix in both supplementary and arxiv. Added results from SoftPaths to the arxiv version. Added a comment in the main body as well.

@@
 	\centering
-	\begin{adjustbox}{width=\columnwidth}
-	\begin{tabular}{lcccccccccc}
+	\begin{adjustbox}{width=\textwidth}
+		\begin{tabular}{l c c c c c c c c c}
 			\toprule
-		Model & & SAMNet & && && Baseline Model&& \\
-		\cmidrule{2-5} \cmidrule{7-11} 
-		&&&&& & paper & code & code & paper&\\
-		\cmidrule{7-9} \cmidrule{10-11}
+			Model & \multicolumn{4}{c}{SAMNet} &  &\multicolumn{4}{c}{Baseline Model} \\
+			\cmidrule(lr){2-5} 
+			\cmidrule(lr){7-10} 
+			&&&&& & paper & code & code & paper\\
+			\cmidrule(lr){7-10} 
 			Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
@@
 			\midrule			
-
 			Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\ 
-
 			\midrule 
-
 			AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
@@
 	\end{adjustbox}
-	\caption{COG test set accuracies for SAMNet and baseline model~\cite{yang2018dataset}.
-Below `paper' denotes results from~\cite{yang2018dataset} with further author clarifications (private communication) while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}.}
+	\caption{COG test set accuracies for SAMNet and the baseline model~\cite{yang2018dataset}.
+The `paper' columns for the baseline model denote results taken from~\cite{yang2018dataset} along with some further author clarifications (private communication) to obtain the performance on individual task types while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}.}
 	\label{tab:all-results}

### 2019-11-22 Transfer_Learning/arxiv_version/experiments.tex
Minor changes

@@
 
-\subsection{Performance of SAMNet vs baseline model~\cite{yang2018dataset}}
+\subsection{Performance of SAMNet vs baseline model}
 \label{sec:cog-baseline-compare}
@@
 Appendix~\ref{sec:cog-all-results} also includes the task-by-task performance of ``SoftPaths'' model~\cite{haurilet2019s} on the Canonical variant of the COG dataset, on which it achieves on overall accuracy of 96.1\%.
-This model is however not recurrent, therefore, it is unsuitable for temporal transfer learning, in contrast to SAMNet or the baseline model of~\cite{yang2018dataset}.
+This model is however not recurrent, therefore, it is not immediately applicable for temporal transfer learning---in contrast to SAMNet or the baseline model of~\cite{yang2018dataset}---but we include it here for completeness.
 
@@
 
-\begin{figure}[!t]
+\begin{figure}[!h]
 	\centering
-	\includegraphics[width=0.8\textwidth]{../img/architecture/hierarchy}
+	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
 	\caption{Hierarchy of Task Groups.}
@@
 \end{figure}
-
-\bigskip
 
@@
 \end{description}
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.85\textwidth]{../results/COG_reasoning_transfer_v3}
-	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
-	\label{fig:COG-reasoning-results}
-\end{figure}
 
@@
 The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
+ \begin{figure}[!b]
+	\centering
+	\includegraphics[width=0.85\textwidth]{../results/COG_reasoning_transfer_v3}
+	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
+	\label{fig:COG-reasoning-results}
+\end{figure}
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[!b]
 	\centering
@@
 \label{sec:feature}
-\begin{table}[ht]
+The final set of experiments we consider is related to feature transfer.
+The CoGenT-A \& -B variants of CLEVR differ by the available combinations of 8 object color-attributes.
+The colors are partitioned into two complementary families: 
+Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}). 
+As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
+
+\begin{table}[h]
 	\centering
@@
 
-The final set of experiments we consider is related to feature transfer.
-The CoGenT-A \& -B variants of CLEVR differ by the available combinations of 8 object color-attributes.
-The colors are partitioned into two complementary families: 
-Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}). 
-As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
 We conduct 2 experiments with SAMNet trained on CoGenT-A:
@@
 
-\begin{figure}[!t]
+Performance of SAMNet on CoGenT (\cref{fig:CoGenT-B-results}) is clearly worse on CoGenT-B than CoGenT-A.
+Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
+Both are consistent with findings from the literature~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.
+
+\begin{figure}[!b]
 	\centering
@@
 \end{figure}
-
-Performance of SAMNet on CoGenT (\cref{fig:CoGenT-B-results}) is clearly worse on CoGenT-B than CoGenT-A.
-Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
-Both are consistent with findings from the literature~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.

### 2019-11-22 Transfer_Learning/cvpr_submission/appendix.tex
Minor changes

@@
 	\end{tabular}
+	\smallskip
 	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
@@
 	\end{tabular}
+	\smallskip
 	\caption{Details of the Canonical and Hard variants of the COG dataset.}
@@
 	\begin{adjustbox}{width=\textwidth}
-		\begin{tabular}{l c c c c c c c c c}
-			\toprule
+		\begin{tabular}{l r r r r r r r r r r}
+			\toprule[1.25pt]
 			Model & \multicolumn{4}{c}{SAMNet} &  &\multicolumn{4}{c}{Baseline Model} \\
@@
 			Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
-			\midrule			
+			\midrule[1pt]	
 			Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\ 
-			\midrule 
+			\midrule[1pt]	
 			AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
@@
 			ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
-			ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
+			ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70.0	&	89.8	&	89.80 \\
 			ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
@@
 			SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
-			\bottomrule
+			\bottomrule[1.25pt]
 		\end{tabular}
 	\end{adjustbox}
-	\caption{COG test set accuracies for SAMNet and the baseline model~\cite{yang2018dataset}.
-The `paper' columns for the baseline model denote results taken from~\cite{yang2018dataset} along with some further author clarifications (private communication) to obtain the performance on individual task types while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}.}
+	\smallskip
+	\caption{COG test set accuracies for SAMNet and the baseline model~\cite{yang2018dataset}. For the baseline model,
+		`paper' denotes results reproduced from~\cite{yang2018dataset} along with some further clarifications by the authors (private communication)  regarding the performance on individual task types while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}.}
 	\label{tab:all-results}
@@
 	\end{adjustbox}
+    \smallskip
 	\caption{Complete set of results for SAMNet on CLEVR-CoGenT.}

### 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Title + author Figure placement

@@
 %%%%%%%%% TITLE
-\title{Transfer Learning in Visual and Relational Reasoning\footnote{%
-		This work was primarily done at IBM Research AI.}}
+\title{Transfer Learning in Visual and Relational Reasoning}
 
@@
 \author{%
-	T.S. Jayram\thanks{IBM Research AI. \textit{Almaden Research Center, San Jose, CA, USA}.} \and  
-	Vincent Marois\thanks{IBM Research AI. \textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \and 
-	Tomasz Kornuta\thanks{Nvidia Research. \textit{Santa Clara, CA, USA}.} \and 
-	Vincent Albouy\thanks{} \and 
-	Emre Sevgen\thanks{Citrine Informatics}  \and 
-	Ahmet Ozcan\footnotemark[2]
+T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
+Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
+Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
+\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
+Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
+Ahmet S. Ozcan\footnotemark[1] \and \\
+IBM Research AI
 }

### 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Minor

@@
 Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
-Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
+Tomasz Kornuta\thanks{Currently at NVIDIA. \textit{Santa Clara, CA, USA}.} \and
 \hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
-Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
+Emre Sevgen\thanks{Currently at Citrine Informatics.}  \hspace{1cm} \and 
 Ahmet S. Ozcan\footnotemark[1] \and \\

### 2019-11-22 Transfer_Learning/cvpr_submission/appendix.tex
Minor

@@
 
-The combinations of attributes in CoGenT-A and CoGenT-B are shown in~\cref{tab:cogent_conditions_supplement}.
+\noindent The combinations of attributes in CoGenT-A and CoGenT-B are shown in~\cref{tab:cogent_conditions_supplement}.
 \begin{table}[ht]
@@
 
-The Canonical and Hard variants of the COG dataset~\cite{yang2018dataset} are contrasted in~\cref{tab:cog_variants_supplement}.
+\noindent The Canonical and Hard variants of the COG dataset~\cite{yang2018dataset} are contrasted in~\cref{tab:cog_variants_supplement}.
 \begin{table}[ht]

### 2019-11-23 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
font adjustments

--- 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
@@
 \author{%
-T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
-Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
-Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
-\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
-Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
+T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1.5cm} \and  
+Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1.5cm} \and 
+Tomasz Kornuta\thanks{Currently at NVIDIA. \textit{Santa Clara, CA, USA}.}  \and
+\hspace{1cm} Vincent Albouy\footnotemark[1]  \hspace{1.5cm} \and 
+Emre Sevgen\thanks{Currently at Citrine Informatics.}  \hspace{1.5cm} \and 
 Ahmet S. Ozcan\footnotemark[1] \and \\
-IBM Research AI
+{\large IBM Research AI}
 }

### 2019-11-27 Transfer_Learning/arxiv_version/submission_folder/appendix.tex
arxiv submission folder self-contained

\section{Datasets: CLEVR-CoGenT and COG}
\label{sec:datasets-desc}
%Here are the details of the COG dataset.
%
The CoGenT dataset~\cite{johnson2017clevr} contains:
\begin{itemize}
	\def\labelitemi{--}
	\item Training set of 70,000 images and 699,960 questions in Condition A,
	\item Validation set of 15,000 images and 149,991 questions in Condition A,
	\item Test set of 15,000 images and 149,980 questions in Condition A (without answers),
	\item Validation set of 15,000 images and 150,000 questions in Condition B,
	\item Test set of 15,000 images and 149,992 questions in Condition B (without answers),
	\item Scene graphs and functional programs for all training/validation images/questions.
\end{itemize}

\noindent The combinations of attributes in CoGenT-A and CoGenT-B are shown in~\cref{tab:cogent_conditions_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{cccc}
		\toprule
		Dataset	&	Cubes	&	Cylinders	&	Spheres	\\
		\midrule
		CoGenT-A	&	Gray / Blue / Brown / Yellow	&	Red / Green / Purple / Cyan	&	Any color	\\
		CoGenT-B	&	Red / Green / Purple / Cyan	&	Gray / Blue / Brown / Yellow	&	Any color 	\\
		\bottomrule
	\end{tabular}
	\caption{Colors \& shapes combinations present in CoGenT-A \& -B datasets.}
	\label{tab:cogent_conditions_supplement}
\end{table}

\noindent The Canonical and Hard variants of the COG dataset~\cite{yang2018dataset} are contrasted in~\cref{tab:cog_variants_supplement}.
\begin{table}[ht]
	\centering
	\begin{tabular}{lcccccc}
		\toprule
		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
		& of   & memory & number of & of & of & of  \\
		& frames & duration & distractors & training set & validation set & test set \\
		\midrule
		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
		\bottomrule	
	\end{tabular}
	\caption{Details of the Canonical and Hard variants of the COG dataset.}
	\label{tab:cog_variants_supplement}
\end{table}
%
%\begin{table}[ht]
%	\centering
%	\begin{tabular}{lcccccc}.
%		\toprule
%		Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
%		& of   & memory & number of & of & of & of 
%%		& frames & duration & distractors & training set & validation set & test set \\
%		\midrule
%		Canonical & 4 & 3 & 1 & 10000320 & 500016 & 500016 \\	
%		Hard  & 8 & 7 & 10 & 10000320 & 500016  & 500016 \\
%		\bottomrule	
%	\end{tabular}
%	\caption{Details of the Canonical and Hard variants of the COG dataset.}
%	\label{tab:cog_variants_supplement}
%\end{table}

\clearpage
\section{Complete COG results}
\label{sec:cog-all-results}

\begin{table*}[htb]
	\centering
	\begin{adjustbox}{width=\columnwidth}
		\begin{tabular}{l r r r r r r r r r r r}
			\toprule[1.25pt]
			Model & \multicolumn{4}{c}{SAMNet} &  &\multicolumn{4}{c}{Baseline Model} & & SoftPaths \\
			\cmidrule(lr){2-5} 
			\cmidrule(lr){7-10} 
			\cmidrule(lr){12-12}
			&&&&& & paper & code & code & paper\\
			\cmidrule(lr){7-10} 
			Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard & & canonical\\ 
			Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - & & -\\ 
			Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard & & canonical \\ 
			\midrule[1pt]	
			Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1     &   &  96.1  \\ 
			\midrule[1pt] 
			AndCompareColor    &    93.5    &    82.7    &    89.2    &    80.6    &    &    81.9    &    57.1    &    60.7    &    51.4    &   &    77.9    \\
			AndCompareShape    &    93.2    &    83.7    &    89.7    &    80.1    &    &    80.0    &    53.1    &    50.3    &    50.7    &   &    77.0    \\
			AndSimpleCompareColor    &    99.2    &    85.3    &    97.6    &    99.4    &    &    99.7    &    53.4    &    77.1    &    78.2    &   &    92.9    \\
			AndSimpleCompareShape    &    99.2    &    85.8    &    97.6    &    99.2    &    &    100.0    &    56.7    &    79.3    &    77.9    &   &    93.4    \\
			CompareColor    &    98.1    &    89.3    &    95.9    &    99.7    &    &    99.2    &    56.1    &    67.9    &    50.1    &   &    95.7    \\
			CompareShape    &    98.0    &    89.7    &    95.9    &    99.2    &    &    99.4    &    66.8    &    65.4    &    50.5    &   &    95.1    \\
			Exist    &    100.0    &    99.7    &    99.8    &    99.8    &    &    100.0    &    63.5    &    96.1    &    99.3    &   &    98.6    \\
			ExistColor    &    100.0    &    99.6    &    99.9    &    99.9    &    &    99.0    &    70.9    &    99.0    &    89.8    &   &    100.0    \\
			ExistColorOf    &    99.9    &    95.5    &    99.7    &    99.8    &    &    99.7    &    51.5    &    76.1    &    73.1    &   &    99.7    \\
			ExistColorSpace    &    94.1    &    88.8    &    91.0    &    90.8    &    &    98.9    &    72.8    &    77.3    &    89.2    &   &    97.8    \\
			ExistLastColorSameShape    &    99.5    &    99.4    &    99.4    &    98.0    &    &    100.0    &    65.0    &    62.5    &    50.4    &   &    100.0    \\
			ExistLastObjectSameObject    &    97.3    &    97.5    &    97.7    &    97.5    &    &    98.0    &    77.5    &    61.7    &    60.2    &   &    100.0    \\
			ExistLastShapeSameColor    &    98.2    &    98.5    &    98.8    &    97.5    &    &    100.0    &    87.8    &    60.4    &    50.3    &   &    100.0    \\
			ExistShape    &    100.0    &    99.5    &    100.0    &    100.0    &    &    100.0    &    77.1    &    98.2    &    92.5    &   &    100.0    \\
			ExistShapeOf    &    99.4    &    95.9    &    99.2    &    99.2    &    &    100.0    &    52.7    &    74.7    &    72.7    &   &    99.8    \\
			ExistShapeSpace    &    93.4    &    87.5    &    91.1    &    90.5    &    &    97.7    &    70.0    &    89.8    &    89.8    &   &    98.0    \\
			ExistSpace    &    95.3    &    89.7    &    93.2    &    93.3    &    &    98.9    &    71.1    &    88.1    &    92.8    &   &    98.6    \\
			GetColor    &    100.0    &    95.8    &    99.9    &    100.0    &    &    100.0    &    71.4    &    83.1    &    97.9    &   &    100.0    \\
			GetColorSpace    &    98.0    &    90.0    &    95.0    &    95.4    &    &    98.2    &    71.8    &    73.0    &    92.3    &   &    98.3    \\
			GetShape    &    100.0    &    97.3    &    99.9    &    99.9    &    &    100.0    &    83.5    &    89.2    &    97.1    &   &    100.0    \\
			GetShapeSpace    &    97.5    &    89.4    &    93.9    &    94.3    &    &    98.1    &    78.7    &    77.3    &    90.3    &   &    98.3    \\
			SimpleCompareShape    &    99.9    &    91.4    &    99.7    &    99.9    &    &    100.0    &    67.7    &    96.7    &    99.3    &   &    94.5    \\
			SimpleCompareColor    &    100.0    &    91.6    &    99.8    &    99.9    &    &    100.0    &    64.2    &    90.4    &    99.3    &   &    94.1    \\
			\bottomrule[1.25pt]
		\end{tabular}
	\end{adjustbox}
	\caption{COG test set accuracies for SAMNet, the baseline model~\cite{yang2018dataset} and the ``SoftPaths'' model~\cite{haurilet2019s}. For the baseline model, `paper' denotes results reproduced from~\cite{yang2018dataset} along with some further clarifications by the authors (private communication)  regarding the performance on individual task types while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}. Similarly, the performance of  the ``SoftPaths'' model on individual task types was obtained from the authors of that paper upon our request.} 
    \label{tab:all-results}
\end{table*}

\clearpage
\section{Complete CLEVR-CoGenT results}
\label{sec:full-cogent-results}

\begin{table*}[htb]
	\centering
	\begin{adjustbox}{width=\textwidth}
	\begin{tabular}{c c c c c c c}
		\toprule
		& \multicolumn{6}{c}{\textbf{Test Accuracy (\%)}} \\  
	    & \multicolumn{6}{c}{on \texttt{valA} -- 150,000 samples} \\ 
		\cmidrule(lr){2-7}
		\textbf{Experiments} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}
		%{Exist only} 
		Exist only & 26.07 & \textbf{74.20}	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
		Count only & 14.89  & 0.0	& \textbf{62.78}	& 0.0 & 0.0 & 0.0 \\ 
		CompareInteger only & 23.44 & 48.15	& 0.0	& \textbf{77.98}	& 54.08 & 0.0 \\ 
		CompareAttribute only & 23.50 & 51.93	& 0.0 & 59.06 & \textbf{61.73} & 0.0 \\ 
		QueryAttribute only & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & \textbf{97.08} \\ 		
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		All tasks & 95.32 & 98.4 	& 86.75	& 96.0	& 98.65	& 98.02 \\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		All tasks but Exist & 90.33 	& \textbf{60.42}	& 86.12	& 96.18	& 98.52 & 98.60 \\ 
		All tasks but Count & 74.59 	& 97.51	& \textbf{0.0}	& 94.37	& 98.42 & 98.47 \\ 
		All tasks but CompareInteger & 91.53 	& 98.22	& 86.09	& \textbf{56.35}	& 98.78 & 98.40 \\ 
		All tasks but CompareAttribute & 81.92 	& 98.32	& 86.36	& 95.86	& \textbf{23.18} & 98.44 \\ 
		All tasks but QueryAttribute & 42.17 	& 76.79	& 54.64	& 79.87 & 64.13 & \textbf{0.0} \\

		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		\textit{Trained on all tasks -- Finetune on $t$} & &  & &  & &\\ 
		Exist & 94.16 & \textbf{98.04} & 82.96 & 95.02 & 98.12 & 97.97 \\ 
		Count & 95.10 & 96.46 & \textbf{88.28} & 94.78 & 97.01 & 98.26 \\
		CompareInteger & 95.31 & 98.39 & 86.56 & \textbf{96.07} & 98.70 & 98.09 \\
		CompareAttribute & 95.31 & 98.40 & 86.78 & 96.00 & \textbf{98.66} & 98.04 \\
		QueryAttribute & 93.49 & 97.45 & 82.09 & 92.23 & 97.85& \textbf{97.76} \\

		\bottomrule
	\end{tabular}
	\end{adjustbox}
	\caption{Complete set of results for SAMNet on CLEVR-CoGenT.}
	\label{tab:CoGenT-results}
\end{table*}

### 2020-02-05 Transfer_Learning/cvpr_rebuttal/egrebuttal.tex
Added cvpr_rebuttal with LateX template.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{7813}
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

\title{Transfer Learning in Visual and Relational Reasoning -- Rebuttal}

\maketitle
\thispagestyle{empty}

\section{Introduction}

{\small
\bibliographystyle{ieee}
\bibliography{}
}

\end{document}

### 2020-02-05 Transfer_Learning/arxiv_version/submission_folder/experiments.tex

--- 2019-11-22 Transfer_Learning/arxiv_version/experiments.tex
@@
 		\centering
-		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
+		\includegraphics[width=\textwidth]{figures/samnet_cog_orig_canonical_no_labels.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_hard.png}
+		\includegraphics[width=\textwidth]{figures/samnet_cog_orig_hard.png}
 	\end{subfigure}%
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../results/CoGenT_results.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/CoGenT_results.pdf}
 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
@@
 
-\begin{figure}[!h]
+\begin{figure}[!t]
 	\centering
-	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
+	\includegraphics[width=0.6\textwidth]{figures/hierarchy}
 	\caption{Hierarchy of Task Groups.}
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{../results/COG_reasoning_transfer_v3}
+	\includegraphics[width=0.85\textwidth]{figures/COG_reasoning_transfer_v3}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../results/samnet_cog_overall_transfer.png}
+	\includegraphics[width=0.8\textwidth]{figures/samnet_cog_overall_transfer.png}
 	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 
-\begin{figure}[!b]
+\begin{figure}[!t]
 	\centering
-	\includegraphics[width=0.6\textwidth]{../results/CoGenT_B_results.pdf}
+	\includegraphics[width=0.6\textwidth]{figures/CoGenT_B_results.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}

### 2020-02-05 Transfer_Learning/cvpr_rebuttal/egrebuttal.tex
Start answering questions of reviewer #2.

@@
 
+\newcommand{\tk}[1]{\textcolor{red}{TK: #1}}
+\newcommand{\ao}[1]{\textcolor{green}{AO: #1}}
+\newcommand{\tsj}[1]{\textcolor{magenta}{TSJ: #1}}
+\newcommand{\vm}[1]{\textcolor{blue}{VM: #1}}
+
 % Include other packages here, before hyperref.
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
 
@@
 \title{Transfer Learning in Visual and Relational Reasoning -- Rebuttal}
-
 \maketitle
@@
 
-\section{Introduction}
+\section{Reviewer \#2 questions}
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{}
-}
+\begin{enumerate}
+  \item What are $vo_tt$ and $mo_t$ and how they differ (lines 400-403)?
+What is the difference between both objects?
+\vm{$vo_t$ is the result of a retrieval operation on the content of the current input frame.
+$mo_t$ is the result of a similar operation on the memory content.
+The difference between both objects is thus their source.}
+
+  \item How the temporal classifier $\tau_t$ is trained and used? Do you use its logits or classes directly (lines 389-397)?
+  \item What are $va_t$ and in general all other symbols. How they are computed. \vm{$va_t$ is the visual attention vector, as defined on lines 412 - 413. $va_t$ is the result of a softmax layer}.
+  \item What is pseudo-attention (line 453)?
+Why such a name?
+\vm{$w_t$ is called a pseudo-attention vector as its norm may not always be 1 (just like a probability vector), but rather vary between 0 (no change) to 1 (complete change)}.
+  \item What are reasoning operations (lines 389-391)? \vm{One iteration of the SAM Cell is considered to be a reasoning operation, as defined on lines 376 - 377}.
+  \item How many 'reasoning operations' (what is k)? \vm{8 reasoning steps, as noted on lines 532-533.}
+  \item Figure 4 shows results on CLEVR-CoGenT.
+CLEVR-CoGenT uses a transfer between objects of type A and objects of type B (e.g.
+different combination of shapes and colors).
+Is this used here?
+Or this is standard CLEVR results?
+What are the results on the regular CLEVR, is it 95\% from the supp.
+material?
+\vm{The results presented in Fig 4 are reported on the condition A of CLEVR-CoGenT.
+No results are reported for CLEVR.}
+  \item Why the paper doesn't compare to other methods on CLEVR?
+\end{enumerate}
+
+% References
+% {\small
+% \bibliographystyle{ieee}
+% \bibliography{}
+% }
 

### 2020-02-05 Transfer_Learning/cvpr_2nd_submission/cvpr_paper_main.tex
cvpr 2nd submission - start
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

--- 2019-11-16 cvpr_submission/paper_main.tex
@@
 
-%%%%%%%%% AUTHORS
-% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
-\author{T.S. Jayram \and  Vincent Marois \and Vincent Albouy \and Tomasz Kornuta  \and Emre Sevgen \and Ahmet Ozcan\\
-IBM Research AI\\
-Almaden Research Center, San Jose, CA 95120, USA\\
-Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
-{\tt\small {jayram,  asozcan}@us.ibm.com}
-{\tt\small {tkornuta, sesevgen}@gmail.com}
-{\tt\small vincent.marois@ibm.com}
+\author{%
+	T.S. Jayram\thanks{IBM Research AI.} \and  
+	Vincent Marois\footnotemark[2] \and 
+	Tomasz Kornuta\thanks{Nvidia Research.} \and 
+	Vincent Albouy\thanks{} \and 
+	Emre Sevgen\thanks{Citrine Informatics.}  \and 
+	Ahmet Ozcan\footnotemark[2]
 }
+%
+%\author{T.S. Jayram \and  Vincent Marois \and Vincent Albouy \and Tomasz Kornuta  \and Emre Sevgen \and Ahmet Ozcan\\
+%IBM Research AI\\
+%Almaden Research Center, San Jose, CA 95120, USA\\
+%Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
+%{\tt\small {jayram,  asozcan}@us.ibm.com}
+%{\tt\small {tkornuta, sesevgen}@gmail.com}
+%{\tt\small vincent.marois@ibm.com}
+%}
 
@@
 \begin{abstract}
-  Transfer learning is becoming the de facto solution for vision and text encoders in the front-end processing of machine learning solutions.
-Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited.
-In this paper, we analyze the efficiency of transfer learning in visual reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.
-Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline.
-We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer.
-Based on extensive experimentation on transfer learning on the two datasets, we show the performance of the new model along each axis.
 \end{abstract}
@@
 
+\input{samnet}
+
 \input{transfer_learning}
-
-\input{samnet}
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{bibliography}
+\bibliography{../bibliography}
 }

### 2020-02-05 Transfer_Learning/cvpr_2nd_submission/experiments.tex
cvpr 2nd submission - start
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

--- 2019-11-20 Transfer_Learning/cvpr_submission/experiments.tex
@@
 \section{Experiments}
-\label{sec:experiments}
-We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
-We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
-There are 23 classification question categories in COG and the 5 original question categories in CLEVR.
-Our experiments were designed to study SAMNet's performance in terms of generalization and transfer learning abilities in different settings,
-and involved incorporating variants of both datasets.  
-For COG, the Canonical (easy) and Hard variant differ mainly on the number of frames in the video, 
-the maximum amount of look-back in frame history containing relevant information for reasoning, 
-and the number of object distractors (see~\cref{tab:cog_variants}).
-For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attribute values (details in~\cref{sec:temporal}).
-%In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
-%involving \emph{finetuning}.
-%Recall that the former involves evaluating the trained model of the source directly on the target while for the latter we do additional lightweight 
-%training on the target labeled data before evaluating its performance. 
+\tk{order: CLEVR + baselines without TL, COG + baseline without TL, Feature Transfer-CLEVR/CoGenT, Temporal Transfer - COG, Reasoning Transfer - CLEVR/CoGenT, Reasoning Transfer-COG}
+
+\newpage
+\subsection{CLEVR/CoGenT dataset: baseline comparison}
+
+\tk{description of CLEVR and CoGenT datasets, task families/groups}
+
 \begin{table}[ht]
 	\centering
-		\begin{tabular}{lccc}
+	%\begin{adjustbox}{width=0.45\textwidth}
+	\begin{tabular}{cccc}
 		\toprule
-			Variant	& Frames & History	& Distractors \\ 
+		Dataset	& Cubes	& Cylinders &	Spheres	\\
 		\midrule
-			Canonical (Easy) & 4 & 3 & 1\\	
-			Hard  & 8 & 7 & 10\\
+		CoGenT A &  Family A  & Family B 	&	Any color  \\
+		CoGenT B	&	Family B  &	Family A	&	Any color \\
 		\bottomrule
 	\end{tabular}
-	\caption{Details of the Canonical and Hard variants of COG.}
-	\label{tab:cog_variants}
-\end{table}\vspace{5pt}
+	%\end{adjustbox}
+	\caption{Restrictions on feature combinations in A \& B conditions of the CoGenT variant of the CLEVR dataset.}
+	\label{tab:cogent_conditions}
+\end{table}
 
-%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
+\tk{comparison of our model with selected baselines - pure CLEVR? (or CoGenT?), no transfer learning}
 
-\subsection{Performance of SAMNet vs baseline model~\cite{yang2018dataset}}
-\label{sec:cog-baseline-compare}
+\tk{figure(s) with accuracy on CLEVR/CoGenT is/are missing!}
 
-We trained SAMNet using 8 reasoning steps and external memory of 8 address locations, each storing an array of 128 floats. 
-%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
-We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
-
-\begin{figure*}[htb]
+\begin{figure*}[htbp]
 	\centering
@@
 
-For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, 
-compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better 
-accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
-For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating
-that our model can adapt to larger number of frames and distractors.
-Despite there being some tasks in the Canonical variant where SAMNet achieved slightly lower accuracies,
-% (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it improves upon the baseline model on all tasks, 
-with improvements varying from 0.5 to more than 30 points, and especially on the more complex tasks in the dataset.
+\newpage
+\subsection{COG dataset: baseline comparison}
 
-\subsection{Reasoning transfer on CLEVR and COG}
-\label{sec:reasoning}
-In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
-of each task relative to others using appropriate groupings of tasks.
-%For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
-%appropriate experiments to study the effectiveness of transfer learning across task families.
+\tk{description of dataset, task families/groups}
+\tk{figure 5 from the orig paper}
 
-\subsubsection{CLEVR}
-\label{sec:reasoning-clevr}
-For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
-We conduct the following experiments:
-\begin{itemize}
-	\compresslist
-	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
-	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
-	This is a transfer learning setting where for the source task family, the task is sampled from all questions,
-	while for the target task family, the samples consist of questions from group $t$ only;
-	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$.
-	This can also be viewed as a transfer learning setting similar to the previous case.
-	%These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
-\end{itemize}
-
-Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
-
-Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object-attribute values (15 labels).
-
-Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
-These improvements suggest that related tasks benefit from joint training.
-\textit{QueryAttribute} only sees an increase of one point.
-One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
-%We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
-We hypothesize that the improvements on e.g.
-\textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e., labels domain).
-
-Finally, the ``all-tasks-but-$t$'' experiments (yellow) demonstrate that while tasks are related, one does not subsume another in terms of learning.
-Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
-We also observe no learning for \textit{Count} and \textit{QueryAttribute}. As these categories have labels that do not overlap with other categories, the model cannot predict these labels.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth]{../results/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
-	\label{fig:CoGenT-results}
-\end{figure}
-
-An additional set of experiments, for which results are available in the supplementary material,
-%Appendix \ref{sec:full-cogent-results}
-fine-tune the model trained on all tasks on each task $t$ respectively.
-%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the fine-tuned task and the drop, if any, on other tasks.
-Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
-Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
-
-\subsubsection{COG}
-\label{sec:reasoning-cog}
-Since the number of task classes (=23) in the COG dataset is large, we designed a 2-level hierarchy of task groups using the
-description of these tasks, as shown in~\cref{fig:task-groups}.
-
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\centering
@@
 
-\begin{figure}[!t]
+\tk{comparison of our model with baseline - pure COG, no transfer learning}
+\tk{figure 3 from the orig paper}
+
+baseline model~\cite{yang2018dataset}
+
+We trained SAMNet using 8 reasoning steps (k=8) and external memory of 8 address locations, each storing an array of 128 floats. 
+%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
+We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
+
+\tk{comparison with results from softpahts?}
+
+\newpage
+\subsection{Feature transfer on CLEVR-CoGenT}
+
+\tk{comparison of our model with baselines - CoGenT}
+\tk{figure 3 from the orig paper}
+
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=\columnwidth]{../results/COG_reasoning_transfer_v3}
-	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
-	\label{fig:COG-reasoning-results}
+	\includegraphics[width=0.8\columnwidth]{../results/CoGenT_B_results.pdf}
+	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
+	\label{fig:CoGenT-B-results}
 \end{figure}
 
-We then conducted the following experiments using the Canonical variant of COG to study 
-whether transfer learning was effective in leveraging information gained by training a task family at a higher level
-of the hierarchy:
- \begin{itemize}
- 	\compresslist
-	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (Single-task training);
-	\item Jointly train on:
-	\begin{itemize}
-		\item 	 \textbf{Group A} and test on each task from the lowest groups (i.e. \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare}) separately;
-		\item \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
-	\end{itemize}
-	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
-	can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately (All-task training).
-\end{itemize}
-
-The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
-
-First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive tasks and therefore do not benefit from training with other task families.
-With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
-Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
-The former saw an accuracy jump from 68.6\% by training on samples from that family alone
-to 97.0\% when training on all samples. To further emphasize this behavior, notice that 
-just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
-In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed
-of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
-Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
-is a slight loss incurred by including everything.
-As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%).
-To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.
-
+\newpage
 \subsection{Temporal transfer in COG}
@@
 
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\centering
@@
 
-\subsection{Feature transfer on CLEVR-CoGenT}
-\label{sec:feature}
-\begin{table}[ht]
+\newpage
+\subsection{Reasoning transfer on CLEVR-CoGenT}
+
+\begin{figure}[htbp]
 	\centering
-	%\begin{adjustbox}{width=0.45\textwidth}
-		\begin{tabular}{cccc}
-			\toprule
-			Dataset	& Cubes	& Cylinders &	Spheres	\\
-			\midrule
-			CoGenT A &  Family A  & Family B 	&	Any color  \\
-			CoGenT B	&	Family B  &	Family A	&	Any color \\
-			\bottomrule
-		\end{tabular}
-	%\end{adjustbox}
-	\caption{Restrictions on feature combinations in A \& B conditions of the CoGenT variant of the CLEVR dataset.}
-	\label{tab:cogent_conditions}
-\end{table}
-
-The final set of experiments we consider is related to feature transfer.
-The CoGenT-A \& -B variants of CLEVR differ by the available combinations of 8 object color-attributes.
-The colors are partitioned into two complementary families: 
-Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}). 
-As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
-We conduct 2 experiments with SAMNet trained on CoGenT-A:
-\begin{itemize}
-\item an immediate test (zero-shot learning) from A to B; and 
-\item fine-tuning for a single epoch on 30k samples from CoGenT-B (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
-\end{itemize}
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{../results/CoGenT_B_results.pdf}
-	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
-	\label{fig:CoGenT-B-results}
+	\includegraphics[width=\columnwidth]{../results/CoGenT_results.pdf}
+	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
+	\label{fig:CoGenT-results}
 \end{figure}
 
-Performance of SAMNet on CoGenT (\cref{fig:CoGenT-B-results}) is clearly worse on CoGenT-B than CoGenT-A.
-Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
-Both are consistent with findings from the literature~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.
+\newpage
+\subsubsection{Reasoning transfer on COG}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth]{../results/COG_reasoning_transfer_v3}
+	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
+	\label{fig:COG-reasoning-results}
+\end{figure}

### 2020-02-05 Transfer_Learning/cvpr_2nd_submission/introduction.tex
cvpr 2nd submission - start
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

--- 2019-11-20 Transfer_Learning/arxiv_version/introduction.tex
@@
 
-%pan2009survey: we categorize transfer learning under three sub-settings: inductive transfer learning, transductive transfer learning and unsupervised transfer learning,
+\tk{Two-three sentences about TL in CV and NLP - short!!}
 
-In Computer Vision, it is now standard practice to pretrain an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as segmentation of cars~\cite{iglovikov2018ternausnet} or Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging}.
-Such performance improvements are appealing, especially in cases where both the domain (natural vs.
-medical images) and the task (image classification vs.
-image segmentation vs VQA) change significantly.
-%This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
-
-Similar developments have emerged in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, has become a standard procedure when working with different NLP domains and tasks.
-Recently, there is a clear, growing trend of utilization of deep contextualized word representations such as ELMo~\cite{peters2018deep} (based on bidirectional LSTMs~\cite{hochreiter1997long}) or BERT~\cite{devlin2018bert} (based on the Transformer~\cite{vaswani2017attention} architecture), where entire deep networks (not just the input layer) are pretrained on very large corporas.
-In analogy to pretrained image encoders, the NLP community has also started to create model repositories, some with dozens of pretrained models ready to be downloaded and used.
-HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
-
-The success of transfer learning raises several research questions, such as the characteristics which make a dataset more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
-One of the most systematic works in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aimed at discovering the dependencies between twenty-six 2D, 2.5D, 3D, and semantic computer vision tasks.
+\tk{The following needs to be rewritten - stronger!}
 

### 2020-02-05 Transfer_Learning/cvpr_2nd_submission/related_work.tex
cvpr 2nd submission - start
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

--- 2019-11-16 cvpr_submission/introduction.tex
@@
-\section{Introduction}
-%dummy
-In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
-At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.\ sampled from a common input space under similar data distribution characteristics.
-However, in many real-world scenarios, this assumption does not hold.
-Moreover, as modern neural models often have millions of trainable parameters, training them requires vast amounts of data, which for some domains (e.g., medical) can be very expensive and/or extremely difficult to collect.
-One of the widely used solutions for the above mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances model performance by transferring \emph{information} from one domain to another.
+\section{Related work}
 
-%pan2009survey: we categorize transfer learning under three sub-settings: inductive transfer learning, transductive transfer learning and unsupervised transfer learning,
+\tk{That section will focus \textbf{only} on transfer learning}
 
@@
 
-In this work we focus on transfer learning in multi-modal tasks combining vision and language~\cite{mogadala2019trends} .
-More precisely, we narrow the scope to transfer learning between visual reasoning tasks that have a ``nice'' logical structure, e.g.,~\cite{johnson2017clevr,yang2018dataset,song2018explore}. 
-While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
-once the modalities have been fused.
-For example, the CoGenT (Constrained Generalization Test) variant of the CLEVR~\cite{johnson2017clevr}  
-contains two datasets with similar questions, but differing on combinations of object-attribute values in images 
-(\cref{sec:feature}).
-In this case, training on the first variant might yield entangled feature representations that may fail reasoning tasks
-on the second one.
-In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
-transfer over to longer ones, e.g., the Canonical and the Hard variants of the 
-COG dataset~\cite{yang2018dataset} (\cref{sec:temporal}).
-To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
-and external memory~\cite{graves2014neural, graves2016hybrid,weston2014memory} 
-which facilitate higher-level abstractions, seem more promising.
+\tk{missing review: TL in visual reasoning, refer to CoGenT and COG}
 
-\smallskip
-
-\noindent Motivated by these considerations:
-%Consequently:
-\begin{enumerate}
-	%\compresslist
-	\item We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
-	\item We propose a taxonomy of transfer learning, inspired from~\cite{pan2009survey}, applied to the domain of visual reasoning.
-Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
-	\item Subsequently, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer.
-This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants.
-Several of these experiments show significant transfer learning capabilities of SAMNet.
-\end{enumerate}
+\tk{after reading that section the reader should end up with a conclusion that: there are no good models for TL in VR and, moreover, the datasets are randomly testing this or that, there is no theoretical framework showing that do they mean/bigger picture is missing}

### 2020-02-05 Transfer_Learning/cvpr_2nd_submission/samnet.tex
cvpr 2nd submission - start
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

--- 2019-11-20 Transfer_Learning/cvpr_submission/samnet.tex
@@
 
-%\begin{figure}[!b]
-%\begin{minipage}{0.43\textwidth}
-%	\centering
-%	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
-%\end{minipage}\hfill
-%\begin{minipage}{0.55\textwidth}
-%	\centering
-%	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
-%\end{minipage}\hfill
-%\caption{General architecture of SAMNet (left) and a single reasoning step in SAMCell (right)}
-%\label{fig:samnet}
-%\end{figure}
-
-%Selective Attention Memory Network (SAMNet) is a end-to-end differentiable model made for video reasoning.
-It is a model based on attention mechanisms but also on a Selective Attention Memory which is able to store selected entities.
-This memory enables SAMNet to reason across multiple frames and perform spatio-temporal reasoning.
-%The core of SAMNet is based a recurrent cell called SAMCell.
-By aligning together a series of k SAMCells per frame, the network can perform k reasoning steps over a frame.
-At every new frame, a new series of k SAMCells is initiated.
-The SAMCell can read and write to memory at every frame using a content addressable mechanism.
-This section describes the model and the different units that composed a SAMCell.
-They are called the Question-driven Controller, the Visual Retrieval Unit, the Memory Retrieval Unit, the Reasoning unit, the Memory update unit, and the Summary Object Udpate Unit.
-%The model is also composed of an Image Encoder and a Question Encoder both responsible to pre-process the visual and textual inputs. The output unit is a classifier.
-%All those modules are described below.
-
-SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
-iterative reasoning as proposed e.g.
-in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and use of an external memory, as in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
-
-A distinctive feature of the SAM Network is its frame-by-frame temporal processing approach, where a single frame can be accessed at once.
-This is a notable difference from~\cite{haurilet2019s}, which uses graph traversal reasoning.
-The recurrent nature of SAMNet does not prevent frame sequences longer than those used for training.
-The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video. 
-Each location of the memory stores a $d$-dimensional vector. %, where $d$ is a global parameter.
-The memory can be accessed through either content-based addressing, via dot-product attention, or location-based addressing.
-Using gating mechanisms, correct objects can be retrieved in order to perform multi-step spatio-temporal reasoning over text and video.
-A notable feature of this design is that the number of addresses $N$ can be changed between training and testing, to fit the data characteristics.
-
-%\begin{figure}[t!]
-%	\centering
-%	\includegraphics[width=\textwidth]{img/architecture/samcell_reasoning}
-%	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
-%	\label{fig:samcell}
-%\end{figure}
-
-SAMNet's core is a recurrent cell called the SAM Cell.
-Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}.
-Information flows between frames through the external memory.
-During the $t$-th reasoning step, for $t=1,2, \dots, T$, SAM Cell maintains the following information as part of its recurrent state:
-(a) $\vec{c}_t \in \Reals^d$, the control state used to drive reasoning over objects in the frame and memory; and
-(b) $\vec{so}_t  \in \Reals^d$, the summary visual object representing the relevant object for step $t$.
-Let $\vec{M}_t \in  \Reals^{N \times d}$ denote the external memory with $N$ slots at the end of step $t$.
-Let $\whead_t \in  \Reals^N$ denote an attention vector over the memory locations;
-in a trained model, $\whead_t$ points to the location of the first empty slot in memory for adding new objects.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{img/architecture/SAMNETmodel}
-	\caption{General architecture of SAMNet.}
-	\label{fig:samnet}
-\end{figure*}
-
-\noindent{\textbf{Question-driven Controller.}}
-This module drives attention over the question to produce $k$ control states, one per reasoning operation.
-The control state $\vec{c}_t$ at step $t$ is then fed to a \emph{temporal classifier}, 
-a two-layer feedforward network with ELU activation in the hidden layer of $d$ units.
-The output $\bm{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that reasoning step.	
-For the COG dataset, we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.
-
-The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
-A similar operation on memory yields the object $\vec{mo}_t$.
-The memory operation is based on attention mechanism, and resembles content-based addressing.
-Therefore, we obtain an attention vector over memory addresses that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
-%Note that the returned objects may be invalid, e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid even if the current frame contains a red square.
-
-\noindent{\textbf{Reasoning Unit.}}
-%\paragraph{Reasoning Unit.}
-This module is the backbone of SAMNet, which determines the gating operations to be performed on the external memory, as well as determining the correct object's location for reasoning.
-To resolve whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
-First, we compute a simple aggregate\footnote{%
-	This is closely related to R\'{e}nyi entropy and Tsallis entropy of order~2.} of the visual attention vector $\vec{va}_t$ of dimension $L$ ($L$ denotes the number of feature vectors for the frame):
-$vs_t = \sum_{i=1}^L [\vec{va}_t(i)]^2$. It can be shown that the more localized the attention
-vector, the higher the aggregate value.
-We perform a similar computation on the read head $\rhead_t$ over memory locations.
-We input these two values, along with the temporal class weights $\bm{\tau}_t$, into a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values (in $[0,1]$) for the current reasoning step:
-(a) $\imatch_t$, which determines whether there is a valid visual object;
-(b) $\mmatch_t$, which determines whether there is a valid memory object. 
-(c) $\doreplace_t$, which determines whether the memory should be updated by replacing a previously stored object with a new one; and
-(d) $\doadd_t$, which determines whether a new object should be added to memory.
-We stress that the network has to learn via training how to correctly implement these behaviors.
-
-\noindent{\textbf{Memory Update Unit.}}
-The unit first determines the memory location where an object could be added:
-\[ \vec{w}_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
-Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
-$\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
-We then update the memory accordingly as:
-\[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t,\]
-where $\vec{vo}_t$ denotes the object returned by the visual retrieval unit. 
-Here $\vec{J}$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product. 
-Note that the memory is unchanged in the case where $\vec{w}_t = 0$, i.e., $\vec{M}_t = \vec{M}_{t-1}$.
-We finally update the write head so that it points to the succeeding address if an object was added to memory or otherwise stay the same.
-Let $\whead'_{t-1}$ denote the circular shift to the right of $\whead_{t-1}$ which corresponds to the soft version of the head update.
-Then:
-\[ \whead_t = \doadd \cdot \whead'_{t-1} + (1-\doadd) \cdot \whead_{t-1} \]
-
-\noindent{\textbf{Summary Update Unit.}}
-%\paragraph{Summary Update Unit.}
-This unit updates the (recurrent) summary object to equal the outcome of the $t$-th reasoning step.
-We first determine whether the relevant object $\vec{ro}_t$ should be obtained from memory or the frame according to:
-\[ \vec{ro}_t = \imatch_t \cdot \vec{vo}_t + \mmatch_t \cdot \vec{mo}_t \]
-Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
-Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
-This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
-
-%For details of the modules not covered here, please see the appendix.
+\tk{Description of the SAMNet}

### 2020-02-05 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
cvpr 2nd submission - start
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

\section{Transfer Learning}

\tk{description of the theoretical framework being the foundation driving our experiments}

\subsection{Feature transfer}

\subsection{Temporal transfer}

\subsection{Reasoning transfer}

\tk{experiments should follow that order AND should be consistent with the used terminology}

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/related_work.tex
motivation - in related work
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 
+\tk{The experimental results clearly indicate that transfer learning is helping, despite that the core assumptions on the compatibility/similarity of domains is broken (transfering between domains having similar distribution).
+We do not understand this fully, thus the need for a more systematic research on that topic emerges.
+The paper adresses that by introducing a theoretical framework/taxonomy enabling to categorise visual reasoning tasks. 
+As a starting point, we picked two visual reasoning datasets and analyse the achieved results through the prism of the proposed taxonomy.
+}
+
 \tk{after reading that section the reader should end up with a conclusion that: there are no good models for TL in VR and, moreover, the datasets are randomly testing this or that, there is no theoretical framework showing that do they mean/bigger picture is missing}

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/cvpr_paper_main.tex

@@
 \begin{abstract}
+Transfer learning has become the de facto standard in computer vision and natural language processing, especially where labeled data is scarce.
+Accuracy can be significantly improved by using pre-trained models and subsequent fine-tuning.
+In visual reasoning tasks, such as image question answering, transfer learning is more complex.
+In addition to transferring the capability to recognize visual features, we also expect to transfer the system’s ability to reason.
+Moreover, for video data, temporal reasoning adds another dimension.
+In this work, we formalize these unique aspects of transfer learning and propose a theoretical framework for visual reasoning, exemplified by the well-established CLEVR and COG datasets.
+Furthermore, we introduce a new, end-to-end differentiable recurrent model (SAMNet), which shows state-of-the-art accuracy and better performance in transfer learning on both datasets.
+The improved performance of SAMNet stems from its capability to decouple the abstract multi-step reasoning from the length of the sequence and its selective attention enabling to store only the question-relevant objects in the external memory.
 \end{abstract}

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/introduction.tex
updated intro

@@
 In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
-At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.\ sampled from a common input space under similar data distribution characteristics.
+Neural networks, being statistical models~\cite{ripley1993statistical,warner1996understanding}, rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.\ sampled from a common input space under similar data distribution characteristics.
 However, in many real-world scenarios, this assumption does not hold.
 Moreover, as modern neural models often have millions of trainable parameters, training them requires vast amounts of data, which for some domains (e.g., medical) can be very expensive and/or extremely difficult to collect.
-One of the widely used solutions for the above mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances model performance by transferring \emph{information} from one domain to another.
+One of the widely used solutions is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances model performance by transferring \emph{information} from one domain to another.
 
-\tk{Two-three sentences about TL in CV and NLP - short!!}
+In this work we focus on transfer learning in multi-modal reasoning tasks combining vision and language~\cite{mogadala2019trends}.
+Recently introduced visual reasoning datasets, such as ~\cite{johnson2017clevr,yang2018dataset,song2018explore}, attempt to probe the generalization capabilities of models under various transfer learning scenarios.
+For example, CLEVR-CoGenT offers two dataset variants with different combinations of visual attributes.
+Whereas, the COG dataset contains two variants with different number of frames and scene complexity.
+Both datasets come with a number of task classes that require similar reasoning abilities (e.g.
+compare or count objects).
+The open question is whether we can build a neural architecture that fosters transfer learning and generalizes from simpler to more complex reasoning tasks.
 
-\tk{The following needs to be rewritten - stronger!}
-
-In this work we focus on transfer learning in multi-modal tasks combining vision and language~\cite{mogadala2019trends}.
-More precisely, we narrow the scope to transfer learning between visual reasoning tasks that have a ``nice'' logical structure, e.g.,~\cite{johnson2017clevr,yang2018dataset,song2018explore}. 
-While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
-once the modalities have been fused.
-For example, the CoGenT (Constrained Generalization Test) variant of the CLEVR dataset~\cite{johnson2017clevr}  
-contains two sets with similar questions, but differing on combinations of object-attribute values in images 
-(\cref{sec:feature}).
-In this case, training on the first variant might yield entangled feature representations that may fail reasoning tasks
-on the second one.
-In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
-transfer over to longer ones, e.g., the Canonical and the Hard variants of the 
-COG dataset~\cite{yang2018dataset} (\cref{sec:temporal}).
-To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
-and external memory~\cite{graves2014neural, graves2016hybrid,weston2014memory} 
-which facilitate higher-level abstractions, seem more promising.
-
-\smallskip
-
-\noindent Motivated by these considerations:
+\noindent The contributions of this paper are the following:
 %Consequently:

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/introduction.tex
finalized intro

@@
 Recently introduced visual reasoning datasets, such as ~\cite{johnson2017clevr,yang2018dataset,song2018explore}, attempt to probe the generalization capabilities of models under various transfer learning scenarios.
-For example, CLEVR-CoGenT offers two dataset variants with different combinations of visual attributes.
-Whereas, the COG dataset contains two variants with different number of frames and scene complexity.
+For example, CLEVR/CoGenT \cite{johnson2017clevr} offers two dataset variants with different combinations of visual attributes.
+Whereas, the COG \cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants with different number of frames and scene complexity.
 Both datasets come with a number of task classes that require similar reasoning abilities (e.g.
@@
 	%\compresslist
-	\item We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
-	\item We propose a taxonomy of transfer learning, inspired from~\cite{pan2009survey}, applied to the domain of visual reasoning.
-Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
-	\item Subsequently, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer.
-This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants.
-Several of these experiments show significant transfer learning capabilities of SAMNet.
+	\item We introduce a new model called SAMNet (Selective Attention Memory Network).
+	The unique features of SAMNet include the dynamic processing of video input frame-by-frame, multi-step reasoning over a given image and remembering the relevant concepts.
+
+	\item We propose a taxonomy of transfer learning to highlight new research directions, identify missing areas and encourage new datasets for transfer learning in visual reasoning.
+We evaluated the CLEVR/CoGenT and COG tasks to show how they map onto the proposed theoretical framework.
+	\item We performed an extensive set of experiments, comparing our model with baselines on the existing tasks, achieving the state-of-the-art results on COG~\cite{yang2018dataset}.
+We also designed two new tasks for reasoning transfer and show that the design of SAMNet  promotes transfer learning capabilities and generalization.
+
 \end{enumerate}

### 2020-02-06 Transfer_Learning/cvpr_rebuttal/egrebuttal.tex
Updated rebuttal

@@
 \thispagestyle{empty}
+
+We would like to thank all three reviewers for their time to read our manuscript and providing us useful feedback.
+Reviewers agree on the strengths of the paper, namely the introduction of a new model which out-performed the baselines, and commonly point out to the same weaknesses, which is about the writing, motivation and organization of the paper.
+The specific recommendations about how to improve the paper were extremely valuable for us.
+Based on these, we overhauled the paper and re-wrote most of it (please see the revised version at the end of this document).
+Below, we also provide answers to the technical questions raised by the reviewers.
+
+Here are the changes we have made:
+\begin{enumerate}
+	\item Re-wrote the \textbf{Abstract} to clarify the problem statement and our contribution.
+	\item Re-wrote most of the \textbf{Introduction}, shortened it and sharpened the focus about the main contributions.
+	\item \textbf{Related Work} section focused more on Transfer learning, and the deficiencies of existing solutions.
+	\item We moved the \textbf{Transfer Learning} section just before the Experiments to tie the theoretical framework to the experiments.
+	\item \textbf{Model}:  We added a \textbf{new figure} to show the details of SAMNet and depicted the variables to connect to the equations.
+We also improved the description of the Model based on Rev.2's recommendations.
+	\item We \textbf{added baselines} for CLEVR/CoGenT in Figure X.
+	\item We rearranged the order of \textbf{Experiments} to better align with the theoretical framework.
+	\item In \textbf{Supplementary} section, we added snapshots from our visualization tool to show the behavior of the model in terms of visual attention, the retrieval of objects from the frame and the use of memory.
+\end{enumerate}
+
+We appreciate the time of the reviewers for a second time and hope that they would change their rating to give this work a chance to reach the broader CVPR audience.
+
+\section{Reviewer \#1 questions}
+
+We agree that further ablation studies would be valuable however, per CVPR guidelines, we are not able to preform new experiments during rebuttal.
+
+We pledge to make our code available prior to the conference, however we do not have necessary the approvals yet before the rebuttal period ends.
+
+We've added baselines to the feature transfer.
+Note that some of the transfer learning experiment settings are novel with no external baselines.
+We hope that future studies will use our methodology and compare against our model.
 

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Reworked experiments figure to make them more readable. Also add baselines results to the feature transfer experiment on CoGenT.

@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{../results/CoGenT_B_results.pdf}
+	\includegraphics[width=\columnwidth]{../results/CoGenT_B_results_with_baselines.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\includegraphics[width=\columnwidth]{../results/samnet_cog_overall_transfer_new.pdf}
+	\caption{Total accuracies of SAMNet (blue) and baseline models (gray / yellow) when testing generalization from Canonical to Hard variants of the dataset.}
 	\label{fig:samnet_cog_overall_transfer}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../results/CoGenT_results.pdf}
+	\includegraphics[width=\columnwidth]{../results/CoGenT_results_new.pdf}
 	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.

### 2020-02-06 Transfer_Learning/cvpr_rebuttal/egrebuttal.tex

@@
 
+\section{Reviewer \#3 questions}
+ - We overhauled the abstract and  introduction to address your criticism about the contributions.
+
+ - We made changes (listed above) to make motivations clear.
+Comment about the memory size (i.e.
+why is it a good thing to change the memory size?): The size of the memory affects the training time significantly.
+Therefore, there is a big advantage if the model learns an abstract capability to use the memory independent of its size.
+This will allow to scale-up models without re-training.
 % References

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex

@@
 
-\tk{description of the theoretical framework being the foundation driving our experiments}
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
+	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
+\end{figure*}
 
-\subsection{Feature transfer}
+We follow the notations in the survey by~\cite{pan2009survey}.
+A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
+For visual reasoning problems considered in this paper, 
+$\cX$ will consist of purely visual inputs, i.e., either images or videos in some cases, or 
+a combination of both visual inputs and questions in other cases. 
+A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
+When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the 
+question\footnote{%
+	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas for typical video answering datasets,
+	only a single answer is needed for the entire video.}. % 
+If the domain elements consist of just the visual inputs, then the task is defined by the question so that each question 
+defines a separate task.
 
-\subsection{Temporal transfer}
+\begin{definition}[\cite{pan2009survey}]
+	\label{defn:transfer}
+	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 
+	learning of the target predictive function $f_T(\cdot)$ in $\cD_T$ using the knowledge  in $\cD_S$ and $\cT_S$, where $\cD_S \ne \cD_T$, or $\cT_S \ne \cT_T$.
+\end{definition}
+In all our applications, $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the marginal distributions $P_S$ and $P_T$ are different.
+Similarly, $\cT_S \ne \cT_T$ means that either $Y_S \ne Y_T$ or that the associated prediction functions are different.
 
-\subsection{Reasoning transfer}
+Although~\cref{defn:transfer} is quite general, it does not adequately capture all artifacts present in visual reasoning.
+For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
+but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
+As mentioned in the introduction, one setting is the case of static images, 
+where this could be due to having different feature combinations in the source and target.
+A different setting is in the context of video reasoning where the number of frames can increase significantly going from source to target.
+These require possibly very different methods: the first involves building disentangled feature representations that can generalize across 
+domains; the second might need external memory to remember relevant objects to generalize across frame lengths.
+Another situation is when the questions themselves can be grouped into families such as count-based queries, 
+comparison of objects, or existence of objects with certain features etc.
+This entails studying transfer learning between families of tasks which requires extending the above definition.
 
-\tk{experiments should follow that order AND should be consistent with the used terminology}
+Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
+Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
+\begin{description}
+	%\compresslist % used to reduce spacing
+	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
+	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
+	over all questions in $\cQ$.
+	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
+	thereof.
+
+	\item[Temporal Transfer:] This setting is similar to attribute adaptation in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
+	and there is a single task.
+	The key difference is that we introduce a notion of complexity $C(v) = (n, m)$ for a visual input $v$,
+	where $n$ equals the maximum number of objects $n$ in an image, and $m$
+	equals  the number of frames in a video. 
+	For any visual input $v_S$ coming from $\cX_S$ with $C(v_S) = (n_S, m_S)$
+	and for any visual input $v_T$ coming from $\cX_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and 
+	$m_T \ge m_S$ with at least one inequality being a strict one. 
+	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.
+
+	\item[Reasoning Transfer:]
+	This setting requires an extension of~\cref{defn:transfer} above to investigate transfer learning when
+	grouping questions into families. Let $\cV$ be the feature space consisting of visual inputs only, shared by
+	all tasks, with a common marginal distribution $P(X)$. For each question $q \in \cQ$, we define the task 
+	$\cT_q = (\cY_q, f_q(\cdot))$ where
+	the output set $\cY_q$ is the set of legitimate answers to $q$ and $f_q(v)$, for a visual input $v$, 
+	is the answer to question $q$ on visual input $v$.
+	Thus, tasks are in a 1-1 correspondence with questions.
+	A \emph{task family} is a probability distribution on tasks which in our case can be obtained by defining the distribution on $\cQ$. 
+	Given a task family, the goal is to learn a prediction function that gives an answer to $f_q(v)$ for $v \in \cV$ chosen according 
+	to the feature space distribution and $q$ chosen according to the task probability distribution.
+	Suppose $\cF_S$ is the source task family and $\cF_T$ is the target task family.
+	Transfer learning aims to help improve the learning of the predictive function for the target task family 
+	using the knowledge in the source task family.
+
+\end{description}
+
+If labeled data is available for $\cX_T$, a training algorithm distinction we make is between \emph{zero-shot learning} and \emph{finetuning}.
+Finetuning entails the use of labeled data in the target domain $\cD_T$, foreseeing performance gain on the target task $\cX_T$, after initial training on $\cX_S$ and additional training on $\cX_T$.
+Zero-shot learning thus refers to immediate test on $\cX_T$ after initial training on $\cX_S$.

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/samnet.tex
updated SAMNet

--- 2019-11-20 Transfer_Learning/cvpr_submission/samnet.tex
@@
 %All those modules are described below.
+\ao{Method: Start high level, how different modules interface each other, and what the motivation is for each such a module.
+Then it should define standard parts such as attention over questions, and introduce all the variables that appear from nowhere.
+I would also like to see a more clear Figure 2 depicting the architecture.
+There is very little correspondence between that figure and the equations used in the paper.}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{img/architecture/SAMNETmodel}
+	\includegraphics[width=\textwidth]{../img/architecture/SAMNETmodel}
 	\caption{General architecture of SAMNet.}

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
no message

@@
 \end{figure*}
+Due to the complex nature of visual reasoning, it turns out that
+transfer learning from a source domain to a target domain can be investigated in 
+multiple ways depend on how the features are related between the two domains, including attributes such as size, color and shape, as well as temporal characteristics reflected in the number of frames and the scene complexity.
+To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.
 
-We follow the notations in the survey by~\cite{pan2009survey}.
 A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
@@
 
-Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
-Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
+We now formally define 3 kinds of transfer learning problems, namely,
+\emph{feature transfer}, \emph{temporal transfer}, 
+and \emph{reasoning transfer}. 
+These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG datasets that are particularly suited for experimental
+investigations of transfer learning.
+In the next section we detail the performance of
+SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset
+for feature transfer, the COG dataset for temporal transfer, and finally
+both datasets for reasoning transfer, with appropriate baseline comparisons.
+
+Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.
 \begin{description}

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
SAMNet

@@
 
-SAMNet's core is a recurrent cell called the SAM Cell.
+The input to SAMNet consists of a question component and a visual component that is either a single frame in case of a static image or a sequence of frames in case of a video
+The question is represented as a sequence of word embeddings (either one-hot or preprocessed by GloVe~\cite{}) corresponding to words in the question.
+Each frame of the visual input is encoded using raw pixels or preprocessed by a pre-trained deep network such as RESNet~\cite{}. 
+The language input of $L$ word embeddings is processed by a Bi-LSTM based question encoder that produces \emph{contextual words} $\vec{cw} \in \Reals^{L \times d}$.
+The final states in either direction of the BI-LSTM are also concatenated and passed through a linear layer to produce a global representation of the question in $\Reals^d$, called the \emph{question embedding}.
+The $j$-th frame of the visual input, where $j$ indexes over the frames in temporal order, is processed by an image encoder---a CNN with appropriately chosen number of layers---to produce a \emph{feature map} $F_j \in \Reals^{H \times W \times d}$.
+
+The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell.
 Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}.

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/introduction.tex
Small corrections and improvements in Intro / SAMNet & Transfer Learning.

@@
 %dummy
-In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
+In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural}, among others.
 Neural networks, being statistical models~\cite{ripley1993statistical,warner1996understanding}, rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.\ sampled from a common input space under similar data distribution characteristics.
@@
 For example, CLEVR/CoGenT \cite{johnson2017clevr} offers two dataset variants with different combinations of visual attributes.
-Whereas, the COG \cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants with different number of frames and scene complexity.
+Whereas, COG \cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants with different number of frames and scene complexity.
 Both datasets come with a number of task classes that require similar reasoning abilities (e.g.
@@
 	The unique features of SAMNet include the dynamic processing of video input frame-by-frame, multi-step reasoning over a given image and remembering the relevant concepts.
-
 	\item We propose a taxonomy of transfer learning to highlight new research directions, identify missing areas and encourage new datasets for transfer learning in visual reasoning.
-We evaluated the CLEVR/CoGenT and COG tasks to show how they map onto the proposed theoretical framework.
-	\item We performed an extensive set of experiments, comparing our model with baselines on the existing tasks, achieving the state-of-the-art results on COG~\cite{yang2018dataset}.
+We evaluate the CLEVR/CoGenT and COG tasks to show how they map onto the proposed theoretical framework.
+	\item We perform an extensive set of experiments, comparing our model with baselines on the existing tasks, achieving the state-of-the-art results on COG~\cite{yang2018dataset}.
 We also designed two new tasks for reasoning transfer and show that the design of SAMNet promotes transfer learning capabilities and generalization.

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
Small corrections and improvements in Intro / SAMNet & Transfer Learning.

@@
 
-The input to SAMNet consists of a question component and a visual component that is either a single frame in case of a static image or a sequence of frames in case of a video
-The question is represented as a sequence of word embeddings (either one-hot or preprocessed by GloVe~\cite{}) corresponding to words in the question.
-Each frame of the visual input is encoded using raw pixels or preprocessed by a pre-trained deep network such as RESNet~\cite{}. 
+\noindent{\textbf{Input Units.}}
+The input to SAMNet consists of a question component and a visual component that is either a single frame in case of a static image or a sequence of frames in case of a video.
+The question is represented as a sequence of word embeddings (either one-hot or preprocessed by GloVe~\cite{pennington2014glove}) corresponding to words in the question.
+Each frame of the visual input is encoded using raw pixels or preprocessed by a pre-trained deep network such as RESNet~\cite{he2016deep}.
 The language input of $L$ word embeddings is processed by a Bi-LSTM based question encoder that produces \emph{contextual words} $\vec{cw} \in \Reals^{L \times d}$.

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
Small corrections and improvements in Intro / SAMNet & Transfer Learning.

@@
 \end{figure*}
-Due to the complex nature of visual reasoning, it turns out that
+Due to the complex nature of visual reasoning, it appears that
 transfer learning from a source domain to a target domain can be investigated in
-multiple ways depend on how the features are related between the two domains, including attributes such as size, color and shape, as well as temporal characteristics reflected in the number of frames and the scene complexity.
+multiple ways, depending on how the features are related between the two domains.
+This includes attributes such as size, color and shape, as well as temporal characteristics reflected in the number of frames and the scene complexity.
 To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/cvpr_paper_main.tex
Reworked experiments figure to make them more readable. Also add baselines results to the feature transfer experiment on CoGenT.
Rewrite Experiments section and add back Summary.

@@
 
-\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{enumerate} or \begin{enumerate}
+\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{itemize} or \begin{enumerate}
 \setlength{\itemsep}{1pt}

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Finish standardizing experiments figures visual appearance.
Rewrite Experiments section and add back Summary.

--- 2019-11-20 Transfer_Learning/cvpr_submission/experiments.tex
@@
 \label{sec:experiments}
+% \tk{order: CLEVR + baselines without TL, COG + baseline without TL, Feature Transfer-CLEVR/CoGenT, Temporal Transfer - COG, Reasoning Transfer - CLEVR/CoGenT, Reasoning Transfer-COG}
+
 We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}.
-We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
-There are 23 classification question categories in COG and the 5 original question categories in CLEVR.
-Our experiments were designed to study SAMNet's performance in terms of generalization and transfer learning abilities in different settings,
-and involved incorporating variants of both datasets.  
-For COG, the Canonical (easy) and Hard variant differ mainly on the number of frames in the video, 
-the maximum amount of look-back in frame history containing relevant information for reasoning, 
-and the number of object distractors (see~\cref{tab:cog_variants}).
-For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attribute values (details in~\cref{sec:temporal}).
-%In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
-%involving \emph{finetuning}.
-%Recall that the former involves evaluating the trained model of the source directly on the target while for the latter we do additional lightweight 
-%training on the target labeled data before evaluating its performance. 
+We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.\\
+Drawing on the taxonomy presented in \cref{sec:transfer_learning}, we organize the experiments in the following order.
+We first briefly describe both datasets and how their characteristics help evaluate transfer learning abilities, before comparing SAMNet to existing baselines.
+Next, we interest ourselves in the feature transfer setting using CoGenT, followed by the temporal transfer on COG.
+Then, we assess SAMNet's capacity to transfer reasoning, by presenting a final set of experiments using the questions categories in both datasets.
+
+\subsection{Performance of SAMNet on CLEVR}
+\label{sec:clevr-baseline-compare}
+
+% \tk{description of CLEVR and CoGenT datasets, task families/groups}
+% \tk{comparison of our model with selected baselines - pure CLEVR? (or CoGenT?), no transfer learning}
+% \tk{figure(s) with accuracy on CLEVR/CoGenT is/are missing!}
+
+\begin{table}[ht]
+	\centering
+	%\begin{adjustbox}{width=0.45\textwidth}
+		\begin{tabular}{cccc}
+			\toprule
+			Dataset	& Cubes	& Cylinders &	Spheres	\\
+			\midrule
+			CoGenT A &  Family A  & Family B 	&	Any color  \\
+			CoGenT B	&	Family B  &	Family A	&	Any color \\
+			\bottomrule
+		\end{tabular}
+	%\end{adjustbox}
+	\caption{Restrictions on feature combinations in A \& B conditions of the CoGenT variant of the CLEVR dataset.}%\vspace{2pts}
+	\label{tab:cogent_conditions}
+\end{table}
+
+For the CLEVR dataset, we consider the 5 question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+We also consider the CoGenT (Constrained Generalization Test) variant of CLEVR which contains 2 conditions, differing by the available combinations of 8 object color-attributes.
+The colors are partitioned into two complementary families:
+Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}.
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}).
+As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
+
+We compare SAMNet's performance to several models: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE), presented in \cite{johnson2017inferring}.
+For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
+Results are shown in \cref{fig:clevr-baseline-compare}. \vm{Not sure what else to say here..}
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
+	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
+	\label{fig:clevr-baseline-compare}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
+	\caption{Hierarchy of Task Groups in the COG dataset.}
+	\label{fig:task-groups}
+\end{figure}
+
+\begin{figure*}[htbp]
+	\centering
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_canonical_no_labels.pdf}
+	\end{subfigure}%
+	\newline
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_hard.pdf}
+	\end{subfigure}%
+	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the baseline model~\cite{yang2018dataset} (dotted gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+	\label{fig:samnet_cog_detailed}
+\end{figure*}
+
+\subsection{Performance of SAMNet on COG}
+\label{sec:cog-baseline-compare}
+
+% \tk{description of dataset, task families/groups}
+% \tk{figure 5 from the orig paper}
+% \tk{comparison of our model with baseline - pure COG, no transfer learning}
+% \tk{figure 3 from the orig paper}
+% \tk{baseline model~\cite{yang2018dataset}}
+\tk{comparison with results from softpahts?}
+
 \begin{table}[ht]
@@
 
-%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
-
-\subsection{Performance of SAMNet vs baseline model~\cite{yang2018dataset}}
-\label{sec:cog-baseline-compare}
-
-We trained SAMNet using 8 reasoning steps and external memory of 8 address locations, each storing an array of 128 floats. 
-%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
-We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
-
-\begin{figure*}[htb]
-	\centering
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
-	\end{subfigure}%
-	\newline
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_hard.png}
-	\end{subfigure}%
-	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
-		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-	\label{fig:samnet_cog_detailed}
-\end{figure*}
-
-For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, 
-compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better 
-accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
-For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating
-that our model can adapt to larger number of frames and distractors.
-Despite there being some tasks in the Canonical variant where SAMNet achieved slightly lower accuracies,
-% (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it improves upon the baseline model on all tasks, 
-with improvements varying from 0.5 to more than 30 points, and especially on the more complex tasks in the dataset.
-
-\subsection{Reasoning transfer on CLEVR and COG}
-\label{sec:reasoning}
-In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
-of each task relative to others using appropriate groupings of tasks.
-%For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
-%appropriate experiments to study the effectiveness of transfer learning across task families.
-
-\subsubsection{CLEVR}
-\label{sec:reasoning-clevr}
-For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
-We conduct the following experiments:
-\begin{itemize}
-	\compresslist
-	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
-	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
-	This is a transfer learning setting where for the source task family, the task is sampled from all questions,
-	while for the target task family, the samples consist of questions from group $t$ only;
-	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$.
-	This can also be viewed as a transfer learning setting similar to the previous case.
-	%These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
-\end{itemize}
-
-Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
-
-Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object-attribute values (15 labels).
-
-Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
-These improvements suggest that related tasks benefit from joint training.
-\textit{QueryAttribute} only sees an increase of one point.
-One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
-%We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
-We hypothesize that the improvements on e.g.
-\textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e., labels domain).
-
-Finally, the ``all-tasks-but-$t$'' experiments (yellow) demonstrate that while tasks are related, one does not subsume another in terms of learning.
-Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
-We also observe no learning for \textit{Count} and \textit{QueryAttribute}. As these categories have labels that do not overlap with other categories, the model cannot predict these labels.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth]{../results/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
-	\label{fig:CoGenT-results}
-\end{figure}
-
-An additional set of experiments, for which results are available in the supplementary material,
-%Appendix \ref{sec:full-cogent-results}
-fine-tune the model trained on all tasks on each task $t$ respectively.
-%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the fine-tuned task and the drop, if any, on other tasks.
-Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
-Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
-
-\subsubsection{COG}
-\label{sec:reasoning-cog}
-Since the number of task classes (=23) in the COG dataset is large, we designed a 2-level hierarchy of task groups using the
+There are 23 classification question categories in COG.
+The Canonical (easy) and Hard variant differ mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors (see~\cref{tab:cog_variants}).
+Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
 description of these tasks, as shown in~\cref{fig:task-groups}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
-	\caption{Hierarchy of Task Groups.}
-	\label{fig:task-groups}
-\end{figure}
-
-\bigskip
 
@@
 
-\begin{figure}[!t]
+We trained SAMNet using $k = 8$ reasoning steps and external memory of 8 address locations, each storing an array of 128 floats.
+We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.
+
+For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
+As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
+For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
+Despite there being some tasks in the Canonical variant where SAMNet achieved slightly lower accuracies, when comparing performances on the Hard variant, it improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, and especially on the more complex tasks in the dataset.
+
+\subsection{Feature transfer in CLEVR-CoGenT}
+\label{sec:feature}
+
+% \tk{comparison of our model with baselines - CoGenT}
+% \tk{figure 3 from the orig paper}
+
+We conduct 2 experiments with SAMNet trained on CoGenT-A to evaluate its feature transfer capacity:
+\begin{itemize}
+\compresslist
+\item an immediate test (zero-shot learning) from A to B; and
+\item fine-tuning for a single epoch on 30k samples from CoGenT-B (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+\end{itemize}
+
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=\columnwidth]{../results/COG_reasoning_transfer_v3}
+	\includegraphics[width=\columnwidth]{../results/CoGenT_B_results_with_baselines.pdf}
+	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue / yellow (striped)) and fine-tuning on CoGenT-B (gray (dotted)).}
+	\label{fig:CoGenT-B-results}
+\end{figure}
+
+We compare SAMNet to TbD~\cite{mascharka2018transparency}, FiLM~\cite{perez2018film} and PG + EE~\cite{johnson2017inferring}.
+\cref{fig:CoGenT-B-results} shows the results.
+Performance of SAMNet on CoGenT is clearly worse on CoGenT-B than CoGenT-A, but shows better zero-shot generalization than TbD.
+Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
+After finetuning on CoGenT-B, SAMNet limits catastrophic forgetting on CoGenT-A, contrarily to FilM and PG + EE.
+
+\subsection{Temporal transfer in COG}
+\label{sec:temporal}
+
+The goal here is to test the transfer learning ability concerning the frame sequence length, frame history required for reasoning, and the number of object distractors.
+For that purpose, we compare both models when trained on the Canonical variant but tested on the Hard variant (\cref{fig:samnet_cog_overall_transfer}).
+The gray (dotted) color indicates original accuracies of the baseline model from paper,
+whereas yellow (striped) indicates accuracies of the baseline model obtained by running the original code provided by the authors~\cite{yang2018implement}.
+
+The first column displays the scores of the traditional ML setup when training and testing on the Canonical variant.
+The observed close scores in gray (dotted) and yellow (striped) underscore the baseline model reproducibility.
+For both cases of zero-shot learning (second column--91.6\% vs. 65.9\%) and fine-tuning using a single epoch (third column--96.7\% vs. 78.1\%), SAMNET outperforms the baseline model significantly.
+Interestingly, this fine-tuning yields a mild boost of +0.6\% on the earlier reported accuracy in~\cref{sec:cog-baseline-compare} (fourth column).
+These results suggest that it suffices to train SAMNet on simpler videos to enable learning of good memory usage and attention on relevant entities in order to achieve comparable, if not better, performance on longer video frames with more complex scenes.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth]{../results/samnet_cog_overall_transfer_new.pdf}
+	\caption{Total accuracies of SAMNet (blue) and baseline models (gray (dotted) / yellow (striped)) when testing generalization from Canonical to Hard variants of the dataset.}
+	\label{fig:samnet_cog_overall_transfer}
+\end{figure}
+
+\subsection{Reasoning transfer in CoGenT}
+\label{sec:reasoning-clevr}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth]{../results/CoGenT_results_new.pdf}
+	\caption{CoGenT-A accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.}
+	\label{fig:CoGenT-results}
+\end{figure}
+
+Using the question categories defined by the author, we conduct the following experiments:
+\begin{itemize}
+	\compresslist
+	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
+	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
+	This is a transfer learning setting where for the source task family, the task is sampled from all questions, while for the target task family, the samples consist of questions from group $t$ only;
+	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$. This can also be viewed as a transfer learning setting similar to the previous case.
+\end{itemize}
+
+Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.
+
+Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
+Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object-attribute values (15 labels).
+
+Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
+These improvements suggest that related tasks benefit from joint training.
+\textit{QueryAttribute} only sees an increase of one point.
+One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
+
+Finally, the ``all-tasks-but-$t$'' experiments (yellow) demonstrate that while tasks are related, one does not subsume another in terms of learning.
+Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
+We also observe no learning for \textit{Count} and \textit{QueryAttribute}. As these categories have labels that do not overlap with other categories, the model cannot predict these labels.
+
+An additional set of experiments, for which results are available in the supplementary material, fine-tune the model trained on all tasks on each task $t$ respectively.
+Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
+Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
+
+\subsection{Reasoning transfer in COG}
+\label{sec:reasoning-cog}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth]{../results/COG_reasoning_transfer_new.pdf}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
 	\label{fig:COG-reasoning-results}
-\end{figure}
+\end{figure}\vspace{2pt}
 
-We then conducted the following experiments using the Canonical variant of COG to study 
-whether transfer learning was effective in leveraging information gained by training a task family at a higher level
+Reusing the task hierarchy in \cref{fig:task-groups}, we conduct the following experiments using the Canonical variant of COG to study whether transfer learning was effective in leveraging information gained by training a task family at a higher level
 of the hierarchy:
@@
 	\end{itemize}
-	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
-	can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately (All-task training).
+	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately (All-task training).
 \end{itemize}
@@
 Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
-The former saw an accuracy jump from 68.6\% by training on samples from that family alone
+The former saw an accuracy jump from 58.6\% by training on samples from that family alone
 to 97.0\% when training on all samples. To further emphasize this behavior, notice that
@@
 To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.
-
-\subsection{Temporal transfer in COG}
-\label{sec:temporal}
-
-The goal here is to test the transfer learning ability concerning the frame sequence length, frame history required
-for reasoning, and the number of object distractors.
-For that purpose, we compare both models when trained on the Canonical variant but tested on the 
-Hard variant (\cref{fig:samnet_cog_overall_transfer}).
-The light gray color indicates original accuracies of the baseline model from paper, 
-whereas dark gray indicates accuracies of the baseline model
-obtained by running the original code provided by the authors~\cite{yang2018implement}.
-
-The first column displays the scores of the traditional ML setup when training and testing on the Canonical variant. 
-The observed close scores in light and dark gray underscore the baseline model reproducibility.
-For both cases of zero-shot learning (second column--91.6\% vs 65.9\%) and fine-tuning using a single epoch 
-(third column--96.7\% vs. 78.1\%), SAMNET outperforms the baseline model significantly.
-Interestingly, this fine-tuning yields a mild boost of +0.6\% on the earlier reported accuracy 
-in~\cref{sec:cog-baseline-compare} (fourth column).
-These results suggest that it suffices to train SAMNet on simpler videos 
-to enable learning of good memory usage and attention on relevant entities  
-in order to achieve comparable, if not better, 
-performance on longer video frames with more complex scenes.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{../results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
-	\label{fig:samnet_cog_overall_transfer}
-\end{figure}
-
-\subsection{Feature transfer on CLEVR-CoGenT}
-\label{sec:feature}
-\begin{table}[ht]
-	\centering
-	%\begin{adjustbox}{width=0.45\textwidth}
-		\begin{tabular}{cccc}
-			\toprule
-			Dataset	& Cubes	& Cylinders &	Spheres	\\
-			\midrule
-			CoGenT A &  Family A  & Family B 	&	Any color  \\
-			CoGenT B	&	Family B  &	Family A	&	Any color \\
-			\bottomrule
-		\end{tabular}
-	%\end{adjustbox}
-	\caption{Restrictions on feature combinations in A \& B conditions of the CoGenT variant of the CLEVR dataset.}
-	\label{tab:cogent_conditions}
-\end{table}
-
-The final set of experiments we consider is related to feature transfer.
-The CoGenT-A \& -B variants of CLEVR differ by the available combinations of 8 object color-attributes.
-The colors are partitioned into two complementary families: 
-Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}). 
-As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
-We conduct 2 experiments with SAMNet trained on CoGenT-A:
-\begin{itemize}
-\item an immediate test (zero-shot learning) from A to B; and 
-\item fine-tuning for a single epoch on 30k samples from CoGenT-B (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
-\end{itemize}
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{../results/CoGenT_B_results.pdf}
-	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
-	\label{fig:CoGenT-B-results}
-\end{figure}
-
-Performance of SAMNet on CoGenT (\cref{fig:CoGenT-B-results}) is clearly worse on CoGenT-B than CoGenT-A.
-Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
-Both are consistent with findings from the literature~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
Small edits in Model section + move Fig 1 on page 4.

@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/SAMNETmodel}
+	\caption{General architecture of SAMNet.}
+	\label{fig:samnet}
+\end{figure*}
+
 A distinctive feature of the SAM Network is its frame-by-frame temporal processing approach, where a single frame can be accessed at once.
@@
 
-The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell.
+\noindent{\textbf{The SAM Cell.}} The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell.
 Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/SAMNETmodel}
-	\caption{General architecture of SAMNet.}
-	\label{fig:samnet}
-\end{figure*}
-
 \noindent{\textbf{Question-driven Controller.}}
@@
 
-The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
+\noindent{\textbf{Retrieval Units.}} The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
 A similar operation on memory yields the object $\vec{mo}_t$.
@@
 Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
-Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
+
+\noindent{\textbf{Output Unit.}} Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
 This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
no message

--- 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
@@
 %All those modules are described below.
-\ao{Method: Start high level, how different modules interface each other, and what the motivation is for each such a module.
+%\ao{Method: Start high level, how different modules interface each other, and what the motivation is for each such a module.
 Then it should define standard parts such as attention over questions, and introduce all the variables that appear from nowhere.
@@
 
-SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
+SAM Network (SAMNet) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
 iterative reasoning as proposed e.g.
@@
 The language input of $L$ word embeddings is processed by a Bi-LSTM based question encoder that produces \emph{contextual words} $\vec{cw} \in \Reals^{L \times d}$.
-The final states in either direction of the BI-LSTM are also concatenated and passed through a linear layer to produce a global representation of the question in $\Reals^d$, called the \emph{question embedding}.
-The $j$-th frame of the visual input, where $j$ indexes over the frames in temporal order, is processed by an image encoder---a CNN with appropriately chosen number of layers---to produce a \emph{feature map} $F_j \in \Reals^{H \times W \times d}$.
+The final states in either direction of the BI-LSTM are also concatenated and passed through a linear layer to produce a global representation of the question 
+$\vec{q} \in \Reals^d$, called the \emph{question embedding}.
+The $j$-th frame of the visual input, where $j$ indexes over the frames in temporal order, is processed by an image encoder---a CNN with appropriately chosen number of layers---to produce a \emph{feature map}
+$\vec{F}_j \in \Reals^{H \times W \times d}$.
 

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Small edits in Experiments & Transfer Learning sections.

@@
 
-For the CLEVR dataset, we consider the 5 question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+For CLEVR, we consider the 5 question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
 We also consider the CoGenT (Constrained Generalization Test) variant of CLEVR which contains 2 conditions, differing by the available combinations of 8 object color-attributes.
@@
 For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
-Results are shown in \cref{fig:clevr-baseline-compare}. \vm{Not sure what else to say here..}
+SAMNet reaches 96.2\% accuracy on CLEVR, compared to 96.9\%, 97.7\% and 98.7\% for PG + EE, FiLM and TbD respectively.
 
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
-	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
-	\label{fig:clevr-baseline-compare}
-\end{figure}
+% \begin{figure}[!t]
+% 	\centering
+% 	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
+% 	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
+% 	\label{fig:clevr-baseline-compare}
+% \end{figure}
 

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
Rewrite Experiments section and add back Summary.
Small edits in Experiments & Transfer Learning sections.

@@
 \section{Transfer Learning}
-
+\label{sec:transfer_learning}
 \begin{figure*}
@@
 investigations of transfer learning.
-In the next section we detail the performance of
+In \cref{sec:experiments}, we detail the performance of
 SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
SAMNet edits

--- 2020-02-07 Transfer_Learning/cvpr_2nd_submission/samnet.tex
@@
 
-\noindent{\textbf{Input Units.}}
+\smallskip
+
+\noindent\textbf{Input Units.}
 The input to SAMNet consists of a question component and a visual component that is either a single frame in case of a static image or a sequence of frames in case of a video.
@@
 $\vec{q} \in \Reals^d$, called the \emph{question embedding}.
-The $j$-th frame of the visual input, where $j$ indexes over the frames in temporal order, is processed by an image encoder---a CNN with appropriately chosen number of layers---to produce a \emph{feature map}
-$\vec{F}_j \in \Reals^{H \times W \times d}$.
+The $k$-th frame of the visual input, where $k$ indexes over the frames in temporal order, is processed by an image encoder---a CNN with appropriately chosen number of layers---to produce a \emph{feature map}
+$\vec{F}_k \in \Reals^{H \times W \times d}$.
 
-The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell.
+\smallskip
+
+\noindent\textbf{The SAM Cell.} The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell.
 Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/SAMNETmodel}
-	\caption{General architecture of SAMNet.}
-	\label{fig:samnet}
-\end{figure*}
+\smallskip
 
-\noindent{\textbf{Question-driven Controller.}}
+\noindent\textbf{Question-driven Controller.}
 This module drives attention over the question to produce $k$ control states, one per reasoning operation.
@@
 
-The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
+\smallskip
+
+\noindent\textbf{Retrieval Units.} The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
 A similar operation on memory yields the object $\vec{mo}_t$.
@@
 
-\noindent{\textbf{Reasoning Unit.}}
+\smallskip
+
+\noindent\textbf{Reasoning Unit.}
 %\paragraph{Reasoning Unit.}
@@
 
-\noindent{\textbf{Memory Update Unit.}}
+\smallskip
+
+\noindent\textbf{Memory Update Unit.}
 The unit first determines the memory location where an object could be added:
@@
 $\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
-We then update the memory accordingly as:
+We then update the memory accordingly:
 \[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t,\]
@@
 
-\noindent{\textbf{Summary Update Unit.}}
+\noindent\textbf{Summary Update Unit.}
 %\paragraph{Summary Update Unit.}
@@
 Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
-Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
+
+\smallskip
+
+\noindent\textbf{Output Unit.} Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
 This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Reworked Figure 1, 6.

@@
 
-% \begin{figure}[!t]
-% 	\centering
-% 	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
-% 	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
-% 	\label{fig:clevr-baseline-compare}
-% \end{figure}
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
+	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
+	\label{fig:clevr-baseline-compare}
+\end{figure}
 
@@
 	\includegraphics[width=\columnwidth]{../results/CoGenT_B_results_with_baselines.pdf}
-	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue / yellow (striped)) and fine-tuning on CoGenT-B (gray (dotted)).}
+	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A and fine-tuning on CoGenT-B.}
 	\label{fig:CoGenT-B-results}

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/summary.tex
Rewrite Experiments section and add back Summary.
updated summary

--- 2019-11-16 cvpr_submission/summary.tex
@@
 
-In this paper, we quantified the impact of Transfer Learning on Visual Reasoning. 
-We have proposed a new taxonomy of transfer learning for Visual Reasoning, articulated around three axes: feature, temporal and reasoning transfer. 
-We have also introduced a novel Memory-Augmented Neural Network model called SAMNet.
-SAMNet, designed to learn to reason over sequences of frames, shows significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieves comparable performance on the CLEVR dataset for Image Reasoning.
+Even though transfer learning in computer vision is a common practice, a holistic view of its impact on visual reasoning was missing.
+To capture and quantify the influence of transfer learning on visual reasoning, we proposed a new taxonomy, articulated around three aspects: feature, temporal and reasoning transfer.
+That enabled us to reuse the existing datasets for image and video QA, namely CLEVR and COG, and isolate splits capturing the reasoning transfer.
+We note that some of the proposed splits form tasks (e.g. Train on all but \textit{t}) that are complementary to well established ones in the literature, e.g. in Taskonomy~\cite{zamir2018taskonomy}.
 
-Taking that as a starting point and leveraging the proposed taxonomy, we have conducted an extensive set of experiments, focusing on the impact of transfer learning in areas that might be considered as higher-level reasoning.
-SAMNet demonstrates very good generalization capabilities along certain axes and, through the cautious use of fine-tuning, can see its performance advanced even further.
-
-Finally, we note that some of the proposed tasks (e.g. Train on all but \textit{t}) are complementary to ones already well established in the literature, e.g. in Taskonomy~\cite{zamir2018taskonomy}.
-We hope these contributions will bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.
+Our experiments on transfer learning showed the shortcomings of existing approaches, especially for video reasoning.
+Hence, we designed a novel Memory-Augmented Neural Network model called SAMNet, with mechanisms to address these deficiencies.
+SAMNet showed significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieved comparable performance on the CLEVR dataset for Image Reasoning.
+It also demonstrated excellent generalization capabilities for temporal and reasoning transfer. Moreover,  through the cautious use of fine-tuning, SAMNet's performance advanced even further.
+We hope that the proposed taxonomy, newly established reasoning transfer tasks, along with the provided baselines will bolster new research on both models and datasets for transfer learning on visual reasoning.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
updated experiments

@@
 
-\begin{figure}[!t]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=0.8\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
+ 	\includegraphics[width=\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
  	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
@@
 	\includegraphics[width=\columnwidth]{../results/CoGenT_B_results_with_baselines.pdf}
-	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A and fine-tuning on CoGenT-B.}
+	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue / yellow (striped)) and fine-tuning on CoGenT-B (gray (dotted)).}
 	\label{fig:CoGenT-B-results}

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
TL minor edit

@@
 transfer learning from a source domain to a target domain can be investigated in
-multiple ways, depending on how the features are related between the two domains.
-This includes attributes such as size, color and shape, as well as temporal characteristics reflected in the number of frames and the scene complexity.
+multiple ways, depending on how the two domains are related.
+This includes visual attributes such as size, color and shape, temporal characteristics reflected in the number of frames and scene complexity, and finally the reasoning difficulty.
 To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Reorganization and polishing of experimental plots
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

--- 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{../results/CLEVR_baselines_comparison.pdf}
+	\includegraphics[width=0.8\columnwidth]{../img/plots/clevr_baselines.pdf}
 	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_canonical_no_labels.pdf}
+		\includegraphics[width=0.9\textwidth]{../img/plots/cog_canonical_baseline_no_labels.pdf}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_hard.pdf}
+		\includegraphics[width=0.9\textwidth]{../img/plots/cog_hard_baseline_labels.pdf}
 	\end{subfigure}%
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../results/CoGenT_B_results_with_baselines.pdf}
+	\includegraphics[width=\columnwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
 	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A and fine-tuning on CoGenT-B.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../results/samnet_cog_overall_transfer_new.pdf}
+	\includegraphics[width=\columnwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
 	\caption{Total accuracies of SAMNet (blue) and baseline models (gray (dotted) / yellow (striped)) when testing generalization from Canonical to Hard variants of the dataset.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../results/CoGenT_results_new.pdf}
+	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
 	\caption{CoGenT-A accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../results/COG_reasoning_transfer_new.pdf}
+	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Experiments: basics, feature transfer
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 
-We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}.
-We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.\\
-Drawing on the taxonomy presented in \cref{sec:transfer_learning}, we organize the experiments in the following order.
-We first briefly describe both datasets and how their characteristics help evaluate transfer learning abilities, before comparing SAMNet to existing baselines.
-Next, we interest ourselves in the feature transfer setting using CoGenT, followed by the temporal transfer on COG.
-Then, we assess SAMNet's capacity to transfer reasoning, by presenting a final set of experiments using the questions categories in both datasets.
+We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}.
+We evaluated the model on 
+the CLEVR dataset~\cite{johnson2017clevr}, a diagnostic dataset for Image Question Answering and on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning.
+We briefly describe both datasets in the following two subsections.
+We also present comparison of SAMNet with the existing baselines as a sanity check. 
+In all experiments we used SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
 
-\subsection{Performance of SAMNet on CLEVR}
-\label{sec:clevr-baseline-compare}
+The rest of experiments is following the proposed taxonomy.
+First, we investigate the feature transfer using the CLEVR-CoGenT variants, followed by the temporal transfer on COG.
+Finally, we assess SAMNet's transfer reasoning capabilities on both datasets by regrouping and reorganizing classes of questions into new training and test splits.
 
-% \tk{description of CLEVR and CoGenT datasets, task families/groups}
-% \tk{comparison of our model with selected baselines - pure CLEVR? (or CoGenT?), no transfer learning}
-% \tk{figure(s) with accuracy on CLEVR/CoGenT is/are missing!}
-
-\begin{table}[ht]
+\begin{table}[b!]
 	\centering
@@
 		\toprule
-			Dataset	& Cubes	& Cylinders &	Spheres	\\
+		Variant	& Cubes	& Cylinders &	Spheres	\\
 		\midrule
-			CoGenT A &  Family A  & Family B 	&	Any color  \\
-			CoGenT B	&	Family B  &	Family A	&	Any color \\
+		CLEVR &  Any Color  & Any Color 	&	Any color  \\
+		CoGenT-A &  Family A  & Family B 	&	Any color  \\
+		CoGenT-B	&	Family B  &	Family A	&	Any color \\
 		\bottomrule
@@
 	%\end{adjustbox}
-	\caption{Restrictions on feature combinations in A \& B conditions of the CoGenT variant of the CLEVR dataset.}%\vspace{2pts}
+	\caption{Allowed feature combinations in the CoGenT-A and CoGenT-B variants of the CLEVR dataset.}%\vspace{2pts}
 	\label{tab:cogent_conditions}
@@
 
-For CLEVR, we consider the 5 question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-We also consider the CoGenT (Constrained Generalization Test) variant of CLEVR which contains 2 conditions, differing by the available combinations of 8 object color-attributes.
-The colors are partitioned into two complementary families:
-Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}.
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}).
-As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
-
-We compare SAMNet's performance to several models: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE), presented in \cite{johnson2017inferring}.
-For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
-SAMNet reaches 96.2\% accuracy on CLEVR, compared to 96.9\%, 97.7\% and 98.7\% for PG + EE, FiLM and TbD respectively.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{../img/plots/clevr_baselines.pdf}
-	\caption{Comparison of SAMNet to baseline models~\cite{mascharka2018transparency, perez2018film, johnson2017inferring} on CLEVR.}
-	\label{fig:clevr-baseline-compare}
-\end{figure}
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
-	\caption{Hierarchy of Task Groups in the COG dataset.}
-	\label{fig:task-groups}
-\end{figure}
-
-\begin{figure*}[htbp]
+\begin{figure*}[t!]
 	\centering
@@
 
-\subsection{Performance of SAMNet on COG}
+\subsection{Basic performance of SAMNet on CLEVR}
+\label{sec:clevr-baseline-compare}
+CLEVR images contain objects characterised by a set of simple atributes (shape, color, size and material), whereas questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+Along with CLEVR the authors also introduced two CLEVR-CoGenT (Constrained Generalization Test) variants, with varying combinations of color-shape attributes.
+The colors are partitioned into two complementary families:
+Gray, Blue, Brown and Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both varianrs (See~\cref{tab:cogent_conditions}).
+As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../img/plots/clevr_baselines.pdf}
+	\caption{Comparison of SAMNet to baselines on CLEVR.}
+	\label{fig:clevr_baselines}
+\end{figure}
+
+We compare SAMNet's performance to selected SOTA models, namely Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
+For performance reasons, we deactivated the external memory and temporal-related modules in SAMNet as they are unnecessary while reasoning about static images.
+As presented in \cref{fig:clevr_baselines}, SAMNet reaches comparable 96.2\% accuracy, compared to 96.9\%, 97.7\% and 98.7\% for PG + EE, FiLM and TbD respectively.
+
+\subsection{Basic performance of SAMNet on COG}
 \label{sec:cog-baseline-compare}
 
-% \tk{description of dataset, task families/groups}
-% \tk{figure 5 from the orig paper}
-% \tk{comparison of our model with baseline - pure COG, no transfer learning}
-% \tk{figure 3 from the orig paper}
-% \tk{baseline model~\cite{yang2018dataset}}
-\tk{comparison with results from softpahts?}
+GOC dataset contains short videos with the associated questions, grouped into 23 question categories~\footnote{Aside of categorical questions, COG also offers tasks expecting the model to point a particular object in the image (out of scope of this paper).}.
+COG comes in two variants: the Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors (see~\cref{tab:cog_variants}).
+Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
+description of tasks, as shown in~\cref{fig:task-groups}.
 
@@
 	\label{tab:cog_variants}
-\end{table}\vspace{5pt}
+\end{table}
 
-There are 23 classification question categories in COG.
-The Canonical (easy) and Hard variant differ mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors (see~\cref{tab:cog_variants}).
-Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
-description of these tasks, as shown in~\cref{fig:task-groups}.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
+	\caption{Hierarchy of Task Groups in the COG dataset.}
+	\label{fig:task-groups}
+\end{figure}
 
@@
 
-We trained SAMNet using $k = 8$ reasoning steps and external memory of 8 address locations, each storing an array of 128 floats.
 We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
@@
 For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
+As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in its external memory.
 For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
-Despite there being some tasks in the Canonical variant where SAMNet achieved slightly lower accuracies, when comparing performances on the Hard variant, it improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, and especially on the more complex tasks in the dataset.
+SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, shining in the most complex (\textit{AndCompare}\uX, \textit{Compare}\uX) tasks.
 
-\subsection{Feature transfer in CLEVR-CoGenT}
+\subsection{Feature transfer using CLEVR-CoGenT}
 \label{sec:feature}
 
-% \tk{comparison of our model with baselines - CoGenT}
-% \tk{figure 3 from the orig paper}
-
-We conduct 2 experiments with SAMNet trained on CoGenT-A to evaluate its feature transfer capacity:
-\begin{itemize}
-\compresslist
-\item an immediate test (zero-shot learning) from A to B; and
-\item fine-tuning for a single epoch on 30k samples from CoGenT-B (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
-\end{itemize}
+In order to quantify SAMNet feature transfer capabilities we used the CoGenT variants of CLEVR and performed set of experiments, starting from training on CoGenT-A followed by:
+an immediate test (zero-shot learning) to test split ot CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following methodology used in~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+In \cref{fig:CoGenT-B-results} we compare the achieved performance with the previously selected SOTA models. 
+As sanity check we also provide accuracies achieved when: tested directly on CoGenT-A; and tested on CoGenT-A after fine-tuning on B.
 
@@
 
-We compare SAMNet to TbD~\cite{mascharka2018transparency}, FiLM~\cite{perez2018film} and PG + EE~\cite{johnson2017inferring}.
-\cref{fig:CoGenT-B-results} shows the results.
-Performance of SAMNet on CoGenT is clearly worse on CoGenT-B than CoGenT-A, but shows better zero-shot generalization than TbD.
-Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
-After finetuning on CoGenT-B, SAMNet limits catastrophic forgetting on CoGenT-A, contrarily to FilM and PG + EE.
+When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models.
+In the case of zero-shot transfer to CoGenT-B all models show relatively good performance (around 75 percent), still being a significant decrease of accuracy (by 17 points)
+As expected, all models are able to recove performance when fine-tuned on CoGenT-B.
+This process results in degradation of performance on originallly mastered CoGenT-A, with SAMNet and TbD showing clear capabilities to limit the impact of catastrophic forgetting.
+This indicates that both SAMNet and TbD managed to develop and sustain (to some extent) representations of features when facing shift from one domain to the other.
+Still, the drop in zero-shot transfer suggests that both struggle with disentanglement of shape and color features.
 

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
work on experiments, up to reasoning transfer
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 We briefly describe both datasets in the following two subsections.
-We also present comparison of SAMNet with the existing baselines as a sanity check. 
 In all experiments we used SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
 
-The rest of experiments is following the proposed taxonomy.
+We start experiments with comparison of SAMNet performance with the selected SOTA baselines on both CLEVR and COG datasets without transfer learning, what we treat as a sinity check.
+The rest of experiments follows the proposed taxonomy.
 First, we investigate the feature transfer using the CLEVR-CoGenT variants, followed by the temporal transfer on COG.
@@
 
-We compare SAMNet's performance to selected SOTA models, namely Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
-For performance reasons, we deactivated the external memory and temporal-related modules in SAMNet as they are unnecessary while reasoning about static images.
-As presented in \cref{fig:clevr_baselines}, SAMNet reaches comparable 96.2\% accuracy, compared to 96.9\%, 97.7\% and 98.7\% for PG + EE, FiLM and TbD respectively.
+\cref{fig:clevr_baselines} presents accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
+When collecting those results we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
+SAMNet reaches comparable 96.2\% accuracy, with TbD achieving the best score with 98.7\%.
 
@@
 
-GOC dataset contains short videos with the associated questions, grouped into 23 question categories~\footnote{Aside of categorical questions, COG also offers tasks expecting the model to point a particular object in the image (out of scope of this paper).}.
-COG comes in two variants: the Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors (see~\cref{tab:cog_variants}).
+COG dataset contains short videos, with the associated questions grouped into 23 categories~\footnote{Aside of categorical questions, COG also offers tasks expecting the model to point a particular object in the image (out of scope of this paper).}.
+COG comes in two variants: the Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
 Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
@@
 	\includegraphics[width=\columnwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
-	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A and fine-tuning on CoGenT-B.}
+	\caption{Feature transfer: test accuracties when transfering between the CoGenT-A and CoGenT-B variants.}
 	\label{fig:CoGenT-B-results}
@@
 
-When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models.
-In the case of zero-shot transfer to CoGenT-B all models show relatively good performance (around 75 percent), still being a significant decrease of accuracy (by 17 points)
+When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, what is consistent with results on the basic CLEVR variant.
+In the case of zero-shot transfer to CoGenT-B all models show relatively good performance (around 75 percent), still being a significant decrease of accuracy (by 17 points).
 As expected, all models are able to recove performance when fine-tuned on CoGenT-B.
-This process results in degradation of performance on originallly mastered CoGenT-A, with SAMNet and TbD showing clear capabilities to limit the impact of catastrophic forgetting.
+However, this process also results in degradation of performance on originallly mastered CoGenT-A, with SAMNet and TbD showing clear capabilities to limit the impact of catastrophic forgetting.
 This indicates that both SAMNet and TbD managed to develop and sustain (to some extent) representations of features when facing shift from one domain to the other.
@@
 
-The goal here is to test the transfer learning ability concerning the frame sequence length, frame history required for reasoning, and the number of object distractors.
-For that purpose, we compare both models when trained on the Canonical variant but tested on the Hard variant (\cref{fig:samnet_cog_overall_transfer}).
-The gray (dotted) color indicates original accuracies of the baseline model from paper,
-whereas yellow (striped) indicates accuracies of the baseline model obtained by running the original code provided by the authors~\cite{yang2018implement}.
-
-The first column displays the scores of the traditional ML setup when training and testing on the Canonical variant.
-The observed close scores in gray (dotted) and yellow (striped) underscore the baseline model reproducibility.
-For both cases of zero-shot learning (second column--91.6\% vs. 65.9\%) and fine-tuning using a single epoch (third column--96.7\% vs. 78.1\%), SAMNET outperforms the baseline model significantly.
-Interestingly, this fine-tuning yields a mild boost of +0.6\% on the earlier reported accuracy in~\cref{sec:cog-baseline-compare} (fourth column).
-These results suggest that it suffices to train SAMNet on simpler videos to enable learning of good memory usage and attention on relevant entities in order to achieve comparable, if not better, performance on longer video frames with more complex scenes.
+Temporal transfer checks the transfer learning ability concerning the frame sequence length, frame history required for reasoning, and the number of object distractors.
+For that reason we train the models on the Canonical variant of COG dataset and test them on the Hard variant~(\cref{fig:samnet_cog_overall_transfer}).
+As the original paper~\cite{yang2018dataset} didn't provided such experiments, we supplement the original accuracies (denoted as gray-dotted) with the ones achieved by the COG baseline model that we have obtained by running the original code (gray-striped) provided by the authors~\cite{yang2018implement}.
 
@@
 	\includegraphics[width=\columnwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
-	\caption{Total accuracies of SAMNet (blue) and baseline models (gray (dotted) / yellow (striped)) when testing generalization from Canonical to Hard variants of the dataset.}
+	\caption{Temporal transfer capabilites of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard variants of the COG dataset.}
 	\label{fig:samnet_cog_overall_transfer}
@@
 
-\subsection{Reasoning transfer in CoGenT}
+The first column displays the aggregated scores when training and testing on the Canonical variant.
+The observed close scores of both base models (gray striped and dotted) underscore the baseline model reproducibility.
+For both cases of zero-shot learning and fine-tuning using a single epoch, SAMNET significantly outperformed the baseline model, by 25 and 17 points respectively.
+This might partially result from the frame-by-frame processing of videos executed by SAMNet by design, as opposed to the processing of aggregated frames performed by the baseline.
+Interestingly, the fine-tuning yields a mild boost of +0.6\% on the accuracy achieved by the model trained exclusively on the Hard variant.
+This suggest that SAMNet managed to develop elementary skills (like good memory usage and attention on relevant entities) and successfully build on them when dealing with longer videos and more complex scenes.
+
+%This suggest that it suffices to train SAMNet on simpler videos to enable learning of good memory usage and attention on relevant entities in order to achieve comparable, if not better, performance on longer video frames with more complex scenes.
+
+\subsection{Reasoning transfer in CLEVR-CoGenT}
 \label{sec:reasoning-clevr}

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/samnet.tex
added t subscript to h^r and h^a

@@
 The unit first determines the memory location where an object could be added:
-\[ \vec{w}_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
+\[ \vec{w}_t = \doreplace_t \cdot \rhead_t + \doadd_t \cdot \whead_{t-1} \]
 Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
@@
 Then:
-\[ \whead_t = \doadd \cdot \whead'_{t-1} + (1-\doadd) \cdot \whead_{t-1} \]
+\[ \whead_t = \doadd_t \cdot \whead'_{t-1} + (1-\doadd_t) \cdot \whead_{t-1} \]
 

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
work on experiments, up to reasoning transfer
Signed-off-by: ibm <tkornuta.ibm@gmail.com>
minor change to TL

@@
 This includes visual attributes such as size, color and shape, temporal characteristics reflected in the number of frames and scene complexity, and finally the reasoning difficulty.
-To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.
+To establish a formal framework for these various aspects, we first recall the formal notions in the framework of transfer learning~\cite{pan2009survey}.
 
@@
 investigations of transfer learning.
-In \cref{sec:experiments}, we detail the performance of
-SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset
-for feature transfer, the COG dataset for temporal transfer, and finally
-both datasets for reasoning transfer, with appropriate baseline comparisons.
-
+%In \cref{sec:experiments}, we detail the performance of SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset for feature transfer, the COG dataset for temporal transfer, and finally both datasets for reasoning transfer, with appropriate baseline comparisons.
 Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
minor

@@
 This includes visual attributes such as size, color and shape, temporal characteristics reflected in the number of frames and scene complexity, and finally the reasoning difficulty.
-To establish a formal framework for these various aspects, we first recall the formal notions in the framework of transfer learning~\cite{pan2009survey}.
+To establish a formal framework for these various aspects, we first recall the basic theoretical notions in transfer learning~\cite{pan2009survey}.
 

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex

@@
 and \emph{reasoning transfer}.
-These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG datasets that are particularly suited for experimental
-investigations of transfer learning.
+These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG. These datasets were chosen because they 
+are particularly suited for experimental investigations of transfer learning described in the following section.
 %In \cref{sec:experiments}, we detail the performance of SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset for feature transfer, the COG dataset for temporal transfer, and finally both datasets for reasoning transfer, with appropriate baseline comparisons.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/related_work.tex
Added small paragraph about TL in Visual Reasoning in Related Works.

@@
 \section{Related work}
-
-\tk{That section will focus \textbf{only} on transfer learning}
+\label{sec:related_work}
 
@@
 image segmentation vs VQA) change significantly.
-%This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
 
@@
 
-\tk{missing review: TL in visual reasoning, refer to CoGenT and COG}
+In Visual Reasoning, transfer learning has helped models generalize better to domains with different distributions.
+Using the CLEVR-CoGenT~\cite{johnson2017clevr} dataset and finetuning, \cite{mascharka2018transparency, perez2018film, johnson2017inferring} have demonstrated impressive accuracy gains on a domain with different attributes combinations than the one used for training.
+Similarly, using the COG dataset, \cite{yang2018dataset} have shown that a model can do significantly better than chance on a task it was not explicitly trained on, by using knowledge learned on other tasks.
 

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex

@@
 In all experiments we used SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats. 
+When working with all CLEVR/CoGenT variants we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
 
-We start experiments with comparison of SAMNet performance with the selected SOTA baselines on both CLEVR and COG datasets without transfer learning, what we treat as a sinity check.
-The rest of experiments follows the proposed taxonomy.
-First, we investigate the feature transfer using the CLEVR-CoGenT variants, followed by the temporal transfer on COG.
-Finally, we assess SAMNet's transfer reasoning capabilities on both datasets by regrouping and reorganizing classes of questions into new training and test splits.
+We start by with a sinity check comparison of the performance of SAMNet and the selected SOTA baselines on both CLEVR and COG datasets without transfer learning.
+The rest of the experiments follows the proposed taxonomy.
+First, we investigate the feature transfer using the CLEVR-CoGenT variants, followed by the temporal transfer on the COG variants.
+Finally, we assess transfer reasoning capabilities on both datasets by regrouping and reorganizing classes of questions into new training and test splits.
 
@@
 CLEVR images contain objects characterised by a set of simple atributes (shape, color, size and material), whereas questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-Along with CLEVR the authors also introduced two CLEVR-CoGenT (Constrained Generalization Test) variants, with varying combinations of color-shape attributes.
+Along with CLEVR the authors also introduced two CLEVR-CoGenT (Constrained Generalization Test) A and B variants, with varying combinations of color-shape attributes.
 The colors are partitioned into two complementary families:
@@
 \cref{fig:clevr_baselines} presents accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
-When collecting those results we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
 SAMNet reaches comparable 96.2\% accuracy, with TbD achieving the best score with 98.7\%.
@@
 %This suggest that it suffices to train SAMNet on simpler videos to enable learning of good memory usage and attention on relevant entities in order to achieve comparable, if not better, performance on longer video frames with more complex scenes.
-
-\subsection{Reasoning transfer in CLEVR-CoGenT}
-\label{sec:reasoning-clevr}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
-	\caption{CoGenT-A accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.}
-	\label{fig:CoGenT-results}
-\end{figure}
-
-Using the question categories defined by the author, we conduct the following experiments:
-\begin{itemize}
-	\compresslist
-	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
-	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
-	This is a transfer learning setting where for the source task family, the task is sampled from all questions, while for the target task family, the samples consist of questions from group $t$ only;
-	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$. This can also be viewed as a transfer learning setting similar to the previous case.
-\end{itemize}
-
-Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.
-
-Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object-attribute values (15 labels).
-
-Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
-These improvements suggest that related tasks benefit from joint training.
-\textit{QueryAttribute} only sees an increase of one point.
-One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
-
-Finally, the ``all-tasks-but-$t$'' experiments (yellow) demonstrate that while tasks are related, one does not subsume another in terms of learning.
-Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
-We also observe no learning for \textit{Count} and \textit{QueryAttribute}. As these categories have labels that do not overlap with other categories, the model cannot predict these labels.
-
-An additional set of experiments, for which results are available in the supplementary material, fine-tune the model trained on all tasks on each task $t$ respectively.
-Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
-Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
-
-\subsection{Reasoning transfer in COG}
-\label{sec:reasoning-cog}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
-	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
-	\label{fig:COG-reasoning-results}
-\end{figure}\vspace{2pt}
-
-Reusing the task hierarchy in \cref{fig:task-groups}, we conduct the following experiments using the Canonical variant of COG to study whether transfer learning was effective in leveraging information gained by training a task family at a higher level
-of the hierarchy:
- \begin{itemize}
- 	\compresslist
-	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (Single-task training);
-	\item Jointly train on:
-	\begin{itemize}
-		\item \textbf{Group A} and test on each task from the lowest groups (i.e. \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare}) separately;
-		\item \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
-	\end{itemize}
-	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately (All-task training).
-\end{itemize}
-
-The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
-
-First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive tasks and therefore do not benefit from training with other task families.
-With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
-Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
-The former saw an accuracy jump from 58.6\% by training on samples from that family alone
-to 97.0\% when training on all samples. To further emphasize this behavior, notice that
-just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%.
-In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed
-of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
-Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
-is a slight loss incurred by including everything.
-As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%).
-To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex

--- 2019-11-20 Transfer_Learning/cvpr_submission/experiments.tex
@@
-\section{Experiments}
-\label{sec:experiments}
-We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
-We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
-There are 23 classification question categories in COG and the 5 original question categories in CLEVR.
-Our experiments were designed to study SAMNet's performance in terms of generalization and transfer learning abilities in different settings,
-and involved incorporating variants of both datasets.  
-For COG, the Canonical (easy) and Hard variant differ mainly on the number of frames in the video, 
-the maximum amount of look-back in frame history containing relevant information for reasoning, 
-and the number of object distractors (see~\cref{tab:cog_variants}).
-For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attribute values (details in~\cref{sec:temporal}).
-%In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
-%involving \emph{finetuning}.
-%Recall that the former involves evaluating the trained model of the source directly on the target while for the latter we do additional lightweight 
-%training on the target labeled data before evaluating its performance. 
-\begin{table}[ht]
+\subsection{Reasoning transfer in CLEVR-CoGenT}
+\label{sec:reasoning-clevr}
+
+\begin{figure}[htbp]
 	\centering
-		\begin{tabular}{lccc}
-			\toprule
-			Variant	& Frames & History	& Distractors \\ 
-			\midrule
-			Canonical (Easy) & 4 & 3 & 1\\	
-			Hard  & 8 & 7 & 10\\
-			\bottomrule	
-		\end{tabular}
-	\caption{Details of the Canonical and Hard variants of COG.}
-	\label{tab:cog_variants}
-\end{table}\vspace{5pt}
+	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
+	\caption{CoGenT-A accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.}
+	\label{fig:CoGenT-results}
+\end{figure}
 
-%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
-
-\subsection{Performance of SAMNet vs baseline model~\cite{yang2018dataset}}
-\label{sec:cog-baseline-compare}
-
-We trained SAMNet using 8 reasoning steps and external memory of 8 address locations, each storing an array of 128 floats. 
-%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
-We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
-
-\begin{figure*}[htb]
-	\centering
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
-	\end{subfigure}%
-	\newline
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{../results/samnet_cog_orig_hard.png}
-	\end{subfigure}%
-	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
-		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-	\label{fig:samnet_cog_detailed}
-\end{figure*}
-
-For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, 
-compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better 
-accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
-For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating
-that our model can adapt to larger number of frames and distractors.
-Despite there being some tasks in the Canonical variant where SAMNet achieved slightly lower accuracies,
-% (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it improves upon the baseline model on all tasks, 
-with improvements varying from 0.5 to more than 30 points, and especially on the more complex tasks in the dataset.
-
-\subsection{Reasoning transfer on CLEVR and COG}
-\label{sec:reasoning}
-In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
-of each task relative to others using appropriate groupings of tasks.
-%For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
-%appropriate experiments to study the effectiveness of transfer learning across task families.
-
-\subsubsection{CLEVR}
-\label{sec:reasoning-clevr}
-For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
-We conduct the following experiments:
+Using the question categories defined by the author, we conduct the following experiments:
 \begin{itemize}
@@
 	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
-	This is a transfer learning setting where for the source task family, the task is sampled from all questions,
-	while for the target task family, the samples consist of questions from group $t$ only;
-	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$.
-	This can also be viewed as a transfer learning setting similar to the previous case.
-	%These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
+	This is a transfer learning setting where for the source task family, the task is sampled from all questions, while for the target task family, the samples consist of questions from group $t$ only;
+	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$. This can also be viewed as a transfer learning setting similar to the previous case.
 \end{itemize}
 
-Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
+Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.
 
@@
 One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
-%We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
-We hypothesize that the improvements on e.g.
-\textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e., labels domain).
 
@@
 
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth]{../results/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
-	\label{fig:CoGenT-results}
-\end{figure}
-
-An additional set of experiments, for which results are available in the supplementary material,
-%Appendix \ref{sec:full-cogent-results}
-fine-tune the model trained on all tasks on each task $t$ respectively.
-%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the fine-tuned task and the drop, if any, on other tasks.
+An additional set of experiments, for which results are available in the supplementary material, fine-tune the model trained on all tasks on each task $t$ respectively.
 Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
@@
 
-\subsubsection{COG}
+\subsection{Reasoning transfer in COG}
 \label{sec:reasoning-cog}
-Since the number of task classes (=23) in the COG dataset is large, we designed a 2-level hierarchy of task groups using the
-description of these tasks, as shown in~\cref{fig:task-groups}.
 
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
-	\caption{Hierarchy of Task Groups.}
-	\label{fig:task-groups}
-\end{figure}
-
-\bigskip
-
-For groups at the lowest level, we chose the following task classes to be placed in those groups.
-Below, substitute each of \textit{Shape} and \textit{Color} for  \uX{} to obtain the task class.
-\begin{description}
-	\compresslist
-	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist};
-	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX;
-	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of};
-	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space};
-	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject}
-\end{description}
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth]{../results/COG_reasoning_transfer_v3}
+	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
 	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
 	\label{fig:COG-reasoning-results}
-\end{figure}
+\end{figure}\vspace{2pt}
 
-We then conducted the following experiments using the Canonical variant of COG to study 
-whether transfer learning was effective in leveraging information gained by training a task family at a higher level
+Reusing the task hierarchy in \cref{fig:task-groups}, we conduct the following experiments using the Canonical variant of COG to study whether transfer learning was effective in leveraging information gained by training a task family at a higher level
 of the hierarchy:

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
minor edits on Experiments

@@
 
-We start by with a sinity check comparison of the performance of SAMNet and the selected SOTA baselines on both CLEVR and COG datasets without transfer learning.
+We start with a sanity check of the performance of SAMNet in comparison with the selected SOTA baselines on both CLEVR and COG datasets without transfer learning.
 The rest of the experiments follows the proposed taxonomy.
@@
 \label{sec:clevr-baseline-compare}
-CLEVR images contain objects characterised by a set of simple atributes (shape, color, size and material), whereas questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-Along with CLEVR the authors also introduced two CLEVR-CoGenT (Constrained Generalization Test) A and B variants, with varying combinations of color-shape attributes.
+CLEVR images contain objects characterized by a set of attributes (shape, color, size and material), whereas the questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+The team behind the CLEVR dataset also introduced two CLEVR-CoGenT (Constrained Generalization Test) A and B variants, with varying combinations of color-shape attributes.
 The colors are partitioned into two complementary families:
@@
 
-COG dataset contains short videos, with the associated questions grouped into 23 categories~\footnote{Aside of categorical questions, COG also offers tasks expecting the model to point a particular object in the image (out of scope of this paper).}.
+COG dataset contains short videos, with the associated questions grouped into 23 categories~\footnote{Aside of categorical questions, COG also offers tasks expecting the model to point a particular object in the image (out of scope for this paper).}.
 COG comes in two variants: the Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
@@
 For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
-SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, shining in the most complex (\textit{AndCompare}\uX, \textit{Compare}\uX) tasks.
+SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex (\textit{AndCompare}\uX, \textit{Compare}\uX) tasks.
 
@@
 
-In order to quantify SAMNet feature transfer capabilities we used the CoGenT variants of CLEVR and performed set of experiments, starting from training on CoGenT-A followed by:
+In order to quantify SAMNet feature transfer capabilities we used the CoGenT variants of CLEVR and performed a set of experiments, starting from training on CoGenT-A followed by:
 an immediate test (zero-shot learning) to test split ot CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following methodology used in~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
@@
 In the case of zero-shot transfer to CoGenT-B all models show relatively good performance (around 75 percent), still being a significant decrease of accuracy (by 17 points).
-As expected, all models are able to recove performance when fine-tuned on CoGenT-B.
-However, this process also results in degradation of performance on originallly mastered CoGenT-A, with SAMNet and TbD showing clear capabilities to limit the impact of catastrophic forgetting.
+As expected, all models are able to recover performance when fine-tuned on CoGenT-B.
+However, this process also results in degradation of performance on originally mastered CoGenT-A, with SAMNet and TbD showing clear capabilities to limit the impact of catastrophic forgetting.
 This indicates that both SAMNet and TbD managed to develop and sustain (to some extent) representations of features when facing shift from one domain to the other.
@@
 
-Temporal transfer checks the transfer learning ability concerning the frame sequence length, frame history required for reasoning, and the number of object distractors.
-For that reason we train the models on the Canonical variant of COG dataset and test them on the Hard variant~(\cref{fig:samnet_cog_overall_transfer}).
+Temporal transfer tests the transfer learning ability concerning the frame sequence length, frame history required for reasoning, and the number of distracting objects.
+Therefore, we train the models on the Canonical variant of COG dataset and test them on the Hard variant~(\cref{fig:samnet_cog_overall_transfer}).
 As the original paper~\cite{yang2018dataset} didn't provided such experiments, we supplement the original accuracies (denoted as gray-dotted) with the ones achieved by the COG baseline model that we have obtained by running the original code (gray-striped) provided by the authors~\cite{yang2018implement}.
@@
 The first column displays the aggregated scores when training and testing on the Canonical variant.
-The observed close scores of both base models (gray striped and dotted) underscore the baseline model reproducibility.
+Similar scores of both base models (gray striped and dotted) underscore the reproducibility of the baseline model .
 For both cases of zero-shot learning and fine-tuning using a single epoch, SAMNET significantly outperformed the baseline model, by 25 and 17 points respectively.
 This might partially result from the frame-by-frame processing of videos executed by SAMNet by design, as opposed to the processing of aggregated frames performed by the baseline.
-Interestingly, the fine-tuning yields a mild boost of +0.6\% on the accuracy achieved by the model trained exclusively on the Hard variant.
+Interestingly, fine-tuning yields a mild boost of +0.6\% on the accuracy achieved by the model trained exclusively on the Hard variant.
 This suggest that SAMNet managed to develop elementary skills (like good memory usage and attention on relevant entities) and successfully build on them when dealing with longer videos and more complex scenes.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex
polishing CLEVR figure
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 \label{sec:reasoning-clevr}
+In the following we have relied on the CoGent-A variant only.
+Using the question groups (categories) defined by the authors, we reorganized training and testing splits with the goal of measuring whether mastering reasoning for one group can help with learning of the other.
 
@@
 	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
-	\caption{CoGenT-A accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.}
-	\label{fig:CoGenT-results}
+	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
+	\label{fig:cogent_reasoning_transfer}
 \end{figure}
 
-Using the question categories defined by the author, we conduct the following experiments:
-\begin{itemize}
-	\compresslist
-	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
-	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
-	This is a transfer learning setting where for the source task family, the task is sampled from all questions, while for the target task family, the samples consist of questions from group $t$ only;
-	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$. This can also be viewed as a transfer learning setting similar to the previous case.
-\end{itemize}
+First we have trained a single SAMNet model and measured its accuracy on each of the task group $t$ separatelly.
+Those results, indicated in \cref{fig:cogent_reasoning_transfer} as "Train on All", form baselines for the next two sets of experiments.
 
-Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.
+Next, we trained and tested 5 SAMNet instances, each on a single task group $t$.
+Interestingly, we observe a significant accuracy drop in all task groups aside of the \textit{Query Attribute}.
+We hypotesize this results from the fact that mastering visual grounding and recognizing object attributes (being the core of the latter task) is a necessary skill the system needed by the other tasks.
+Thus training on \textit{Query Attribute} helps others, whereas without any training on that particular group the system struggles with developing such a skill.
 
-Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object-attribute values (15 labels).
+Finally, we trained 5 SAMNet instances in the extreme reasoning transfer setup: for each task group $t$ we trained a single instance on all tasks but $t$, and next tested its performance on $t$ only.
+As expected, this setup appeared to be difficult to deal with, observing severe performance drops, with accuracy of \textit{Count} and \textit{QueryAttribute} dropping to zero.
+The explanation is that these categories expect  answers (digits 0-9, names of attributes) that do not overlap with answers in the other groups (binary yes/no), thus the model cannot predict these labels on in a zero-shot transfer.
 
-Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
-These improvements suggest that related tasks benefit from joint training.
-\textit{QueryAttribute} only sees an increase of one point.
-One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
+%Besides, the zero accuracy on \textit{Count} can also be explained by the fact that it results from the need of totally different reasoning leading to the answer.
+%The \textit{QueryAttribute} latter is more interesting, as when mastering e.g.
+\textit{Exist} of  \textit{CompareAttribute} the model \textit{had} to develop some kind of understanding object attributes.
+%Still, this result once again suggests that the model learned joint representation of object attributes and struggle with disentangling them without being explicitly trained on task facilitationg that (like the  \textit{QueryAttribute}).
 
-Finally, the ``all-tasks-but-$t$'' experiments (yellow) demonstrate that while tasks are related, one does not subsume another in terms of learning.
-Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
-We also observe no learning for \textit{Count} and \textit{QueryAttribute}. As these categories have labels that do not overlap with other categories, the model cannot predict these labels.
-
-An additional set of experiments, for which results are available in the supplementary material, fine-tune the model trained on all tasks on each task $t$ respectively.
-Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
+% An additional set of experiments, for which results are available in the supplementary material, fine-tune the model trained on all tasks on each task $t$ respectively.
+%Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
 Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
@@
 	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
-	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
+	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}
 	\label{fig:COG-reasoning-results}
@@
 
-Reusing the task hierarchy in \cref{fig:task-groups}, we conduct the following experiments using the Canonical variant of COG to study whether transfer learning was effective in leveraging information gained by training a task family at a higher level
+Reusing the task hierarchy in \cref{fig:task-groups}, we conduct the following experiments using the Canonical variant of COG to study whether reasoning transfer learning was effective in leveraging information gained by training a task family at a higher level
 of the hierarchy:

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/cvpr_paper_main.tex
Experiments: basics, feature transfer
Signed-off-by: ibm <tkornuta.ibm@gmail.com>
reasoning transfer moved to a separate file
Signed-off-by: ibm <tkornuta.ibm@gmail.com>
reasoning transfer - COG
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 \captionsetup[table]{skip=5pt}
-\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
+%\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
 \usepackage{amsmath, amssymb, amsfonts,bm}
@@
 	Vincent Marois\footnotemark[2] \and
-	Tomasz Kornuta\thanks{Nvidia Research.} \and
+	Tomasz Kornuta\thanks{NVIDIA.} \and
 	Vincent Albouy\thanks{} \and
@@
 \input{experiments}
+\input{experiments_reasoning_transfer}
 

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex
reasoning transfer - COG
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 \subsection{Reasoning transfer in CLEVR-CoGenT}
-\label{sec:reasoning-clevr}
+\label{sec:reasoning-transfer-clevr}
 In the following we have relied on the CoGent-A variant only.
@@
 
-First we have trained a single SAMNet model and measured its accuracy on each of the task group $t$ separatelly.
+First we have trained a single SAMNet instance and measured its accuracy on each of the task group $t$ separatelly.
 Those results, indicated in \cref{fig:cogent_reasoning_transfer} as "Train on All", form baselines for the next two sets of experiments.
@@
 Next, we trained and tested 5 SAMNet instances, each on a single task group $t$.
-Interestingly, we observe a significant accuracy drop in all task groups aside of the \textit{Query Attribute}.
+Interestingly, we observe significant accuracy drops (from 18 up to almost 35 points) in all task groups aside of the \textit{Query Attribute}.
 We hypotesize this results from the fact that mastering visual grounding and recognizing object attributes (being the core of the latter task) is a necessary skill the system needed by the other tasks.
@@
 
-\subsection{Reasoning transfer in COG}
-\label{sec:reasoning-cog}
+\subsection{Reasoning transfer in COG Canonical}
+\label{sec:reasoning-transfer-cog}
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
-	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}
-	\label{fig:COG-reasoning-results}
-\end{figure}\vspace{2pt}
+We conduct the following experiments using the Canonical variant of COG to study whether reasoning transfer learning was effective in leveraging information gained by training a task family at a higher level of the hierarchy.
+Order of the performed experiments is analogical to the one from previous chapter.
+First column (\cref{fig:cog_reasoning_transfer}, "Train on All") is our baseline, i.e.
+we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
+Please note that those results are in fact weighted averages when aggregating accuracies of our model on the Canonical variant (\cref{fig:samnet_cog_detailed}).
 
-Reusing the task hierarchy in \cref{fig:task-groups}, we conduct the following experiments using the Canonical variant of COG to study whether reasoning transfer learning was effective in leveraging information gained by training a task family at a higher level
-of the hierarchy:
+Next
+
  \begin{itemize}
@@
 
-The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
+The results of these experiments are shown in~\cref{fig:cog_reasoning_transfer}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
+	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}
+	\label{fig:cog_reasoning_transfer}
+\end{figure}
 

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Polish related works.

@@
 We briefly describe both datasets in the following two subsections.
-In all experiments we used SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats. 
-When working with all CLEVR/CoGenT variants we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
+In all experiments, we trained SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
+When working with CLEVR-CoGenT, we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
 
-We start with a sanity check of the performance of SAMNet in comparison with the selected SOTA baselines on both CLEVR and COG datasets without transfer learning.
+We start with an evaluation of SAMNet's performance, comparing it to baselines on both CLEVR and COG datasets, without transfer learning.
 The rest of the experiments follows the proposed taxonomy.
-First, we investigate the feature transfer using the CLEVR-CoGenT variants, followed by the temporal transfer on the COG variants.
-Finally, we assess transfer reasoning capabilities on both datasets by regrouping and reorganizing classes of questions into new training and test splits.
+We first investigate feature transfer using CLEVR-CoGenT, followed by temporal transfer on the COG variants.
+Finally, we assess the transfer reasoning capabilities on both datasets by reorganizing classes of questions into new training and test splits.
 
@@
 CLEVR images contain objects characterized by a set of attributes (shape, color, size and material), whereas the questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-The team behind the CLEVR dataset also introduced two CLEVR-CoGenT (Constrained Generalization Test) A and B variants, with varying combinations of color-shape attributes.
+The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, A and B, with varying combinations of color-shape attributes.
 The colors are partitioned into two complementary families:
 Gray, Blue, Brown and Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both varianrs (See~\cref{tab:cogent_conditions}).
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (See~\cref{tab:cogent_conditions}).
 As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/introduction.tex
Polish related works.

@@
 In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural}, among others.
-Neural networks, being statistical models~\cite{ripley1993statistical,warner1996understanding}, rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.\ sampled from a common input space under similar data distribution characteristics.
+Neural networks, being statistical models~\cite{ripley1993statistical,warner1996understanding}, rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}).
 However, in many real-world scenarios, this assumption does not hold.

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex

@@
 \label{sec:reasoning-transfer-clevr}
-In the following we have relied on the CoGent-A variant only.
+In the following experiments we have relied on the CoGent-A variant only.
 Using the question groups (categories) defined by the authors, we reorganized training and testing splits with the goal of measuring whether mastering reasoning for one group can help with learning of the other.
@@
 
-Next, we trained and tested 5 SAMNet instances, each on a single task group $t$.
+Next, we trained and tested 5 SAMNet instances, each on a single task group $t$ ("Train on t only").
 Interestingly, we observe significant accuracy drops (from 18 up to almost 35 points) in all task groups aside of the \textit{Query Attribute}.
@@
 \label{sec:reasoning-transfer-cog}
-
-We conduct the following experiments using the Canonical variant of COG to study whether reasoning transfer learning was effective in leveraging information gained by training a task family at a higher level of the hierarchy.
-Order of the performed experiments is analogical to the one from previous chapter.
+In order to further investigate whether reasoning transfer was effective in leveraging information gained by training a task family at a higher level of the hierarchy we also conducted a setof  experiments using the Canonical variant of COG.
+Order of the performed experiments is analogical to the one from previous section.
 First column (\cref{fig:cog_reasoning_transfer}, "Train on All") is our baseline, i.e.
@@
 Please note that those results are in fact weighted averages when aggregating accuracies of our model on the Canonical variant (\cref{fig:samnet_cog_detailed}).
-
-Next
-
- \begin{itemize}
- 	\compresslist
-	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (Single-task training);
-	\item Jointly train on:
-	\begin{itemize}
-		\item \textbf{Group A} and test on each task from the lowest groups (i.e. \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare}) separately;
-		\item \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
-	\end{itemize}
-	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately (All-task training).
-\end{itemize}
-
-The results of these experiments are shown in~\cref{fig:cog_reasoning_transfer}.
 
@@
 
-First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive tasks and therefore do not benefit from training with other task families.
-With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
-Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
-The former saw an accuracy jump from 58.6\% by training on samples from that family alone
-to 97.0\% when training on all samples. To further emphasize this behavior, notice that
-just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%.
-In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed
-of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
-Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
-is a slight loss incurred by including everything.
+Next, we experimented with the "Train on t only" setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. single leaf of the proposed hierarchy).
+For the \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr} task groups the accuracy is matching the baseline, suggesting that each group contain tasks sufficient for developing all necessary skills.
+Therefore models trained on those will not benefit from any additional training on other task groups.
+However, the accuracy drops in the models trained only on tasks from the \textit{Compary} and \textit{Cognitive} task groups suggests the oposite.
+
+For that reason we have performed the third set of experiments ("Train on Group A/B"), where we trained two SAMNet instances: first on tasks from the \textit{Group A} aggregate, tested next on each task from the lowest groups (i.e.
+\textit{Basic}, \textit{Obj-Attr} and \textit{Compare}) separately; and second on tasks from \textit{Group B}, tested separately on \textit{Spatial} and \textit{Cognitive}.
+As expected, training on other tasks from group \textit{Group A} enabled the model to significantly improve on \textit{Compare} task (from 58.6\% to 92.3\%).
+Similar improvement (from 68.8\% to 97.1\%) was observed in the second model, when trained on \textit{Group B} and tested on \textit{Cognitive}.
+Moreover, the achieved accuracy is in fact higher by 1.4 point from the one achieved when training on all tasks (95.7\%).
+This suggest that the model might have been struggling with mastering all that one when faced all kind of questions, maybe lacking the capacity.
+Finally, there is an interesting effect for \textit{Obj-Attr} and \textit{Spatial}: training on the whole group A/B seems not to help the models, and when comparing those accuracies with the ones achieved by the models trained on task $t$ only we observe some slight drops (around 0.3-0.5 point).
+Understanding that effect seems to require further investigation on dependencies between the resoning required by the particular questions and reasoning transfer.
+
+%With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
+%To further emphasize this behavior, notice that just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%.
+%In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
+% Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there is a slight loss incurred by including everything.
 As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%).

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/introduction.tex
intro
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

--- 2020-02-07 Transfer_Learning/cvpr_2nd_submission/introduction.tex
@@
 In this work we focus on transfer learning in multi-modal reasoning tasks combining vision and language~\cite{mogadala2019trends}.
-Recently introduced visual reasoning datasets, such as ~\cite{johnson2017clevr,yang2018dataset,song2018explore}, attempt to probe the generalization capabilities of models under various transfer learning scenarios.
-For example, CLEVR/CoGenT \cite{johnson2017clevr} offers two dataset variants with different combinations of visual attributes.
-Whereas, COG \cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants with different number of frames and scene complexity.
-Both datasets come with a number of task classes that require similar reasoning abilities (e.g.
-compare or count objects).
-The open question is whether we can build a neural architecture that fosters transfer learning and generalizes from simpler to more complex reasoning tasks.
+Recently introduced visual reasoning datasets, such as ~\cite{johnson2017clevr,yang2018dataset,song2018explore}, attempt to probe the generalization capabilities of models under various scenarios, trying to quatify the visual complexity of the analysed scene or compositional complexity of the question.
+Some of those setups seems to be well suited for transfer learning, still, not addressing that isue directly.
+For example, the \cite{johnson2017clevr} paper introduces the CLEVR dataset along with two variants (CoGenT-A and B) with varying combinations of visual attributes.
+Similarly, COG \cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants (Canonical and Hard) with different number of frames and scene complexity.
+Both datasets come with a number of task classes that require similar reasoning abilities (e.g. compare or count objects).
+The open question that we address in this paper is whether we can build a neural architecture that fosters transfer learning and generalizes from simpler to more complex reasoning tasks.
 

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/related_work.tex

--- 2020-02-05 Transfer_Learning/cvpr_2nd_submission/related_work.tex
@@
 
-\tk{missing review: TL in visual reasoning, refer to CoGenT and COG}
+In Visual Reasoning, transfer learning has helped models generalize better to domains with different distributions.
+Using the CLEVR-CoGenT~\cite{johnson2017clevr} dataset and finetuning, \cite{mascharka2018transparency, perez2018film, johnson2017inferring} have demonstrated impressive accuracy gains on a domain with different attributes combinations than the one used for training.
+Similarly, using the COG dataset, \cite{yang2018dataset} have shown that a different model can do significantly better than chance on a task it was not explicitly trained on, by using knowledge learned on other tasks.
 
-\tk{after reading that section the reader should end up with a conclusion that: there are no good models for TL in VR and, moreover, the datasets are randomly testing this or that, there is no theoretical framework showing that do they mean/bigger picture is missing}
+These results clearly indicate the usefulness of transfer learning, despite the assumption of similar distributions between the source and target domains not being respected.
+As this is currently not fully understood, it highlights the need for a more systematic research direction on these topics.
+We propose to address this by introducing a taxonomy of transfer learning in visual reasoning, and illustrate it with two visual reasoning datasets.
+
+% \tk{The experimental results clearly indicate that transfer learning is helping, despite that the core assumptions on the compatibility/similarity of domains is broken (transfering between domains having similar distribution).
+% We do not understand this fully, thus the need for a more systematic research on that topic emerges.
+% The paper adresses that by introducing a theoretical framework/taxonomy enabling to categorise visual reasoning tasks.
+% As a starting point, we picked two visual reasoning datasets and analyse the achieved results through the prism of the proposed taxonomy.
+% }
+%
+%
+% \tk{after reading that section the reader should end up with a conclusion that: there are no good models for TL in VR and, moreover, the datasets are randomly testing this or that, there is no theoretical framework showing that do they mean/bigger picture is missing}

### 2020-02-09 Transfer_Learning/cvpr_2nd_submission/experiments.tex
Proofread Experiments section.

@@
 In all experiments, we trained SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
-When working with CLEVR-CoGenT, we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
+When working with CLEVR, we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
 
@@
 We first investigate feature transfer using CLEVR-CoGenT, followed by temporal transfer on the COG variants.
-Finally, we assess the transfer reasoning capabilities on both datasets by reorganizing classes of questions into new training and test splits.
+Finally, we assess the reasoning transfer capability of SAMNet on both datasets, by reorganizing groups of questions into new training and test splits.
 
@@
 
-\subsection{Basic performance of SAMNet on CLEVR}
+\subsection{Performance of SAMNet on CLEVR}
 \label{sec:clevr-baseline-compare}
-CLEVR images contain objects characterized by a set of attributes (shape, color, size and material), whereas the questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, A and B, with varying combinations of color-shape attributes.
+CLEVR images contain objects characterized by a set of attributes (shape, color, size and material).
+The questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, CoGenT-A and CoGenT-B, with varying combinations of color-shape attributes.
 The colors are partitioned into two complementary families:
@@
 
-\cref{fig:clevr_baselines} presents accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
-SAMNet reaches comparable 96.2\% accuracy, with TbD achieving the best score with 98.7\%.
+\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
+SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.
 
-\subsection{Basic performance of SAMNet on COG}
+\subsection{Performance of SAMNet on COG}
 \label{sec:cog-baseline-compare}
 
-COG dataset contains short videos, with the associated questions grouped into 23 categories~\footnote{Aside of categorical questions, COG also offers tasks expecting the model to point a particular object in the image (out of scope for this paper).}.
-COG comes in two variants: the Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
+COG dataset contains short videos, with associated questions grouped into 23 categories~\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
+COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
 Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
@@
 For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
-SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex (\textit{AndCompare}\uX, \textit{Compare}\uX) tasks.
+SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex tasks (\textit{AndCompare}\uX, \textit{Compare}\uX).
 
@@
 
-In order to quantify SAMNet feature transfer capabilities we used the CoGenT variants of CLEVR and performed a set of experiments, starting from training on CoGenT-A followed by:
-an immediate test (zero-shot learning) to test split ot CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following methodology used in~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
-In \cref{fig:CoGenT-B-results} we compare the achieved performance with the previously selected SOTA models.
-As sanity check we also provide accuracies achieved when: tested directly on CoGenT-A; and tested on CoGenT-A after fine-tuning on B.
+In order to quantify SAMNet's feature transfer ability, we used the CoGenT variants of CLEVR and performed a set of experiments, starting from training on CoGenT-A, followed by:
+an immediate test (zero-shot learning) on CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following the methodology used in~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+In \cref{fig:CoGenT-B-results}, we compare the achieved performance with the previously selected SOTA models.
+We also consider a direct test on CoGenT-A; and a test on CoGenT-A after fine-tuning on B.
 
@@
 	\includegraphics[width=\columnwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
-	\caption{Feature transfer: test accuracties when transfering between the CoGenT-A and CoGenT-B variants.}
+	\caption{Feature transfer: test accuracies when transferring between CoGenT-A and CoGenT-B.}
 	\label{fig:CoGenT-B-results}
@@
 
-When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, what is consistent with results on the basic CLEVR variant.
-In the case of zero-shot transfer to CoGenT-B all models show relatively good performance (around 75 percent), still being a significant decrease of accuracy (by 17 points).
-As expected, all models are able to recover performance when fine-tuned on CoGenT-B.
-However, this process also results in degradation of performance on originally mastered CoGenT-A, with SAMNet and TbD showing clear capabilities to limit the impact of catastrophic forgetting.
-This indicates that both SAMNet and TbD managed to develop and sustain (to some extent) representations of features when facing shift from one domain to the other.
-Still, the drop in zero-shot transfer suggests that both struggle with disentanglement of shape and color features.
+When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, matching the results observed in \cref{sec:clevr-baseline-compare}.
+When zero-shot testing on CoGenT-B, all models show relatively good performance (around 75\%), which represents nonetheless a drop of 17 points with respect to CoGenT-A.
+All models perform better when fine-tuned on CoGenT-B.
+However, this process also results in a degradation of performance on CoGenT-A, with SAMNet and TbD showing an ability to limit this drop in accuracy.
+While this suggests both models were able to adapt representations for both domains, these representations are not fully disentangled.
 
@@
 
-Temporal transfer tests the transfer learning ability concerning the frame sequence length, frame history required for reasoning, and the number of distracting objects.
+Temporal transfer tests the transfer learning ability regarding the frame sequence length, frame history required for reasoning, and the number of distracting objects.
 Therefore, we train the models on the Canonical variant of COG dataset and test them on the Hard variant~(\cref{fig:samnet_cog_overall_transfer}).
-As the original paper~\cite{yang2018dataset} didn't provided such experiments, we supplement the original accuracies (denoted as gray-dotted) with the ones achieved by the COG baseline model that we have obtained by running the original code (gray-striped) provided by the authors~\cite{yang2018implement}.
+As the original paper~\cite{yang2018dataset} didn't provide such experiments, we supplement the original accuracies (denoted as gray-dotted) with the ones achieved by the COG baseline model that we have obtained by running the original code (gray-striped) provided by the authors~\cite{yang2018implement}.
 
@@
 	\includegraphics[width=\columnwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
-	\caption{Temporal transfer capabilites of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard variants of the COG dataset.}
+	\caption{Temporal transfer capabilities of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard  in COG.}
 	\label{fig:samnet_cog_overall_transfer}
@@
 The first column displays the aggregated scores when training and testing on the Canonical variant.
-Similar scores of both base models (gray striped and dotted) underscore the reproducibility of the baseline model .
+The close scores of both base models (gray striped and dotted) highlight the faithful reproduction of the baseline model.
 For both cases of zero-shot learning and fine-tuning using a single epoch, SAMNET significantly outperformed the baseline model, by 25 and 17 points respectively.
-This might partially result from the frame-by-frame processing of videos executed by SAMNet by design, as opposed to the processing of aggregated frames performed by the baseline.
+This might partially results from the frame-by-frame processing of videos executed by SAMNet by design, as opposed to the processing of aggregated frames performed by the baseline.
 Interestingly, fine-tuning yields a mild boost of +0.6\% on the accuracy achieved by the model trained exclusively on the Hard variant.
-This suggest that SAMNet managed to develop elementary skills (like good memory usage and attention on relevant entities) and successfully build on them when dealing with longer videos and more complex scenes.
+This suggests that SAMNet managed to develop elementary skills (such as memory usage and attention on relevant entities) and successfully uses them when dealing with longer videos and more complex scenes.
 

### 2020-02-09 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex
Proofread Experiments section.

@@
 \label{sec:reasoning-transfer-clevr}
-In the following experiments we have relied on the CoGent-A variant only.
-Using the question groups (categories) defined by the authors, we reorganized training and testing splits with the goal of measuring whether mastering reasoning for one group can help with learning of the other.
+In the following experiments, we used CoGent-A only.
+Using the question groups (categories) defined by the authors, we organized training and testing splits with the goal of measuring whether mastering reasoning for one questions group can help learning others.
 
@@
 
-First we have trained a single SAMNet instance and measured its accuracy on each of the task group $t$ separatelly.
-Those results, indicated in \cref{fig:cogent_reasoning_transfer} as "Train on All", form baselines for the next two sets of experiments.
+We first trained a single SAMNet instance and measured its accuracy on each of the task group $t$ separately.
+Those results, indicated in \cref{fig:cogent_reasoning_transfer} as "Train on All", serve as baselines for the next two sets of experiments.
 
-Next, we trained and tested 5 SAMNet instances, each on a single task group $t$ ("Train on t only").
-Interestingly, we observe significant accuracy drops (from 18 up to almost 35 points) in all task groups aside of the \textit{Query Attribute}.
-We hypotesize this results from the fact that mastering visual grounding and recognizing object attributes (being the core of the latter task) is a necessary skill the system needed by the other tasks.
+We next trained and tested 5 SAMNet instances, each on a single task group $t$ ("Train on t only").
+We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, aside of \textit{Query Attribute}.
+We hypothesize this results from the fact that mastering visual grounding and recognizing object attributes (being the core of the latter task) is a necessary skill the system needed by the other tasks.
 Thus training on \textit{Query Attribute} helps others, whereas without any training on that particular group the system struggles with developing such a skill.

### 2020-02-09 Transfer_Learning/cvpr_2nd_submission/related_work.tex

@@
 Similar developments have emerged in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, has become a standard procedure when working with different NLP domains and tasks.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, was de facto a standard procedure accross different NLP domains and tasks for the last several years.
 Recently, there is a clear, growing trend of utilization of deep contextualized word representations such as ELMo~\cite{peters2018deep} (based on bidirectional LSTMs~\cite{hochreiter1997long}) or BERT~\cite{devlin2018bert} (based on the Transformer~\cite{vaswani2017attention} architecture), where entire deep networks (not just the input layer) are pretrained on very large corporas.
-In analogy to pretrained image encoders, the NLP community has also started to create model repositories, some with dozens of pretrained models ready to be downloaded and used.
+%In analogy to repositories with pretrained image encoders in TensorFlow~\cite{} or PyTorch~\cite{}, the NLP community has also started to create model repositories, some with dozens of pretrained models ready to be downloaded and used.
 HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
 
-The success of transfer learning raises several research questions, such as the characteristics which make a dataset more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
-One of the most systematic works in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aimed at discovering the dependencies between twenty-six 2D, 2.5D, 3D, and semantic computer vision tasks.
+Visual Reasoning tasks combining both the visual and language modalities~\cite{mogadala2019trends} naturally draw from those findings by reusing the pretrained image and word/question encoders.
+The community also seems to be realising that the models should not only be able to generalize on the low-level image features, but also on the performed high-level, abstract \textit{reasoning}.
+First notable attemp to establish a framework enabling transfer learning of reasoning skill was CLEVR~\cite{johnson2017clevr} with its two CoGenT variants.
+As a result several interesting works appeared~\cite{mascharka2018transparency, perez2018film, johnson2017inferring,marois2018transfer}, proposing models trying to cope with transfer from one to the other domain with different distributions of visual attribute combinations.
+Similarly, the baseline model introduced along with the COG dataset~\cite{yang2018dataset} have shown that it can do significantly better answer questions belonging to task classes not being explicitly trained on when leveraging knowledge learned on other tasks.
+These results clearly indicate the usefulness of transfer learning, despite the assumption of similar distributions between the source and target domains not being respected.
+At the same time transfer learning several research questions, such as the characteristics which make a whole dataset or a particular task more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
+One of the most systematic works in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies between twenty-six different computer vision tasks.
+In this work we extend that idea further and introduce a taxonomy enabling us to isolate and quantify different aspects of visual reasoning on the performance of our model.
+%We illustrate it with the two above mentioned CLEVR and COG datasets.
+%The taxonomy enabled us to perform more systematic studies and facilitate comparison between the already existing solutions and the newly introduced SAMNet model.
 
-In Visual Reasoning, transfer learning has helped models generalize better to domains with different distributions.
-Using the CLEVR-CoGenT~\cite{johnson2017clevr} dataset and finetuning, \cite{mascharka2018transparency, perez2018film, johnson2017inferring} have demonstrated impressive accuracy gains on a domain with different attributes combinations than the one used for training.
-Similarly, using the COG dataset, \cite{yang2018dataset} have shown that a different model can do significantly better than chance on a task it was not explicitly trained on, by using knowledge learned on other tasks.
+%transfer learning has helped models generalize better to domains with different distributions.
 
-These results clearly indicate the usefulness of transfer learning, despite the assumption of similar distributions between the source and target domains not being respected.
-As this is currently not fully understood, it highlights the need for a more systematic research direction on these topics.
-We propose to address this by introducing a taxonomy of transfer learning in visual reasoning, and illustrate it with two visual reasoning datasets.
+%We propose to address this by introducing a taxonomy of transfer learning in visual reasoning, and illustrate it with two visual reasoning datasets.
 

### 2020-02-09 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
reorganization of images - perfect 8 pages
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 \label{sec:transfer_learning}
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
-	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
-\end{figure*}
 Due to the complex nature of visual reasoning, it appears that
@@
 This entails studying transfer learning between families of tasks which requires extending the above definition.
+
+\begin{table}[b!]
+	\centering
+	%\begin{adjustbox}{width=0.45\textwidth}
+	\begin{tabular}{cccc}
+		\toprule
+		Variant	& Cubes	& Cylinders &	Spheres	\\
+		\midrule
+		CLEVR &  Any Color  & Any Color 	&	Any color  \\
+		CoGenT-A &  Family A  & Family B 	&	Any color  \\
+		CoGenT-B	&	Family B  &	Family A	&	Any color \\
+		\bottomrule
+	\end{tabular}
+	%\end{adjustbox}
+	\caption{Allowed feature combinations in the CoGenT-A and CoGenT-B variants of the CLEVR dataset.}%\vspace{2pts}
+	\label{tab:cogent_conditions}
+\end{table}
 

### 2020-02-09 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex
Proofread Reasoning transfer section in Experiments.

@@
 In the following experiments, we used CoGent-A only.
-Using the question groups (categories) defined by the authors, we organized training and testing splits with the goal of measuring whether mastering reasoning for one questions group can help learning others.
+Using the question groups defined by the authors, we organized training and testing splits with the goal of measuring whether mastering reasoning for one questions group can help learning others.
 
@@
 
-We first trained a single SAMNet instance and measured its accuracy on each of the task group $t$ separately.
+We first trained a single SAMNet instance on CoGenT-A and measured its accuracy on each of the task group $t$ separately.
 Those results, indicated in \cref{fig:cogent_reasoning_transfer} as "Train on All", serve as baselines for the next two sets of experiments.
@@
 We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, aside of \textit{Query Attribute}.
-We hypothesize this results from the fact that mastering visual grounding and recognizing object attributes (being the core of the latter task) is a necessary skill the system needed by the other tasks.
-Thus training on \textit{Query Attribute} helps others, whereas without any training on that particular group the system struggles with developing such a skill.
+We hypothesize \textit{Query Attribute} requires mastering visual grounding and recognizing object attributes, as opposed to the other groups which may not enforce it.
+Thus, training on \textit{Query Attribute} helps others, whereas without any training on that particular group, SAMNet battles developing such skill.
 
-Finally, we trained 5 SAMNet instances in the extreme reasoning transfer setup: for each task group $t$ we trained a single instance on all tasks but $t$, and next tested its performance on $t$ only.
-As expected, this setup appeared to be difficult to deal with, observing severe performance drops, with accuracy of \textit{Count} and \textit{QueryAttribute} dropping to zero.
-The explanation is that these categories expect  answers (digits 0-9, names of attributes) that do not overlap with answers in the other groups (binary yes/no), thus the model cannot predict these labels on in a zero-shot transfer.
+Finally, we trained 5 SAMNet instances as follows: for each task group $t$ we trained a single instance on all tasks but $t$, and tested its performance on $t$ only.
+As expected, this setup appears challenging, causing severe performance drops, with accuracy on \textit{Count} and \textit{QueryAttribute} dropping to zero.
+This stems from the non-overlapping labels spaces of \textit{Count} (digits 0 to 9) and \textit{QueryAttribute} (all attributes names) with the other groups (binary "yes" / "no").
+Thus, the model cannot predict these labels in a zero-shot transfer.
 
@@
 \label{sec:reasoning-transfer-cog}
-In order to further investigate whether reasoning transfer was effective in leveraging information gained by training a task family at a higher level of the hierarchy we also conducted a setof  experiments using the Canonical variant of COG.
-Order of the performed experiments is analogical to the one from previous section.
-First column (\cref{fig:cog_reasoning_transfer}, "Train on All") is our baseline, i.e.
+In order to further investigate whether reasoning transfer is effective in leveraging information gained by training a task family at a higher level of the hierarchy, we also conducted a set of experiments using the Canonical variant of COG.
+The order of the performed experiments is analogical to the one in the previous section.
+The first column (\cref{fig:cog_reasoning_transfer}, "Train on All") is the baseline, i.e.
 we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
-Please note that those results are in fact weighted averages when aggregating accuracies of our model on the Canonical variant (\cref{fig:samnet_cog_detailed}).
+Please note that these results are weighted averages of the accuracies of our model on the Canonical variant tasks (\cref{fig:samnet_cog_detailed}).
 
@@
 Next, we experimented with the "Train on t only" setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. single leaf of the proposed hierarchy).
-For the \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr} task groups the accuracy is matching the baseline, suggesting that each group contain tasks sufficient for developing all necessary skills.
-Therefore models trained on those will not benefit from any additional training on other task groups.
-However, the accuracy drops in the models trained only on tasks from the \textit{Compary} and \textit{Cognitive} task groups suggests the oposite.
+For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the baseline ("Train on All"), suggesting that each group contain sufficient information for developing all necessary skills.
+Therefore, models trained on these groups may not benefit from any additional training on other task groups.
+However, the accuracy drops for \textit{Compary} and \textit{Cognitive}, suggesting the opposite.
 
-For that reason we have performed the third set of experiments ("Train on Group A/B"), where we trained two SAMNet instances: first on tasks from the \textit{Group A} aggregate, tested next on each task from the lowest groups (i.e.
-\textit{Basic}, \textit{Obj-Attr} and \textit{Compare}) separately; and second on tasks from \textit{Group B}, tested separately on \textit{Spatial} and \textit{Cognitive}.
-As expected, training on other tasks from group \textit{Group A} enabled the model to significantly improve on \textit{Compare} task (from 58.6\% to 92.3\%).
-Similar improvement (from 68.8\% to 97.1\%) was observed in the second model, when trained on \textit{Group B} and tested on \textit{Cognitive}.
-Moreover, the achieved accuracy is in fact higher by 1.4 point from the one achieved when training on all tasks (95.7\%).
-This suggest that the model might have been struggling with mastering all that one when faced all kind of questions, maybe lacking the capacity.
-Finally, there is an interesting effect for \textit{Obj-Attr} and \textit{Spatial}: training on the whole group A/B seems not to help the models, and when comparing those accuracies with the ones achieved by the models trained on task $t$ only we observe some slight drops (around 0.3-0.5 point).
-Understanding that effect seems to require further investigation on dependencies between the resoning required by the particular questions and reasoning transfer.
+Therefore, we have performed a final set of experiments ("Train on Group A/B"), where we trained two SAMNet instances: a) trained on all tasks from \textit{Group A} and tested on each task from the lowest groups (i.e.
+\textit{Basic}, \textit{Obj-Attr} and \textit{Compare}) separately; b) trained on all tasks from \textit{Group B} and tested separately on \textit{Spatial} and \textit{Cognitive}.
+As expected, training on the other tasks from \textit{Group A} enabled the model to significantly improve on the \textit{Compare} task (from 58.6\% to 92.3\%).
+A similar improvement (from 68.8\% to 97.1\%) was observed in the second experiment, when trained on \textit{Group B} and tested on \textit{Cognitive}.
+Moreover, the achieved accuracy is in fact higher by 1.4 point than the one achieved when training on all tasks (95.7\%).
+This suggests the model may have lacked capacity to master questions from all tasks and that training on a smaller subset allowed better performance on this subset.
+Finally, we can interestingly note for \textit{Obj-Attr} and \textit{Spatial} that training on the group A/B does not appear to help.
+When comparing with "Train on t only", we observe slight accuracy drops (around 0.3-0.5 point).
+Understanding this phenomenon warrants further investigations on the dependencies between the reasoning required by the particular questions and the transferred reasoning.
 

### 2020-02-09 Transfer_Learning/cvpr_rebuttal/egrebuttal.tex

--- 2020-02-06 Transfer_Learning/cvpr_rebuttal/egrebuttal.tex
@@
 We also improved the description of the Model based on Rev.2's recommendations.
-	\item We \textbf{added baselines} for CLEVR/CoGenT in Figure X.
+	\item We \textbf{added comparison to several baselines}: compared SAMNet with three SOTA models on CLEVR (without transfer learning) in Figure 3, on CoGenT (with transfer learning) whit the same three SOTA models in Figure 6.
+Besides, we more stronly emphasized comparison with the baseline COG model in Figures 4 and 7.
+Please not that the added results are taken from the papers, we have followed the CVPR guidelines and not performed any experiments.
 	\item We rearranged the order of \textbf{Experiments} to better align with the theoretical framework.
@@
 
+\begin{enumerate}
+\item \textbf{Ad. Ablation studies}.
+
 We agree that further ablation studies would be valuable however, per CVPR guidelines, we are not able to preform new experiments during rebuttal.
+
+\item \textbf{Ad. Reproduction and the availability of the code}.
 
@@
 
-We've added baselines to the feature transfer.
-Note that some of the transfer learning experiment settings are novel with no external baselines.
-We hope that future studies will use our methodology and compare against our model.
+\item \textbf{Ad. Performance of QA baselines}.
+
+We have significantly refined the paper and as a result it provides comparison of our model with baselines in \textbf{four} our of \textbf{six} experimental sections, each being aggregation of numerous experiments.
+The remaining \textbf{two} sets of experiments concern the novel reasoning learning setups with no existing external baselines.
+We agree that the comparison will be interesting, but sadly we haven't collected accuracies for any other model aside of SAMNet before the original submission, and CVPR police prevents us from doing so and adding them to the paper now.
+At that point we hope that future studies will use our methodology and compare against our model.
+
+Moreover, there are \textbf{no existing QA baselines} for \textbf{five}  ouf all \textbf{six} experimental setups.
+The only one available QA baseline is for the original CLEVR dataset.
+As in this case we already provided comparison with three SOTA VQA models, we decided to skip QA baseline as not introducing much.
+
+\end{enumerate}
 
@@
 \begin{enumerate}
-  \item What are $vo_tt$ and $mo_t$ and how they differ (lines 400-403)?
-What is the difference between both objects?
-\vm{$vo_t$ is the result of a retrieval operation on the content of the current input frame.
+  \item \textbf{What are $vo_tt$ and $mo_t$ and how they differ (lines 400-403)? What is the difference between both objects?}
+
+  $vo_t$ is the result of a retrieval operation on the content of the current input frame.
 $mo_t$ is the result of a similar operation on the memory content.
-The difference between both objects is thus their source.}
+The difference between both objects is thus their source.
+We have included the explanation in the revised model section.
 
-  \item How the temporal classifier $\tau_t$ is trained and used? Do you use its logits or classes directly (lines 389-397)?
-  \item What are $va_t$ and in general all other symbols. How they are computed. \vm{$va_t$ is the visual attention vector, as defined on lines 412 - 413. $va_t$ is the result of a softmax layer}.
-  \item What is pseudo-attention (line 453)?
-Why such a name?
-\vm{$w_t$ is called a pseudo-attention vector as its norm may not always be 1 (just like a probability vector), but rather vary between 0 (no change) to 1 (complete change)}.
-  \item What are reasoning operations (lines 389-391)? \vm{One iteration of the SAM Cell is considered to be a reasoning operation, as defined on lines 376 - 377}.
-  \item How many 'reasoning operations' (what is k)? \vm{8 reasoning steps, as noted on lines 532-533.}
-  \item Figure 4 shows results on CLEVR-CoGenT.
+  \item \textbf{How the temporal classifier $\tau_t$ is trained and used? Do you use its logits or classes directly (lines 389-397)?}
+
+Thank you for pointing that out.
+We have explained that in revised version of the paper.
+Directly  quoting the paper (in italics), a temporal classifier is: \textit{a two-layer feedforward network with ELU activation in the hidden layer of $d$ units.
+The output $\tau_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that reasoning step.
+For the COG dataset, we pick 4 classes to capture the terms labeled “last”, “latest”, “now”, and “none”.}
+
+  \item \textbf{What are $va_t$ and in general all other symbols. How they are computed.}
+
+  $va_t$ is the visual attention vector, the result of a softmax layer. We have explained that in the revised version of the paper.
+
+  \item \textbf{What is pseudo-attention (line 453)? Why such a name?}
+
+  $w_t$ is called a pseudo-attention vector as it (quotation from the revised paper): \textit{sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.}
+
+  \item \textbf{What are reasoning operations (lines 389-391)?}
+
+  One iteration of the SAM Cell is considered to be a reasoning operation. We have added proper explanation as part of the SAM Cell description.
+
+  \item \textbf{How many 'reasoning operations' (what is k)?}
+
+  In all our experiments we set $k=8$ reasoning steps. In order to better hightlight this we have moved that information to the beginning of the experimental section.
+
+  \item \textbf{Figure 4 shows results on CLEVR-CoGenT.
 CLEVR-CoGenT uses a transfer between objects of type A and objects of type B (e.g.
@@
 What are the results on the regular CLEVR, is it 95\% from the supp.
-material?
-\vm{The results presented in Fig 4 are reported on the condition A of CLEVR-CoGenT.
-No results are reported for CLEVR.}
-  \item Why the paper doesn't compare to other methods on CLEVR?
+material?}
+
+  We agree with the reviewer that this comparison was missing in the main paper, yet important enough to be included in it.
+Hence in the revised version of the paper we have added a new experimental section: \textbf{5.1.
+Performance of SAMNet on CLEVR}, where we present SAMNet accuracy in comparison with the three selected SOTA models.
+
+    \item \textbf{Why the paper doesn't compare to other methods on CLEVR?}
+
+	Please refer to the comment above.
+
+\end{enumerate}
+
+\section{Reviewer \#3 questions}
+
+\begin{enumerate}
+
+\item \textbf{neither the abstract, introduction, nor the related work sections identify clear contributions; what makes SAMNet novel over other nets out there?
+What was missing in previous work that SAMNet has that causes it to have better performance?
+Why is it a good thing that a new taxonomy is proposed?}
+
+ We are extremely grateful for providing this feedback.
+It motivafted us to rethink not only the contributions, but the paper as a whole.
+As w results we overhauled the abstract and  introduction to address the criticism about the contributions.
+We hope that the changes made our motivations clear.
+
+\item \textbf{the paper lacks motivation throughout.
+For example, what was the point of section 3?
+It seems like a set of definitions, but they are abstract and it's unclear what a reader is to take away from the section.}
+
+The third section introduced the taxonomy that enabled develop a holistic view on the whole Transfer Learning in Visual Reasoning and identify the uncovered areas, such as reasoning transfer.
+Besides, it enabled us to design new experiments reusing and reorganizing the existing datasets in different way.
+Still, we agree that the original submission was improperly organized, and, moreover, the experimental section wasn't properly tied with the introduced theoretical framework.
+We addressed both those issues in the revised version of the paper -- in particular, we have reorganized and rewritten the whole experimental section.
+
+\item \textbf{In Section 4 the authors describe SAMNet, but the argument was never made what was missing in existing networks that requires a new network to be proposed.
+Is the problem with previous approaches that they have limited memory, and this is what motivates SAMNet?
+Is it that the number of addresses can be changed between training and testing (and why is that a good thing)?}
+
+The size of the memory affects the training time significantly.
+Therefore, there is a big advantage if the model learns an abstract capability to use the memory independent of its size.
+This will allow to scale-up models without re-training.
+Memory along with the frame-by-frame processing of input videos make SAMNet a unique model, by definition better suited for the temporal transfer.
+
 \end{enumerate}

### 2020-02-10 Transfer_Learning/cvpr_2nd_submission/cvpr_paper_main.tex
authors
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

@@
 \usepackage{cvpr}
+\cvprfinalcopy
+
 \usepackage{times}
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+%\ifcvprfinal\pagestyle{empty}\fi
 
@@
 
+\usepackage{authblk}
+
 %%%%%%%%%%%%%%%
@@
 %%%%%%%%% TITLE
-\title{Transfer Learning in Visual and Relational Reasoning}
+\title{Transfer Learning in Visual and Relational Reasoning\vspace{-1cm}}
 
-\author{%
-	T.S. Jayram\thanks{IBM Research AI.} \and
-	Vincent Marois\footnotemark[2] \and
-	Tomasz Kornuta\thanks{NVIDIA.} \and
-	Vincent Albouy\thanks{} \and
-	Emre Sevgen\thanks{Citrine Informatics.}  \and
-	Ahmet Ozcan\footnotemark[2]
-}
+\author[1]{T.S. Jayram}
+\author[2]{Vincent Marois}
+\author[3]{Tomasz Kornuta}
+\author[ ]{Vincent Albouy\thanks{Work done while at IBM Reseach AI, Almaden Research Center}\hskip -4pt}
+\author[*]{Emre Sevgen}
+\author[1]{Ahmet Ozcan\vspace{-0.3cm}}
+\affil[ ]{$^1$IBM Research AI, Almaden Research Center, San Jose, CA, USA. $^2$IBM Research AI, Thomas J. Watson Research Center, York Town, NY, USA. $^3$NVIDIA, Santa Clara, CA, USA}
+\affil[ ]{\textit {\{jayram,  asozcan\}@us.ibm.com,  \{vincent.marois,vincent.albouy\}@ibm.com, tkornuta@nvidia.com, sesevgen@gmail.com} \vspace{-0.7cm}}
+
 %
@@
 %Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
-%{\tt\small {jayram,  asozcan}@us.ibm.com}
+%{\tt\small }
 %{\tt\small {tkornuta, sesevgen}@gmail.com}

### 2020-02-13 Transfer_Learning/arxiv_version/submission_folder/v1/related_work.tex
Cleanup for arxiv version

--- 2019-11-16 cvpr_submission/related_work.tex
@@
 \section{Related work}
-Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.
-Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
+Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015} is a challenging multimodal task that combines vision and language.
+Most Image Question Answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations.
 Prior work generally relied on dense visual features produced by either CNNs~\cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.

### 2020-02-13 Transfer_Learning/arxiv_version/experiments.tex
Title + author Figure placement
Arxiv version 2 initial commit

--- 2019-11-20 Transfer_Learning/arxiv_version/experiments.tex
@@
 \label{sec:experiments}
-We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on Pytorch~\cite{paszke2017automatic}. 
-We evaluated the model on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning, as well as on the CLEVR dataset~\cite{johnson2017clevr}, created for Image Question Answering research.
-There are 23 classification question categories in COG and the 5 original question categories in CLEVR.
-Our experiments were designed to study SAMNet's performance in terms of generalization and transfer learning abilities in different settings,
-and involved incorporating variants of both datasets.  
-For COG, the Canonical (easy) and Hard variant differ mainly on the number of frames in the video, 
-the maximum amount of look-back in frame history containing relevant information for reasoning, 
-and the number of object distractors (see~\cref{tab:cog_variants}).
-For CLEVR, we consider the CoGenT (Constrained Generalization Test) variant which contains two conditions, differing on the combinations of attribute values (details in~\cref{sec:temporal}).
-%In some of our experiments, we also compare using a \emph{zero-shot learning} approach  for transfer learning to another approach
-%involving \emph{finetuning}.
-%Recall that the former involves evaluating the trained model of the source directly on the target while for the latter we do additional lightweight 
-%training on the target labeled data before evaluating its performance. 
-\begin{table}[ht]
+% \tk{order: CLEVR + baselines without TL, COG + baseline without TL, Feature Transfer-CLEVR/CoGenT, Temporal Transfer - COG, Reasoning Transfer - CLEVR/CoGenT, Reasoning Transfer-COG}
+
+\begin{figure}[b!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../img/plots/clevr_baselines.pdf}
+	\caption{Comparison of SAMNet to baselines on CLEVR.}
+	\label{fig:clevr_baselines}
+\end{figure}
+
+We implemented and trained our SAMNet model using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}.
+We evaluated the model on
+the CLEVR dataset~\cite{johnson2017clevr}, a diagnostic dataset for Image Question Answering and on the COG dataset~\cite{yang2018dataset}, a video reasoning~\cite{mogadala2019trends} dataset developed for the purpose of research on relational and temporal reasoning.
+We briefly describe both datasets in the following two subsections.
+In all experiments, we trained SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
+When working with CLEVR, we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images. 
+Supplementary information regarding the dataset parameters and experiments can be found in the appendix.
+
+We start with an evaluation of SAMNet's performance, comparing it to baselines on both CLEVR and COG datasets, without transfer learning.
+The rest of the experiments follows the proposed taxonomy.
+We first investigate feature transfer using CLEVR-CoGenT, followed by temporal transfer on the COG variants.
+Finally, we assess the reasoning transfer capability of SAMNet on both datasets, by reorganizing groups of questions into new training and test splits.
+
+\begin{figure*}[!t]
+	\centering
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../img/plots/cog_canonical_baseline_no_labels.pdf}
+	\end{subfigure}%
+	\newline
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../img/plots/cog_hard_baseline_labels.pdf}
+	\end{subfigure}%
+	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the baseline model~\cite{yang2018dataset} (dotted gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+	\label{fig:samnet_cog_detailed}\vspace{-10pt}
+\end{figure*}
+
+\subsection{Performance of SAMNet on CLEVR}
+\label{sec:clevr-baseline-compare}
+CLEVR images contain objects characterized by a set of attributes (shape, color, size and material).
+The questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, CoGenT-A and CoGenT-B, with varying combinations of color-shape attributes.
+The colors are partitioned into two complementary families:
+Gray, Blue, Brown and Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (See~\cref{tab:cogent_conditions}).
+As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
+
+\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
+SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.
+
+\subsection{Performance of SAMNet on COG}
+\label{sec:cog-baseline-compare}
+
+COG dataset contains short videos, with associated questions grouped into 23 categories~\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
+COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
+Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
+description of tasks, as shown in~\cref{fig:task-groups}.
+
+\begin{table}[htbp]
 	\centering
@@
 	\label{tab:cog_variants}
-\end{table}\vspace{5pt}
+\end{table}
 
-%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.
-
-\subsection{Performance of SAMNet vs baseline model~\cite{yang2018dataset}}
-\label{sec:cog-baseline-compare}
-
-We trained SAMNet using 8 reasoning steps and external memory of 8 address locations, each storing an array of 128 floats. 
-%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
-We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.
-
-\begin{figure*}[htb]
+\begin{figure}[b!]
 	\centering
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
-	\end{subfigure}%
-	\newline
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_hard.png}
-	\end{subfigure}%
-	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
-		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-	\label{fig:samnet_cog_detailed}
-\end{figure*}
-
-For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, 
-compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better 
-accuracy due to its ability to selectively pick and store relevant objects from the past frames in memory.
-For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating
-that our model can adapt to larger number of frames and distractors.
-Despite there being some tasks in the Canonical variant where SAMNet achieved slightly lower accuracies,
-% (between 0.2 and 1.8 points)
-when comparing performances on the Hard variant, it improves upon the baseline model on all tasks, 
-with improvements varying from 0.5 to more than 30 points, and especially on the more complex tasks in the dataset.
-
-\subsection{Reasoning transfer on CLEVR and COG}
-\label{sec:reasoning}
-In these experiments using the CLEVR and COG datasets, we focus on analyzing the impact 
-of each task relative to others using appropriate groupings of tasks.
-%For each dataset, we defined appropriate task families that reflect the characteristics of that dataset and designed
-%appropriate experiments to study the effectiveness of transfer learning across task families.
-
-\subsubsection{CLEVR}
-\label{sec:reasoning-clevr}
-For the CLEVR dataset, we consider the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-For performance reasons, we deactivated the external memory and temporally-related modules in SAMNet as they are unnecessary while reasoning about static images.
-We conduct the following experiments:
-\begin{itemize}
-	\item Train and test SAMNet on a single task group $t$. These 5 experiments fit into the traditional ML setup of single-task learning;
-	\item Train SAMNet on all task groups jointly and evaluate its performance on each task group $t$ separately.
-	This is a transfer learning setting where for the source task family, the task is sampled from all questions,
-	while for the target task family, the samples consist of questions from group $t$ only;
-	\item Finally, for each task group $t$, we train SAMNet on all tasks but $t$, and test its performance on $t$.
-	This can also be viewed as a transfer learning setting similar to the previous case.
-	%These experiments steer away from single / multi-task training and rather fall under the Domain Adaptation setting, categorized as \emph{transductive} transfer learning in \cite{pan2009survey}.
-\end{itemize}
-
-Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../results/CoGenT_results.pdf}
-	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
-	\label{fig:CoGenT-results}
-\end{figure}
-
-Looking at~\cref{fig:CoGenT-results}, SAMNet does well on \textit{Count} and \textit{QueryAttribute}, but poorer on the 3 other tasks in the single-task learning setting (blue).
-Indeed, \textit{Exist}, \textit{CompareInteger} and \textit{CompareAttribute} are binary tasks; \textit{Count} has output labels digits 0 through 10 (so $<$10\% accuracy by chance) and \textit{QueryAttribute} maps to the set of object-attribute values (15 labels).
-
-Nevertheless, significant accuracy gains are noted when training jointly on all tasks (gray), ranging from 18 points to 37 points on 4 out of 5 tasks.
-These improvements suggest that related tasks benefit from joint training.
-\textit{QueryAttribute} only sees an increase of one point.
-One could qualify it as \textit{self-sufficient} as it does not appear to benefit from joint training with other tasks.
-%We plan to run additional experiments to jointly train on $t$ and all possible subsets of the remaining 4 tasks ($2^4$ experiments per task).
-We hypothesize that the improvements on e.g.
-\textit{Exist} would mostly originate from training jointly on \textit{CompareAttribute} and \textit{CompareInteger} since all 3 tasks share the same output space (i.e., labels domain).
-
-Finally, the ``all-tasks-but-$t$'' experiments (yellow) demonstrate that while tasks are related, one does not subsume another in terms of learning.
-Indeed, we can observe that for \textit{CompareAttribute}, while \textit{Exist} and \textit{CompareInteger} share the same output space, including them and holding out \textit{CompareAttribute} from the training set results in poor accuracy.
-We also observe no learning for \textit{Count} and \textit{QueryAttribute}. As these categories have labels that do not overlap with other categories, the model cannot predict these labels.
-
-An additional set of experiments, for which results are available in the supplementary material,
-%Appendix \ref{sec:full-cogent-results}
-fine-tune the model trained on all tasks on each task $t$ respectively.
-%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the fine-tuned task and the drop, if any, on other tasks.
-Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
-Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
-
-\subsubsection{COG}
-\label{sec:reasoning-cog}
-Since the number of task classes (=23) in the COG dataset is large, we designed a 2-level hierarchy of task groups using the
-description of these tasks, as shown in~\cref{fig:task-groups}.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../img/architecture/hierarchy}
-	\caption{Hierarchy of Task Groups.}
+	\includegraphics[width=\textwidth]{../img/architecture/hierarchy}
+	\caption{Hierarchy of Task Groups in the COG dataset.}
 	\label{fig:task-groups}
 \end{figure}
-
-\bigskip
 
@@
 
-\begin{figure}[!t]
+We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.
+
+For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
+As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in its external memory.
+For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
+SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex tasks (\textit{AndCompare}\uX, \textit{Compare}\uX).
+
+\subsection{Feature transfer using CLEVR-CoGenT}
+\label{sec:feature}
+
+In order to quantify SAMNet's feature transfer ability, we used the CoGenT variants of CLEVR and performed a set of experiments, starting from training on CoGenT-A, followed by:
+an immediate test (zero-shot learning) on CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following the methodology used in~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+In \cref{fig:CoGenT-B-results}, we compare the achieved performance with the previously selected SOTA models.
+We also consider a direct test on CoGenT-A; and a test on CoGenT-A after fine-tuning on B.
+
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=0.85\textwidth]{../results/COG_reasoning_transfer_v3}
-	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
-	\label{fig:COG-reasoning-results}
+	\includegraphics[width=\textwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
+	\caption{Feature transfer: test accuracies when transferring between CoGenT-A and CoGenT-B.}
+	\label{fig:CoGenT-B-results}
 \end{figure}
 
-We then conducted the following experiments using the Canonical variant of COG to study 
-whether transfer learning was effective in leveraging information gained by training a task family at a higher level
-of the hierarchy:
- \begin{itemize}
-	\item Train and test SAMNet on each of the 5 task groups at the lowest level of the hierarchy (Single-task training);
-	\item Jointly train on:
-	\begin{itemize}
-		\item 	 \textbf{Group A} and test on each task from the lowest groups (i.e. \textbf{Basic}, \textbf{Obj-Attr} and \textbf{Compare}) separately;
-		\item \textbf{Group B} and test separately on \textbf{Spatial} and \textbf{Cognitive};
-	\end{itemize}
-	\item As a baseline, we compared the above results to the earlier experiment shown in~\cref{fig:samnet_cog_detailed}, which
-	can be viewed as training jointly on \textbf{All} and testing on each group at the leaf level separately (All-task training).
-\end{itemize}
-
-The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
-
-First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive tasks and therefore do not benefit from training with other task families.
-With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
-Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
-The former saw an accuracy jump from 68.6\% by training on samples from that family alone
-to 97.0\% when training on all samples. To further emphasize this behavior, notice that 
-just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
-In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed
-of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
-Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
-is a slight loss incurred by including everything.
-As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%).
-To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.
+When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, matching the results observed in \cref{sec:clevr-baseline-compare}.
+When zero-shot testing on CoGenT-B, all models show relatively good performance (around 75\%), which represents nonetheless a drop of 17 points with respect to CoGenT-A.
+All models perform better when fine-tuned on CoGenT-B.
+However, this process also results in a degradation of performance on CoGenT-A, with SAMNet and TbD showing an ability to limit this drop in accuracy.
+While this suggests both models were able to adapt representations for both domains, these representations are not fully disentangled.
 
@@
 
-The goal here is to test the transfer learning ability concerning the frame sequence length, frame history required
-for reasoning, and the number of object distractors.
-For that purpose, we compare both models when trained on the Canonical variant but tested on the 
-Hard variant (\cref{fig:samnet_cog_overall_transfer}).
-The light gray color indicates original accuracies of the baseline model from paper, 
-whereas dark gray indicates accuracies of the baseline model
-obtained by running the original code provided by the authors~\cite{yang2018implement}.
+Temporal transfer tests the transfer learning ability regarding the frame sequence length, frame history required for reasoning, and the number of distracting objects.
+Therefore, we train the models on the Canonical variant of COG dataset and test them on the Hard variant~(\cref{fig:samnet_cog_overall_transfer}).
+As the original paper~\cite{yang2018dataset} didn't provide such experiments, we supplement the original accuracies (denoted as gray-dotted) with the ones achieved by the COG baseline model that we have obtained by running the original code (gray-striped) provided by the authors~\cite{yang2018implement}.
 
-The first column displays the scores of the traditional ML setup when training and testing on the Canonical variant. 
-The observed close scores in light and dark gray underscore the baseline model reproducibility.
-For both cases of zero-shot learning (second column--91.6\% vs 65.9\%) and fine-tuning using a single epoch 
-(third column--96.7\% vs. 78.1\%), SAMNET outperforms the baseline model significantly.
-Interestingly, this fine-tuning yields a mild boost of +0.6\% on the earlier reported accuracy 
-in~\cref{sec:cog-baseline-compare} (fourth column).
-These results suggest that it suffices to train SAMNet on simpler videos 
-to enable learning of good memory usage and attention on relevant entities  
-in order to achieve comparable, if not better, 
-performance on longer video frames with more complex scenes.
-
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=0.8\textwidth]{../results/samnet_cog_overall_transfer.png}
-	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
+	\includegraphics[width=\textwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
+	\caption{Temporal transfer capabilities of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard  in COG.}
 	\label{fig:samnet_cog_overall_transfer}
@@
 
-\subsection{Feature transfer on CLEVR-CoGenT}
-\label{sec:feature}
-\begin{table}[ht]
-	\centering
-	%\begin{adjustbox}{width=0.45\textwidth}
-		\begin{tabular}{cccc}
-			\toprule
-			Dataset	& Cubes	& Cylinders &	Spheres	\\
-			\midrule
-			CoGenT A &  Family A  & Family B 	&	Any color  \\
-			CoGenT B	&	Family B  &	Family A	&	Any color \\
-			\bottomrule
-		\end{tabular}
-	%\end{adjustbox}
-	\caption{Restrictions on feature combinations in A \& B conditions of the CoGenT variant of the CLEVR dataset.}
-	\label{tab:cogent_conditions}
-\end{table}
+The first column displays the aggregated scores when training and testing on the Canonical variant.
+The close scores of both base models (gray striped and dotted) highlight the faithful reproduction of the baseline model.
+For both cases of zero-shot learning and fine-tuning using a single epoch, SAMNET significantly outperformed the baseline model, by 25 and 17 points respectively.
+This might partially results from the frame-by-frame processing of videos executed by SAMNet by design, as opposed to the processing of aggregated frames performed by the baseline.
+Interestingly, fine-tuning yields a mild boost of +0.6\% on the accuracy achieved by the model trained exclusively on the Hard variant.
+This suggests that SAMNet managed to develop elementary skills (such as memory usage and attention on relevant entities) and successfully uses them when dealing with longer videos and more complex scenes.
 
-The final set of experiments we consider is related to feature transfer.
-The CoGenT-A \& -B variants of CLEVR differ by the available combinations of 8 object color-attributes.
-The colors are partitioned into two complementary families: 
-Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations while the spheres can take any color (See~\cref{tab:cogent_conditions}). 
-As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
-We conduct 2 experiments with SAMNet trained on CoGenT-A:
-\begin{itemize}
-\item an immediate test (zero-shot learning) from A to B; and 
-\item fine-tuning for a single epoch on 30k samples from CoGenT-B (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
-\end{itemize}
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../results/CoGenT_B_results.pdf}
-	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
-	\label{fig:CoGenT-B-results}
-\end{figure}
-
-Performance of SAMNet on CoGenT (\cref{fig:CoGenT-B-results}) is clearly worse on CoGenT-B than CoGenT-A.
-Fine-tuning for a single epoch allows an observable increase of 15 pts on CoGenT-B, and a slight drop on CoGenT-A.
-Both are consistent with findings from the literature~\cite{johnson2017inferring, mascharka2018transparency, perez2018film}.
+%This suggest that it suffices to train SAMNet on simpler videos to enable learning of good memory usage and attention on relevant entities in order to achieve comparable, if not better, performance on longer video frames with more complex scenes.

### 2020-02-13 Transfer_Learning/arxiv_version/experiments_reasoning_transfer.tex
Arxiv version 2 initial commit

--- 2020-02-09 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
+	\includegraphics[width=\textwidth]{../img/plots/cogent_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
+	\includegraphics[width=\textwidth]{../img/plots/cog_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}

### 2020-02-13 Transfer_Learning/arxiv_version/introduction.tex
Minor changes
Arxiv version 2 initial commit

--- 2019-11-16 cvpr_submission/introduction.tex
@@
 %dummy
-In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
-At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e.\ sampled from a common input space under similar data distribution characteristics.
+In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural}, among others.
+Neural networks, being statistical models~\cite{ripley1993statistical,warner1996understanding}, rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}).
 However, in many real-world scenarios, this assumption does not hold.
 Moreover, as modern neural models often have millions of trainable parameters, training them requires vast amounts of data, which for some domains (e.g., medical) can be very expensive and/or extremely difficult to collect.
-One of the widely used solutions for the above mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances model performance by transferring \emph{information} from one domain to another.
+One of the widely used solutions is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances model performance by transferring \emph{information} from one domain to another.
 
-%pan2009survey: we categorize transfer learning under three sub-settings: inductive transfer learning, transductive transfer learning and unsupervised transfer learning,
+In this work we focus on transfer learning in multi-modal reasoning tasks combining vision and language~\cite{mogadala2019trends}.
+Recently introduced visual reasoning datasets, such as ~\cite{johnson2017clevr,yang2018dataset,song2018explore}, attempt to probe the generalization capabilities of models under various scenarios, trying to quantify the visual complexity of the scene or the compositional complexity of the question.
+While these datasets seem to be well suited for transfer learning, they do not tackle that issue directly.
+In particular, \cite{johnson2017clevr} introduces the CLEVR dataset along with two variants (CoGenT-A and -B) with varying combinations of visual attributes.
+Similarly, COG \cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants (Canonical and Hard) with different number of frames and scene complexity.
+Both datasets come with a number of task classes that require similar reasoning abilities (e.g. compare or count objects).
+The open question we address in this paper is whether we can build a neural architecture that fosters transfer learning and generalizes from simpler to more complex reasoning tasks.
 
-In Computer Vision, it is now standard practice to pretrain an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as segmentation of cars~\cite{iglovikov2018ternausnet} or Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging}.
-Such performance improvements are appealing, especially in cases where both the domain (natural vs.
-medical images) and the task (image classification vs.
-image segmentation vs VQA) change significantly.
-%This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.
-
-Similar developments have emerged in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, has become a standard procedure when working with different NLP domains and tasks.
-Recently, there is a clear, growing trend of utilization of deep contextualized word representations such as ELMo~\cite{peters2018deep} (based on bidirectional LSTMs~\cite{hochreiter1997long}) or BERT~\cite{devlin2018bert} (based on the Transformer~\cite{vaswani2017attention} architecture), where entire deep networks (not just the input layer) are pretrained on very large corporas.
-In analogy to pretrained image encoders, the NLP community has also started to create model repositories, some with dozens of pretrained models ready to be downloaded and used.
-HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.
-
-The success of transfer learning raises several research questions, such as the characteristics which make a dataset more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
-One of the most systematic works in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aimed at discovering the dependencies between twenty-six 2D, 2.5D, 3D, and semantic computer vision tasks.
-
-In this work we focus on transfer learning in multi-modal tasks combining vision and language~\cite{mogadala2019trends} .
-More precisely, we narrow the scope to transfer learning between visual reasoning tasks that have a ``nice'' logical structure, e.g.,~\cite{johnson2017clevr,yang2018dataset,song2018explore}. 
-While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
-once the modalities have been fused.
-For example, the CoGenT (Constrained Generalization Test) variant of the CLEVR~\cite{johnson2017clevr}  
-contains two datasets with similar questions, but differing on combinations of object-attribute values in images 
-(\cref{sec:feature}).
-In this case, training on the first variant might yield entangled feature representations that may fail reasoning tasks
-on the second one.
-In video reasoning, an additional challenge in the temporal dimension is whether a model trained on shorter video sequences will 
-transfer over to longer ones, e.g., the Canonical and the Hard variants of the 
-COG dataset~\cite{yang2018dataset} (\cref{sec:temporal}).
-To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
-and external memory~\cite{graves2014neural, graves2016hybrid,weston2014memory} 
-which facilitate higher-level abstractions, seem more promising.
-
-\smallskip
-
-\noindent Motivated by these considerations:
+\noindent The contributions of this paper are the following:
 %Consequently:
@@
 	%\compresslist
-	\item We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
-	\item We propose a taxonomy of transfer learning, inspired from~\cite{pan2009survey}, applied to the domain of visual reasoning.
-Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
-	\item Subsequently, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer.
-This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants.
-Several of these experiments show significant transfer learning capabilities of SAMNet.
+	\item We introduce a new model called SAMNet (Selective Attention Memory Network).
+	The unique features of SAMNet include the dynamic processing of video input frame-by-frame, multi-step reasoning over a given image and remembering the relevant concepts.
+	\item We propose a taxonomy of transfer learning to highlight new research directions, identify missing areas and encourage new datasets for transfer learning in visual reasoning.
+We evaluate the CLEVR/CoGenT and COG tasks to show how they map onto the proposed theoretical framework.
+	\item We perform an extensive set of experiments, comparing our model with baselines on the existing tasks, achieving state-of-the-art results on COG~\cite{yang2018dataset}.
+We also designed two new tasks for reasoning transfer and show that the design of SAMNet promotes transfer learning capabilities and generalization.
+
 \end{enumerate}

### 2020-02-13 Transfer_Learning/arxiv_version/related_work.tex
Arxiv version 2 initial commit

--- 2020-02-09 Transfer_Learning/cvpr_2nd_submission/related_work.tex
@@
 Similar developments have emerged in the Natural Language Processing (NLP) community.
-Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, was de facto a standard procedure accross different NLP domains and tasks for the last several years.
+Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, has been a standard procedure across different NLP domains and tasks.
 Recently, there is a clear, growing trend of utilization of deep contextualized word representations such as ELMo~\cite{peters2018deep} (based on bidirectional LSTMs~\cite{hochreiter1997long}) or BERT~\cite{devlin2018bert} (based on the Transformer~\cite{vaswani2017attention} architecture), where entire deep networks (not just the input layer) are pretrained on very large corporas.
@@
 
-Visual Reasoning tasks combining both the visual and language modalities~\cite{mogadala2019trends} naturally draw from those findings by reusing the pretrained image and word/question encoders.
-The community also seems to be realising that the models should not only be able to generalize on the low-level image features, but also on the performed high-level, abstract \textit{reasoning}.
-First notable attemp to establish a framework enabling transfer learning of reasoning skill was CLEVR~\cite{johnson2017clevr} with its two CoGenT variants.
-As a result several interesting works appeared~\cite{mascharka2018transparency, perez2018film, johnson2017inferring,marois2018transfer}, proposing models trying to cope with transfer from one to the other domain with different distributions of visual attribute combinations.
-Similarly, the baseline model introduced along with the COG dataset~\cite{yang2018dataset} have shown that it can do significantly better answer questions belonging to task classes not being explicitly trained on when leveraging knowledge learned on other tasks.
+Visual Reasoning tasks, combining both the visual and language modalities~\cite{mogadala2019trends}, naturally draw from those findings by reusing the pretrained image and word/question encoders.
+Ensuring models can generalize on high-level, abstract \emph{reasoning} has been a recent interest of the community.
+The first attempt at establishing a framework enabling transfer learning of reasoning skills was CLEVR~\cite{johnson2017clevr} with its two CoGenT variants.
+This fostered research~\cite{mascharka2018transparency, perez2018film, johnson2017inferring,marois2018transfer}, proposing models designed to transfer from one domain to another, with different distributions of visual attribute combinations.
+Similarly, the baseline model introduced alongside the COG dataset~\cite{yang2018dataset} has shown the ability to solve tasks not explicitly trained on, by leveraging knowledge learned on other tasks.
+
 These results clearly indicate the usefulness of transfer learning, despite the assumption of similar distributions between the source and target domains not being respected.
-At the same time transfer learning several research questions, such as the characteristics which make a whole dataset or a particular task more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
+Conjointly, transfer learning raises several research questions, such as the characteristics which make a whole dataset or a particular task more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
 One of the most systematic works in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies between twenty-six different computer vision tasks.
-In this work we extend that idea further and introduce a taxonomy enabling us to isolate and quantify different aspects of visual reasoning on the performance of our model.
+In this work, we extend this idea further and introduce a taxonomy allowing us to isolate and quantify different aspects of visual reasoning.
 %We illustrate it with the two above mentioned CLEVR and COG datasets.

### 2020-02-13 Transfer_Learning/arxiv_version/samnet.tex
Rearranging folders and references
Arxiv version 2 initial commit

--- 2019-11-20 Transfer_Learning/cvpr_submission/samnet.tex
@@
 %All those modules are described below.
+%\ao{Method: Start high level, how different modules interface each other, and what the motivation is for each such a module.
+Then it should define standard parts such as attention over questions, and introduce all the variables that appear from nowhere.
+I would also like to see a more clear Figure 2 depicting the architecture.
+There is very little correspondence between that figure and the equations used in the paper.}
 
-SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
+SAM Network (SAMNet) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
 iterative reasoning as proposed e.g.
 in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and use of an external memory, as in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/SAMNETmodel}
+	\caption{General architecture of SAMNet.}
+	\label{fig:samnet}\vspace{-10pt}
+\end{figure*}
 
@@
 
-SAMNet's core is a recurrent cell called the SAM Cell.
+\smallskip
+
+\noindent\textbf{Input Units.}
+The input to SAMNet consists of a question component and a visual component that is either a single frame in case of a static image or a sequence of frames in case of a video.
+The question is represented as a sequence of word embeddings (either one-hot or preprocessed by GloVe~\cite{pennington2014glove}) corresponding to words in the question.
+Each frame of the visual input is encoded using raw pixels or preprocessed by a pre-trained deep network such as RESNet~\cite{he2016deep}.
+The language input of $L$ word embeddings is processed by a Bi-LSTM based question encoder that produces \emph{contextual words} $\vec{cw} \in \Reals^{L \times d}$.
+The final states in either direction of the BI-LSTM are also concatenated and passed through a linear layer to produce a global representation of the question 
+$\vec{q} \in \Reals^d$, called the \emph{question embedding}.
+The $k$-th frame of the visual input, where $k$ indexes over the frames in temporal order, is processed by an image encoder---a CNN with appropriately chosen number of layers---to produce a \emph{feature map}
+$\vec{F}_k \in \Reals^{H \times W \times d}$.
+
+\smallskip
+
+\noindent\textbf{The SAM Cell.} The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell.
 Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{img/architecture/SAMNETmodel}
-	\caption{General architecture of SAMNet.}
-	\label{fig:samnet}
-\end{figure*}
+\smallskip
 
-\noindent{\textbf{Question-driven Controller.}}
+\noindent\textbf{Question-driven Controller.}
 This module drives attention over the question to produce $k$ control states, one per reasoning operation.
@@
 
-\noindent{\textbf{Memory Update Unit.}}
+\smallskip
+
+\noindent\textbf{Memory Update Unit.}
 The unit first determines the memory location where an object could be added:
-\[ \vec{w}_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
+\[ \vec{w}_t = \doreplace_t \cdot \rhead_t + \doadd_t \cdot \whead_{t-1} \]
 Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
 $\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
-We then update the memory accordingly as:
+We then update the memory accordingly:
 \[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t,\]
@@
 Then:
-\[ \whead_t = \doadd \cdot \whead'_{t-1} + (1-\doadd) \cdot \whead_{t-1} \]
+\[ \whead_t = \doadd_t \cdot \whead'_{t-1} + (1-\doadd_t) \cdot \whead_{t-1} \]
 
-\noindent{\textbf{Summary Update Unit.}}
+\begin{figure*}[htbp]
+	\centering
+	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
+	\caption{Transfer learning taxonomy.}
+	\label{fig:taskonomy}\vspace{-10pt}
+\end{figure*}
+
+\noindent\textbf{Summary Update Unit.}
 %\paragraph{Summary Update Unit.}

### 2020-02-13 Transfer_Learning/arxiv_version/summary.tex
Arxiv version 2 initial commit

--- 2020-02-08 Transfer_Learning/cvpr_2nd_submission/summary.tex
@@
 To capture and quantify the influence of transfer learning on visual reasoning, we proposed a new taxonomy, articulated around three aspects: feature, temporal and reasoning transfer.
-That enabled us to reuse the existing datasets for image and video QA, namely CLEVR and COG, and isolate splits capturing the reasoning transfer.
-We note that some of the proposed splits form tasks (e.g. Train on all but \textit{t}) that are complementary to well established ones in the literature, e.g. in Taskonomy~\cite{zamir2018taskonomy}.
+This enabled us to reuse the existing datasets for image and video QA, namely CLEVR and COG, and isolate splits better capturing reasoning transfer.
+We note that some of the proposed splits form tasks (e.g. Train on all but \textit{t}) which are complementary to well established ones in the literature, e.g. in Taskonomy~\cite{zamir2018taskonomy}.
 

### 2020-02-13 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Submitted files to arxiv in a single folder
Margin
Arxiv version 2 initial commit
Fixed author affiliations and added new abstract

--- 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
@@
+\RequirePackage{snapshot}
+
 \documentclass[11pt]{article}
@@
 \usepackage[letterpaper,margin=1in]{geometry}
+\usepackage[auth-sc,affil-sl]{authblk}
 \usepackage{times}
@@
 
+\usepackage[hyperpageref]{backref}
 \usepackage{cleveref}
@@
 % WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
-\author{%
-T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
-Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
-Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
-\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
-Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
-Ahmet S. Ozcan\footnotemark[1] \and \\
-IBM Research AI
+%\author{%
+%T.S. Jayram\thanks{\textit{IBM Almaden Research Center, San Jose, CA, USA}.} \hspace{1.5cm} \and  
+%Vincent Marois\thanks{\textit{IBM Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1.5cm} \and 
+%Tomasz Kornuta\thanks{Currently at NVIDIA. \textit{Santa Clara, CA, USA}.}  \and
+%\hspace{1cm} Vincent Albouy\footnotemark[1]  \hspace{1.5cm} \and 
+%Emre Sevgen\thanks{Currently at Citrine Informatics.}  \hspace{1.5cm} \and 
+%Ahmet S. Ozcan\footnotemark[1] \and \\
+%{\large IBM Research AI}
+%}
+
+\newcommand\blfootnote[1]{%
+	\begingroup
+	\renewcommand\thefootnote{}\footnote{#1}%
+	\addtocounter{footnote}{-1}%
+	\endgroup
 }
+
+\renewcommand\Authands{ and }
+\author[1]{T.S. Jayram}
+\author[2]{Vincent Marois}
+\author[3]{Tomasz Kornuta}
+\author[ ]{Vincent Albouy\thanks{Work done while at IBM Research AI, Almaden Research Center}}
+\author[*]{\\Emre Sevgen}
+\author[1]{Ahmet Ozcan}
+\affil[1]{IBM Research AI, Almaden Research Center, San Jose, CA, USA.}
+\affil[2]{IBM Research AI, Thomas J. Watson Research Center, Yorktown, NY, USA.}
+\affil[3]{NVIDIA, Santa Clara, CA, USA}
 
@@
 \maketitle
+\blfootnote{E-mail: {\scriptsize \textit{\{jayram,asozcan\}@us.ibm.com,  \{vincent.marois,vincent.albouy\}@ibm.com, tkornuta@nvidia.com, sesevgen@gmail.com}}}
 
@@
 \begin{abstract}
-  Transfer learning is becoming the de facto solution for vision and text encoders in the front-end processing of machine learning solutions.
-Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited.
-In this paper, we analyze the efficiency of transfer learning in visual reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.
-Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline.
-We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer.
-Based on extensive experimentation of transfer learning on each of the two datasets, we show the performance of the new model along each axis.
+	Transfer learning has become the de facto standard in computer vision and natural language processing, especially where labeled data is scarce.
+Accuracy can be significantly improved by using pre-trained models and subsequent fine-tuning.
+In visual reasoning tasks, such as image question answering, transfer learning is more complex.
+In addition to transferring the capability to recognize visual features, we also expect to transfer the system’s ability to reason.
+Moreover, for video data, temporal reasoning adds another dimension.
+In this work, we formalize these unique aspects of transfer learning and propose a theoretical framework for visual reasoning, exemplified by the well-established CLEVR and COG datasets.
+Furthermore, we introduce a new, end-to-end differentiable recurrent model (SAMNet), which shows state-of-the-art accuracy and better performance in transfer learning on both datasets.
+The improved performance of SAMNet stems from its capability to decouple the abstract multi-step reasoning from the length of the sequence and its selective attention enabling to store only the question-relevant objects in the external memory.
 \end{abstract}
 
+%%%%%%%%% BODY TEXT
 %%%%%%%%% BODY TEXT
@@
 
+\input{samnet}
+
 \input{transfer_learning}
 
-\input{samnet}
-
 \input{experiments}
+\input{experiments_reasoning_transfer}
 

### 2020-02-13 Transfer_Learning/arxiv_version/experiments.tex
Tried resizing figures. Not perfect but ok

@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../img/plots/clevr_baselines.pdf}
+	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
 	\caption{Comparison of SAMNet to baselines on CLEVR.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/architecture/hierarchy}
+	\includegraphics[width=0.7\textwidth]{../img/architecture/hierarchy}
 	\caption{Hierarchy of Task Groups in the COG dataset.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
+	\includegraphics[width=0.9\textwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
 	\caption{Feature transfer: test accuracies when transferring between CoGenT-A and CoGenT-B.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
+	\includegraphics[width=0.9\textwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
 	\caption{Temporal transfer capabilities of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard  in COG.}

### 2020-02-13 Transfer_Learning/arxiv_version/experiments_reasoning_transfer.tex
Tried resizing figures. Not perfect but ok

@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/plots/cogent_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\textwidth]{../img/plots/cogent_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../img/plots/cog_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\textwidth]{../img/plots/cog_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}

### 2020-02-14 Transfer_Learning/arxiv_version/submission_folder/v2/experiments.tex
arxiv v2 submission files

--- 2020-02-13 Transfer_Learning/arxiv_version/experiments.tex
@@
 % \tk{order: CLEVR + baselines without TL, COG + baseline without TL, Feature Transfer-CLEVR/CoGenT, Temporal Transfer - COG, Reasoning Transfer - CLEVR/CoGenT, Reasoning Transfer-COG}
-
-\begin{figure}[b!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
-	\caption{Comparison of SAMNet to baselines on CLEVR.}
-	\label{fig:clevr_baselines}
-\end{figure}
 
@@
 When working with CLEVR, we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images. 
-Supplementary information regarding the dataset parameters and experiments can be found in the appendix.
+Additional information regarding the dataset parameters 
+can be found in~\cref{sec:datasets-desc}.
 
@@
 Finally, we assess the reasoning transfer capability of SAMNet on both datasets, by reorganizing groups of questions into new training and test splits.
-
-\begin{figure*}[!t]
-	\centering
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../img/plots/cog_canonical_baseline_no_labels.pdf}
-	\end{subfigure}%
-	\newline
-	\begin{subfigure}{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../img/plots/cog_hard_baseline_labels.pdf}
-	\end{subfigure}%
-	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the baseline model~\cite{yang2018dataset} (dotted gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-	\label{fig:samnet_cog_detailed}\vspace{-10pt}
-\end{figure*}
 
@@
 
-\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
+\Cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected state-of-the-art models: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
 SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.
+
+\begin{figure}[hbtp]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
+	\caption{Comparison of SAMNet to baselines on CLEVR.}
+	\label{fig:clevr_baselines}
+\end{figure}
 
@@
 
-COG dataset contains short videos, with associated questions grouped into 23 categories~\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
+COG dataset contains short videos, with associated questions grouped into 23 categories\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
 COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
-Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
-description of tasks, as shown in~\cref{fig:task-groups}.
 
@@
 
-\begin{figure}[b!]
+Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
+description of tasks, as shown in~\cref{fig:task-groups}.
+
+\begin{figure}[hbtp]
 	\centering
@@
 
-We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.
+We compared our results with the baseline model introduced in~\cite{yang2018dataset}, the same paper as the COG dataset.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in~\cref{sec:cog-all-results}.
+
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../img/plots/cog_canonical_baseline_no_labels.pdf}
+	\end{subfigure}%
+	\newline
+	\begin{subfigure}{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../img/plots/cog_hard_baseline_labels.pdf}
+	\end{subfigure}%
+	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the baseline model~\cite{yang2018dataset} (dotted gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
+	\label{fig:samnet_cog_detailed}\vspace{-10pt}
+\end{figure}
 
@@
 an immediate test (zero-shot learning) on CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following the methodology used in~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
-In \cref{fig:CoGenT-B-results}, we compare the achieved performance with the previously selected SOTA models.
-We also consider a direct test on CoGenT-A; and a test on CoGenT-A after fine-tuning on B.
+In \cref{fig:CoGenT-B-results}, we compare the achieved performance with the previously selected state-of-the-art models.
+We also consider a direct test on CoGenT-A; and a test on CoGenT-A after fine-tuning on CoGenT-B.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[b!]
 	\centering
-	\includegraphics[width=0.9\textwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
+	\includegraphics[width=0.8\textwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
 	\caption{Temporal transfer capabilities of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard  in COG.}

### 2020-02-14 Transfer_Learning/arxiv_version/submission_folder/v2/experiments_reasoning_transfer.tex
arxiv v2 submission files

--- 2020-02-13 Transfer_Learning/arxiv_version/experiments_reasoning_transfer.tex
@@
 We first trained a single SAMNet instance on CoGenT-A and measured its accuracy on each of the task group $t$ separately.
-Those results, indicated in \cref{fig:cogent_reasoning_transfer} as "Train on All", serve as baselines for the next two sets of experiments.
+Those results, indicated in \cref{fig:cogent_reasoning_transfer} as ``Train on All'', serve as baselines for the next two sets of experiments.
 
-We next trained and tested 5 SAMNet instances, each on a single task group $t$ ("Train on t only").
+We next trained and tested 5 SAMNet instances, each on a single task group $t$ (``Train on t only'').
 We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, aside of \textit{Query Attribute}.
@@
 As expected, this setup appears challenging, causing severe performance drops, with accuracy on \textit{Count} and \textit{QueryAttribute} dropping to zero.
-This stems from the non-overlapping labels spaces of \textit{Count} (digits 0 to 9) and \textit{QueryAttribute} (all attributes names) with the other groups (binary "yes" / "no").
+This stems from the non-overlapping labels spaces of \textit{Count} (digits 0 to 9) and \textit{QueryAttribute} (all attributes names) with the other groups (binary ``yes'' / ``no'').
 Thus, the model cannot predict these labels in a zero-shot transfer.
@@
 \label{sec:reasoning-transfer-cog}
-In order to further investigate whether reasoning transfer is effective in leveraging information gained by training a task family at a higher level of the hierarchy, we also conducted a set of experiments using the Canonical variant of COG.
-The order of the performed experiments is analogical to the one in the previous section.
-The first column (\cref{fig:cog_reasoning_transfer}, "Train on All") is the baseline, i.e.
-we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
-Please note that these results are weighted averages of the accuracies of our model on the Canonical variant tasks (\cref{fig:samnet_cog_detailed}).
-
-\begin{figure}[htbp]
+\begin{figure}[b!]
 	\centering
@@
 
-Next, we experimented with the "Train on t only" setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. single leaf of the proposed hierarchy).
-For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the baseline ("Train on All"), suggesting that each group contain sufficient information for developing all necessary skills.
+In order to further investigate whether reasoning transfer is effective in leveraging information gained by training a task family at a higher level of the hierarchy, we also conducted a set of experiments using the Canonical variant of COG.
+The order of the performed experiments is analogical to the one in the previous section.
+In~\cref{fig:cog_reasoning_transfer}, the first bar in each cluster, ``Train on All'', is the baseline, i.e.
+we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
+Note that these results are weighted averages of the accuracies of our model on the Canonical variant tasks (\cref{fig:samnet_cog_detailed}).
+
+Next, we experimented with the ``Train on t only'' setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. single leaf of the proposed hierarchy).
+For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the baseline (``Train on All''), suggesting that each group contain sufficient information for developing all necessary skills.
 Therefore, models trained on these groups may not benefit from any additional training on other task groups.
@@
 
-Therefore, we have performed a final set of experiments ("Train on Group A/B"), where we trained two SAMNet instances: a) trained on all tasks from \textit{Group A} and tested on each task from the lowest groups (i.e.
+Therefore, we have performed a final set of experiments (``Train on Group A/B''), where we trained two SAMNet instances: a) trained on all tasks from \textit{Group A} and tested on each task from the lowest groups (i.e.
 \textit{Basic}, \textit{Obj-Attr} and \textit{Compare}) separately; b) trained on all tasks from \textit{Group B} and tested separately on \textit{Spatial} and \textit{Cognitive}.
@@
 Finally, we can interestingly note for \textit{Obj-Attr} and \textit{Spatial} that training on the group A/B does not appear to help.
-When comparing with "Train on t only", we observe slight accuracy drops (around 0.3-0.5 point).
+When comparing with ``Train on t only'', we observe slight accuracy drops (around 0.3-0.5 point).
 Understanding this phenomenon warrants further investigations on the dependencies between the reasoning required by the particular questions and the transferred reasoning.

### 2020-02-14 Transfer_Learning/arxiv_version/submission_folder/v2/summary.tex
arxiv v2 submission files

--- 2020-02-13 Transfer_Learning/arxiv_version/summary.tex
@@
 Hence, we designed a novel Memory-Augmented Neural Network model called SAMNet, with mechanisms to address these deficiencies.
-SAMNet showed significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieved comparable performance on the CLEVR dataset for Image Reasoning.
+SAMNet showed significant improvements over state-of-the-art models on the COG dataset for Video Reasoning  and achieved comparable performance on the CLEVR dataset for Image Reasoning.
 It also demonstrated excellent generalization capabilities for temporal and reasoning transfer. Moreover, through the cautious use of fine-tuning, SAMNet's performance advanced even further.

### 2020-02-15 Transfer_Learning/arxiv_version/submission_folder/v2/experiments.tex
v2 submitted version to arxiv

@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
+	\includegraphics[width=0.5\textwidth]{figures/clevr_baselines.pdf}
 	\caption{Comparison of SAMNet to baselines on CLEVR.}
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{../img/architecture/hierarchy}
+	\includegraphics[width=0.7\textwidth]{figures/hierarchy}
 	\caption{Hierarchy of Task Groups in the COG dataset.}
@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/plots/cog_canonical_baseline_no_labels.pdf}
+		\includegraphics[width=\textwidth]{figures/cog_canonical_baseline_no_labels.pdf}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=\textwidth]{../img/plots/cog_hard_baseline_labels.pdf}
+		\includegraphics[width=\textwidth]{figures/cog_hard_baseline_labels.pdf}
 	\end{subfigure}%
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
+	\includegraphics[width=0.9\textwidth]{figures/cogent_feature_transfer_baselines.pdf}
 	\caption{Feature transfer: test accuracies when transferring between CoGenT-A and CoGenT-B.}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/cog_temporal_transfer_baselines.pdf}
 	\caption{Temporal transfer capabilities of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard  in COG.}

### 2020-02-15 Transfer_Learning/arxiv_version/submission_folder/v2/experiments_reasoning_transfer.tex
v2 submitted version to arxiv

@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../img/plots/cogent_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/cogent_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../img/plots/cog_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/cog_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}

### 2020-02-28 Transfer_Learning/cvpr_2nd_submission/experiments.tex
reorganization of images - perfect 8 pages
Signed-off-by: ibm <tkornuta.ibm@gmail.com>
\vspace{-10pt} for three two-column images, rest normal, 8 pages
Signed-off-by: ibm <tkornuta.ibm@gmail.com>
Remove blank spaces in \cite{} with multiple references.

@@
 % \tk{order: CLEVR + baselines without TL, COG + baseline without TL, Feature Transfer-CLEVR/CoGenT, Temporal Transfer - COG, Reasoning Transfer - CLEVR/CoGenT, Reasoning Transfer-COG}
+
+\begin{figure}[b!]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{../img/plots/clevr_baselines.pdf}
+	\caption{Comparison of SAMNet to baselines on CLEVR.}
+	\label{fig:clevr_baselines}
+\end{figure}
 
@@
 
-\begin{table}[b!]
-	\centering
-	%\begin{adjustbox}{width=0.45\textwidth}
-	\begin{tabular}{cccc}
-		\toprule
-		Variant	& Cubes	& Cylinders &	Spheres	\\
-		\midrule
-		CLEVR &  Any Color  & Any Color 	&	Any color  \\
-		CoGenT-A &  Family A  & Family B 	&	Any color  \\
-		CoGenT-B	&	Family B  &	Family A	&	Any color \\
-		\bottomrule
-	\end{tabular}
-	%\end{adjustbox}
-	\caption{Allowed feature combinations in the CoGenT-A and CoGenT-B variants of the CLEVR dataset.}%\vspace{2pts}
-	\label{tab:cogent_conditions}
-\end{table}
-
-\begin{figure*}[t!]
+\begin{figure*}[!t]
 	\centering
@@
 	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the baseline model~\cite{yang2018dataset} (dotted gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
-	\label{fig:samnet_cog_detailed}
+	\label{fig:samnet_cog_detailed}\vspace{-10pt}
 \end{figure*}
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.8\columnwidth]{../img/plots/clevr_baselines.pdf}
-	\caption{Comparison of SAMNet to baselines on CLEVR.}
-	\label{fig:clevr_baselines}
-\end{figure}
-
 \cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
@@
 
-\begin{table}[ht]
+\begin{table}[htbp]
 	\centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[b!]
 	\centering
@@
 In order to quantify SAMNet's feature transfer ability, we used the CoGenT variants of CLEVR and performed a set of experiments, starting from training on CoGenT-A, followed by:
-an immediate test (zero-shot learning) on CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following the methodology used in~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}).
+an immediate test (zero-shot learning) on CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following the methodology used in~\cite{johnson2017inferring,mascharka2018transparency,perez2018film,marois2018transfer}).
 In \cref{fig:CoGenT-B-results}, we compare the achieved performance with the previously selected SOTA models.

### 2020-02-28 Transfer_Learning/cvpr_2nd_submission/related_work.tex
Remove blank spaces in \cite{} with multiple references.

@@
 
-Visual Reasoning tasks combining both the visual and language modalities~\cite{mogadala2019trends} naturally draw from those findings by reusing the pretrained image and word/question encoders.
-The community also seems to be realising that the models should not only be able to generalize on the low-level image features, but also on the performed high-level, abstract \textit{reasoning}.
-First notable attemp to establish a framework enabling transfer learning of reasoning skill was CLEVR~\cite{johnson2017clevr} with its two CoGenT variants.
-As a result several interesting works appeared~\cite{mascharka2018transparency, perez2018film, johnson2017inferring,marois2018transfer}, proposing models trying to cope with transfer from one to the other domain with different distributions of visual attribute combinations.
-Similarly, the baseline model introduced along with the COG dataset~\cite{yang2018dataset} have shown that it can do significantly better answer questions belonging to task classes not being explicitly trained on when leveraging knowledge learned on other tasks.
+Visual Reasoning tasks, combining both the visual and language modalities~\cite{mogadala2019trends}, naturally draw from those findings by reusing the pretrained image and word/question encoders.
+Ensuring models can generalize on high-level, abstract \emph{reasoning} has been a recent interest of the community.
+The first attempt at establishing a framework enabling transfer learning of reasoning skills was CLEVR~\cite{johnson2017clevr} with its two CoGenT variants.
+This fostered research~\cite{mascharka2018transparency,perez2018film,johnson2017inferring,marois2018transfer}, proposing models designed to transfer from one domain to another, with different distributions of visual attribute combinations.
+Similarly, the baseline model introduced alongside the COG dataset~\cite{yang2018dataset} has shown the ability to solve tasks not explicitly trained on, by leveraging knowledge learned on other tasks.
+
 These results clearly indicate the usefulness of transfer learning, despite the assumption of similar distributions between the source and target domains not being respected.
-At the same time transfer learning several research questions, such as the characteristics which make a whole dataset or a particular task more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
+Conjointly, transfer learning raises several research questions, such as the characteristics which make a whole dataset or a particular task more favorable to be used in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
 One of the most systematic works in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies between twenty-six different computer vision tasks.
-In this work we extend that idea further and introduce a taxonomy enabling us to isolate and quantify different aspects of visual reasoning on the performance of our model.
+In this work, we extend this idea further and introduce a taxonomy allowing us to isolate and quantify different aspects of visual reasoning.
 %We illustrate it with the two above mentioned CLEVR and COG datasets.

### 2020-02-28 Transfer_Learning/eccv_submission/eccv_paper_main.tex
Initial commit of the ECCV version.

--- 2020-02-07 Transfer_Learning/cvpr_2nd_submission/cvpr_paper_main.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% updated April 2002 by Antje Endemann
+% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016; AAS, 2020
 
-\usepackage{cvpr}
+\documentclass[runningheads]{llncs}
+\usepackage{amsmath,amssymb,amsfonts,bm} % define this before the line numbering.
 \usepackage{times}
-%\usepackage{epsfig}
 \usepackage{graphicx}
+\usepackage{comment}
 \usepackage[font=small]{subcaption}
-\captionsetup[figure]{skip=5pt}
-\captionsetup[table]{skip=5pt}
-\setlength{\belowcaptionskip}{-15pt}  % reduce padding below figure
-\usepackage{amsmath, amssymb, amsfonts,bm}
-\usepackage{amsthm}
+\usepackage{color}
+
+% INITIAL SUBMISSION - The following two lines are NOT commented
+% CAMERA READY - Comment OUT the following two lines
+\usepackage{ruler}
+\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
 
@@
 \crefname{definition}{Definition}{Definitions}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{definition}[theorem]{Definition}
-
-\theoremstyle{remark}
-\newtheorem*{notation}{Notation}
-%\newtheorem*{remark}{Remark}
-\newtheorem*{note}{Note}
-
-\newtheorem{fact}{Fact}
-\newtheorem*{observation}{Observation}
-\newtheorem*{condition}{Condition}
-\newtheorem*{claim}{Claim}
-\newtheorem*{example}{Example}
-\newtheorem*{question}{Question}
-
-\usepackage{enumitem}
-\setlist{leftmargin=*}
 
@@
 
-%%%%%%%%%%%%%%%
+\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
 
 \begin{document}
+% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
+% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
+% \linenumbers
+\pagestyle{headings}
+\mainmatter
+\def\ECCVSubNumber{100}  % Insert your submission number here
 
-%%%%%%%%% TITLE
-\title{Transfer Learning in Visual and Relational Reasoning}
+\title{Transfer Learning in Visual and Relational Reasoning} % Replace with your title
 
-\author{%
-	T.S. Jayram\thanks{IBM Research AI.} \and
-	Vincent Marois\footnotemark[2] \and
-	Tomasz Kornuta\thanks{Nvidia Research.} \and
-	Vincent Albouy\thanks{} \and
-	Emre Sevgen\thanks{Citrine Informatics.}  \and
-	Ahmet Ozcan\footnotemark[2]
-}
+% INITIAL SUBMISSION
+\author{Anonymous ECCV submission}
+\institute{Paper ID \ECCVSubNumber}
+
+\begin{comment}
+\author{T.S.
+Jayram\inst{1} \and  Vincent Marois\inst{2} \and Vincent Albouy\thanks{Work done while at IBM Research AI, Almaden Research Center} \and Tomasz Kornuta\inst{3}  \and Emre Sevgen\samethanks \and Ahmet Ozcan\inst{1}}
+
+\institute{IBM Research AI, Almaden Research Center, San Jose, CA, USA\\ \email{\{jayram,  asozcan\}@us.ibm.com}
+      \and IBM Research AI, Thomas J. Watson Research Center, York Town, NY, USA\\ \email{vincent.marois@ibm.com}
+      \and NVIDIA, Santa Clara, CA, USA\\ \email{tkornuta@nvidia.com}}
+\end{comment}
+%******************
+
+% CAMERA READY SUBMISSION
+\begin{comment}
+\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
 %
-%\author{T.S. Jayram \and  Vincent Marois \and Vincent Albouy \and Tomasz Kornuta  \and Emre Sevgen \and Ahmet Ozcan\\
-%IBM Research AI\\
-%Almaden Research Center, San Jose, CA 95120, USA\\
-%Thomas J. Watson Research Center, Yorktown Heights, NY 10598, USA\\
-%{\tt\small {jayram,  asozcan}@us.ibm.com}
-%{\tt\small {tkornuta, sesevgen}@gmail.com}
-%{\tt\small vincent.marois@ibm.com}
-%}
-
+\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
+Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
+Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+%
+\authorrunning{F. Author et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Princeton University, Princeton NJ 08544, USA \and
+Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
+\email{lncs@springer.com}\\
+\url{http://www.springer.com/gp/computer-science/lncs} \and
+ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
+\email{\{abc,lncs\}@uni-heidelberg.de}}
+\end{comment}
+%******************
 \maketitle
 
-%%%%%%%%% ABSTRACT
 \begin{abstract}
@@
 %%%%%%%%% BODY TEXT
-\input{introduction}
+\input{../cvpr_2nd_submission/introduction}
 
-\input{related_work}
+\input{../cvpr_2nd_submission/related_work}
 
-\input{samnet}
+\input{../cvpr_2nd_submission/samnet}
 
-\input{transfer_learning}
+\input{../cvpr_2nd_submission/transfer_learning}
 
-\input{experiments}
+\input{../cvpr_2nd_submission/experiments}
+\input{../cvpr_2nd_submission/experiments_reasoning_transfer}
 
-\input{summary}
+\input{../cvpr_2nd_submission/summary}
 
 \clearpage
-{\small
-\bibliographystyle{ieee_fullname}
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
 \bibliography{../bibliography}
-}
-
-%\clearpage
-%\input{appendix}
-
 \end{document}

### 2020-03-02 Transfer_Learning/eccv_submission/eccv_paper_main.tex
Add Paper ID and slight clean up.

@@
 
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
 \begin{document}
@@
 \mainmatter
-\def\ECCVSubNumber{100}  % Insert your submission number here
+\def\ECCVSubNumber{7169}
 
-\title{Transfer Learning in Visual and Relational Reasoning} % Replace with your title
+\title{Transfer Learning in Visual and Relational Reasoning}
 
@@
 
+% CAMERA READY SUBMISSION
 \begin{comment}
-\author{T.S.
-Jayram\inst{1} \and  Vincent Marois\inst{2} \and Vincent Albouy\thanks{Work done while at IBM Research AI, Almaden Research Center} \and Tomasz Kornuta\inst{3}  \and Emre Sevgen\samethanks \and Ahmet Ozcan\inst{1}}
+\author{T.S. Jayram\inst{1} \and  Vincent Marois\inst{2} \and Vincent Albouy\thanks{Work done while at IBM Research AI, Almaden Research Center} \and Tomasz Kornuta\inst{3} \and Ahmet Ozcan\inst{1}}
+
+\authorrunning{T.S. Jayram et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
 
@@
       \and NVIDIA, Santa Clara, CA, USA\\ \email{tkornuta@nvidia.com}}
-\end{comment}
-%******************
-
-% CAMERA READY SUBMISSION
-\begin{comment}
-\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
-%
-\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
 \end{comment}
@@
 % ---- Bibliography ----
-%
 % BibTeX users should specify bibliography style 'splncs04'.
 % References will then be sorted and formatted in the correct style.
-%
 \bibliographystyle{splncs04}

### 2020-03-02 Transfer_Learning/cvpr_2nd_submission/related_work.tex
Small corrections throughout the paper.

@@
 medical images) and the task (image classification vs.
-image segmentation vs VQA) change significantly.
+image segmentation vs.
+VQA) change significantly.
 
@@
 Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses from e.g.\ Wikipedia or Twitter, has been a standard procedure across different NLP domains and tasks.
-Recently, there is a clear, growing trend of utilization of deep contextualized word representations such as ELMo~\cite{peters2018deep} (based on bidirectional LSTMs~\cite{hochreiter1997long}) or BERT~\cite{devlin2018bert} (based on the Transformer~\cite{vaswani2017attention} architecture), where entire deep networks (not just the input layer) are pretrained on very large corporas.
+Recently, there is a clear, growing trend in the utilization of deep contextualized word representations such as ELMo~\cite{peters2018deep} (based on bidirectional LSTMs~\cite{hochreiter1997long}) or BERT~\cite{devlin2018bert} (based on the Transformer~\cite{vaswani2017attention} architecture), where entire deep networks (not just the input layer) are pretrained on very large corporas.
 %In analogy to repositories with pretrained image encoders in TensorFlow~\cite{} or PyTorch~\cite{}, the NLP community has also started to create model repositories, some with dozens of pretrained models ready to be downloaded and used.

### 2020-03-02 Transfer_Learning/eccv_submission/experiments.tex
Make copy of source tex files + correct figures sizes / positions.

--- 2020-02-28 Transfer_Learning/cvpr_2nd_submission/experiments.tex
@@
 	\centering
-	\includegraphics[width=0.8\columnwidth]{../img/plots/clevr_baselines.pdf}
+	\includegraphics[width=0.5\columnwidth]{../img/plots/clevr_baselines.pdf}
 	\caption{Comparison of SAMNet to baselines on CLEVR.}
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{../img/plots/cog_canonical_baseline_no_labels.pdf}
+		\includegraphics[width=\textwidth]{../img/plots/cog_canonical_baseline_no_labels.pdf}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{../img/plots/cog_hard_baseline_labels.pdf}
+		\includegraphics[width=\textwidth]{../img/plots/cog_hard_baseline_labels.pdf}
 	\end{subfigure}%
@@
 The colors are partitioned into two complementary families:
-Gray, Blue, Brown and Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
+Gray, Blue, Brown, Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
 The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (See~\cref{tab:cogent_conditions}).

### 2020-03-02 Transfer_Learning/eccv_submission/experiments_reasoning_transfer.tex
Make copy of source tex files + correct figures sizes / positions.

--- 2020-02-09 Transfer_Learning/cvpr_2nd_submission/experiments_reasoning_transfer.tex
@@
 We next trained and tested 5 SAMNet instances, each on a single task group $t$ ("Train on t only").
-We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, aside of \textit{Query Attribute}.
+We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, except for \textit{Query Attribute}.
 We hypothesize \textit{Query Attribute} requires mastering visual grounding and recognizing object attributes, as opposed to the other groups which may not enforce it.
-Thus, training on \textit{Query Attribute} helps others, whereas without any training on that particular group, SAMNet battles developing such skill.
+Thus, training on \textit{Query Attribute} helps others, whereas without any training on that particular group, SAMNet struggles developing such skill.
 
@@
 The order of the performed experiments is analogical to the one in the previous section.
-The first column (\cref{fig:cog_reasoning_transfer}, "Train on All") is the baseline, i.e.
+The first column (\cref{fig:cog_reasoning_transfer}, "Train on All") is taken as a reference, i.e.
 we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
@@
 
-Next, we experimented with the "Train on t only" setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. single leaf of the proposed hierarchy).
-For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the baseline ("Train on All"), suggesting that each group contain sufficient information for developing all necessary skills.
+Next, we experimented with the "Train on t only" setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. the leaves of the proposed hierarchy).
+For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the reference ("Train on All"), suggesting that each group contains sufficient information for developing all necessary skills.
 Therefore, models trained on these groups may not benefit from any additional training on other task groups.
-However, the accuracy drops for \textit{Compary} and \textit{Cognitive}, suggesting the opposite.
+However, accuracy on \textit{Compary} and \textit{Cognitive} dropped, suggesting the contrary.
 

### 2020-03-02 Transfer_Learning/eccv_submission/transfer_learning.tex
Make copy of source tex files + correct figures sizes / positions.

--- 2020-02-09 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
@@
 \label{sec:transfer_learning}
+
+\begin{figure*}[htbp]
+	\centering
+	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
+	\caption{Transfer learning taxonomy.}
+	\label{fig:taskonomy}\vspace{-10pt}
+\end{figure*}
+
 Due to the complex nature of visual reasoning, it appears that

### 2020-03-02 Transfer_Learning/eccv_submission/experiments_reasoning_transfer.tex
Changed font to respect constraint and trying to respect page limit.

@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}

### 2020-03-03 Transfer_Learning/eccv_submission/experiments.tex
Changed font to respect constraint and trying to respect page limit.
Merging changes in cvpr (v2) and arxiv (v2) into this version.

@@
 	\centering
-	\includegraphics[width=0.5\columnwidth]{../img/plots/clevr_baselines.pdf}
+	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
 	\caption{Comparison of SAMNet to baselines on CLEVR.}
@@
 
-\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected SOTA models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
+\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected state-of-the-art models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
 SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.
@@
 
-COG dataset contains short videos, with associated questions grouped into 23 categories~\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
+COG dataset contains short videos, with associated questions grouped into 23 categories\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
 COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
+	\includegraphics[width=0.5\textwidth]{../img/architecture/hierarchy}
 	\caption{Hierarchy of Task Groups in the COG dataset.}
@@
 
-We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
+We compared our results with the baseline model introduced in in~\cite{yang2018dataset}, the same paper as the COG dataset.
 The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.
@@
 an immediate test (zero-shot learning) on CoGenT-B; and fine-tuning for a single epoch on 30k samples from CoGenT-B before testing (following the methodology used in~\cite{johnson2017inferring,mascharka2018transparency,perez2018film,marois2018transfer}).
-In \cref{fig:CoGenT-B-results}, we compare the achieved performance with the previously selected SOTA models.
+In \cref{fig:CoGenT-B-results}, we compare the achieved performance with the previously selected state-of-the-art models.
 We also consider a direct test on CoGenT-A; and a test on CoGenT-A after fine-tuning on B.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
+	\includegraphics[width=\textwidth]{../img/plots/cogent_feature_transfer_baselines.pdf}
 	\caption{Feature transfer: test accuracies when transferring between CoGenT-A and CoGenT-B.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
+	\includegraphics[width=0.8\textwidth]{../img/plots/cog_temporal_transfer_baselines.pdf}
 	\caption{Temporal transfer capabilities of SAMNet (blue) and baseline models (gray -striped and -dotted) when moving from Canonical to Hard  in COG.}

### 2020-03-03 Transfer_Learning/eccv_submission/experiments_reasoning_transfer.tex
Merging changes in cvpr (v2) and arxiv (v2) into this version.

--- 2020-03-02 Transfer_Learning/eccv_submission/experiments_reasoning_transfer.tex
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\textwidth]{../img/plots/cogent_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
@@
 We first trained a single SAMNet instance on CoGenT-A and measured its accuracy on each of the task group $t$ separately.
-Those results, indicated in \cref{fig:cogent_reasoning_transfer} as "Train on All", serve as baselines for the next two sets of experiments.
+Those results, indicated in \cref{fig:cogent_reasoning_transfer} as ``Train on All'', serve as baselines for the next two sets of experiments.
 
-We next trained and tested 5 SAMNet instances, each on a single task group $t$ ("Train on t only").
+We next trained and tested 5 SAMNet instances, each on a single task group $t$ (``Train on t only'').
 We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, except for \textit{Query Attribute}.
@@
 The order of the performed experiments is analogical to the one in the previous section.
-The first column (\cref{fig:cog_reasoning_transfer}, "Train on All") is taken as a reference, i.e.
+The first column (\cref{fig:cog_reasoning_transfer}, ``Train on All'') is taken as a reference, i.e.
 we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
+	\includegraphics[width=0.8\textwidth]{../img/plots/cog_reasoning_transfer.pdf}
 	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}
@@
 
-Next, we experimented with the "Train on t only" setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. the leaves of the proposed hierarchy).
-For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the reference ("Train on All"), suggesting that each group contains sufficient information for developing all necessary skills.
+Next, we experimented with the ``Train on t only'' setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. the leaves of the proposed hierarchy).
+For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the reference (``Train on All''), suggesting that each group contains sufficient information for developing all necessary skills.
 Therefore, models trained on these groups may not benefit from any additional training on other task groups.

### 2020-03-03 Transfer_Learning/eccv_submission/samnet.tex
Make copy of source tex files + correct figures sizes / positions.
Merging changes in cvpr (v2) and arxiv (v2) into this version.
no message

--- 2020-02-08 Transfer_Learning/cvpr_2nd_submission/samnet.tex
@@
 	\caption{General architecture of SAMNet.}
-	\label{fig:samnet}
+	\label{fig:samnet}\vspace{-10pt}
 \end{figure*}
@@
 The language input of $L$ word embeddings is processed by a Bi-LSTM based question encoder that produces \emph{contextual words} $\vec{cw} \in \Reals^{L \times d}$.
-The final states in either direction of the BI-LSTM are also concatenated and passed through a linear layer to produce a global representation of the question 
+The final states in either direction of the Bi-LSTM are also concatenated and passed through a linear layer to produce a global representation of the question
 $\vec{q} \in \Reals^d$, called the \emph{question embedding}.
@@
 $\vec{F}_k \in \Reals^{H \times W \times d}$.
+Similar to the memory, we view $\vec{F}_k$ as a content-addressable memory with 
+$H \times W$ locations, each containing a$d$-dimensional feature vector.
 
@@
 \noindent\textbf{Question-driven Controller.}
-This module drives attention over the question to produce $k$ control states, one per reasoning operation.
+This module drives attention over the question to produce $T$ control states, one per reasoning operation.
 The control state $\vec{c}_t$ at step $t$ is then fed to a \emph{temporal classifier},
@@
 
-\noindent\textbf{Retrieval Units.} The visual retrieval unit uses the information generated above to extract a relevant object $\vec{vo}_t$ from the frame.
-A similar operation on memory yields the object $\vec{mo}_t$.
-The memory operation is based on attention mechanism, and resembles content-based addressing.
-Therefore, we obtain an attention vector over memory addresses that we interpret to be the \emph{read head}, denoted by $\rhead_t$.
+\noindent\textbf{Retrieval Units.} The visual retrieval unit uses the information generated above to extract an attention vector $\vec{va}_t \in \Reals^{H \times W}$ over the feature vectors in $\vec{F}_k$ and a frame object
+$\vec{vo}_t \in \Reals^d$.
+A similar operation on memory yields an attention vector $\rhead_t \in \Reals^N$ over the $N$ memory addresses, called the \emph{read head}, and a memory object
+$\vec{mo}_t \in \Reals^d$.
 %Note that the returned objects may be invalid, e.g., if the current reasoning step focuses on the phrase ``last red square'', $\vec{vo}_t$ is invalid even if the current frame contains a red square.
@@
 To resolve whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
-First, we compute a simple aggregate\footnote{%
-	This is closely related to R\'{e}nyi entropy and Tsallis entropy of order~2.} of the visual attention vector $\vec{va}_t$ of dimension $L$ ($L$ denotes the number of feature vectors for the frame):
-$vs_t = \sum_{i=1}^L [\vec{va}_t(i)]^2$. It can be shown that the more localized the attention
+First, we compute a simple aggregate%\footnote{%
+%	This is closely related to R\'{e}nyi entropy and Tsallis entropy of 
+%	order~2.}%
+of the visual attention vector $\vec{va}_t$:
+$vs_t = \sum_{i=1}^H \sum_{j=1}^W [\vec{va}_t(i,j)]^2$. It can be shown that the more localized the attention
 vector, the higher the aggregate value.
@@
 This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
-
-%For details of the modules not covered here, please see the appendix.

### 2020-03-03 Transfer_Learning/eccv_submission/eccv_supplementary_material.tex

--- 2020-03-02 Transfer_Learning/eccv_submission/eccv_paper_main.tex
@@
-% updated April 2002 by Antje Endemann
-% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016; AAS, 2020
+\documentclass[runningheads]{llncs}
 
-\documentclass[runningheads]{llncs}
-\usepackage{amsmath,amssymb,amsfonts,bm} % define this before the line numbering.
-\usepackage{times}
-\usepackage{graphicx}
+\usepackage{booktabs}
+\usepackage{adjustbox}
+\usepackage{xcolor}
 \usepackage{comment}
-\usepackage[font=small]{subcaption}
-\usepackage{color}
 
@@
 
-% Include other packages here, before hyperref.
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{adjustbox}
-\usepackage{tabularx}
-\usepackage{xcolor}
-
 \usepackage{hyperref}
 \hypersetup{
-	pagebackref,
 	colorlinks,
 	breaklinks,
-	bookmarks=false,
 	linkcolor={red!50!black},
@@
 \usepackage{cleveref}
-\crefname{section}{Section}{Sections}
-\crefname{figure}{Figure}{Figures}
 \crefname{table}{Table}{Tables}
-\crefname{appendix}{Appendix}{Appendices}
-\crefname{definition}{Definition}{Definitions}
-
-%% User's macros %%
-\newcommand{\Reals}{\mathbb{R}}
-\newcommand{\cD}{\mathcal{D}}
-\newcommand{\cT}{\mathcal{T}}
-\newcommand{\cX}{\mathcal{X}}
-\newcommand{\cY}{\mathcal{Y}}
-\newcommand{\cQ}{\mathcal{Q}}
-\newcommand{\cV}{\mathcal{V}}
-\newcommand{\cF}{\mathcal{F}}
-
-\renewcommand{\vec}[1]{\mathbf{#1}}
-\newcommand{\vc}{\vec{c}}
-\newcommand{\vso}{\vec{so}}
-\newcommand{\vone}{\vec{1}}
-\newcommand{\proj}{\mathrm{proj}}
-\newcommand{\vx}{\vec{x}}
-\newcommand{\vy}{\vec{y}}
-
-\newcommand{\imatch}{g^{\mathrm{v}}}
-\newcommand{\mmatch}{g^{\mathrm{m}}}
-
-\newcommand{\doadd}{h^{\mathrm{a}}}
-\newcommand{\doreplace}{h^{\mathrm{r}}}
-
-\newcommand{\tlast}{\tau^{\mathrm{last}}}
-\newcommand{\tlatest}{\tau^{\mathrm{latest}}}
-\newcommand{\tnow}{\tau^{\mathrm{now}}}
-\newcommand{\tnone}{\tau^{\mathrm{none}}}
-
-\newcommand{\rhead}{\vec{rh}}
-\newcommand{\whead}{\vec{wh}}
-
-\newcommand{\uX}{\underline{X}}
-
-\newcommand{\tk}[1]{\textcolor{red}{TK: #1}}
-\newcommand{\ao}[1]{\textcolor{green}{AO: #1}}
-\newcommand{\tsj}[1]{\textcolor{magenta}{TSJ: #1}}
-\newcommand{\vm}[1]{\textcolor{blue}{VM: #1}}
-
-\newcommand{\compresslist}{ % Define a command to reduce spacing within itemize/enumerate environments, this is used right after \begin{itemize} or \begin{enumerate}
-\setlength{\itemsep}{1pt}
-\setlength{\parskip}{0pt}
-\setlength{\parsep}{0pt}}
 
 \begin{document}
-% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
-% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers
+
+%%%%%%%%% TITLE
 \pagestyle{headings}
 \mainmatter
-\def\ECCVSubNumber{7169}
+\def\ECCVSubNumber{7169}  % Insert your submission number here
 
-\title{Transfer Learning in Visual and Relational Reasoning}
+\title{Transfer Learning in Visual and Relational Reasoning -- Supplementary Material}
 
 % INITIAL SUBMISSION
+%\begin{comment}
+\titlerunning{ECCV-20 submission ID \ECCVSubNumber}
+\authorrunning{ECCV-20 submission ID \ECCVSubNumber}
 \author{Anonymous ECCV submission}
 \institute{Paper ID \ECCVSubNumber}
+%\end{comment}
 
@@
 \end{comment}
-%******************
+
 \maketitle
 
-\begin{abstract}
-Transfer learning has become the de facto standard in computer vision and natural language processing, especially where labeled data is scarce.
-Accuracy can be significantly improved by using pre-trained models and subsequent fine-tuning.
-In visual reasoning tasks, such as image question answering, transfer learning is more complex.
-In addition to transferring the capability to recognize visual features, we also expect to transfer the system’s ability to reason.
-Moreover, for video data, temporal reasoning adds another dimension.
-In this work, we formalize these unique aspects of transfer learning and propose a theoretical framework for visual reasoning, exemplified by the well-established CLEVR and COG datasets.
-Furthermore, we introduce a new, end-to-end differentiable recurrent model (SAMNet), which shows state-of-the-art accuracy and better performance in transfer learning on both datasets.
-The improved performance of SAMNet stems from its capability to decouple the abstract multi-step reasoning from the length of the sequence and its selective attention enabling to store only the question-relevant objects in the external memory.
-\end{abstract}
+\input{appendix}
 
-%%%%%%%%% BODY TEXT
-\input{../cvpr_2nd_submission/introduction}
-
-\input{../cvpr_2nd_submission/related_work}
-
-\input{../cvpr_2nd_submission/samnet}
-
-\input{../cvpr_2nd_submission/transfer_learning}
-
-\input{../cvpr_2nd_submission/experiments}
-\input{../cvpr_2nd_submission/experiments_reasoning_transfer}
-
-\input{../cvpr_2nd_submission/summary}
+\bigskip
 
 \clearpage
-% ---- Bibliography ----
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
 \bibliographystyle{splncs04}
 \bibliography{../bibliography}
+
 \end{document}

### 2020-03-05 Transfer_Learning/eccv_submission/introduction.tex
CHanges to samnet section Minor edits

--- 2020-02-13 Transfer_Learning/arxiv_version/introduction.tex
@@
 In this work we focus on transfer learning in multi-modal reasoning tasks combining vision and language~\cite{mogadala2019trends}.
-Recently introduced visual reasoning datasets, such as ~\cite{johnson2017clevr,yang2018dataset,song2018explore}, attempt to probe the generalization capabilities of models under various scenarios, trying to quantify the visual complexity of the scene or the compositional complexity of the question.
+Recently introduced visual reasoning datasets, such as~\cite{johnson2017clevr,yang2018dataset,song2018explore}, attempt to probe the generalization capabilities of models under various scenarios, trying to quantify the visual complexity of the scene or the compositional complexity of the question.
 While these datasets seem to be well suited for transfer learning, they do not tackle that issue directly.
-In particular, \cite{johnson2017clevr} introduces the CLEVR dataset along with two variants (CoGenT-A and -B) with varying combinations of visual attributes.
-Similarly, COG \cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants (Canonical and Hard) with different number of frames and scene complexity.
+In particular,~\cite{johnson2017clevr} introduces the CLEVR dataset along with two variants (CoGenT-A and CoGenT-B) with varying combinations of visual attributes.
+Similarly, COG~\cite{yang2018dataset}, a Video QA reasoning dataset, contains two variants (Canonical and Hard) with different number of frames and scene complexity.
 Both datasets come with a number of task classes that require similar reasoning abilities (e.g. compare or count objects).

### 2020-03-05 Transfer_Learning/eccv_submission/samnet.tex
CHanges to samnet section Minor edits

@@
-\section{Selective Attention Memory (SAM) Network}
+\section{Selective Attention Memory Network (SAMNet)}
 
@@
 
-SAM Network (SAMNet) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
-iterative reasoning as proposed e.g.
-in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and use of an external memory, as in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
+SAMNet is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}). At the conceptual level, SAMNet draws from two core ideas:
+iterative reasoning as proposed in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer} and an external memory as proposed in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.
 
@@
 
-A distinctive feature of the SAM Network is its frame-by-frame temporal processing approach, where a single frame can be accessed at once.
-This is a notable difference from~\cite{haurilet2019s}, which uses graph traversal reasoning.
-The recurrent nature of SAMNet does not prevent frame sequences longer than those used for training.
+A distinctive feature of SAMNet is its frame-by-frame temporal processing in a recurrent fashion; this allows for the model to be used on frame sequences longer than those used for training.
+This is a notable difference from~\cite{haurilet2019s}, which uses graph traversal reasoning on a fixed number of frames.
 The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video.
@@
 Using gating mechanisms, correct objects can be retrieved in order to perform multi-step spatio-temporal reasoning over text and video.
-A notable feature of this design is that the number of addresses $N$ can be changed between training and testing, to fit the data characteristics.
+A flexible aspect of this design is that the number of addresses $N$ can be changed between training and testing to fit the data characteristics.
 
@@
 $\vec{F}_k \in \Reals^{H \times W \times d}$.
-Similar to the memory, we view $\vec{F}_k$ as a content-addressable memory with 
-$H \times W$ locations, each containing a$d$-dimensional feature vector.
+Similar to the memory, we view $\vec{F}_k$ as a content-addressable (read-only) memory with 
+$H \times W$ locations, each containing a $d$-dimensional feature vector.
 
@@
 
-\noindent\textbf{The SAM Cell.} The contextual words, question embedding and frame-by-frame feature map form the inputs to SAMNet's core, namely, a recurrent cell called the SAM Cell.
+\noindent\textbf{SAM Cell.}
+The contextual words, question embedding and frame-by-frame feature maps form the inputs to SAM Cell, a recurrent cell that forms the core of SAMNet.
 Unrolling a new series of $T$ cells for each frame allows $T$ steps of iterative reasoning, similar to~\cite{hudson2018compositional}.
@@
 in a trained model, $\whead_t$ points to the location of the first empty slot in memory for adding new objects.
+See the figure in supplementary material giving a detailed view of the information flow in SAM Cell.
 
@@
 
-\noindent\textbf{Retrieval Units.} The visual retrieval unit uses the information generated above to extract an attention vector $\vec{va}_t \in \Reals^{H \times W}$ over the feature vectors in $\vec{F}_k$ and a frame object
-$\vec{vo}_t \in \Reals^d$.
+\noindent\textbf{Retrieval Units.} The visual retrieval unit uses the information generated above to extract an attention vector $\vec{va}_t \in \Reals^{H \times W}$ over the feature vectors in $\vec{F}_k$; via dot-product attention on $\vec{F}_k$, this yields  a frame object $\vec{vo}_t \in \Reals^d$.
 A similar operation on memory yields an attention vector $\rhead_t \in \Reals^N$ over the $N$ memory addresses, called the \emph{read head}, and a memory object
@@
 To resolve whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
-First, we compute a simple aggregate%\footnote{%
+First, we compute a simple aggregate $vs_t$ %\footnote{
 %	This is closely related to R\'{e}nyi entropy and Tsallis entropy of 
@@
 $vs_t = \sum_{i=1}^H \sum_{j=1}^W [\vec{va}_t(i,j)]^2$. It can be shown that the more localized the attention
-vector, the higher the aggregate value.
+vector $\vec{va}_t$ is, the higher is the aggregate value $vs_t$.
 We perform a similar computation on the read head $\rhead_t$ over memory locations.
-We input these two values, along with the temporal class weights $\bm{\tau}_t$, into a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values (in $[0,1]$) for the current reasoning step:
+We input these two aggregate values, along with the temporal class weights $\bm{\tau}_t$, into a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values (in $[0,1]$) for the current reasoning step:
 (a) $\imatch_t$, which determines whether there is a valid visual object;
@@
 Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
-$\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
+The vector $\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
 We then update the memory accordingly:
-\[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t,\]
-where $\vec{vo}_t$ denotes the object returned by the visual retrieval unit.
-Here $\vec{J}$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product.
+\[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t\]
+Above, $\vec{J}$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product
+(Recall that $\vec{vo}_t$ denotes the frame object returned by the visual retrieval unit).
 Note that the memory is unchanged in the case where $\vec{w}_t = 0$, i.e., $\vec{M}_t = \vec{M}_{t-1}$.
@@
 \[ \vec{ro}_t = \imatch_t \cdot \vec{vo}_t + \mmatch_t \cdot \vec{mo}_t \]
-Note that $\vec{ro}_t$ is allowed to be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
+Note that $\vec{ro}_t$ can be null (i.e. 0 vector) when neither gate evaluates to true.
 
@@
 
-\noindent\textbf{Output Unit.} Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and the previous summary object $\vec{so}_{t-1}$.
-This serves to retain additional information in $\vec{so}_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.
+\noindent\textbf{Output Unit.} Finally, $\vec{so}_t$ is the output of a linear layer whose inputs are $\vec{ro}_t$ and previous summary object $\vec{so}_{t-1}$.
+This serves to retain additional information in $\vec{so}_{t-1}$, e.g., the partial result of a complex query with Boolean connectives.

### 2020-03-05 Transfer_Learning/eccv_submission/experiments.tex
Correct number of reasoning steps in experiments section.
Remove tables about COG & CLEVR & add pointers to supp material.

@@
 We briefly describe both datasets in the following two subsections.
-In all experiments, we trained SAMNet using $k = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
+In all experiments, we trained SAMNet using $T = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
 When working with CLEVR, we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
@@
 Gray, Blue, Brown, Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (See~\cref{tab:cogent_conditions}).
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (see the dataset description in the supplementary material).
 As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
@@
 COG dataset contains short videos, with associated questions grouped into 23 categories\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
-COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video, the maximum amount of look-back in frame history containing relevant information for reasoning, and the number of object distractors present in a given frame (see~\cref{tab:cog_variants}).
+COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video (4 vs.
+8), the maximum amount of look-back in frame history containing relevant information for reasoning (3 vs.
+7), and the number of object distractors present in a given frame (1 vs.
+10) (see the dataset description in the supplementary material).
 Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
@@
 
-\begin{table}[htbp]
-	\centering
-	\begin{tabular}{lccc}
-		\toprule
-		Variant	& Frames & History	& Distractors \\
-		\midrule
-		Canonical (Easy) & 4 & 3 & 1\\
-		Hard  & 8 & 7 & 10\\
-		\bottomrule
-	\end{tabular}
-	\caption{Details of the Canonical and Hard variants of COG.}
-	\label{tab:cog_variants}
-\end{table}
+% \begin{table}[htbp]
+% 	\centering
+% 	\begin{tabular}{lccc}
+% 		\toprule
+% 		Variant	& Frames & History	& Distractors \\
+% 		\midrule
+% 		Canonical (Easy) & 4 & 3 & 1\\
+% 		Hard  & 8 & 7 & 10\\
+% 		\bottomrule
+% 	\end{tabular}
+% 	\caption{Details of the Canonical and Hard variants of COG.}
+% 	\label{tab:cog_variants}
+% \end{table}
 

### 2020-03-05 Transfer_Learning/eccv_submission/experiments.tex
added d=128
transfer learning changes

@@
 We briefly describe both datasets in the following two subsections.
-In all experiments, we trained SAMNet using $T = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of 128 floats.
+In all experiments, we trained SAMNet using $T = 8$ reasoning steps and external memory with $N = 8$ slots, each storing an array of $d = 128$ floats.
 When working with CLEVR, we deactivated SAMNet's external memory and temporal-related modules as they are unnecessary while reasoning about static images.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../img/architecture/hierarchy}
+	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
 	\caption{Hierarchy of Task Groups in the COG dataset.}
@@
 \begin{description}
-	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist};
-	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX;
-	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of};
-	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space};
-	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject}
+	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist} (5 task classes);
+	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX\ (4 task classes);
+	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of} (6 task classes);
+	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space} (5 task classes);
+	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject} (3 task classes)
 \end{description}

### 2020-03-05 Transfer_Learning/eccv_submission/transfer_learning.tex
Remove tables about COG & CLEVR & add pointers to supp material.
transfer learning changes

@@
 \label{sec:transfer_learning}
-
-\begin{figure*}[htbp]
-	\centering
-	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
-	\caption{Transfer learning taxonomy.}
-	\label{fig:taskonomy}\vspace{-10pt}
-\end{figure*}
 
@@
 This includes visual attributes such as size, color and shape, temporal characteristics reflected in the number of frames and scene complexity, and finally the reasoning difficulty.
-To establish a formal framework for these various aspects, we first recall the basic theoretical notions in transfer learning~\cite{pan2009survey}.
+To establish a formal framework for these various aspects, we first recall the basic theoretical notions in transfer learning~\cite{pan2009survey} relevant to our setting.
 
-A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
+A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a probability distribution on $\cX$.
 For visual reasoning problems considered in this paper,
@@
 question\footnote{% 
-	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas for typical video answering datasets,
-	only a single answer is needed for the entire video.}. %
-If the domain elements consist of just the visual inputs, then the task is defined by the question so that each question
+	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas typical video answering datasets only require a single answer for the entire video.}.
+If the domain elements consist of just the visual inputs, then the task is further parameterized the question so that each question
 defines a separate task.
@@
 \end{definition}
-In all our applications, $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the marginal distributions $P_S$ and $P_T$ are different.
-Similarly, $\cT_S \ne \cT_T$ means that either $Y_S \ne Y_T$ or that the associated prediction functions are different.
+In this paper, we study the setting of \emph{domain adaptation}
+where $\cT_S \ne \cT_T$ and $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the distributions $P_S$ and $P_T$ are different.
 
-Although~\cref{defn:transfer} is quite general, it does not adequately capture all artifacts present in visual reasoning.
-For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same
-but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
+\Cref{defn:transfer} is quite general but does not give a nuanced view of different aspects of visual reasoning.
 As mentioned in the introduction, one setting is the case of static images,
@@
 comparison of objects, or existence of objects with certain features etc.
-This entails studying transfer learning between families of tasks which requires extending the above definition.
+This entails studying transfer learning in specific settings.
 
-\begin{table}[b!]
+\begin{figure*}[!t]
 	\centering
-	%\begin{adjustbox}{width=0.45\textwidth}
-	\begin{tabular}{cccc}
-		\toprule
-		Variant	& Cubes	& Cylinders &	Spheres	\\
-		\midrule
-		CLEVR &  Any Color  & Any Color 	&	Any color  \\
-		CoGenT-A &  Family A  & Family B 	&	Any color  \\
-		CoGenT-B	&	Family B  &	Family A	&	Any color \\
-		\bottomrule
-	\end{tabular}
-	%\end{adjustbox}
-	\caption{Allowed feature combinations in the CoGenT-A and CoGenT-B variants of the CLEVR dataset.}%\vspace{2pts}
-	\label{tab:cogent_conditions}
-\end{table}
+	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
+	\caption{Transfer learning taxonomy.}
+	\label{fig:taskonomy}\vspace{-10pt}
+\end{figure*}
 
@@
 and \emph{reasoning transfer}.
-These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG. These datasets were chosen because they
+These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR using dataset variants CoGenT-A and CoGenT-B, and COG using two dataset types: canonical and hard.
+These datasets were chosen because they
 are particularly suited for experimental investigations of transfer learning described in the following section.
@@
 	over all questions in $\cQ$.
-	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
+	The distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
 	thereof.
+	For example, CoGenT-A and CoGenT-B variants of CLEVR use complementary colors
+	for cubes and cylinders (\cref{fig:taskonomy}), so $P_S$ and $P_T$ have disjoint support when conditioned on these shapes. This is empirically investigated in~\cref{sec:feature}.
 
-	\item[Temporal Transfer:] This setting is similar to attribute adaptation in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
-	and there is a single task.
-	The key difference is that we introduce a notion of complexity $C(v) = (n, m)$ for a visual input $v$,
-	where $n$ equals the maximum number of objects $n$ in an image, and $m$
-	equals  the number of frames in a video.
-	For any visual input $v_S$ coming from $\cX_S$ with $C(v_S) = (n_S, m_S)$
-	and for any visual input $v_T$ coming from $\cX_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and
-	$m_T \ge m_S$ with at least one inequality being a strict one.
-	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.
+	\item[Temporal Transfer:] This is again similar to feature transfer in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
+	and there is a single task.	The key difference is that we introduce a complexity measure $C(q,v)$ that reflects the ease or difficulty of answering question $q$ on visual input $v$. 
+	For any $(q_S,v_S)$ and $(q_T,v_T)$ in the support of $P_S$ and $P_T$ respectively, we require that $C(q_S,v_S)$ is strictly less than $C(q_T,v_T)$.
+	For example, going from the COG canonical dataset to the hard dataset, we see that there are more distracting objects in each frame and more frames to process that could cumulatively affect the ability to transfer the learned model for the canonical dataset to the hard version.
+This is empirically investigated in~\cref{sec:temporal}.
 
 	\item[Reasoning Transfer:]
-	This setting requires an extension of~\cref{defn:transfer} above to investigate transfer learning when
-	grouping questions into families. Let $\cV$ be the feature space consisting of visual inputs only, shared by
-	all tasks, with a common marginal distribution $P(X)$. For each question $q \in \cQ$, we define the task
-	$\cT_q = (\cY_q, f_q(\cdot))$ where
-	the output set $\cY_q$ is the set of legitimate answers to $q$ and $f_q(v)$, for a visual input $v$,
-	is the answer to question $q$ on visual input $v$.
-	Thus, tasks are in a 1-1 correspondence with questions.
-	A \emph{task family} is a probability distribution on tasks which in our case can be obtained by defining the distribution on $\cQ$.
-	Given a task family, the goal is to learn a prediction function that gives an answer to $f_q(v)$ for $v \in \cV$ chosen according
-	to the feature space distribution and $q$ chosen according to the task probability distribution.
-	Suppose $\cF_S$ is the source task family and $\cF_T$ is the target task family.
-	Transfer learning aims to help improve the learning of the predictive function for the target task family
-	using the knowledge in the source task family.
+	Here, we investigate whether reasoning processes can be transferred in the setting where questions in the source and target domain belong to different categories.
+	A \emph{task family} is defined by a fixing subset of $\cQ$ that share common traits.
+	\Cref{fig:taskonomy} shows representative questions for two task families: \textit{CompareColor} and \textit{AndCompareColor}.
+	Given a fixed global distribution on $\cQ \times \cV$, this induces a marginal distribution for each task family.
+	Let $\cF_S$ be the source task family and $\cF_T$ be the target task family.
+	In typical cases of transfer learning, $\cF_S$ and $\cF_T$ will involve disjoint sets of tasks and therefore, the support of $P_S$ and $P_T$ of the induced distribution on $\cQ \times \cV$ will also be disjoint.
+	In such cases, transfer learning is most effective when the two categories share common attributes in the reasoning process.
+This is evident in the case of \textit{CompareColor} and \textit{AndCompareColor} where the latter task, despite being complex, involves reasoning elements that can be found in the former task.
+The effectiveness of reasoning transfer with respect to various combinations of source-target pairs is thoroughly investigated in~\cref{sec:reasoning-transfer-clevr} using the CoGenT-A variant of CLEVR and in~\cref{sec:reasoning-transfer-cog} using the COG canonical dataset.
 
+%	\item[Temporal Transfer:] This is again a domain adaptation setting similar to feature transfer in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
+%	and there is a single task.
+%	The key difference is that we introduce a notion of complexity $C(v) = (n, m)$ for a visual input $v$,
+%	where $n$ equals the maximum number of objects $n$ in an image, and $m$
+%	equals  the number of frames in a video.
+%	For any visual input $v_S$ coming from $\cX_S$ with $C(v_S) = (n_S, m_S)$
+%	and for any visual input $v_T$ coming from $\cX_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and
+%	$m_T \ge m_S$ with at least one inequality being a strict one.
+%	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.
+%	For example, going from the COG canonical dataset to the hard dataset, we see that there are more distracting objects in each frame and more frames to process that could cumulatively affect the ability to transfer the learned model for the canonical dataset to the hard version.
+This is empirically investigated in~\cref{sec:temporal}.
+%	\item[Reasoning Transfer:]
+%	This setting requires an extension of~\cref{defn:transfer} above to investigate transfer learning when
+%	grouping questions into families. Let $\cV$ be the feature space consisting of visual inputs only, shared by
+%	all tasks, with a common distribution $P(X)$. For each question $q \in \cQ$, we define the task
+%	$\cT_q = (\cY_q, f_q(\cdot))$ where
+%	the output set $\cY_q$ is the set of legitimate answers to $q$ and $f_q(v)$, for a visual input $v$,
+%	is the answer to question $q$ on visual input $v$.
+%	Thus, tasks are in a 1-1 correspondence with questions.
+%	\Cref{fig:taskonomy} shows representative questions for two task families: \textit{CompareColor} and \textit{AndCompareColor}.
+%	A \emph{task family} is a probability distribution on tasks is obtained in our case by defining the distribution on $\cQ$. T
+%	
+%	Given a task family, the goal is to learn a prediction function that gives an answer to $f_q(v)$ for $v \in \cV$ chosen according
+%	to the feature space distribution and $q$ chosen according to the task probability distribution.
+%	Suppose $\cF_S$ is the source task family and $\cF_T$ is the target task family.
+%	Transfer learning aims to help improve the learning of the predictive function for the target task family
+%	using the knowledge in the source task family.
+%	Referring to the same example above,  
+%	This is empirically investigated in~\cref{sec:reasoning-transfer-clevr} using the CoGenT-A variant of CLEVR and in~\cref{sec:reasoning-transfer-cog} using the COG canonical dataset.
 \end{description}

### 2020-03-05 Transfer_Learning/eccv_submission/experiments.tex
Final submitted version

@@
 \label{sec:experiments}
-% \tk{order: CLEVR + baselines without TL, COG + baseline without TL, Feature Transfer-CLEVR/CoGenT, Temporal Transfer - COG, Reasoning Transfer - CLEVR/CoGenT, Reasoning Transfer-COG}
-
-\begin{figure}[b!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
-	\caption{Comparison of SAMNet to baselines on CLEVR.}
-	\label{fig:clevr_baselines}
-\end{figure}
 
@@
 Finally, we assess the reasoning transfer capability of SAMNet on both datasets, by reorganizing groups of questions into new training and test splits.
+
+\subsection{Description of the Datasets}
+\label{sec:datasets-desc}
+
+CLEVR images contain objects characterized by a set of attributes (shape, color, size and material).
+The questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
+The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, CoGenT-A and CoGenT-B, with varying combinations of color-shape attributes.
+The colors are partitioned into two complementary families:
+Gray, Blue, Brown, Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
+The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (see the dataset description in the supplementary material).
+As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
+
+COG dataset contains short videos with associated questions (classification)
+grouped into 23 categories\footnote{COG also proposes pointing-type questions, which are not considered here.}.
+COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video (4 vs.
+8), the maximum amount of look-back in frame history containing relevant information for reasoning (3 vs.
+7), and the number of object distractors present in a given frame (1 vs.
+10) (see the dataset description in the supplementary material).
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
+	\caption{Hierarchy of Question Categories in the COG dataset.}
+	\label{fig:question-groups}
+\end{figure}
+
+Since the number of questions categories is large, we designed a 2-level hierarchy  (see~\cref{fig:question-groups})
+that groups these categories appropriately using their descriptions. 
+For groups at the lowest level, we chose the following question categories to be placed in those groups.
+Below, substitute each of \textit{Shape} and \textit{Color} for  \uX{} to obtain the group.
+\begin{description}
+	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist} (5 categories);
+	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX{} (4 categories);
+	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of} (6 categories);
+	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space} (5 categories);
+	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject} (3 categories)
+\end{description}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\begin{tabular}{lccc}
+% 		\toprule
+% 		Variant	& Frames & History	& Distractors \\
+% 		\midrule
+% 		Canonical (Easy) & 4 & 3 & 1\\
+% 		Hard  & 8 & 7 & 10\\
+% 		\bottomrule
+% 	\end{tabular}
+% 	\caption{Details of the Canonical and Hard variants of COG.}
+% 	\label{tab:cog_variants}
+% \end{table}
+
+\subsection{Performance of SAMNet on CLEVR and COG}
+\label{sec:baseline-compare}
+
+\begin{figure}[!b]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../img/plots/clevr_baselines.pdf}
+	\caption{Comparison of SAMNet to baselines on CLEVR.}
+	\label{fig:clevr_baselines}
+\end{figure}
+
+\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet on CLEVR
+when compared to selected state-of-the-art models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
+SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.
+
+For COG, we compared our results with the baseline model introduced in~\cite{yang2018dataset}, the same paper as the COG dataset.
+The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.
 
@@
 
-\subsection{Performance of SAMNet on CLEVR}
-\label{sec:clevr-baseline-compare}
-CLEVR images contain objects characterized by a set of attributes (shape, color, size and material).
-The questions are grouped into 5 categories: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}.
-The CLEVR authors also introduced CLEVR-CoGenT (Constrained Generalization Test), containing 2 variants, CoGenT-A and CoGenT-B, with varying combinations of color-shape attributes.
-The colors are partitioned into two complementary families:
-Gray, Blue, Brown, Yellow in Family A; and Red, Green, Purple, Cyan in Family B.
-The cubes and cylinders take colors from complementary families in each variant with opposite configurations; the spheres can take any color in both variants (see the dataset description in the supplementary material).
-As the input domain consist of the set of objects with all attribute values, both variants differ by their marginal distributions $P_S$ and $P_T$.
-
-\cref{fig:clevr_baselines} presents the accuracy achieved by SAMNet when compared to selected state-of-the-art models, namely: Transparency by Design networks (TbD)~\cite{mascharka2018transparency}, Feature-wise Linear Modulation (FiLM)~\cite{perez2018film} and the Program Generator + Execution Engine (PG + EE)~\cite{johnson2017inferring}.
-SAMNet reaches a comparable 96.2\% accuracy, with TbD achieving the best score of 98.7\%.
-
-\subsection{Performance of SAMNet on COG}
-\label{sec:cog-baseline-compare}
-
-COG dataset contains short videos, with associated questions grouped into 23 categories\footnote{COG also proposes a pointing version of the tasks, which are not considered in this work.}.
-COG comes in two variants: Canonical (easy) and Hard, differing mainly on the number of frames in the video (4 vs.
-8), the maximum amount of look-back in frame history containing relevant information for reasoning (3 vs.
-7), and the number of object distractors present in a given frame (1 vs.
-10) (see the dataset description in the supplementary material).
-Since the number of task classes is large, we designed a 2-level hierarchy of task groups using the
-description of tasks, as shown in~\cref{fig:task-groups}.
-
-% \begin{table}[htbp]
-% 	\centering
-% 	\begin{tabular}{lccc}
-% 		\toprule
-% 		Variant	& Frames & History	& Distractors \\
-% 		\midrule
-% 		Canonical (Easy) & 4 & 3 & 1\\
-% 		Hard  & 8 & 7 & 10\\
-% 		\bottomrule
-% 	\end{tabular}
-% 	\caption{Details of the Canonical and Hard variants of COG.}
-% 	\label{tab:cog_variants}
-% \end{table}
-
-\begin{figure}[b!]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
-	\caption{Hierarchy of Task Groups in the COG dataset.}
-	\label{fig:task-groups}
-\end{figure}
-
-For groups at the lowest level, we chose the following task classes to be placed in those groups.
-Below, substitute each of \textit{Shape} and \textit{Color} for  \uX{} to obtain the task class.
-\begin{description}
-	\item[Basic:] \textit{Exist}\uX, \textit{Get}\uX{} and \textit{Exist} (5 task classes);
-	\item[Obj-Attr:] \emph{SimpleCompare}\uX{} and \textit{AndSimpleCompare}\uX\ (4 task classes);
-	\item[Compare:] \textit{Compare}\uX,  \textit{AndCompare}\uX{} \& \textit{Exist}\uX\textit{Of} (6 task classes);
-	\item[Spatial:] \textit{ExistSpace}, \textit{Exist}\uX\textit{Space}, and \textit{Get}\uX\textit{Space} (5 task classes);
-	\item[Cognitive:] \textit{ExistLastColorSameShape}, \textit{ExistLastShapeSameColor} and \textit{ExistLastObjectSameObject} (3 task classes)
-\end{description}
-
-We compared our results with the baseline model introduced in in~\cite{yang2018dataset}, the same paper as the COG dataset.
-The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.
-
-For the Canonical variant (top row), we achieve similar accuracies for the majority of tasks (with a total average accuracy of 98.0\%, compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for \textit{AndCompare} tasks.
-As these tasks focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in its external memory.
+For the Canonical variant (top row), we achieve similar accuracies for the majority of categories (with a total average accuracy of 98.0\%, compared to 97.6\% for the baseline model), with significant improvements (around 13 points) for the \textit{AndCompare} category.
+As these question categories focus on compositional questions referring to two objects, we hypothesize that our model achieves better accuracy due to its ability to selectively pick and store relevant objects from the past frames in its external memory.
 For the Hard variant, we achieve a total average accuracy of 96.1\% compared to 80.1\% for the baseline model, demonstrating that our model can adapt to larger number of frames and distractors.
-SAMNet improves upon the baseline model on all tasks, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex tasks (\textit{AndCompare}\uX, \textit{Compare}\uX).
+SAMNet improves upon the baseline model on all categories, with improvements varying from 0.5 to more than 30 points, especially outperforming in the most complex categories (\textit{AndCompare}\uX, \textit{Compare}\uX).
 
@@
 
-When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, matching the results observed in \cref{sec:clevr-baseline-compare}.
+When training and testing on CoGenT-A, SAMNet performs slightly worse than the other models, matching the results observed in \cref{sec:baseline-compare}.
 When zero-shot testing on CoGenT-B, all models show relatively good performance (around 75\%), which represents nonetheless a drop of 17 points with respect to CoGenT-A.

### 2020-03-05 Transfer_Learning/eccv_submission/experiments_reasoning_transfer.tex
Final submitted version

@@
 In the following experiments, we used CoGent-A only.
-Using the question groups defined by the authors, we organized training and testing splits with the goal of measuring whether mastering reasoning for one questions group can help learning others.
+Using the question categories defined by the authors, we organized training and testing splits with the goal of measuring whether mastering reasoning for one question category can help learning others.
 
@@
 
-We first trained a single SAMNet instance on CoGenT-A and measured its accuracy on each of the task group $t$ separately.
+We first trained a single SAMNet instance on CoGenT-A and measured its accuracy on each of the question category $t$ separately.
 Those results, indicated in \cref{fig:cogent_reasoning_transfer} as ``Train on All'', serve as baselines for the next two sets of experiments.
 
-We next trained and tested 5 SAMNet instances, each on a single task group $t$ (``Train on t only'').
-We observe significant accuracy drops (from 18 up to almost 35 points) in all task groups, except for \textit{Query Attribute}.
+We next trained and tested 5 SAMNet instances, each on a single question category $t$ (``Train on $t$ only'').
+We observe significant accuracy drops (from 18 up to almost 35 points) in all question categories, except for \textit{Query Attribute}.
 We hypothesize \textit{Query Attribute} requires mastering visual grounding and recognizing object attributes, as opposed to the other groups which may not enforce it.
@@
 
-Finally, we trained 5 SAMNet instances as follows: for each task group $t$ we trained a single instance on all tasks but $t$, and tested its performance on $t$ only.
+Finally, we trained 5 SAMNet instances as follows: for each category $t$, we trained a single instance on all categories but $t$, and tested its performance on
+category $t$ only.
 As expected, this setup appears challenging, causing severe performance drops, with accuracy on \textit{Count} and \textit{QueryAttribute} dropping to zero.
@@
 
-%Besides, the zero accuracy on \textit{Count} can also be explained by the fact that it results from the need of totally different reasoning leading to the answer.
-%The \textit{QueryAttribute} latter is more interesting, as when mastering e.g.
-\textit{Exist} of  \textit{CompareAttribute} the model \textit{had} to develop some kind of understanding object attributes.
-%Still, this result once again suggests that the model learned joint representation of object attributes and struggle with disentangling them without being explicitly trained on task facilitationg that (like the  \textit{QueryAttribute}).
-
-% An additional set of experiments, for which results are available in the supplementary material, fine-tune the model trained on all tasks on each task $t$ respectively.
-%Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks.
-Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.
-
 \subsection{Reasoning transfer in COG Canonical}
 \label{sec:reasoning-transfer-cog}
-In order to further investigate whether reasoning transfer is effective in leveraging information gained by training a task family at a higher level of the hierarchy, we also conducted a set of experiments using the Canonical variant of COG.
+In order to further investigate whether reasoning transfer is effective in leveraging information gained by training a question group at a higher level of the hierarchy, we also conducted a set of experiments using the Canonical variant of COG.
 The order of the performed experiments is analogical to the one in the previous section.
 The first column (\cref{fig:cog_reasoning_transfer}, ``Train on All'') is taken as a reference, i.e.
-we train a single SAMNet instance on all tasks and test on each of the five task groups from the task hierarchy presented in \cref{fig:task-groups}.
-Please note that these results are weighted averages of the accuracies of our model on the Canonical variant tasks (\cref{fig:samnet_cog_detailed}).
+we train a single SAMNet instance on all questions and test on each of the five question groups from the hierarchy shown in~\cref{fig:question-groups}.
+Note that these results are weighted averages of accuracies of our model on the Canonical variant (\cref{fig:samnet_cog_detailed}).
 
@@
 
-Next, we experimented with the ``Train on t only'' setup, i.e. training and testing each of 5 SAMNet instances on a single task group $t$ (i.e. the leaves of the proposed hierarchy).
+Next, we experimented with the ``Train on $t$ only'' setup, i.e. training and testing each of 5 SAMNet instances on a single question group $t$ (i.e. the leaves of the proposed hierarchy).
 For \textit{Basic}, \textit{Spatial} and \textit{Obj-Attr}, the accuracy is matching the reference (``Train on All''), suggesting that each group contains sufficient information for developing all necessary skills.
-Therefore, models trained on these groups may not benefit from any additional training on other task groups.
+Therefore, models trained on these groups may not benefit from any additional training on other question groups.
 However, accuracy on \textit{Compary} and \textit{Cognitive} dropped, suggesting the contrary.
 
-Therefore, we have performed a final set of experiments (``Train on Group A/B''), where we trained two SAMNet instances: a) trained on all tasks from \textit{Group A} and tested on each task from the lowest groups (i.e.
-\textit{Basic}, \textit{Obj-Attr} and \textit{Compare}) separately; b) trained on all tasks from \textit{Group B} and tested separately on \textit{Spatial} and \textit{Cognitive}.
-As expected, training on the other tasks from \textit{Group A} enabled the model to significantly improve on the \textit{Compare} task (from 58.6\% to 92.3\%).
+Therefore, we performed a final set of experiments (``Train on Group A/B''), where we trained two SAMNet instances: a) trained on all questions from \textit{Group A} and tested on each of the lowest groups below \textit{Group A}, i.e.
+\textit{Basic}, \textit{Obj-Attr} and \textit{Compare}, separately; b) trained on all questions from \textit{Group B} and tested separately on \textit{Spatial} and \textit{Cognitive} groups.
+As expected, training on the other questions from \textit{Group A} enabled the model to significantly improve on the \textit{Compare} category (from 58.6\% to 92.3\%).
 A similar improvement (from 68.8\% to 97.1\%) was observed in the second experiment, when trained on \textit{Group B} and tested on \textit{Cognitive}.
-Moreover, the achieved accuracy is in fact higher by 1.4 point than the one achieved when training on all tasks (95.7\%).
-This suggests the model may have lacked capacity to master questions from all tasks and that training on a smaller subset allowed better performance on this subset.
-Finally, we can interestingly note for \textit{Obj-Attr} and \textit{Spatial} that training on the group A/B does not appear to help.
-When comparing with ``Train on t only'', we observe slight accuracy drops (around 0.3-0.5 point).
+Moreover, the achieved accuracy is in fact higher by 1.4 point than the one achieved when training on all questions (95.7\%).
+This suggests the model may have lacked capacity to master questions from all questions and that training on a smaller subset allowed better performance on this subset.
+Finally, we can interestingly note for \textit{Obj-Attr} and \textit{Spatial} that training on the Group A/B does not appear to help.
+When comparing with ``Train on $t$ only'', we observe slight accuracy drops (around 0.3-0.5 point).
 Understanding this phenomenon warrants further investigations on the dependencies between the reasoning required by the particular questions and the transferred reasoning.
-
-%With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
-%To further emphasize this behavior, notice that just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%.
-%In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
-% Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there is a slight loss incurred by including everything.
-As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%).
-To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.

### 2020-03-05 Transfer_Learning/eccv_submission/transfer_learning.tex
Final submitted version

@@
 A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a probability distribution on $\cX$.
-For visual reasoning problems considered in this paper,
-$\cX$ will consist of purely visual inputs, i.e., either images or videos in some cases, or
-a combination of both visual inputs and questions in other cases.
+For visual reasoning problems considered in this paper, the feature space
+$\cX$ is some appropriate subset of the Cartesian product of visual inputs and questions.
 A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function.
-When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the
-question\footnote{% 
+For visual reasoning, the task is simply to answer the
+given question on the given visual input\footnote{% 
 	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas typical video answering datasets only require a single answer for the entire video.}.
-If the domain elements consist of just the visual inputs, then the task is further parameterized the question so that each question
-defines a separate task.
 
@@
 In this paper, we study the setting of \emph{domain adaptation}
-where $\cT_S \ne \cT_T$ and $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the distributions $P_S$ and $P_T$ are different.
+where $\cT_S = \cT_T$ and $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the distributions $P_S$ and $P_T$ are different.
 
-\Cref{defn:transfer} is quite general but does not give a nuanced view of different aspects of visual reasoning.
+\Cref{defn:transfer} is quite general but does not give a nuanced view of 
+the different aspects of visual reasoning.
 As mentioned in the introduction, one setting is the case of static images,
@@
 comparison of objects, or existence of objects with certain features etc.
-This entails studying transfer learning in specific settings.
+This motivates studying transfer learning for visual reasoning using a more detailed approach.
 
@@
 
-We now formally define 3 kinds of transfer learning problems, namely,
-\emph{feature transfer}, \emph{temporal transfer},
-and \emph{reasoning transfer}.
+We now formally define 3 kinds of transfer learning problems for visual reasoning, 
+namely, \emph{feature transfer}, \emph{temporal transfer}, and \emph{reasoning transfer}.
 These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR using dataset variants CoGenT-A and CoGenT-B, and COG using two dataset types: canonical and hard.
@@
 Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.
+The feature space is $\cQ \times \cV$ and the task is to answer
+the question $q \in \cQ$ on visual input $v \in \cV$.
+The output set $\cY$ is the union of legitimate answers
+over all questions in $\cQ$.
 \begin{description}
 	%\compresslist % used to reduce spacing
-	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
-	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
-	over all questions in $\cQ$.
-	The distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
+	\item[Feature Transfer:] In this setting of domain adaptation, 
+	the distributions $P_S$ and $P_T$ of the source and target, respectively, differ in the feature attributes such as shape, color, and size, or their combinations
 	thereof.
@@
 
-	\item[Temporal Transfer:] This is again similar to feature transfer in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
-	and there is a single task.	The key difference is that we introduce a complexity measure $C(q,v)$ that reflects the ease or difficulty of answering question $q$ on visual input $v$. 
+	\item[Temporal Transfer:] Here we introduce a complexity measure $C(q,v)$ that reflects the ease or difficulty of answering question $q$ on 
+	visual input $v$ that takes the temporal aspect of reasoning into account.
 	For any $(q_S,v_S)$ and $(q_T,v_T)$ in the support of $P_S$ and $P_T$ respectively, we require that $C(q_S,v_S)$ is strictly less than $C(q_T,v_T)$.
@@
 	\item[Reasoning Transfer:]
-	Here, we investigate whether reasoning processes can be transferred in the setting where questions in the source and target domain belong to different categories.
-	A \emph{task family} is defined by a fixing subset of $\cQ$ that share common traits.
-	\Cref{fig:taskonomy} shows representative questions for two task families: \textit{CompareColor} and \textit{AndCompareColor}.
-	Given a fixed global distribution on $\cQ \times \cV$, this induces a marginal distribution for each task family.
-	Let $\cF_S$ be the source task family and $\cF_T$ be the target task family.
-	In typical cases of transfer learning, $\cF_S$ and $\cF_T$ will involve disjoint sets of tasks and therefore, the support of $P_S$ and $P_T$ of the induced distribution on $\cQ \times \cV$ will also be disjoint.
-	In such cases, transfer learning is most effective when the two categories share common attributes in the reasoning process.
-This is evident in the case of \textit{CompareColor} and \textit{AndCompareColor} where the latter task, despite being complex, involves reasoning elements that can be found in the former task.
+	Here, we investigate whether the reasoning processes can be transferred in the setting where questions in the source and target domain belong to different categories.
+	Fix a subset $\cQ' \subseteq \cQ$ of questions sharing a common structure.
+	\Cref{fig:taskonomy} shows representative questions for two subsets with  self-explanatory names: \textit{CompareColor} and \textit{AndCompareColor}.
+	Given a fixed global distribution on $\cQ \times \cV$, observe that
+	$\cQ'$ induces a conditional distribution on $\cQ \times \cV$.
+	Let $\cQ_S$ and $\cQ_T$ be the source and target questions, respectively; typically, $\cQ_S$ and $\cQ_T$ will be disjoint, therefore, this also holds for the support of $P_S$ and $P_T$ on the induced distribution.
+	Transfer learning in this setting is most effective when the source and target questions
+	share common attributes in the reasoning process.
+This is evidently true for \textit{CompareColor} and the more complex \textit{AndCompareColor}; the latter category involves reasoning elements that can be found in the former category.
 The effectiveness of reasoning transfer with respect to various combinations of source-target pairs is thoroughly investigated in~\cref{sec:reasoning-transfer-clevr} using the CoGenT-A variant of CLEVR and in~\cref{sec:reasoning-transfer-cog} using the COG canonical dataset.

### 2020-03-12 Transfer_Learning/eccv_submission/appendix.tex
Added SAM Cell flow diagram with description

--- 2019-11-22 Transfer_Learning/cvpr_submission/appendix.tex
@@
+\section{SAMCell Data Flow}
+\label{sec:samcell-detail}
+
+The diagram in~\Cref{fig:samcell} shows the various modules of 
+SAM Cell and describes the flow of information between them.
+In the figure, the gray box on the left shows SAM Cell processing the $k$-th frame of the video, whose feature map equals $F_k$, for $T$ reasoning steps.
+The contextual words $\vec{cw}$ and question embedding $\vec{q}$ form the remaining
+inputs to SAM Cell.
+The state of memory (contents) at the beginning of this reasoning process is denoted by $M_0$.
+This is updated for each of the $T$ reasoning steps along with the various recurrent states of SAM Cell, namely, $\vec{wh}_t$, $\vec{c}_t$ and $\vec{so}_t$.
+The gray box on the right details what happens across the various modules
+during a single reasoning step $t$.
+The main document describes the role played by each tensor shown going between
+various modules within that box.
+\begin{figure*}[hbtp]
+	\centering
+	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
+	\caption{Archirecture of SAM Cell.}
+	\label{fig:samcell}
+\end{figure*}
+
+\clearpage
+
 \section{Datasets: CLEVR-CoGenT and COG}
@@
 	\item Test set of 15,000 images and 149,992 questions in Condition B (without answers),
-	\item Scene graphs and functional programs for all training/validation images/questions.
+	\item Scene graphs and functional programs for all training / validation images and questions.
 \end{itemize}
@@
 	\centering
-	\begin{adjustbox}{width=\columnwidth}
+	\begin{adjustbox}{width=\textwidth}
 	\begin{tabular}{c c c c c c c }\toprule
